### 2019-03-26 Variable creation.Rmd
added stuff

---
title: "Variable creation ObjectInAction"
author: "Kat Kyuchukova"
date: "11/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load packages
```{r}
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
select <- dplyr::select

#set working directory
setwd("/Users/katerinakyuchukova/Downloads/kat/")
```

Load data
```{r}
#clark
clark_measures <- read_spss("Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

#smith
smith <- read_spss("College_Relationship_Dyadic_September_14_2018_12_17.sav")

clark_sentences <- read.csv("sexist sentences/coded_sentences.csv")

#trigrams
trigram_check <- read.csv("Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
```

Clark Scale Scores--creating scale scores for the Clark data.
```{r}
#Social Physique Anxiety
clark_measures <- clark_measures %>%
  #reverse code physical anxiety variable
  mutate(physanx5.r = (min(physanx_5, na.rm = TRUE) + max(physanx_5, na.rm = TRUE) - physanx_5),
         #get average for scale score
         physanx = (physanx_1 +physanx_2 +physanx_3+physanx_4+physanx5.r+physanx_6)/6)

#SOO -- subtract internal SOO from external SOO
clark_measures$extSOO <- rowMeans(dplyr::select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE) #get average

clark_measures$intSOO <- rowMeans(dplyr::select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE) #get average

clark_measures$a2pSOO <- clark_measures$extSOO - clark_measures$intSOO #subtract internal from external

#Meta SOO--subtract internal from external
clark_measures$extmetaSOO <- rowMeans(dplyr::select(clark_measures, metaint_1, metaint_2, metaint_5, metaint_6, metaint_10), na.rm=TRUE)

clark_measures$intmetaSOO <- rowMeans(dplyr::select(clark_measures, metaint_3, metaint_4, metaint_7, metaint_8, metaint_9, metaint_11, metaint_12), na.rm=TRUE)

clark_measures$metaSOO <- clark_measures$extmetaSOO - clark_measures$intmetaSOO

#Interaction Authenticity
clark_measures$authenticity <- rowMeans(dplyr::select(clark_measures, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))

#SSO--average of how body 1 and how body 2
clark_measures <- clark_measures %>%
  mutate(howbody_avg = (howbody_1+howbody_2)/2)

#Relationship Agency
clark_measures$relag <- rowMeans(dplyr::select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))

#Career Aspirations--reverse code 4, 7, and 10 and average with the rest
clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

clark_measures$careerasp <- rowMeans(dplyr::select(clark_measures, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))

#TSO--subtract internal from external, multiply by -1
clark_measures$funcTSO <- rowMeans(dplyr::select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9))
clark_measures$physTSO <- rowMeans(dplyr::select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10))

clark_measures$TSO <- clark_measures$physTSO - clark_measures$funcTSO
clark_measures$TSO <- clark_measures$TSO*(-1)

#satisfaction--reverse code negative variables and then average with the rest
clark_measures <- clark_measures %>%
  mutate(anxious.r = (min(inter_2, na.rm = TRUE) + max(inter_2, na.rm = TRUE) - inter_2)) %>%
  mutate(uncomfort.r = (min(inter_4, na.rm = TRUE) + max(inter_4, na.rm = TRUE) - inter_4)) %>%
  mutate(hostile.r = (min(inter_8, na.rm = TRUE) + max(inter_8, na.rm = TRUE) - inter_8)) %>%
  mutate(apprehen.r = (min(inter_11, na.rm = TRUE) + max(inter_11, na.rm = TRUE) - inter_11)) %>%
  mutate(aggressive.r = (min(inter_13, na.rm = TRUE) + max(inter_13, na.rm = TRUE) - inter_13))

clark_measures$satisfaction <- rowMeans(select(clark_measures, anxious.r, uncomfort.r, hostile.r, apprehen.r, aggressive.r, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_6), na.rm=TRUE)
```

SMITH SCALE SCORES
```{r}
smith <- smith %>%
  arrange(dyadID) %>%
  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) #filter out dyads with no data

#Social Physique Anxiety
smith <- smith %>%
  mutate(physanx5.r = (min(physanx_5, na.rm = TRUE) + max(physanx_5, na.rm = TRUE) - physanx_5),
         physanx = (physanx_1 +physanx_2 +physanx_3+physanx_4+physanx5.r+physanx_6)/6) #reverse code physical anxiety variable

#SOO
smith$extSOO <- rowMeans(dplyr::select(smith, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE)

smith$intSOO <- rowMeans(dplyr::select(smith, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE)

smith$a2pSOO <- smith$extSOO - smith$intSOO

#Meta SOO
smith$extmetaSOO <- rowMeans(dplyr::select(smith, metaint_1, metaint_2, metaint_5, metaint_6, metaint_10), na.rm=TRUE)

smith$intmetaSOO <- rowMeans(dplyr::select(smith, metaint_3, metaint_4, metaint_7, metaint_8, metaint_9, metaint_11, metaint_12), na.rm=TRUE)

smith$metaSOO <- smith$extmetaSOO - smith$intmetaSOO

#Interaction Authenticity
smith$authenticity <- rowMeans(dplyr::select(smith, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))

#SSO
smith <- smith %>%
  mutate(howbody_avg = (howbody_1+howbody_2)/2)

#Relationship Agency
smith$relag <- rowMeans(dplyr::select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))

#Career Aspirations
smith <- smith %>%
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

smith$careerasp <- rowMeans(dplyr::select(smith, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))

#TSO
smith$funcTSO <- rowMeans(dplyr::select(smith,tso_1, tso_2, tso_4, tso_7, tso_9))
smith$physTSO <- rowMeans(dplyr::select(smith, tso_3, tso_5, tso_6, tso_8, tso_10))

smith$TSO <- smith$physTSO-smith$funcTSO
smith$TSO <- smith$TSO*-1

#satisfaction--reverse code negative variables and then average with the rest
smith <- smith %>%
  mutate(anxious.r = (min(inter_2, na.rm = TRUE) + max(inter_2, na.rm = TRUE) - inter_2)) %>%
  mutate(uncomfort.r = (min(inter_4, na.rm = TRUE) + max(inter_4, na.rm = TRUE) - inter_4)) %>%
  mutate(hostile.r = (min(inter_8, na.rm = TRUE) + max(inter_8, na.rm = TRUE) - inter_8)) %>%
  mutate(apprehen.r = (min(inter_11, na.rm = TRUE) + max(inter_11, na.rm = TRUE) - inter_11)) %>%
  mutate(aggressive.r = (min(inter_13, na.rm = TRUE) + max(inter_13, na.rm = TRUE) - inter_13))

smith$satisfaction <- rowMeans(select(smith, anxious.r, uncomfort.r, hostile.r, apprehen.r, aggressive.r, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_6), na.rm=TRUE)
```

Trigrams
```{r}
###Clark
#Eliminate unnecessary columns
trigram_check <- trigram_check[,1:8]

#correct dummy variable to account for the correct trigrams that excel missed
trigram_check <- trigram_check %>%
  mutate(trigram_correct = ifelse(accurate.=="yes", Correct...1.0., 1))

#create a correct trigram score for each participant
trigram_clark <- trigram_check %>%
  group_by(partID) %>%
  summarise(trigram_score = sum(trigram_correct)) %>%
  dplyr::select(partID, trigram_score)

#merge trigram data with big clark data file
clark <- merge(x=clark_measures, y=trigram_clark, by="partID", all.x=TRUE)
```

```{r}
###SMITH
#select only trigram related variables
smith_trigrams <- smith %>%
  dplyr::select(partID, dyadID, rat1_1.0, rat2_1.0,rat3_1.0, rat4_1.0,rat5_1.0, rat6_1.0, rat7_1.0, rat8_1.0, rat9_1.0, rat10_1) %>%
  arrange(dyadID, partID)

smith_trigrams_long <- gather(smith_trigrams, trigram, response, rat1_1.0:rat10_1)

#change trigram from generic name to the specific trigram
smith_trigrams_long <- smith_trigrams_long %>%
  mutate(trigram = ifelse(trigram=="rat1_1.0", "QUACK:POND:WADDLE",
                          ifelse(trigram=="rat2_1.0", "ATHLETES:WEB:RABBIT",
                                 ifelse(trigram=="rat3_1.0", "HONEY:SWARM:STING",
                                        ifelse(trigram=="rat4_1.0", "MATCHES:SMOKE:BUSH",
                                               ifelse(trigram=="rat5_1.0", "CHOCOLATE:FORTUNE:TIN",
                                                      ifelse(trigram=="rat6_1.0", "CURIOSITY:NAP:WHISKERS",
                                                             ifelse(trigram=="rat7_1.0", "STALK:TRAINER:KING",
                                                                    ifelse(trigram=="rat8_1.0", "SURPRISE:LINE:BIRTHDAY",
                                                                           ifelse(trigram=="rat9_1.0", "RED:GO:CAR", 
                                                                                  ifelse(trigram=="rat10_1", "MOUSE : SHARP : BLUE", NA)))))))))))

#create a correct response column
smith_trigrams_long <- smith_trigrams_long %>%
  mutate(correct_response=ifelse(trigram=="QUACK:POND:WADDLE", "Duck",
                          ifelse(trigram=="ATHLETES:WEB:RABBIT", "Foot",
                                 ifelse(trigram=="HONEY:SWARM:STING","Bee",
                                        ifelse(trigram=="MATCHES:SMOKE:BUSH", "Fire", 
                                               ifelse(trigram=="CHOCOLATE:FORTUNE:TIN", "Cookie",
                                                      ifelse(trigram=="CURIOSITY:NAP:WHISKERS","Cat",
                                                             ifelse(trigram=="STALK:TRAINER:KING","Lion",
                                                                    ifelse(trigram=="SURPRISE:LINE:BIRTHDAY", "Party",
                                                                           ifelse(trigram=="RED:GO:CAR", "Stop",
                                                                                  ifelse(trigram=="MOUSE : SHARP : BLUE", "Cheese", NA))))))))))) %>%
  arrange(partID, dyadID)

smith_trigrams_long <- smith_trigrams_long[,c(1,2,3,5,4)]

##Write out file to grade
#write.csv(smith_trigrams_long, "/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)

#Read in graded trigram file
smith_trigrams_graded <- read.csv("Smith College Relationships Data/trigrams_graded.csv")

#Summarize a final correct trigram
smith_triscore <- smith_trigrams_graded %>%
  group_by(partID, dyadID) %>%
  summarise(trigram_score=sum(final_correct))%>%
  dplyr::select(partID, dyadID, trigram_score)

#Merge with big smith data
smith <- merge(x=smith, y=smith_triscore, x.all=TRUE)
```

sexist sentences
```{r}
#Calculate ICC score to see if we can average
clark_sentences <- clark_sentences[,1:8]

clark_sentences <- clark_sentences %>%
  filter(!is.na(dyadID))

clark_sentences <- na.omit(clark_sentences)
clark_icc <- clark_sentences %>%
  select(Hannah, Jennie, Amelia)

icc(clark_icc, model="twoway", unit="average")

#Remove sentence 4
clark_sentences <- clark_sentences %>%
  filter(Sentence!=4)

#ICC is good enough to get an average

#Total sentence average
clark_sentence_avg <- clark_sentences %>%
  mutate(sexism=(Hannah+Jennie+Amelia)/3) %>%
  group_by(partID) %>%
  summarise(avg_sexism = mean(sexism)) %>%
  select(partID, avg_sexism)

#sentence average with just the logel sentences
clark_logel <- clark_sentences %>%
  filter(Sentence==3|Sentence==5|Sentence==6) %>%
  mutate(sexism=(Hannah+Jennie+Amelia)/3) %>%
  group_by(partID) %>%
  summarise(sexism_logel = mean(sexism)) %>%
  select(partID, sexism_logel)

#Merge together 
clark_sexism <- merge(x=clark, y=clark_sentence_avg, by="partID", all.x=TRUE)
clark_final <- merge (x=clark_sexism, y=clark_logel, by="partID", all.x=TRUE)
```

```{r}
#Smith

#Creating sexist sentence file
smith$dyadID <- as.numeric(smith$dyadID)
smith$partID <- as.numeric(smith$partID)
smith_sentences_long <- smith %>%
  #remove dyads with no data
  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) %>%
  #select just sexism related variables
  select(partID, dyadID, sexismpre_1:sexismpre_8) %>%
  arrange(dyadID)

#make data long
smith_sentences_long <- gather(smith_sentences_long, sentence, target, sexismpre_1:sexismpre_8)

#create a column with the actual sentence as well as a sentence number column
smith_sentences_long <- smith_sentences_long %>%
  mutate(stem=ifelse(sentence=="sexismpre_1", "Linda swatted at the flies", 
                     ifelse(sentence=="sexismpre_2", "Helen crammed for the test",
                            ifelse(sentence=="sexismpre_3", "Shirley asked for help getting home",
                                   ifelse(sentence=="sexismpre_4", "Sam read the newspaper",
                                          ifelse(sentence=="sexismpre_5", "Jenny went home to cook dinner",
                                                 ifelse(sentence=="sexismpre_6", "Katherine baby-sat the neighbor's kids",
                                                        ifelse(sentence=="sexismpre_7", "Tom bottle fed the baby",
                                                               ifelse(sentence=="sexismpre_8", "Bert changed the oil", NA))))))))) %>%
    mutate(sentence=ifelse(sentence=="sexismpre_1", 1, 
                     ifelse(sentence=="sexismpre_2", 2,
                            ifelse(sentence=="sexismpre_3", 3,
                                   ifelse(sentence=="sexismpre_4", 4,
                                          ifelse(sentence=="sexismpre_5", 5,
                                                 ifelse(sentence=="sexismpre_6", 6,
                                                        ifelse(sentence=="sexismpre_7", 7,
                                                               ifelse(sentence=="sexismpre_8", 8, NA)))))))))

#change order of sentences
smith_sentences_long <- smith_sentences_long[,c(1,2,3,5,4)]

#remove rows with no target data
smith_sentences_long <- smith_sentences_long %>%
  filter(target!="") %>%
  arrange(dyadID, partID)

#Write out csv
#write.csv(smith_sentences_long, "/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)

#Read in coded sentences, code correlations
kat_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_recode.csv")

xinyu_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_recode.csv")

coded_sentences <- merge(x=kat_codes, y=xinyu_codes, all.x = TRUE)

smith_icc <- coded_sentences %>%
  #remove sentence 4
  filter(sentence!=4)

icc(smith_icc, model="twoway", unit="average")

#making average file
#all sentenes (minus 4)
smith_sentence_avg <- coded_sentences %>%
  mutate(sexism=(katscore2+Xinyu)/2) %>%
  group_by(partID) %>%
  summarise(avg_sexism = mean(sexism)) %>%
  select(partID, avg_sexism)

#just logel sentences
smith_logel <- coded_sentences %>%
  filter(sentence==3|sentence==5|sentence==6) %>%
  mutate(sexism=(katscore2+Xinyu)/2) %>%
  group_by(partID) %>%
  summarise(sexism_logel = mean(sexism)) %>%
  select(partID, sexism_logel)

#merge data
smith_sexism <- merge(x=smith, y=smith_sentence_avg, by="partID", all.x=TRUE)
smith_final <- merge (x=smith_sexism, y=smith_logel, by="partID", all.x=TRUE)
```

Write out cleaned data!
```{r}
write.csv(smith_final, "/Users/katerinakyuchukova/Desktop/ObjectInAction/Cleaned data/smith_final.csv" )
write.csv(clark_final, "/Users/katerinakyuchukova/Desktop/ObjectInAction/Cleaned data/clark_final.csv")
```

### 2019-03-26 full analysis file.Rmd
added a file

---
title: "Objectification Special Studies Analysis"
author: "Kat Kyuchukova"
date: "9/18/2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r}
library(nlme)
library(haven)
library(devtools)
#install_github("RandiLGarcia/dyadr")
#library(dyadr)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
library(lavaan)
select <- dplyr::select
```

Load data
```{r}
#clark
clark_measures <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

#smith
smith <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")

#sentence data
#clark_sentence_long1 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_long.sav")

#clark_sentence_wide1 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_wide.sav")

#clark_sentences_long2 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_long2.sav")

#clark_sentence_wide2 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_wide2.sav")

clark_sentences <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/coded_sentences.csv")

#trigrams
trigram_check <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
```

#looking at variables
```{r}
view <- variable_view(clark_measures)
glimpse(clark_measures)
glimpse(clark_pairwise)
names(clark_measures)

variable_view(clark_measures)

```

CLARK SCALE SCORES
```{r}
#Social Physique Anxiety
clark_measures <- clark_measures %>%
  mutate(physanx5.r = (min(physanx_5, na.rm = TRUE) + max(physanx_5, na.rm = TRUE) - physanx_5),
         physanx = (physanx_1 +physanx_2 +physanx_3+physanx_4+physanx5.r+physanx_6)/6)

#SOO
clark_measures$extSOO <- rowMeans(dplyr::select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE)

clark_measures$intSOO <- rowMeans(dplyr::select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE)

clark_measures$a2pSOO <- clark_measures$extSOO - clark_measures$intSOO

psych::alpha(select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE)

psych::alpha(select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE)

#Meta SOO
clark_measures$extmetaSOO <- rowMeans(dplyr::select(clark_measures, metaint_1, metaint_2, metaint_5, metaint_6, metaint_10), na.rm=TRUE)

clark_measures$intmetaSOO <- rowMeans(dplyr::select(clark_measures, metaint_3, metaint_4, metaint_7, metaint_8, metaint_9, metaint_11, metaint_12), na.rm=TRUE)

clark_measures$metaSOO <- clark_measures$extmetaSOO - clark_measures$intmetaSOO

#Interaction Authenticity
clark_measures$authenticity <- rowMeans(dplyr::select(clark_measures, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))

psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))

#SSO
clark_measures <- clark_measures %>%
  mutate(howbody_avg = (howbody_1+howbody_2)/2)

#Relationship Agency
clark_measures$relag <- rowMeans(dplyr::select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))

psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))

#Career Aspirations
clark_measures <- clark_measures %>%
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

clark_measures$careerasp <- rowMeans(dplyr::select(clark_measures, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))

psych::alpha(select(clark_measures, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))

#TSO
clark_measures$funcTSO <- rowMeans(dplyr::select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9))
clark_measures$physTSO <- rowMeans(dplyr::select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10))

clark_measures$TSO <- clark_measures$physTSO - clark_measures$funcTSO
clark_measures$TSO <- clark_measures$TSO*(-1)

#satisfaction--reverse code negative variables and then average with the rest
clark_measures <- clark_measures %>%
  mutate(anxious.r = (min(inter_2, na.rm = TRUE) + max(inter_2, na.rm = TRUE) - inter_2)) %>%
  mutate(uncomfort.r = (min(inter_4, na.rm = TRUE) + max(inter_4, na.rm = TRUE) - inter_4)) %>%
  mutate(hostile.r = (min(inter_8, na.rm = TRUE) + max(inter_8, na.rm = TRUE) - inter_8)) %>%
  mutate(apprehen.r = (min(inter_11, na.rm = TRUE) + max(inter_11, na.rm = TRUE) - inter_11)) %>%
  mutate(aggressive.r = (min(inter_13, na.rm = TRUE) + max(inter_13, na.rm = TRUE) - inter_13))

clark_measures$satisfaction <- rowMeans(select(clark_measures, anxious.r, uncomfort.r, hostile.r, apprehen.r, aggressive.r, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_6), na.rm=TRUE)
```

SMITH SCALE SCORES
```{r}
smith <- smith %>%
  arrange(dyadID) %>%
  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999)

#Social Physique Anxiety
smith <- smith %>%
  mutate(physanx5.r = (min(physanx_5, na.rm = TRUE) + max(physanx_5, na.rm = TRUE) - physanx_5),
         physanx = (physanx_1 +physanx_2 +physanx_3+physanx_4+physanx5.r+physanx_6)/6)

#SOO
smith$extSOO <- rowMeans(dplyr::select(smith, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE)

psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE)
smith$intSOO <- rowMeans(dplyr::select(smith, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE)

psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE)
smith$a2pSOO <- smith$extSOO - smith$intSOO

#Meta SOO
smith$extmetaSOO <- rowMeans(dplyr::select(smith, metaint_1, metaint_2, metaint_5, metaint_6, metaint_10), na.rm=TRUE)

smith$intmetaSOO <- rowMeans(dplyr::select(smith, metaint_3, metaint_4, metaint_7, metaint_8, metaint_9, metaint_11, metaint_12), na.rm=TRUE)

smith$metaSOO <- smith$extmetaSOO - smith$intmetaSOO

#Interaction Authenticity
smith$authenticity <- rowMeans(dplyr::select(smith, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))

psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))

#SSO
smith <- smith %>%
  mutate(howbody_avg = (howbody_1+howbody_2)/2)

#Relationship Agency
smith$relag <- rowMeans(dplyr::select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))

psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))

#Career Aspirations
smith <- smith %>%
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

smith$careerasp <- rowMeans(dplyr::select(smith, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))

psych::alpha(select(smith, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))

#TSO
smith$funcTSO <- rowMeans(dplyr::select(smith,tso_1, tso_2, tso_4, tso_7, tso_9))
smith$physTSO <- rowMeans(dplyr::select(smith, tso_3, tso_5, tso_6, tso_8, tso_10))

smith$TSO <- smith$physTSO-smith$funcTSO
smith$TSO <- smith$TSO*-1

#satisfaction--reverse code negative variables and then average with the rest
smith <- smith %>%
  mutate(anxious.r = (min(inter_2, na.rm = TRUE) + max(inter_2, na.rm = TRUE) - inter_2)) %>%
  mutate(uncomfort.r = (min(inter_4, na.rm = TRUE) + max(inter_4, na.rm = TRUE) - inter_4)) %>%
  mutate(hostile.r = (min(inter_8, na.rm = TRUE) + max(inter_8, na.rm = TRUE) - inter_8)) %>%
  mutate(apprehen.r = (min(inter_11, na.rm = TRUE) + max(inter_11, na.rm = TRUE) - inter_11)) %>%
  mutate(aggressive.r = (min(inter_13, na.rm = TRUE) + max(inter_13, na.rm = TRUE) - inter_13))

smith$satisfaction <- rowMeans(select(smith, anxious.r, uncomfort.r, hostile.r, apprehen.r, aggressive.r, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_6), na.rm=TRUE)
```

TRIGRAMS
```{r}

###CLARK
trigram_check <- trigram_check[,1:8]

trigram_check <- trigram_check %>%
  mutate(trigram_correct = ifelse(accurate.=="yes", Correct...1.0., 1))

trigram_clark <- trigram_check %>%
  group_by(partID) %>%
  summarise(trigram_score = sum(trigram_correct)) %>%
  dplyr::select(partID, trigram_score)

#merging
clark <- merge(x=clark_measures, y=trigram_clark, by="partID", all.x=TRUE)

###SMITH
smith_trigrams <- smith %>%
  dplyr::select(partID, dyadID, rat1_1.0, rat2_1.0,rat3_1.0, rat4_1.0,rat5_1.0, rat6_1.0, rat7_1.0, rat8_1.0, rat9_1.0, rat10_1) %>%
  arrange(dyadID, partID)

smith_trigrams_long <- gather(smith_trigrams, trigram, response, rat1_1.0:rat10_1)

smith_trigrams_long <- smith_trigrams_long %>%
  mutate(trigram = ifelse(trigram=="rat1_1.0", "QUACK:POND:WADDLE",
                          ifelse(trigram=="rat2_1.0", "ATHLETES:WEB:RABBIT",
                                 ifelse(trigram=="rat3_1.0", "HONEY:SWARM:STING",
                                        ifelse(trigram=="rat4_1.0", "MATCHES:SMOKE:BUSH",
                                               ifelse(trigram=="rat5_1.0", "CHOCOLATE:FORTUNE:TIN",
                                                      ifelse(trigram=="rat6_1.0", "CURIOSITY:NAP:WHISKERS",
                                                             ifelse(trigram=="rat7_1.0", "STALK:TRAINER:KING",
                                                                    ifelse(trigram=="rat8_1.0", "SURPRISE:LINE:BIRTHDAY",
                                                                           ifelse(trigram=="rat9_1.0", "RED:GO:CAR", 
                                                                                  ifelse(trigram=="rat10_1", "MOUSE : SHARP : BLUE", NA)))))))))))

smith_trigrams_long <- smith_trigrams_long %>%
  mutate(correct_response=ifelse(trigram=="QUACK:POND:WADDLE", "Duck",
                          ifelse(trigram=="ATHLETES:WEB:RABBIT", "Foot",
                                 ifelse(trigram=="HONEY:SWARM:STING","Bee",
                                        ifelse(trigram=="MATCHES:SMOKE:BUSH", "Fire", 
                                               ifelse(trigram=="CHOCOLATE:FORTUNE:TIN", "Cookie",
                                                      ifelse(trigram=="CURIOSITY:NAP:WHISKERS","Cat",
                                                             ifelse(trigram=="STALK:TRAINER:KING","Lion",
                                                                    ifelse(trigram=="SURPRISE:LINE:BIRTHDAY", "Party",
                                                                           ifelse(trigram=="RED:GO:CAR", "Stop",
                                                                                  ifelse(trigram=="MOUSE : SHARP : BLUE", "Cheese", NA))))))))))) %>%
  arrange(partID, dyadID)

smith_trigrams_long <- smith_trigrams_long[,c(1,2,3,5,4)]

#write.csv(smith_trigrams_long, "/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)

smith_trigrams_graded <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/trigrams_graded.csv")

smith_triscore <- smith_trigrams_graded %>%
  group_by(partID, dyadID) %>%
  summarise(trigram_score=sum(final_correct))%>%
  dplyr::select(partID, dyadID, trigram_score)

smith <- merge(x=smith, y=smith_triscore, x.all=TRUE)
```
sexist sentences
```{r}
#ICC
clark_sentences <- clark_sentences[,1:8]

clark_sentences <- clark_sentences %>%
  filter(!is.na(dyadID))

clark_sentences <- na.omit(clark_sentences)
clark_icc <- clark_sentences %>%
  select(Hannah, Jennie, Amelia)

icc(clark_icc, model="twoway", unit="average")

#per sentence
clark_icc1 <- clark_sentences %>%
  filter(Sentence==1) %>%
  select(Hannah, Jennie, Amelia)

clark_icc2 <- clark_sentences %>%
  filter(Sentence==2) %>%
  select(Hannah, Jennie, Amelia)

clark_icc3 <- clark_sentences %>%
  filter(Sentence==3) %>%
  select(Hannah, Jennie, Amelia)

clark_icc4 <- clark_sentences %>%
  filter(Sentence==4) %>%
  select(Hannah, Jennie, Amelia)

clark_icc5 <- clark_sentences %>%
  filter(Sentence==5) %>%
  select(Hannah, Jennie, Amelia)

clark_icc6 <- clark_sentences %>%
  filter(Sentence==6) %>%
  select(Hannah, Jennie, Amelia)

clark_icc7 <- clark_sentences %>%
  filter(Sentence==7) %>%
  select(Hannah, Jennie, Amelia)

clark_icc8 <- clark_sentences %>%
  filter(Sentence==8) %>%
  select(Hannah, Jennie, Amelia)

icc(clark_icc1, model="twoway", unit="average")
icc(clark_icc2, model="twoway", unit="average")
icc(clark_icc3, model="twoway", unit="average")
icc(clark_icc4, model="twoway", unit="average")
icc(clark_icc5, model="twoway", unit="average")
icc(clark_icc6, model="twoway", unit="average")
icc(clark_icc7, model="twoway", unit="average")
icc(clark_icc8, model="twoway", unit="average")

clark_test <- clark_sentences %>%
  filter(Sentence!=4) %>%
  select(Hannah, Jennie, Amelia)

icc(clark_test, model="twoway", unit="average")

clark_sentences <- clark_sentences %>%
  filter(Sentence!=4)

#good enough to get an average??

clark_sentence_avg <- clark_sentences %>%
  mutate(sexism=(Hannah+Jennie+Amelia)/3) %>%
  group_by(partID) %>%
  summarise(avg_sexism = mean(sexism)) %>%
  select(partID, avg_sexism)

clark_logel <- clark_sentences %>%
  filter(Sentence==3|Sentence==5|Sentence==6) %>%
  mutate(sexism=(Hannah+Jennie+Amelia)/3) %>%
  group_by(partID) %>%
  summarise(sexism_logel = mean(sexism)) %>%
  select(partID, sexism_logel)

clark_sexism <- merge(x=clark, y=clark_sentence_avg, by="partID", all.x=TRUE)
clark_final <- merge (x=clark_sexism, y=clark_logel, by="partID", all.x=TRUE)

#Smith

#Creating sexist sentence file
smith$dyadID <- as.numeric(smith$dyadID)
smith$partID <- as.numeric(smith$partID)
smith_sentences_long <- smith %>%
  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) %>%
  select(partID, dyadID, sexismpre_1:sexismpre_8) %>%
  arrange(dyadID)

smith_sentences_long <- gather(smith_sentences_long, sentence, target, sexismpre_1:sexismpre_8)

smith_sentences_long <- smith_sentences_long %>%
  mutate(stem=ifelse(sentence=="sexismpre_1", "Linda swatted at the flies", 
                     ifelse(sentence=="sexismpre_2", "Helen crammed for the test",
                            ifelse(sentence=="sexismpre_3", "Shirley asked for help getting home",
                                   ifelse(sentence=="sexismpre_4", "Sam read the newspaper",
                                          ifelse(sentence=="sexismpre_5", "Jenny went home to cook dinner",
                                                 ifelse(sentence=="sexismpre_6", "Katherine baby-sat the neighbor's kids",
                                                        ifelse(sentence=="sexismpre_7", "Tom bottle fed the baby",
                                                               ifelse(sentence=="sexismpre_8", "Bert changed the oil", NA))))))))) %>%
    mutate(sentence=ifelse(sentence=="sexismpre_1", 1, 
                     ifelse(sentence=="sexismpre_2", 2,
                            ifelse(sentence=="sexismpre_3", 3,
                                   ifelse(sentence=="sexismpre_4", 4,
                                          ifelse(sentence=="sexismpre_5", 5,
                                                 ifelse(sentence=="sexismpre_6", 6,
                                                        ifelse(sentence=="sexismpre_7", 7,
                                                               ifelse(sentence=="sexismpre_8", 8, NA)))))))))

smith_sentences_long <- smith_sentences_long[,c(1,2,3,5,4)]

smith_sentences_long <- smith_sentences_long %>%
  filter(target!="") %>%
  arrange(dyadID, partID)

#write.csv(smith_sentences_long, "/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)

#coding correlations
kat_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_sentences_coded.csv")

xinyu_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_sentences.csv")

coded_sentences <- merge(x=kat_codes, y=xinyu_codes, all.x = TRUE)

smith_icc <- coded_sentences %>%
  select(kat_score, Xinyu)

icc(smith_icc, model="twoway", unit="average")

##TAKE TWOOOO
kat_codes2 <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_recode.csv")

xinyu_codes2 <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_recode.csv")

coded_sentences2 <- merge(x=kat_codes2, y=xinyu_codes2, all.x = TRUE)

smith_icc2 <- coded_sentences2 %>%
  filter(sentence!=4)

icc(smith_icc2, model="twoway", unit="average")

#making average file
smith_sentence_avg <- coded_sentences2 %>%
  mutate(sexism=(katscore2+Xinyu)/2) %>%
  group_by(partID) %>%
  summarise(avg_sexism = mean(sexism)) %>%
  select(partID, avg_sexism)

smith_logel <- coded_sentences2 %>%
  filter(sentence==3|sentence==5|sentence==6) %>%
  mutate(sexism=(katscore2+Xinyu)/2) %>%
  group_by(partID) %>%
  summarise(sexism_logel = mean(sexism)) %>%
  select(partID, sexism_logel)

smith_sexism <- merge(x=smith, y=smith_sentence_avg, by="partID", all.x=TRUE)
smith_final <- merge (x=smith_sexism, y=smith_logel, by="partID", all.x=TRUE)

```

Making Pairwise
```{r}

#Clark

clark<- clark_final %>%
  filter(dyadID!=4, dyadID!=14, dyadID!=19) %>%
  arrange(dyadID) %>%
  mutate(person=rep(1:2, times=22)) %>%
  select(dyadID, person, partID, gender, age, race, sexor, physanx, a2pSOO, metaSOO, trigram_score, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel, satisfaction) %>%
  arrange(person)

tempA <- clark %>% 
  mutate(personE = ifelse(person == 1, -1, 1), 
         partnum = 1,
         person = ifelse(person == 1, "A", "P")) %>%
  gather(variable, value, partID:partnum)%>%
  unite(var_person, variable, person)%>%
  spread(var_person, value)

tempB <- clark %>% 
  mutate(personE = ifelse(person == 1, -1, 1), 
         partnum = 2,
         person = ifelse(person == 1, "P", "A")) %>%
  gather(variable, value, partID:partnum) %>%
  unite(var_person, variable, person) %>%
  spread(var_person, value)

clark_pair <- bind_rows(tempA, tempB) %>%
  arrange(dyadID)

rm(tempA, tempB)

head(clark_pair)

#Smith

#making these numeric
smith_final$dyadID <- as.numeric(smith_final$dyadID)
smith_final$partID <- as.numeric(smith_final$partID)

#checking weird dyads to see if there is post interaction information
smith_checK <- smith %>%
  filter(dyadID==16|is.na(dyadID)|dyadID==798797|dyadID==999|dyadID==999999|dyadID==9999)%>%
  arrange(dyadID) %>%
  select(dyadID, partID, otherint_1:otherint_12)

smith <- smith_final %>%
  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999, dyadID!=7) %>%
  arrange(dyadID) %>%
  mutate(person=rep(1:2, times=23),
         partID= ifelse(dyadID==31 & person==2, 83, partID),
         dyadID= ifelse(dyadID==2 & partID==4|partID==5, 1, dyadID)) %>%
  select(dyadID, person, partID, gender, age, race, sexor, physanx, a2pSOO, metaSOO, trigram_score, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel, satisfaction)  %>%
  arrange(person)

tempA <- smith %>% 
  mutate(personE = ifelse(person == 1, -1, 1), 
         partnum = 1,
         person = ifelse(person == 1, "A", "P")) %>%
  gather(variable, value, partID:partnum)%>%
  unite(var_person, variable, person) %>%
  spread(var_person, value)

tempB <- smith %>% 
  mutate(personE = ifelse(person == 1, -1, 1), 
         partnum = 2,
         person = ifelse(person == 1, "P", "A")) %>%
  gather(variable, value, partID:partnum) %>%
  unite(var_person, variable, person) %>%
  spread(var_person, value)

smith_pair <- bind_rows(tempA, tempB)

rm(tempA, tempB)

head(smith_pair)
```

Next steps: correlations, matrices etc
```{r}

#making shit numeric
ix <- 1:39
smith_pair[,ix] <- lapply(smith_pair[,ix], as.numeric)
clark_pair[,ix] <-lapply(clark_pair[,ix], as.numeric)

#same gender
samegender_clark <- clark_pair %>%
  filter(gender_A==gender_P)

samegender_smith <- smith_pair %>%
  filter(gender_A==gender_P)

samegender_smith[,ix] <- lapply(samegender_smith[,ix], as.numeric)
samegender_clark[,ix] <-lapply(samegender_clark[,ix], as.numeric)

corr.test(select(samegender_smith, physanx_A, a2pSOO_A, metaSOO_A, authenticity_A, howbody_avg_A, relag_A, careerasp_A, TSO_A, avg_sexism_A, sexism_logel_A))
corr.test(select(samegender_clark, physanx, a2pSOO, metaSOO, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel))

corr.test(select(samegender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
corr.test(select(diffgender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
corr.test(select(samegender_clark, authenticity_A, careerasp_A, relag_A))

diffgender_clark <- clark_pair %>%
  filter(gender_A!=gender_P)

#smith
corr.test(select(smith_final, physanx, a2pSOO, metaSOO, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel, howbody_1, howbody_2))

corr.test(select(smith_pair, physanx_A, a2pSOO_A, metaSOO_A, authenticity_A, howbody_avg_A, relag_A, careerasp_A, TSO_A, avg_sexism_A, sexism_logel_A))

corr.test(select(samegender_smith, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))

corr.test(select(smith_pair, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
corr.test(select(smith_pair, authenticity_A, careerasp_A, relag_A))

#clark
corr.test(select(clark_final, physanx, a2pSOO, metaSOO, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel, howbody_1, howbody_2))

corr.test(select(clark_pair, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
corr.test(select(clark_pair, authenticity_A, careerasp_A, relag_A))

#sexism histogram
#all gender
#ggplot(smith_final, aes(x=avg_sexism)) + geom_histogram(bins = 15)
#ggplot(clark_final, aes(x=avg_sexism)) + geom_histogram(bins=15)

#same

#A2p soo
#ggplot(smith_pair, aes(x=a2pSOO_A)) + geom_histogram(bins=15)
#ggplot(clark_pair, aes(x=a2pSOO_A)) + geom_histogram(bins=15)
#ggplot(samegender_smith, aes(x=a2pSOO_A)) + geom_histogram(bins=15)
#ggplot(samegender_clark, aes(x=a2pSOO_A)) + geom_histogram(bins=15)

#meta SOO
#ggplot(smith_pair, aes(x=metaSOO_A)) + geom_histogram(bins=15)
#ggplot(clark_pair, aes(x=metaSOO_A)) + geom_histogram(bins=15)
#ggplot(samegender_smith, aes(x=metaSOO_A)) + geom_histogram(bins=15)
#ggplot(samegender_clark, aes(x=metaSOO_A)) + geom_histogram(bins=15)

#TSO
# ggplot(smith_pair, aes(x=TSO_A)) + geom_histogram(bins=15)
# ggplot(clark_pair, aes(x=TSO_A)) + geom_histogram(bins=15)
# ggplot(samegender_smith, aes(x=TSO_A)) + geom_histogram(bins=15)
# ggplot(samegender_clark, aes(x=TSO_A)) + geom_histogram(bins=15)
# 
# #authenticity
# ggplot(smith_pair, aes(x=authenticity_A)) + geom_histogram(bins=10)
# ggplot(clark_pair, aes(x=authenticity_A)) + geom_histogram(bins=10)
# ggplot(samegender_smith, aes(x=TSO_A)) + geom_histogram(bins=15)
# ggplot(samegender_clark, aes(x=TSO_A)) + geom_histogram(bins=15)

#boxplots
smith_howbody <- smith_final %>%
  select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
  gather(variable, value, howbody_1:howbody_avg)

clark_howbody <- clark_final %>%
  select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
  gather(variable, value, howbody_1:howbody_avg)

smith_howbody$value <- as.numeric(smith_howbody$value)
clark_howbody$value <- as.numeric(clark_howbody$value)

# ggplot(smith_howbody, aes(x=variable, y=value)) + geom_boxplot()
# ggplot(clark_howbody, aes(x=variable, y=value)) + geom_boxplot()
# 
# ggplot(samegender_clark, aes(x=gender_A, y=a2pSOO_A)) + geom_boxplot()
# ggplot(samegender_clark, aes(x=gender_A, y=TSO_A)) + geom_boxplot()
# ggplot(clark_pair, aes(x=gender_A, y=TSO_A)) + geom_boxplot()

#howbody
corr.test(select(smith_final, howbody_1, howbody_2, howbody_3))
corr.test(select(clark_final, howbody_1, howbody_2, howbody_3))
psych::alpha(select(smith_final, howbody_1, howbody_2, howbody_3))
psych::alpha(select(clark_final, howbody_1, howbody_2, howbody_3))

# ggplot(smith_pair, aes(x=howbody_avg_A)) + geom_histogram(bins=15)
# ggplot(clark_pair, aes(x=howbody_avg_A)) + geom_histogram(bins=15)
# ggplot(samegender_smith, aes(x=howbody_avg_A)) + geom_histogram(bins=15) 
# ggplot(samegender_clark, aes(x=howbody_avg_A)) + geom_histogram(bins=15)

psych::alpha(select(smith_final, howbody_1, howbody_2, howbody_3))

test <- clark_measures[,140:150]
```

MODELING THE APIM
```{r}
#merging clark and smith same sex data
samegender_smith <- samegender_smith %>%
  mutate(smith_or_clark = "Smith",
         dyadID = dyadID + 100)

samegender_clark <- samegender_clark %>%
  mutate(smith_or_clark = "Clark")

clarksmith_same <- merge(x=samegender_smith, y=samegender_clark, all.x=TRUE, all.y=TRUE)

clarksmith_women <- clarksmith_same %>%
  filter(gender_A==2)

#indistinguishable dyads

apim <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + TSO_A*a2pSOO_P,
            data=clarksmith_same,
            correlation=corCompSymm(form=~1|dyadID),
            na.action = na.omit)
summary(apim)

apim_in_empty <- gls(satisfaction_A ~ 1,
                     data = clarksmith_same,
                     correlation = corCompSymm(form=~1|dyadID),
                     na.action = na.omit)
summary(apim_in_empty)

r2 <- 1-(apim$sigma^2/apim_in_empty$sigma^2)
r2
```

##Descriptive stats
```{r}
favstats(~TSO_A, data=clarksmith_women)
favstats(~a2pSOO_A, data=clarksmith_women)
favstats(~howbody_avg_A, data=clarksmith_women)
favstats(~relag_A, data=clarksmith_women)
favstats(~careerasp_A, data=clarksmith_women)
favstats(~authenticity_A, data=clarksmith_women)
favstats(~trigram_score_A, data=clarksmith_women)

corr.test(select(clarksmith_women, TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, relag_A, careerasp_A,  trigram_score_A, TSO_P, authenticity_P, a2pSOO_P, howbody_avg_P, relag_P, careerasp_P, trigram_score_P))
```

##Participant info
```{r}
clark_final$age <- as.numeric(clark_final$age)
smith_final$age <- as.numeric(smith_final$age)
favstats(~age, data=clark_final)
favstats(~age, data=smith_final)

favstats(~age_A, data=clarksmith_women)
tally(clarksmith_women$race_A==clarksmith_women$race_P)

psych::alpha(select(clarksmith_women, a2pSOO_A, a2pSOO_P))

tally(~race_A, data=clarksmith_women)
tally(~sexor_A, data=clarksmith_women)
tally(~gender_A, data=clarksmith_women)

table(clarksmith_women$race_A, clarksmith_women$race_P)

test <- clarksmith_women %>%
  filter(race_A==3, race_A!=race_P)

tally(~gender, data=clark)
tally(~gender, data=smith)

```

```{r}
#Running direct correlations
SSO_authenticity <- gls(howbody_avg_A~authenticity_A, data=clarksmith_women)
auth_RAT <- gls(authenticity_A~trigram_score_A, data=clarksmith_women, na.action=na.omit)
auth_ASP <- gls(authenticity_A ~ careerasp_A, data=clarksmith_women)
auth_relag <- gls(authenticity_A ~ relag_A, data=clarksmith_women)

SSO_RAT <- gls(howbody_avg_A~trigram_score_A, data=clarksmith_women, na.action=na.omit)

summary(SSO_authenticity)
summary(auth_ASP)
summary(auth_relag)
summary(auth_RAT)
summary(SSO_RAT)
```

PATH model
```{r}
dyad_cswomen <- clarksmith_women %>%
  mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
         TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
  filter(partnum_A==1)
```

```{r}
model <- '#####regressions 
howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P
howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A
authenticity_A ~ d*howbody_avg_A
authenticity_P ~ d*howbody_avg_P
trigram_score_A ~ e1*authenticity_A
careerasp_A ~ e2*authenticity_A
relag_A ~ e3*authenticity_A
trigram_score_P ~ e1*authenticity_P
careerasp_P ~ e2*authenticity_P
relag_P ~ e3*authenticity_P
######covariances
#endogenous
howbody_avg_A ~~ howbody_avg_P
authenticity_A ~~ authenticity_P
trigram_score_A ~~ trigram_score_P
careerasp_A ~~ careerasp_P
relag_A ~~ relag_P
trigram_score_A ~~ 0*careerasp_A
trigram_score_A ~~ 0*relag_A
trigram_score_A ~~ 0*careerasp_P
trigram_score_A ~~ 0*relag_P
careerasp_A ~~ 0*relag_A
careerasp_A ~~ 0*trigram_score_P
careerasp_A ~~ 0*relag_P
relag_A ~~ 0*trigram_score_P
relag_A ~~ 0*careerasp_P
trigram_score_P ~~ 0*careerasp_P
trigram_score_P ~~ 0*relag_P
careerasp_P ~~ 0*relag_P
#####variances
howbody_avg_A ~~ v1*howbody_avg_A
howbody_avg_P ~~ v1*howbody_avg_P
TSO_A ~~ v2*TSO_A
TSO_P ~~ v2*TSO_P
a2pSOO_A ~~ v3*a2pSOO_A
a2pSOO_P ~~ v3*a2pSOO_P
authenticity_A ~~ v4*authenticity_A
authenticity_P ~~ v4*authenticity_P
##endogenous intercepts
howbody_avg_A ~ i*1
howbody_avg_P ~ i*1
authenticity_A ~ i2*1
authenticity_P ~ i2*1
trigram_score_A ~ i3*1
trigram_score_P ~ i4*1
careerasp_A ~ i5*1
careerasp_P ~ i5*1
relag_A ~ i6*1
relag_P ~ i6*1
##exogenous means
TSO_A ~ m*1
TSO_P ~ m*1
a2pSOO_A ~ m2*1
a2pSOO_P ~ m2*1
TSO_P_SOO_A ~ m3*1
TSO_A_SOO_P ~ m3*1
## exogenous covariances
TSO_A_SOO_P ~~ c1*TSO_A
TSO_P_SOO_A ~~ c1*TSO_P
TSO_A_SOO_P ~~ c2*a2pSOO_P
TSO_P_SOO_A ~~ c2*a2pSOO_A
TSO_A ~~ c3*a2pSOO_P
TSO_P ~~ c3*a2pSOO_A
TSO_A ~~ c4*a2pSOO_A
TSO_P ~~ c4*a2pSOO_P
'
#hi
fit <- sem(model, data=dyad_cswomen)
summary(fit)
```

### 2019-03-26 full analysis file.Rmd
testing

@@
 '
-#hi
+
 fit <- sem(model, data=dyad_cswomen)

### 2019-03-26 full analysis file.Rmd
Fixed paths

@@
 #clark
-clark_measures <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/College_Relationship_Measures_1.sav")
-clark_pairwise <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")
+clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
+clark_pairwise <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")
 
 #smith
-smith <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")
+smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")
 
 #sentence data
-#clark_sentence_long1 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_long.sav")
 
-#clark_sentence_wide1 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_wide.sav")
-
-#clark_sentences_long2 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_long2.sav")
-
-#clark_sentence_wide2 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_wide2.sav")
-
-clark_sentences <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/coded_sentences.csv")
+clark_sentences <- read.csv("Raw data/Clark College Relationships Data/sexist sentences/coded_sentences.csv")
 
 #trigrams
-trigram_check <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
+trigram_check <- read.csv("Raw data/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
 ```
@@
 
-smith_trigrams_graded <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/trigrams_graded.csv")
+smith_trigrams_graded <- read.csv("Raw data/Smith College Relationships Data/trigrams_graded.csv")
 
@@
 #coding correlations
-kat_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_sentences_coded.csv")
+kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_sentences_coded.csv")
 
-xinyu_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_sentences.csv")
+xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_sentences.csv")
 
@@
 ##TAKE TWOOOO
-kat_codes2 <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_recode.csv")
+kat_codes2 <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")
 
-xinyu_codes2 <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_recode.csv")
+xinyu_codes2 <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")
 

### 2019-03-26 Final Manuscript.Rmd
trying papaja

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "Kat Kyuchukova"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Asha Hinson"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Smith College"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, include=FALSE}
x <- 7
```

hi I'm the number `r x`.

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-03-26 Final Manuscript.Rmd
added randi

@@
   - name          : "Asha Hinson"
+    affiliation   : "1"
+  - name          : "Randi L. Garcia"
     affiliation   : "1"

### 2019-03-26 Variable creation.Rmd
Fixed paths and other stuff

@@
 select <- dplyr::select
-
-#set working directory
-setwd("/Users/katerinakyuchukova/Downloads/kat/")
 ```
@@
 #clark
-clark_measures <- read_spss("Clark College Relationships Data/College_Relationship_Measures_1.sav")
-clark_pairwise <- read_spss("Clark College Relationships Data/College_Relationship_Pairwise_1.sav")
+clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
+clark_pairwise <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")
 
 #smith
-smith <- read_spss("College_Relationship_Dyadic_September_14_2018_12_17.sav")
+smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")
 
-clark_sentences <- read.csv("sexist sentences/coded_sentences.csv")
+clark_sentences <- read.csv("Raw data/Clark College Relationships Data/sexist sentences/coded_sentences.csv")
 
 #trigrams
-trigram_check <- read.csv("Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
+trigram_check <- read.csv("Raw data/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
 ```
@@
 ##Write out file to grade
-#write.csv(smith_trigrams_long, "/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)
+#write.csv(smith_trigrams_long, "Raw data/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)
 
@@
 #Write out csv
-#write.csv(smith_sentences_long, "/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)
+#write.csv(smith_sentences_long, "Raw data/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)
 
 #Read in coded sentences, code correlations
-kat_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_recode.csv")
+kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")
 
-xinyu_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_recode.csv")
+xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")
 
@@
 ```{r}
-write.csv(smith_final, "/Users/katerinakyuchukova/Desktop/ObjectInAction/Cleaned data/smith_final.csv" )
-write.csv(clark_final, "/Users/katerinakyuchukova/Desktop/ObjectInAction/Cleaned data/clark_final.csv")
+write.csv(smith_final, "ObjectInAction/Cleaned data/smith_final.csv" )
+write.csv(clark_final, "ObjectInAction/Cleaned data/clark_final.csv")
 ```

### 2019-03-26 full analysis file.Rmd
Fixed paths and other stuff

@@
 ```{r}
-view <- variable_view(clark_measures)
 glimpse(clark_measures)
@@
 names(clark_measures)
-
-variable_view(clark_measures)
-
 ```
@@
 
-#making shit numeric
+#making variables numeric
 ix <- 1:39
@@
 
-corr.test(select(samegender_smith, physanx_A, a2pSOO_A, metaSOO_A, authenticity_A, howbody_avg_A, relag_A, careerasp_A, TSO_A, avg_sexism_A, sexism_logel_A))
-corr.test(select(samegender_clark, physanx, a2pSOO, metaSOO, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel))
+#corr.test(select(samegender_smith, physanx_A, a2pSOO_A, metaSOO_A, authenticity_A, howbody_avg_A, relag_A, careerasp_A, TSO_A, avg_sexism_A, sexism_logel_A))
+#corr.test(select(samegender_clark, physanx, a2pSOO, metaSOO, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel))
 
-corr.test(select(samegender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
-corr.test(select(diffgender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
-corr.test(select(samegender_clark, authenticity_A, careerasp_A, relag_A))
+#corr.test(select(samegender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
+#corr.test(select(diffgender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
+#corr.test(select(samegender_clark, authenticity_A, careerasp_A, relag_A))
 
@@
 #boxplots
-smith_howbody <- smith_final %>%
-  select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
-  gather(variable, value, howbody_1:howbody_avg)
+#smith_howbody <- smith_final %>%
+  #select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
+  #gather(variable, value, howbody_1:howbody_avg)
 
-clark_howbody <- clark_final %>%
-  select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
-  gather(variable, value, howbody_1:howbody_avg)
+#clark_howbody <- clark_final %>%
+  #select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
+  #gather(variable, value, howbody_1:howbody_avg)
 
-smith_howbody$value <- as.numeric(smith_howbody$value)
-clark_howbody$value <- as.numeric(clark_howbody$value)
+#smith_howbody$value <- as.numeric(smith_howbody$value)
+#clark_howbody$value <- as.numeric(clark_howbody$value)
 

### 2019-04-01 Final Manuscript.Rmd
more testing!
Adding alphas to manuscript, fixing manuscript data file, other stuff!!

@@
 library("papaja")
+library(nlme)
+library(haven)
+library(devtools)
+library(psych)
+library(mosaic)
+library(tidyr)
+library(dplyr)
+library(irr)
+
+clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
+smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")
 ```
@@
 ```{r, include=FALSE}
-x <- 7
+#######Alphas
+
+###SOO
+
+#Clark
+#SOO
+clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10))$total[2]
+clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12))
+#Smith
+smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10))$total[2]
+smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
+
+##Interaction Authenticity
+#Clark
+clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))$total[2]
+#Smith
+smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))$total[2]
+
+##SSO
+#Clark
+clark_howbody_alpha <- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
+#Smith
+smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]
+
+##Relationship Agency
+#Clark
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))$total[2]
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))$total[2]
+
+##Career Aspirations
+#Clark
+clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
+  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
+         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
+         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
+
+clark_careerasp_alpha <- psych::alpha(select(clark_measures, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))$total[2]
+
+#Smith
+smith <- smith %>% #reverse code certain career aspiration variables
+  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
+         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
+         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
+
+smith_careerasp_alpha <- psych::alpha(select(smith, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))$total[2]
+
+###TSO
+#Clark--external and internal
+clark_funcTSO_alpha <- psych::alpha(select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9))$total[2]
+clark_physTSO_alpha <- psych::alpha(select(clark_measures,tso_3, tso_5, tso_6, tso_8, tso_10))$total[2]
+#Smith--external and internal
+smith_funcTSO_alpha <- psych::alpha(select(smith,tso_1, tso_2, tso_4, tso_7, tso_9))$total[2]
+smith_physTSO_alpha <- psych::alpha(select(smith,tso_3, tso_5, tso_6, tso_8, tso_10))$total[2]
 ```
-
-hi I'm the number `r x`.
 
@@
 ## Participants
+The data collected in this study sought to replicate Garcia et al.
+(2016), which sought to measure objectification in previously unacquainted male-female pairs.
+This data was given to us by Dr.
+Garcia, who collected data from both Smith College and Clark University.
+The data was ultimately merged and filtered to only include only self-identified female same-sex pairs from both schools.
+The two samples are often referred to below as Sample 1 (data from Clark University) and Sample 2 (data from Smith College).
+These participants were mostly first-year college students, with an average age of 18.85 years (SD=1.04).
+The sample was 48% White/European American, 9% Black/African-American, 28% Asian/Pacific Islander, 9% Latinx, and 5% mixed-race.
+There were eight White/White pairs and four same race racial minority pairs, for a total of twelve same-race pairs.
+The remaining twenty were mixed race pairs, of which fifteen were White/racial minority pairings and five were cross-racial minority group pairs.
+64% of the sample identified as heterosexual, and 23% identified as gay, lesbian or bisexual.
+The data is organized in a pairwise fashion such that each row corresponds to one participant in the study, and includes data for themselves and their partner.
+We would want to generalize these findings to general interactions between women.
 

### 2019-04-01 Variable creation.Rmd
Adding alphas to manuscript, fixing manuscript data file, other stuff!!

@@
 ```{r}
-#Social Physique Anxiety
-clark_measures <- clark_measures %>%
-  #reverse code physical anxiety variable
-  mutate(physanx5.r = (min(physanx_5, na.rm = TRUE) + max(physanx_5, na.rm = TRUE) - physanx_5),
-         #get average for scale score
-         physanx = (physanx_1 +physanx_2 +physanx_3+physanx_4+physanx5.r+physanx_6)/6)
-
 #SOO -- subtract internal SOO from external SOO
@@
 clark_measures$TSO <- clark_measures$TSO*(-1)
-
-#satisfaction--reverse code negative variables and then average with the rest
-clark_measures <- clark_measures %>%
-  mutate(anxious.r = (min(inter_2, na.rm = TRUE) + max(inter_2, na.rm = TRUE) - inter_2)) %>%
-  mutate(uncomfort.r = (min(inter_4, na.rm = TRUE) + max(inter_4, na.rm = TRUE) - inter_4)) %>%
-  mutate(hostile.r = (min(inter_8, na.rm = TRUE) + max(inter_8, na.rm = TRUE) - inter_8)) %>%
-  mutate(apprehen.r = (min(inter_11, na.rm = TRUE) + max(inter_11, na.rm = TRUE) - inter_11)) %>%
-  mutate(aggressive.r = (min(inter_13, na.rm = TRUE) + max(inter_13, na.rm = TRUE) - inter_13))
-
-clark_measures$satisfaction <- rowMeans(select(clark_measures, anxious.r, uncomfort.r, hostile.r, apprehen.r, aggressive.r, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_6), na.rm=TRUE)
 ```
@@
   filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) #filter out dyads with no data
-
-#Social Physique Anxiety
-smith <- smith %>%
-  mutate(physanx5.r = (min(physanx_5, na.rm = TRUE) + max(physanx_5, na.rm = TRUE) - physanx_5),
-         physanx = (physanx_1 +physanx_2 +physanx_3+physanx_4+physanx5.r+physanx_6)/6) #reverse code physical anxiety variable
 
@@
 smith$TSO <- smith$TSO*-1
-
-#satisfaction--reverse code negative variables and then average with the rest
-smith <- smith %>%
-  mutate(anxious.r = (min(inter_2, na.rm = TRUE) + max(inter_2, na.rm = TRUE) - inter_2)) %>%
-  mutate(uncomfort.r = (min(inter_4, na.rm = TRUE) + max(inter_4, na.rm = TRUE) - inter_4)) %>%
-  mutate(hostile.r = (min(inter_8, na.rm = TRUE) + max(inter_8, na.rm = TRUE) - inter_8)) %>%
-  mutate(apprehen.r = (min(inter_11, na.rm = TRUE) + max(inter_11, na.rm = TRUE) - inter_11)) %>%
-  mutate(aggressive.r = (min(inter_13, na.rm = TRUE) + max(inter_13, na.rm = TRUE) - inter_13))
-
-smith$satisfaction <- rowMeans(select(smith, anxious.r, uncomfort.r, hostile.r, apprehen.r, aggressive.r, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_6), na.rm=TRUE)
 ```
@@
 #Read in graded trigram file
-smith_trigrams_graded <- read.csv("Smith College Relationships Data/trigrams_graded.csv")
+smith_trigrams_graded <- read.csv("Raw data/Smith College Relationships Data/trigrams_graded.csv")
 

### 2019-04-03 Final Manuscript.Rmd
adding methods draft

@@
 #Clark
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))$total[2]
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))$total[2]
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))$total[2]
+#Smith
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))$total[2]
+##DROPPING ITEM 9
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
 
@@
 
+```{r, include=FALSE}
+favstats(~TSO_A, data=clarksmith_women)
+favstats(~a2pSOO_A, data=clarksmith_women)
+favstats(~howbody_avg_A, data=clarksmith_women)
+favstats(~relag_A, data=clarksmith_women)
+favstats(~careerasp_A, data=clarksmith_women)
+favstats(~authenticity_A, data=clarksmith_women)
+favstats(~trigram_score_A, data=clarksmith_women)
+
+clark_final$age <- as.numeric(clark_final$age)
+smith_final$age <- as.numeric(smith_final$age)
+favstats(~age, data=clark_final)
+favstats(~age, data=smith_final)
+
+clarkmeanage <- favstats(~age, data=clark_final)$mean
+smithmeanage <- favstats(~age, data=smith_final)$mean
+
+favstats(~age_A, data=clarksmith_women)
+tally(clarksmith_women$race_A==clarksmith_women$race_P)
+
+psych::alpha(select(clarksmith_women, a2pSOO_A, a2pSOO_P))
+
+tally(~race_A, data=clarksmith_women)
+tally(~sexor_A, data=clarksmith_women)
+tally(~gender_A, data=clarksmith_women)
+
+table(clarksmith_women$race_A, clarksmith_women$race_P)
+
+test <- clarksmith_women %>%
+  filter(race_A==3, race_A!=race_P)
+
+tally(~gender, data=clark)
+tally(~gender, data=smith)
+
+```
+
 # Methods
@@
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+Method
 
-## Participants
-The data collected in this study sought to replicate Garcia et al.
-(2016), which sought to measure objectification in previously unacquainted male-female pairs.
-This data was given to us by Dr.
-Garcia, who collected data from both Smith College and Clark University.
-The data was ultimately merged and filtered to only include only self-identified female same-sex pairs from both schools.
-The two samples are often referred to below as Sample 1 (data from Clark University) and Sample 2 (data from Smith College).
+##Procedure
+The procedure used was identical to that in Garcia, Earnshaw & Quinn (2016), except for the instructions that the participants were given.
+In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to preventa ny communication between the participants before the interaction.
+In addition, each participant was screened for prior acquaintance to confirm that they had not met prior to the study.
+They were asked to sign the consent form to participate, and the study was described as follows: “This is a study looking at how students form different types of relationships at college.” A prompt on the computer screen told the participants that they were assigned to the “College Relationships” condition and gave the following instructions:
+
+There are many types of relationships people form in college.
+During the interaction, please think about your partner's potential as a romantic partner.
+Even if they are not the gender you are attracted to, you can still judge their potential as a romantic partner.
+After the interaction you will be asked to evaluate how dateable your partner is.
+In other words, we would like to know if you think someone would date your interaction partner.
+Also, your interaction partner will be evaluating you in the same manner.
+Two participants were then brought into a larger interaction room where they sat on stools prearranged to be 36 inches apart.
+The experimenter instructed the participants to “get to know each other” for 10 minutes and then left the room.
+After 10 minutes, the experimenter came back into the room and stopped the interaction.
+The participants then went back to their individual cubicles and completed a set of post-interaction measures.
+Participants were then thanked for their participation and debriefed (Garcia et al., 2016).
+The full methodology used is found in Garcia et al.
+(2016)’s study.
+
+##Combining Samples
+Data from two different samples was used for this study.
+They are discussed below.
+In the measures section that follows we refer to them as Sample 1 and Sample 2.
+Sample 1 is from a co-ed liberal arts college in the northeast and Sample 2 is from a women’s liberal arts college in the northeast.
+
+##Post interaction Measures
+
+The following measures were collected in the order they are presented following the interaction. Correlations appear in Table 1, and descriptive statistics appear in Table 2.
+
+###Cognitive performance. 
+Cognitive performance was assessed using trigrams from the Remote Associates Task (McFarlin & Blascovich, 1984).
+Ten items were selected and presented to participants.
+For example, the correct answer for the trigram “Quack: Pond: Waddle” would be “Duck”.
+Participants are limited to 30 seconds.
+For every correct answer, 1 point is given.
+The mean score was 5.03.
+Cognitive performance was measured first in order to measure potential immediate detriments to performance (Garcia et al., 2016).
+
+###SOO.
+To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts of several aspects of their partner (Garcia et al., 2016).
+Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
+All questions were to be rated on a scale from 1 (not at all) to 7 (constantly).
+Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits (α=.78 for Sample 1, α=.74 for Sample 2) and frequency of thought about their partner’s internal traits (α=.70 for Sample 1, α=.78 for Sample 2).
+A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
+
+###Interaction Authenticity.
+Just like Garcia et al.
+(2016), we assessed the extent to which participants felt comfortable in the interaction and felt it was authentic.
+We did this by asking them to rate the extent to which they felt the interaction was comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale from 1 (not at all) to 7 (very much).
+Participants were also asked whether they thought their partner was authentic in the interaction, and if they felt they were authentic in the interaction.
+These questions were ranked on a scale from 1 (not authentic at all).
+These were combined to form the authenticity scale (α=.91).
+
+###SSO.
+To assess state self-objectification, we used an average of two items from Saguy et al.
+(2010) that was also used in Garcia et al.
+(2016).
+Participants were asked to rank how much they agreed with the following statements: “During the interaction I felt more like a body than a full self” and “I felt more like a body than as a real person in the interaction”.
+Saguy et al.
+(2010) originally used 3 items, but the 3rd item had a low reliability score (r=*), so we chose to only use the first two for our measure of SSO.
+
+###Relationship Agency. 
+To assess how much relationship agency participants felt they would have in future relationships, we used the scale from Garcia et al.
+(2016), asking how likely it was that they would do the following: ‘‘ask someone out on a date,’’ ‘‘open the door for your date,’’ ‘‘pay for a date,’’ ‘‘ask your boyfriend/girlfriend to marry you,’’ ‘‘initiate sex with your girlfriend/boyfriend,’’ ‘‘initiate condom use during sex,’’ ‘‘surprise your boyfriend/ girlfriend with a gift,’’ and ‘‘ask your girlfriend/boyfriend to move with you to a new place.’’ Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
+This item had high reliability for Sample 1 (α=0.73) but low reliability for Sample 2 (α=0.58).
+
+###Career Aspirations.
+To measure career aspirations, we used the 10-item adaptation of Gray & O’Brien (2007)’s Career Aspiration Scale used in Garcia et al.
+(2016).
+This asked participants how true statements were about their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
+Items include ‘‘I hope to become a leader in my career field’’ and ‘‘I hope to move up through any organization or business I work in.’’ Items were fairly reliable (α=0.72 for Sample 1, α=0.81 for Sample 2).
+
+###TSO. 
+TSO was assessed using the Self-Objectification Questionnaire (Fredrickson et al., 1998; Noll & Fredrickson, 1998).
+This asks participants to rank order functional aspects of their bodies as well as physical self-concepts.
+The average rank of the functional aspects is then subtracted from the rank of the physical self-concepts.
+As was done in Garcia et al.
+(2016), all measures are multiplied by -1 so that positive scores correspond to more TSO.
+
+###Description of the Samples
+Participants consisted of thirty-two previously unacquainted female-identifying pairs from two liberal arts colleges in the northeast, for a total of sixty-four participants.
+Twelve of the pairs came from Sample 1, a co-ed liberal arts college, and twenty pairs came from Sample 2, a women’s liberal arts college.
+Data was originally collected from multiple genders in both same sex and mixed sex pairs.
+Sample 1 originally consisted of twenty-two pairs consisting of twelve men and thirty-two women.
+Sample 2 originally consisted of twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either category.
+Because the pattern of correlations between important study variables were similar across samples, the two datasets were then combined.
+For the purpose of consistency when combining data from the two schools, we limited the participants to same sex female pairs at the two colleges.
 These participants were mostly first-year college students, with an average age of 18.85 years (SD=1.04).
@@
 64% of the sample identified as heterosexual, and 23% identified as gay, lesbian or bisexual.
-The data is organized in a pairwise fashion such that each row corresponds to one participant in the study, and includes data for themselves and their partner.
-We would want to generalize these findings to general interactions between women.
 

### 2019-04-03 Final Manuscript.Rmd
adding numbers

@@
 
-clark_final$age <- as.numeric(clark_final$age)
-smith_final$age <- as.numeric(smith_final$age)
-favstats(~age, data=clark_final)
-favstats(~age, data=smith_final)
-
-clarkmeanage <- favstats(~age, data=clark_final)$mean
-smithmeanage <- favstats(~age, data=smith_final)$mean
-
-favstats(~age_A, data=clarksmith_women)
+mean_age <- favstats(~age_A, data=clarksmith_women)$mean
+sd_age <- favstats(~age_A, data=clarksmith_women)$sd
 tally(clarksmith_women$race_A==clarksmith_women$race_P)
@@
 tally(~race_A, data=clarksmith_women)
+percentage_black <- 6/(6+18+31+6+3)*100
+percent_asian <- 18/(6+18+31+6+3)*100
+percent_white <- 31/(6+18+31+6+3)*100
+percent_latinx <- 6/(6+18+31+6+3)*100
+percent_other <- 3/(6+18+31+6+3)*100
 tally(~sexor_A, data=clarksmith_women)
@@
 For the purpose of consistency when combining data from the two schools, we limited the participants to same sex female pairs at the two colleges.
-These participants were mostly first-year college students, with an average age of 18.85 years (SD=1.04).
-The sample was 48% White/European American, 9% Black/African-American, 28% Asian/Pacific Islander, 9% Latinx, and 5% mixed-race.
+These participants were mostly first-year college students, with an average age of `mean_age` (SD=`sd_age`).
+The sample was `percent_white`% White/European American, `percentage_black`% Black/African-American, `percent_asian`% Asian/Pacific Islander, `percent_latinx`% Latinx, and 5% mixed-race.
 There were eight White/White pairs and four same race racial minority pairs, for a total of twelve same-race pairs.

### 2019-04-07 Final Manuscript.Rmd
trying to add number formatting

--- 2019-04-03 Final Manuscript.Rmd
@@
 ```{r setup, include = FALSE}
-library("papaja")
+library(papaja)
 library(nlme)
@@
 library(irr)
+library(apaTables)
 
-clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
-smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")
+clark_measures <- read.csv("Cleaned data/clark_measures.csv")
+smith <- read.csv("Cleaned data/smith.csv")
+clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
 ```
@@
 
-clark_final$age <- as.numeric(clark_final$age)
-smith_final$age <- as.numeric(smith_final$age)
-favstats(~age, data=clark_final)
-favstats(~age, data=smith_final)
-
-clarkmeanage <- favstats(~age, data=clark_final)$mean
-smithmeanage <- favstats(~age, data=smith_final)$mean
-
-favstats(~age_A, data=clarksmith_women)
+#Mean and SD of age of sample
+mean_age <- favstats(~age_A, data=clarksmith_women)$mean
+sd_age <- favstats(~age_A, data=clarksmith_women)$sd
 tally(clarksmith_women$race_A==clarksmith_women$race_P)
 
-psych::alpha(select(clarksmith_women, a2pSOO_A, a2pSOO_P))
-
+#Calculating race percentages
 tally(~race_A, data=clarksmith_women)
+percentage_black <- 6/(6+18+31+6+3)*100
+percent_asian <- 18/(6+18+31+6+3)*100
+percent_white <- 31/(6+18+31+6+3)*100
+percent_latinx <- 6/(6+18+31+6+3)*100
+percent_other <- 3/(6+18+31+6+3)*100
 tally(~sexor_A, data=clarksmith_women)
@@
 
-tally(~gender, data=clark)
+tally(~gender, data=clark_measures)
 tally(~gender, data=smith)
+
+clarksmith_correlations <- clarksmith_women %>%
+  select(TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, relag_A, careerasp_A,  trigram_score_A, TSO_P, authenticity_P, a2pSOO_P, howbody_avg_P, relag_P, careerasp_P, trigram_score_P)
+
+#Correlation tables
+correlations <- apa.cor.table(clarksmith_correlations, table.number=1)
 
@@
 For the purpose of consistency when combining data from the two schools, we limited the participants to same sex female pairs at the two colleges.
-These participants were mostly first-year college students, with an average age of 18.85 years (SD=1.04).
-The sample was 48% White/European American, 9% Black/African-American, 28% Asian/Pacific Islander, 9% Latinx, and 5% mixed-race.
+These participants were mostly first-year college students, with an average age of `r mean_age` ($SD = `r sd_age`$).
+The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx` % Latinx, and 5% mixed-race.
 There were eight White/White pairs and four same race racial minority pairs, for a total of twelve same-race pairs.
@@
 \newpage
+#Tables
+```{r}
+# descriptives <- clarksmith_women %>%
+#   summarize(
+#     Mean = mean(Recall)
+#     , Median = median(Recall)
+#     , SD = sd(Recall)
+#     , Min = min(Recall)
+#     , Max = max(Recall)
+#   )
+# descriptives[, -1] <- printnum(descriptives[, -1])
+# 
+# apa_table(
+#   descriptives
+#   , caption = "(ref:mixed-table-caption)"
+#   , note = "(ref:mixed-table-note)"
+#   , escape = TRUE
+# )
+
+```
+
+```{r}
+glrstab<- function(x, export=FALSE) {
+
+ r <-corr.test(x)$r	#taking just the correlation matrix; no N, or p
+ p <-corr.test(x)$p	#taking the p*s
+
+#define notions for significance levels
+ mystars <- ifelse(p < .001, "**"
+                   , ifelse(p < .01, "**"
+                            , ifelse(p < .05, "*"
+                                     , ifelse(p < .10, "+", " "))))
+
+ #round r, define new matrix Rnew with the correlations from rnd and paste mystars
+ rnd  <- papaja::printnum(r, gt1 = FALSE, digits = 2)  #round, drop leading 0 - Thanks CRSH!								                     
+ Rnew <- matrix(paste(rnd, mystars, sep=""), ncol=ncol(rnd))
+
+  #remove 1.0 correlations from diagonal  and set the strings
+ diag(Rnew) <- ''		
+ Rnew[upper.tri(Rnew)] <- ''
+
+ rownames(Rnew) <- paste(1:ncol(rnd), colnames(rnd), sep=" ")         #define number and name
+ colnames(Rnew) <- paste(1:ncol(rnd), "", sep="") 			       #define number
+
+#fun-part: we trim the top half 
+ Rnew[upper.tri(Rnew)] <- ''			
+ Rnew
+
+ Rnew <- cbind(round(describe(x)[,3:4],2), Rnew)		     #describe x, M sD - put them in the matrix
+ colnames(Rnew)[1:2] <- c("M","SD")					      		#Beschriftung der neuen Spalten
+ Rnew <- Rnew[,1:(ncol(Rnew)-1)]							        	#delete the last column (ugly)
+
+ #export to clipboard
+
+   if (export==TRUE){
+   result<-write.table(Rnew
+                       , "clipboard"
+                       , sep=";"
+                       , row.names=FALSE)
+ }
+ else result <- Rnew
+ return(result)
+
+}
+
+corr_cswomen <- clarksmith_women %>%
+  select(TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, relag_A, trigram_score_A)
+
+corr.table <- glrstab(corr_cswomen)
+rownames(corr.table) <- c("Actor's trait self objectification (TSO)", "Actor's authenticity of interaction", "Actor's objectification of partner", "Actor's state self-objectification", "Actor's future relationship agency", "Actor's cognitive performance")
+colnames(corr.table)   <- c("$M$", "$SD$", "1", "2", "3", "4", "5")
+
+apa_table(corr.table, escape=FALSE)
+```
+
+\newpage
 

### 2019-04-07 Final Manuscript.Rmd
finalized numbers for methods section

@@
 smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]
+#with 3
+clark_howbody3 <- psych::alpha(select(clark_measures, howbody_1, howbody_2, howbody_3))
+smith_howbody3 <- psych::alpha(select(smith, howbody_1, howbody_2, howbody_3))
 
@@
 smith_physTSO_alpha <- psych::alpha(select(smith,tso_3, tso_5, tso_6, tso_8, tso_10))$total[2]
+
+#Cognitive performance
+mean_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$mean
+sd_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$sd
 ```
@@
 tally(~sexor_A, data=clarksmith_women)
+percent_straight <-(41/64)*100
+percent_queer <- (3+8+5)/64*100
 tally(~gender_A, data=clarksmith_women)
@@
 table(clarksmith_women$race_A, clarksmith_women$race_P)
+samerace_white <- 16/2 #divide by 2 since table is people, not pairs
+samerace_minority <- (6+2)/2
+mixedrace_white <- 2+10+2+1
+mixedrace_minority <- 1+2+1+1
 
@@
 For every correct answer, 1 point is given.
-The mean score was 5.03.
+The mean score was `r mean_trigram` (SD = `r sd_trigram`).
 Cognitive performance was measured first in order to measure potential immediate detriments to performance (Garcia et al., 2016).
@@
 All questions were to be rated on a scale from 1 (not at all) to 7 (constantly).
-Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits (α=.78 for Sample 1, α=.74 for Sample 2) and frequency of thought about their partner’s internal traits (α=.70 for Sample 1, α=.78 for Sample 2).
+Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits (α = `r printnum(clark_physTSO_alpha)[1,1]` for Sample 1, α = `r printnum(smith_physTSO_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_funcTSO_alpha)[1,1]` for Sample 1, α = `r printnum(smith_funcTSO_alpha)[1,1]` for Sample 2).
 A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
@@
 These questions were ranked on a scale from 1 (not authentic at all).
-These were combined to form the authenticity scale (α=.91).
+These were combined to form the authenticity scale (α = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, α = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
 
@@
 Saguy et al.
-(2010) originally used 3 items, but the 3rd item had a low reliability score (r=*), so we chose to only use the first two for our measure of SSO.
+(2010) originally used 3 items, but in both samples the reliability of the scale was higher if we removed the third item, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale (α = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and α = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
 
@@
 To assess how much relationship agency participants felt they would have in future relationships, we used the scale from Garcia et al.
-(2016), asking how likely it was that they would do the following: ‘‘ask someone out on a date,’’ ‘‘open the door for your date,’’ ‘‘pay for a date,’’ ‘‘ask your boyfriend/girlfriend to marry you,’’ ‘‘initiate sex with your girlfriend/boyfriend,’’ ‘‘initiate condom use during sex,’’ ‘‘surprise your boyfriend/ girlfriend with a gift,’’ and ‘‘ask your girlfriend/boyfriend to move with you to a new place.’’ Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
-This item had high reliability for Sample 1 (α=0.73) but low reliability for Sample 2 (α=0.58).
+(2016), asking how likely it was that they would do the following: "ask someone out on a date," "open the door for your date," "pay for a date," "ask your boyfriend/girlfriend to marry you," "initiate sex with your girlfriend/boyfriend," "initiate condom use during sex," "surprise your boyfriend/ girlfriend with a gift," and "ask your girlfriend/boyfriend to move with you to a new place." Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
+* talk about removing item 9.
+Once this item was removed, the scale had moderately high reliability for both samples (α = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, (α = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
 
@@
 This asked participants how true statements were about their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
-Items include ‘‘I hope to become a leader in my career field’’ and ‘‘I hope to move up through any organization or business I work in.’’ Items were fairly reliable (α=0.72 for Sample 1, α=0.81 for Sample 2).
+Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable (α = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, α = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
 
@@
 For the purpose of consistency when combining data from the two schools, we limited the participants to same sex female pairs at the two colleges.
-These participants were mostly first-year college students, with an average age of `r mean_age` ($SD = `r sd_age`$).
-The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx` % Latinx, and 5% mixed-race.
-There were eight White/White pairs and four same race racial minority pairs, for a total of twelve same-race pairs.
-The remaining twenty were mixed race pairs, of which fifteen were White/racial minority pairings and five were cross-racial minority group pairs.
-64% of the sample identified as heterosexual, and 23% identified as gay, lesbian or bisexual.
+These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
+The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
+There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
+The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
+`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
 
@@
 #Tables
-```{r}
-# descriptives <- clarksmith_women %>%
-#   summarize(
-#     Mean = mean(Recall)
-#     , Median = median(Recall)
-#     , SD = sd(Recall)
-#     , Min = min(Recall)
-#     , Max = max(Recall)
-#   )
-# descriptives[, -1] <- printnum(descriptives[, -1])
-# 
-# apa_table(
-#   descriptives
-#   , caption = "(ref:mixed-table-caption)"
-#   , note = "(ref:mixed-table-note)"
-#   , escape = TRUE
-# )
 
-```
-
-```{r}
+```{r, results='asis'}
+#Table 1
 glrstab<- function(x, export=FALSE) {
@@
 
-apa_table(corr.table, escape=FALSE)
+apa_table(corr.table, caption="Correlations among study variables.", escape=FALSE)
+```
+
+```{r, results='asis'}
+#table 2
+descriptives_cswomen <- clarksmith_women %>%
+  select(TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, relag_A, trigram_score_A)
+descriptives <- describe(descriptives_cswomen)
+
+descriptives <- descriptives %>%
+  select(mean, sd)
+
+rownames(descriptives) <- c("Actor's trait self objectification (TSO)", "Actor's authenticity of interaction", "Actor's objectification of partner", "Actor's state self-objectification", "Actor's future relationship agency", "Actor's cognitive performance")
+
+colnames(descriptives) <- c("M", "SD")
+
+apa_table(descriptives, caption = "Descriptive Statistics for Study Variables")
 ```

### 2019-04-08 Final Manuscript.Rmd
changes!

@@
 ##Procedure
-The procedure used was identical to that in Garcia, Earnshaw & Quinn (2016), except for the instructions that the participants were given.
+The procedure used was identical to that in @garcia2016objectification, except for the instructions that the participants were given.
 In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to preventa ny communication between the participants before the interaction.
@@
 The participants then went back to their individual cubicles and completed a set of post-interaction measures.
-Participants were then thanked for their participation and debriefed (Garcia et al., 2016).
-The full methodology used is found in Garcia et al.
-(2016)’s study.
+Participants were then thanked for their participation and debriefed @garcia2016objectification.
+The full methodology used is found in @garcia2016objectification’s study.
 
 ##Combining Samples
-Data from two different samples was used for this study.
-They are discussed below.
+Data from two different samples were used for this study and are discussed below.
 In the measures section that follows we refer to them as Sample 1 and Sample 2.
@@
 ##Post interaction Measures
-
 The following measures were collected in the order they are presented following the interaction. Correlations appear in Table 1, and descriptive statistics appear in Table 2.
@@
 ###Cognitive performance. 
-Cognitive performance was assessed using trigrams from the Remote Associates Task (McFarlin & Blascovich, 1984).
+Trigrams from the Remote Associates Task @mcfarlinblascovich1984 were utilized to assess cognitive performance after the interaction.
 Ten items were selected and presented to participants.
@@
 The mean score was `r mean_trigram` (SD = `r sd_trigram`).
-Cognitive performance was measured first in order to measure potential immediate detriments to performance (Garcia et al., 2016).
+Cognitive performance was measured first in order to measure potential immediate detriments to performance @garcia2016objectification.
 
 ###SOO.
-To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts of several aspects of their partner (Garcia et al., 2016).
+To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner @garcia2016objectification.
 Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
@@
 ###Interaction Authenticity.
-Just like Garcia et al.
-(2016), we assessed the extent to which participants felt comfortable in the interaction and felt it was authentic.
-We did this by asking them to rate the extent to which they felt the interaction was comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale from 1 (not at all) to 7 (very much).
-Participants were also asked whether they thought their partner was authentic in the interaction, and if they felt they were authentic in the interaction.
-These questions were ranked on a scale from 1 (not authentic at all).
+To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike @garcia2016objectification.
+Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: ‘‘Do you think your partner was authentic during your interaction?’’ and ‘‘Were you authentic during your interaction?’’ These questions were ranked on a scale from 1 (not authentic at all).
 These were combined to form the authenticity scale (α = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, α = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
@@
 ###SSO.
-To assess state self-objectification, we used an average of two items from Saguy et al.
-(2010) that was also used in Garcia et al.
-(2016).
+To assess state self-objectification, we used an average of two items from @saguyetal2010 that were also used in @garcia2016objectification.
 Participants were asked to rank how much they agreed with the following statements: “During the interaction I felt more like a body than a full self” and “I felt more like a body than as a real person in the interaction”.
-Saguy et al.
-(2010) originally used 3 items, but in both samples the reliability of the scale was higher if we removed the third item, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale (α = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and α = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
+Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale (α = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and α = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
 
 ###Relationship Agency. 
-To assess how much relationship agency participants felt they would have in future relationships, we used the scale from Garcia et al.
-(2016), asking how likely it was that they would do the following: "ask someone out on a date," "open the door for your date," "pay for a date," "ask your boyfriend/girlfriend to marry you," "initiate sex with your girlfriend/boyfriend," "initiate condom use during sex," "surprise your boyfriend/ girlfriend with a gift," and "ask your girlfriend/boyfriend to move with you to a new place." Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
-* talk about removing item 9.
-Once this item was removed, the scale had moderately high reliability for both samples (α = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, (α = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
+A scale was used from @garcia2016objectification to assess how much agency an individual believes they would possess in future romantic relationships.
+Participants were asked how likely it was that they would do the following: ‘‘ask someone out on a date,’’ ‘‘open the door for your date,’’ ‘‘pay for a date,’’ ‘‘ask your boyfriend/girlfriend to marry you,’’ ‘‘initiate sex with your girlfriend/boyfriend,’’ ‘‘initiate condom use during sex,’’ ‘‘surprise your boyfriend/ girlfriend with a gift,’’ and ‘‘ask your girlfriend/boyfriend to move with you to a new place.’’ Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
+Item 9 was removed, and as a result, the scale had moderately high reliability for both samples (α = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, (α = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
 
 ###Career Aspirations.
-To measure career aspirations, we used the 10-item adaptation of Gray & O’Brien (2007)’s Career Aspiration Scale used in Garcia et al.
-(2016).
-This asked participants how true statements were about their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
+To conceptualize participants’ career aspirations after the interaction, we used the 10-item adaptation of @grayobrien2007’s Career Aspiration Scale employed in @garcia2016objectification, which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
 Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable (α = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, α = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
@@
 ###TSO. 
-TSO was assessed using the Self-Objectification Questionnaire (Fredrickson et al., 1998; Noll & Fredrickson, 1998).
-This asks participants to rank order functional aspects of their bodies as well as physical self-concepts.
-The average rank of the functional aspects is then subtracted from the rank of the physical self-concepts.
-As was done in Garcia et al.
-(2016), all measures are multiplied by -1 so that positive scores correspond to more TSO.
+Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire (@fredricksonetal1998; @nollfredrickson1998), which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
+The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
+Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness).
+Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.
 
 ###Description of the Samples
-Participants consisted of thirty-two previously unacquainted female-identifying pairs from two liberal arts colleges in the northeast, for a total of sixty-four participants.
-Twelve of the pairs came from Sample 1, a co-ed liberal arts college, and twenty pairs came from Sample 2, a women’s liberal arts college.
-Data was originally collected from multiple genders in both same sex and mixed sex pairs.
-Sample 1 originally consisted of twenty-two pairs consisting of twelve men and thirty-two women.
-Sample 2 originally consisted of twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either category.
-Because the pattern of correlations between important study variables were similar across samples, the two datasets were then combined.
-For the purpose of consistency when combining data from the two schools, we limited the participants to same sex female pairs at the two colleges.
+Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
+More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college.
+Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
+Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
+Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
+Due to similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
+For consistency, we limited participant data to same sex female pairs at the two colleges.
 These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).

### 2019-04-11 Final Manuscript.Rmd
fixing relationship agency explanation + adding citation

@@
 ---
-title             : "The title"
+title             : "Objectification in Action"
 shorttitle        : "Title"
@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : ["r-references.bib", "references.bib"]
 
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 classoption       : "man"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 ---
@@
 smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
+
+corr.test(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+corr.test(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
 
@@
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
-Method
 
@@
 The procedure used was identical to that in @garcia2016objectification, except for the instructions that the participants were given.
-In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to preventa ny communication between the participants before the interaction.
+In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to prevent any communication between the participants before the interaction.
 In addition, each participant was screened for prior acquaintance to confirm that they had not met prior to the study.
@@
 Also, your interaction partner will be evaluating you in the same manner.
+
 Two participants were then brought into a larger interaction room where they sat on stools prearranged to be 36 inches apart.
@@
 ##Post interaction Measures
-The following measures were collected in the order they are presented following the interaction. Correlations appear in Table 1, and descriptive statistics appear in Table 2.
+The following measures were collected in the order they are presented following the interaction.
+Correlations appear in Table\ \@ref(tab:corrtable), and descriptive statistics appear in Table\ \@ref(tab:descriptives).
 
-###Cognitive performance. 
-Trigrams from the Remote Associates Task @mcfarlinblascovich1984 were utilized to assess cognitive performance after the interaction.
+###Cognitive performance
+Trigrams from the Remote Associates Task @mcfarlin1984remote were utilized to assess cognitive performance after the interaction.
 Ten items were selected and presented to participants.
@@
 
-###SOO.
+###SOO
 To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner @garcia2016objectification.
@@
 All questions were to be rated on a scale from 1 (not at all) to 7 (constantly).
-Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits (α = `r printnum(clark_physTSO_alpha)[1,1]` for Sample 1, α = `r printnum(smith_physTSO_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_funcTSO_alpha)[1,1]` for Sample 1, α = `r printnum(smith_funcTSO_alpha)[1,1]` for Sample 2).
+Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_physTSO_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_physTSO_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_funcTSO_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_funcTSO_alpha)[1,1]` for Sample 2).
 A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
 
-###Interaction Authenticity.
+###Interaction Authenticity
 To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike @garcia2016objectification.
 Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: ‘‘Do you think your partner was authentic during your interaction?’’ and ‘‘Were you authentic during your interaction?’’ These questions were ranked on a scale from 1 (not authentic at all).
-These were combined to form the authenticity scale (α = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, α = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
+These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
 
-###SSO.
+###SSO
 To assess state self-objectification, we used an average of two items from @saguyetal2010 that were also used in @garcia2016objectification.
 Participants were asked to rank how much they agreed with the following statements: “During the interaction I felt more like a body than a full self” and “I felt more like a body than as a real person in the interaction”.
-Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale (α = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and α = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
+Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
 
-###Relationship Agency. 
+###Relationship Agency
 A scale was used from @garcia2016objectification to assess how much agency an individual believes they would possess in future romantic relationships.
 Participants were asked how likely it was that they would do the following: ‘‘ask someone out on a date,’’ ‘‘open the door for your date,’’ ‘‘pay for a date,’’ ‘‘ask your boyfriend/girlfriend to marry you,’’ ‘‘initiate sex with your girlfriend/boyfriend,’’ ‘‘initiate condom use during sex,’’ ‘‘surprise your boyfriend/ girlfriend with a gift,’’ and ‘‘ask your girlfriend/boyfriend to move with you to a new place.’’ Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
-Item 9 was removed, and as a result, the scale had moderately high reliability for both samples (α = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, (α = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
+The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
+The item was intended to be reverse coded, but correlations were still low enough to make the scale unreliable.
+Therefore, the ninth item was removed.
+As a result, the scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
 
-###Career Aspirations.
+###Career Aspirations
 To conceptualize participants’ career aspirations after the interaction, we used the 10-item adaptation of @grayobrien2007’s Career Aspiration Scale employed in @garcia2016objectification, which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
-Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable (α = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, α = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
+Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
 
-###TSO. 
+###TSO
 Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire (@fredricksonetal1998; @nollfredrickson1998), which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
@@
 
-\newpage
-#Tables
-
-```{r, results='asis'}
+```{r corrtable, include=TRUE, echo=FALSE, results='asis'}
 #Table 1
@@
 
-```{r, results='asis'}
+```{r descriptives, include=TRUE, echo=FALSE, results='asis'}
 #table 2
@@
 ```{r create_r-references}
+cite_r(file = "references.bib")
 r_refs(file = "r-references.bib")

### 2019-04-25 Final Manuscript.Rmd
results

@@
 library(apaTables)
-
+library(knitr)
+library(kutils)
+library(tidyverse)
+library(lavaan)
+library(xtable)
 clark_measures <- read.csv("Cleaned data/clark_measures.csv")
@@
 
+## Analysis Strategy
+In Figure\ \@ref(fig:semfigure)
+
+##Main Results
+All model estimates and p-values are found in Table\ \@ref(tab:sem).
+The most important findings from @garcia2016objectification were the significant partner effect between actor SSO and partner objectification (specifically men's objectification of women and women's SSO), and the link between actor SSO and actor authenticity (also specifically for women).
+We did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which means we do not have evidence to support the idea that partner objectification is the cause for the negative effects related to relationship inauthenticity.
+However, we did find a significant relationship between partner objectification and actor SSO ($\beta$= .25, $p$=.03), which supports our hypothesis that objectification from other women also causes women to self-objectify just as it does in interactions between male-female pairs.
+We also found a significantly negative effect of authenticity on career aspirations ($\beta$= .18, $p$=.01) and relationship agency ($\beta$=.27, $p$=.01).
+We found that the model had good fit.
+
 # Discussion
@@
 
+```{r, include=FALSE}
+#Filtering for just one partnum and creating TSO * objectification interaction
+dyad_cswomen <- clarksmith_women %>%
+  mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
+         TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
+  filter(partnum_A==1)
+
+model <- '#####regressions 
+howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P + c*TSO_A_SOO_P
+authenticity_A ~ d*howbody_avg_A
+howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A + c*TSO_P_SOO_A
+authenticity_P ~ d*howbody_avg_P
+trigram_score_A ~ e1*authenticity_A
+careerasp_A ~ e2*authenticity_A
+relag_A ~ e3*authenticity_A
+trigram_score_P ~ e1*authenticity_P
+careerasp_P ~ e2*authenticity_P
+relag_P ~ e3*authenticity_P
+######covariances
+#endogenous
+howbody_avg_A ~~ howbody_avg_P
+authenticity_A ~~ authenticity_P
+trigram_score_A ~~ trigram_score_P
+careerasp_A ~~ careerasp_P
+relag_A ~~ relag_P
+trigram_score_A ~~ 0*careerasp_A
+trigram_score_A ~~ 0*relag_A
+trigram_score_A ~~ 0*careerasp_P
+trigram_score_A ~~ 0*relag_P
+careerasp_A ~~ 0*relag_A
+careerasp_A ~~ 0*trigram_score_P
+careerasp_A ~~ 0*relag_P
+relag_A ~~ 0*trigram_score_P
+relag_A ~~ 0*careerasp_P
+trigram_score_P ~~ 0*careerasp_P
+trigram_score_P ~~ 0*relag_P
+careerasp_P ~~ 0*relag_P
+#####variances
+howbody_avg_A ~~ v1*howbody_avg_A
+howbody_avg_P ~~ v1*howbody_avg_P
+TSO_A ~~ v2*TSO_A
+TSO_P ~~ v2*TSO_P
+a2pSOO_A ~~ v3*a2pSOO_A
+a2pSOO_P ~~ v3*a2pSOO_P
+authenticity_A ~~ v4*authenticity_A
+authenticity_P ~~ v4*authenticity_P
+##endogenous intercepts
+howbody_avg_A ~ i*1
+howbody_avg_P ~ i*1
+authenticity_A ~ i2*1
+authenticity_P ~ i2*1
+trigram_score_A ~ i3*1
+trigram_score_P ~ i4*1
+careerasp_A ~ i5*1
+careerasp_P ~ i5*1
+relag_A ~ i6*1
+relag_P ~ i6*1
+##exogenous means
+TSO_A ~ m*1
+TSO_P ~ m*1
+a2pSOO_A ~ m2*1
+a2pSOO_P ~ m2*1
+TSO_P_SOO_A ~ m3*1
+TSO_A_SOO_P ~ m3*1
+## exogenous covariances
+TSO_A_SOO_P ~~ c1*TSO_A
+TSO_P_SOO_A ~~ c1*TSO_P
+TSO_A_SOO_P ~~ c2*a2pSOO_P
+TSO_P_SOO_A ~~ c2*a2pSOO_A
+TSO_A ~~ c3*a2pSOO_P
+TSO_P ~~ c3*a2pSOO_A
+TSO_A ~~ c4*a2pSOO_A
+TSO_P ~~ c4*a2pSOO_P
+TSO_A_SOO_P ~~ c5*a2pSOO_A
+TSO_P_SOO_A ~~ c5*a2pSOO_P
+TSO_A_SOO_P ~~ c6*TSO_P
+TSO_P_SOO_A ~~ c6*TSO_A
+'
+
+isatmodel <- '#####regressions 
+#Part one/two
+howbody_avg_A ~~ t*TSO_A
+howbody_avg_A ~~ a*a2pSOO_A
+howbody_avg_A ~~ b*a2pSOO_P 
+howbody_avg_A ~~ c*TSO_A_SOO_P
+
+howbody_avg_P ~~ t*TSO_P
+howbody_avg_P ~~ a*a2pSOO_P 
+howbody_avg_P ~~ b*a2pSOO_A 
+howbody_avg_P ~~ c*TSO_P_SOO_A
+
+TSO_A ~~ f*howbody_avg_P
+TSO_P ~~ f*howbody_avg_A
+TSO_A_SOO_P ~~ g*howbody_avg_P
+TSO_P_SOO_A ~~ g*howbody_avg_A
+
+#Part two/three
+authenticity_A ~~ d*howbody_avg_A
+authenticity_P ~~ d*howbody_avg_P
+howbody_avg_A ~~ h*authenticity_P
+howbody_avg_P ~~ h*authenticity_A
+
+#Part three/four
+trigram_score_A ~~ e1*authenticity_A
+trigram_score_P ~~ e1*authenticity_P
+careerasp_A ~~ e2*authenticity_A
+careerasp_P ~~ e2*authenticity_P
+relag_A ~~ e3*authenticity_A
+relag_P ~~ e3*authenticity_P
+trigram_score_A ~~ e4*relag_P
+trigram_score_P ~~ e4*relag_A
+trigram_score_A ~~ e5*careerasp_P
+trigram_score_P ~~ e5*careerasp_A
+trigram_score_A ~~ e6*trigram_score_P
+#trigram_score_P ~~ e6*trigram_score_A
+careerasp_A ~~ e7*relag_P
+careerasp_P ~~ e7*relag_A
+careerasp_A ~~ e8*careerasp_P
+#careerasp_A ~~ e9*trigram_score_P
+#careerasp_P ~~ e9*trigram_score_A
+relag_A ~~ e10*relag_P
+
+#One to three
+#direct actor effects
+authenticity_A ~~ k1*TSO_A_SOO_P
+authenticity_P ~~ k1*TSO_P_SOO_A
+authenticity_A ~~ k2*TSO_A
+authenticity_P ~~ k2*TSO_P
+authenticity_A ~~k3*a2pSOO_A
+authenticity_P ~~k3*a2pSOO_P
+
+#direct partner effects
+authenticity_A ~~ k4*TSO_P_SOO_A
+authenticity_P ~~k4*TSO_A_SOO_P
+authenticity_A ~~ k5*TSO_P
+authenticity_P ~~ k5*TSO_A
+authenticity_A ~~ k6*a2pSOO_P
+authenticity_P ~~ k6*a2pSOO_A
+
+#One to four
+#Direct actor effects
+trigram_score_A ~~ l1*TSO_A_SOO_P
+trigram_score_P ~~ l1*TSO_P_SOO_A
+trigram_score_A ~~ l2*TSO_A
+trigram_score_P ~~ l2*TSO_P
+trigram_score_A ~~ l3*a2pSOO_A
+trigram_score_P ~~ l3*a2pSOO_P
+careerasp_A ~~ l4*TSO_A_SOO_P
+careerasp_P ~~ l4*TSO_P_SOO_A
+careerasp_A ~~ l5*TSO_A
+careerasp_P ~~ l5*TSO_P
+careerasp_A ~~ l6*a2pSOO_A
+careerasp_P ~~ l6*a2pSOO_P
+relag_A ~~ l7*TSO_A_SOO_P
+relag_P ~~ l7*TSO_P_SOO_A
+relag_A ~~ l8*TSO_A
+relag_P ~~ l8*TSO_P
+relag_A ~~ l9*a2pSOO_A
+relag_P ~~ l9*a2pSOO_P
+
+#direct partner effects
+trigram_score_A ~~ m1*TSO_P_SOO_A
+trigram_score_P ~~ m1*TSO_A_SOO_P
+trigram_score_A ~~ m2*TSO_P
+trigram_score_P ~~ m2*TSO_A
+trigram_score_A ~~ m3*a2pSOO_P
+trigram_score_P ~~ m3*a2pSOO_A
+careerasp_A ~~ m4*TSO_P_SOO_A
+careerasp_P ~~ m4*TSO_A_SOO_P
+careerasp_A ~~ m5*TSO_P
+careerasp_P ~~ m5*TSO_A
+careerasp_A ~~ m6*a2pSOO_P
+careerasp_P ~~ m6*a2pSOO_A
+relag_A ~~ m7*TSO_P_SOO_A
+relag_P ~~ m7*TSO_A_SOO_P
+relag_A ~~ m8*TSO_P
+relag_P ~~ m8*TSO_A
+relag_A ~~ m9*a2pSOO_P
+relag_P ~~ m9*a2pSOO_A
+
+#Two to four
+#direct actor effects
+trigram_score_A ~~ o1*howbody_avg_A
+trigram_score_P ~~ o1*howbody_avg_P
+careerasp_A ~~ o2*howbody_avg_A
+careerasp_P ~~ o2*howbody_avg_P
+relag_A ~~ o3*howbody_avg_A
+relag_P ~~ o3*howbody_avg_P
+
+#direct partner effects
+trigram_score_A ~~ o1*howbody_avg_P
+trigram_score_P ~~ o1*howbody_avg_A
+careerasp_A ~~ o2*howbody_avg_P
+careerasp_P ~~ o2*howbody_avg_A
+relag_A ~~ o3*howbody_avg_P
+relag_P ~~ o3*howbody_avg_A
+
+######covariances
+#endogenous
+howbody_avg_A ~~ howbody_avg_P
+authenticity_A ~~ authenticity_P
+#trigram_score_A ~~ trigram_score_P
+#careerasp_A ~~ careerasp_P
+#relag_A ~~ relag_P
+trigram_score_A ~~ q1*careerasp_A 
+trigram_score_A ~~ q2*relag_A
+
+careerasp_A ~~ q3*relag_A
+
+trigram_score_P ~~ q1*careerasp_P
+trigram_score_P ~~ q2*relag_P
+
+careerasp_P ~~ q3*relag_P
+
+trigram_score_A ~~ q4*careerasp_P
+trigram_score_A ~~ q5*relag_P
+
+trigram_score_P ~~ q4*careerasp_A
+trigram_score_P ~~ q5*relag_A
+
+careerasp_A ~~ q6*relag_P
+careerasp_P ~~ q6*relag_A
+
+#####variances
+howbody_avg_A ~~ v1*howbody_avg_A
+howbody_avg_P ~~ v1*howbody_avg_P
+TSO_A ~~ v2*TSO_A
+TSO_P ~~ v2*TSO_P
+a2pSOO_A ~~ v3*a2pSOO_A
+a2pSOO_P ~~ v3*a2pSOO_P
+authenticity_A ~~ v4*authenticity_A
+authenticity_P ~~ v4*authenticity_P
+##endogenous intercepts
+howbody_avg_A ~ i*1
+howbody_avg_P ~ i*1
+authenticity_A ~ i2*1
+authenticity_P ~ i2*1
+trigram_score_A ~ i3*1
+trigram_score_P ~ i4*1
+careerasp_A ~ i5*1
+careerasp_P ~ i5*1
+relag_A ~ i6*1
+relag_P ~ i6*1
+##exogenous means
+TSO_A ~ m*1
+TSO_P ~ m*1
+a2pSOO_A ~ m2*1
+a2pSOO_P ~ m2*1
+TSO_P_SOO_A ~ m3*1
+TSO_A_SOO_P ~ m3*1
+## exogenous covariances
+TSO_A_SOO_P ~~ c1*TSO_A
+TSO_P_SOO_A ~~ c1*TSO_P
+TSO_A_SOO_P ~~ c2*a2pSOO_P
+TSO_P_SOO_A ~~ c2*a2pSOO_A
+TSO_A ~~ c3*a2pSOO_P
+TSO_P ~~ c3*a2pSOO_A
+TSO_A ~~ c4*a2pSOO_A
+TSO_P ~~ c4*a2pSOO_P
+TSO_A_SOO_P ~~ c5*a2pSOO_A
+TSO_P_SOO_A ~~ c5*a2pSOO_P
+TSO_A_SOO_P ~~ c6*TSO_P
+TSO_P_SOO_A ~~ c6*TSO_A
+'
+
+fit <- sem(model, data=dyad_cswomen)
+```
+
+```{r sem, include=TRUE, results='asis'}
+fit_table <- xtable(parameterEstimates(fit))
+
+fit_table <- fit_table %>%
+  filter(op=="~") %>%
+  mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO", 
+                      ifelse(lhs=="authenticity_A", "Actor Authenticity",
+                             ifelse(lhs=="howbody_avg_P", "Partner SSO",
+                                    ifelse(lhs=="authenticity_P", "Partner Authenticity", 
+                                           ifelse(lhs=="relag_A", "Actor Rel. Agency",
+                                                  ifelse(lhs=="relag_P", "Partner Rel. Agency",
+                                                         ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
+                                                                ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
+                                                                       ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
+                                                                              ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
+         rhs = ifelse(rhs=="TSO_A", "Actor TSO",
+                      ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
+                             ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
+                                    ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
+                                           ifelse(rhs == "howbody_avg_A", "Actor SSO",
+                                                  ifelse(rhs=="howbody_avg_P", "Partner SSO",
+                                                         ifelse(rhs=="TSO_P", "Partner TSO",
+                                                                ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
+                                                                       ifelse(rhs=="authenticity_A", "Actor Authenticity", 
+                                                                              ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
+  select(lhs, op, rhs, est, se, z, pvalue) %>%
+  #taking out partner-partner estimates
+  slice(1:5,11:13)
+
+colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
+
+apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
+```
+
+```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
+include_graphics("SEMfigure.png")
+```
+
 \newpage

### 2019-05-09 Final_Manuscript.Rmd
adding all the changes i've made!

--- 2019-04-25 Final Manuscript.Rmd
@@
 ---
-title             : "Objectification in Action"
-shorttitle        : "Title"
+title             : "Objectification in Action: Self- and Other-Objectification in Same-gender Interactions"
+shorttitle        : "Objectification in Action"
 
@@
     affiliation   : "1"
+  - name          : "Asha Hinson"
+    affiliation   : "1"
+  - name          : "Randi L. Garcia"
     corresponding : yes    # Define only one corresponding author
@@
     email         : "my@email.com"
-  - name          : "Asha Hinson"
-    affiliation   : "1"
-  - name          : "Randi L. Garcia"
     affiliation   : "1"
@@
 
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  Objectification theory is a valuable framework for conceptualizing the psychological consequences of being female within a society that sexually objectifies the female body, and considering the ways in which girls and women are acculturated to then internalize an observer’s perspective as a primary view of their appearance.
+Empirical evidence has largely elucidated links between objectification, self-objectification, and negative outcomes for woman within interpersonal interactions between male-female pairs particularly.
+The purpose of the present study was to extend past research and consider the relationships between such valuable phenomena and their effects on authenticity within interactions between female pairs.
+Woman were brought into the laboratory and interacted in same-sex dyads.
+Dyadic analysis was utilized to detect whether partners’ objectification of each other affected state self-objectification, and the resulting feelings of comfort and authenticity during the interaction.
+After the interaction, participants completed a questionnaire which measured many constructs including cognitive performance, career aspirations, and relationship agency.
+Results revealed no significant relationship between self-objectification and authenticity.
+Further, although there were significantly negative effects on career aspirations and relationship agency resulting from a lack of relationship authenticity, there was no evidence that this is due to feelings of sexual objectification.
+The significant partner effect of objectification on actor self-objectification suggests that women being objectified by other women still results in feelings of self-objectification, and such research has powerful implications for the ways that women interact in both sexual and non-sexual settings.
 
 keywords          : "keywords"
-wordcount         : "X"
 
@@
 clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10))$total[2]
-clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12))
+
+clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
 #Smith
@@
 #Clark
-clark_howbody_alpha <- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
+clark_howbody_alpha<- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
 #Smith
@@
 #Clark--external and internal
-clark_funcTSO_alpha <- psych::alpha(select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9))$total[2]
-clark_physTSO_alpha <- psych::alpha(select(clark_measures,tso_3, tso_5, tso_6, tso_8, tso_10))$total[2]
+clark_funcTSO_alpha <- psych::alpha(select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
+clark_physTSO_alpha <- psych::alpha(select(clark_measures,tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
 #Smith--external and internal
-smith_funcTSO_alpha <- psych::alpha(select(smith,tso_1, tso_2, tso_4, tso_7, tso_9))$total[2]
-smith_physTSO_alpha <- psych::alpha(select(smith,tso_3, tso_5, tso_6, tso_8, tso_10))$total[2]
+smith_funcTSO_alpha <- psych::alpha(select(smith,tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
+smith_physTSO_alpha <- psych::alpha(select(smith,tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
 
@@
 
+#Introduction
+Theorists across diverse disciplines have explored the multiple ways that the body conveys social meaning, as well as how these meanings shape gendered experiences and therefore inform individuals’ thinking, feeling, and behavior, especially during interpersonal interactions with members of different social groups [@Kaschak].
+Empirical evidence illustrates how women, in particular,  continue to be objects of perpetual discrimination as a result of psychosocial markers, like gender, that produce modes through which their identity is understood [@swimetal].
+Objectification theory, a valuable theoretical framework proposed by @robertsfredrickson which works to contextualize female bodies as socio-cultural constructions, can be employed to illuminate the gender oppression and negative lived experiences of girls and women.
+Additionally, one of the most detrimental forms of discrimination against them is thought to be the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
+Sexual objectification occurs with both “endless variety and monotonous similarity,” and is thus mediated by unique combinations of race, ethnicity, sexuality, age, and class [@fredricksonetal2011; @rubin1975, cited in @frasernicholson1989, p.
+28].
+Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
+Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
+Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
+Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008].
+@calogero2011 proposes that the construct of self-objectification can be conceptualized as a learned trait.
+Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@calogero2011, @moradi2008].
+Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO).
+In the current work, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification,  but between same-sex female interpersonal interactions.
+We predicted that being objectified by one’s interaction partner would lead to self-objectification, in addition to modified feelings of authenticity in postinteraciton outcomes, including feelings of agency in romantic relationships, career aspiration, and cognitive performance [@quinnetal].
+Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@swimetal].
+Moreover, it was the goal of this research to empirically explore the role of interaction authenticity in objectification by utilizing a structural equation modeling to examine the effects for both women simultaneously.
+We expected to replicate the results found in the previous @garcia2016objectification study.
+More specifically, we expected to find a positive relationship between state-other objectification and self-state objectification, and a resulting negative relationship between self-state objectification and interaction authenticity.
+Finally, we expected there to be a positive relationship between interaction authenticity and cognitive performance, relationship agency, and career aspirations.
+
 # Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 
@@
 
-###Cognitive performance
-Trigrams from the Remote Associates Task @mcfarlin1984remote were utilized to assess cognitive performance after the interaction.
+###Cognitive Performance
+Trigrams from the Remote Associates Task [@mcfarlin1984remote] were utilized to assess cognitive performance after the interaction.
 Ten items were selected and presented to participants.
@@
 The mean score was `r mean_trigram` (SD = `r sd_trigram`).
-Cognitive performance was measured first in order to measure potential immediate detriments to performance @garcia2016objectification.
+Cognitive performance was measured first in order to measure potential immediate detriments to performance [@garcia2016objectification].
 
-###SOO
+###State Other-Objectification
 To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner @garcia2016objectification.
@@
 All questions were to be rated on a scale from 1 (not at all) to 7 (constantly).
-Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_physTSO_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_physTSO_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_funcTSO_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_funcTSO_alpha)[1,1]` for Sample 2).
+Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2).
 A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
@@
 ###Interaction Authenticity
-To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike @garcia2016objectification.
+To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike [@garcia2016objectification].
 Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: ‘‘Do you think your partner was authentic during your interaction?’’ and ‘‘Were you authentic during your interaction?’’ These questions were ranked on a scale from 1 (not authentic at all).
@@
 
-###SSO
+###State Self-Objectification
 To assess state self-objectification, we used an average of two items from @saguyetal2010 that were also used in @garcia2016objectification.
@@
 
-###TSO
-Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire (@fredricksonetal1998; @nollfredrickson1998), which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
+###Trait Self-Objectification
+Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
 The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
@@
 
-## Material
-
-## Procedure
-
 ## Data analysis
@@
 ## Analysis Strategy
-In Figure\ \@ref(fig:semfigure)
+
+This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used dyadic analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
+See Figure\ \@ref(fig:2016figure) for the path analysis results of the previous study.
+We hope to investigate how the main effects found in the previous study relay to interactions between women: specifically, the relationship between state-other objectification and self-state objectification and the resulting effect of self-state objectification on inauthenticity during the interaction.
+
+We used path analysis to obtain our estimates, but because our sample is nonindependent, we used the indistinguishable actor–partner interdependence model [@olsen2006structural].
+The APIM can be defined as a "model of dyadic relationships that integrates a conceptual view of interdependence with the appropriate statistical techniques for measuring and testing it" [@olsen2006structural].
+See Figure\ \@ref(fig:apim) for a basic APIM model.
+Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
+Due to constraints of the basic APIM, in that this was an exploration of indistinguishable female dyads, we had to fix all path estimates to be the same across/between people and partners, in addition to all variances, covariances, endogenous intercepts, and exogenous means.
+Due to the complexity of the original @garcia2016objectification study, we also had to set the exogenous covariances equal.
+More specifically, the covariances between TSO, actor and partner objectification, and the interaction between actor TSO and partner objectification (and vice versa).
+
+In order to interpret model fit, which refers to the ability of a model to reproduce the data (i.e., usually the varience-covariance matrix) we utilized both the I-SAT (saturated) model, and the Null model to ensure that all possible corresponding covariences are fixed to be equal across partners.
+We obtained fit estimates by subtracting the chi-square estimate for the I-SAT model from the analysis model [@olsen2006structural, @peugh2013analyzing].
 
@@
 We also found a significantly negative effect of authenticity on career aspirations ($\beta$= .18, $p$=.01) and relationship agency ($\beta$=.27, $p$=.01).
-We found that the model had good fit.
+We found that the model had good fit ($\chi^2$=22.33, $df$=34).
+In this case, a good fit indicates that there are no direct effects of SSO or SOO on the outcomes on cognitive performance, relationship agency, and career aspirations, which indicates that the path we chose makes sense.
 
 # Discussion
+As stated previously, we did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to relationship inauthenticity.
+However, we did observe a significant partner effect of objectification on actor self-objectification, which does align with our hypothesis that theorized objectification from other women can also cause women to self-objectify just as they do within interactions between male-female pairs.
+The results of this study demonstrate the complex and ambivalent nature of female sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
+The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008].
+Because “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015].
+Further, sexualzing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014; @bury2016].
+Considering the fact that the average mean age of the investigated participants of this current study was 18.85 years, research among younger and older individuals is needed, especially because self-objectification may change over time [@robertsfredrickson].
+It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexulizing content.
+Also, future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operalization of self-objectification may be improved.
+Regardless, the results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts.
+These results are quite useful for promoting mental health and within early action programs for girls and young women, where scholars and practitioners might provide the tools necessary to circumvent or mitigate negative effects on self-objectification, and combat such experiences.
 
@@
 
+```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
+include_graphics("APIM_figure.png")
+```
+
+```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
+include_graphics("2016_figure.jpg")
+```
+
 ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
@@
 # References
-```{r create_r-references}
+```{r create_r-references, warning=FALSE, message=FALSE}
 cite_r(file = "references.bib")

### 2019-05-09 Final_Manuscript.tex
adding all the changes i've made!

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Kat Kyuchukova, Asha Hinson, \& Randi L. Garcia},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Objectification in Action: Self- and Other-Objectification in
Same-gender Interactions}
    \author{Kat Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \&
Randi L. Garcia\textsuperscript{1}}
    \date{}

\shorttitle{Objectification in Action}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Smith College}
\keywords{keywords}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother

\

\abstract{
Objectification theory is a valuable framework for conceptualizing the
psychological consequences of being female within a society that
sexually objectifies the female body, and considering the ways in which
girls and women are acculturated to then internalize an observer's
perspective as a primary view of their appearance. Empirical evidence
has largely elucidated links between objectification,
self-objectification, and negative outcomes for woman within
interpersonal interactions between male-female pairs particularly. The
purpose of the present study was to extend past research and consider
the relationships between such valuable phenomena and their effects on
authenticity within interactions between female pairs. Woman were
brought into the laboratory and interacted in same-sex dyads. Dyadic
analysis was utilized to detect whether partners' objectification of
each other affected state self-objectification, and the resulting
feelings of comfort and authenticity during the interaction. After the
interaction, participants completed a questionnaire which measured many
constructs including cognitive performance, career aspirations, and
relationship agency. Results revealed no significant relationship
between self-objectification and authenticity. Further, although there
were significantly negative effects on career aspirations and
relationship agency resulting from a lack of relationship authenticity,
there was no evidence that this is due to feelings of sexual
objectification. The significant partner effect of objectification on
actor self-objectification suggests that women being objectified by
other women still results in feelings of self-objectification, and such
research has powerful implications for the ways that women interact in
both sexual and non-sexual settings.
}

\begin{document}
\maketitle

\section{Introduction}\label{introduction}

Theorists across diverse disciplines have explored the multiple ways
that the body conveys social meaning, as well as how these meanings
shape gendered experiences and therefore inform individuals' thinking,
feeling, and behavior, especially during interpersonal interactions with
members of different social groups (``Engendered lives,'' 1993).
Empirical evidence illustrates how women, in particular, continue to be
objects of perpetual discrimination as a result of psychosocial markers,
like gender, that produce modes through which their identity is
understood (Swim, Hyers, Cohen, \& Ferguson, 2001). Objectification
theory, a valuable theoretical framework proposed by Roberts and
Fredrickson (1997) which works to contextualize female bodies as
socio-cultural constructions, can be employed to illuminate the gender
oppression and negative lived experiences of girls and women.
Additionally, one of the most detrimental forms of discrimination
against them is thought to be the process by which their whole being is
viewed as a collection of sexualized body parts valued predominantly for
commodification, a phenomena termed sexual objectification (Bartky,
1990). Sexual objectification occurs with both \enquote{endless variety
and monotonous similarity,} and is thus mediated by unique combinations
of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
Nicholson (1989), p.~28). Amid such heterogeneity though,
\enquote{having a reproductively mature female body} proposed by Roberts
and Fredrickson (1997) is likely to create a shared vulnerability to
sexual objectification and a variety of shared negative experiences as a
result. Studies have shown that within social encounters women are gazed
at more than men (Briton \& Hall, 1995), often times feel
\enquote{looked at} within interpersonal interactions (Argyle \&
Williams, 1969), and will more than likely internalize the objectifying
gaze on physical self (Young, 1979). Moreover, perhaps the most adverse
effect of objectifying treatment is that it effectively socializes girls
and women to treat themselves as objects to be looked at and evaluated,
an effect termed self-objectification (Bartky, 1990; Berger, Cohen, \&
Zelditch Jr, 1972; L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge,
1998). Self-objectification is a multidimensional process that accounts
for the cognitive mechanism that translates experiences of sexualization
at the cultural level to psychological (e.g., anxiety, self-esteem,
authenticity, motivational states) and behavioral (cognitive
performance, body monitoring) features of mental health and well-being
at the individual level (Calogero, Tantleff-Dunn, \& Thompson, 2011;
Moradi \& Huang, 2008). Calogero et al. (2011) proposes that the
construct of self-objectification can be conceptualized as a learned
trait. Furthermore, it can also be elicited momentarily, through the
media, for example, with sexualized images in movies and magazines,
which can lead to a state of self-objectification (Calogero et al.,
2011, Moradi and Huang (2008)). Being objectified by another person and
possessing trait-level self-objectification (TSO) may interact to
influence experiences of feeling like a body, or state
self-objectification (SSO). In the current work, we sought to examine
what occurs during an interaction in which one or both partners are
objectifying each other, similarly to Garcia, Earnshaw, and Quinn
(2016), but between same-sex female interpersonal interactions. We
predicted that being objectified by one's interaction partner would lead
to self-objectification, in addition to modified feelings of
authenticity in postinteraciton outcomes, including feelings of agency
in romantic relationships, career aspiration, and cognitive performance
(D. M. Quinn, Chaudoir, \& Kallen, 2011). Empirical evidence reveals
that objectification manifests through inauthenticity in romantic
relationships (Brunell et al., 2010), adverse attitudes in regard to
career aspirations, and a decrease in concentration and impairment in
female cognitive performance (Swim et al., 2001). Moreover, it was the
goal of this research to empirically explore the role of interaction
authenticity in objectification by utilizing a structural equation
modeling to examine the effects for both women simultaneously. We
expected to replicate the results found in the previous Garcia et al.
(2016) study. More specifically, we expected to find a positive
relationship between state-other objectification and self-state
objectification, and a resulting negative relationship between
self-state objectification and interaction authenticity. Finally, we
expected there to be a positive relationship between interaction
authenticity and cognitive performance, relationship agency, and career
aspirations.

\section{Methods}\label{methods}

\subsection{Procedure}\label{procedure}

The procedure used was identical to that in Garcia et al. (2016), except
for the instructions that the participants were given. In brief, that
methodology is that each participant arrived at the laboratory and were
then led into separate cubicles to prevent any communication between the
participants before the interaction. In addition, each participant was
screened for prior acquaintance to confirm that they had not met prior
to the study. They were asked to sign the consent form to participate,
and the study was described as follows: \enquote{This is a study looking
at how students form different types of relationships at college.} A
prompt on the computer screen told the participants that they were
assigned to the \enquote{College Relationships} condition and gave the
following instructions:

There are many types of relationships people form in college. During the
interaction, please think about your partner's potential as a romantic
partner. Even if they are not the gender you are attracted to, you can
still judge their potential as a romantic partner. After the interaction
you will be asked to evaluate how dateable your partner is. In other
words, we would like to know if you think someone would date your
interaction partner. Also, your interaction partner will be evaluating
you in the same manner.

Two participants were then brought into a larger interaction room where
they sat on stools prearranged to be 36 inches apart. The experimenter
instructed the participants to \enquote{get to know each other} for 10
minutes and then left the room. After 10 minutes, the experimenter came
back into the room and stopped the interaction. The participants then
went back to their individual cubicles and completed a set of
post-interaction measures. Participants were then thanked for their
participation and debriefed Garcia et al. (2016). The full methodology
used is found in Garcia et al. (2016)'s study.

\subsection{Combining Samples}\label{combining-samples}

Data from two different samples were used for this study and are
discussed below. In the measures section that follows we refer to them
as Sample 1 and Sample 2. Sample 1 is from a co-ed liberal arts college
in the northeast and Sample 2 is from a women's liberal arts college in
the northeast.

\subsection{Post interaction Measures}\label{post-interaction-measures}

The following measures were collected in the order they are presented
following the interaction. Correlations appear in
Table~\ref{tab:corrtable}, and descriptive statistics appear in
Table~\ref{tab:descriptives}.

\subsubsection{Cognitive Performance}\label{cognitive-performance}

Trigrams from the Remote Associates Task (McFarlin \& Blascovich, 1984)
were utilized to assess cognitive performance after the interaction. Ten
items were selected and presented to participants. For example, the
correct answer for the trigram \enquote{Quack: Pond: Waddle} would be
\enquote{Duck}. Participants are limited to 30 seconds. For every
correct answer, 1 point is given. The mean score was 5.03 (SD = 2.29).
Cognitive performance was measured first in order to measure potential
immediate detriments to performance (Garcia et al., 2016).

\subsubsection{State
Other-Objectification}\label{state-other-objectification}

To measure the participant's objectification of their partner in the
interaction, participants were asked a series of questions about the
frequency of thoughts in relation to multiple characteristics of their
partner Garcia et al. (2016). Questions included aspects of their
partner's internal traits such as personality, friends, family, and
extracurricular interests, as well as external traits such as body,
appearance, clothing, and body parts. All questions were to be rated on
a scale from 1 (not at all) to 7 (constantly). Objectification was
measured by getting the difference between the average frequency of
thought about their partner's external traits (\(\alpha\) = 0.79 for
Sample 1, \(\alpha\) = 0.79 for Sample 2) and frequency of thought about
their partner's internal traits (\(\alpha\) = 0.79 for Sample 1,
\(\alpha\) = 0.76 for Sample 2). A positive score in this scale would
indicate that the participant thought about their partner's external
traits more than the partner's internal traits, and a negative score
would indicate the opposite.

\subsubsection{Interaction Authenticity}\label{interaction-authenticity}

To assess the magnitude to which individuals felt comfortable in the
interaction and perceived the interaction to be authentic, we asked
participants to rate the extent to which they felt comfortable, happy,
friendly, warm, easygoing, sincere, and authentic on a scale ranging
from 1 (not at all) to 7 (very much), much alike (Garcia et al., 2016).
Participants were additionally asked to rate their interaction partner's
authenticity as well as their own: \enquote{`Do you think your partner
was authentic during your interaction?}' and \enquote{`Were you
authentic during your interaction?}' These questions were ranked on a
scale from 1 (not authentic at all). These were combined to form the
authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) = 0.91
for Sample 2).

\subsubsection{State
Self-Objectification}\label{state-self-objectification}

To assess state self-objectification, we used an average of two items
from Saguy, Quinn, F Dovidio, and Pratto (2010) that were also used in
Garcia et al. (2016). Participants were asked to rank how much they
agreed with the following statements: \enquote{During the interaction I
felt more like a body than a full self} and \enquote{I felt more like a
body than as a real person in the interaction}. Originally, Saguy et al.
(2010) used 3 items, but in both samples the reliability of the scale
was higher once the third item was removed, so we chose to only use the
first two for our measure of SSO, leaving us with a reliable scale
(\(\alpha\) = 0.84 for Sample 1, and \(\alpha\) = 0.85 for Sample 2.)

\subsubsection{Relationship Agency}\label{relationship-agency}

A scale was used from Garcia et al. (2016) to assess how much agency an
individual believes they would possess in future romantic relationships.
Participants were asked how likely it was that they would do the
following: \enquote{`ask someone out on a date,}' \enquote{`open the
door for your date,}' \enquote{`pay for a date,}' \enquote{`ask your
boyfriend/girlfriend to marry you,}' \enquote{`initiate sex with your
girlfriend/boyfriend,}' \enquote{`initiate condom use during sex,}'
\enquote{`surprise your boyfriend/ girlfriend with a gift,}' and
\enquote{`ask your girlfriend/boyfriend to move with you to a new
place.}' Responses were measured on a scale ranging from 1 (not at all
likely) to 7 (extremely likely). The scale originally had 9 items, but
the 9th item had low correlations with the remaining items, ranging from
.02 to .30 for the first sample, and .04 to .30 for the second sample.
The item was intended to be reverse coded, but correlations were still
low enough to make the scale unreliable. Therefore, the ninth item was
removed. As a result, the scale had moderately high reliability for both
samples (\(\alpha\) = 0.72 for Sample 1, (\(\alpha\) = 0.74 for Sample
2).

\subsubsection{Career Aspirations}\label{career-aspirations}

To conceptualize participants' career aspirations after the interaction,
we used the 10-item adaptation of P. Gray and M. OBrien (2007)'s Career
Aspiration Scale employed in Garcia et al. (2016), which asked
participants to consider how true 10 statements were in regard to their
future careers on a scale from 0 (not at all true of me) to 4 (very true
of me). Items include \enquote{I hope to become a leader in my career
field} and \enquote{I hope to move up through any organization or
business I work in.} Items were fairly reliable (\(\alpha\) = 0.73 for
Sample 1, \(\alpha\) = 0.80 for Sample 2).

\subsubsection{Trait
Self-Objectification}\label{trait-self-objectification}

Trait self-objectification (TSO) was assessed using the
Self-Objectification Questionnaire (L. Fredrickson et al., 1998; M. Noll
\& L. Fredrickson, 1998), which evaluates the extent to which
individuals view their bodies in observable versus nonobservable ways.
The questionnaire asked participants to rank order both appearance and
functional aspects of their bodies, from 1 (least important) to 10 (most
important), with respect to physical self-concepts. Of the ten body
attributes, five of the items were appearance-based (weight, sex appeal,
physical attractiveness, firm/sculpted muscles and body measurements),
and five of the items were competence-based (strength, physical
coordination, energy level, health and physical fitness). Difference
scores were computed by subtracting the sum of the 5 functional
aspects/competence attributes (e.g., health, strength) from the sum of
the 5 physical self-concepts/appearance attributes (e.g., physical
attractiveness, weight), and all measures were multiplied by -1, as was
done in Garcia et al. (2016), so that positive scores indicated greater
TSO.

\subsubsection{Description of the
Samples}\label{description-of-the-samples}

Thirty-two previously unacquainted self-identifying female-sex dyads (64
total participants) from two liberal arts institutions in the Northeast
of the United States participated in this study. More specifically,
twelve of the pairs, which derived from Sample 1, were students at a
co-ed liberal arts college, while the remaining twenty pairs who came
from Sample 2 attended a women's liberal arts college. Initially, data
was collected from same-sex and mixed-sex dyads that comprised of male
and female gendered individuals. Sample 1 originally consisted of
twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs
made up of forty-three women and one man, as well as two participants
who did not identify with either gender category, formed Sample 2. Due
to similarities across samples in regard to correlation patterns between
significant variables within this study, the two datasets were combined.
For consistency, we limited participant data to same sex female pairs at
the two colleges. These participants were mostly first-year college
students, with an average age of 18.85 (SD = 1.04). The sample was
48.44\% White/European American, 9.38\% Black/African-American, 28.12\%
Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
8 White/White pairs and 4 same race racial minority pairs, for a total
of 12 same-race pairs. The remaining 20 were mixed race pairs, of which
15 were White/racial minority pairings and 5 were cross-racial minority
group pairs. 64.06\% of the sample identified as heterosexual, and 25\%
identified as gay, lesbian or bisexual.

\subsection{Data analysis}\label{data-analysis}

We used R (Version 3.4.1; R Core Team, 2017) and the R-packages
\emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools}
(Version 2.0.1; Wickham, Hester, \& Chang, 2018), \emph{dplyr} (Version
0.8.0.1; Wickham, François, Henry, \& Müller, 2018), \emph{forcats}
(Version 0.3.0; Wickham, 2018), \emph{ggformula} (Version 0.6; D. Kaplan
\& Pruim, 2017), \emph{ggplot2} (Version 3.1.0.9000; Wickham, 2016),
\emph{haven} (Version 2.1.0; Wickham \& Miller, 2019), \emph{irr}
(Version 0.84; Gamer, Lemon, \&
\textless{}puspendra.pusp22@gmail.com\textgreater{}, 2012), \emph{knitr}
(Version 1.22; Xie, 2015), \emph{kutils} (Version 1.67; Johnson, Kite,
\& Redmon, 2019), \emph{lattice} (Version 0.20.35; Sarkar, 2008),
\emph{lavaan} (Version 0.6.3; Rosseel, 2012), \emph{lpSolve} (Version
5.6.13; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.10; Bates
\& Maechler, 2017), \emph{mosaic} (Version 1.1.0; Pruim, Kaplan, \&
Horton, 2017, 2016), \emph{mosaicData} (Version 0.14.0; Pruim et al.,
2016), \emph{nlme} (Version 3.1.131; Pinheiro, Bates, DebRoy, Sarkar, \&
R Core Team, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
2018), \emph{psych} (Version 1.7.8; Revelle, 2017), \emph{purrr}
(Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.1.1;
Wickham, Hester, \& Francois, 2017), \emph{stringr} (Version 1.4.0;
Wickham, 2019), \emph{tibble} (Version 2.1.1; Müller \& Wickham, 2019),
\emph{tidyr} (Version 0.8.3; Wickham \& Henry, 2019), \emph{tidyverse}
(Version 1.2.1; Wickham, 2017), \emph{usethis} (Version 1.4.0; Wickham
\& Bryan, 2018), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen,
Magnusson, \& Swinton, 2019) for all our analyses.

\section{Results}\label{results}

\subsection{Analysis Strategy}\label{analysis-strategy}

This study sought to replicate the results of Garcia et al. (2016)'s
study, done with male-female pairs, which used dyadic analysis to detect
whether partners' objectification of one another affected state
self-objectification (SSO). See Figure~\ref{fig:2016figure} for the path
analysis results of the previous study. We hope to investigate how the
main effects found in the previous study relay to interactions between
women: specifically, the relationship between state-other
objectification and self-state objectification and the resulting effect
of self-state objectification on inauthenticity during the interaction.

We used path analysis to obtain our estimates, but because our sample is
nonindependent, we used the indistinguishable actor--partner
interdependence model (Olsen \& Kenny, 2006). The APIM can be defined as
a \enquote{model of dyadic relationships that integrates a conceptual
view of interdependence with the appropriate statistical techniques for
measuring and testing it} (Olsen \& Kenny, 2006). See
Figure~\ref{fig:apim} for a basic APIM model. Unlike the original Garcia
et al. (2016) study, our study deals with indistinguishable dyads,
meaning the designation of who is designated as \enquote{actor} and who
is designated as \enquote{partner} is arbitrary. Due to constraints of
the basic APIM, in that this was an exploration of indistinguishable
female dyads, we had to fix all path estimates to be the same
across/between people and partners, in addition to all variances,
covariances, endogenous intercepts, and exogenous means. Due to the
complexity of the original Garcia et al. (2016) study, we also had to
set the exogenous covariances equal. More specifically, the covariances
between TSO, actor and partner objectification, and the interaction
between actor TSO and partner objectification (and vice versa).

In order to interpret model fit, which refers to the ability of a model
to reproduce the data (i.e., usually the varience-covariance matrix) we
utilized both the I-SAT (saturated) model, and the Null model to ensure
that all possible corresponding covariences are fixed to be equal across
partners. We obtained fit estimates by subtracting the chi-square
estimate for the I-SAT model from the analysis model (Olsen \& Kenny,
2006, Peugh, DiLillo, and Panuzio (2013)).

\subsection{Main Results}\label{main-results}

All model estimates and p-values are found in Table~\ref{tab:sem}. The
most important findings from Garcia et al. (2016) were the significant
partner effect between actor SSO and partner objectification
(specifically men's objectification of women and women's SSO), and the
link between actor SSO and actor authenticity (also specifically for
women). We did not find a significant effect between actor SSO and actor
authenticity (\(\beta\)= -.10, \(p\)=.38), which means we do not have
evidence to support the idea that partner objectification is the cause
for the negative effects related to relationship inauthenticity.
However, we did find a significant relationship between partner
objectification and actor SSO (\(\beta\)= .25, \(p\)=.03), which
supports our hypothesis that objectification from other women also
causes women to self-objectify just as it does in interactions between
male-female pairs. We also found a significantly negative effect of
authenticity on career aspirations (\(\beta\)= .18, \(p\)=.01) and
relationship agency (\(\beta\)=.27, \(p\)=.01). We found that the model
had good fit (\(\chi^2\)=22.33, \(df\)=34). In this case, a good fit
indicates that there are no direct effects of SSO or SOO on the outcomes
on cognitive performance, relationship agency, and career aspirations,
which indicates that the path we chose makes sense.

\section{Discussion}\label{discussion}

As stated previously, we did not find a significant effect between actor
SSO and actor authenticity (\(\beta\)= -.10, \(p\)=.38), which suggests
that there is not sufficient evidence to support the claim that partner
objectification is the cause for the diverse range of negative effects
related to relationship inauthenticity. However, we did observe a
significant partner effect of objectification on actor
self-objectification, which does align with our hypothesis that
theorized objectification from other women can also cause women to
self-objectify just as they do within interactions between male-female
pairs. The results of this study demonstrate the complex and ambivalent
nature of female sexual objectification and additionally highlight the
psychological and social consequences of such objectification processes
on women's social relationships and well-being. The sample of the
current study was comprised of Western women, being that sexual
objectification is most prevalent in this culture (Loughnan et al.,
2015), and research on objectification conducted outside of Western or
Westernized countries is scarce (Moradi \& Huang, 2008). Because
\enquote{bodies exist within social and cultural contexts, and hence are
also constructed through sociocultural practices and discourses}
(Roberts \& Fredrickson, 1997, p. 174), it is important to consider how
diverse social identities within unique cultural contexts may inform
sexual objectification phenomenon to test the cross-cultural
applicability of theoretical frameworks (Loughnan et al., 2015).
Further, sexualzing experiences and self-objectification are thought to
begin a very young age, and thus, researchers have only recently begun
to examine such experiences among children (Bury, Tiggemann, \& Slater,
2016; e.g., Holland \& Haslam, 2016; Jongenelis, Byrne, \& Pettigrew,
2014). Considering the fact that the average mean age of the
investigated participants of this current study was 18.85 years,
research among younger and older individuals is needed, especially
because self-objectification may change over time (Roberts \&
Fredrickson, 1997). It may be valuable to question the extent to which
children, adolescents, or emerging adults of different races or
ethnicities are exposed to varied amounts of sexulizing content. Also,
future experiments or longitudinal studies should explore the external
validity of the notions of self-objectification and how the
operalization of self-objectification may be improved. Regardless, the
results from the current analysis highlight how subtle forms of sexist
discrimination operate to inform prevention and intervention efforts in
both clinical and educational contexts. These results are quite useful
for promoting mental health and within early action programs for girls
and young women, where scholars and practitioners might provide the
tools necessary to circumvent or mitigate negative effects on
self-objectification, and combat such experiences.

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:corrtable}Correlations among study variables.}
\begin{tabular}{llllllll}
\toprule
 & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5}\\
\midrule
Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  & \\
Actor's authenticity of interaction & 5.23 & 1.02 & -.02 &  &  &  & \\
Actor's objectification of partner & -1.58 & 1.21 & .20 & -.07 &  &  & \\
Actor's state self-objectification & 1.92 & 1.13 & .13 & -.10 & -.09 &  & \\
Actor's future relationship agency & 4.69 & 0.96 & .04 & .23+ & .09 & -.09 & \\
Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .11 & .02 & .07\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:descriptives}Descriptive Statistics for Study Variables}
\begin{tabular}{lll}
\toprule
 & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD}\\
\midrule
Actor's trait self objectification (TSO) & -0.35 & 2.64\\
Actor's authenticity of interaction & 5.23 & 1.02\\
Actor's objectification of partner & -1.58 & 1.21\\
Actor's state self-objectification & 1.92 & 1.13\\
Actor's future relationship agency & 4.69 & 0.96\\
Actor's cognitive performance & 5.03 & 2.29\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:sem}Estimates from final Path Analysis Model}
\small{
\begin{tabular}{lllllll}
\toprule
Path & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{z-value} & \multicolumn{1}{c}{p-value}\\
\midrule
Actor SSO & \textasciitilde{} & Actor TSO & 0.08 & 0.09 & 0.91 & 0.36\\
Actor SSO & \textasciitilde{} & Actor Obj. of Partner & -0.17 & 0.12 & -1.41 & 0.16\\
Actor SSO & \textasciitilde{} & Partner Obj. of Actor & 0.25 & 0.12 & 2.15 & 0.03\\
Actor SSO & \textasciitilde{} & Actor TSO x Partner Obj. & 0.00 & 0.04 & -0.10 & 0.92\\
Actor Authenticity & \textasciitilde{} & Actor SSO & -0.10 & 0.12 & -0.88 & 0.38\\
Actor Cog. Performance & \textasciitilde{} & Actor Authenticity & 0.33 & 0.27 & 1.22 & 0.22\\
Actor Career Aspirations & \textasciitilde{} & Actor Authenticity & 0.18 & 0.07 & 2.66 & 0.01\\
Actor Rel. Agency & \textasciitilde{} & Actor Authenticity & 0.27 & 0.10 & 2.64 & 0.01\\
\bottomrule
\end{tabular}
}
\end{threeparttable}
\end{center}
\end{table}

\begin{figure}
\includegraphics[width=400px]{APIM_figure} \caption{Basic actor-partner interdependence model (APIM) depiction.}\label{fig:apim}
\end{figure}

\begin{figure}
\includegraphics[width=400px]{2016_figure} \caption{Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads.}\label{fig:2016figure}
\end{figure}

\begin{figure}
\includegraphics[width=400px]{SEMfigure} \caption{Path Analysis Model with Estimates}\label{fig:semfigure}
\end{figure}

\newpage

\section{References}\label{references}

\begin{verbatim}
## [1] "R [Version 3.4.1; @R-base]"
\end{verbatim}

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-argyle1969}{}
Argyle, M., \& Williams, M. (1969). Observer or observed? A reversible
perspective in person perception. \emph{Sociometry}, 396--412.

\hypertarget{ref-R-papaja}{}
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\hypertarget{ref-Bartky}{}
Bartky, S. L. (1990). Femininity and domination studies in the
phenomenology of oppression.

\hypertarget{ref-R-Matrix}{}
Bates, D., \& Maechler, M. (2017). \emph{Matrix: Sparse and dense matrix
classes and methods}. Retrieved from
\url{https://CRAN.R-project.org/package=Matrix}

\hypertarget{ref-berger1972}{}
Berger, J., Cohen, B. P., \& Zelditch Jr, M. (1972). Status
characteristics and social interaction. \emph{American Sociological
Review}, 241--255.

\hypertarget{ref-R-lpSolve}{}
Berkelaar, M., \& others. (2015). \emph{LpSolve: Interface to
'lp\_solve' v. 5.5 to solve linear/integer programs}. Retrieved from
\url{https://CRAN.R-project.org/package=lpSolve}

\hypertarget{ref-briton1995}{}
Briton, N. J., \& Hall, J. A. (1995). Beliefs about female and male
nonverbal communication. \emph{Sex Roles}, \emph{32}(1-2), 79--90.

\hypertarget{ref-brunelletal2010}{}
Brunell, A. B., Kernis, M. H., Goldman, B. M., Heppner, W., Davis, P.,
Cascio, E. V., \& Webster, G. D. (2010). Dispositional authenticity and
romantic relationship functioning. \emph{Personality and Individual
Differences}, \emph{48}(8), 900--905.
doi:\href{https://doi.org/10.1016/j.paid.2010.02.018}{10.1016/j.paid.2010.02.018}

\hypertarget{ref-bury2016}{}
Bury, B., Tiggemann, M., \& Slater, A. (2016). Disclaimer labels on
fashion magazine advertisements: Impact on visual attention and
relationship with body dissatisfaction. \emph{Body Image}, \emph{16},
1--9.

\hypertarget{ref-calogero2011}{}
Calogero, R. M., Tantleff-Dunn, S. E., \& Thompson, J. (2011).
\emph{Self-objectification in women: Causes, consequences, and
counteractions.} American Psychological Association.

\hypertarget{ref-R-xtable}{}
Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J.
(2019). \emph{Xtable: Export tables to latex or html}. Retrieved from
\url{https://CRAN.R-project.org/package=xtable}

\hypertarget{ref-Kaschak}{}
Engendered lives: A new psychology of womens experience. (1993).
\emph{Choice Reviews Online}, \emph{30}(07).
doi:\href{https://doi.org/10.5860/choice.30-4102}{10.5860/choice.30-4102}

\hypertarget{ref-frasernicholson1989}{}
Fraser, N., \& Nicholson, L. (1989). Social criticism without
philosophy: An encounter between feminism and postmodernism.
\emph{Social Text}, (21), 83.
doi:\href{https://doi.org/10.2307/827810}{10.2307/827810}

\hypertarget{ref-fredricksonetal2011}{}
Fredrickson, B. L., Hendler, L. M., Nilsen, S., O'Barr, J. F., \&
Roberts, T.-A. (2011). Bringing back the body. \emph{Psychology of Women
Quarterly}, \emph{35}(4), 689--696.
doi:\href{https://doi.org/10.1177/0361684311426690}{10.1177/0361684311426690}

\hypertarget{ref-R-irr}{}
Gamer, M., Lemon, J., \&
\textless{}puspendra.pusp22@gmail.com\textgreater{}, I. F. P. S. (2012).
\emph{Irr: Various coefficients of interrater reliability and
agreement}. Retrieved from \url{https://CRAN.R-project.org/package=irr}

\hypertarget{ref-garcia2016objectification}{}
Garcia, R. L., Earnshaw, V. A., \& Quinn, D. M. (2016). Objectification
in action: Self-and other-objectification in mixed-sex interpersonal
interactions. \emph{Psychology of Women Quarterly}, \emph{40}(2),
213--228.

\hypertarget{ref-R-purrr}{}
Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

\hypertarget{ref-holland2016}{}
Holland, E., \& Haslam, N. (2016). Cute little things: The
objectification of prepubescent girls. \emph{Psychology of Women
Quarterly}, \emph{40}(1), 108--119.

\hypertarget{ref-R-kutils}{}
Johnson, P., Kite, B., \& Redmon, C. (2019). \emph{Kutils: Project
management tools}. Retrieved from
\url{https://CRAN.R-project.org/package=kutils}

\hypertarget{ref-jongenelis2014}{}
Jongenelis, M. I., Byrne, S. M., \& Pettigrew, S. (2014).
Self-objectification, body image disturbance, and eating disorder
symptoms in young australian children. \emph{Body Image}, \emph{11}(3),
290--302.

\hypertarget{ref-R-ggformula}{}
Kaplan, D., \& Pruim, R. (2017). \emph{Ggformula: Formula interface to
the grammar of graphics}. Retrieved from
\url{https://CRAN.R-project.org/package=ggformula}

\hypertarget{ref-fredricksonetal1998}{}
L. Fredrickson, B., Roberts, T.-A., M. Noll, S., Quinn, D., \& Twenge,
J. (1998). That swimsuit becomes you: Sex differences in
self-objedification, restrained eating, and math performance.
\emph{Journal of Personality and Social Psychology}, \emph{75}, 269--84.
doi:\href{https://doi.org/10.1037/0022-3514.75.1.269}{10.1037/0022-3514.75.1.269}

\hypertarget{ref-loughnan2015}{}
Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
Harada, C., \ldots{} Tsuchiya, K. (2015). Exploring the role of culture
in sexual objectification: A seven nations study. \emph{Revue
Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.

\hypertarget{ref-nollfredrickson1998}{}
M. Noll, S., \& L. Fredrickson, B. (1998). A mediational model linking
self-objectification, body shame, and disordered eating.
\emph{Psychology of Women Quarterly}, \emph{22}, 623--636.
doi:\href{https://doi.org/10.1111/j.1471-6402.1998.tb00181.x}{10.1111/j.1471-6402.1998.tb00181.x}

\hypertarget{ref-mcfarlin1984remote}{}
McFarlin, D. B., \& Blascovich, J. (1984). On the remote associates test
(rat) as an alternative to illusory performance feedback: A
methodological note. \emph{Basic and Applied Social Psychology},
\emph{5}(3), 223--229.

\hypertarget{ref-moradi2008}{}
Moradi, B., \& Huang, Y.-P. (2008). Objectification theory and
psychology of women: A decade of advances and future directions.
\emph{Psychology of Women Quarterly}, \emph{32}(4), 377--398.

\hypertarget{ref-R-tibble}{}
Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
Retrieved from \url{https://CRAN.R-project.org/package=tibble}

\hypertarget{ref-olsen2006structural}{}
Olsen, J. A., \& Kenny, D. A. (2006). Structural equation modeling with
interchangeable dyads. \emph{Psychological Methods}, \emph{11}(2), 127.

\hypertarget{ref-grayobrien2007}{}
P. Gray, M., \& M. OBrien, K. (2007). Advancing the assessment of
women's career choices: The career aspiration scale. \emph{Journal of
Career Assessment - J CAREER ASSESSMENT}, \emph{15}, 317--337.
doi:\href{https://doi.org/10.1177/1069072707301211}{10.1177/1069072707301211}

\hypertarget{ref-peugh2013analyzing}{}
Peugh, J. L., DiLillo, D., \& Panuzio, J. (2013). Analyzing mixed-dyadic
data using structural equation models. \emph{Structural Equation
Modeling: A Multidisciplinary Journal}, \emph{20}(2), 314--337.

\hypertarget{ref-R-nlme}{}
Pinheiro, J., Bates, D., DebRoy, S., Sarkar, D., \& R Core Team. (2017).
\emph{nlme: Linear and nonlinear mixed effects models}. Retrieved from
\url{https://CRAN.R-project.org/package=nlme}

\hypertarget{ref-R-mosaic}{}
Pruim, R., Kaplan, D. T., \& Horton, N. J. (2017). The mosaic package:
Helping students to 'think with data' using r. \emph{The R Journal},
\emph{9}(1), 77--102. Retrieved from
\url{https://journal.r-project.org/archive/2017/RJ-2017-024/index.html}

\hypertarget{ref-R-mosaicData}{}
Pruim, R., Kaplan, D., \& Horton, N. (2016). \emph{MosaicData: Project
mosaic data sets}. Retrieved from
\url{https://CRAN.R-project.org/package=mosaicData}

\hypertarget{ref-quinnetal}{}
Quinn, D. M., Chaudoir, S. R., \& Kallen, R. W. (2011). Performance and
flow: A review and integration of self-objectification research.
\emph{Self-Objectification in Women: Causes, Consequences, and
Counteractions.}, 119--138.
doi:\href{https://doi.org/10.1037/12304-006}{10.1037/12304-006}

\hypertarget{ref-R-base}{}
R Core Team. (2017). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\hypertarget{ref-R-psych}{}
Revelle, W. (2017). \emph{Psych: Procedures for psychological,
psychometric, and personality research}. Evanston, Illinois:
Northwestern University. Retrieved from
\url{https://CRAN.R-project.org/package=psych}

\hypertarget{ref-robertsfredrickson}{}
Roberts, T.-A., \& Fredrickson, B. L. (1997). Objectification theory.
\emph{Encyclopedia of Social Psychology}.
doi:\href{https://doi.org/10.4135/9781412956253.n377}{10.4135/9781412956253.n377}

\hypertarget{ref-R-lavaan}{}
Rosseel, Y. (2012). lavaan: An R package for structural equation
modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36.
Retrieved from \url{http://www.jstatsoft.org/v48/i02/}

\hypertarget{ref-rubin1975}{}
Rubin, J. (1975). What the ``good language learner'' can teach us.
\emph{TESOL Quarterly}, \emph{9}(1), 41.
doi:\href{https://doi.org/10.2307/3586011}{10.2307/3586011}

\hypertarget{ref-saguyetal2010}{}
Saguy, T., Quinn, D., F Dovidio, J., \& Pratto, F. (2010). Interacting
like a body: Objectification can lead women to narrow their presence in
social interactions. \emph{Psychological Science}, \emph{21}, 178--82.
doi:\href{https://doi.org/10.1177/0956797609357751}{10.1177/0956797609357751}

\hypertarget{ref-R-lattice}{}
Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with
r}. New York: Springer. Retrieved from
\url{http://lmdvr.r-forge.r-project.org}

\hypertarget{ref-R-apaTables}{}
Stanley, D. (2018). \emph{ApaTables: Create american psychological
association (apa) style tables}. Retrieved from
\url{https://CRAN.R-project.org/package=apaTables}

\hypertarget{ref-swimetal}{}
Swim, J. K., Hyers, L. L., Cohen, L. L., \& Ferguson, M. J. (2001).
Everyday sexism: Evidence for its incidence, nature, and psychological
impact from three daily diary studies. \emph{Journal of Social Issues},
\emph{57}(1), 31--53.
doi:\href{https://doi.org/10.1111/0022-4537.00200}{10.1111/0022-4537.00200}

\hypertarget{ref-R-ggplot2}{}
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
Springer-Verlag New York. Retrieved from
\url{https://ggplot2.tidyverse.org}

\hypertarget{ref-R-tidyverse}{}
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
'tidyverse'}. Retrieved from
\url{https://CRAN.R-project.org/package=tidyverse}

\hypertarget{ref-R-forcats}{}
Wickham, H. (2018). \emph{Forcats: Tools for working with categorical
variables (factors)}. Retrieved from
\url{https://CRAN.R-project.org/package=forcats}

\hypertarget{ref-R-stringr}{}
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for
common string operations}. Retrieved from
\url{https://CRAN.R-project.org/package=stringr}

\hypertarget{ref-R-usethis}{}
Wickham, H., \& Bryan, J. (2018). \emph{Usethis: Automate package and
project setup}. Retrieved from
\url{https://CRAN.R-project.org/package=usethis}

\hypertarget{ref-R-tidyr}{}
Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Easily tidy data with
'spread()' and 'gather()' functions}. Retrieved from
\url{https://CRAN.R-project.org/package=tidyr}

\hypertarget{ref-R-haven}{}
Wickham, H., \& Miller, E. (2019). \emph{Haven: Import and export
'spss', 'stata' and 'sas' files}. Retrieved from
\url{https://CRAN.R-project.org/package=haven}

\hypertarget{ref-R-dplyr}{}
Wickham, H., François, R., Henry, L., \& Müller, K. (2018). \emph{Dplyr:
A grammar of data manipulation}. Retrieved from
\url{https://CRAN.R-project.org/package=dplyr}

\hypertarget{ref-R-devtools}{}
Wickham, H., Hester, J., \& Chang, W. (2018). \emph{Devtools: Tools to
make developing r packages easier}. Retrieved from
\url{https://CRAN.R-project.org/package=devtools}

\hypertarget{ref-R-readr}{}
Wickham, H., Hester, J., \& Francois, R. (2017). \emph{Readr: Read
rectangular text data}. Retrieved from
\url{https://CRAN.R-project.org/package=readr}

\hypertarget{ref-R-knitr}{}
Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.).
Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from
\url{https://yihui.name/knitr/}

\hypertarget{ref-young1979}{}
Young, I. M. (1979). \emph{Proceedings of the second sex---Thirty years
later: A commemorative conference on feminist theory,}

\endgroup

\end{document}

### 2019-05-09 Variable creation.Rmd
adding all the changes i've made!

@@
 #Relationship Agency
-clark_measures$relag <- rowMeans(dplyr::select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))
+#Reverse code relationship agency 9
+clark_measures <- clark_measures %>%
+  mutate(relag_9.r=(min(relag_9, na.rm=TRUE) + max(relag_9, na.rm=TRUE) - relag_9))
+
+clark_measures$relag <- rowMeans(dplyr::select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
 
@@
 #Relationship Agency
-smith$relag <- rowMeans(dplyr::select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))
+
+smith <- smith %>%
+  mutate(relag_9.r=(min(relag_9, na.rm=TRUE) + max(relag_9, na.rm=TRUE) - relag_9))
+
+smith$relag <- rowMeans(dplyr::select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
 
@@
 smith$TSO <- smith$TSO*-1
+
+#Write out csv with created variables
+write.csv(clark_measures, "Cleaned data/clark_measures.csv")
+write.csv(smith, "Cleaned data/smith.csv")
 ```
@@
 ```{r}
-write.csv(smith_final, "ObjectInAction/Cleaned data/smith_final.csv" )
-write.csv(clark_final, "ObjectInAction/Cleaned data/clark_final.csv")
+write.csv(smith_final, "Cleaned data/smith_final.csv" )
+write.csv(clark_final, "Cleaned data/clark_final.csv")
 ```

### 2020-01-23 i-sat_fit_statistics.Rmd
some random files I had

```{r}
chi_isat <- 89.135
df_isat <- 75

#this is definitely right  
chi_mod <- 120.502
df_mod <- 112

chi_null <- 218.844
df_null <- 129
```

adjust

```{r}
chi_mod_adj <- chi_mod - chi_isat
df_mod_adj <- df_mod - df_isat

chi_null_adj <- chi_null - chi_isat
df_null_adj <- df_null - df_isat
```

Chi-square test for model fit

```{r}
pchisq(chi_mod_adj, df_mod_adj, lower.tail = FALSE)
```

Fit statistics

```{r}
RMSEA <- sqrt(((chi_mod_adj/df_mod_adj)-1)/(32-1))
chi_mod_adj/df_mod_adj-1
sqrt(-.15/31)

#Trying to take square root of negative number...so zero. Because df is smaller than chi-sqaure. 
RMSEA <- 0 
```

```{r}
CFI <- 1-((chi_mod_adj-df_mod_adj)/(chi_null_adj-df_null_adj))
CFI
```

### 2020-02-29 Final_Manuscript.Rmd
Small edits to absratct and intro structure.

@@
 abstract: |
-  Objectification theory is a valuable framework for conceptualizing the psychological consequences of being female within a society that sexually objectifies the female body, and considering the ways in which girls and women are acculturated to then internalize an observer’s perspective as a primary view of their appearance.
-Empirical evidence has largely elucidated links between objectification, self-objectification, and negative outcomes for woman within interpersonal interactions between male-female pairs particularly.
+  Empirical evidence has only found links between objectification, self-objectification, and negative outcomes for woman within interpersonal interactions between male-female pairs.
 The purpose of the present study was to extend past research and consider the relationships between such valuable phenomena and their effects on authenticity within interactions between female pairs.
@@
 #SOO
-clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10))$total[2]
+clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, 
+                                          otherint_5, otherint_6, otherint_10))$total[2]
 
-clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
+clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, 
+                                          otherint_7, otherint_8, otherint_9, otherint_11, 
+                                          otherint_12))$total[2]
 #Smith
-smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10))$total[2]
-smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
+smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, 
+                                          otherint_6, otherint_10))$total[2]
+smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, 
+                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
 
@@
 #Clark
-clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))$total[2]
+clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, 
+                                           inter_6, inter_7, inter_9, inter_10, interaux_5, 
+                                           interaux_6))$total[2]
 #Smith
-smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))$total[2]
+smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, 
+                                           inter_7, inter_9, inter_10, interaux_5, 
+                                           interaux_6))$total[2]
 
@@
 #Clark
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))$total[2]
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
+                                         relag_4, relag_5, relag_6, relag_7, relag_8, 
+                                         relag_9.r))$total[2]
 #Smith
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))$total[2]
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
+                                         relag_5, relag_6, relag_7, relag_8, 
+                                         relag_9.r))$total[2]
 ##DROPPING ITEM 9
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
+                                         relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
+
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
+                                         relag_5, relag_6, relag_7, relag_8))$total[2]
 
@@
 clark_physTSO_alpha <- psych::alpha(select(clark_measures,tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
+
 #Smith--external and internal
@@
 Objectification theory, a valuable theoretical framework proposed by @robertsfredrickson which works to contextualize female bodies as socio-cultural constructions, can be employed to illuminate the gender oppression and negative lived experiences of girls and women.
+
 Additionally, one of the most detrimental forms of discrimination against them is thought to be the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
@@
 @calogero2011 proposes that the construct of self-objectification can be conceptualized as a learned trait.
+
 Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@calogero2011, @moradi2008].
 Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO).
+
 In the current work, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification,  but between same-sex female interpersonal interactions.
@@
 Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@swimetal].
+
 Moreover, it was the goal of this research to empirically explore the role of interaction authenticity in objectification by utilizing a structural equation modeling to examine the effects for both women simultaneously.

### 2020-06-22 Final_Manuscript.Rmd
change author order, affiliation

@@
 author: 
+  - name          : "Randi L. Garcia"
+    affiliation   : "1, 2"
+    corresponding : yes    # Define only one corresponding author
+    address       : "415 Bass Hall, Smith College, Northampton, MA 01060"
+    email         : "rgarcia@smith.edu"
   - name          : "Kat Kyuchukova"
@@
     affiliation   : "1"
-  - name          : "Randi L. Garcia"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    affiliation   : "1"
 
@@
   - id            : "1"
-    institution   : "Smith College"
+    institution   : "Department of Psychology, Smith College"
+  - id            : "2"
+    institution   : "Program in Statistical and Data Sciences, Smith College"
 
@@
 
-#Introduction
 Theorists across diverse disciplines have explored the multiple ways that the body conveys social meaning, as well as how these meanings shape gendered experiences and therefore inform individuals’ thinking, feeling, and behavior, especially during interpersonal interactions with members of different social groups [@Kaschak].

### 2020-06-23 Final_Manuscript.Rmd
recorganized text and code

@@
 
-```{r setup, include = FALSE}
+```{r setup, analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, include = FALSE)
+```
+
+```{r packages}
 library(papaja)
@@
 library(xtable)
-clark_measures <- read.csv("Cleaned data/clark_measures.csv")
-smith <- read.csv("Cleaned data/smith.csv")
-clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-```{r, include=FALSE}
-#######Alphas
-
-###SOO
-
-#Clark
-#SOO
-clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, 
-                                          otherint_5, otherint_6, otherint_10))$total[2]
-
-clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, 
-                                          otherint_7, otherint_8, otherint_9, otherint_11, 
-                                          otherint_12))$total[2]
-#Smith
-smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, 
-                                          otherint_6, otherint_10))$total[2]
-smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, 
-                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
-
-##Interaction Authenticity
-#Clark
-clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, 
-                                           inter_6, inter_7, inter_9, inter_10, interaux_5, 
-                                           interaux_6))$total[2]
-#Smith
-smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, 
-                                           inter_7, inter_9, inter_10, interaux_5, 
-                                           interaux_6))$total[2]
-
-##SSO
-#Clark
-clark_howbody_alpha<- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
-#Smith
-smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]
-#with 3
-clark_howbody3 <- psych::alpha(select(clark_measures, howbody_1, howbody_2, howbody_3))
-smith_howbody3 <- psych::alpha(select(smith, howbody_1, howbody_2, howbody_3))
-
-##Relationship Agency
-#Clark
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
-                                         relag_4, relag_5, relag_6, relag_7, relag_8, 
-                                         relag_9.r))$total[2]
-#Smith
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
-                                         relag_5, relag_6, relag_7, relag_8, 
-                                         relag_9.r))$total[2]
-##DROPPING ITEM 9
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
-                                         relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
-
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
-                                         relag_5, relag_6, relag_7, relag_8))$total[2]
-
-corr.test(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
-corr.test(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
-
-##Career Aspirations
-#Clark
-clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
-  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
-         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
-         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
-
-clark_careerasp_alpha <- psych::alpha(select(clark_measures, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))$total[2]
-
-#Smith
-smith <- smith %>% #reverse code certain career aspiration variables
-  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
-         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
-         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
-
-smith_careerasp_alpha <- psych::alpha(select(smith, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))$total[2]
-
-###TSO
-#Clark--external and internal
-clark_funcTSO_alpha <- psych::alpha(select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
-clark_physTSO_alpha <- psych::alpha(select(clark_measures,tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
-
-#Smith--external and internal
-smith_funcTSO_alpha <- psych::alpha(select(smith,tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
-smith_physTSO_alpha <- psych::alpha(select(smith,tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
-
-#Cognitive performance
-mean_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$mean
-sd_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$sd
-```
-
-```{r, include=FALSE}
-favstats(~TSO_A, data=clarksmith_women)
-favstats(~a2pSOO_A, data=clarksmith_women)
-favstats(~howbody_avg_A, data=clarksmith_women)
-favstats(~relag_A, data=clarksmith_women)
-favstats(~careerasp_A, data=clarksmith_women)
-favstats(~authenticity_A, data=clarksmith_women)
-favstats(~trigram_score_A, data=clarksmith_women)
-
-#Mean and SD of age of sample
-mean_age <- favstats(~age_A, data=clarksmith_women)$mean
-sd_age <- favstats(~age_A, data=clarksmith_women)$sd
-tally(clarksmith_women$race_A==clarksmith_women$race_P)
-
-#Calculating race percentages
-tally(~race_A, data=clarksmith_women)
-percentage_black <- 6/(6+18+31+6+3)*100
-percent_asian <- 18/(6+18+31+6+3)*100
-percent_white <- 31/(6+18+31+6+3)*100
-percent_latinx <- 6/(6+18+31+6+3)*100
-percent_other <- 3/(6+18+31+6+3)*100
-tally(~sexor_A, data=clarksmith_women)
-percent_straight <-(41/64)*100
-percent_queer <- (3+8+5)/64*100
-tally(~gender_A, data=clarksmith_women)
-
-table(clarksmith_women$race_A, clarksmith_women$race_P)
-samerace_white <- 16/2 #divide by 2 since table is people, not pairs
-samerace_minority <- (6+2)/2
-mixedrace_white <- 2+10+2+1
-mixedrace_minority <- 1+2+1+1
-
-test <- clarksmith_women %>%
-  filter(race_A==3, race_A!=race_P)
-
-tally(~gender, data=clark_measures)
-tally(~gender, data=smith)
-
-clarksmith_correlations <- clarksmith_women %>%
-  select(TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, relag_A, careerasp_A,  trigram_score_A, TSO_P, authenticity_P, a2pSOO_P, howbody_avg_P, relag_P, careerasp_P, trigram_score_P)
-
-#Correlation tables
-correlations <- apa.cor.table(clarksmith_correlations, table.number=1)
-
 ```
@@
 
+```{r data}
+clark_measures <- read.csv("Cleaned data/clark_measures.csv")
+smith <- read.csv("Cleaned data/smith.csv")
+clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
+```
+
 ##Combining Samples
@@
 
-##Post interaction Measures
-The following measures were collected in the order they are presented following the interaction.
-Correlations appear in Table\ \@ref(tab:corrtable), and descriptive statistics appear in Table\ \@ref(tab:descriptives).
+```{r alphas}
+#######Alphas
 
-###Cognitive Performance
-Trigrams from the Remote Associates Task [@mcfarlin1984remote] were utilized to assess cognitive performance after the interaction.
-Ten items were selected and presented to participants.
-For example, the correct answer for the trigram “Quack: Pond: Waddle” would be “Duck”.
-Participants are limited to 30 seconds.
-For every correct answer, 1 point is given.
-The mean score was `r mean_trigram` (SD = `r sd_trigram`).
-Cognitive performance was measured first in order to measure potential immediate detriments to performance [@garcia2016objectification].
+##SOO
+#Clark
+clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, 
+                                          otherint_5, otherint_6, otherint_10))$total[2]
+clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, 
+                                          otherint_7, otherint_8, otherint_9, otherint_11, 
+                                          otherint_12))$total[2]
+#Smith
+smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, 
+                                          otherint_6, otherint_10))$total[2]
+smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, 
+                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
 
-###State Other-Objectification
-To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner @garcia2016objectification.
-Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
-All questions were to be rated on a scale from 1 (not at all) to 7 (constantly).
-Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2).
-A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
+##Interaction Authenticity
+#Clark
+clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, 
+                                           inter_6, inter_7, inter_9, inter_10, interaux_5, 
+                                           interaux_6))$total[2]
+#Smith
+smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, 
+                                           inter_7, inter_9, inter_10, interaux_5, 
+                                           interaux_6))$total[2]
 
-###Interaction Authenticity
-To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike [@garcia2016objectification].
-Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: ‘‘Do you think your partner was authentic during your interaction?’’ and ‘‘Were you authentic during your interaction?’’ These questions were ranked on a scale from 1 (not authentic at all).
-These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
+##SSO
+#Clark - two items
+clark_howbody_alpha<- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
+#Smith - two items
+smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]
+#Clark - three items
+clark_howbody3 <- psych::alpha(select(clark_measures, howbody_1, howbody_2, howbody_3))
+#Smith - three items
+smith_howbody3 <- psych::alpha(select(smith, howbody_1, howbody_2, howbody_3))
 
-###State Self-Objectification
-To assess state self-objectification, we used an average of two items from @saguyetal2010 that were also used in @garcia2016objectification.
-Participants were asked to rank how much they agreed with the following statements: “During the interaction I felt more like a body than a full self” and “I felt more like a body than as a real person in the interaction”.
-Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
+##Relationship Agency
+#Clark
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
+                                         relag_4, relag_5, relag_6, relag_7, relag_8, 
+                                         relag_9.r))$total[2]
+#Smith
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
+                                         relag_5, relag_6, relag_7, relag_8, 
+                                         relag_9.r))$total[2]
 
-###Relationship Agency
-A scale was used from @garcia2016objectification to assess how much agency an individual believes they would possess in future romantic relationships.
-Participants were asked how likely it was that they would do the following: ‘‘ask someone out on a date,’’ ‘‘open the door for your date,’’ ‘‘pay for a date,’’ ‘‘ask your boyfriend/girlfriend to marry you,’’ ‘‘initiate sex with your girlfriend/boyfriend,’’ ‘‘initiate condom use during sex,’’ ‘‘surprise your boyfriend/ girlfriend with a gift,’’ and ‘‘ask your girlfriend/boyfriend to move with you to a new place.’’ Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
-The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
-The item was intended to be reverse coded, but correlations were still low enough to make the scale unreliable.
-Therefore, the ninth item was removed.
-As a result, the scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
+#corr.test(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+#corr.test(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+##DROPPING ITEM 9
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
+                                         relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
 
-###Career Aspirations
-To conceptualize participants’ career aspirations after the interaction, we used the 10-item adaptation of @grayobrien2007’s Career Aspiration Scale employed in @garcia2016objectification, which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
-Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
+                                         relag_5, relag_6, relag_7, relag_8))$total[2]
 
-###Trait Self-Objectification
-Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
-The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
-Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness).
-Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.
+##Career Aspirations
+#Clark
+clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
+  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
+         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
+         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
 
-###Description of the Samples
-Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
-More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college.
-Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
-Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
-Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
-Due to similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
-For consistency, we limited participant data to same sex female pairs at the two colleges.
-These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
-The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
-There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
-The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
-`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
+clark_careerasp_alpha <- psych::alpha(select(clark_measures, careerasp_1, careerasp_2, 
+                                             careerasp_3, careerasp4.r, careerasp_5, 
+                                             careerasp_6, careerasp7.r, careerasp_8, 
+                                             careerasp_9, careerasp10.r))$total[2]
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+#Smith
+smith <- smith %>% #reverse code certain career aspiration variables
+  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
+         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
+         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
 
-# Results
+smith_careerasp_alpha <- psych::alpha(select(smith, careerasp_1, careerasp_2, 
+                                             careerasp_3, careerasp4.r, careerasp_5, 
+                                             careerasp_6, careerasp7.r, careerasp_8, 
+                                             careerasp_9, careerasp10.r))$total[2]
 
-## Analysis Strategy
+###TSO
+#Clark--external and internal
+clark_funcTSO_alpha <- psych::alpha(select(clark_measures, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
+clark_physTSO_alpha <- psych::alpha(select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
 
-This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used dyadic analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
-See Figure\ \@ref(fig:2016figure) for the path analysis results of the previous study.
-We hope to investigate how the main effects found in the previous study relay to interactions between women: specifically, the relationship between state-other objectification and self-state objectification and the resulting effect of self-state objectification on inauthenticity during the interaction.
+#Smith--external and internal
+smith_funcTSO_alpha <- psych::alpha(select(smith, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
+smith_physTSO_alpha <- psych::alpha(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
 
-We used path analysis to obtain our estimates, but because our sample is nonindependent, we used the indistinguishable actor–partner interdependence model [@olsen2006structural].
-The APIM can be defined as a "model of dyadic relationships that integrates a conceptual view of interdependence with the appropriate statistical techniques for measuring and testing it" [@olsen2006structural].
-See Figure\ \@ref(fig:apim) for a basic APIM model.
-Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
-Due to constraints of the basic APIM, in that this was an exploration of indistinguishable female dyads, we had to fix all path estimates to be the same across/between people and partners, in addition to all variances, covariances, endogenous intercepts, and exogenous means.
-Due to the complexity of the original @garcia2016objectification study, we also had to set the exogenous covariances equal.
-More specifically, the covariances between TSO, actor and partner objectification, and the interaction between actor TSO and partner objectification (and vice versa).
+```
 
-In order to interpret model fit, which refers to the ability of a model to reproduce the data (i.e., usually the varience-covariance matrix) we utilized both the I-SAT (saturated) model, and the Null model to ensure that all possible corresponding covariences are fixed to be equal across partners.
-We obtained fit estimates by subtracting the chi-square estimate for the I-SAT model from the analysis model [@olsen2006structural, @peugh2013analyzing].
+```{r demographics}
+#favstats(~TSO_A, data=clarksmith_women)
+#favstats(~a2pSOO_A, data=clarksmith_women)
+#favstats(~howbody_avg_A, data=clarksmith_women)
+#favstats(~relag_A, data=clarksmith_women)
+#favstats(~careerasp_A, data=clarksmith_women)
+#favstats(~authenticity_A, data=clarksmith_women)
+#favstats(~trigram_score_A, data=clarksmith_women)
 
-##Main Results
-All model estimates and p-values are found in Table\ \@ref(tab:sem).
-The most important findings from @garcia2016objectification were the significant partner effect between actor SSO and partner objectification (specifically men's objectification of women and women's SSO), and the link between actor SSO and actor authenticity (also specifically for women).
-We did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which means we do not have evidence to support the idea that partner objectification is the cause for the negative effects related to relationship inauthenticity.
-However, we did find a significant relationship between partner objectification and actor SSO ($\beta$= .25, $p$=.03), which supports our hypothesis that objectification from other women also causes women to self-objectify just as it does in interactions between male-female pairs.
-We also found a significantly negative effect of authenticity on career aspirations ($\beta$= .18, $p$=.01) and relationship agency ($\beta$=.27, $p$=.01).
-We found that the model had good fit ($\chi^2$=22.33, $df$=34).
-In this case, a good fit indicates that there are no direct effects of SSO or SOO on the outcomes on cognitive performance, relationship agency, and career aspirations, which indicates that the path we chose makes sense.
+#Mean and SD of age of sample
+mean_age <- favstats(~age_A, data = clarksmith_women)$mean
+sd_age <- favstats(~age_A, data = clarksmith_women)$sd
+tally(clarksmith_women$race_A == clarksmith_women$race_P)
 
-# Discussion
-As stated previously, we did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to relationship inauthenticity.
-However, we did observe a significant partner effect of objectification on actor self-objectification, which does align with our hypothesis that theorized objectification from other women can also cause women to self-objectify just as they do within interactions between male-female pairs.
-The results of this study demonstrate the complex and ambivalent nature of female sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
-The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008].
-Because “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015].
-Further, sexualzing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014; @bury2016].
-Considering the fact that the average mean age of the investigated participants of this current study was 18.85 years, research among younger and older individuals is needed, especially because self-objectification may change over time [@robertsfredrickson].
-It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexulizing content.
-Also, future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operalization of self-objectification may be improved.
-Regardless, the results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts.
-These results are quite useful for promoting mental health and within early action programs for girls and young women, where scholars and practitioners might provide the tools necessary to circumvent or mitigate negative effects on self-objectification, and combat such experiences.
+#Calculating race percentages
+tally(~race_A, data = clarksmith_women)  #Note that we can add "format = percentage" and not need to calculate
+percentage_black <- 6/(6+18+31+6+3)*100
+percent_asian <- 18/(6+18+31+6+3)*100
+percent_white <- 31/(6+18+31+6+3)*100
+percent_latinx <- 6/(6+18+31+6+3)*100
+percent_other <- 3/(6+18+31+6+3)*100
+tally(~sexor_A, data=clarksmith_women)
+percent_straight <-(41/64)*100
+percent_queer <- (3+8+5)/64*100
+tally(~gender_A, data=clarksmith_women)
+
+table(clarksmith_women$race_A, clarksmith_women$race_P)
+samerace_white <- 16/2 #divide by 2 since table is people, not pairs
+samerace_minority <- (6+2)/2
+mixedrace_white <- 2+10+2+1
+mixedrace_minority <- 1+2+1+1
+
+test <- clarksmith_women %>%
+  filter(race_A==3, race_A!=race_P)
+
+tally(~gender, data=clark_measures)
+tally(~gender, data=smith)
+```
+
+```{r correaltions}
+clarksmith_correlations <- clarksmith_women %>%
+  select(TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, 
+         relag_A, careerasp_A,  trigram_score_A, TSO_P, 
+         authenticity_P, a2pSOO_P, howbody_avg_P, 
+         relag_P, careerasp_P, trigram_score_P)
+
+#Correlation tables
+correlations <- apa.cor.table(clarksmith_correlations, table.number=1)
+```
+
+```{r trigram}
+#Cognitive performance - Full sample
+mean_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$mean
+sd_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$sd
+```
 
@@
 
-rownames(descriptives) <- c("Actor's trait self objectification (TSO)", "Actor's authenticity of interaction", "Actor's objectification of partner", "Actor's state self-objectification", "Actor's future relationship agency", "Actor's cognitive performance")
+rownames(descriptives) <- c("Actor's trait self objectification (TSO)", 
+                            "Actor's authenticity of interaction", 
+                            "Actor's objectification of partner", 
+                            "Actor's state self-objectification", 
+                            "Actor's future relationship agency", 
+                            "Actor's cognitive performance")
 
@@
 
-```{r, include=FALSE}
+##Post interaction Measures
+The following measures were collected in the order they are presented following the interaction.
+Correlations appear in Table\ \@ref(tab:corrtable), and descriptive statistics appear in Table\ \@ref(tab:descriptives).
+
+###Cognitive Performance
+Trigrams from the Remote Associates Task [@mcfarlin1984remote] were utilized to assess cognitive performance after the interaction.
+Ten items were selected and presented to participants.
+For example, the correct answer for the trigram “Quack: Pond: Waddle” would be “Duck”.
+Participants are limited to 30 seconds.
+For every correct answer, 1 point is given.
+The mean score was `r mean_trigram` (SD = `r sd_trigram`).
+Cognitive performance was measured first in order to measure potential immediate detriments to performance [@garcia2016objectification].
+
+###State Other-Objectification
+To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner @garcia2016objectification.
+Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
+All questions were to be rated on a scale from 1 (not at all) to 7 (constantly).
+Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2).
+A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
+
+###Interaction Authenticity
+To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike [@garcia2016objectification].
+Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: ‘‘Do you think your partner was authentic during your interaction?’’ and ‘‘Were you authentic during your interaction?’’ These questions were ranked on a scale from 1 (not authentic at all).
+These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
+
+###State Self-Objectification
+To assess state self-objectification, we used an average of two items from @saguyetal2010 that were also used in @garcia2016objectification.
+Participants were asked to rank how much they agreed with the following statements: “During the interaction I felt more like a body than a full self” and “I felt more like a body than as a real person in the interaction”.
+Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
+
+###Relationship Agency
+A scale was used from @garcia2016objectification to assess how much agency an individual believes they would possess in future romantic relationships.
+Participants were asked how likely it was that they would do the following: ‘‘ask someone out on a date,’’ ‘‘open the door for your date,’’ ‘‘pay for a date,’’ ‘‘ask your boyfriend/girlfriend to marry you,’’ ‘‘initiate sex with your girlfriend/boyfriend,’’ ‘‘initiate condom use during sex,’’ ‘‘surprise your boyfriend/ girlfriend with a gift,’’ and ‘‘ask your girlfriend/boyfriend to move with you to a new place.’’ Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
+The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
+The item was intended to be reverse coded, but correlations were still low enough to make the scale unreliable.
+Therefore, the ninth item was removed.
+As a result, the scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
+
+###Career Aspirations
+To conceptualize participants’ career aspirations after the interaction, we used the 10-item adaptation of @grayobrien2007’s Career Aspiration Scale employed in @garcia2016objectification, which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
+Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
+
+###Trait Self-Objectification
+Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
+The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
+Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness).
+Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.
+
+###Description of the Samples
+Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
+More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college.
+Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
+Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
+Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
+Due to similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
+For consistency, we limited participant data to same sex female pairs at the two colleges.
+These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
+The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
+There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
+The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
+`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
+
+## Data analysis
+
+```{r create_r-references, warning=FALSE, message=FALSE}
+#cite_r(file = "references.bib")
+r_refs(file = "r-references.bib")
+```
+
+We used `r cite_r("r-references.bib")` for all our analyses.
+
+```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
+include_graphics("APIM_figure.png")
+```
+
+```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
+include_graphics("2016_figure.jpg")
+```
+
+# Results
+
+## Analysis Strategy
+
+This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used dyadic analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
+See Figure\ \@ref(fig:2016figure) for the path analysis results of the previous study.
+We hope to investigate how the main effects found in the previous study relay to interactions between women: specifically, the relationship between state-other objectification and self-state objectification and the resulting effect of self-state objectification on inauthenticity during the interaction.
+
+We used path analysis to obtain our estimates, but because our sample is nonindependent, we used the indistinguishable actor–partner interdependence model [@olsen2006structural].
+The APIM can be defined as a "model of dyadic relationships that integrates a conceptual view of interdependence with the appropriate statistical techniques for measuring and testing it" [@olsen2006structural].
+See Figure\ \@ref(fig:apim) for a basic APIM model.
+Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
+Due to constraints of the basic APIM, in that this was an exploration of indistinguishable female dyads, we had to fix all path estimates to be the same across/between people and partners, in addition to all variances, covariances, endogenous intercepts, and exogenous means.
+Due to the complexity of the original @garcia2016objectification study, we also had to set the exogenous covariances equal.
+More specifically, the covariances between TSO, actor and partner objectification, and the interaction between actor TSO and partner objectification (and vice versa).
+
+In order to interpret model fit, which refers to the ability of a model to reproduce the data (i.e., usually the varience-covariance matrix) we utilized both the I-SAT (saturated) model, and the Null model to ensure that all possible corresponding covariences are fixed to be equal across partners.
+We obtained fit estimates by subtracting the chi-square estimate for the I-SAT model from the analysis model [@olsen2006structural, @peugh2013analyzing].
+
+```{r}
 #Filtering for just one partnum and creating TSO * objectification interaction
@@
 
-```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
-include_graphics("APIM_figure.png")
-```
-
-```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
-include_graphics("2016_figure.jpg")
-```
-
 ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
@@
 
+##Main Results
+All model estimates and p-values are found in Table\ \@ref(tab:sem) and the relationships are depicted in Figure\ \@ref(fig:semfigure).
+The most important findings from @garcia2016objectification were the significant partner effect between actor SSO and partner objectification (specifically men's objectification of women and women's SSO), and the link between actor SSO and actor authenticity (also specifically for women).
+We did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which means we do not have evidence to support the idea that partner objectification is the cause for the negative effects related to relationship inauthenticity.
+However, we did find a significant relationship between partner objectification and actor SSO ($\beta$= .25, $p$=.03), which supports our hypothesis that objectification from other women also causes women to self-objectify just as it does in interactions between male-female pairs.
+We also found a significantly negative effect of authenticity on career aspirations ($\beta$= .18, $p$=.01) and relationship agency ($\beta$=.27, $p$=.01).
+We found that the model had good fit ($\chi^2$=22.33, $df$=34).
+In this case, a good fit indicates that there are no direct effects of SSO or SOO on the outcomes on cognitive performance, relationship agency, and career aspirations, which indicates that the path we chose makes sense.
+
+# Discussion
+As stated previously, we did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to relationship inauthenticity.
+However, we did observe a significant partner effect of objectification on actor self-objectification, which does align with our hypothesis that theorized objectification from other women can also cause women to self-objectify just as they do within interactions between male-female pairs.
+The results of this study demonstrate the complex and ambivalent nature of female sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
+The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008].
+Because “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015].
+Further, sexualzing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014; @bury2016].
+Considering the fact that the average mean age of the investigated participants of this current study was 18.85 years, research among younger and older individuals is needed, especially because self-objectification may change over time [@robertsfredrickson].
+It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexulizing content.
+Also, future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operalization of self-objectification may be improved.
+Regardless, the results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts.
+These results are quite useful for promoting mental health and within early action programs for girls and young women, where scholars and practitioners might provide the tools necessary to circumvent or mitigate negative effects on self-objectification, and combat such experiences.
+
 \newpage
-
-# References
-```{r create_r-references, warning=FALSE, message=FALSE}
-cite_r(file = "references.bib")
-r_refs(file = "r-references.bib")
-```
 

### 2020-06-24 Final_Manuscript.Rmd
Edits to intro

@@
 
-Theorists across diverse disciplines have explored the multiple ways that the body conveys social meaning, as well as how these meanings shape gendered experiences and therefore inform individuals’ thinking, feeling, and behavior, especially during interpersonal interactions with members of different social groups [@Kaschak].
-Empirical evidence illustrates how women, in particular,  continue to be objects of perpetual discrimination as a result of psychosocial markers, like gender, that produce modes through which their identity is understood [@swimetal].
+Theorists across diverse disciplines have explored the multiple ways that the body conveys social meaning, as well as how these meanings shape gendered experiences, especially during interpersonal interactions with members of different social groups [@Kaschak, @garcia2016objectification].
 Objectification theory, a valuable theoretical framework proposed by @robertsfredrickson which works to contextualize female bodies as socio-cultural constructions, can be employed to illuminate the gender oppression and negative lived experiences of girls and women.
-
-Additionally, one of the most detrimental forms of discrimination against them is thought to be the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
+Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and expereince daily sexist hassles [@swimetal].
+One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
 Sexual objectification occurs with both “endless variety and monotonous similarity,” and is thus mediated by unique combinations of race, ethnicity, sexuality, age, and class [@fredricksonetal2011; @rubin1975, cited in @frasernicholson1989, p.
@@
 Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
-Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
-Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
+
 Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008].
 @calogero2011 proposes that the construct of self-objectification can be conceptualized as a learned trait.
+Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@calogero2011, @moradi2008].
+Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [CITE swimsuit sweater, @garcia2016objectification].
 
-Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@calogero2011, @moradi2008].
-Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO).
+Studies have shown that within social encounters women are gazed at more than men [@briton1995, CITE saguy skype study, calogero video walking study], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
+Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
 
-In the current work, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification,  but between same-sex female interpersonal interactions.
-We predicted that being objectified by one’s interaction partner would lead to self-objectification, in addition to modified feelings of authenticity in postinteraciton outcomes, including feelings of agency in romantic relationships, career aspiration, and cognitive performance [@quinnetal].
-Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@swimetal].
+ENTIRE PARAGRAPH ON MODERN (POST-2016) STUDIES OF INTERPERSONAL OBJECTIFICATION.
 
-Moreover, it was the goal of this research to empirically explore the role of interaction authenticity in objectification by utilizing a structural equation modeling to examine the effects for both women simultaneously.
-We expected to replicate the results found in the previous @garcia2016objectification study.
-More specifically, we expected to find a positive relationship between state-other objectification and self-state objectification, and a resulting negative relationship between self-state objectification and interaction authenticity.
-Finally, we expected there to be a positive relationship between interaction authenticity and cognitive performance, relationship agency, and career aspirations.
+Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@quinnetal].
+
+In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification,  but between same-sex female interpersonal interactions.
+Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously.
+We expected to replicate the results found in @garcia2016objectification.
+We predicted that being objectified by one’s interaction partner would lead to self-objectification, which in turn would lead to feelings of inauthenticity, then reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
+Specifically, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
+We also expect to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
 

### 2020-06-24 Final_Manuscript.Rmd
more organization

@@
 ##Combining Samples
-Data from two different samples were used for this study and are discussed below.
-In the measures section that follows we refer to them as Sample 1 and Sample 2.
-Sample 1 is from a co-ed liberal arts college in the northeast and Sample 2 is from a women’s liberal arts college in the northeast.
 
-```{r alphas}
-#######Alphas
-
-##SOO
-#Clark
-clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, 
-                                          otherint_5, otherint_6, otherint_10))$total[2]
-clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, 
-                                          otherint_7, otherint_8, otherint_9, otherint_11, 
-                                          otherint_12))$total[2]
-#Smith
-smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, 
-                                          otherint_6, otherint_10))$total[2]
-smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, 
-                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
-
-##Interaction Authenticity
-#Clark
-clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, 
-                                           inter_6, inter_7, inter_9, inter_10, interaux_5, 
-                                           interaux_6))$total[2]
-#Smith
-smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, 
-                                           inter_7, inter_9, inter_10, interaux_5, 
-                                           interaux_6))$total[2]
-
-##SSO
-#Clark - two items
-clark_howbody_alpha<- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
-#Smith - two items
-smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]
-#Clark - three items
-clark_howbody3 <- psych::alpha(select(clark_measures, howbody_1, howbody_2, howbody_3))
-#Smith - three items
-smith_howbody3 <- psych::alpha(select(smith, howbody_1, howbody_2, howbody_3))
-
-##Relationship Agency
-#Clark
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
-                                         relag_4, relag_5, relag_6, relag_7, relag_8, 
-                                         relag_9.r))$total[2]
-#Smith
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
-                                         relag_5, relag_6, relag_7, relag_8, 
-                                         relag_9.r))$total[2]
-
-#corr.test(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
-#corr.test(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
-##DROPPING ITEM 9
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
-                                         relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
-
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
-                                         relag_5, relag_6, relag_7, relag_8))$total[2]
-
-##Career Aspirations
-#Clark
-clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
-  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
-         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
-         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
-
-clark_careerasp_alpha <- psych::alpha(select(clark_measures, careerasp_1, careerasp_2, 
-                                             careerasp_3, careerasp4.r, careerasp_5, 
-                                             careerasp_6, careerasp7.r, careerasp_8, 
-                                             careerasp_9, careerasp10.r))$total[2]
-
-#Smith
-smith <- smith %>% #reverse code certain career aspiration variables
-  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
-         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
-         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
-
-smith_careerasp_alpha <- psych::alpha(select(smith, careerasp_1, careerasp_2, 
-                                             careerasp_3, careerasp4.r, careerasp_5, 
-                                             careerasp_6, careerasp7.r, careerasp_8, 
-                                             careerasp_9, careerasp10.r))$total[2]
-
-###TSO
-#Clark--external and internal
-clark_funcTSO_alpha <- psych::alpha(select(clark_measures, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
-clark_physTSO_alpha <- psych::alpha(select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
-
-#Smith--external and internal
-smith_funcTSO_alpha <- psych::alpha(select(smith, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
-smith_physTSO_alpha <- psych::alpha(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
-
+```{r}
+ns <- clarksmith_women %>%
+  group_by(smith_or_clark) %>%
+  summarise(n = n()) %>%
+  as.matrix() %>% as.numeric()
 ```
 
-```{r demographics}
-#favstats(~TSO_A, data=clarksmith_women)
-#favstats(~a2pSOO_A, data=clarksmith_women)
-#favstats(~howbody_avg_A, data=clarksmith_women)
-#favstats(~relag_A, data=clarksmith_women)
-#favstats(~careerasp_A, data=clarksmith_women)
-#favstats(~authenticity_A, data=clarksmith_women)
-#favstats(~trigram_score_A, data=clarksmith_women)
-
-#Mean and SD of age of sample
-mean_age <- favstats(~age_A, data = clarksmith_women)$mean
-sd_age <- favstats(~age_A, data = clarksmith_women)$sd
-tally(clarksmith_women$race_A == clarksmith_women$race_P)
-
-#Calculating race percentages
-tally(~race_A, data = clarksmith_women)  #Note that we can add "format = percentage" and not need to calculate
-percentage_black <- 6/(6+18+31+6+3)*100
-percent_asian <- 18/(6+18+31+6+3)*100
-percent_white <- 31/(6+18+31+6+3)*100
-percent_latinx <- 6/(6+18+31+6+3)*100
-percent_other <- 3/(6+18+31+6+3)*100
-tally(~sexor_A, data=clarksmith_women)
-percent_straight <-(41/64)*100
-percent_queer <- (3+8+5)/64*100
-tally(~gender_A, data=clarksmith_women)
-
-table(clarksmith_women$race_A, clarksmith_women$race_P)
-samerace_white <- 16/2 #divide by 2 since table is people, not pairs
-samerace_minority <- (6+2)/2
-mixedrace_white <- 2+10+2+1
-mixedrace_minority <- 1+2+1+1
-
-test <- clarksmith_women %>%
-  filter(race_A==3, race_A!=race_P)
-
-tally(~gender, data=clark_measures)
-tally(~gender, data=smith)
-```
+Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study.
+In the measures section that follows we refer to them as Sample 1 and Sample 2.
+Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US.
 
 ```{r correaltions}
-clarksmith_correlations <- clarksmith_women %>%
-  select(TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, 
-         relag_A, careerasp_A,  trigram_score_A, TSO_P, 
-         authenticity_P, a2pSOO_P, howbody_avg_P, 
-         relag_P, careerasp_P, trigram_score_P)
+#NOT SURE WHAT THIS CHUNK WAS FOR BUT ITS NOT NEEDED
 
-#Correlation tables
-correlations <- apa.cor.table(clarksmith_correlations, table.number=1)
-```
-
-```{r trigram}
-#Cognitive performance - Full sample
-mean_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$mean
-sd_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$sd
+# clarksmith_correlations <- clarksmith_women %>%
+#   select(TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, 
+#          relag_A, careerasp_A,  trigram_score_A, TSO_P, 
+#          authenticity_P, a2pSOO_P, howbody_avg_P, 
+#          relag_P, careerasp_P, trigram_score_P)
+# 
+# #Correlation tables
+# correlations <- apa.cor.table(clarksmith_correlations, table.number=1)
 ```
@@
 
+```{r trigram}
+#Cognitive performance - Full sample
+mean_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$mean
+sd_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$sd
+```
+
 ###Cognitive Performance
@@
 
+```{r alpha_SOO}
+##SOO
+#Clark
+clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, 
+                                          otherint_5, otherint_6, otherint_10))$total[2]
+clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, 
+                                          otherint_7, otherint_8, otherint_9, otherint_11, 
+                                          otherint_12))$total[2]
+#Smith
+smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, 
+                                          otherint_6, otherint_10))$total[2]
+smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, 
+                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
+```
+
 ###State Other-Objectification
@@
 
+```{r alpha_intauth}
+##Interaction Authenticity
+#Clark
+clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, 
+                                           inter_6, inter_7, inter_9, inter_10, interaux_5, 
+                                           interaux_6))$total[2]
+#Smith
+smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, 
+                                           inter_7, inter_9, inter_10, interaux_5, 
+                                           interaux_6))$total[2]
+```
+
 ###Interaction Authenticity
@@
 
+```{r alpha_SSO}
+##SSO
+#Clark - two items
+clark_howbody_alpha<- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
+#Smith - two items
+smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]
+#Clark - three items
+clark_howbody3 <- psych::alpha(select(clark_measures, howbody_1, howbody_2, howbody_3))
+#Smith - three items
+smith_howbody3 <- psych::alpha(select(smith, howbody_1, howbody_2, howbody_3))
+```
+
 ###State Self-Objectification
@@
 Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
+
+```{r alpha_relagen}
+##Relationship Agency
+#Clark
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
+                                         relag_4, relag_5, relag_6, relag_7, relag_8, 
+                                         relag_9.r))$total[2]
+#Smith
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
+                                         relag_5, relag_6, relag_7, relag_8, 
+                                         relag_9.r))$total[2]
+
+#corr.test(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+#corr.test(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+##DROPPING ITEM 9
+clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
+                                         relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
+
+smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
+                                         relag_5, relag_6, relag_7, relag_8))$total[2]
+```
 
@@
 
+```{r alpha_career}
+##Career Aspirations
+#Clark
+clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
+  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
+         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
+         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
+
+clark_careerasp_alpha <- psych::alpha(select(clark_measures, careerasp_1, careerasp_2, 
+                                             careerasp_3, careerasp4.r, careerasp_5, 
+                                             careerasp_6, careerasp7.r, careerasp_8, 
+                                             careerasp_9, careerasp10.r))$total[2]
+
+#Smith
+smith <- smith %>% #reverse code certain career aspiration variables
+  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
+         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
+         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))
+
+smith_careerasp_alpha <- psych::alpha(select(smith, careerasp_1, careerasp_2, 
+                                             careerasp_3, careerasp4.r, careerasp_5, 
+                                             careerasp_6, careerasp7.r, careerasp_8, 
+                                             careerasp_9, careerasp10.r))$total[2]
+```
+
 ###Career Aspirations
@@
 Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
+
+```{r alpha_TSO}
+###TSO
+#Clark--external and internal
+clark_funcTSO_alpha <- psych::alpha(select(clark_measures, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
+clark_physTSO_alpha <- psych::alpha(select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
+
+#Smith--external and internal
+smith_funcTSO_alpha <- psych::alpha(select(smith, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
+smith_physTSO_alpha <- psych::alpha(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
+
+```
 
@@
 Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.
+
+```{r demographics}
+#favstats(~TSO_A, data=clarksmith_women)
+#favstats(~a2pSOO_A, data=clarksmith_women)
+#favstats(~howbody_avg_A, data=clarksmith_women)
+#favstats(~relag_A, data=clarksmith_women)
+#favstats(~careerasp_A, data=clarksmith_women)
+#favstats(~authenticity_A, data=clarksmith_women)
+#favstats(~trigram_score_A, data=clarksmith_women)
+
+#Mean and SD of age of sample
+mean_age <- favstats(~age_A, data = clarksmith_women)$mean
+sd_age <- favstats(~age_A, data = clarksmith_women)$sd
+tally(clarksmith_women$race_A == clarksmith_women$race_P)
+
+#Calculating race percentages
+tally(~race_A, data = clarksmith_women)  #Note that we can add "format = percentage" and not need to calculate
+percentage_black <- 6/(6+18+31+6+3)*100
+percent_asian <- 18/(6+18+31+6+3)*100
+percent_white <- 31/(6+18+31+6+3)*100
+percent_latinx <- 6/(6+18+31+6+3)*100
+percent_other <- 3/(6+18+31+6+3)*100
+tally(~sexor_A, data=clarksmith_women)
+percent_straight <-(41/64)*100
+percent_queer <- (3+8+5)/64*100
+tally(~gender_A, data=clarksmith_women)
+
+table(clarksmith_women$race_A, clarksmith_women$race_P)
+samerace_white <- 16/2 #divide by 2 since table is people, not pairs
+samerace_minority <- (6+2)/2
+mixedrace_white <- 2+10+2+1
+mixedrace_minority <- 1+2+1+1
+
+test <- clarksmith_women %>%
+  filter(race_A==3, race_A!=race_P)
+
+tally(~gender, data=clark_measures)
+tally(~gender, data=smith)
+```
 
@@
 
-## Data analysis
-
+# Results
 ```{r create_r-references, warning=FALSE, message=FALSE}
@@
 
+## Data analysis
 We used `r cite_r("r-references.bib")` for all our analyses.
@@
 
-# Results
-
 ## Analysis Strategy
-
 This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used dyadic analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
@@
 
-# Discussion
+#Discussion
 As stated previously, we did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to relationship inauthenticity.
@@
 
+#References
+
 \newpage

### 2020-06-26 Final_Manuscript.Rmd
started MLM analyses

@@
 
-```{r packages}
+```{r packages, warning = FALSE, message = FALSE}
 library(papaja)
@@
  Rnew <- cbind(round(describe(x)[,3:4],2), Rnew)		 #describe x, M sD - put them in the matrix
- colnames(Rnew)[1:2] <- c("M","SD")					      		#Beschriftung der neuen Spalten
+ colnames(Rnew)[1:2] <- c("M","SD")			#Beschriftung der neuen Spalten-"labeling of the new columns"
  Rnew <- Rnew[,1:(ncol(Rnew)-1)]							   	#delete the last column (ugly)
@@
 smith_physTSO_alpha <- psych::alpha(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
-
 ```
@@
 ## Analysis Strategy
-This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used dyadic analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
-See Figure\ \@ref(fig:2016figure) for the path analysis results of the previous study.
-We hope to investigate how the main effects found in the previous study relay to interactions between women: specifically, the relationship between state-other objectification and self-state objectification and the resulting effect of self-state objectification on inauthenticity during the interaction.
+This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
+See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study.
+We hope to investigate how the central effects found in the previous study relate to interactions between two women.
+Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affecs feelings of inauthenticity during the interaction.
+In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification.
+Further, we will investigate the realtionships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.
 
-We used path analysis to obtain our estimates, but because our sample is nonindependent, we used the indistinguishable actor–partner interdependence model [@olsen2006structural].
+While @garcia2016objectification used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling.
+Dyadic analyses for distingishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structual Equation Modeling (SEM) than it is for indistinguishable dayds (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation].
+One reason for this asymmetry is that, due to the arbitrary distinctions made bewteen "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality contraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural].
+Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models.
+The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation paterns.
+See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.
+
+Testing the @garcia2016objectification model on the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approch for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:2016figure)).
+Thus, we ran five APIM's to test all the hypothesized relationships.
+See Figure\ \@ref(fig:apim) for a basic APIM model.
+The APIM includes effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$).
+Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
+Recall that the indistinguiahble nature of the dyads in the current study led us to choose the MLM approach over SEM.
+These analyses are considered exploratory, given the lack of prior research theorizing about these linkages.
+
+<!-- The model differences as a result of adopting this MLM approach include an examination of the partner effect of TSO on SSO, partner effect of SSO on authenticity, and partner effects of authenticity on congitive performance, relationship agency, and career aspirations.
+-->
+
+<!-- We used path analysis to obtain our estimates, but because our sample is nonindependent, we used the indistinguishable actor–partner interdependence model [@olsen2006structural].
 The APIM can be defined as a "model of dyadic relationships that integrates a conceptual view of interdependence with the appropriate statistical techniques for measuring and testing it" [@olsen2006structural].
-See Figure\ \@ref(fig:apim) for a basic APIM model.
-Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
-Due to constraints of the basic APIM, in that this was an exploration of indistinguishable female dyads, we had to fix all path estimates to be the same across/between people and partners, in addition to all variances, covariances, endogenous intercepts, and exogenous means.
 Due to the complexity of the original @garcia2016objectification study, we also had to set the exogenous covariances equal.
 More specifically, the covariances between TSO, actor and partner objectification, and the interaction between actor TSO and partner objectification (and vice versa).
+-->
 
-In order to interpret model fit, which refers to the ability of a model to reproduce the data (i.e., usually the varience-covariance matrix) we utilized both the I-SAT (saturated) model, and the Null model to ensure that all possible corresponding covariences are fixed to be equal across partners.
+<!-- In order to interpret model fit, which refers to the ability of a model to reproduce the data (i.e., usually the varience-covariance matrix) we utilized both the I-SAT (saturated) model, and the Null model to ensure that all possible corresponding covariences are fixed to be equal across partners.
 We obtained fit estimates by subtracting the chi-square estimate for the I-SAT model from the analysis model [@olsen2006structural, @peugh2013analyzing].
+-->
 
 ```{r}
-#Filtering for just one partnum and creating TSO * objectification interaction
-dyad_cswomen <- clarksmith_women %>%
-  mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
-         TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
-  filter(partnum_A==1)
-
-model <- '#####regressions 
-howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P + c*TSO_A_SOO_P
-authenticity_A ~ d*howbody_avg_A
-howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A + c*TSO_P_SOO_A
-authenticity_P ~ d*howbody_avg_P
-trigram_score_A ~ e1*authenticity_A
-careerasp_A ~ e2*authenticity_A
-relag_A ~ e3*authenticity_A
-trigram_score_P ~ e1*authenticity_P
-careerasp_P ~ e2*authenticity_P
-relag_P ~ e3*authenticity_P
-######covariances
-#endogenous
-howbody_avg_A ~~ howbody_avg_P
-authenticity_A ~~ authenticity_P
-trigram_score_A ~~ trigram_score_P
-careerasp_A ~~ careerasp_P
-relag_A ~~ relag_P
-trigram_score_A ~~ 0*careerasp_A
-trigram_score_A ~~ 0*relag_A
-trigram_score_A ~~ 0*careerasp_P
-trigram_score_A ~~ 0*relag_P
-careerasp_A ~~ 0*relag_A
-careerasp_A ~~ 0*trigram_score_P
-careerasp_A ~~ 0*relag_P
-relag_A ~~ 0*trigram_score_P
-relag_A ~~ 0*careerasp_P
-trigram_score_P ~~ 0*careerasp_P
-trigram_score_P ~~ 0*relag_P
-careerasp_P ~~ 0*relag_P
-#####variances
-howbody_avg_A ~~ v1*howbody_avg_A
-howbody_avg_P ~~ v1*howbody_avg_P
-TSO_A ~~ v2*TSO_A
-TSO_P ~~ v2*TSO_P
-a2pSOO_A ~~ v3*a2pSOO_A
-a2pSOO_P ~~ v3*a2pSOO_P
-authenticity_A ~~ v4*authenticity_A
-authenticity_P ~~ v4*authenticity_P
-##endogenous intercepts
-howbody_avg_A ~ i*1
-howbody_avg_P ~ i*1
-authenticity_A ~ i2*1
-authenticity_P ~ i2*1
-trigram_score_A ~ i3*1
-trigram_score_P ~ i4*1
-careerasp_A ~ i5*1
-careerasp_P ~ i5*1
-relag_A ~ i6*1
-relag_P ~ i6*1
-##exogenous means
-TSO_A ~ m*1
-TSO_P ~ m*1
-a2pSOO_A ~ m2*1
-a2pSOO_P ~ m2*1
-TSO_P_SOO_A ~ m3*1
-TSO_A_SOO_P ~ m3*1
-## exogenous covariances
-TSO_A_SOO_P ~~ c1*TSO_A
-TSO_P_SOO_A ~~ c1*TSO_P
-TSO_A_SOO_P ~~ c2*a2pSOO_P
-TSO_P_SOO_A ~~ c2*a2pSOO_A
-TSO_A ~~ c3*a2pSOO_P
-TSO_P ~~ c3*a2pSOO_A
-TSO_A ~~ c4*a2pSOO_A
-TSO_P ~~ c4*a2pSOO_P
-TSO_A_SOO_P ~~ c5*a2pSOO_A
-TSO_P_SOO_A ~~ c5*a2pSOO_P
-TSO_A_SOO_P ~~ c6*TSO_P
-TSO_P_SOO_A ~~ c6*TSO_A
-'
-
-isatmodel <- '#####regressions 
-#Part one/two
-howbody_avg_A ~~ t*TSO_A
-howbody_avg_A ~~ a*a2pSOO_A
-howbody_avg_A ~~ b*a2pSOO_P 
-howbody_avg_A ~~ c*TSO_A_SOO_P
-
-howbody_avg_P ~~ t*TSO_P
-howbody_avg_P ~~ a*a2pSOO_P 
-howbody_avg_P ~~ b*a2pSOO_A 
-howbody_avg_P ~~ c*TSO_P_SOO_A
-
-TSO_A ~~ f*howbody_avg_P
-TSO_P ~~ f*howbody_avg_A
-TSO_A_SOO_P ~~ g*howbody_avg_P
-TSO_P_SOO_A ~~ g*howbody_avg_A
-
-#Part two/three
-authenticity_A ~~ d*howbody_avg_A
-authenticity_P ~~ d*howbody_avg_P
-howbody_avg_A ~~ h*authenticity_P
-howbody_avg_P ~~ h*authenticity_A
-
-#Part three/four
-trigram_score_A ~~ e1*authenticity_A
-trigram_score_P ~~ e1*authenticity_P
-careerasp_A ~~ e2*authenticity_A
-careerasp_P ~~ e2*authenticity_P
-relag_A ~~ e3*authenticity_A
-relag_P ~~ e3*authenticity_P
-trigram_score_A ~~ e4*relag_P
-trigram_score_P ~~ e4*relag_A
-trigram_score_A ~~ e5*careerasp_P
-trigram_score_P ~~ e5*careerasp_A
-trigram_score_A ~~ e6*trigram_score_P
-#trigram_score_P ~~ e6*trigram_score_A
-careerasp_A ~~ e7*relag_P
-careerasp_P ~~ e7*relag_A
-careerasp_A ~~ e8*careerasp_P
-#careerasp_A ~~ e9*trigram_score_P
-#careerasp_P ~~ e9*trigram_score_A
-relag_A ~~ e10*relag_P
-
-#One to three
-#direct actor effects
-authenticity_A ~~ k1*TSO_A_SOO_P
-authenticity_P ~~ k1*TSO_P_SOO_A
-authenticity_A ~~ k2*TSO_A
-authenticity_P ~~ k2*TSO_P
-authenticity_A ~~k3*a2pSOO_A
-authenticity_P ~~k3*a2pSOO_P
-
-#direct partner effects
-authenticity_A ~~ k4*TSO_P_SOO_A
-authenticity_P ~~k4*TSO_A_SOO_P
-authenticity_A ~~ k5*TSO_P
-authenticity_P ~~ k5*TSO_A
-authenticity_A ~~ k6*a2pSOO_P
-authenticity_P ~~ k6*a2pSOO_A
-
-#One to four
-#Direct actor effects
-trigram_score_A ~~ l1*TSO_A_SOO_P
-trigram_score_P ~~ l1*TSO_P_SOO_A
-trigram_score_A ~~ l2*TSO_A
-trigram_score_P ~~ l2*TSO_P
-trigram_score_A ~~ l3*a2pSOO_A
-trigram_score_P ~~ l3*a2pSOO_P
-careerasp_A ~~ l4*TSO_A_SOO_P
-careerasp_P ~~ l4*TSO_P_SOO_A
-careerasp_A ~~ l5*TSO_A
-careerasp_P ~~ l5*TSO_P
-careerasp_A ~~ l6*a2pSOO_A
-careerasp_P ~~ l6*a2pSOO_P
-relag_A ~~ l7*TSO_A_SOO_P
-relag_P ~~ l7*TSO_P_SOO_A
-relag_A ~~ l8*TSO_A
-relag_P ~~ l8*TSO_P
-relag_A ~~ l9*a2pSOO_A
-relag_P ~~ l9*a2pSOO_P
-
-#direct partner effects
-trigram_score_A ~~ m1*TSO_P_SOO_A
-trigram_score_P ~~ m1*TSO_A_SOO_P
-trigram_score_A ~~ m2*TSO_P
-trigram_score_P ~~ m2*TSO_A
-trigram_score_A ~~ m3*a2pSOO_P
-trigram_score_P ~~ m3*a2pSOO_A
-careerasp_A ~~ m4*TSO_P_SOO_A
-careerasp_P ~~ m4*TSO_A_SOO_P
-careerasp_A ~~ m5*TSO_P
-careerasp_P ~~ m5*TSO_A
-careerasp_A ~~ m6*a2pSOO_P
-careerasp_P ~~ m6*a2pSOO_A
-relag_A ~~ m7*TSO_P_SOO_A
-relag_P ~~ m7*TSO_A_SOO_P
-relag_A ~~ m8*TSO_P
-relag_P ~~ m8*TSO_A
-relag_A ~~ m9*a2pSOO_P
-relag_P ~~ m9*a2pSOO_A
-
-#Two to four
-#direct actor effects
-trigram_score_A ~~ o1*howbody_avg_A
-trigram_score_P ~~ o1*howbody_avg_P
-careerasp_A ~~ o2*howbody_avg_A
-careerasp_P ~~ o2*howbody_avg_P
-relag_A ~~ o3*howbody_avg_A
-relag_P ~~ o3*howbody_avg_P
-
-#direct partner effects
-trigram_score_A ~~ o1*howbody_avg_P
-trigram_score_P ~~ o1*howbody_avg_A
-careerasp_A ~~ o2*howbody_avg_P
-careerasp_P ~~ o2*howbody_avg_A
-relag_A ~~ o3*howbody_avg_P
-relag_P ~~ o3*howbody_avg_A
-
-######covariances
-#endogenous
-howbody_avg_A ~~ howbody_avg_P
-authenticity_A ~~ authenticity_P
-#trigram_score_A ~~ trigram_score_P
-#careerasp_A ~~ careerasp_P
-#relag_A ~~ relag_P
-trigram_score_A ~~ q1*careerasp_A 
-trigram_score_A ~~ q2*relag_A
-
-careerasp_A ~~ q3*relag_A
-
-trigram_score_P ~~ q1*careerasp_P
-trigram_score_P ~~ q2*relag_P
-
-careerasp_P ~~ q3*relag_P
-
-trigram_score_A ~~ q4*careerasp_P
-trigram_score_A ~~ q5*relag_P
-
-trigram_score_P ~~ q4*careerasp_A
-trigram_score_P ~~ q5*relag_A
-
-careerasp_A ~~ q6*relag_P
-careerasp_P ~~ q6*relag_A
-
-#####variances
-howbody_avg_A ~~ v1*howbody_avg_A
-howbody_avg_P ~~ v1*howbody_avg_P
-TSO_A ~~ v2*TSO_A
-TSO_P ~~ v2*TSO_P
-a2pSOO_A ~~ v3*a2pSOO_A
-a2pSOO_P ~~ v3*a2pSOO_P
-authenticity_A ~~ v4*authenticity_A
-authenticity_P ~~ v4*authenticity_P
-##endogenous intercepts
-howbody_avg_A ~ i*1
-howbody_avg_P ~ i*1
-authenticity_A ~ i2*1
-authenticity_P ~ i2*1
-trigram_score_A ~ i3*1
-trigram_score_P ~ i4*1
-careerasp_A ~ i5*1
-careerasp_P ~ i5*1
-relag_A ~ i6*1
-relag_P ~ i6*1
-##exogenous means
-TSO_A ~ m*1
-TSO_P ~ m*1
-a2pSOO_A ~ m2*1
-a2pSOO_P ~ m2*1
-TSO_P_SOO_A ~ m3*1
-TSO_A_SOO_P ~ m3*1
-## exogenous covariances
-TSO_A_SOO_P ~~ c1*TSO_A
-TSO_P_SOO_A ~~ c1*TSO_P
-TSO_A_SOO_P ~~ c2*a2pSOO_P
-TSO_P_SOO_A ~~ c2*a2pSOO_A
-TSO_A ~~ c3*a2pSOO_P
-TSO_P ~~ c3*a2pSOO_A
-TSO_A ~~ c4*a2pSOO_A
-TSO_P ~~ c4*a2pSOO_P
-TSO_A_SOO_P ~~ c5*a2pSOO_A
-TSO_P_SOO_A ~~ c5*a2pSOO_P
-TSO_A_SOO_P ~~ c6*TSO_P
-TSO_P_SOO_A ~~ c6*TSO_A
-'
-
-fit <- sem(model, data=dyad_cswomen)
+# #Filtering for just one partnum and creating TSO * objectification interaction
+# dyad_cswomen <- clarksmith_women %>%
+#   mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
+#          TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
+#   filter(partnum_A==1)
+# 
+# 
+# model <- '#####regressions 
+# howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P + c*TSO_A_SOO_P
+# authenticity_A ~ d*howbody_avg_A
+# howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A + c*TSO_P_SOO_A
+# authenticity_P ~ d*howbody_avg_P
+# trigram_score_A ~ e1*authenticity_A
+# careerasp_A ~ e2*authenticity_A
+# relag_A ~ e3*authenticity_A
+# trigram_score_P ~ e1*authenticity_P
+# careerasp_P ~ e2*authenticity_P
+# relag_P ~ e3*authenticity_P
+# ######covariances
+# #endogenous
+# howbody_avg_A ~~ howbody_avg_P
+# authenticity_A ~~ authenticity_P
+# trigram_score_A ~~ trigram_score_P
+# careerasp_A ~~ careerasp_P
+# relag_A ~~ relag_P
+# trigram_score_A ~~ 0*careerasp_A
+# trigram_score_A ~~ 0*relag_A
+# trigram_score_A ~~ 0*careerasp_P
+# trigram_score_A ~~ 0*relag_P
+# careerasp_A ~~ 0*relag_A
+# careerasp_A ~~ 0*trigram_score_P
+# careerasp_A ~~ 0*relag_P
+# relag_A ~~ 0*trigram_score_P
+# relag_A ~~ 0*careerasp_P
+# trigram_score_P ~~ 0*careerasp_P
+# trigram_score_P ~~ 0*relag_P
+# careerasp_P ~~ 0*relag_P
+# #####variances
+# howbody_avg_A ~~ v1*howbody_avg_A
+# howbody_avg_P ~~ v1*howbody_avg_P
+# TSO_A ~~ v2*TSO_A
+# TSO_P ~~ v2*TSO_P
+# a2pSOO_A ~~ v3*a2pSOO_A
+# a2pSOO_P ~~ v3*a2pSOO_P
+# authenticity_A ~~ v4*authenticity_A
+# authenticity_P ~~ v4*authenticity_P
+# ##endogenous intercepts
+# howbody_avg_A ~ i*1
+# howbody_avg_P ~ i*1
+# authenticity_A ~ i2*1
+# authenticity_P ~ i2*1
+# trigram_score_A ~ i3*1
+# trigram_score_P ~ i4*1
+# careerasp_A ~ i5*1
+# careerasp_P ~ i5*1
+# relag_A ~ i6*1
+# relag_P ~ i6*1
+# ##exogenous means
+# TSO_A ~ m*1
+# TSO_P ~ m*1
+# a2pSOO_A ~ m2*1
+# a2pSOO_P ~ m2*1
+# TSO_P_SOO_A ~ m3*1
+# TSO_A_SOO_P ~ m3*1
+# ## exogenous covariances
+# TSO_A_SOO_P ~~ c1*TSO_A
+# TSO_P_SOO_A ~~ c1*TSO_P
+# TSO_A_SOO_P ~~ c2*a2pSOO_P
+# TSO_P_SOO_A ~~ c2*a2pSOO_A
+# TSO_A ~~ c3*a2pSOO_P
+# TSO_P ~~ c3*a2pSOO_A
+# TSO_A ~~ c4*a2pSOO_A
+# TSO_P ~~ c4*a2pSOO_P
+# TSO_A_SOO_P ~~ c5*a2pSOO_A
+# TSO_P_SOO_A ~~ c5*a2pSOO_P
+# TSO_A_SOO_P ~~ c6*TSO_P
+# TSO_P_SOO_A ~~ c6*TSO_A
+# '
+# 
+# isatmodel <- '#####regressions 
+# #Part one/two
+# howbody_avg_A ~~ t*TSO_A
+# howbody_avg_A ~~ a*a2pSOO_A
+# howbody_avg_A ~~ b*a2pSOO_P 
+# howbody_avg_A ~~ c*TSO_A_SOO_P
+# 
+# howbody_avg_P ~~ t*TSO_P
+# howbody_avg_P ~~ a*a2pSOO_P 
+# howbody_avg_P ~~ b*a2pSOO_A 
+# howbody_avg_P ~~ c*TSO_P_SOO_A
+# 
+# TSO_A ~~ f*howbody_avg_P
+# TSO_P ~~ f*howbody_avg_A
+# TSO_A_SOO_P ~~ g*howbody_avg_P
+# TSO_P_SOO_A ~~ g*howbody_avg_A
+# 
+# #Part two/three
+# authenticity_A ~~ d*howbody_avg_A
+# authenticity_P ~~ d*howbody_avg_P
+# howbody_avg_A ~~ h*authenticity_P
+# howbody_avg_P ~~ h*authenticity_A
+# 
+# 
+# #Part three/four
+# trigram_score_A ~~ e1*authenticity_A
+# trigram_score_P ~~ e1*authenticity_P
+# careerasp_A ~~ e2*authenticity_A
+# careerasp_P ~~ e2*authenticity_P
+# relag_A ~~ e3*authenticity_A
+# relag_P ~~ e3*authenticity_P
+# trigram_score_A ~~ e4*relag_P
+# trigram_score_P ~~ e4*relag_A
+# trigram_score_A ~~ e5*careerasp_P
+# trigram_score_P ~~ e5*careerasp_A
+# trigram_score_A ~~ e6*trigram_score_P
+# #trigram_score_P ~~ e6*trigram_score_A
+# careerasp_A ~~ e7*relag_P
+# careerasp_P ~~ e7*relag_A
+# careerasp_A ~~ e8*careerasp_P
+# #careerasp_A ~~ e9*trigram_score_P
+# #careerasp_P ~~ e9*trigram_score_A
+# relag_A ~~ e10*relag_P
+# 
+# #One to three
+# #direct actor effects
+# authenticity_A ~~ k1*TSO_A_SOO_P
+# authenticity_P ~~ k1*TSO_P_SOO_A
+# authenticity_A ~~ k2*TSO_A
+# authenticity_P ~~ k2*TSO_P
+# authenticity_A ~~k3*a2pSOO_A
+# authenticity_P ~~k3*a2pSOO_P
+# 
+# #direct partner effects
+# authenticity_A ~~ k4*TSO_P_SOO_A
+# authenticity_P ~~k4*TSO_A_SOO_P
+# authenticity_A ~~ k5*TSO_P
+# authenticity_P ~~ k5*TSO_A
+# authenticity_A ~~ k6*a2pSOO_P
+# authenticity_P ~~ k6*a2pSOO_A
+# 
+# #One to four
+# #Direct actor effects
+# trigram_score_A ~~ l1*TSO_A_SOO_P
+# trigram_score_P ~~ l1*TSO_P_SOO_A
+# trigram_score_A ~~ l2*TSO_A
+# trigram_score_P ~~ l2*TSO_P
+# trigram_score_A ~~ l3*a2pSOO_A
+# trigram_score_P ~~ l3*a2pSOO_P
+# careerasp_A ~~ l4*TSO_A_SOO_P
+# careerasp_P ~~ l4*TSO_P_SOO_A
+# careerasp_A ~~ l5*TSO_A
+# careerasp_P ~~ l5*TSO_P
+# careerasp_A ~~ l6*a2pSOO_A
+# careerasp_P ~~ l6*a2pSOO_P
+# relag_A ~~ l7*TSO_A_SOO_P
+# relag_P ~~ l7*TSO_P_SOO_A
+# relag_A ~~ l8*TSO_A
+# relag_P ~~ l8*TSO_P
+# relag_A ~~ l9*a2pSOO_A
+# relag_P ~~ l9*a2pSOO_P
+# 
+# #direct partner effects
+# trigram_score_A ~~ m1*TSO_P_SOO_A
+# trigram_score_P ~~ m1*TSO_A_SOO_P
+# trigram_score_A ~~ m2*TSO_P
+# trigram_score_P ~~ m2*TSO_A
+# trigram_score_A ~~ m3*a2pSOO_P
+# trigram_score_P ~~ m3*a2pSOO_A
+# careerasp_A ~~ m4*TSO_P_SOO_A
+# careerasp_P ~~ m4*TSO_A_SOO_P
+# careerasp_A ~~ m5*TSO_P
+# careerasp_P ~~ m5*TSO_A
+# careerasp_A ~~ m6*a2pSOO_P
+# careerasp_P ~~ m6*a2pSOO_A
+# relag_A ~~ m7*TSO_P_SOO_A
+# relag_P ~~ m7*TSO_A_SOO_P
+# relag_A ~~ m8*TSO_P
+# relag_P ~~ m8*TSO_A
+# relag_A ~~ m9*a2pSOO_P
+# relag_P ~~ m9*a2pSOO_A
+# 
+# #Two to four
+# #direct actor effects
+# trigram_score_A ~~ o1*howbody_avg_A
+# trigram_score_P ~~ o1*howbody_avg_P
+# careerasp_A ~~ o2*howbody_avg_A
+# careerasp_P ~~ o2*howbody_avg_P
+# relag_A ~~ o3*howbody_avg_A
+# relag_P ~~ o3*howbody_avg_P
+# 
+# #direct partner effects
+# trigram_score_A ~~ o1*howbody_avg_P
+# trigram_score_P ~~ o1*howbody_avg_A
+# careerasp_A ~~ o2*howbody_avg_P
+# careerasp_P ~~ o2*howbody_avg_A
+# relag_A ~~ o3*howbody_avg_P
+# relag_P ~~ o3*howbody_avg_A
+# 
+# 
+# ######covariances
+# #endogenous
+# howbody_avg_A ~~ howbody_avg_P
+# authenticity_A ~~ authenticity_P
+# #trigram_score_A ~~ trigram_score_P
+# #careerasp_A ~~ careerasp_P
+# #relag_A ~~ relag_P
+# trigram_score_A ~~ q1*careerasp_A 
+# trigram_score_A ~~ q2*relag_A
+# 
+# careerasp_A ~~ q3*relag_A
+# 
+# trigram_score_P ~~ q1*careerasp_P
+# trigram_score_P ~~ q2*relag_P
+# 
+# careerasp_P ~~ q3*relag_P
+# 
+# trigram_score_A ~~ q4*careerasp_P
+# trigram_score_A ~~ q5*relag_P
+# 
+# 
+# trigram_score_P ~~ q4*careerasp_A
+# trigram_score_P ~~ q5*relag_A
+# 
+# careerasp_A ~~ q6*relag_P
+# careerasp_P ~~ q6*relag_A
+# 
+# 
+# #####variances
+# howbody_avg_A ~~ v1*howbody_avg_A
+# howbody_avg_P ~~ v1*howbody_avg_P
+# TSO_A ~~ v2*TSO_A
+# TSO_P ~~ v2*TSO_P
+# a2pSOO_A ~~ v3*a2pSOO_A
+# a2pSOO_P ~~ v3*a2pSOO_P
+# authenticity_A ~~ v4*authenticity_A
+# authenticity_P ~~ v4*authenticity_P
+# ##endogenous intercepts
+# howbody_avg_A ~ i*1
+# howbody_avg_P ~ i*1
+# authenticity_A ~ i2*1
+# authenticity_P ~ i2*1
+# trigram_score_A ~ i3*1
+# trigram_score_P ~ i4*1
+# careerasp_A ~ i5*1
+# careerasp_P ~ i5*1
+# relag_A ~ i6*1
+# relag_P ~ i6*1
+# ##exogenous means
+# TSO_A ~ m*1
+# TSO_P ~ m*1
+# a2pSOO_A ~ m2*1
+# a2pSOO_P ~ m2*1
+# TSO_P_SOO_A ~ m3*1
+# TSO_A_SOO_P ~ m3*1
+# ## exogenous covariances
+# TSO_A_SOO_P ~~ c1*TSO_A
+# TSO_P_SOO_A ~~ c1*TSO_P
+# TSO_A_SOO_P ~~ c2*a2pSOO_P
+# TSO_P_SOO_A ~~ c2*a2pSOO_A
+# TSO_A ~~ c3*a2pSOO_P
+# TSO_P ~~ c3*a2pSOO_A
+# TSO_A ~~ c4*a2pSOO_A
+# TSO_P ~~ c4*a2pSOO_P
+# TSO_A_SOO_P ~~ c5*a2pSOO_A
+# TSO_P_SOO_A ~~ c5*a2pSOO_P
+# TSO_A_SOO_P ~~ c6*TSO_P
+# TSO_P_SOO_A ~~ c6*TSO_A
+# '
+# 
+# 
+# 
+# fit <- sem(model, data=dyad_cswomen)
+# ```
+# 
+# ```{r sem, include=TRUE, results='asis'}
+# fit_table <- xtable(parameterEstimates(fit))
+# 
+# fit_table <- fit_table %>%
+#   filter(op=="~") %>%
+#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
+#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
+#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
+#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
+#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
+#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
+#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
+#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
+#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
+#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
+#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
+#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
+#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
+#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
+#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
+#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
+#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
+#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
+#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
+#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
+#   select(lhs, op, rhs, est, se, z, pvalue) %>%
+#   #taking out partner-partner estimates
+#   slice(1:5,11:13)
+# 
+# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
+# 
+# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
+# ```
+# 
+# ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
+# include_graphics("SEMfigure.png")
+# ```
 ```
 
-```{r sem, include=TRUE, results='asis'}
-fit_table <- xtable(parameterEstimates(fit))
+```{r}
+#SSO
+apim1 <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + a2pSOO_P*TSO_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
 
-fit_table <- fit_table %>%
-  filter(op=="~") %>%
-  mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO", 
-                      ifelse(lhs=="authenticity_A", "Actor Authenticity",
-                             ifelse(lhs=="howbody_avg_P", "Partner SSO",
-                                    ifelse(lhs=="authenticity_P", "Partner Authenticity", 
-                                           ifelse(lhs=="relag_A", "Actor Rel. Agency",
-                                                  ifelse(lhs=="relag_P", "Partner Rel. Agency",
-                                                         ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
-                                                                ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
-                                                                       ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
-                                                                              ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
-         rhs = ifelse(rhs=="TSO_A", "Actor TSO",
-                      ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
-                             ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
-                                    ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
-                                           ifelse(rhs == "howbody_avg_A", "Actor SSO",
-                                                  ifelse(rhs=="howbody_avg_P", "Partner SSO",
-                                                         ifelse(rhs=="TSO_P", "Partner TSO",
-                                                                ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
-                                                                       ifelse(rhs=="authenticity_A", "Actor Authenticity", 
-                                                                              ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
-  select(lhs, op, rhs, est, se, z, pvalue) %>%
-  #taking out partner-partner estimates
-  slice(1:5,11:13)
+summary(apim1)
+```
 
-colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
+```{r}
+#authenticity
+apim2 <- gls(authenticity_A ~ howbody_avg_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
 
-apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
+summary(apim2)
+```
+
+```{r}
+#cognitive performance
+apim3 <- gls(trigram_score_A ~ authenticity_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim3)
+```
+
+```{r}
+#relationship agency
+apim4 <- gls(relag_A ~ authenticity_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim4)
+```
+
+```{r}
+#career aspirations
+apim5 <- gls(careerasp_A ~ authenticity_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim5)
+```
+
+```{r}
+# pround <- function(val){ 
+#   ifelse(val < .001, 
+#          return(sub("^(-?)0.", "\\1.", sprintf("%.3f", .001))), 
+#          return(sub("^(-?)0.", "\\1.", sprintf("%.3f", val))))
+# }
+# 
+# estround <- function(val){ 
+#   ifelse(abs(val) < .01, 
+#          return(.01), 
+#          return(round(val, 2)))
+# }
+
+#only works for merModlmerTest objects or when p-values on are in column 4, "lm" objects
+# report_stats <- function(mod, est){
+#   
+#   b <- coef(summary(mod))[,1]
+#   se <- coef(summary(mod))[,2]
+#   ifelse(class(mod) == "merModLmerTest", 
+#          p <- coef(summary(mod))[,5], 
+#          p <- coef(summary(mod))[,4])
+#   
+#   paste(ifelse(abs(b[est]) < .01,"*b* < ","*b* = "), as.character(estround(b[est])), 
+#         ifelse(se[est] < .01, ", *SE* < ", ", *SE* = "), as.character(estround(se[est])), 
+#         ifelse(p[est] < .001, ", *p* < ", ", *p* = "),  as.character(pround(p[est])), 
+#         sep = "") %>%
+#     return()
+# }
+
+# randomeffects <- as.data.frame(VarCorr(mlm_mod1.0))
+# randomeffects2 <- as.data.frame(VarCorr(mlm_mod2.0))
+```
+
+```{r mlm, include=TRUE, results='asis'}
+# fit_table <- xtable(parameterEstimates(fit))
+# 
+# fit_table <- fit_table %>%
+#   filter(op=="~") %>%
+#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
+#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
+#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
+#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
+#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
+#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
+#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
+#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
+#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
+#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
+#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
+#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
+#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
+#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
+#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
+#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
+#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
+#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
+#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
+#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
+#   select(lhs, op, rhs, est, se, z, pvalue) %>%
+#   #taking out partner-partner estimates
+#   slice(1:5,11:13)
+# 
+# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
+# 
+# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
 ```
@@
 ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
-include_graphics("SEMfigure.png")
+# include_graphics("SEMfigure.png")
 ```
@@
 ##Main Results
-All model estimates and p-values are found in Table\ \@ref(tab:sem) and the relationships are depicted in Figure\ \@ref(fig:semfigure).
-The most important findings from @garcia2016objectification were the significant partner effect between actor SSO and partner objectification (specifically men's objectification of women and women's SSO), and the link between actor SSO and actor authenticity (also specifically for women).
+All model estimates and p-values are found in Table\ \@ref(tab:mlm) and the relationships with estimates included are depicted in Figure\ \@ref(fig:semfigure).
+
+<!-- The most important findings from @garcia2016objectification were the significant partner effect between actor SSO and partner objectification (specifically men's objectification of women and women's SSO), and the link between actor SSO and actor authenticity (also specifically for women).
 We did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which means we do not have evidence to support the idea that partner objectification is the cause for the negative effects related to relationship inauthenticity.
@@
 In this case, a good fit indicates that there are no direct effects of SSO or SOO on the outcomes on cognitive performance, relationship agency, and career aspirations, which indicates that the path we chose makes sense.
+-->
 

### 2020-06-29 Final_Manuscript.Rmd
Added to the results section

@@
 The significant partner effect of objectification on actor self-objectification suggests that women being objectified by other women still results in feelings of self-objectification, and such research has powerful implications for the ways that women interact in both sexual and non-sexual settings.
+AUTHOR NOTE: mention Clark trigram coders Hannah et al.
 
@@
 library(mosaic)
+#library(dyadr)
 library(tidyr)
@@
 
+apim1.b <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
 summary(apim1)
@@
 summary(apim2)
+
+#Trying to perform analyses for each item for a footnote...will need to get to the bottom of this. 
+# inter_1, inter_3, inter_5, inter_6, 
+# inter_7, inter_9, inter_10, interaux_5, 
+# interaux_6
+# 
+# apim2 <- gls(inter_1 ~ howbody_avg_A, 
+#                  na.action=na.omit, 
+#                  correlation=corCompSymm (form=~1|dyadID),
+#                  data=clarksmith_women)
+
+apim2.b <- gls(authenticity_A ~ howbody_avg_A + a2pSOO_P, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim2.b)
+
+apim2.c <- gls(authenticity_A ~a2pSOO_P, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim2.c)
 ```
@@
 summary(apim3)
+
+apim3.b <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim3.b)
+
+apim3.c <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim3.c)
 ```
@@
 summary(apim4)
+
+apim4.b <- gls(relag_A ~ authenticity_A + howbody_avg_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim4.b)
+
+apim4.c <- gls(relag_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim4.c)
 ```
@@
 summary(apim5)
+
+apim5.b <- gls(careerasp_A ~ authenticity_A + howbody_avg_A, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim5.b)
+
+apim5.c <- gls(careerasp_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
+summary(apim5.c)
 ```
 
-```{r}
-# pround <- function(val){ 
-#   ifelse(val < .001, 
-#          return(sub("^(-?)0.", "\\1.", sprintf("%.3f", .001))), 
-#          return(sub("^(-?)0.", "\\1.", sprintf("%.3f", val))))
-# }
-# 
-# estround <- function(val){ 
-#   ifelse(abs(val) < .01, 
-#          return(.01), 
-#          return(round(val, 2)))
-# }
-
-#only works for merModlmerTest objects or when p-values on are in column 4, "lm" objects
-# report_stats <- function(mod, est){
-#   
-#   b <- coef(summary(mod))[,1]
-#   se <- coef(summary(mod))[,2]
-#   ifelse(class(mod) == "merModLmerTest", 
-#          p <- coef(summary(mod))[,5], 
-#          p <- coef(summary(mod))[,4])
-#   
-#   paste(ifelse(abs(b[est]) < .01,"*b* < ","*b* = "), as.character(estround(b[est])), 
-#         ifelse(se[est] < .01, ", *SE* < ", ", *SE* = "), as.character(estround(se[est])), 
-#         ifelse(p[est] < .001, ", *p* < ", ", *p* = "),  as.character(pround(p[est])), 
-#         sep = "") %>%
-#     return()
-# }
-
-# randomeffects <- as.data.frame(VarCorr(mlm_mod1.0))
-# randomeffects2 <- as.data.frame(VarCorr(mlm_mod2.0))
+```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
+include_graphics("SEMfigure.png")
 ```
@@
 
-```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
-# include_graphics("SEMfigure.png")
+```{r presentation-functions}
+ pround <- function(val){
+  ifelse(val < .001,
+         return(sub("^(-?)0.", "\\1.", sprintf("%.3f", .001))),
+         return(sub("^(-?)0.", "\\1.", sprintf("%.3f", val))))
+}
+
+estround <- function(val){
+  ifelse(abs(val) < .01,
+         return(.01),
+         return(round(val, 2)))
+}
+
+#only works for merModlmerTest objects or when p-values on are in column 4, "lm" objects
+report_stats <- function(mod, est){
+
+  b <- coef(summary(mod))[,1]
+  se <- coef(summary(mod))[,2]
+  ifelse(class(mod) == "merModLmerTest",
+         p <- coef(summary(mod))[,5],
+         p <- coef(summary(mod))[,4])
+
+  paste(ifelse(abs(b[est]) < .01,"*b* < ","*b* = "), as.character(estround(b[est])),
+        ifelse(se[est] < .01, ", *SE* < ", ", *SE* = "), as.character(estround(se[est])),
+        ifelse(p[est] < .001, ", *p* < ", ", *p* = "),  as.character(pround(p[est])),
+        sep = "") %>%
+    return()
+}
+
+report_stats(apim1, 2)
+
+# randomeffects <- as.data.frame(VarCorr(mlm_mod1.0))
+# randomeffects2 <- as.data.frame(VarCorr(mlm_mod2.0))
 ```
@@
 
-<!-- The most important findings from @garcia2016objectification were the significant partner effect between actor SSO and partner objectification (specifically men's objectification of women and women's SSO), and the link between actor SSO and actor authenticity (also specifically for women).
-We did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which means we do not have evidence to support the idea that partner objectification is the cause for the negative effects related to relationship inauthenticity.
-However, we did find a significant relationship between partner objectification and actor SSO ($\beta$= .25, $p$=.03), which supports our hypothesis that objectification from other women also causes women to self-objectify just as it does in interactions between male-female pairs.
-We also found a significantly negative effect of authenticity on career aspirations ($\beta$= .18, $p$=.01) and relationship agency ($\beta$=.27, $p$=.01).
-We found that the model had good fit ($\chi^2$=22.33, $df$=34).
-In this case, a good fit indicates that there are no direct effects of SSO or SOO on the outcomes on cognitive performance, relationship agency, and career aspirations, which indicates that the path we chose makes sense.
--->
+The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
+As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically signficant, `r report_stats(apim1, 3)`, replicating @garcia2016objectification's fiding.
+One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
+Contrary to past finding however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
+There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.
+
+Contrary to expectations, there was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
+Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also tested the effect of SSO on these items individually...ADD ANALYSIS...Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship bewteen SSO and authencity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, `r report_stats(apim2.b, 3)` (nor was the total effect of partner's other objectification on authenticity, `r report_stats(apim2.c, 2)`).
+
+Lastly, althought there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performace, career aspirations, and relationship agency, as it did in @garcia2016objectification.
+We again used MLM and thus, these efefcts were tested in three separate models.
+There was no significant effect of interaction authenticity on cognitive performance, `r report_stats(apim3, 2)`, but authenticity was significantly positively related to both career aspirations, `r report_stats(apim5, 2)`, and relationships agency, `r report_stats(apim4, 2)`.
+There was no direct effect of SSO on cognitive performance, `r report_stats(apim3.b, 3)`, and no direct effect of partner's other objectificaiton on cognifitve performance, `r report_stats(apim3.c, 4)`.
+There was no direct effect of SSO on career aspirations, `r report_stats(apim5.b, 3)`, and no direct effect of partner's other objectificaiton on career aspirations, `r report_stats(apim5.c, 4)`.
+There was no direct effect of SSO on relationship agency, `r report_stats(apim4.b, 3)`, and no direct effect of partner's other objectificaiton on relationship agency, `r report_stats(apim4.c, 4)`.
 

### 2020-06-29 Final_Manuscript.Rmd
updates about combining samples

@@
 Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US.
+The results section contains more detail about equivalence analyses to support the decision to combine these two samples.
 
@@
 ```
-
 ## Data analysis
 We used `r cite_r("r-references.bib")` for all our analyses.
-
 ```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
@@
 ```
-
 ```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
@@
 ```
-
 ## Analysis Strategy
@@
 
+Before moving to the main analyses, we discuss statistical equivalence test that provide support for combining Sample 1 and Sample 2 in one analysis sample.
+The online supplemental material contains the main analyses separated by samples.
+
 <!-- The model differences as a result of adopting this MLM approach include an examination of the partner effect of TSO on SSO, partner effect of SSO on authenticity, and partner effects of authenticity on congitive performance, relationship agency, and career aspirations.
@@
 
+### Combining Samples
+
+The correaltions between study variables is similar across samples.
+The realibialities for the study scales were also equivalent.
+(Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS.
 ```{r}
@@
 ```
-
 ```{r}
@@
 ```
-
 ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
@@
 ```
-
 ```{r mlm, include=TRUE, results='asis'}
@@
 
+The results were similar for analyses conducted on Sample 1 and Sample 2 individually. See the online supplemental material for more detail on these analyses.
+
 #Discussion

### 2020-06-30 Final_Manuscript.Rmd
reorganized files

@@
 clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
+
+smith$inter_1
 ```

### 2020-06-30 Final_Manuscript.tex
reorganized files

@@
             pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
-            pdfauthor={Kat Kyuchukova, Asha Hinson, \& Randi L. Garcia},
+            pdfauthor={Randi L. Garcia, Kat Kyuchukova, \& Asha Hinson},
             pdfkeywords={keywords},
@@
 Same-gender Interactions}
-    \author{Kat Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \&
-Randi L. Garcia\textsuperscript{1}}
+    \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
+Kyuchukova\textsuperscript{1}, \& Asha Hinson\textsuperscript{1}}
     \date{}
@@
 \vspace{0.5cm}
-\textsuperscript{1} Smith College}
+\textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
 \keywords{keywords}
@@
 
-\
+\authornote{
+
+Correspondence concerning this article should be addressed to Randi L.
+Garcia, 415 Bass Hall, Smith College, Northampton, MA 01060. E-mail:
+\href{mailto:rgarcia@smith.edu}{\nolinkurl{rgarcia@smith.edu}}}
 
 \abstract{
-Objectification theory is a valuable framework for conceptualizing the
-psychological consequences of being female within a society that
-sexually objectifies the female body, and considering the ways in which
-girls and women are acculturated to then internalize an observer's
-perspective as a primary view of their appearance. Empirical evidence
-has largely elucidated links between objectification,
+Empirical evidence has only found links between objectification,
 self-objectification, and negative outcomes for woman within
-interpersonal interactions between male-female pairs particularly. The
-purpose of the present study was to extend past research and consider
-the relationships between such valuable phenomena and their effects on
-authenticity within interactions between female pairs. Woman were
-brought into the laboratory and interacted in same-sex dyads. Dyadic
-analysis was utilized to detect whether partners' objectification of
-each other affected state self-objectification, and the resulting
-feelings of comfort and authenticity during the interaction. After the
-interaction, participants completed a questionnaire which measured many
-constructs including cognitive performance, career aspirations, and
-relationship agency. Results revealed no significant relationship
-between self-objectification and authenticity. Further, although there
-were significantly negative effects on career aspirations and
-relationship agency resulting from a lack of relationship authenticity,
-there was no evidence that this is due to feelings of sexual
-objectification. The significant partner effect of objectification on
-actor self-objectification suggests that women being objectified by
-other women still results in feelings of self-objectification, and such
+interpersonal interactions between male-female pairs. The purpose of the
+present study was to extend past research and consider the relationships
+between such valuable phenomena and their effects on authenticity within
+interactions between female pairs. Woman were brought into the
+laboratory and interacted in same-sex dyads. Dyadic analysis was
+utilized to detect whether partners' objectification of each other
+affected state self-objectification, and the resulting feelings of
+comfort and authenticity during the interaction. After the interaction,
+participants completed a questionnaire which measured many constructs
+including cognitive performance, career aspirations, and relationship
+agency. Results revealed no significant relationship between
+self-objectification and authenticity. Further, although there were
+significantly negative effects on career aspirations and relationship
+agency resulting from a lack of relationship authenticity, there was no
+evidence that this is due to feelings of sexual objectification. The
+significant partner effect of objectification on actor
+self-objectification suggests that women being objectified by other
+women still results in feelings of self-objectification, and such
 research has powerful implications for the ways that women interact in
-both sexual and non-sexual settings.
+both sexual and non-sexual settings. AUTHOR NOTE: mention Clark trigram
+coders Hannah et al.
+
 }
@@
 
-\section{Introduction}\label{introduction}
-
 Theorists across diverse disciplines have explored the multiple ways
 that the body conveys social meaning, as well as how these meanings
-shape gendered experiences and therefore inform individuals' thinking,
-feeling, and behavior, especially during interpersonal interactions with
-members of different social groups (``Engendered lives,'' 1993).
-Empirical evidence illustrates how women, in particular, continue to be
-objects of perpetual discrimination as a result of psychosocial markers,
-like gender, that produce modes through which their identity is
-understood (Swim, Hyers, Cohen, \& Ferguson, 2001). Objectification
-theory, a valuable theoretical framework proposed by Roberts and
-Fredrickson (1997) which works to contextualize female bodies as
-socio-cultural constructions, can be employed to illuminate the gender
-oppression and negative lived experiences of girls and women.
-Additionally, one of the most detrimental forms of discrimination
-against them is thought to be the process by which their whole being is
-viewed as a collection of sexualized body parts valued predominantly for
-commodification, a phenomena termed sexual objectification (Bartky,
-1990). Sexual objectification occurs with both \enquote{endless variety
-and monotonous similarity,} and is thus mediated by unique combinations
-of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
-Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
-Nicholson (1989), p.~28). Amid such heterogeneity though,
-\enquote{having a reproductively mature female body} proposed by Roberts
-and Fredrickson (1997) is likely to create a shared vulnerability to
-sexual objectification and a variety of shared negative experiences as a
-result. Studies have shown that within social encounters women are gazed
-at more than men (Briton \& Hall, 1995), often times feel
-\enquote{looked at} within interpersonal interactions (Argyle \&
-Williams, 1969), and will more than likely internalize the objectifying
-gaze on physical self (Young, 1979). Moreover, perhaps the most adverse
-effect of objectifying treatment is that it effectively socializes girls
-and women to treat themselves as objects to be looked at and evaluated,
-an effect termed self-objectification (Bartky, 1990; Berger, Cohen, \&
-Zelditch Jr, 1972; L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge,
-1998). Self-objectification is a multidimensional process that accounts
-for the cognitive mechanism that translates experiences of sexualization
-at the cultural level to psychological (e.g., anxiety, self-esteem,
+shape gendered experiences, especially during interpersonal interactions
+with members of different social groups (``Engendered lives,'' 1993,
+Garcia, Earnshaw, and Quinn (2016)). Objectification theory, a valuable
+theoretical framework proposed by Roberts and Fredrickson (1997) which
+works to contextualize female bodies as socio-cultural constructions,
+can be employed to illuminate the gender oppression and negative lived
+experiences of girls and women. Empirical evidence illustrates how women
+continue to be objects of interpersonal discrimination and expereince
+daily sexist hassles (Swim, Hyers, Cohen, \& Ferguson, 2001). One form
+of interpersonal discrimination women face is the process by which their
+whole being is viewed as a collection of sexualized body parts valued
+predominantly for commodification, a phenomena termed sexual
+objectification (Bartky, 1990). Sexual objectification occurs with both
+\enquote{endless variety and monotonous similarity,} and is thus
+mediated by unique combinations of race, ethnicity, sexuality, age, and
+class (Fredrickson, Hendler, Nilsen, O'Barr, \& Roberts, 2011; Rubin,
+1975, cited in Fraser and Nicholson (1989), p.~28). Amid such
+heterogeneity though, \enquote{having a reproductively mature female
+body} proposed by Roberts and Fredrickson (1997) is likely to create a
+shared vulnerability to sexual objectification and a variety of shared
+negative experiences as a result.
+
+Self-objectification is a multidimensional process that accounts for the
+cognitive mechanism that translates experiences of sexualization at the
+cultural level to psychological (e.g., anxiety, self-esteem,
 authenticity, motivational states) and behavioral (cognitive
@@
 influence experiences of feeling like a body, or state
-self-objectification (SSO). In the current work, we sought to examine
-what occurs during an interaction in which one or both partners are
-objectifying each other, similarly to Garcia, Earnshaw, and Quinn
-(2016), but between same-sex female interpersonal interactions. We
-predicted that being objectified by one's interaction partner would lead
-to self-objectification, in addition to modified feelings of
-authenticity in postinteraciton outcomes, including feelings of agency
-in romantic relationships, career aspiration, and cognitive performance
-(D. M. Quinn, Chaudoir, \& Kallen, 2011). Empirical evidence reveals
-that objectification manifests through inauthenticity in romantic
-relationships (Brunell et al., 2010), adverse attitudes in regard to
-career aspirations, and a decrease in concentration and impairment in
-female cognitive performance (Swim et al., 2001). Moreover, it was the
-goal of this research to empirically explore the role of interaction
-authenticity in objectification by utilizing a structural equation
-modeling to examine the effects for both women simultaneously. We
-expected to replicate the results found in the previous Garcia et al.
-(2016) study. More specifically, we expected to find a positive
-relationship between state-other objectification and self-state
-objectification, and a resulting negative relationship between
-self-state objectification and interaction authenticity. Finally, we
-expected there to be a positive relationship between interaction
-authenticity and cognitive performance, relationship agency, and career
-aspirations.
+self-objectification (SSO) (CITE swimsuit sweater, Garcia et al., 2016).
+
+Studies have shown that within social encounters women are gazed at more
+than men (Briton \& Hall, 1995, CITE saguy skype study, calogero video
+walking study), often times feel \enquote{looked at} within
+interpersonal interactions (Argyle \& Williams, 1969), and will more
+than likely internalize the objectifying gaze on physical self (Young,
+1979). Moreover, perhaps the most adverse effect of objectifying
+treatment is that it effectively socializes girls and women to treat
+themselves as objects to be looked at and evaluated, an effect termed
+self-objectification (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972;
+L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge, 1998).
+
+ENTIRE PARAGRAPH ON MODERN (POST-2016) STUDIES OF INTERPERSONAL
+OBJECTIFICATION.
+
+Empirical evidence reveals that objectification manifests through
+inauthenticity in romantic relationships (Brunell et al., 2010), adverse
+attitudes in regard to career aspirations, and a decrease in
+concentration and impairment in female cognitive performance (D. M.
+Quinn, Chaudoir, \& Kallen, 2011).
+
+In the current study, we sought to examine what occurs during an
+interaction in which one or both partners are objectifying each other,
+similarly to Garcia et al. (2016), but between same-sex female
+interpersonal interactions. Moreover, the current study uses a
+face-to-face interaction paradigm and dyadic data analysis techniques to
+examine the effects for both women simultaneously. We expected to
+replicate the results found in Garcia et al. (2016). We predicted that
+being objectified by one's interaction partner would lead to
+self-objectification, which in turn would lead to feelings of
+inauthenticity, then reduced feelings of agency in romantic
+relationships, reduced career aspiration, and reduced cognitive
+performance. Specifically, we expected to find a positive relationship
+between other-objectification by one's partner and state
+self-objectification. We also expect to find a negative relationship
+between self-state objectification and interaction authenticity, and
+that interaction authenticity will be positively related to cognitive
+performance, relationship agency, and career aspirations.
 
@@
 
-Data from two different samples were used for this study and are
-discussed below. In the measures section that follows we refer to them
-as Sample 1 and Sample 2. Sample 1 is from a co-ed liberal arts college
-in the northeast and Sample 2 is from a women's liberal arts college in
-the northeast.
+Data from two different, but demographically equivalent, samples were
+combined to create the final analysis sample (\emph{N =} 64) used in
+this study. In the measures section that follows we refer to them as
+Sample 1 and Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal
+arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
+women's liberal arts college in the northeast US.
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:corrtable}Correlations among study variables.}
+\begin{tabular}{llllllll}
+\toprule
+ & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5}\\
+\midrule
+Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  & \\
+Actor's authenticity of interaction & 5.23 & 1.02 & -.02 &  &  &  & \\
+Actor's objectification of partner & -1.58 & 1.21 & .20 & -.07 &  &  & \\
+Actor's state self-objectification & 1.92 & 1.13 & .13 & -.10 & -.09 &  & \\
+Actor's future relationship agency & 4.69 & 0.96 & .04 & .23+ & .09 & -.09 & \\
+Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .11 & .02 & .07\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:descriptives}Descriptive Statistics for Study Variables}
+\begin{tabular}{lll}
+\toprule
+ & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD}\\
+\midrule
+Actor's trait self objectification (TSO) & -0.35 & 2.64\\
+Actor's authenticity of interaction & 5.23 & 1.02\\
+Actor's objectification of partner & -1.58 & 1.21\\
+Actor's state self-objectification & 1.92 & 1.13\\
+Actor's future relationship agency & 4.69 & 0.96\\
+Actor's cognitive performance & 5.03 & 2.29\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
 
@@
 
+\section{Results}\label{results}
+
 \subsection{Data analysis}\label{data-analysis}
 
-We used R (Version 3.4.1; R Core Team, 2017) and the R-packages
+We used R (Version 3.5.2; R Core Team, 2017) and the R-packages
 \emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools}
-(Version 2.0.1; Wickham, Hester, \& Chang, 2018), \emph{dplyr} (Version
-0.8.0.1; Wickham, François, Henry, \& Müller, 2018), \emph{forcats}
-(Version 0.3.0; Wickham, 2018), \emph{ggformula} (Version 0.6; D. Kaplan
-\& Pruim, 2017), \emph{ggplot2} (Version 3.1.0.9000; Wickham, 2016),
+(Version 1.13.5; Wickham, Hester, \& Chang, 2018), \emph{dplyr} (Version
+0.8.3; Wickham, François, Henry, \& Müller, 2018), \emph{forcats}
+(Version 0.3.0; Wickham, 2018), \emph{ggformula} (Version 0.7.0; D.
+Kaplan \& Pruim, 2017), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
 \emph{haven} (Version 2.1.0; Wickham \& Miller, 2019), \emph{irr}
-(Version 0.84; Gamer, Lemon, \&
+(Version 0.84.1; Gamer, Lemon, \&
 \textless{}puspendra.pusp22@gmail.com\textgreater{}, 2012), \emph{knitr}
-(Version 1.22; Xie, 2015), \emph{kutils} (Version 1.67; Johnson, Kite,
-\& Redmon, 2019), \emph{lattice} (Version 0.20.35; Sarkar, 2008),
-\emph{lavaan} (Version 0.6.3; Rosseel, 2012), \emph{lpSolve} (Version
-5.6.13; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.10; Bates
-\& Maechler, 2017), \emph{mosaic} (Version 1.1.0; Pruim, Kaplan, \&
-Horton, 2017, 2016), \emph{mosaicData} (Version 0.14.0; Pruim et al.,
-2016), \emph{nlme} (Version 3.1.131; Pinheiro, Bates, DebRoy, Sarkar, \&
+(Version 1.25; Xie, 2015), \emph{kutils} (Version 1.70; Johnson, Kite,
+\& Redmon, 2019), \emph{lattice} (Version 0.20.38; Sarkar, 2008),
+\emph{lavaan} (Version 0.6.1; Rosseel, 2012), \emph{lpSolve} (Version
+5.6.15; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.15; Bates
+\& Maechler, 2017), \emph{mosaic} (Version 1.2.0; Pruim, Kaplan, \&
+Horton, 2017, 2016), \emph{mosaicData} (Version 0.17.0; Pruim et al.,
+2016), \emph{nlme} (Version 3.1.137; Pinheiro, Bates, DebRoy, Sarkar, \&
 R Core Team, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
-2018), \emph{psych} (Version 1.7.8; Revelle, 2017), \emph{purrr}
+2018), \emph{psych} (Version 1.8.4; Revelle, 2017), \emph{purrr}
 (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.1.1;
 Wickham, Hester, \& Francois, 2017), \emph{stringr} (Version 1.4.0;
-Wickham, 2019), \emph{tibble} (Version 2.1.1; Müller \& Wickham, 2019),
-\emph{tidyr} (Version 0.8.3; Wickham \& Henry, 2019), \emph{tidyverse}
-(Version 1.2.1; Wickham, 2017), \emph{usethis} (Version 1.4.0; Wickham
-\& Bryan, 2018), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen,
-Magnusson, \& Swinton, 2019) for all our analyses.
+Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
+\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse}
+(Version 1.2.1; Wickham, 2017), \emph{usethis} (Wickham \& Bryan, 2018),
+and \emph{xtable} (Version 1.8.3; Dahl, Scott, Roosen, Magnusson, \&
+Swinton, 2019) for all our analyses.
 
-\section{Results}\label{results}
+\begin{figure}
+\includegraphics[width=400px]{APIM_figure} \caption{Basic actor-partner interdependence model (APIM) depiction.}\label{fig:apim}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=400px]{2016_figure} \caption{Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads.}\label{fig:2016figure}
+\end{figure}
 
@@
 This study sought to replicate the results of Garcia et al. (2016)'s
-study, done with male-female pairs, which used dyadic analysis to detect
-whether partners' objectification of one another affected state
-self-objectification (SSO). See Figure~\ref{fig:2016figure} for the path
-analysis results of the previous study. We hope to investigate how the
-main effects found in the previous study relay to interactions between
-women: specifically, the relationship between state-other
-objectification and self-state objectification and the resulting effect
-of self-state objectification on inauthenticity during the interaction.
+study, done with male-female pairs, which used a dyadic path analysis to
+detect whether partners' objectification of one another affected state
+self-objectification (SSO). See Figure~\ref{fig:2016figure} for the
+results of the analysis from this previous study. We hope to investigate
+how the central effects found in the previous study relate to
+interactions between two women. Specifically, we are interested in
+testing the relationship between state-other objectification and SSO,
+and how SSO in turn, affecs feelings of inauthenticity during the
+interaction. In addition, we will also test if the effect of
+other-objectification in an interaction on SSO is only present for those
+women who are high in trait self-objectification, as in Garcia et al.
+(2016). Further, we will investigate the realtionships between
+experiencing interaction inauthenticity and relationship agency, career
+aspirations, and cognitive performance.
 
-We used path analysis to obtain our estimates, but because our sample is
-nonindependent, we used the indistinguishable actor--partner
-interdependence model (Olsen \& Kenny, 2006). The APIM can be defined as
-a \enquote{model of dyadic relationships that integrates a conceptual
-view of interdependence with the appropriate statistical techniques for
-measuring and testing it} (Olsen \& Kenny, 2006). See
-Figure~\ref{fig:apim} for a basic APIM model. Unlike the original Garcia
-et al. (2016) study, our study deals with indistinguishable dyads,
-meaning the designation of who is designated as \enquote{actor} and who
-is designated as \enquote{partner} is arbitrary. Due to constraints of
-the basic APIM, in that this was an exploration of indistinguishable
-female dyads, we had to fix all path estimates to be the same
-across/between people and partners, in addition to all variances,
-covariances, endogenous intercepts, and exogenous means. Due to the
-complexity of the original Garcia et al. (2016) study, we also had to
-set the exogenous covariances equal. More specifically, the covariances
-between TSO, actor and partner objectification, and the interaction
-between actor TSO and partner objectification (and vice versa).
+While Garcia et al. (2016) used dyadic path analysis, we will conduct
+our dyadic analyses using multilevel modeling. Dyadic analyses for
+distingishable dyads (e.g., mixed-gender interacting pairs) is more
+natural in Structual Equation Modeling (SEM) than it is for
+indistinguishable dayds (e.g., same-gender interacting pairs) (Garcia,
+Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
+this asymmetry is that, due to the arbitrary distinctions made bewteen
+\enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads,
+many estimates need to be fixed to be equal (i.e., paths, variances,
+covariances, endogenous intercepts, and exogenous means) for
+indistinguishable dyads but these equality contraints should not then be
+considered in the degrees of freedom calculations for fit estimations
+(Olsen \& Kenny, 2006). Further, Olsen and Kenny (2006) detail how a new
+independence model and the corresponding fit measure should be
+re-calculated for indistinguishable dyads models. The current study uses
+dyadic multilevel modeling (MLM) to test all relationships and mediation
+paterns. See Ledermann and Kenny (2017) for a more complete discussion
+of the considerations for using SEM versus MLM for dyadic analysis.
 
-In order to interpret model fit, which refers to the ability of a model
-to reproduce the data (i.e., usually the varience-covariance matrix) we
-utilized both the I-SAT (saturated) model, and the Null model to ensure
-that all possible corresponding covariences are fixed to be equal across
-partners. We obtained fit estimates by subtracting the chi-square
-estimate for the I-SAT model from the analysis model (Olsen \& Kenny,
-2006, Peugh, DiLillo, and Panuzio (2013)).
+Testing the Garcia et al. (2016) model on the current, same-gender,
+sample, involves using the Actor-Partner Independence Model (APIM)
+approch for each outcome variable (i.e., endogenous variable in
+Figure~\ref{fig:2016figure}). Thus, we ran five APIM's to test all the
+hypothesized relationships. See Figure~\ref{fig:apim} for a basic APIM
+model. The APIM includes effects due to one's own, as well as one's
+partner's, predictor variables (\(X\)'s) on the one's own outcome
+variable (\(Y\)). Unlike the original Garcia et al. (2016) study, our
+study deals with indistinguishable dyads, meaning the designation of who
+is designated as \enquote{actor} and who is designated as
+\enquote{partner} is arbitrary. Recall that the indistinguiahble nature
+of the dyads in the current study led us to choose the MLM approach over
+SEM. These analyses are considered exploratory, given the lack of prior
+research theorizing about these linkages.
+
+\begin{figure}
+\includegraphics[width=400px]{SEMfigure} \caption{Path Analysis Model with Estimates}\label{fig:semfigure}
+\end{figure}
 
@@
 
-All model estimates and p-values are found in Table~\ref{tab:sem}. The
-most important findings from Garcia et al. (2016) were the significant
-partner effect between actor SSO and partner objectification
-(specifically men's objectification of women and women's SSO), and the
-link between actor SSO and actor authenticity (also specifically for
-women). We did not find a significant effect between actor SSO and actor
-authenticity (\(\beta\)= -.10, \(p\)=.38), which means we do not have
-evidence to support the idea that partner objectification is the cause
-for the negative effects related to relationship inauthenticity.
-However, we did find a significant relationship between partner
-objectification and actor SSO (\(\beta\)= .25, \(p\)=.03), which
-supports our hypothesis that objectification from other women also
-causes women to self-objectify just as it does in interactions between
-male-female pairs. We also found a significantly negative effect of
-authenticity on career aspirations (\(\beta\)= .18, \(p\)=.01) and
-relationship agency (\(\beta\)=.27, \(p\)=.01). We found that the model
-had good fit (\(\chi^2\)=22.33, \(df\)=34). In this case, a good fit
-indicates that there are no direct effects of SSO or SOO on the outcomes
-on cognitive performance, relationship agency, and career aspirations,
-which indicates that the path we chose makes sense.
+All model estimates and p-values are found in Table~\ref{tab:mlm} and
+the relationships with estimates included are depicted in
+Figure~\ref{fig:semfigure}.
+
+The most important finding from Garcia et al. (2016) was the significant
+partner effect of other objectification and SSO (specifically men's
+objectification of women and women's SSO). As expected, the partner
+effect of other-objectification on SSO in the current all-women sample
+was statistically signficant, \emph{b} = 0.29, \emph{SE} = 0.12,
+\emph{p} = .017, replicating Garcia et al. (2016)'s fiding. One's own
+other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
+= 0.12, \emph{p} = .193. Contrary to past finding however, there was no
+statistically significant interaction of partner's other objectification
+and the person's trait self-objectification on SSO, \emph{b} = -0.02,
+\emph{SE} = 0.04, \emph{p} = .589. There was also no significant main
+effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
+0.05, \emph{p} = .170.
+
+Contrary to expectations, there was no significant effect of SSO on
+interaction authenticity, although the estimate of this effect was in
+the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.11,
+\emph{p} = .415. Because authenticity was a composite score of 9 items,
+two of which were interaction specific authenticity items, we also
+tested the effect of SSO on these items individually\ldots{}ADD
+ANALYSIS\ldots{}Although we hypothesized that SSO would mediate the
+relationship between partner's other objectification and interaction
+authenticity, after finding no relationship bewteen SSO and authencity,
+we also tested if the partner's other objectification had a direct
+effect on authenticity, but this effect was not significant, \emph{b} =
+0.05, \emph{SE} = 0.11, \emph{p} = .662 (nor was the total effect of
+partner's other objectification on authenticity, \emph{b} = 0.02,
+\emph{SE} = 0.1, \emph{p} = .855).
+
+Lastly, althought there was no evidence that SSO was related to
+interaction authenticity in the current sample, we tested if interaction
+authenticity (composite of nine items) had effects on cognitive
+performace, career aspirations, and relationship agency, as it did in
+Garcia et al. (2016). We again used MLM and thus, these efefcts were
+tested in three separate models. There was no significant effect of
+interaction authenticity on cognitive performance, \emph{b} = 0.31,
+\emph{SE} = 0.28, \emph{p} = .262, but authenticity was significantly
+positively related to both career aspirations, \emph{b} = 0.19,
+\emph{SE} = 0.07, \emph{p} = .009, and relationships agency, \emph{b} =
+0.23, \emph{SE} = 0.12, \emph{p} = .048. There was no direct effect of
+SSO on cognitive performance, \emph{b} = 0.05, \emph{SE} = 0.25,
+\emph{p} = .846, and no direct effect of partner's other objectificaiton
+on cognifitve performance, \emph{b} = 0.03, \emph{SE} = 0.26, \emph{p} =
+.900. There was no direct effect of SSO on career aspirations, \emph{b}
+= 0.03, \emph{SE} = 0.06, \emph{p} = .653, and no direct effect of
+partner's other objectificaiton on career aspirations, \emph{b} = -0.05,
+\emph{SE} = 0.06, \emph{p} = .405. There was no direct effect of SSO on
+relationship agency, \emph{b} = -0.04, \emph{SE} = 0.11, \emph{p} =
+.699, and no direct effect of partner's other objectificaiton on
+relationship agency, \emph{b} = -0.07, \emph{SE} = 0.1, \emph{p} = .474.
 
@@
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:corrtable}Correlations among study variables.}
-\begin{tabular}{llllllll}
-\toprule
- & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5}\\
-\midrule
-Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  & \\
-Actor's authenticity of interaction & 5.23 & 1.02 & -.02 &  &  &  & \\
-Actor's objectification of partner & -1.58 & 1.21 & .20 & -.07 &  &  & \\
-Actor's state self-objectification & 1.92 & 1.13 & .13 & -.10 & -.09 &  & \\
-Actor's future relationship agency & 4.69 & 0.96 & .04 & .23+ & .09 & -.09 & \\
-Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .11 & .02 & .07\\
-\bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:descriptives}Descriptive Statistics for Study Variables}
-\begin{tabular}{lll}
-\toprule
- & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD}\\
-\midrule
-Actor's trait self objectification (TSO) & -0.35 & 2.64\\
-Actor's authenticity of interaction & 5.23 & 1.02\\
-Actor's objectification of partner & -1.58 & 1.21\\
-Actor's state self-objectification & 1.92 & 1.13\\
-Actor's future relationship agency & 4.69 & 0.96\\
-Actor's cognitive performance & 5.03 & 2.29\\
-\bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:sem}Estimates from final Path Analysis Model}
-\small{
-\begin{tabular}{lllllll}
-\toprule
-Path & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{z-value} & \multicolumn{1}{c}{p-value}\\
-\midrule
-Actor SSO & \textasciitilde{} & Actor TSO & 0.08 & 0.09 & 0.91 & 0.36\\
-Actor SSO & \textasciitilde{} & Actor Obj. of Partner & -0.17 & 0.12 & -1.41 & 0.16\\
-Actor SSO & \textasciitilde{} & Partner Obj. of Actor & 0.25 & 0.12 & 2.15 & 0.03\\
-Actor SSO & \textasciitilde{} & Actor TSO x Partner Obj. & 0.00 & 0.04 & -0.10 & 0.92\\
-Actor Authenticity & \textasciitilde{} & Actor SSO & -0.10 & 0.12 & -0.88 & 0.38\\
-Actor Cog. Performance & \textasciitilde{} & Actor Authenticity & 0.33 & 0.27 & 1.22 & 0.22\\
-Actor Career Aspirations & \textasciitilde{} & Actor Authenticity & 0.18 & 0.07 & 2.66 & 0.01\\
-Actor Rel. Agency & \textasciitilde{} & Actor Authenticity & 0.27 & 0.10 & 2.64 & 0.01\\
-\bottomrule
-\end{tabular}
-}
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\begin{figure}
-\includegraphics[width=400px]{APIM_figure} \caption{Basic actor-partner interdependence model (APIM) depiction.}\label{fig:apim}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=400px]{2016_figure} \caption{Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads.}\label{fig:2016figure}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=400px]{SEMfigure} \caption{Path Analysis Model with Estimates}\label{fig:semfigure}
-\end{figure}
+\section{References}\label{references}
 
 \newpage
-
-\section{References}\label{references}
-
-\begin{verbatim}
-## [1] "R [Version 3.4.1; @R-base]"
-\end{verbatim}
 
@@
 
+\hypertarget{ref-garcia2015moderation}{}
+Garcia, R. L., Kenny, D. A., \& Ledermann, T. (2015). Moderation in the
+actor--partner interdependence model. \emph{Personal Relationships},
+\emph{22}(1), 8--29.
+
 \hypertarget{ref-R-purrr}{}
@@
 doi:\href{https://doi.org/10.1037/0022-3514.75.1.269}{10.1037/0022-3514.75.1.269}
+
+\hypertarget{ref-ledermann2017analyzing}{}
+Ledermann, T., \& Kenny, D. A. (2017). Analyzing dyadic data with
+multilevel modeling versus structural equation modeling: A tale of two
+methods. \emph{Journal of Family Psychology}, \emph{31}(4), 442.
 
@@
 doi:\href{https://doi.org/10.1177/1069072707301211}{10.1177/1069072707301211}
-
-\hypertarget{ref-peugh2013analyzing}{}
-Peugh, J. L., DiLillo, D., \& Panuzio, J. (2013). Analyzing mixed-dyadic
-data using structural equation models. \emph{Structural Equation
-Modeling: A Multidisciplinary Journal}, \emph{20}(2), 314--337.
 

### 2020-07-06 Final_Manuscript.Rmd
Cleaned file i-o

--- 2020-06-29 Final_Manuscript.Rmd
@@
 ```{r data}
-clark_measures <- read.csv("Cleaned data/clark_measures.csv")
-smith <- read.csv("Cleaned data/smith.csv")
+clark_final <- read.csv("Cleaned data/clark_final.csv")
+smith_final <- read.csv("Cleaned data/smith_final.csv")
 clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
@@
 
-##Combining Samples
+##Combined Samples
 
@@
 Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US.
+The description of the samples section below contains more detail about equivalence analyses to support the decision to combine these two samples.
 
@@
 #Clark
-clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, 
+clark_extsoo_alpha <- psych::alpha(select(clark_final, otherint_1, otherint_2, 
                                           otherint_5, otherint_6, otherint_10))$total[2]
-clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, 
+clark_intsoo_alpha <- psych::alpha(select(clark_final, otherint_3, otherint_4, 
                                           otherint_7, otherint_8, otherint_9, otherint_11, 
@@
 #Smith
-smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, 
+smith_extsoo_alpha <- psych::alpha(select(smith_final, otherint_1, otherint_2, otherint_5, 
                                           otherint_6, otherint_10))$total[2]
-smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, 
+smith_intsoo_alpha <- psych::alpha(select(smith_final, otherint_3, otherint_4, otherint_7, 
                                           otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
@@
 #Clark
-clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, 
+clark_intauth_alpha <- psych::alpha(select(clark_final, inter_1, inter_3, inter_5, 
                                            inter_6, inter_7, inter_9, inter_10, interaux_5, 
@@
 #Smith
-smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, 
+smith_intauth_alpha <- psych::alpha(select(smith_final, inter_1, inter_3, inter_5, inter_6, 
                                            inter_7, inter_9, inter_10, interaux_5, 
@@
 #Clark - two items
-clark_howbody_alpha<- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
+clark_howbody_alpha<- psych::alpha(select(clark_final, howbody_1, howbody_2))$total[2]
 #Smith - two items
-smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]
+smith_howbody_alpha <- psych::alpha(select(smith_final,  howbody_1, howbody_2))$total[2]
 #Clark - three items
-clark_howbody3 <- psych::alpha(select(clark_measures, howbody_1, howbody_2, howbody_3))
+clark_howbody3 <- psych::alpha(select(clark_final, howbody_1, howbody_2, howbody_3))
 #Smith - three items
-smith_howbody3 <- psych::alpha(select(smith, howbody_1, howbody_2, howbody_3))
+smith_howbody3 <- psych::alpha(select(smith_final, howbody_1, howbody_2, howbody_3))
 ```
@@
 #Clark
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
+clark_relag_alpha <- psych::alpha(select(clark_final, relag_1, relag_2, relag_3, 
                                          relag_4, relag_5, relag_6, relag_7, relag_8, 
@@
 #Smith
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
+smith_relag_alpha <- psych::alpha(select(smith_final, relag_1, relag_2, relag_3, relag_4, 
                                          relag_5, relag_6, relag_7, relag_8, 
@@
 
-#corr.test(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
-#corr.test(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+#corr.test(select(clark_final, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+#corr.test(select(smith_final, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
 ##DROPPING ITEM 9
-clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
+clark_relag_alpha <- psych::alpha(select(clark_final, relag_1, relag_2, relag_3, 
                                          relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]
 
-smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
+smith_relag_alpha <- psych::alpha(select(smith_final, relag_1, relag_2, relag_3, relag_4, 
                                          relag_5, relag_6, relag_7, relag_8))$total[2]
@@
 #Clark
-clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
+clark_final <- clark_final %>% #reverse code certain career aspiration variables
   mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
@@
 
-clark_careerasp_alpha <- psych::alpha(select(clark_measures, careerasp_1, careerasp_2, 
+clark_careerasp_alpha <- psych::alpha(select(clark_final, careerasp_1, careerasp_2, 
                                              careerasp_3, careerasp4.r, careerasp_5, 
@@
 #Smith
-smith <- smith %>% #reverse code certain career aspiration variables
+smith_final <- smith_final %>% #reverse code certain career aspiration variables
   mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
@@
 
-smith_careerasp_alpha <- psych::alpha(select(smith, careerasp_1, careerasp_2, 
+smith_careerasp_alpha <- psych::alpha(select(smith_final, careerasp_1, careerasp_2, 
                                              careerasp_3, careerasp4.r, careerasp_5, 
@@
 #Clark--external and internal
-clark_funcTSO_alpha <- psych::alpha(select(clark_measures, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
-clark_physTSO_alpha <- psych::alpha(select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
+clark_funcTSO_alpha <- psych::alpha(select(clark_final, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
+clark_physTSO_alpha <- psych::alpha(select(clark_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
 
 #Smith--external and internal
-smith_funcTSO_alpha <- psych::alpha(select(smith, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
-smith_physTSO_alpha <- psych::alpha(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
+smith_funcTSO_alpha <- psych::alpha(select(smith_final, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
+smith_physTSO_alpha <- psych::alpha(select(smith_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
 ```
@@
 Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.
+
+###Description of the Samples
+Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
+More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college.
+Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
+Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
+Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
+For consistency, we limited participant data to same sex female pairs at the two colleges.
+
+```{r}
+##Correlations
+round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Smith"), 
+                 a2pSOO_A, a2pSOO_P, TSO_A,
+                 howbody_avg_A,
+                 authenticity_A, 
+                 trigram_score_A, careerasp_A, relag_A))$r, 3)
+
+round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Clark"), 
+                 a2pSOO_A, a2pSOO_P, TSO_A, 
+                 howbody_avg_A,
+                 authenticity_A, 
+                 trigram_score_A, careerasp_A, relag_A))$r, 3)
+```
+
+There were some similar correaltions bewtween study variables across samples.
+
+Due these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
+These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
+The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
+There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
+The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
+`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
 
@@
 
-tally(~gender, data=clark_measures)
-tally(~gender, data=smith)
+tally(~gender, data=clark_final)
+tally(~gender, data=smith_final)
 ```
-
-###Description of the Samples
-Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
-More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college.
-Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
-Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
-Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
-Due to similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
-For consistency, we limited participant data to same sex female pairs at the two colleges.
-These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
-The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
-There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
-The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
-`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
 
@@
 ```
-
 ## Data analysis
@@
 
-```{r}
-# #Filtering for just one partnum and creating TSO * objectification interaction
-# dyad_cswomen <- clarksmith_women %>%
-#   mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
-#          TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
-#   filter(partnum_A==1)
-# 
-# 
-# model <- '#####regressions 
-# howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P + c*TSO_A_SOO_P
-# authenticity_A ~ d*howbody_avg_A
-# howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A + c*TSO_P_SOO_A
-# authenticity_P ~ d*howbody_avg_P
-# trigram_score_A ~ e1*authenticity_A
-# careerasp_A ~ e2*authenticity_A
-# relag_A ~ e3*authenticity_A
-# trigram_score_P ~ e1*authenticity_P
-# careerasp_P ~ e2*authenticity_P
-# relag_P ~ e3*authenticity_P
-# ######covariances
-# #endogenous
-# howbody_avg_A ~~ howbody_avg_P
-# authenticity_A ~~ authenticity_P
-# trigram_score_A ~~ trigram_score_P
-# careerasp_A ~~ careerasp_P
-# relag_A ~~ relag_P
-# trigram_score_A ~~ 0*careerasp_A
-# trigram_score_A ~~ 0*relag_A
-# trigram_score_A ~~ 0*careerasp_P
-# trigram_score_A ~~ 0*relag_P
-# careerasp_A ~~ 0*relag_A
-# careerasp_A ~~ 0*trigram_score_P
-# careerasp_A ~~ 0*relag_P
-# relag_A ~~ 0*trigram_score_P
-# relag_A ~~ 0*careerasp_P
-# trigram_score_P ~~ 0*careerasp_P
-# trigram_score_P ~~ 0*relag_P
-# careerasp_P ~~ 0*relag_P
-# #####variances
-# howbody_avg_A ~~ v1*howbody_avg_A
-# howbody_avg_P ~~ v1*howbody_avg_P
-# TSO_A ~~ v2*TSO_A
-# TSO_P ~~ v2*TSO_P
-# a2pSOO_A ~~ v3*a2pSOO_A
-# a2pSOO_P ~~ v3*a2pSOO_P
-# authenticity_A ~~ v4*authenticity_A
-# authenticity_P ~~ v4*authenticity_P
-# ##endogenous intercepts
-# howbody_avg_A ~ i*1
-# howbody_avg_P ~ i*1
-# authenticity_A ~ i2*1
-# authenticity_P ~ i2*1
-# trigram_score_A ~ i3*1
-# trigram_score_P ~ i4*1
-# careerasp_A ~ i5*1
-# careerasp_P ~ i5*1
-# relag_A ~ i6*1
-# relag_P ~ i6*1
-# ##exogenous means
-# TSO_A ~ m*1
-# TSO_P ~ m*1
-# a2pSOO_A ~ m2*1
-# a2pSOO_P ~ m2*1
-# TSO_P_SOO_A ~ m3*1
-# TSO_A_SOO_P ~ m3*1
-# ## exogenous covariances
-# TSO_A_SOO_P ~~ c1*TSO_A
-# TSO_P_SOO_A ~~ c1*TSO_P
-# TSO_A_SOO_P ~~ c2*a2pSOO_P
-# TSO_P_SOO_A ~~ c2*a2pSOO_A
-# TSO_A ~~ c3*a2pSOO_P
-# TSO_P ~~ c3*a2pSOO_A
-# TSO_A ~~ c4*a2pSOO_A
-# TSO_P ~~ c4*a2pSOO_P
-# TSO_A_SOO_P ~~ c5*a2pSOO_A
-# TSO_P_SOO_A ~~ c5*a2pSOO_P
-# TSO_A_SOO_P ~~ c6*TSO_P
-# TSO_P_SOO_A ~~ c6*TSO_A
-# '
-# 
-# isatmodel <- '#####regressions 
-# #Part one/two
-# howbody_avg_A ~~ t*TSO_A
-# howbody_avg_A ~~ a*a2pSOO_A
-# howbody_avg_A ~~ b*a2pSOO_P 
-# howbody_avg_A ~~ c*TSO_A_SOO_P
-# 
-# howbody_avg_P ~~ t*TSO_P
-# howbody_avg_P ~~ a*a2pSOO_P 
-# howbody_avg_P ~~ b*a2pSOO_A 
-# howbody_avg_P ~~ c*TSO_P_SOO_A
-# 
-# TSO_A ~~ f*howbody_avg_P
-# TSO_P ~~ f*howbody_avg_A
-# TSO_A_SOO_P ~~ g*howbody_avg_P
-# TSO_P_SOO_A ~~ g*howbody_avg_A
-# 
-# #Part two/three
-# authenticity_A ~~ d*howbody_avg_A
-# authenticity_P ~~ d*howbody_avg_P
-# howbody_avg_A ~~ h*authenticity_P
-# howbody_avg_P ~~ h*authenticity_A
-# 
-# 
-# #Part three/four
-# trigram_score_A ~~ e1*authenticity_A
-# trigram_score_P ~~ e1*authenticity_P
-# careerasp_A ~~ e2*authenticity_A
-# careerasp_P ~~ e2*authenticity_P
-# relag_A ~~ e3*authenticity_A
-# relag_P ~~ e3*authenticity_P
-# trigram_score_A ~~ e4*relag_P
-# trigram_score_P ~~ e4*relag_A
-# trigram_score_A ~~ e5*careerasp_P
-# trigram_score_P ~~ e5*careerasp_A
-# trigram_score_A ~~ e6*trigram_score_P
-# #trigram_score_P ~~ e6*trigram_score_A
-# careerasp_A ~~ e7*relag_P
-# careerasp_P ~~ e7*relag_A
-# careerasp_A ~~ e8*careerasp_P
-# #careerasp_A ~~ e9*trigram_score_P
-# #careerasp_P ~~ e9*trigram_score_A
-# relag_A ~~ e10*relag_P
-# 
-# #One to three
-# #direct actor effects
-# authenticity_A ~~ k1*TSO_A_SOO_P
-# authenticity_P ~~ k1*TSO_P_SOO_A
-# authenticity_A ~~ k2*TSO_A
-# authenticity_P ~~ k2*TSO_P
-# authenticity_A ~~k3*a2pSOO_A
-# authenticity_P ~~k3*a2pSOO_P
-# 
-# #direct partner effects
-# authenticity_A ~~ k4*TSO_P_SOO_A
-# authenticity_P ~~k4*TSO_A_SOO_P
-# authenticity_A ~~ k5*TSO_P
-# authenticity_P ~~ k5*TSO_A
-# authenticity_A ~~ k6*a2pSOO_P
-# authenticity_P ~~ k6*a2pSOO_A
-# 
-# #One to four
-# #Direct actor effects
-# trigram_score_A ~~ l1*TSO_A_SOO_P
-# trigram_score_P ~~ l1*TSO_P_SOO_A
-# trigram_score_A ~~ l2*TSO_A
-# trigram_score_P ~~ l2*TSO_P
-# trigram_score_A ~~ l3*a2pSOO_A
-# trigram_score_P ~~ l3*a2pSOO_P
-# careerasp_A ~~ l4*TSO_A_SOO_P
-# careerasp_P ~~ l4*TSO_P_SOO_A
-# careerasp_A ~~ l5*TSO_A
-# careerasp_P ~~ l5*TSO_P
-# careerasp_A ~~ l6*a2pSOO_A
-# careerasp_P ~~ l6*a2pSOO_P
-# relag_A ~~ l7*TSO_A_SOO_P
-# relag_P ~~ l7*TSO_P_SOO_A
-# relag_A ~~ l8*TSO_A
-# relag_P ~~ l8*TSO_P
-# relag_A ~~ l9*a2pSOO_A
-# relag_P ~~ l9*a2pSOO_P
-# 
-# #direct partner effects
-# trigram_score_A ~~ m1*TSO_P_SOO_A
-# trigram_score_P ~~ m1*TSO_A_SOO_P
-# trigram_score_A ~~ m2*TSO_P
-# trigram_score_P ~~ m2*TSO_A
-# trigram_score_A ~~ m3*a2pSOO_P
-# trigram_score_P ~~ m3*a2pSOO_A
-# careerasp_A ~~ m4*TSO_P_SOO_A
-# careerasp_P ~~ m4*TSO_A_SOO_P
-# careerasp_A ~~ m5*TSO_P
-# careerasp_P ~~ m5*TSO_A
-# careerasp_A ~~ m6*a2pSOO_P
-# careerasp_P ~~ m6*a2pSOO_A
-# relag_A ~~ m7*TSO_P_SOO_A
-# relag_P ~~ m7*TSO_A_SOO_P
-# relag_A ~~ m8*TSO_P
-# relag_P ~~ m8*TSO_A
-# relag_A ~~ m9*a2pSOO_P
-# relag_P ~~ m9*a2pSOO_A
-# 
-# #Two to four
-# #direct actor effects
-# trigram_score_A ~~ o1*howbody_avg_A
-# trigram_score_P ~~ o1*howbody_avg_P
-# careerasp_A ~~ o2*howbody_avg_A
-# careerasp_P ~~ o2*howbody_avg_P
-# relag_A ~~ o3*howbody_avg_A
-# relag_P ~~ o3*howbody_avg_P
-# 
-# #direct partner effects
-# trigram_score_A ~~ o1*howbody_avg_P
-# trigram_score_P ~~ o1*howbody_avg_A
-# careerasp_A ~~ o2*howbody_avg_P
-# careerasp_P ~~ o2*howbody_avg_A
-# relag_A ~~ o3*howbody_avg_P
-# relag_P ~~ o3*howbody_avg_A
-# 
-# 
-# ######covariances
-# #endogenous
-# howbody_avg_A ~~ howbody_avg_P
-# authenticity_A ~~ authenticity_P
-# #trigram_score_A ~~ trigram_score_P
-# #careerasp_A ~~ careerasp_P
-# #relag_A ~~ relag_P
-# trigram_score_A ~~ q1*careerasp_A 
-# trigram_score_A ~~ q2*relag_A
-# 
-# careerasp_A ~~ q3*relag_A
-# 
-# trigram_score_P ~~ q1*careerasp_P
-# trigram_score_P ~~ q2*relag_P
-# 
-# careerasp_P ~~ q3*relag_P
-# 
-# trigram_score_A ~~ q4*careerasp_P
-# trigram_score_A ~~ q5*relag_P
-# 
-# 
-# trigram_score_P ~~ q4*careerasp_A
-# trigram_score_P ~~ q5*relag_A
-# 
-# careerasp_A ~~ q6*relag_P
-# careerasp_P ~~ q6*relag_A
-# 
-# 
-# #####variances
-# howbody_avg_A ~~ v1*howbody_avg_A
-# howbody_avg_P ~~ v1*howbody_avg_P
-# TSO_A ~~ v2*TSO_A
-# TSO_P ~~ v2*TSO_P
-# a2pSOO_A ~~ v3*a2pSOO_A
-# a2pSOO_P ~~ v3*a2pSOO_P
-# authenticity_A ~~ v4*authenticity_A
-# authenticity_P ~~ v4*authenticity_P
-# ##endogenous intercepts
-# howbody_avg_A ~ i*1
-# howbody_avg_P ~ i*1
-# authenticity_A ~ i2*1
-# authenticity_P ~ i2*1
-# trigram_score_A ~ i3*1
-# trigram_score_P ~ i4*1
-# careerasp_A ~ i5*1
-# careerasp_P ~ i5*1
-# relag_A ~ i6*1
-# relag_P ~ i6*1
-# ##exogenous means
-# TSO_A ~ m*1
-# TSO_P ~ m*1
-# a2pSOO_A ~ m2*1
-# a2pSOO_P ~ m2*1
-# TSO_P_SOO_A ~ m3*1
-# TSO_A_SOO_P ~ m3*1
-# ## exogenous covariances
-# TSO_A_SOO_P ~~ c1*TSO_A
-# TSO_P_SOO_A ~~ c1*TSO_P
-# TSO_A_SOO_P ~~ c2*a2pSOO_P
-# TSO_P_SOO_A ~~ c2*a2pSOO_A
-# TSO_A ~~ c3*a2pSOO_P
-# TSO_P ~~ c3*a2pSOO_A
-# TSO_A ~~ c4*a2pSOO_A
-# TSO_P ~~ c4*a2pSOO_P
-# TSO_A_SOO_P ~~ c5*a2pSOO_A
-# TSO_P_SOO_A ~~ c5*a2pSOO_P
-# TSO_A_SOO_P ~~ c6*TSO_P
-# TSO_P_SOO_A ~~ c6*TSO_A
-# '
-# 
-# 
-# 
-# fit <- sem(model, data=dyad_cswomen)
-# ```
-# 
-# ```{r sem, include=TRUE, results='asis'}
-# fit_table <- xtable(parameterEstimates(fit))
-# 
-# fit_table <- fit_table %>%
-#   filter(op=="~") %>%
-#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
-#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
-#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
-#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
-#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
-#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
-#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
-#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
-#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
-#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
-#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
-#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
-#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
-#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
-#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
-#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
-#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
-#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
-#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
-#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
-#   select(lhs, op, rhs, est, se, z, pvalue) %>%
-#   #taking out partner-partner estimates
-#   slice(1:5,11:13)
-# 
-# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
-# 
-# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
-# ```
-# 
-# ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
-# include_graphics("SEMfigure.png")
-# ```
-```
+### Combining Samples
+
+The correaltions between study variables is similar across samples.
+The realibialities for the study scales were also equivalent.
+(Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS.
 

### 2020-07-06 Final_Manuscript.tex
Cleaned file i-o

@@
 arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
-women's liberal arts college in the northeast US.
+women's liberal arts college in the northeast US. The results section
+contains more detail about equivalence analyses to support the decision
+to combine these two samples.
 
@@
 
+Before moving to the main analyses, we discuss statistical equivalence
+test that provide support for combining Sample 1 and Sample 2 in one
+analysis sample. The online supplemental material contains the main
+analyses separated by samples.
+
+\subsubsection{Combining Samples}\label{combining-samples-1}
+
+The correaltions between study variables is similar across samples. The
+realibialities for the study scales were also equivalent. (Note that the
+two samples were two small to conduct formal measurement equivalence
+tests for scales.) There are no statistically significant differences
+between samples in demographics including age, STATS, and ethnicity,
+STATS.
+
 \begin{figure}
@@
 relationship agency, \emph{b} = -0.07, \emph{SE} = 0.1, \emph{p} = .474.
+
+The results were similar for analyses conducted on Sample 1 and Sample 2
+individually. See the online supplemental material for more detail on
+these analyses.
 

### 2020-07-06 Variable creation.Rmd
Cleaned file i-o

@@
 library(tidyr)
+library(irr)
 library(dplyr)
-library(irr)
-select <- dplyr::select
 ```
 
-Load data
+#Load data
 ```{r}
@@
 
-Clark Scale Scores--creating scale scores for the Clark data.
+#Scale Scores
+
+Creating scale scores for the Clark data.
+
 ```{r}
 #SOO -- subtract internal SOO from external SOO
-clark_measures$extSOO <- rowMeans(dplyr::select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE) #get average
+clark_measures$extSOO <- rowMeans(select(clark_measures, otherint_1, otherint_2, 
+                                         otherint_5, otherint_6, otherint_10), na.rm=TRUE) #get average
 
-clark_measures$intSOO <- rowMeans(dplyr::select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE) #get average
+clark_measures$intSOO <- rowMeans(select(clark_measures, otherint_3, otherint_4, 
+                                         otherint_7, otherint_8, otherint_9, 
+                                         otherint_11, otherint_12), na.rm=TRUE) #get average
 
@@
 #Meta SOO--subtract internal from external
-clark_measures$extmetaSOO <- rowMeans(dplyr::select(clark_measures, metaint_1, metaint_2, metaint_5, metaint_6, metaint_10), na.rm=TRUE)
+clark_measures$extmetaSOO <- rowMeans(select(clark_measures, metaint_1, metaint_2, 
+                                             metaint_5, metaint_6, metaint_10), na.rm=TRUE)
 
-clark_measures$intmetaSOO <- rowMeans(dplyr::select(clark_measures, metaint_3, metaint_4, metaint_7, metaint_8, metaint_9, metaint_11, metaint_12), na.rm=TRUE)
+clark_measures$intmetaSOO <- rowMeans(select(clark_measures, metaint_3, metaint_4, 
+                                             metaint_7, metaint_8, metaint_9, 
+                                             metaint_11, metaint_12), na.rm=TRUE)
 
@@
 #Interaction Authenticity
-clark_measures$authenticity <- rowMeans(dplyr::select(clark_measures, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))
+clark_measures$authenticity <- rowMeans(select(clark_measures, inter_1, inter_3, 
+                                               inter_5, inter_6, inter_7, inter_9, 
+                                               inter_10, interaux_5, interaux_6), na.rm=TRUE)
 
 #SSO--average of how body 1 and how body 2
-clark_measures <- clark_measures %>%
-  mutate(howbody_avg = (howbody_1+howbody_2)/2)
+clark_measures$howbody_avg <- rowMeans(select(clark_measures, howbody_1, howbody_2), na.rm=TRUE)
 
@@
 
-clark_measures$relag <- rowMeans(dplyr::select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+clark_measures$relag <- rowMeans(select(clark_measures, relag_1, relag_2, 
+                                        relag_3, relag_4, relag_5, relag_6, 
+                                        relag_7, relag_8, relag_9.r), na.rm=TRUE)
 
@@
 
-clark_measures$careerasp <- rowMeans(dplyr::select(clark_measures, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))
+clark_measures$careerasp <- rowMeans(select(clark_measures, careerasp_1, careerasp_2, 
+                                            careerasp_3, careerasp4.r, careerasp_5, 
+                                            careerasp_6, careerasp7.r, careerasp_8, 
+                                            careerasp_9, careerasp10.r), na.rm=TRUE)
 
 #TSO--subtract internal from external, multiply by -1
-clark_measures$funcTSO <- rowMeans(dplyr::select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9))
-clark_measures$physTSO <- rowMeans(dplyr::select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10))
+clark_measures$funcTSO <- rowMeans(select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9), na.rm=TRUE)
+clark_measures$physTSO <- rowMeans(select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10), na.rm=TRUE)
 
-clark_measures$TSO <- clark_measures$physTSO - clark_measures$funcTSO
-clark_measures$TSO <- clark_measures$TSO*(-1)
+clark_measures$TSO <- (clark_measures$physTSO - clark_measures$funcTSO)*(-1)
 ```
 
-SMITH SCALE SCORES
+Creating scale scores for the Smith data.
+
 ```{r}
@@
   arrange(dyadID) %>%
-  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) #filter out dyads with no data
+  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, 
+         dyadID!=999, dyadID!=999999, dyadID!=9999) #filter out dyads with no data
+```
 
+```{r}
 #SOO
-smith$extSOO <- rowMeans(dplyr::select(smith, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE)
+smith$extSOO <- rowMeans(select(smith, otherint_1, otherint_2, 
+                                otherint_5, otherint_6, otherint_10), na.rm=TRUE)
 
-smith$intSOO <- rowMeans(dplyr::select(smith, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE)
+smith$intSOO <- rowMeans(select(smith, otherint_3, otherint_4, 
+                                otherint_7, otherint_8, otherint_9, 
+                                otherint_11, otherint_12), na.rm=TRUE)
 
@@
 #Meta SOO
-smith$extmetaSOO <- rowMeans(dplyr::select(smith, metaint_1, metaint_2, metaint_5, metaint_6, metaint_10), na.rm=TRUE)
+smith$extmetaSOO <- rowMeans(select(smith, metaint_1, metaint_2, 
+                                    metaint_5, metaint_6, metaint_10), na.rm=TRUE)
 
-smith$intmetaSOO <- rowMeans(dplyr::select(smith, metaint_3, metaint_4, metaint_7, metaint_8, metaint_9, metaint_11, metaint_12), na.rm=TRUE)
+smith$intmetaSOO <- rowMeans(select(smith, metaint_3, metaint_4, 
+                                    metaint_7, metaint_8, metaint_9, 
+                                    metaint_11, metaint_12), na.rm=TRUE)
 
@@
 #Interaction Authenticity
-smith$authenticity <- rowMeans(dplyr::select(smith, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))
+smith$authenticity <- rowMeans(select(smith, inter_1, inter_3, inter_5, 
+                                      inter_6, inter_7, inter_9, inter_10, 
+                                      interaux_5, interaux_6), na.rm=TRUE)
 
 #SSO
-smith <- smith %>%
-  mutate(howbody_avg = (howbody_1+howbody_2)/2)
+smith$howbody_avg <- rowMeans(select(smith, howbody_1, howbody_2), na.rm=TRUE)
 
@@
 
-smith$relag <- rowMeans(dplyr::select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
+smith$relag <- rowMeans(select(smith, relag_1, relag_2, relag_3, 
+                               relag_4, relag_5, relag_6, relag_7, 
+                               relag_8, relag_9.r), na.rm=TRUE)
 
@@
 
-smith$careerasp <- rowMeans(dplyr::select(smith, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))
+smith$careerasp <- rowMeans(select(smith, careerasp_1, careerasp_2, 
+                                   careerasp_3, careerasp4.r, careerasp_5, 
+                                   careerasp_6, careerasp7.r, careerasp_8, 
+                                   careerasp_9, careerasp10.r), na.rm=TRUE)
 
 #TSO
-smith$funcTSO <- rowMeans(dplyr::select(smith,tso_1, tso_2, tso_4, tso_7, tso_9))
-smith$physTSO <- rowMeans(dplyr::select(smith, tso_3, tso_5, tso_6, tso_8, tso_10))
+smith$funcTSO <- rowMeans(select(smith,tso_1, tso_2, tso_4, tso_7, tso_9), na.rm=TRUE)
+smith$physTSO <- rowMeans(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), na.rm=TRUE)
 
-smith$TSO <- smith$physTSO-smith$funcTSO
-smith$TSO <- smith$TSO*-1
-
-#Write out csv with created variables
-write.csv(clark_measures, "Cleaned data/clark_measures.csv")
-write.csv(smith, "Cleaned data/smith.csv")
+smith$TSO <- (smith$physTSO - smith$funcTSO)*(-1)
 ```
 
-Trigrams
+Step not needed...processing continues
+```{r}
+#Write out csv with created variables
+#write.csv(clark_measures, "Cleaned data/clark_measures.csv")
+#write.csv(smith, "Cleaned data/smith.csv")
+```
+
+#Trigrams
+
+Clark
+
 ```{r}
@@
   summarise(trigram_score = sum(trigram_correct)) %>%
-  dplyr::select(partID, trigram_score)
+  select(partID, trigram_score)
 
@@
 
+Smith
+
 ```{r}
 ###SMITH
+
+#comented code here used only ONCE to grade trigrams...graded trigrams file is read in at the bottom of this chunk
+
 #select only trigram related variables
-smith_trigrams <- smith %>%
-  dplyr::select(partID, dyadID, rat1_1.0, rat2_1.0,rat3_1.0, rat4_1.0,rat5_1.0, rat6_1.0, rat7_1.0, rat8_1.0, rat9_1.0, rat10_1) %>%
-  arrange(dyadID, partID)
-
-smith_trigrams_long <- gather(smith_trigrams, trigram, response, rat1_1.0:rat10_1)
-
-#change trigram from generic name to the specific trigram
-smith_trigrams_long <- smith_trigrams_long %>%
-  mutate(trigram = ifelse(trigram=="rat1_1.0", "QUACK:POND:WADDLE",
-                          ifelse(trigram=="rat2_1.0", "ATHLETES:WEB:RABBIT",
-                                 ifelse(trigram=="rat3_1.0", "HONEY:SWARM:STING",
-                                        ifelse(trigram=="rat4_1.0", "MATCHES:SMOKE:BUSH",
-                                               ifelse(trigram=="rat5_1.0", "CHOCOLATE:FORTUNE:TIN",
-                                                      ifelse(trigram=="rat6_1.0", "CURIOSITY:NAP:WHISKERS",
-                                                             ifelse(trigram=="rat7_1.0", "STALK:TRAINER:KING",
-                                                                    ifelse(trigram=="rat8_1.0", "SURPRISE:LINE:BIRTHDAY",
-                                                                           ifelse(trigram=="rat9_1.0", "RED:GO:CAR", 
-                                                                                  ifelse(trigram=="rat10_1", "MOUSE : SHARP : BLUE", NA)))))))))))
-
-#create a correct response column
-smith_trigrams_long <- smith_trigrams_long %>%
-  mutate(correct_response=ifelse(trigram=="QUACK:POND:WADDLE", "Duck",
-                          ifelse(trigram=="ATHLETES:WEB:RABBIT", "Foot",
-                                 ifelse(trigram=="HONEY:SWARM:STING","Bee",
-                                        ifelse(trigram=="MATCHES:SMOKE:BUSH", "Fire", 
-                                               ifelse(trigram=="CHOCOLATE:FORTUNE:TIN", "Cookie",
-                                                      ifelse(trigram=="CURIOSITY:NAP:WHISKERS","Cat",
-                                                             ifelse(trigram=="STALK:TRAINER:KING","Lion",
-                                                                    ifelse(trigram=="SURPRISE:LINE:BIRTHDAY", "Party",
-                                                                           ifelse(trigram=="RED:GO:CAR", "Stop",
-                                                                                  ifelse(trigram=="MOUSE : SHARP : BLUE", "Cheese", NA))))))))))) %>%
-  arrange(partID, dyadID)
-
-smith_trigrams_long <- smith_trigrams_long[,c(1,2,3,5,4)]
+# smith_trigrams <- smith %>%
+#   select(partID, dyadID, rat1_1.0, rat2_1.0,rat3_1.0, rat4_1.0,
+#          rat5_1.0, rat6_1.0, rat7_1.0, rat8_1.0, rat9_1.0, rat10_1) %>%
+#   arrange(dyadID, partID)
+# 
+# smith_trigrams_long <- gather(smith_trigrams, trigram, response, rat1_1.0:rat10_1)
+# 
+# #change trigram from generic name to the specific trigram
+# smith_trigrams_long <- smith_trigrams_long %>%
+#   mutate(trigram = ifelse(trigram=="rat1_1.0", 
+#                           "QUACK:POND:WADDLE",
+#                           ifelse(trigram=="rat2_1.0", 
+#                                  "ATHLETES:WEB:RABBIT",
+#                                  ifelse(trigram=="rat3_1.0", 
+#                                         "HONEY:SWARM:STING",
+#                                         ifelse(trigram=="rat4_1.0", 
+#                                                "MATCHES:SMOKE:BUSH",
+#                                                ifelse(trigram=="rat5_1.0", 
+#                                                       "CHOCOLATE:FORTUNE:TIN",
+#                                                       ifelse(trigram=="rat6_1.0", 
+#                                                              "CURIOSITY:NAP:WHISKERS",
+#                                                              ifelse(trigram=="rat7_1.0", 
+#                                                                     "STALK:TRAINER:KING",
+#                                                                     ifelse(trigram=="rat8_1.0", 
+#                                                                            "SURPRISE:LINE:BIRTHDAY",
+#                                                                            ifelse(trigram=="rat9_1.0", 
+#                                                                                   "RED:GO:CAR", 
+#                                                                                   ifelse(trigram=="rat10_1", 
+#                                                                                          "MOUSE : SHARP : BLUE", 
+#                                                                                          NA)))))))))))
+# 
+# #create a correct response column
+# smith_trigrams_long <- smith_trigrams_long %>%
+#   mutate(correct_response=ifelse(trigram=="QUACK:POND:WADDLE", 
+#                                  "Duck",
+#                           ifelse(trigram=="ATHLETES:WEB:RABBIT", 
+#                                  "Foot",
+#                                  ifelse(trigram=="HONEY:SWARM:STING",
+#                                         "Bee",
+#                                         ifelse(trigram=="MATCHES:SMOKE:BUSH", 
+#                                                "Fire", 
+#                                                ifelse(trigram=="CHOCOLATE:FORTUNE:TIN", 
+#                                                       "Cookie",
+#                                                       ifelse(trigram=="CURIOSITY:NAP:WHISKERS",
+#                                                              "Cat",
+#                                                              ifelse(trigram=="STALK:TRAINER:KING",
+#                                                                     "Lion",
+#                                                                     ifelse(trigram=="SURPRISE:LINE:BIRTHDAY", 
+#                                                                            "Party",
+#                                                                            ifelse(trigram=="RED:GO:CAR", 
+#                                                                                   "Stop",
+#                                                                                   ifelse(trigram=="MOUSE : SHARP : BLUE", 
+#                                                                                          "Cheese", 
+#                                                                                          NA))))))))))) %>%
+#   arrange(partID, dyadID)
+# 
+# smith_trigrams_long <- smith_trigrams_long[,c(1,2,3,5,4)]
 
@@
   summarise(trigram_score=sum(final_correct))%>%
-  dplyr::select(partID, dyadID, trigram_score)
+  select(partID, dyadID, trigram_score)
 
@@
 
-sexist sentences
+#Sexist Sentences
+
+Clark
+
 ```{r}
@@
 
+Smith
+
 ```{r}
@@
 
+#comented code here used only ONCE to code sentences...graded trigrams file is read in at the bottom of this chunk
+
 #Creating sexist sentence file
-smith$dyadID <- as.numeric(smith$dyadID)
-smith$partID <- as.numeric(smith$partID)
-smith_sentences_long <- smith %>%
-  #remove dyads with no data
-  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) %>%
-  #select just sexism related variables
-  select(partID, dyadID, sexismpre_1:sexismpre_8) %>%
-  arrange(dyadID)
-
-#make data long
-smith_sentences_long <- gather(smith_sentences_long, sentence, target, sexismpre_1:sexismpre_8)
-
-#create a column with the actual sentence as well as a sentence number column
-smith_sentences_long <- smith_sentences_long %>%
-  mutate(stem=ifelse(sentence=="sexismpre_1", "Linda swatted at the flies", 
-                     ifelse(sentence=="sexismpre_2", "Helen crammed for the test",
-                            ifelse(sentence=="sexismpre_3", "Shirley asked for help getting home",
-                                   ifelse(sentence=="sexismpre_4", "Sam read the newspaper",
-                                          ifelse(sentence=="sexismpre_5", "Jenny went home to cook dinner",
-                                                 ifelse(sentence=="sexismpre_6", "Katherine baby-sat the neighbor's kids",
-                                                        ifelse(sentence=="sexismpre_7", "Tom bottle fed the baby",
-                                                               ifelse(sentence=="sexismpre_8", "Bert changed the oil", NA))))))))) %>%
-    mutate(sentence=ifelse(sentence=="sexismpre_1", 1, 
-                     ifelse(sentence=="sexismpre_2", 2,
-                            ifelse(sentence=="sexismpre_3", 3,
-                                   ifelse(sentence=="sexismpre_4", 4,
-                                          ifelse(sentence=="sexismpre_5", 5,
-                                                 ifelse(sentence=="sexismpre_6", 6,
-                                                        ifelse(sentence=="sexismpre_7", 7,
-                                                               ifelse(sentence=="sexismpre_8", 8, NA)))))))))
-
-#change order of sentences
-smith_sentences_long <- smith_sentences_long[,c(1,2,3,5,4)]
-
-#remove rows with no target data
-smith_sentences_long <- smith_sentences_long %>%
-  filter(target!="") %>%
-  arrange(dyadID, partID)
+# smith$dyadID <- as.numeric(smith$dyadID)
+# smith$partID <- as.numeric(smith$partID)
+# smith_sentences_long <- smith %>%
+#   #remove dyads with no data
+#   filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) %>%
+#   #select just sexism related variables
+#   select(partID, dyadID, sexismpre_1:sexismpre_8) %>%
+#   arrange(dyadID)
+# 
+# #make data long
+# smith_sentences_long <- gather(smith_sentences_long, sentence, target, sexismpre_1:sexismpre_8)
+# 
+# #create a column with the actual sentence as well as a sentence number column
+# smith_sentences_long <- smith_sentences_long %>%
+#   mutate(stem=ifelse(sentence=="sexismpre_1", 
+#                      "Linda swatted at the flies", 
+#                      ifelse(sentence=="sexismpre_2", 
+#                             "Helen crammed for the test",
+#                             ifelse(sentence=="sexismpre_3", 
+#                                    "Shirley asked for help getting home",
+#                                    ifelse(sentence=="sexismpre_4", 
+#                                           "Sam read the newspaper",
+#                                           ifelse(sentence=="sexismpre_5", 
+#                                                  "Jenny went home to cook dinner",
+#                                                  ifelse(sentence=="sexismpre_6", 
+#                                                         "Katherine baby-sat the neighbor's kids",
+#                                                         ifelse(sentence=="sexismpre_7", 
+#                                                                "Tom bottle fed the baby",
+#                                                                ifelse(sentence=="sexismpre_8", 
+#                                                                       "Bert changed the oil", NA))))))))) %>%
+#     mutate(sentence=ifelse(sentence=="sexismpre_1", 1, 
+#                      ifelse(sentence=="sexismpre_2", 2,
+#                             ifelse(sentence=="sexismpre_3", 3,
+#                                    ifelse(sentence=="sexismpre_4", 4,
+#                                           ifelse(sentence=="sexismpre_5", 5,
+#                                                  ifelse(sentence=="sexismpre_6", 6,
+#                                                         ifelse(sentence=="sexismpre_7", 7,
+#                                                                ifelse(sentence=="sexismpre_8", 8, NA)))))))))
+# 
+# #change order of sentences
+# smith_sentences_long <- smith_sentences_long[,c(1,2,3,5,4)]
+# 
+# #remove rows with no target data
+# smith_sentences_long <- smith_sentences_long %>%
+#   filter(target!="") %>%
+#   arrange(dyadID, partID)
 
@@
 kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")
-
 xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")

### 2020-07-06 Final_Manuscript.Rmd
added correlations with auth items

@@
 
+##Combined Samples
+
 ```{r data}
@@
 ```
-
-##Combined Samples
 
@@
 The description of the samples section below contains more detail about equivalence analyses to support the decision to combine these two samples.
+
+##Post interaction Measures
 
@@
 
-##Post interaction Measures
 The following measures were collected in the order they are presented following the interaction.
@@
 
+###Cognitive Performance
 ```{r trigram}
@@
 
-###Cognitive Performance
 Trigrams from the Remote Associates Task [@mcfarlin1984remote] were utilized to assess cognitive performance after the interaction.
@@
 
+###State Other-Objectification
 ```{r alpha_SOO}
@@
 ```
-
-###State Other-Objectification
 To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner @garcia2016objectification.
@@
 
+###Interaction Authenticity
 ```{r alpha_intauth}
@@
 ```
-
-###Interaction Authenticity
 To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike [@garcia2016objectification].
@@
 
+###State Self-Objectification
 ```{r alpha_SSO}
@@
 ```
-
-###State Self-Objectification
 To assess state self-objectification, we used an average of two items from @saguyetal2010 that were also used in @garcia2016objectification.
@@
 
+###Relationship Agency
 ```{r alpha_relagen}
@@
 ```
-
-###Relationship Agency
 A scale was used from @garcia2016objectification to assess how much agency an individual believes they would possess in future romantic relationships.
@@
 
+###Career Aspirations
 ```{r alpha_career}
@@
 ```
-
-###Career Aspirations
 To conceptualize participants’ career aspirations after the interaction, we used the 10-item adaptation of @grayobrien2007’s Career Aspiration Scale employed in @garcia2016objectification, which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
@@
 
+###Trait Self-Objectification
 ```{r alpha_TSO}
@@
 ```
-
-###Trait Self-Objectification
 Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
@@
 For consistency, we limited participant data to same sex female pairs at the two colleges.
-
-```{r}
-##Correlations
-round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Smith"), 
-                 a2pSOO_A, a2pSOO_P, TSO_A,
-                 howbody_avg_A,
-                 authenticity_A, 
-                 trigram_score_A, careerasp_A, relag_A))$r, 3)
-
-round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Clark"), 
-                 a2pSOO_A, a2pSOO_P, TSO_A, 
-                 howbody_avg_A,
-                 authenticity_A, 
-                 trigram_score_A, careerasp_A, relag_A))$r, 3)
-```
-
-There were some similar correaltions bewtween study variables across samples.
-
-Due these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
-These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
-The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
-There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
-The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
-`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
 
@@
 
+Due these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
+These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
+The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
+There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
+The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
+`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
+
 # Results
+## Data analysis
 ```{r create_r-references, warning=FALSE, message=FALSE}
@@
 ```
-## Data analysis
 We used `r cite_r("r-references.bib")` for all our analyses.
 
+## Analysis Strategy
 ```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
@@
 ```
-
-## Analysis Strategy
 This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
@@
 ### Combining Samples
+```{r}
+##Correlations
+round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Smith"), 
+                 a2pSOO_A, a2pSOO_P, TSO_A,
+                 howbody_avg_A,
+                 authenticity_A, 
+                 trigram_score_A, careerasp_A, relag_A))$r, 3)
 
+round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Clark"), 
+                 a2pSOO_A, a2pSOO_P, TSO_A, 
+                 howbody_avg_A,
+                 authenticity_A, 
+                 trigram_score_A, careerasp_A, relag_A))$r, 3)
+```
 The correaltions between study variables is similar across samples.
@@
 (Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS.
+
+##Main Results
+```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
+include_graphics("SEMfigure.png")
+```
+
+```{r mlm, include=TRUE, results='asis'}
+# fit_table <- xtable(parameterEstimates(fit))
+# 
+# fit_table <- fit_table %>%
+#   filter(op=="~") %>%
+#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
+#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
+#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
+#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
+#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
+#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
+#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
+#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
+#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
+#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
+#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
+#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
+#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
+#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
+#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
+#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
+#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
+#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
+#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
+#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
+#   select(lhs, op, rhs, est, se, z, pvalue) %>%
+#   #taking out partner-partner estimates
+#   slice(1:5,11:13)
+# 
+# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
+# 
+# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
+```
+
+```{r presentation-functions}
+ pround <- function(val){
+  ifelse(val < .001,
+         return(sub("^(-?)0.", "\\1.", sprintf("%.3f", .001))),
+         return(sub("^(-?)0.", "\\1.", sprintf("%.3f", val))))
+}
+
+estround <- function(val){
+  ifelse(abs(val) < .01,
+         return(.01),
+         return(round(val, 2)))
+}
+
+#only works for merModlmerTest objects or when p-values on are in column 4, "lm" objects
+report_stats <- function(mod, est){
+
+  b <- coef(summary(mod))[,1]
+  se <- coef(summary(mod))[,2]
+  ifelse(class(mod) == "merModLmerTest",
+         p <- coef(summary(mod))[,5],
+         p <- coef(summary(mod))[,4])
+
+  paste(ifelse(abs(b[est]) < .01,"*b* < ","*b* = "), as.character(estround(b[est])),
+        ifelse(se[est] < .01, ", *SE* < ", ", *SE* = "), as.character(estround(se[est])),
+        ifelse(p[est] < .001, ", *p* < ", ", *p* = "),  as.character(pround(p[est])),
+        sep = "") %>%
+    return()
+}
+# randomeffects <- as.data.frame(VarCorr(mlm_mod1.0))
+# randomeffects2 <- as.data.frame(VarCorr(mlm_mod2.0))
+```
+
+All model estimates and p-values are found in Table\ \@ref(tab:mlm) and the relationships with estimates included are depicted in Figure\ \@ref(fig:semfigure).
 
@@
 ```
+The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
+As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically signficant, `r report_stats(apim1, 3)`, replicating @garcia2016objectification's fiding.
+One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
+Contrary to past finding however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
+There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.
 
@@
 
-#Trying to perform analyses for each item for a footnote...will need to get to the bottom of this. 
-# inter_1, inter_3, inter_5, inter_6, 
-# inter_7, inter_9, inter_10, interaux_5, 
-# interaux_6
-# 
-# apim2 <- gls(inter_1 ~ howbody_avg_A, 
-#                  na.action=na.omit, 
-#                  correlation=corCompSymm (form=~1|dyadID),
-#                  data=clarksmith_women)
+#correlations between howbody and each authenticity item individually. 
+min_corr <- min(abs(round(corr.test(select(clarksmith_women, 
+                 howbody_avg_A, inter_1_A, inter_3_A, inter_5_A, 
+                 inter_6_A, inter_7_A, inter_9_A, inter_10_A, 
+                 interaux_5_A, interaux_6_A))$r, 3)[,1]))
+max_corr <- as.numeric(sort(abs(round(corr.test(select(clarksmith_women, 
+                 howbody_avg_A, inter_1_A, inter_3_A, inter_5_A, 
+                 inter_6_A, inter_7_A, inter_9_A, inter_10_A, 
+                 interaux_5_A, interaux_6_A))$r, 3)[,1]), decreasing = T)[2])
 
@@
 ```
+Contrary to expectations, there was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
+Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also estimated the pairwise correlations bewteen SSO and all these items individually.
+They were all small, ranging from only `r -1*min_corr` to `r -1*max_corr`.
+Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship bewteen SSO and authencity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, `r report_stats(apim2.b, 3)` (nor was the total effect of partner's other objectification on authenticity, `r report_stats(apim2.c, 2)`).
 
@@
 ```
-
-```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
-include_graphics("SEMfigure.png")
-```
-
-```{r mlm, include=TRUE, results='asis'}
-# fit_table <- xtable(parameterEstimates(fit))
-# 
-# fit_table <- fit_table %>%
-#   filter(op=="~") %>%
-#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
-#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
-#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
-#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
-#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
-#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
-#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
-#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
-#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
-#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
-#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
-#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
-#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
-#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
-#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
-#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
-#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
-#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
-#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
-#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
-#   select(lhs, op, rhs, est, se, z, pvalue) %>%
-#   #taking out partner-partner estimates
-#   slice(1:5,11:13)
-# 
-# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
-# 
-# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
-```
-
-```{r presentation-functions}
- pround <- function(val){
-  ifelse(val < .001,
-         return(sub("^(-?)0.", "\\1.", sprintf("%.3f", .001))),
-         return(sub("^(-?)0.", "\\1.", sprintf("%.3f", val))))
-}
-
-estround <- function(val){
-  ifelse(abs(val) < .01,
-         return(.01),
-         return(round(val, 2)))
-}
-
-#only works for merModlmerTest objects or when p-values on are in column 4, "lm" objects
-report_stats <- function(mod, est){
-
-  b <- coef(summary(mod))[,1]
-  se <- coef(summary(mod))[,2]
-  ifelse(class(mod) == "merModLmerTest",
-         p <- coef(summary(mod))[,5],
-         p <- coef(summary(mod))[,4])
-
-  paste(ifelse(abs(b[est]) < .01,"*b* < ","*b* = "), as.character(estround(b[est])),
-        ifelse(se[est] < .01, ", *SE* < ", ", *SE* = "), as.character(estround(se[est])),
-        ifelse(p[est] < .001, ", *p* < ", ", *p* = "),  as.character(pround(p[est])),
-        sep = "") %>%
-    return()
-}
-
-report_stats(apim1, 2)
-
-# randomeffects <- as.data.frame(VarCorr(mlm_mod1.0))
-# randomeffects2 <- as.data.frame(VarCorr(mlm_mod2.0))
-```
-
-##Main Results
-All model estimates and p-values are found in Table\ \@ref(tab:mlm) and the relationships with estimates included are depicted in Figure\ \@ref(fig:semfigure).
-
-The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
-As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically signficant, `r report_stats(apim1, 3)`, replicating @garcia2016objectification's fiding.
-One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
-Contrary to past finding however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
-There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.
-
-Contrary to expectations, there was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
-Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also tested the effect of SSO on these items individually...ADD ANALYSIS...Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship bewteen SSO and authencity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, `r report_stats(apim2.b, 3)` (nor was the total effect of partner's other objectification on authenticity, `r report_stats(apim2.c, 2)`).
-
 Lastly, althought there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performace, career aspirations, and relationship agency, as it did in @garcia2016objectification.

### 2020-07-06 Final_Manuscript.tex
added correlations with auth items

@@
 
-\subsection{Combining Samples}\label{combining-samples}
+\subsection{Combined Samples}\label{combined-samples}
 
@@
 arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
-women's liberal arts college in the northeast US. The results section
-contains more detail about equivalence analyses to support the decision
-to combine these two samples.
+women's liberal arts college in the northeast US. The description of the
+samples section below contains more detail about equivalence analyses to
+support the decision to combine these two samples.
 
@@
 made up of forty-three women and one man, as well as two participants
-who did not identify with either gender category, formed Sample 2. Due
-to similarities across samples in regard to correlation patterns between
-significant variables within this study, the two datasets were combined.
-For consistency, we limited participant data to same sex female pairs at
-the two colleges. These participants were mostly first-year college
-students, with an average age of 18.85 (SD = 1.04). The sample was
-48.44\% White/European American, 9.38\% Black/African-American, 28.12\%
+who did not identify with either gender category, formed Sample 2. For
+consistency, we limited participant data to same sex female pairs at the
+two colleges.
+
+There were some similar correaltions bewtween study variables across
+samples.
+
+Due these similarities across samples in regard to correlation patterns
+between significant variables within this study, the two datasets were
+combined. These participants were mostly first-year college students,
+with an average age of 18.85 (SD = 1.04). The sample was 48.44\%
+White/European American, 9.38\% Black/African-American, 28.12\%
 Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
@@
 
-\subsubsection{Combining Samples}\label{combining-samples-1}
+\subsubsection{Combining Samples}\label{combining-samples}
 

### 2020-07-09 Final_Manuscript.Rmd
small changes closing github issues

@@
 The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation paterns.
+The online supplementary materials contains analysis using SEM.
 See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.
@@
 The online supplemental material contains the main analyses separated by samples.
+All results presented below are from models including sample as a control variable.
 
@@
 #SSO
-apim1 <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + a2pSOO_P*TSO_A, 
+apim1 <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + a2pSOO_P*TSO_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim1.b <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A, 
+apim1.b <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 summary(apim1)
+summary(apim1.b)
 ```
@@
 #authenticity
-apim2 <- gls(authenticity_A ~ howbody_avg_A, 
+apim2 <- gls(authenticity_A ~ howbody_avg_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim2.b <- gls(authenticity_A ~ howbody_avg_A + a2pSOO_P, 
+apim2.b <- gls(authenticity_A ~ howbody_avg_A + a2pSOO_P + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim2.c <- gls(authenticity_A ~a2pSOO_P, 
+apim2.c <- gls(authenticity_A ~a2pSOO_P + smith_or_clark, 
                  na.action=na.omit, 
@@
 #cognitive performance
-apim3 <- gls(trigram_score_A ~ authenticity_A, 
+apim3 <- gls(trigram_score_A ~ authenticity_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim3.b <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A, 
+apim3.b <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim3.c <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
+apim3.c <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A + a2pSOO_P + smith_or_clark, 
                  na.action=na.omit, 
@@
 #relationship agency
-apim4 <- gls(relag_A ~ authenticity_A, 
+apim4 <- gls(relag_A ~ authenticity_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim4.b <- gls(relag_A ~ authenticity_A + howbody_avg_A, 
+apim4.b <- gls(relag_A ~ authenticity_A + howbody_avg_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim4.c <- gls(relag_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
+apim4.c <- gls(relag_A ~ authenticity_A + howbody_avg_A + a2pSOO_P + smith_or_clark, 
                  na.action=na.omit, 
@@
 #career aspirations
-apim5 <- gls(careerasp_A ~ authenticity_A, 
+apim5 <- gls(careerasp_A ~ authenticity_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim5.b <- gls(careerasp_A ~ authenticity_A + howbody_avg_A, 
+apim5.b <- gls(careerasp_A ~ authenticity_A + howbody_avg_A + smith_or_clark, 
                  na.action=na.omit, 
@@
 
-apim5.c <- gls(careerasp_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
+apim5.c <- gls(careerasp_A ~ authenticity_A + howbody_avg_A + a2pSOO_P + smith_or_clark, 
                  na.action=na.omit, 

### 2020-07-09 Final_Manuscript.tex
small changes closing github issues

@@
 
+\subsection{Post interaction Measures}\label{post-interaction-measures}
+
 \begin{table}[tbp]
@@
 \end{table}
-
-\subsection{Post interaction Measures}\label{post-interaction-measures}
 
@@
 
-There were some similar correaltions bewtween study variables across
-samples.
-
 Due these similarities across samples in regard to correlation patterns
@@
 
+\subsection{Analysis Strategy}\label{analysis-strategy}
+
 \begin{figure}
@@
 \end{figure}
-
-\subsection{Analysis Strategy}\label{analysis-strategy}
 
@@
 
+\subsection{Main Results}\label{main-results}
+
 \begin{figure}
@@
 \end{figure}
-
-\subsection{Main Results}\label{main-results}
 
@@
 was statistically signficant, \emph{b} = 0.29, \emph{SE} = 0.12,
-\emph{p} = .017, replicating Garcia et al. (2016)'s fiding. One's own
+\emph{p} = .019, replicating Garcia et al. (2016)'s fiding. One's own
 other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
-= 0.12, \emph{p} = .193. Contrary to past finding however, there was no
+= 0.12, \emph{p} = .210. Contrary to past finding however, there was no
 statistically significant interaction of partner's other objectification
-and the person's trait self-objectification on SSO, \emph{b} = -0.02,
-\emph{SE} = 0.04, \emph{p} = .589. There was also no significant main
+and the person's trait self-objectification on SSO, \emph{b} = 0.03,
+\emph{SE} = 0.27, \emph{p} = .910. There was also no significant main
 effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
-0.05, \emph{p} = .170.
+0.05, \emph{p} = .183.
 
@@
 interaction authenticity, although the estimate of this effect was in
-the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.11,
-\emph{p} = .415. Because authenticity was a composite score of 9 items,
+the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12,
+\emph{p} = .431. Because authenticity was a composite score of 9 items,
 two of which were interaction specific authenticity items, we also
-tested the effect of SSO on these items individually\ldots{}ADD
-ANALYSIS\ldots{}Although we hypothesized that SSO would mediate the
-relationship between partner's other objectification and interaction
-authenticity, after finding no relationship bewteen SSO and authencity,
-we also tested if the partner's other objectification had a direct
-effect on authenticity, but this effect was not significant, \emph{b} =
-0.05, \emph{SE} = 0.11, \emph{p} = .662 (nor was the total effect of
-partner's other objectification on authenticity, \emph{b} = 0.02,
-\emph{SE} = 0.1, \emph{p} = .855).
+estimated the pairwise correlations bewteen SSO and all these items
+individually. They were all small, ranging from only -0.01 to -0.14.
+Although we hypothesized that SSO would mediate the relationship between
+partner's other objectification and interaction authenticity, after
+finding no relationship bewteen SSO and authencity, we also tested if
+the partner's other objectification had a direct effect on authenticity,
+but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
+\emph{p} = .608 (nor was the total effect of partner's other
+objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11,
+\emph{p} = .787).
 
@@
 tested in three separate models. There was no significant effect of
-interaction authenticity on cognitive performance, \emph{b} = 0.31,
-\emph{SE} = 0.28, \emph{p} = .262, but authenticity was significantly
-positively related to both career aspirations, \emph{b} = 0.19,
-\emph{SE} = 0.07, \emph{p} = .009, and relationships agency, \emph{b} =
-0.23, \emph{SE} = 0.12, \emph{p} = .048. There was no direct effect of
-SSO on cognitive performance, \emph{b} = 0.05, \emph{SE} = 0.25,
-\emph{p} = .846, and no direct effect of partner's other objectificaiton
-on cognifitve performance, \emph{b} = 0.03, \emph{SE} = 0.26, \emph{p} =
-.900. There was no direct effect of SSO on career aspirations, \emph{b}
-= 0.03, \emph{SE} = 0.06, \emph{p} = .653, and no direct effect of
-partner's other objectificaiton on career aspirations, \emph{b} = -0.05,
-\emph{SE} = 0.06, \emph{p} = .405. There was no direct effect of SSO on
-relationship agency, \emph{b} = -0.04, \emph{SE} = 0.11, \emph{p} =
-.699, and no direct effect of partner's other objectificaiton on
-relationship agency, \emph{b} = -0.07, \emph{SE} = 0.1, \emph{p} = .474.
+interaction authenticity on cognitive performance, \emph{b} = 0.32,
+\emph{SE} = 0.28, \emph{p} = .258, but authenticity was significantly
+positively related to both career aspirations, \emph{b} = 0.18,
+\emph{SE} = 0.07, \emph{p} = .010, and relationships agency, \emph{b} =
+0.23, \emph{SE} = 0.12, \emph{p} = .049. There was no direct effect of
+SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25,
+\emph{p} = .872, and no direct effect of partner's other objectificaiton
+on cognifitve performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
+.962. There was no direct effect of SSO on career aspirations, \emph{b}
+= 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of
+partner's other objectificaiton on career aspirations, \emph{b} = -0.06,
+\emph{SE} = 0.07, \emph{p} = .378. There was no direct effect of SSO on
+relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} =
+.659, and no direct effect of partner's other objectificaiton on
+relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.
 

### 2020-07-20 Final_Manuscript.Rmd
worked on intro

@@
 
-Theorists across diverse disciplines have explored the multiple ways that the body conveys social meaning, as well as how these meanings shape gendered experiences, especially during interpersonal interactions with members of different social groups [@Kaschak, @garcia2016objectification].
-Objectification theory, a valuable theoretical framework proposed by @robertsfredrickson which works to contextualize female bodies as socio-cultural constructions, can be employed to illuminate the gender oppression and negative lived experiences of girls and women.
-Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and expereince daily sexist hassles [@swimetal].
-One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
-Sexual objectification occurs with both “endless variety and monotonous similarity,” and is thus mediated by unique combinations of race, ethnicity, sexuality, age, and class [@fredricksonetal2011; @rubin1975, cited in @frasernicholson1989, p.
-28].
-Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
+OUTLINE
+  - Introduction: Objectification theory says stuff.
+Recently we've learned about interpersonal objectification but we only know it about mixed gender.
+We know women objectify each other, but what about in interpersonal interactions?
+  - Self-objectification
+    - SSO versus TSO
+    - Does this process of self-objectification also lead women to objectify other women?
+  - Women objectifying other women
+    - Lots of evidence, but we don't know if this happens interpersonally
+  - Interpersonal objectifcation research is a whole thing now, but there are no studies (or theoretical models) that include women-on-women interpersonal objectification processes. 
+  - Relationships and objectification 
+    - Both romantic relationships and relationships in general have been studies in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
+  - Authenticity paragraph?
+  - Current Study
+  - Alternative predictions
+
+@robertsfredrickson's Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
+Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link.
+For exmaple, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men's reported objectificaiton of their female interaction partner during an interaction was associated with increased sefl-objectification reported by their partner.
+@gervais2020social has reviewed the literature on interpersonal self-objectification and has organized the the process in a theoretical model called the SIMO, but this model is only relevant for mixed-gender encouters.
+Although there is ample evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], there is currently no studies investigating the process of interpersonal objectification same-gender interactions.
+Does objectification by a female interaction partner have the same downstream negative consequences as being objectified by a male interaction partner?
+For example, perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men outlined in @gervais2020social occur.
 
@@
 Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [CITE swimsuit sweater, @garcia2016objectification].
+Does this habit self-objectification lead women to also objectify other women, possibly to compare oneself?
 
+Some studies have found that women objectify other women to a greater extent than they objectify men [@loughnan2015exploring].
+Women objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but we know next to nothing about interpersonal sexual objectification among women and what the immediate effects might be.
+Further, do women objectify non-sexualized women they are interacting with?
+What might be different for same-gender interactions?
+@harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women participants, although men scored high than women on a measure of belief that objectification of women is natural for men.
+
+SIMO model and literature review [@gervais2020social].
 Studies have shown that within social encounters women are gazed at more than men [@briton1995, CITE saguy skype study, calogero video walking study], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
 Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
+We don't know about women-on-women interpersonal objectification.
+What might be different?
 
-ENTIRE PARAGRAPH ON MODERN (POST-2016) STUDIES OF INTERPERSONAL OBJECTIFICATION.
+Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because in our culture women need to look attractive to obtain and maintain successfuol relationship, thus, the "college relationships condition may highten self-objectification and the evaluation of other women in a sexualized way.
+Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds].
+Evidence is mixed, and women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship [@meltzer2020women], less is known about first dates.
+But this literature is also only about heterosexual relationships.
+A recent study has investigated the effect of self-objectification on the reduction of relationship biulding skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor].
+Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@quinnetal].
 
-Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@quinnetal].
+MAYBE SEPARATE PARAGRAPH ABOUT AUTHENTICITY LINK SPECIFICALLY.
+And how woman-woman interpersonal objectificaiton preocesses might diverge from this process.
+[again CITE PWQ paper I reviewed, Yoder editor].
 
@@
 We also expect to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
+
+@puvia2013being would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (...well, dehumanize a sexualized woman, but also @strelan2005women would predict the TSO->SOO link and @harsey2020men too), and this is mediated by the woman's own state self-objectification (SSO).
+So we also tested this as a possible alternative model.
 
@@
 
-There are many types of relationships people form in college.
+>There are many types of relationships people form in college.
 During the interaction, please think about your partner's potential as a romantic partner.
@@
 Also, your interaction partner will be evaluating you in the same manner.
+
+The decision was made to ask even heterosexual women to judge their women partners as potential romantic partners.
+We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study.
+Past research has found that women, largely due to an increase self-objectifying state, are indeed able to evaluate other women's potential as romantic partners--indeed, women may be unfortunutely used to thinking this way about themselves, and we suspect other women.
 
@@
                                           otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
+
+descsplit <- clarksmith_women %>%
+  group_by(sexor_A == 1) %>%
+  summarize(mean_soo = mean(a2pSOO_A, na.rm = TRUE),
+            sd_soo = sd(a2pSOO_A, na.rm = TRUE))
+
+soo_diff <- t.test(a2pSOO_A ~ (sexor_A == 1), data = clarksmith_women)
 ```
@@
 A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
+
+As can be seen in Table\ \@ref(tab:descriptives), the mean other-objectification of women by women was *M =* `r descriptives[3,1]` (*SD =* `r descriptives[3,2]`).
+This corresponds to women objectifying other women to a *greater* extent than women's objectification of men reported in @garcia2016objectification (*M =* -1.68, *SD =* 1.52).
+Further, in the current sample the difference in other-objectification between heterosexual (*M =* `r round(as.numeric(descsplit[2,2]),2)`, *SD =* `r round(as.numeric(descsplit[2,3]),2)`) and non-heterosexual women (*M =* `r round(as.numeric(descsplit[1,2]),2)`, *SD =* `r round(as.numeric(descsplit[1,3]),2)`) was not statistically significant, *t*(`r round(soo_diff$parameter,2)`) = `r round(soo_diff$statistic, 2)`, *p =* `r round(soo_diff$p.value,3)`.
 
@@
 #Discussion
-As stated previously, we did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to relationship inauthenticity.
+
+As stated previously, we did not find a significant effect between actor SSO and actor authenticity, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to relationship inauthenticity.
 However, we did observe a significant partner effect of objectification on actor self-objectification, which does align with our hypothesis that theorized objectification from other women can also cause women to self-objectify just as they do within interactions between male-female pairs.
-The results of this study demonstrate the complex and ambivalent nature of female sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
+
+##Sexism and Sexual Discrimination
+Sexism has recently been found to be related to the objectification of women, but not men, for both men and women [@harsey2020men].
+Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and expereince daily sexist hassles [@swimetal].
+One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
+Sexual objectification occurs with both “endless variety and monotonous similarity,” and is thus mediated by unique combinations of race, ethnicity, sexuality, age, and class [@fredricksonetal2011; @rubin1975, cited in @frasernicholson1989, p.
+28].
+Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
+
+##Limitations and Future Directions
+
+###Sample Characteristics
 The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008].
@@
 It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexulizing content.
+
+###Measurement
 Also, future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operalization of self-objectification may be improved.
+
+###Alternative Model
+@puvia2013being alternative model. TSO -> SOO, mediated by SSO.
+
+##Clinical Implications
 Regardless, the results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts.
 These results are quite useful for promoting mental health and within early action programs for girls and young women, where scholars and practitioners might provide the tools necessary to circumvent or mitigate negative effects on self-objectification, and combat such experiences.
+
+#Conclusion
+The results of this study demonstrate the complex and ambivalent nature of female sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
 

### 2020-07-20 Final_Manuscript.tex
worked on intro

@@
 
+\begin{quote}
 There are many types of relationships people form in college. During the
@@
 you in the same manner.
+\end{quote}
+
+The decision was made to ask even heterosexual women to judge their
+women partners as potential romantic partners. We felt that this prompt
+would keep the study closest to a replication of the previous Garcia et
+al. (2016) version of the study. Past research has found that women,
+largely due to an increase self-objectifying state, are indeed able to
+evaluate other women's potential as romantic partners--indeed, women may
+be unfortunutely used to thinking this way about themselves, and we
+suspect other women.
 
@@
 would indicate the opposite.
+
+As can be seen in Table~\ref{tab:descriptives}, the mean
+other-objectification of women by women was \emph{M =} -1.58 (\emph{SD
+=} 1.21). This corresponds to women objectifying other women to a
+\emph{greater} extent than women's objectification of men reported in
+Garcia et al. (2016) (\emph{M =} -1.68, \emph{SD =} 1.52). Further, in
+the current sample the difference in other-objectification between
+heterosexual (\emph{M =} -1.77, \emph{SD =} 1.14) and non-heterosexual
+women (\emph{M =} -1.39, \emph{SD =} 1.35) was not statistically
+significant, \emph{t}(25.89) = 1.02, \emph{p =} 0.32.
 
@@
 dyadic multilevel modeling (MLM) to test all relationships and mediation
-paterns. See Ledermann and Kenny (2017) for a more complete discussion
-of the considerations for using SEM versus MLM for dyadic analysis.
+paterns. The online supplementary materials contains analysis using SEM.
+See Ledermann and Kenny (2017) for a more complete discussion of the
+considerations for using SEM versus MLM for dyadic analysis.
 
@@
 analysis sample. The online supplemental material contains the main
-analyses separated by samples.
+analyses separated by samples. All results presented below are from
+models including sample as a control variable.
 

### 2020-07-21 Final_Manuscript.Rmd
fixed bib

@@
 Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds].
-Evidence is mixed, and women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship [@meltzer2020women], less is known about first dates.
+Evidence is mixed, and women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship and they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], less is known about first dates.
 But this literature is also only about heterosexual relationships.

### 2020-07-21 Final_Manuscript.tex
fixed bib

@@
 
-Theorists across diverse disciplines have explored the multiple ways
-that the body conveys social meaning, as well as how these meanings
-shape gendered experiences, especially during interpersonal interactions
-with members of different social groups (``Engendered lives,'' 1993,
-Garcia, Earnshaw, and Quinn (2016)). Objectification theory, a valuable
-theoretical framework proposed by Roberts and Fredrickson (1997) which
-works to contextualize female bodies as socio-cultural constructions,
-can be employed to illuminate the gender oppression and negative lived
-experiences of girls and women. Empirical evidence illustrates how women
-continue to be objects of interpersonal discrimination and expereince
-daily sexist hassles (Swim, Hyers, Cohen, \& Ferguson, 2001). One form
-of interpersonal discrimination women face is the process by which their
-whole being is viewed as a collection of sexualized body parts valued
-predominantly for commodification, a phenomena termed sexual
-objectification (Bartky, 1990). Sexual objectification occurs with both
-\enquote{endless variety and monotonous similarity,} and is thus
-mediated by unique combinations of race, ethnicity, sexuality, age, and
-class (Fredrickson, Hendler, Nilsen, O'Barr, \& Roberts, 2011; Rubin,
-1975, cited in Fraser and Nicholson (1989), p.~28). Amid such
-heterogeneity though, \enquote{having a reproductively mature female
-body} proposed by Roberts and Fredrickson (1997) is likely to create a
-shared vulnerability to sexual objectification and a variety of shared
-negative experiences as a result.
+OUTLINE - Introduction: Objectification theory says stuff. Recently
+we've learned about interpersonal objectification but we only know it
+about mixed gender. We know women objectify each other, but what about
+in interpersonal interactions? - Self-objectification - SSO versus TSO -
+Does this process of self-objectification also lead women to objectify
+other women? - Women objectifying other women - Lots of evidence, but we
+don't know if this happens interpersonally - Interpersonal
+objectifcation research is a whole thing now, but there are no studies
+(or theoretical models) that include women-on-women interpersonal
+objectification processes. - Relationships and objectification - Both
+romantic relationships and relationships in general have been studies in
+the context of objectification, but neither of these literatures have
+investigated specifically same-gender relationships. - Authenticity
+paragraph? - Current Study - Alternative predictions
+
+Roberts and Fredrickson (1997)\enquote{s Objectification Theory,
+suggests that women are objectified in interpersonal encounters, and
+that the effect might be strongest from men, but possibly also from
+women. Psychological researchers studying the sexual objectification of
+women, and the resulting self-objectification that follows, have in
+recent years explored the interpersonal process of the objectification -
+self-objectification link. For exmaple, in a face-to-face mixed-gender
+dyadic study, Garcia, Earnshaw, and Quinn (2016) found that men's
+reported objectificaiton of their female interaction partner during an
+interaction was associated with increased sefl-objectification reported
+by their partner. Gervais, Sáez, Riemer, and Klein (2020) has reviewed
+the literature on interpersonal self-objectification and has organized
+the the process in a theoretical model called the SIMO, but this model
+is only relevant for mixed-gender encouters. Although there is ample
+evidence that women objectify other women (Loughnan et al., 2015a; Puvia
+\& Vaes, 2013), there is currently no studies investigating the process
+of interpersonal objectification same-gender interactions. Does
+objectification by a female interaction partner have the same downstream
+negative consequences as being objectified by a male interaction
+partner? For example, perhaps women could be amplifying each others}
+self-objectification as they get ready to go out for the night,
+\emph{before} the theoretical encounters with men outlined in Gervais et
+al. (2020) occur.
 
@@
 self-objectification (SSO) (CITE swimsuit sweater, Garcia et al., 2016).
-
-Studies have shown that within social encounters women are gazed at more
-than men (Briton \& Hall, 1995, CITE saguy skype study, calogero video
-walking study), often times feel \enquote{looked at} within
-interpersonal interactions (Argyle \& Williams, 1969), and will more
-than likely internalize the objectifying gaze on physical self (Young,
-1979). Moreover, perhaps the most adverse effect of objectifying
-treatment is that it effectively socializes girls and women to treat
-themselves as objects to be looked at and evaluated, an effect termed
+Does this habit self-objectification lead women to also objectify other
+women, possibly to compare oneself?
+
+Some studies have found that women objectify other women to a greater
+extent than they objectify men (Loughnan et al., 2015a). Women objectify
+(dehumanized) sexualized targets presented as images (Puvia \& Vaes,
+2013), but we know next to nothing about interpersonal sexual
+objectification among women and what the immediate effects might be.
+Further, do women objectify non-sexualized women they are interacting
+with? What might be different for same-gender interactions? Harsey and
+Zurbriggen (2020) found that self-objectification was related to the
+objectification of women to a similar degree for men and women
+participants, although men scored high than women on a measure of belief
+that objectification of women is natural for men.
+
+SIMO model and literature review (Gervais et al., 2020). Studies have
+shown that within social encounters women are gazed at more than men
+(Briton \& Hall, 1995, CITE saguy skype study, calogero video walking
+study), often times feel \enquote{looked at} within interpersonal
+interactions (Argyle \& Williams, 1969), and will more than likely
+internalize the objectifying gaze on physical self (Young, 1979).
+Moreover, perhaps the most adverse effect of objectifying treatment is
+that it effectively socializes girls and women to treat themselves as
+objects to be looked at and evaluated, an effect termed
 self-objectification (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972;
-L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge, 1998).
-
-ENTIRE PARAGRAPH ON MODERN (POST-2016) STUDIES OF INTERPERSONAL
-OBJECTIFICATION.
-
-Empirical evidence reveals that objectification manifests through
-inauthenticity in romantic relationships (Brunell et al., 2010), adverse
-attitudes in regard to career aspirations, and a decrease in
-concentration and impairment in female cognitive performance (D. M.
-Quinn, Chaudoir, \& Kallen, 2011).
+L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge, 1998). We don't know
+about women-on-women interpersonal objectification. What might be
+different?
+
+Self-objectification has been found to occur after a mere relationship
+prime among women (Sanchez \& Broccoli, 2008) because in our culture
+women need to look attractive to obtain and maintain successfuol
+relationship, thus, the ``college relationships condition may highten
+self-objectification and the evaluation of other women in a sexualized
+way. Researchers have also studied interpersonal objectification and
+self-objectification in romantic relationships (Strelan \& Pagoudis,
+2018). Evidence is mixed, and women can sometimes have positive outcomes
+from appearance valuation within the context of an established romantic
+relationship and they experience less SSO after appearance comments
+within romantic relationships (Meltzer, 2020), less is known about first
+dates. But this literature is also only about heterosexual
+relationships. A recent study has investigated the effect of
+self-objectification on the reduction of relationship biulding skills in
+general (including same-sex friendships) {[}CITE PWQ paper I reviewed,
+Yoder editor{]}. Empirical evidence reveals that objectification
+manifests through inauthenticity in romantic relationships (Brunell et
+al., 2010), adverse attitudes in regard to career aspirations, and a
+decrease in concentration and impairment in female cognitive performance
+(D. M. Quinn, Chaudoir, \& Kallen, 2011).
+
+MAYBE SEPARATE PARAGRAPH ABOUT AUTHENTICITY LINK SPECIFICALLY. And how
+woman-woman interpersonal objectificaiton preocesses might diverge from
+this process. {[}again CITE PWQ paper I reviewed, Yoder editor{]}.
 
@@
 performance, relationship agency, and career aspirations.
+
+Puvia and Vaes (2013) would alternatively predict that women's tendency
+to self-objectify (TSO) leads them to objectify other women
+(\ldots{}well, dehumanize a sexualized woman, but also Strelan and
+Hargreaves (2005) would predict the TSO-\textgreater{}SOO link and
+Harsey and Zurbriggen (2020) too), and this is mediated by the woman's
+own state self-objectification (SSO). So we also tested this as a
+possible alternative model.
 
@@
 As stated previously, we did not find a significant effect between actor
-SSO and actor authenticity (\(\beta\)= -.10, \(p\)=.38), which suggests
-that there is not sufficient evidence to support the claim that partner
-objectification is the cause for the diverse range of negative effects
-related to relationship inauthenticity. However, we did observe a
-significant partner effect of objectification on actor
-self-objectification, which does align with our hypothesis that
-theorized objectification from other women can also cause women to
-self-objectify just as they do within interactions between male-female
-pairs. The results of this study demonstrate the complex and ambivalent
-nature of female sexual objectification and additionally highlight the
-psychological and social consequences of such objectification processes
-on women's social relationships and well-being. The sample of the
-current study was comprised of Western women, being that sexual
-objectification is most prevalent in this culture (Loughnan et al.,
-2015), and research on objectification conducted outside of Western or
-Westernized countries is scarce (Moradi \& Huang, 2008). Because
-\enquote{bodies exist within social and cultural contexts, and hence are
-also constructed through sociocultural practices and discourses}
-(Roberts \& Fredrickson, 1997, p. 174), it is important to consider how
-diverse social identities within unique cultural contexts may inform
-sexual objectification phenomenon to test the cross-cultural
-applicability of theoretical frameworks (Loughnan et al., 2015).
+SSO and actor authenticity, which suggests that there is not sufficient
+evidence to support the claim that partner objectification is the cause
+for the diverse range of negative effects related to relationship
+inauthenticity. However, we did observe a significant partner effect of
+objectification on actor self-objectification, which does align with our
+hypothesis that theorized objectification from other women can also
+cause women to self-objectify just as they do within interactions
+between male-female pairs.
+
+\subsection{Sexism and Sexual
+Discrimination}\label{sexism-and-sexual-discrimination}
+
+Sexism has recently been found to be related to the objectification of
+women, but not men, for both men and women (Harsey \& Zurbriggen, 2020).
+Empirical evidence illustrates how women continue to be objects of
+interpersonal discrimination and expereince daily sexist hassles (Swim,
+Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
+discrimination women face is the process by which their whole being is
+viewed as a collection of sexualized body parts valued predominantly for
+commodification, a phenomena termed sexual objectification (Bartky,
+1990). Sexual objectification occurs with both \enquote{endless variety
+and monotonous similarity,} and is thus mediated by unique combinations
+of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
+Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
+Nicholson (1989), p.~28). Amid such heterogeneity though,
+\enquote{having a reproductively mature female body} proposed by Roberts
+and Fredrickson (1997) is likely to create a shared vulnerability to
+sexual objectification and a variety of shared negative experiences as a
+result.
+
+\subsection{Limitations and Future
+Directions}\label{limitations-and-future-directions}
+
+\subsubsection{Sample Characteristics}\label{sample-characteristics}
+
+The sample of the current study was comprised of Western women, being
+that sexual objectification is most prevalent in this culture (Loughnan
+et al., 2015b), and research on objectification conducted outside of
+Western or Westernized countries is scarce (Moradi \& Huang, 2008).
+Because \enquote{bodies exist within social and cultural contexts, and
+hence are also constructed through sociocultural practices and
+discourses} (Roberts \& Fredrickson, 1997, p. 174), it is important to
+consider how diverse social identities within unique cultural contexts
+may inform sexual objectification phenomenon to test the cross-cultural
+applicability of theoretical frameworks (Loughnan et al., 2015b).
 Further, sexualzing experiences and self-objectification are thought to
@@
 children, adolescents, or emerging adults of different races or
-ethnicities are exposed to varied amounts of sexulizing content. Also,
-future experiments or longitudinal studies should explore the external
-validity of the notions of self-objectification and how the
-operalization of self-objectification may be improved. Regardless, the
-results from the current analysis highlight how subtle forms of sexist
-discrimination operate to inform prevention and intervention efforts in
-both clinical and educational contexts. These results are quite useful
-for promoting mental health and within early action programs for girls
-and young women, where scholars and practitioners might provide the
-tools necessary to circumvent or mitigate negative effects on
-self-objectification, and combat such experiences.
+ethnicities are exposed to varied amounts of sexulizing content.
+
+\subsubsection{Measurement}\label{measurement}
+
+Also, future experiments or longitudinal studies should explore the
+external validity of the notions of self-objectification and how the
+operalization of self-objectification may be improved.
+
+\subsubsection{Alternative Model}\label{alternative-model}
+
+Puvia and Vaes (2013) alternative model. TSO -\textgreater{} SOO,
+mediated by SSO.
+
+\subsection{Clinical Implications}\label{clinical-implications}
+
+Regardless, the results from the current analysis highlight how subtle
+forms of sexist discrimination operate to inform prevention and
+intervention efforts in both clinical and educational contexts. These
+results are quite useful for promoting mental health and within early
+action programs for girls and young women, where scholars and
+practitioners might provide the tools necessary to circumvent or
+mitigate negative effects on self-objectification, and combat such
+experiences.
+
+\section{Conclusion}\label{conclusion}
+
+The results of this study demonstrate the complex and ambivalent nature
+of female sexual objectification and additionally highlight the
+psychological and social consequences of such objectification processes
+on women's social relationships and well-being.
 
@@
 
-\hypertarget{ref-Kaschak}{}
-Engendered lives: A new psychology of womens experience. (1993).
-\emph{Choice Reviews Online}, \emph{30}(07).
-doi:\href{https://doi.org/10.5860/choice.30-4102}{10.5860/choice.30-4102}
-
 \hypertarget{ref-frasernicholson1989}{}
@@
 \emph{22}(1), 8--29.
+
+\hypertarget{ref-gervais2020social}{}
+Gervais, S. J., Sáez, G., Riemer, A. R., \& Klein, O. (2020). The social
+interaction model of objectification: A process model of goal-based
+objectifying exchanges between men and women. \emph{British Journal of
+Social Psychology}, \emph{59}(1), 248--283.
+
+\hypertarget{ref-harsey2020men}{}
+Harsey, S. J., \& Zurbriggen, E. L. (2020). Men and women's
+self-objectification, objectification of women, and sexist beliefs.
+\emph{Self and Identity}, 1--8.
 
@@
 
+\hypertarget{ref-loughnan2015exploring}{}
+Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
+Harada, C., \ldots{} Tsuchiya, K. (2015a). Exploring the role of culture
+in sexual objectification: A seven nations study. \emph{Revue
+Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
+
 \hypertarget{ref-loughnan2015}{}
 Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
-Harada, C., \ldots{} Tsuchiya, K. (2015). Exploring the role of culture
+Harada, C., \ldots{} Tsuchiya, K. (2015b). Exploring the role of culture
 in sexual objectification: A seven nations study. \emph{Revue
@@
 
+\hypertarget{ref-meltzer2020women}{}
+Meltzer, A. L. (2020). Women can benefit from sexual and physical
+valuation in the context of a romantic relationship. \emph{Personality
+and Social Psychology Bulletin}, \emph{46}(2), 243--257.
+
 \hypertarget{ref-moradi2008}{}
@@
 \url{https://CRAN.R-project.org/package=mosaicData}
+
+\hypertarget{ref-puvia2013being}{}
+Puvia, E., \& Vaes, J. (2013). Being a body: Women's appearance related
+self-views and their dehumanization of sexually objectified female
+targets. \emph{Sex Roles}, \emph{68}(7-8), 484--495.
 
@@
 
+\hypertarget{ref-sanchez2008romance}{}
+Sanchez, D. T., \& Broccoli, T. L. (2008). The romance of
+self-objectification: Does priming romantic relationships induce states
+of self-objectification among women? \emph{Sex Roles}, \emph{59}(7-8),
+545--554.
+
 \hypertarget{ref-R-lattice}{}
@@
 \url{https://CRAN.R-project.org/package=apaTables}
+
+\hypertarget{ref-strelan2005women}{}
+Strelan, P., \& Hargreaves, D. (2005). Women who objectify other women:
+The vicious circle of objectification? \emph{Sex Roles},
+\emph{52}(9-10), 707--712.
+
+\hypertarget{ref-strelan2018birds}{}
+Strelan, P., \& Pagoudis, S. (2018). Birds of a feather flock together:
+The interpersonal process of objectification within intimate
+heterosexual relationships. \emph{Sex Roles}, \emph{79}(1-2), 72--82.
 

### 2020-07-21 Final_Manuscript.Rmd
paragraph on authenticity

@@
 
-@robertsfredrickson's Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
+@robertsfredrickson Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
 Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link.
-For exmaple, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men's reported objectificaiton of their female interaction partner during an interaction was associated with increased sefl-objectification reported by their partner.
-@gervais2020social has reviewed the literature on interpersonal self-objectification and has organized the the process in a theoretical model called the SIMO, but this model is only relevant for mixed-gender encouters.
+For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men's reported objectification of their female interaction partner during an interaction was associated with increased self-objectification reported by their partner.
+@gervais2020social has reviewed the literature on interpersonal self-objectification and has organized the the process in a theoretical model called the SIMO, but this model is only relevant for mixed-gender encounters.
 Although there is ample evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], there is currently no studies investigating the process of interpersonal objectification same-gender interactions.
@@
 SIMO model and literature review [@gervais2020social].
-Studies have shown that within social encounters women are gazed at more than men [@briton1995, CITE saguy skype study, calogero video walking study], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
+Studies have shown that within social encounters women are gazed at more than men [@briton1995, CITE saguy Skype study, calogero video walking study], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
 Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
@@
 
-Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because in our culture women need to look attractive to obtain and maintain successfuol relationship, thus, the "college relationships condition may highten self-objectification and the evaluation of other women in a sexualized way.
+Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because in our culture women need to look attractive to obtain and maintain successful relationship, thus, the "college relationships condition may heighten self-objectification and the evaluation of other women in a sexualized way.
 Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds].
@@
 But this literature is also only about heterosexual relationships.
-A recent study has investigated the effect of self-objectification on the reduction of relationship biulding skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor].
+A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor].
 Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@quinnetal].
+Thus, there is evidence that the expereince of state self-objectification in mixed-gender contexts (stranger and romantic) and within the self in any moment (trying on a swimsuit) has negative consequences, but what about in the context of interaction with other women?
 
-MAYBE SEPARATE PARAGRAPH ABOUT AUTHENTICITY LINK SPECIFICALLY.
-And how woman-woman interpersonal objectificaiton preocesses might diverge from this process.
-[again CITE PWQ paper I reviewed, Yoder editor].
+There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor].
+This link has been justified by the lierature on stigmatized-stigmatizer interactions, viewing the experience of being objectified in an interaction as an identity threat situation.
+When a woman is objectified by a man, and then experiences self-objectification, this intergroup encounter might trigger identitiy threat, but is the same negative consequence present when a woman is objectified by another woman?
+woman-woman interpersonal objectification processes might diverge from this process.
+One the one hand, she may not be having the same negative consequences the cascade from situations that threated group-based identity [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in an interaction may be enough to reduce feelings of authenticity and social competnce, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
 
@@
 We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study.
-Past research has found that women, largely due to an increase self-objectifying state, are indeed able to evaluate other women's potential as romantic partners--indeed, women may be unfortunutely used to thinking this way about themselves, and we suspect other women.
+Past research has found that women, largely due to an increase self-objectifying state, are indeed able to evaluate other women's potential as romantic partners--indeed, women may be unfortunately used to thinking this way about themselves, and we suspect other women.
 
@@
 ```
-Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
+Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus non-observable ways.
 The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
@@
 We hope to investigate how the central effects found in the previous study relate to interactions between two women.
-Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affecs feelings of inauthenticity during the interaction.
+Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction.
 In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification.
-Further, we will investigate the realtionships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.
+Further, we will investigate the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.
 
 While @garcia2016objectification used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling.
-Dyadic analyses for distingishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structual Equation Modeling (SEM) than it is for indistinguishable dayds (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation].
-One reason for this asymmetry is that, due to the arbitrary distinctions made bewteen "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality contraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural].
+Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dayds (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation].
+One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural].
 Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models.
-The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation paterns.
+The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation patterns.
 The online supplementary materials contains analysis using SEM.
@@
 
-Testing the @garcia2016objectification model on the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approch for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:2016figure)).
+Testing the @garcia2016objectification model on the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approach for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:2016figure)).
 Thus, we ran five APIM's to test all the hypothesized relationships.
@@
 Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
-Recall that the indistinguiahble nature of the dyads in the current study led us to choose the MLM approach over SEM.
+Recall that the indistinguishable nature of the dyads in the current study led us to choose the MLM approach over SEM.
 These analyses are considered exploratory, given the lack of prior research theorizing about these linkages.
@@
 ```
-The correaltions between study variables is similar across samples.
-The realibialities for the study scales were also equivalent.
+The correlations between study variables is similar across samples.
+The reliabilities for the study scales were also equivalent.
 (Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS.
@@
 The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
-As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically signficant, `r report_stats(apim1, 3)`, replicating @garcia2016objectification's fiding.
+As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically significant, `r report_stats(apim1, 3)`, replicating @garcia2016objectification's finding.
 One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
@@
 Contrary to expectations, there was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
-Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also estimated the pairwise correlations bewteen SSO and all these items individually.
+Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also estimated the pairwise correlations between SSO and all these items individually.
 They were all small, ranging from only `r -1*min_corr` to `r -1*max_corr`.
-Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship bewteen SSO and authencity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, `r report_stats(apim2.b, 3)` (nor was the total effect of partner's other objectification on authenticity, `r report_stats(apim2.c, 2)`).
+Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship between SSO and authenticity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, `r report_stats(apim2.b, 3)` (nor was the total effect of partner's other objectification on authenticity, `r report_stats(apim2.c, 2)`).
 
@@
 ```
-Lastly, althought there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performace, career aspirations, and relationship agency, as it did in @garcia2016objectification.
-We again used MLM and thus, these efefcts were tested in three separate models.
+Lastly, although there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performance, career aspirations, and relationship agency, as it did in @garcia2016objectification.
+We again used MLM and thus, these effects were tested in three separate models.
 There was no significant effect of interaction authenticity on cognitive performance, `r report_stats(apim3, 2)`, but authenticity was significantly positively related to both career aspirations, `r report_stats(apim5, 2)`, and relationships agency, `r report_stats(apim4, 2)`.
-There was no direct effect of SSO on cognitive performance, `r report_stats(apim3.b, 3)`, and no direct effect of partner's other objectificaiton on cognifitve performance, `r report_stats(apim3.c, 4)`.
-There was no direct effect of SSO on career aspirations, `r report_stats(apim5.b, 3)`, and no direct effect of partner's other objectificaiton on career aspirations, `r report_stats(apim5.c, 4)`.
-There was no direct effect of SSO on relationship agency, `r report_stats(apim4.b, 3)`, and no direct effect of partner's other objectificaiton on relationship agency, `r report_stats(apim4.c, 4)`.
+There was no direct effect of SSO on cognitive performance, `r report_stats(apim3.b, 3)`, and no direct effect of partner's other objectification on cognitive performance, `r report_stats(apim3.c, 4)`.
+There was no direct effect of SSO on career aspirations, `r report_stats(apim5.b, 3)`, and no direct effect of partner's other objectification on career aspirations, `r report_stats(apim5.c, 4)`.
+There was no direct effect of SSO on relationship agency, `r report_stats(apim4.b, 3)`, and no direct effect of partner's other objectification on relationship agency, `r report_stats(apim4.c, 4)`.
 
@@
 Sexism has recently been found to be related to the objectification of women, but not men, for both men and women [@harsey2020men].
-Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and expereince daily sexist hassles [@swimetal].
+Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and experience daily sexist hassles [@swimetal].
 One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
@@
 ###Measurement
-Also, future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operalization of self-objectification may be improved.
+Also, future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operationalization of self-objectification may be improved.
 

### 2020-07-22 Final_Manuscript.Rmd
added lanee

@@
   - name          : "Asha Hinson"
+    affiliation   : "1"
+  - name          : "Lanee Jung"
     affiliation   : "1"
@@
 
-OUTLINE
-  - Introduction: Objectification theory says stuff.
-Recently we've learned about interpersonal objectification but we only know it about mixed gender.
-We know women objectify each other, but what about in interpersonal interactions?
-  - Self-objectification
-    - SSO versus TSO
-    - Does this process of self-objectification also lead women to objectify other women?
-  - Women objectifying other women
-    - Lots of evidence, but we don't know if this happens interpersonally
-  - Interpersonal objectifcation research is a whole thing now, but there are no studies (or theoretical models) that include women-on-women interpersonal objectification processes.
-  - Relationships and objectification
-    - Both romantic relationships and relationships in general have been studies in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
-  - Authenticity paragraph?
-  - Current Study
-  - Alternative predictions
-
 @robertsfredrickson Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
@@
 
+##Self-Objectification
 Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008].
@@
 
+##Women Objectifying Women
 Some studies have found that women objectify other women to a greater extent than they objectify men [@loughnan2015exploring].
@@
 
+##Interpersonal Objectification
 SIMO model and literature review [@gervais2020social].
-Studies have shown that within social encounters women are gazed at more than men [@briton1995, CITE saguy Skype study, calogero video walking study], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
+Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
 Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
@@
 Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@quinnetal].
-Thus, there is evidence that the expereince of state self-objectification in mixed-gender contexts (stranger and romantic) and within the self in any moment (trying on a swimsuit) has negative consequences, but what about in the context of interaction with other women?
+Both romantic relationships and relationships in general have been studies in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
 
+There is evidence that the expereince of state self-objectification in mixed-gender contexts (stranger and romantic) and within the self in any moment (trying on a swimsuit) has negative consequences, but what about in the context of interaction with other women?
+Is the self-objectification expreience in mixed-gender interactions the same as that experienced in same-gender interactions?
+The ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my].
+Women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], but when they do it, does it lead to self-ibjectification in the same way men's objectification of women does [@garcia2016objectification]?
+If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that ineraction?
+
+##Interpersonal Objectification and Authenticity
 There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor].
@@
 
+##The Current Study
 In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification,  but between same-sex female interpersonal interactions.
@@
 ```{r}
+# apim0 <- gls(a2pSOO_A ~ TSO_A, 
+#                  na.action=na.omit, 
+#                  correlation=corCompSymm (form=~1|dyadID),
+#                  data=clarksmith_women)
+# summary(apim0)
+
 #SSO

### 2020-07-24 Final_Manuscript.Rmd
example
Add accent on e

@@
     affiliation   : "1"
-  - name          : "Lanee Jung"
+  - name          : "Lanee Jung(edit)"
     affiliation   : "1"
@@
 Both romantic relationships and relationships in general have been studies in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
+LANEE: COMMENT IN ALL CAP LIKE THIS!
 

### 2020-07-26 Final_Manuscript.Rmd
added references

@@
 Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@calogero2011, @moradi2008].
-Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [CITE swimsuit sweater, @garcia2016objectification].
+Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [@fredrickson1998swimsuit, @garcia2016objectification].
 Does this habit self-objectification lead women to also objectify other women, possibly to compare oneself?
@@
 SIMO model and literature review [@gervais2020social].
-Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
+Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@young1979].
 Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
@@
 A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor].
-Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@quinnetal].
+Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
 Both romantic relationships and relationships in general have been studies in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
-LANEE: COMMENT IN ALL CAP LIKE THIS!
 
-There is evidence that the expereince of state self-objectification in mixed-gender contexts (stranger and romantic) and within the self in any moment (trying on a swimsuit) has negative consequences, but what about in the context of interaction with other women?
-Is the self-objectification expreience in mixed-gender interactions the same as that experienced in same-gender interactions?
+There is evidence that the experience of state self-objectification in mixed-gender contexts (stranger and romantic) and within the self in any moment (trying on a swimsuit) has negative consequences, but what about in the context of interaction with other women?
+Is the self-objectification experience in mixed-gender interactions the same as that experienced in same-gender interactions?
 The ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my].
-Women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], but when they do it, does it lead to self-ibjectification in the same way men's objectification of women does [@garcia2016objectification]?
+Women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], but when they do it, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
 If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that ineraction?
@@
 There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor].
-This link has been justified by the lierature on stigmatized-stigmatizer interactions, viewing the experience of being objectified in an interaction as an identity threat situation.
+This link has been justified by the literature on stigmatized-stigmatizer interactions, viewing the experience of being objectified in an interaction as an identity threat situation.
 When a woman is objectified by a man, and then experiences self-objectification, this intergroup encounter might trigger identitiy threat, but is the same negative consequence present when a woman is objectified by another woman?
 woman-woman interpersonal objectification processes might diverge from this process.
-One the one hand, she may not be having the same negative consequences the cascade from situations that threated group-based identity [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in an interaction may be enough to reduce feelings of authenticity and social competnce, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
+One the one hand, she may not be having the same negative consequences the cascade from situations that threated group-based identity [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in an interaction may be enough to reduce feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
 

### 2020-07-27 Final_Manuscript.Rmd
added references

@@
 ##Self-Objectification
-Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008].
+Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level [@loughnan2015exploring] to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008].
 @calogero2011 proposes that the construct of self-objectification can be conceptualized as a learned trait.
-Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@calogero2011, @moradi2008].
+Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@bernard2018bodies; @calogero2011; @moradi2008].
 Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [@fredrickson1998swimsuit, @garcia2016objectification].
@@
 SIMO model and literature review [@gervais2020social].
-Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@young1979].
+Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979].
 Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].

### 2020-07-27 Final_Manuscript.Rmd
fixed reference

@@
     affiliation   : "1"
-  - name          : "Lanee Jung(edit)"
+  - name          : "Lanee Jung"
     affiliation   : "1"
@@
 Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979].
-Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
+Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredrickson1998swimsuit].
 We don't know about women-on-women interpersonal objectification.
@@
 ```
-Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus non-observable ways.
+Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredrickson1998swimsuit; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus non-observable ways.
 The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.

### 2020-07-27 Final_Manuscript.tex
fixed reference

@@
             pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
-            pdfauthor={Randi L. Garcia, Kat Kyuchukova, \& Asha Hinson},
+            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Lanee Jung},
             pdfkeywords={keywords},
@@
     \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
-Kyuchukova\textsuperscript{1}, \& Asha Hinson\textsuperscript{1}}
+Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \& Lanee
+Jung\textsuperscript{1}}
     \date{}
@@
 
-OUTLINE - Introduction: Objectification theory says stuff. Recently
-we've learned about interpersonal objectification but we only know it
-about mixed gender. We know women objectify each other, but what about
-in interpersonal interactions? - Self-objectification - SSO versus TSO -
-Does this process of self-objectification also lead women to objectify
-other women? - Women objectifying other women - Lots of evidence, but we
-don't know if this happens interpersonally - Interpersonal
-objectifcation research is a whole thing now, but there are no studies
-(or theoretical models) that include women-on-women interpersonal
-objectification processes. - Relationships and objectification - Both
-romantic relationships and relationships in general have been studies in
-the context of objectification, but neither of these literatures have
-investigated specifically same-gender relationships. - Authenticity
-paragraph? - Current Study - Alternative predictions
-
-Roberts and Fredrickson (1997)\enquote{s Objectification Theory,
-suggests that women are objectified in interpersonal encounters, and
-that the effect might be strongest from men, but possibly also from
-women. Psychological researchers studying the sexual objectification of
-women, and the resulting self-objectification that follows, have in
-recent years explored the interpersonal process of the objectification -
-self-objectification link. For exmaple, in a face-to-face mixed-gender
+Roberts and Fredrickson (1997) Objectification Theory, suggests that
+women are objectified in interpersonal encounters, and that the effect
+might be strongest from men, but possibly also from women. Psychological
+researchers studying the sexual objectification of women, and the
+resulting self-objectification that follows, have in recent years
+explored the interpersonal process of the objectification -
+self-objectification link. For example, in a face-to-face mixed-gender
 dyadic study, Garcia, Earnshaw, and Quinn (2016) found that men's
-reported objectificaiton of their female interaction partner during an
-interaction was associated with increased sefl-objectification reported
+reported objectification of their female interaction partner during an
+interaction was associated with increased self-objectification reported
 by their partner. Gervais, Sáez, Riemer, and Klein (2020) has reviewed
@@
 the the process in a theoretical model called the SIMO, but this model
-is only relevant for mixed-gender encouters. Although there is ample
+is only relevant for mixed-gender encounters. Although there is ample
 evidence that women objectify other women (Loughnan et al., 2015a; Puvia
@@
 negative consequences as being objectified by a male interaction
-partner? For example, perhaps women could be amplifying each others}
+partner? For example, perhaps women could be amplifying each others'
 self-objectification as they get ready to go out for the night,
@@
 
+\subsection{Self-Objectification}\label{self-objectification}
+
 Self-objectification is a multidimensional process that accounts for the
 cognitive mechanism that translates experiences of sexualization at the
-cultural level to psychological (e.g., anxiety, self-esteem,
-authenticity, motivational states) and behavioral (cognitive
-performance, body monitoring) features of mental health and well-being
-at the individual level (Calogero, Tantleff-Dunn, \& Thompson, 2011;
-Moradi \& Huang, 2008). Calogero et al. (2011) proposes that the
-construct of self-objectification can be conceptualized as a learned
-trait. Furthermore, it can also be elicited momentarily, through the
-media, for example, with sexualized images in movies and magazines,
-which can lead to a state of self-objectification (Calogero et al.,
-2011, Moradi and Huang (2008)). Being objectified by another person and
-possessing trait-level self-objectification (TSO) may interact to
-influence experiences of feeling like a body, or state
-self-objectification (SSO) (CITE swimsuit sweater, Garcia et al., 2016).
-Does this habit self-objectification lead women to also objectify other
-women, possibly to compare oneself?
+cultural level (Loughnan et al., 2015a) to psychological (e.g., anxiety,
+self-esteem, authenticity, motivational states) and behavioral
+(cognitive performance, body monitoring) features of mental health and
+well-being at the individual level (Calogero, Tantleff-Dunn, \&
+Thompson, 2011; Moradi \& Huang, 2008). Calogero et al. (2011) proposes
+that the construct of self-objectification can be conceptualized as a
+learned trait. Furthermore, it can also be elicited momentarily, through
+the media, for example, with sexualized images in movies and magazines,
+which can lead to a state of self-objectification (Bernard, Legrand, \&
+Klein, 2018; Calogero et al., 2011; Moradi \& Huang, 2008). Being
+objectified by another person and possessing trait-level
+self-objectification (TSO) may interact to influence experiences of
+feeling like a body, or state self-objectification (SSO) (B. L.
+Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998, Garcia et al.
+(2016)). Does this habit self-objectification lead women to also
+objectify other women, possibly to compare oneself?
+
+\subsection{Women Objectifying Women}\label{women-objectifying-women}
 
@@
 
+\subsection{Interpersonal
+Objectification}\label{interpersonal-objectification}
+
 SIMO model and literature review (Gervais et al., 2020). Studies have
 shown that within social encounters women are gazed at more than men
-(Briton \& Hall, 1995, CITE saguy skype study, calogero video walking
-study), often times feel \enquote{looked at} within interpersonal
-interactions (Argyle \& Williams, 1969), and will more than likely
-internalize the objectifying gaze on physical self (Young, 1979).
-Moreover, perhaps the most adverse effect of objectifying treatment is
-that it effectively socializes girls and women to treat themselves as
-objects to be looked at and evaluated, an effect termed
-self-objectification (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972;
-L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge, 1998). We don't know
-about women-on-women interpersonal objectification. What might be
-different?
+(Briton \& Hall, 1995), often times feel \enquote{looked at} within
+interpersonal interactions (Argyle \& Williams, 1969; Miles-McLean et
+al., 2015), and will more than likely internalize the objectifying gaze
+on physical self (Puvia \& Vaes, 2013; Young, 1979). Moreover, perhaps
+the most adverse effect of objectifying treatment is that it effectively
+socializes girls and women to treat themselves as objects to be looked
+at and evaluated, an effect termed self-objectification (Bartky, 1990;
+Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et al., 1998). We
+don't know about women-on-women interpersonal objectification. What
+might be different?
 
@@
 prime among women (Sanchez \& Broccoli, 2008) because in our culture
-women need to look attractive to obtain and maintain successfuol
-relationship, thus, the ``college relationships condition may highten
+women need to look attractive to obtain and maintain successful
+relationship, thus, the ``college relationships condition may heighten
 self-objectification and the evaluation of other women in a sexualized
@@
 relationships. A recent study has investigated the effect of
-self-objectification on the reduction of relationship biulding skills in
+self-objectification on the reduction of relationship building skills in
 general (including same-sex friendships) {[}CITE PWQ paper I reviewed,
@@
 decrease in concentration and impairment in female cognitive performance
-(D. M. Quinn, Chaudoir, \& Kallen, 2011).
-
-MAYBE SEPARATE PARAGRAPH ABOUT AUTHENTICITY LINK SPECIFICALLY. And how
-woman-woman interpersonal objectificaiton preocesses might diverge from
-this process. {[}again CITE PWQ paper I reviewed, Yoder editor{]}.
+(Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn, Chaudoir, \& Kallen,
+2011). Both romantic relationships and relationships in general have
+been studies in the context of objectification, but neither of these
+literatures have investigated specifically same-gender relationships.
+
+There is evidence that the experience of state self-objectification in
+mixed-gender contexts (stranger and romantic) and within the self in any
+moment (trying on a swimsuit) has negative consequences, but what about
+in the context of interaction with other women? Is the
+self-objectification experience in mixed-gender interactions the same as
+that experienced in same-gender interactions? The ample research
+demonstrating that the male gaze has a particularly detrimental effect
+would suggest no (Gay \& Castano, 2010; Gervais, Vescio, \& Allen, 2011;
+Saguy, Quinn, F Dovidio, \& Pratto, 2010, Calogero (2004)). Women do
+objectify other women (Harsey \& Zurbriggen, 2020; Loughnan et al.,
+2015a; Puvia \& Vaes, 2013), but when they do it, does it lead to
+self-objectification in the same way men's objectification of women does
+(Garcia et al., 2016)? If so, does the self-objectification experienced
+in these same-gender interactions have the same negative consequences
+for authenticity in that ineraction?
+
+\subsection{Interpersonal Objectification and
+Authenticity}\label{interpersonal-objectification-and-authenticity}
+
+There is some evidence that reduced authenticity is a consequence of
+self-objectification in the moment {[}Garcia et al. (2016); again CITE
+PWQ paper I reviewed, Yoder editor{]}. This link has been justified by
+the literature on stigmatized-stigmatizer interactions, viewing the
+experience of being objectified in an interaction as an identity threat
+situation. When a woman is objectified by a man, and then experiences
+self-objectification, this intergroup encounter might trigger identitiy
+threat, but is the same negative consequence present when a woman is
+objectified by another woman? woman-woman interpersonal objectification
+processes might diverge from this process. One the one hand, she may not
+be having the same negative consequences the cascade from situations
+that threated group-based identity (Deaux \& Major, 1987; Dovidio, Hebl,
+Richeson, \& Shelton, 2006; M. R. Hebl \& Dovidio, 2005), but feeling
+like a body, rather than a full human, in an interaction may be enough
+to reduce feelings of authenticity and social competence, regardless of
+the gender of the objectifyer {[}Tolman, Impett, Tracy, and Michael
+(2006); PWQ paper I reviewed, Yoder editor{]}.
+
+\subsection{The Current Study}\label{the-current-study}
 
@@
 evaluate other women's potential as romantic partners--indeed, women may
-be unfortunutely used to thinking this way about themselves, and we
+be unfortunately used to thinking this way about themselves, and we
 suspect other women.
@@
 To assess state self-objectification, we used an average of two items
-from Saguy, Quinn, F Dovidio, and Pratto (2010) that were also used in
-Garcia et al. (2016). Participants were asked to rank how much they
-agreed with the following statements: \enquote{During the interaction I
-felt more like a body than a full self} and \enquote{I felt more like a
-body than as a real person in the interaction}. Originally, Saguy et al.
-(2010) used 3 items, but in both samples the reliability of the scale
-was higher once the third item was removed, so we chose to only use the
-first two for our measure of SSO, leaving us with a reliable scale
-(\(\alpha\) = 0.84 for Sample 1, and \(\alpha\) = 0.85 for Sample 2.)
+from Saguy et al. (2010) that were also used in Garcia et al. (2016).
+Participants were asked to rank how much they agreed with the following
+statements: \enquote{During the interaction I felt more like a body than
+a full self} and \enquote{I felt more like a body than as a real person
+in the interaction}. Originally, Saguy et al. (2010) used 3 items, but
+in both samples the reliability of the scale was higher once the third
+item was removed, so we chose to only use the first two for our measure
+of SSO, leaving us with a reliable scale (\(\alpha\) = 0.84 for Sample
+1, and \(\alpha\) = 0.85 for Sample 2.)
 
@@
 Trait self-objectification (TSO) was assessed using the
-Self-Objectification Questionnaire (L. Fredrickson et al., 1998; M. Noll
-\& L. Fredrickson, 1998), which evaluates the extent to which
-individuals view their bodies in observable versus nonobservable ways.
+Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; M.
+Noll \& L. Fredrickson, 1998), which evaluates the extent to which
+individuals view their bodies in observable versus non-observable ways.
 The questionnaire asked participants to rank order both appearance and
@@
 testing the relationship between state-other objectification and SSO,
-and how SSO in turn, affecs feelings of inauthenticity during the
+and how SSO in turn, affects feelings of inauthenticity during the
 interaction. In addition, we will also test if the effect of
@@
 women who are high in trait self-objectification, as in Garcia et al.
-(2016). Further, we will investigate the realtionships between
+(2016). Further, we will investigate the relationships between
 experiencing interaction inauthenticity and relationship agency, career
@@
 our dyadic analyses using multilevel modeling. Dyadic analyses for
-distingishable dyads (e.g., mixed-gender interacting pairs) is more
-natural in Structual Equation Modeling (SEM) than it is for
+distinguishable dyads (e.g., mixed-gender interacting pairs) is more
+natural in Structural Equation Modeling (SEM) than it is for
 indistinguishable dayds (e.g., same-gender interacting pairs) (Garcia,
 Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
-this asymmetry is that, due to the arbitrary distinctions made bewteen
+this asymmetry is that, due to the arbitrary distinctions made between
 \enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads,
@@
 covariances, endogenous intercepts, and exogenous means) for
-indistinguishable dyads but these equality contraints should not then be
-considered in the degrees of freedom calculations for fit estimations
+indistinguishable dyads but these equality constraints should not then
+be considered in the degrees of freedom calculations for fit estimations
 (Olsen \& Kenny, 2006). Further, Olsen and Kenny (2006) detail how a new
@@
 dyadic multilevel modeling (MLM) to test all relationships and mediation
-paterns. The online supplementary materials contains analysis using SEM.
-See Ledermann and Kenny (2017) for a more complete discussion of the
-considerations for using SEM versus MLM for dyadic analysis.
+patterns. The online supplementary materials contains analysis using
+SEM. See Ledermann and Kenny (2017) for a more complete discussion of
+the considerations for using SEM versus MLM for dyadic analysis.
 
@@
 sample, involves using the Actor-Partner Independence Model (APIM)
-approch for each outcome variable (i.e., endogenous variable in
+approach for each outcome variable (i.e., endogenous variable in
 Figure~\ref{fig:2016figure}). Thus, we ran five APIM's to test all the
@@
 is designated as \enquote{actor} and who is designated as
-\enquote{partner} is arbitrary. Recall that the indistinguiahble nature
+\enquote{partner} is arbitrary. Recall that the indistinguishable nature
 of the dyads in the current study led us to choose the MLM approach over
@@
 
-The correaltions between study variables is similar across samples. The
-realibialities for the study scales were also equivalent. (Note that the
+The correlations between study variables is similar across samples. The
+reliabilities for the study scales were also equivalent. (Note that the
 two samples were two small to conduct formal measurement equivalence
@@
 effect of other-objectification on SSO in the current all-women sample
-was statistically signficant, \emph{b} = 0.29, \emph{SE} = 0.12,
-\emph{p} = .019, replicating Garcia et al. (2016)'s fiding. One's own
+was statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12,
+\emph{p} = .019, replicating Garcia et al. (2016)'s finding. One's own
 other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
@@
 two of which were interaction specific authenticity items, we also
-estimated the pairwise correlations bewteen SSO and all these items
+estimated the pairwise correlations between SSO and all these items
 individually. They were all small, ranging from only -0.01 to -0.14.
@@
 partner's other objectification and interaction authenticity, after
-finding no relationship bewteen SSO and authencity, we also tested if
+finding no relationship between SSO and authenticity, we also tested if
 the partner's other objectification had a direct effect on authenticity,
@@
 
-Lastly, althought there was no evidence that SSO was related to
+Lastly, although there was no evidence that SSO was related to
 interaction authenticity in the current sample, we tested if interaction
 authenticity (composite of nine items) had effects on cognitive
-performace, career aspirations, and relationship agency, as it did in
-Garcia et al. (2016). We again used MLM and thus, these efefcts were
+performance, career aspirations, and relationship agency, as it did in
+Garcia et al. (2016). We again used MLM and thus, these effects were
 tested in three separate models. There was no significant effect of
@@
 SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25,
-\emph{p} = .872, and no direct effect of partner's other objectificaiton
-on cognifitve performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
+\emph{p} = .872, and no direct effect of partner's other objectification
+on cognitive performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
 .962. There was no direct effect of SSO on career aspirations, \emph{b}
 = 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of
-partner's other objectificaiton on career aspirations, \emph{b} = -0.06,
+partner's other objectification on career aspirations, \emph{b} = -0.06,
 \emph{SE} = 0.07, \emph{p} = .378. There was no direct effect of SSO on
 relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} =
-.659, and no direct effect of partner's other objectificaiton on
+.659, and no direct effect of partner's other objectification on
 relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.
@@
 Empirical evidence illustrates how women continue to be objects of
-interpersonal discrimination and expereince daily sexist hassles (Swim,
+interpersonal discrimination and experience daily sexist hassles (Swim,
 Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
@@
 external validity of the notions of self-objectification and how the
-operalization of self-objectification may be improved.
+operationalization of self-objectification may be improved.
 
@@
 
+\hypertarget{ref-bernard2018bodies}{}
+Bernard, P., Legrand, S., \& Klein, O. (2018). From bodies to blame:
+Exposure to sexually objectifying media increases tolerance toward
+sexual harassment. \emph{Psychology of Popular Media Culture},
+\emph{7}(2), 99.
+
 \hypertarget{ref-briton1995}{}
@@
 
+\hypertarget{ref-calogero2004test}{}
+Calogero, R. M. (2004). A test of objectification theory: The effect of
+the male gaze on appearance concerns in college women. \emph{Psychology
+of Women Quarterly}, \emph{28}(1), 16--21.
+
 \hypertarget{ref-calogero2011}{}
@@
 \url{https://CRAN.R-project.org/package=xtable}
+
+\hypertarget{ref-deaux1987putting}{}
+Deaux, K., \& Major, B. (1987). Putting gender into context: An
+interactive model of gender-related behavior. \emph{Psychological
+Review}, \emph{94}(3), 369.
+
+\hypertarget{ref-dovidio2006nonverbal}{}
+Dovidio, J. F., Hebl, M., Richeson, J. A., \& Shelton, J. N. (2006).
+Nonverbal communication, race, and intergroup interaction.
 
@@
 
+\hypertarget{ref-fredrickson1998swimsuit}{}
+Fredrickson, B. L., Roberts, T.-A., Noll, S. M., Quinn, D. M., \&
+Twenge, J. M. (1998). That swimsuit becomes you: Sex differences in
+self-objectification, restrained eating, and math performance.
+\emph{Journal of Personality and Social Psychology}, \emph{75}(1), 269.
+
 \hypertarget{ref-R-irr}{}
@@
 
+\hypertarget{ref-gay2010my}{}
+Gay, R. K., \& Castano, E. (2010). My body or my mind: The impact of
+state and trait objectification on women's cognitive resources.
+\emph{European Journal of Social Psychology}, \emph{40}(5), 695--703.
+
 \hypertarget{ref-gervais2020social}{}
@@
 
+\hypertarget{ref-gervais2011you}{}
+Gervais, S. J., Vescio, T. K., \& Allen, J. (2011). When what you see is
+what you get: The consequences of the objectifying gaze for women and
+men. \emph{Psychology of Women Quarterly}, \emph{35}(1), 5--17.
+
 \hypertarget{ref-harsey2020men}{}
@@
 \emph{Self and Identity}, 1--8.
+
+\hypertarget{ref-hebl2005promoting}{}
+Hebl, M. R., \& Dovidio, J. F. (2005). Promoting the ``social'' in the
+examination of social stigmas. \emph{Personality and Social Psychology
+Review}, \emph{9}(2), 156--182.
 
@@
 
+\hypertarget{ref-kahalon2018don}{}
+Kahalon, R., Shnabel, N., \& Becker, J. C. (2018). ``Don't bother your
+pretty little head'' appearance compliments lead to improved mood but
+impaired cognitive performance. \emph{Psychology of Women Quarterly},
+\emph{42}(2), 136--150.
+
 \hypertarget{ref-R-ggformula}{}
@@
 \url{https://CRAN.R-project.org/package=ggformula}
-
-\hypertarget{ref-fredricksonetal1998}{}
-L. Fredrickson, B., Roberts, T.-A., M. Noll, S., Quinn, D., \& Twenge,
-J. (1998). That swimsuit becomes you: Sex differences in
-self-objedification, restrained eating, and math performance.
-\emph{Journal of Personality and Social Psychology}, \emph{75}, 269--84.
-doi:\href{https://doi.org/10.1037/0022-3514.75.1.269}{10.1037/0022-3514.75.1.269}
 
@@
 and Social Psychology Bulletin}, \emph{46}(2), 243--257.
+
+\hypertarget{ref-miles2015stop}{}
+Miles-McLean, H., Liss, M., Erchull, M. J., Robertson, C. M., Hagerman,
+C., Gnoleba, M. A., \& Papp, L. J. (2015). ``Stop looking at me!''
+interpersonal sexual objectification as a source of insidious trauma.
+\emph{Psychology of Women Quarterly}, \emph{39}(3), 363--374.
 
@@
 
+\hypertarget{ref-tolman2006looking}{}
+Tolman, D. L., Impett, E. A., Tracy, A. J., \& Michael, A. (2006).
+Looking good, sounding good: Femininity ideology and adolescent girls'
+mental health. \emph{Psychology of Women Quarterly}, \emph{30}(1),
+85--95.
+
 \hypertarget{ref-R-ggplot2}{}

### 2020-07-27 Final_Manuscript.Rmd
added some to discussion

@@
 In the measures section that follows we refer to them as Sample 1 and Sample 2.
+Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
 Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US.
-The description of the samples section below contains more detail about equivalence analyses to support the decision to combine these two samples.
+More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college.
+Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
+Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
+Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
+For consistency, we limited participant data to same sex female pairs at the two colleges.
+
+```{r demographics}
+#favstats(~TSO_A, data=clarksmith_women)
+#favstats(~a2pSOO_A, data=clarksmith_women)
+#favstats(~howbody_avg_A, data=clarksmith_women)
+#favstats(~relag_A, data=clarksmith_women)
+#favstats(~careerasp_A, data=clarksmith_women)
+#favstats(~authenticity_A, data=clarksmith_women)
+#favstats(~trigram_score_A, data=clarksmith_women)
+
+#Mean and SD of age of sample
+mean_age <- favstats(~age_A, data = clarksmith_women)$mean
+sd_age <- favstats(~age_A, data = clarksmith_women)$sd
+tally(clarksmith_women$race_A == clarksmith_women$race_P)
+
+#Calculating race percentages
+tally(~race_A, data = clarksmith_women)  #Note that we can add "format = percentage" and not need to calculate
+percentage_black <- 6/(6+18+31+6+3)*100
+percent_asian <- 18/(6+18+31+6+3)*100
+percent_white <- 31/(6+18+31+6+3)*100
+percent_latinx <- 6/(6+18+31+6+3)*100
+percent_other <- 3/(6+18+31+6+3)*100
+tally(~sexor_A, data=clarksmith_women)
+percent_straight <-(41/64)*100
+percent_queer <- (3+8+5)/64*100
+tally(~gender_A, data=clarksmith_women)
+
+table(clarksmith_women$race_A, clarksmith_women$race_P)
+samerace_white <- 16/2 #divide by 2 since table is people, not pairs
+samerace_minority <- (6+2)/2
+mixedrace_white <- 2+10+2+1
+mixedrace_minority <- 1+2+1+1
+
+test <- clarksmith_women %>%
+  filter(race_A==3, race_A!=race_P)
+
+tally(~gender, data=clark_final)
+tally(~gender, data=smith_final)
+```
+
+Due these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
+These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
+The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
+There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
+The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
+`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
 
@@
 Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.
-
-###Description of the Samples
-Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
-More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college.
-Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
-Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
-Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
-For consistency, we limited participant data to same sex female pairs at the two colleges.
-
-```{r demographics}
-#favstats(~TSO_A, data=clarksmith_women)
-#favstats(~a2pSOO_A, data=clarksmith_women)
-#favstats(~howbody_avg_A, data=clarksmith_women)
-#favstats(~relag_A, data=clarksmith_women)
-#favstats(~careerasp_A, data=clarksmith_women)
-#favstats(~authenticity_A, data=clarksmith_women)
-#favstats(~trigram_score_A, data=clarksmith_women)
-
-#Mean and SD of age of sample
-mean_age <- favstats(~age_A, data = clarksmith_women)$mean
-sd_age <- favstats(~age_A, data = clarksmith_women)$sd
-tally(clarksmith_women$race_A == clarksmith_women$race_P)
-
-#Calculating race percentages
-tally(~race_A, data = clarksmith_women)  #Note that we can add "format = percentage" and not need to calculate
-percentage_black <- 6/(6+18+31+6+3)*100
-percent_asian <- 18/(6+18+31+6+3)*100
-percent_white <- 31/(6+18+31+6+3)*100
-percent_latinx <- 6/(6+18+31+6+3)*100
-percent_other <- 3/(6+18+31+6+3)*100
-tally(~sexor_A, data=clarksmith_women)
-percent_straight <-(41/64)*100
-percent_queer <- (3+8+5)/64*100
-tally(~gender_A, data=clarksmith_women)
-
-table(clarksmith_women$race_A, clarksmith_women$race_P)
-samerace_white <- 16/2 #divide by 2 since table is people, not pairs
-samerace_minority <- (6+2)/2
-mixedrace_white <- 2+10+2+1
-mixedrace_minority <- 1+2+1+1
-
-test <- clarksmith_women %>%
-  filter(race_A==3, race_A!=race_P)
-
-tally(~gender, data=clark_final)
-tally(~gender, data=smith_final)
-```
-
-Due these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
-These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
-The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
-There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
-The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
-`r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
 
@@
 #Discussion
+The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women only.
+Although past reserach has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if this other-objectification by women is related to self-objectification in women.
+As hypothesized, the current study did find a significant relationship bewteen a woman's partner's report of having objectified her and her own post-interaction feelings of self-objectification.
+
+Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and felt inauthenticity [@garcia2016objectification].
+In addition, we found to evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations.
+Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes.
+This is somewhat suprising given the extant research on interpersonal other-ojectification and cognitive functioning [CITE that logel study], and the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; CITE; CITE; CITE].
+This lack of evidence could potentially signal diverging processs between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [CITE; CITE; CITE], and perhaps the self-objectification experienced within an interaction with a women is not as detrimental as the self-objectificatoin experienced within an interaction with a man.
+This lack of evidence could also be due to the relatively small sample size.
+
+What we did find, however,
 

### 2020-07-28 Final_Manuscript.Rmd
added more Zotero references, comments on intro

--- 2020-07-27 Final_Manuscript.Rmd
@@
 @robertsfredrickson Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
-Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link.
+Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link (CITE INTERPERSONAL PROCESS LINKS).
 For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men's reported objectification of their female interaction partner during an interaction was associated with increased self-objectification reported by their partner.
@@
 @calogero2011 proposes that the construct of self-objectification can be conceptualized as a learned trait.
-Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@bernard2018bodies; @calogero2011; @moradi2008].
+Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines [@morry2001magazine], which can lead to a state of self-objectification [@bernard2018bodies; @calogero2011; @moradi2008].
 Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [@fredrickson1998swimsuit, @garcia2016objectification].
@@
 ##Women Objectifying Women
+Past research has focused on men’s objectifying behaviors, with little attention to the role that women may also play in enacting objectification of women.
+@hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well (THEY DIDN'T DETERMINE THIS IN PERSON).
 Some studies have found that women objectify other women to a greater extent than they objectify men [@loughnan2015exploring].
@@
 @harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women participants, although men scored high than women on a measure of belief that objectification of women is natural for men.
+ASK RANDI-WE KNOW OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN (Gervais, Vescio, & Allen, 2011; Moradi & Huang, 2008; Saguy, Quinn, Dovidio, & Pratto, 2010)...MENTION THAT...HOWEVER DOES WOMEN OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?...STILL TRYING TO FIGURE THAT OUT?
+ADDITIONALLY @strelan2005women FOUND THAT THE MORE WOMEN SELF-OBJECTIFY, THE MORE THEY OBJECTIFY OTHER WOMEN.
 
@@
 Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because in our culture women need to look attractive to obtain and maintain successful relationship, thus, the "college relationships condition may heighten self-objectification and the evaluation of other women in a sexualized way.
+Among heterosexual male and female college students, self- objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
 Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds].
@@
 Women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], but when they do it, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
-If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that ineraction?
+If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that interaction?
 
@@
 There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor].
-This link has been justified by the literature on stigmatized-stigmatizer interactions, viewing the experience of being objectified in an interaction as an identity threat situation.
+This link has been justified by the literature on stigmatized-stigmatizer interactions (CITE LITERATURE DIDN'T COME ACROSS THIS), viewing the experience of being objectified in an interaction as an identity threat situation (MAYBE CITE MILES-MCLEAN PAPER "STOP LOOKING AT ME!").
 When a woman is objectified by a man, and then experiences self-objectification, this intergroup encounter might trigger identitiy threat, but is the same negative consequence present when a woman is objectified by another woman?
@@
 One the one hand, she may not be having the same negative consequences the cascade from situations that threated group-based identity [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in an interaction may be enough to reduce feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
+I DONT KNOW WHERE THIS PAPER IS?
+ASK RANDI ABOUT IDENTITY_THREAT PAPERS
 
@@
 ###Sample Characteristics
-The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008].
+The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008], although more current work examines objectification from a cross-cultural framework [@loughnan2015, @wollast2020cultural].
 Because “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015].
-Further, sexualzing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014; @bury2016].
+Further, sexualizing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014; @bury2016].
 Considering the fact that the average mean age of the investigated participants of this current study was 18.85 years, research among younger and older individuals is needed, especially because self-objectification may change over time [@robertsfredrickson].
-It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexulizing content.
+It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.
 

### 2020-07-28 Final_Manuscript.Rmd
added comments on intro

@@
 @robertsfredrickson Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
-Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link (CITE INTERPERSONAL PROCESS LINKS).
+Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link (CITE INTERPERSONAL PROCESS LINKS LITERATURE).
 For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men's reported objectification of their female interaction partner during an interaction was associated with increased self-objectification reported by their partner.

### 2020-07-28 Final_Manuscript.tex
lab meeting changes

@@
 explored the interpersonal process of the objectification -
-self-objectification link. For example, in a face-to-face mixed-gender
-dyadic study, Garcia, Earnshaw, and Quinn (2016) found that men's
-reported objectification of their female interaction partner during an
-interaction was associated with increased self-objectification reported
-by their partner. Gervais, Sáez, Riemer, and Klein (2020) has reviewed
-the literature on interpersonal self-objectification and has organized
-the the process in a theoretical model called the SIMO, but this model
-is only relevant for mixed-gender encounters. Although there is ample
-evidence that women objectify other women (Loughnan et al., 2015a; Puvia
-\& Vaes, 2013), there is currently no studies investigating the process
-of interpersonal objectification same-gender interactions. Does
-objectification by a female interaction partner have the same downstream
-negative consequences as being objectified by a male interaction
-partner? For example, perhaps women could be amplifying each others'
+self-objectification link (CITE INTERPERSONAL PROCESS LINKS LITERATURE).
+For example, in a face-to-face mixed-gender dyadic study, Garcia,
+Earnshaw, and Quinn (2016) found that men's reported objectification of
+their female interaction partner during an interaction was associated
+with increased self-objectification reported by their partner. Gervais,
+Sáez, Riemer, and Klein (2020) has reviewed the literature on
+interpersonal self-objectification and has organized the the process in
+a theoretical model called the SIMO, but this model is only relevant for
+mixed-gender encounters. Although there is ample evidence that women
+objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013),
+there is currently no studies investigating the process of interpersonal
+objectification same-gender interactions. Does objectification by a
+female interaction partner have the same downstream negative
+consequences as being objectified by a male interaction partner? For
+example, perhaps women could be amplifying each others'
 self-objectification as they get ready to go out for the night,
@@
 learned trait. Furthermore, it can also be elicited momentarily, through
-the media, for example, with sexualized images in movies and magazines,
-which can lead to a state of self-objectification (Bernard, Legrand, \&
-Klein, 2018; Calogero et al., 2011; Moradi \& Huang, 2008). Being
-objectified by another person and possessing trait-level
-self-objectification (TSO) may interact to influence experiences of
-feeling like a body, or state self-objectification (SSO) (B. L.
-Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998, Garcia et al.
-(2016)). Does this habit self-objectification lead women to also
-objectify other women, possibly to compare oneself?
+the media, for example, with sexualized images in movies and magazines
+(Morry \& Staska, 2001), which can lead to a state of
+self-objectification (Bernard, Legrand, \& Klein, 2018; Calogero et al.,
+2011; Moradi \& Huang, 2008). Being objectified by another person and
+possessing trait-level self-objectification (TSO) may interact to
+influence experiences of feeling like a body, or state
+self-objectification (SSO) (B. L. Fredrickson, Roberts, Noll, Quinn, \&
+Twenge, 1998, Garcia et al. (2016)). Does this habit
+self-objectification lead women to also objectify other women, possibly
+to compare oneself?
 
@@
 
+Past research has focused on men's objectifying behaviors, with little
+attention to the role that women may also play in enacting
+objectification of women. Hill and Fischer (2008) assessed women's
+experiences of objectification from men separately from women's
+experiences of objectification from women and found that women may be
+socialized not only to see themselves as objects but perhaps to see
+other women as objects as well (THEY DIDN'T DETERMINE THIS IN PERSON).
 Some studies have found that women objectify other women to a greater
@@
 participants, although men scored high than women on a measure of belief
-that objectification of women is natural for men.
+that objectification of women is natural for men. ASK RANDI-WE KNOW
+OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN
+(Gervais, Vescio, \& Allen, 2011; Moradi \& Huang, 2008; Saguy, Quinn,
+Dovidio, \& Pratto, 2010)\ldots{}MENTION THAT\ldots{}HOWEVER DOES WOMEN
+OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?\ldots{}STILL
+TRYING TO FIGURE THAT OUT? ADDITIONALLY Strelan and Hargreaves (2005)
+FOUND THAT THE MORE WOMEN SELF-OBJECTIFY, THE MORE THEY OBJECTIFY OTHER
+WOMEN.
 
@@
 self-objectification and the evaluation of other women in a sexualized
-way. Researchers have also studied interpersonal objectification and
-self-objectification in romantic relationships (Strelan \& Pagoudis,
-2018). Evidence is mixed, and women can sometimes have positive outcomes
-from appearance valuation within the context of an established romantic
-relationship and they experience less SSO after appearance comments
-within romantic relationships (Meltzer, 2020), less is known about first
-dates. But this literature is also only about heterosexual
-relationships. A recent study has investigated the effect of
-self-objectification on the reduction of relationship building skills in
-general (including same-sex friendships) {[}CITE PWQ paper I reviewed,
-Yoder editor{]}. Empirical evidence reveals that objectification
-manifests through inauthenticity in romantic relationships (Brunell et
-al., 2010), adverse attitudes in regard to career aspirations, and a
-decrease in concentration and impairment in female cognitive performance
-(Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn, Chaudoir, \& Kallen,
-2011). Both romantic relationships and relationships in general have
-been studies in the context of objectification, but neither of these
-literatures have investigated specifically same-gender relationships.
+way. Among heterosexual male and female college students, self-
+objectification has been found to be positively associated with the
+extent to which they objectify their romantic partners (Zurbriggen,
+Ramsey, \& Jaworski, 2011). Researchers have also studied interpersonal
+objectification and self-objectification in romantic relationships
+(Strelan \& Pagoudis, 2018). Evidence is mixed, and women can sometimes
+have positive outcomes from appearance valuation within the context of
+an established romantic relationship and they experience less SSO after
+appearance comments within romantic relationships (Meltzer, 2020), less
+is known about first dates. But this literature is also only about
+heterosexual relationships. A recent study has investigated the effect
+of self-objectification on the reduction of relationship building skills
+in general (including same-sex friendships) {[}CITE PWQ paper I
+reviewed, Yoder editor{]}. Empirical evidence reveals that
+objectification manifests through inauthenticity in romantic
+relationships (Brunell et al., 2010), adverse attitudes in regard to
+career aspirations, and a decrease in concentration and impairment in
+female cognitive performance (Kahalon, Shnabel, \& Becker, 2018; D. M.
+Quinn, Chaudoir, \& Kallen, 2011). Both romantic relationships and
+relationships in general have been studies in the context of
+objectification, but neither of these literatures have investigated
+specifically same-gender relationships.
 
@@
 in these same-gender interactions have the same negative consequences
-for authenticity in that ineraction?
+for authenticity in that interaction?
 
@@
 PWQ paper I reviewed, Yoder editor{]}. This link has been justified by
-the literature on stigmatized-stigmatizer interactions, viewing the
-experience of being objectified in an interaction as an identity threat
-situation. When a woman is objectified by a man, and then experiences
-self-objectification, this intergroup encounter might trigger identitiy
-threat, but is the same negative consequence present when a woman is
-objectified by another woman? woman-woman interpersonal objectification
-processes might diverge from this process. One the one hand, she may not
-be having the same negative consequences the cascade from situations
-that threated group-based identity (Deaux \& Major, 1987; Dovidio, Hebl,
-Richeson, \& Shelton, 2006; M. R. Hebl \& Dovidio, 2005), but feeling
-like a body, rather than a full human, in an interaction may be enough
-to reduce feelings of authenticity and social competence, regardless of
-the gender of the objectifyer {[}Tolman, Impett, Tracy, and Michael
-(2006); PWQ paper I reviewed, Yoder editor{]}.
+the literature on stigmatized-stigmatizer interactions (CITE LITERATURE
+DIDN'T COME ACROSS THIS), viewing the experience of being objectified in
+an interaction as an identity threat situation (MAYBE CITE MILES-MCLEAN
+PAPER \enquote{STOP LOOKING AT ME!}). When a woman is objectified by a
+man, and then experiences self-objectification, this intergroup
+encounter might trigger identitiy threat, but is the same negative
+consequence present when a woman is objectified by another woman?
+woman-woman interpersonal objectification processes might diverge from
+this process. One the one hand, she may not be having the same negative
+consequences the cascade from situations that threated group-based
+identity (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \& Shelton,
+2006; M. R. Hebl \& Dovidio, 2005), but feeling like a body, rather than
+a full human, in an interaction may be enough to reduce feelings of
+authenticity and social competence, regardless of the gender of the
+objectifyer {[}Tolman, Impett, Tracy, and Michael (2006); PWQ paper I
+reviewed, Yoder editor{]}. I DONT KNOW WHERE THIS PAPER IS? ASK RANDI
+ABOUT IDENTITY\_THREAT PAPERS
 
@@
 this study. In the measures section that follows we refer to them as
-Sample 1 and Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal
-arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
-women's liberal arts college in the northeast US. The description of the
-samples section below contains more detail about equivalence analyses to
-support the decision to combine these two samples.
+Sample 1 and Sample 2. Thirty-two previously unacquainted
+self-identifying female-sex dyads (64 total participants) from two
+liberal arts institutions in the Northeast of the United States
+participated in this study. Sample 1 (\emph{N =} 24) is from a co-ed
+liberal arts college in the northeast US and Sample 2 (\emph{N =} 40) is
+from a women's liberal arts college in the northeast US. More
+specifically, twelve of the pairs, which derived from Sample 1, were
+students at a co-ed liberal arts college, while the remaining twenty
+pairs who came from Sample 2 attended a women's liberal arts college.
+Initially, data was collected from same-sex and mixed-sex dyads that
+comprised of male and female gendered individuals. Sample 1 originally
+consisted of twenty-two pairs, twelve men and thirty-two women.
+Twenty-three pairs made up of forty-three women and one man, as well as
+two participants who did not identify with either gender category,
+formed Sample 2. For consistency, we limited participant data to same
+sex female pairs at the two colleges.
+
+Due these similarities across samples in regard to correlation patterns
+between significant variables within this study, the two datasets were
+combined. These participants were mostly first-year college students,
+with an average age of 18.85 (SD = 1.04). The sample was 48.44\%
+White/European American, 9.38\% Black/African-American, 28.12\%
+Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
+8 White/White pairs and 4 same race racial minority pairs, for a total
+of 12 same-race pairs. The remaining 20 were mixed race pairs, of which
+15 were White/racial minority pairings and 5 were cross-racial minority
+group pairs. 64.06\% of the sample identified as heterosexual, and 25\%
+identified as gay, lesbian or bisexual.
 
@@
 TSO.
-
-\subsubsection{Description of the
-Samples}\label{description-of-the-samples}
-
-Thirty-two previously unacquainted self-identifying female-sex dyads (64
-total participants) from two liberal arts institutions in the Northeast
-of the United States participated in this study. More specifically,
-twelve of the pairs, which derived from Sample 1, were students at a
-co-ed liberal arts college, while the remaining twenty pairs who came
-from Sample 2 attended a women's liberal arts college. Initially, data
-was collected from same-sex and mixed-sex dyads that comprised of male
-and female gendered individuals. Sample 1 originally consisted of
-twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs
-made up of forty-three women and one man, as well as two participants
-who did not identify with either gender category, formed Sample 2. For
-consistency, we limited participant data to same sex female pairs at the
-two colleges.
-
-Due these similarities across samples in regard to correlation patterns
-between significant variables within this study, the two datasets were
-combined. These participants were mostly first-year college students,
-with an average age of 18.85 (SD = 1.04). The sample was 48.44\%
-White/European American, 9.38\% Black/African-American, 28.12\%
-Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
-8 White/White pairs and 4 same race racial minority pairs, for a total
-of 12 same-race pairs. The remaining 20 were mixed race pairs, of which
-15 were White/racial minority pairings and 5 were cross-racial minority
-group pairs. 64.06\% of the sample identified as heterosexual, and 25\%
-identified as gay, lesbian or bisexual.
 
@@
 
+The current study tested whether the model of interpersonal
+objectification and state self-objectification (SSO) used in Garcia et
+al. (2016) replicates in a same-gender dyadic sample of women only.
+Although past reserach has found that women do objectify other women
+(Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes,
+2013), this is the first study to test if this other-objectification by
+women is related to self-objectification in women. As hypothesized, the
+current study did find a significant relationship bewteen a woman's
+partner's report of having objectified her and her own post-interaction
+feelings of self-objectification.
+
+Where the results of the current study diverge most notably from the
+results of studies testing interpersonal objectification among
+mixed-gender dyads is the lack of evidence for relationships between SSO
+and felt inauthenticity (Garcia et al., 2016). In addition, we found to
+evidence of \emph{direct} or \emph{indirect} relationships between SSO
+and cognitive functioning, relationship agency, and career aspirations.
+Nor was there evidence of \emph{direct} or \emph{indirect} relationships
+between other-objectification and any of these outcomes. This is
+somewhat suprising given the extant research on interpersonal
+other-ojectification and cognitive functioning {[}CITE that logel
+study{]}, and the plentiful evidence linking SSO and cognitive
+functioning {[}B. L. Fredrickson et al. (1998); CITE; CITE; CITE{]}.
+This lack of evidence could potentially signal diverging processs
+between women's experiences with interpersonal objectification from men
+and interpersonal objectification from women. There is quite a bit of
+evidence suggesting that the male gaze is particularly detrimental
+{[}CITE; CITE; CITE{]}, and perhaps the self-objectification experienced
+within an interaction with a women is not as detrimental as the
+self-objectificatoin experienced within an interaction with a man. This
+lack of evidence could also be due to the relatively small sample size.
+
+What we did find, however,
+
 As stated previously, we did not find a significant effect between actor
@@
 et al., 2015b), and research on objectification conducted outside of
-Western or Westernized countries is scarce (Moradi \& Huang, 2008).
-Because \enquote{bodies exist within social and cultural contexts, and
-hence are also constructed through sociocultural practices and
-discourses} (Roberts \& Fredrickson, 1997, p. 174), it is important to
-consider how diverse social identities within unique cultural contexts
-may inform sexual objectification phenomenon to test the cross-cultural
-applicability of theoretical frameworks (Loughnan et al., 2015b).
-Further, sexualzing experiences and self-objectification are thought to
-begin a very young age, and thus, researchers have only recently begun
-to examine such experiences among children (Bury, Tiggemann, \& Slater,
-2016; e.g., Holland \& Haslam, 2016; Jongenelis, Byrne, \& Pettigrew,
-2014). Considering the fact that the average mean age of the
-investigated participants of this current study was 18.85 years,
-research among younger and older individuals is needed, especially
-because self-objectification may change over time (Roberts \&
+Western or Westernized countries is scarce (Moradi \& Huang, 2008),
+although more current work examines objectification from a
+cross-cultural framework (Loughnan et al., 2015b, Wollast et al.
+(2020)). Because \enquote{bodies exist within social and cultural
+contexts, and hence are also constructed through sociocultural practices
+and discourses} (Roberts \& Fredrickson, 1997, p. 174), it is important
+to consider how diverse social identities within unique cultural
+contexts may inform sexual objectification phenomenon to test the
+cross-cultural applicability of theoretical frameworks (Loughnan et al.,
+2015b). Further, sexualizing experiences and self-objectification are
+thought to begin a very young age, and thus, researchers have only
+recently begun to examine such experiences among children (Bury,
+Tiggemann, \& Slater, 2016; e.g., Holland \& Haslam, 2016; Jongenelis,
+Byrne, \& Pettigrew, 2014). Considering the fact that the average mean
+age of the investigated participants of this current study was 18.85
+years, research among younger and older individuals is needed,
+especially because self-objectification may change over time (Roberts \&
 Fredrickson, 1997). It may be valuable to question the extent to which
 children, adolescents, or emerging adults of different races or
-ethnicities are exposed to varied amounts of sexulizing content.
+ethnicities are exposed to varied amounts of sexualizing content.
 
@@
 
+\hypertarget{ref-hill2008examining}{}
+Hill, M. S., \& Fischer, A. R. (2008). Examining objectification theory:
+Lesbian and heterosexual women's experiences with sexual-and
+self-objectification. \emph{The Counseling Psychologist}, \emph{36}(5),
+745--776.
+
 \hypertarget{ref-holland2016}{}
@@
 \emph{Psychology of Women Quarterly}, \emph{32}(4), 377--398.
+
+\hypertarget{ref-morry2001magazine}{}
+Morry, M. M., \& Staska, S. L. (2001). Magazine exposure:
+Internalization, self-objectification, eating attitudes, and body
+satisfaction in male and female university students. \emph{Canadian
+Journal of Behavioural Science/Revue Canadienne Des Sciences Du
+Comportement}, \emph{33}(4), 269.
 
@@
 
+\hypertarget{ref-wollast2020cultural}{}
+Wollast, R., Riemer, A. R., Gervais, S. J., Grigoryan, L., Bernard, P.,
+\& Klein, O. (2020). How cultural orientation and self-compassion shape
+objectified body consciousness for women from america, belgium, russia,
+and thailand. \emph{Self and Identity}, 1--21.
+
 \hypertarget{ref-R-knitr}{}
@@
 
+\hypertarget{ref-zurbriggen2011self}{}
+Zurbriggen, E. L., Ramsey, L. R., \& Jaworski, B. K. (2011). Self-and
+partner-objectification in romantic relationships: Associations with
+media consumption and relationship satisfaction. \emph{Sex Roles},
+\emph{64}(7-8), 449--462.
+
 \endgroup

### 2020-07-29 Final_Manuscript.Rmd
added to discussion

@@
 The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women only.
-Although past reserach has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if this other-objectification by women is related to self-objectification in women.
+Although past reserach has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if this interpersonal other-objectification by women is related to self-objectification in women.
 As hypothesized, the current study did find a significant relationship bewteen a woman's partner's report of having objectified her and her own post-interaction feelings of self-objectification.
+That is, there was a significant partner effect of other-objectification on SSO.
+This effect extends the equivalent relationship found in mixed-gender interactions to the context of same-gender interactions between women.
+Thus, it could be that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also results in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
 
-Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and felt inauthenticity [@garcia2016objectification].
-In addition, we found to evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations.
+As is the case in all correlational studies, we cannot be sure in the causal direction.
+It could be that women's SSO causes them to be objectified by their interaction partner.
+This interpretation holds up given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO this relates to being objectified by one's partner.
+However, Objectification Thoery [@robertsfredrickson] as past experimental studies [@saguyetal2010; CITE] suggest that the causal direction is indeed in the direction whereby other-objectification causes SSO.
+Although, importantly, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.
+
+Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and felt inauthenticity.
+In addition, we found no evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations.
 Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes.
-This is somewhat suprising given the extant research on interpersonal other-ojectification and cognitive functioning [CITE that logel study], and the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; CITE; CITE; CITE].
+This is somewhat suprising given the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification].
 This lack of evidence could potentially signal diverging processs between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
 There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [CITE; CITE; CITE], and perhaps the self-objectification experienced within an interaction with a women is not as detrimental as the self-objectificatoin experienced within an interaction with a man.
-This lack of evidence could also be due to the relatively small sample size.
+We need to be careful not to interpret a null result as evidence of no relationship.
 
-What we did find, however,
+The lack of evidence for a relationship between SSO and interaction authenticity is surprising and again, should not be interpreted as evidence of no realtionship---this lack of statistical significance could also be due to the relatively small sample size in the current study.
+The estimate of this relationship was very small, but in the negative direction, as anticipated.
+If it is the case that there is a smaller, or weaker, connection between women's feelings of SSO in interactions with other women then in interactions with men, models of interpersonal objectification, like the SIMO, could be extended by including inauthenticity as a potential mediated factor in decisions to continue objectifying interactions.
+Further, gender of the objectifyer/interaction partner could also be added to the model to help extend our understanding of under what circumstances other-objectificant and SSO have negative concequences for women.
 
-As stated previously, we did not find a significant effect between actor SSO and actor authenticity, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to relationship inauthenticity.
-However, we did observe a significant partner effect of objectification on actor self-objectification, which does align with our hypothesis that theorized objectification from other women can also cause women to self-objectify just as they do within interactions between male-female pairs.
-
-##Sexism and Sexual Discrimination
-Sexism has recently been found to be related to the objectification of women, but not men, for both men and women [@harsey2020men].
-Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and experience daily sexist hassles [@swimetal].
-One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
-Sexual objectification occurs with both “endless variety and monotonous similarity,” and is thus mediated by unique combinations of race, ethnicity, sexuality, age, and class [@fredricksonetal2011; @rubin1975, cited in @frasernicholson1989, p.
-28].
-Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
+Although we did not fid a connection bewteen SSO and authenticity we did find significant relationships in
 
@@
 It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.
+
+###Sexual Objectification and the Objectifyer's Gender
+
+LANEE PLEASE ADD THESE AS BIBTEX CITATIONS
+
+Previous research has found that when compared to heterosexual women, lesbian women report less concern with physical appearance [Siever, 1994; Strong, Williamson, Netemeyer, & Geer, 2000], less internalization of sociocultural beauty norms [Bergeron & Senn, 1998; Share & Mintz, 2002], and less self-objectification [Brownlow, 1997; Noffsinger-Frazier, 2004].
+None of these studies examined the relationship between self-objectification and experiences of cultural sexual objectification.
+Thus, it is unclear whether lesbians indeed experience similar levels of cultural sexual objectification but internalize them less than heterosexual women do.
+Based on theoretical literature suggesting that lesbians may internalize cultural sexual objectification less than do heterosexual women [e.g., Brown, 1987; Dworkin, 1988; Pitman, 1999; Rothblum, 1994; Siever, 1994; Striegel-Moore et al., 1986]
+
+However, since both men and women are socialized in a culture that sexually objectifies women, both men and women may come to internalize this socialization and sexually objectify women.
+Women come to experience not only themselves, but other women as well, through the “eyes of the indeterminate observer” [Kaschak, 1992, p.
+178].
+Indeed, recent research has found that the more women self- objectify, the more they objectify other women [CITE], although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women [Strelan & Hargreaves, 2005].
+
+###Sexism and Sexual Discrimination
+Sexism has recently been found to be related to the objectification of women, but not men, for both men and women [@harsey2020men].
+Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and experience daily sexist hassles [@swimetal].
+One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
+Sexual objectification occurs with both “endless variety and monotonous similarity,” and is thus mediated by unique combinations of race, ethnicity, sexuality, age, and class [@fredricksonetal2011; @rubin1975, cited in @frasernicholson1989, p.
+28].
+Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
 
@@
 The results of this study demonstrate the complex and ambivalent nature of female sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
+We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity.
 

### 2020-07-29 Final_Manuscript.Rmd
Added .bib citations to #Limitations and Future Directions. Fixed CITE, CITE, CITE's

@@
 Is the self-objectification experience in mixed-gender interactions the same as that experienced in same-gender interactions?
-The ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my].
+The ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose].
 Women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], but when they do it, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
@@
 This interpretation holds up given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO this relates to being objectified by one's partner.
-However, Objectification Thoery [@robertsfredrickson] as past experimental studies [@saguyetal2010; CITE] suggest that the causal direction is indeed in the direction whereby other-objectification causes SSO.
+However, Objectification Theory [@robertsfredrickson] as past experimental studies [@saguyetal2010; CITE] suggest that the causal direction is indeed in the direction whereby other-objectification causes SSO.
 Although, importantly, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.
@@
 This lack of evidence could potentially signal diverging processs between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [CITE; CITE; CITE], and perhaps the self-objectification experienced within an interaction with a women is not as detrimental as the self-objectificatoin experienced within an interaction with a man.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as detrimental as the self-objectificatoin experienced within an interaction with a man.
 We need to be careful not to interpret a null result as evidence of no relationship.
@@
 
-LANEE PLEASE ADD THESE AS BIBTEX CITATIONS
-
-Previous research has found that when compared to heterosexual women, lesbian women report less concern with physical appearance [Siever, 1994; Strong, Williamson, Netemeyer, & Geer, 2000], less internalization of sociocultural beauty norms [Bergeron & Senn, 1998; Share & Mintz, 2002], and less self-objectification [Brownlow, 1997; Noffsinger-Frazier, 2004].
-None of these studies examined the relationship between self-objectification and experiences of cultural sexual objectification.
+Previous research has found that when compared to heterosexual women, lesbian women report less concern with physical appearance [@siever1994sexual; @strong2000eating], and less self-objectification [@brownlow1998relationship; @noffsinger2004objectification].
+However none of these studies examined the relationship between self-objectification and experiences of sexual objectification.
 Thus, it is unclear whether lesbians indeed experience similar levels of cultural sexual objectification but internalize them less than heterosexual women do.
-Based on theoretical literature suggesting that lesbians may internalize cultural sexual objectification less than do heterosexual women [e.g., Brown, 1987; Dworkin, 1988; Pitman, 1999; Rothblum, 1994; Siever, 1994; Striegel-Moore et al., 1986]
+Consistent with previous reseach @hill2008examining determined lesbians existed less physical appearance concerns compared to heterosexual women, however there was no difference found that lesbian women self-objectify less than heterosexual women and they did not find that sexual orientation moderates the relationshiotn between sexual objecitifcantion and self-objectification This contradicts older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women [@brown1987lesbians; @pitman1999body; @lum1994lesbians; @siever1994sexual]
 
 However, since both men and women are socialized in a culture that sexually objectifies women, both men and women may come to internalize this socialization and sexually objectify women.
-Women come to experience not only themselves, but other women as well, through the “eyes of the indeterminate observer” [Kaschak, 1992, p.
-178].
-Indeed, recent research has found that the more women self- objectify, the more they objectify other women [CITE], although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women [Strelan & Hargreaves, 2005].
+Indeed, recent research has found that the more women self-objectify, the more they objectify other women [@loughnan2015exploring; @puvia2013being], although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women [@strelan2005women].
 

### 2020-08-01 Final_Manuscript.Rmd
added accent on e (I think)

@@
     affiliation   : "1"
-  - name          : "Lanee Jung"
+  - name          : "Laneé Jung"
     affiliation   : "1"

### 2020-08-03 Final_Manuscript.tex
Worked on discussion

@@
             pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
-            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Lanee Jung},
+            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
             pdfkeywords={keywords},
@@
     \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
-Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \& Lanee
+Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \& Laneé
 Jung\textsuperscript{1}}
@@
 would suggest no (Gay \& Castano, 2010; Gervais, Vescio, \& Allen, 2011;
-Saguy, Quinn, F Dovidio, \& Pratto, 2010, Calogero (2004)). Women do
-objectify other women (Harsey \& Zurbriggen, 2020; Loughnan et al.,
-2015a; Puvia \& Vaes, 2013), but when they do it, does it lead to
-self-objectification in the same way men's objectification of women does
-(Garcia et al., 2016)? If so, does the self-objectification experienced
-in these same-gender interactions have the same negative consequences
-for authenticity in that interaction?
+Saguy, Quinn, F Dovidio, \& Pratto, 2010, Calogero (2004); Yilmaz \&
+Bozo, 2019). Women do objectify other women (Harsey \& Zurbriggen, 2020;
+Loughnan et al., 2015a; Puvia \& Vaes, 2013), but when they do it, does
+it lead to self-objectification in the same way men's objectification of
+women does (Garcia et al., 2016)? If so, does the self-objectification
+experienced in these same-gender interactions have the same negative
+consequences for authenticity in that interaction?
 
@@
 (Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes,
-2013), this is the first study to test if this other-objectification by
-women is related to self-objectification in women. As hypothesized, the
+2013), this is the first study to test if \emph{interpersonal}
+other-objectification by women is related to state self-objectification
+in their woman-identified interaction partners. As hypothesized, the
 current study did find a significant relationship bewteen a woman's
 partner's report of having objectified her and her own post-interaction
-feelings of self-objectification.
+feelings of self-objectification. That is, there was a significant
+partner effect of other-objectification on SSO. This effect extends the
+equivalent relationship found in mixed-gender interactions to the
+context of same-gender interactions between women. Thus, it could be
+that it is not only the male gaze, and male other-objectification that
+is related to women's state self-objectification, but being objectified
+by another woman can also results in SSO, at least in the context of a
+scenario where they know they are being evaluated as a potential dating
+partner.
+
+As is the case in all correlational studies, we cannot be sure in the
+causal direction. It could be that women's SSO causes them to be
+objectified by their interaction partner. This interpretation in
+theoreticall interesting given that, in both the Garcia et al. (2016)
+study and in the current study, it is \emph{women's} SSO this relates to
+being objectified by one's partner. However, Objectification Theory
+(Roberts \& Fredrickson, 1997), as well as past experimental studies
+{[}Saguy et al. (2010); CITE{]}, suggest that the causal flow is from
+other-objectification to SSO. Although, importantly, the current study
+found evidence for the partner effect of other-objectification on SSO,
+there was a lack of evidence for the connections between SSO and
+downstream negative consequences.
 
@@
 mixed-gender dyads is the lack of evidence for relationships between SSO
-and felt inauthenticity (Garcia et al., 2016). In addition, we found to
-evidence of \emph{direct} or \emph{indirect} relationships between SSO
-and cognitive functioning, relationship agency, and career aspirations.
-Nor was there evidence of \emph{direct} or \emph{indirect} relationships
-between other-objectification and any of these outcomes. This is
-somewhat suprising given the extant research on interpersonal
-other-ojectification and cognitive functioning {[}CITE that logel
-study{]}, and the plentiful evidence linking SSO and cognitive
-functioning {[}B. L. Fredrickson et al. (1998); CITE; CITE; CITE{]}.
-This lack of evidence could potentially signal diverging processs
-between women's experiences with interpersonal objectification from men
-and interpersonal objectification from women. There is quite a bit of
-evidence suggesting that the male gaze is particularly detrimental
-{[}CITE; CITE; CITE{]}, and perhaps the self-objectification experienced
-within an interaction with a women is not as detrimental as the
-self-objectificatoin experienced within an interaction with a man. This
-lack of evidence could also be due to the relatively small sample size.
-
-What we did find, however,
-
-As stated previously, we did not find a significant effect between actor
-SSO and actor authenticity, which suggests that there is not sufficient
-evidence to support the claim that partner objectification is the cause
-for the diverse range of negative effects related to relationship
-inauthenticity. However, we did observe a significant partner effect of
-objectification on actor self-objectification, which does align with our
-hypothesis that theorized objectification from other women can also
-cause women to self-objectify just as they do within interactions
-between male-female pairs.
-
-\subsection{Sexism and Sexual
-Discrimination}\label{sexism-and-sexual-discrimination}
-
-Sexism has recently been found to be related to the objectification of
-women, but not men, for both men and women (Harsey \& Zurbriggen, 2020).
-Empirical evidence illustrates how women continue to be objects of
-interpersonal discrimination and experience daily sexist hassles (Swim,
-Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
-discrimination women face is the process by which their whole being is
-viewed as a collection of sexualized body parts valued predominantly for
-commodification, a phenomena termed sexual objectification (Bartky,
-1990). Sexual objectification occurs with both \enquote{endless variety
-and monotonous similarity,} and is thus mediated by unique combinations
-of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
-Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
-Nicholson (1989), p.~28). Amid such heterogeneity though,
-\enquote{having a reproductively mature female body} proposed by Roberts
-and Fredrickson (1997) is likely to create a shared vulnerability to
-sexual objectification and a variety of shared negative experiences as a
-result.
+and felt inauthenticity. In addition, we found no evidence of
+\emph{direct} or \emph{indirect} relationships between SSO and cognitive
+functioning, relationship agency, and career aspirations. Nor was there
+evidence of \emph{direct} or \emph{indirect} relationships between
+other-objectification and any of these outcomes. This is somewhat
+suprising given the plentiful evidence linking SSO and cognitive
+functioning (B. L. Fredrickson et al., 1998; Quinn, Chaudoir, \& Kallen,
+2011) and the small, but extant research on interpersonal
+other-ojectification and cognitive functioning (Garcia et al., 2016;
+Logel et al., 2009). This lack of evidence could potentially signal
+diverging processs between women's experiences with interpersonal
+objectification from men and interpersonal objectification from women.
+There is quite a bit of evidence suggesting that the male gaze is
+particularly detrimental (Calogero, 2004; Gervais, Holland, \& Dodd,
+2013; Gervais et al., 2011; Roberts \& Fredrickson, 1997), and perhaps
+the self-objectification experienced within an interaction with a women
+is not as harmful as the self-objectificatoin experienced within an
+interaction with a man. However, as a strong note of caution, we need to
+be careful not to interpret a null result as evidence of no
+relationship.
+
+The lack of evidence for a relationship between SSO and interaction
+authenticity is surprising and again, should not be interpreted as
+evidence of no realtionship. It should be noted that the estimate of
+this relationship was very small, but in the negative direction, as
+anticipated. If it is the case that there is a smaller (i.e., weaker)
+connection between women's feelings of SSO and inauthenticity in
+interactions with other women then in interactions with men, models of
+interpersonal objectification, like the SIMO (Gervais et al., 2020),
+could be extended by including inauthenticity as a potential mediating
+factor in decisions to continue objectifying interactions. Further,
+gender of the objectifyer/interaction partner could also be added to the
+SIMO model to help extend our understanding of under what circumstances
+other-objectification and SSO have negative concequences for women.
+
+Although we did not find a connection bewteen SSO and authenticity we
+did find significant positive relationships between authenticity and
+relationship agency and career aspirations. The relationship between
+authenticity and cognitive functioning was also estimated as positive,
+but it was not statistically signfiicant. Again, due to the lack of
+connection between SSO and authenticity, we found no evidence of
+\emph{indirect} relationships between SSO and these outcome variables.
+This evidence of a relationship between authenticity and the relational
+outcome variables (i.e., relationship agency and career aspirations)
+provides evidence that corrborates past findings that felt authenticity
+in interactions is important for healthy relationship functioning
+{[}Garcia et al. (2016); PWQ paper I reviewed{]}. Just as authenticity
+has been found to be important in intergroup interactions {[}CITE; CITE;
+CITE{]}, we again find more evidence here that distuptions in feelings
+of authenticity can negatively impact relationships beyond the current
+partner. Although the current study did not find a connection between
+authenticity and SSO, this seems theoretically to be a natural
+connection, and more work needs to be done to discover when and how SSO
+leads to inauthenticity in interpersonal objectification situations.
 
@@
 \subsubsection{Sample Characteristics}\label{sample-characteristics}
+
+The sample size was small and combined across two higher education
+institutions.
 
@@
 
+\subsubsection{Sexual Objectification and the Objectifyer's
+Gender}\label{sexual-objectification-and-the-objectifyers-gender}
+
+The current sample contained a mixture of heterosexual and
+non-heterosexual women, but all participants were asked to think about
+and evaluate their partner as a potential data parter. While we think
+that hetereosexual women are indeed able to do this with other women as
+their target---indeed, there is evidence that they might do this readily
+(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---they might be more
+apt to activate social comparison processes (Festinger, 1954) than women
+who are sexually attracted to other women (non-heterosexual women). This
+differential psychological process between women with differing
+sexualities might have served to dampen our ability to detect
+relationships, adding variability.
+
+Previous research has found that when compared to heterosexual women,
+lesbian women report less concern with physical appearance (Siever,
+1994; Strong, Williamson, Netemeyer, \& Geer, 2000), and less
+self-objectification (Brownlow, 1998; Noffsinger-Frazier, 2004). However
+none of these studies examined the relationship between
+self-objectification and experiences of sexual objectification. Thus, it
+is unclear whether lesbians indeed experience similar levels of cultural
+sexual objectification but internalize them less than heterosexual women
+do. Consistent with previous reseach Hill and Fischer (2008) determined
+lesbians existed less physical appearance concerns compared to
+heterosexual women, however there was no difference found that lesbian
+women self-objectify less than heterosexual women and they did not find
+that sexual orientation moderates the relationshiotn between sexual
+objecitifcantion and self-objectification This contradicts older
+theoretical literature that suggests that lesbians internalize cultural
+sexual objectification less than do heterosexual women (Brown, 1987;
+LUM, 1994; Pitman, 1999; Siever, 1994)
+
+However, since both men and women are socialized in a culture that
+sexually objectifies women, both men and women may come to internalize
+this socialization and sexually objectify women. Indeed, recent research
+has found that the more women self-objectify, the more they objectify
+other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013), although not
+to the degree exhibited by men; that is, men were found to objectify
+women significantly more than women objectify other women (Strelan \&
+Hargreaves, 2005).
+
+\subsubsection{Sexism and Sexual
+Discrimination}\label{sexism-and-sexual-discrimination}
+
+Sexism has recently been found to be related to the objectification of
+women, but not men, for both men and women (Harsey \& Zurbriggen, 2020).
+Empirical evidence illustrates how women continue to be objects of
+interpersonal discrimination and experience daily sexist hassles (Swim,
+Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
+discrimination women face is the process by which their whole being is
+viewed as a collection of sexualized body parts valued predominantly for
+commodification, a phenomena termed sexual objectification (Bartky,
+1990). Sexual objectification occurs with both \enquote{endless variety
+and monotonous similarity,} and is thus mediated by unique combinations
+of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
+Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
+Nicholson (1989), p.~28). Amid such heterogeneity though,
+\enquote{having a reproductively mature female body} proposed by Roberts
+and Fredrickson (1997) is likely to create a shared vulnerability to
+sexual objectification and a variety of shared negative experiences as a
+result.
+
 \subsubsection{Measurement}\label{measurement}
@@
 psychological and social consequences of such objectification processes
-on women's social relationships and well-being.
+on women's social relationships and well-being. We did not find a
+significant effect between actor SSO and felt authenticity in the
+interaction, which suggests that there is not sufficient evidence to
+support the claim that partner objectification is the cause for the
+diverse range of negative effects related to interaction inauthenticity.
 
@@
 nonverbal communication. \emph{Sex Roles}, \emph{32}(1-2), 79--90.
+
+\hypertarget{ref-brown1987lesbians}{}
+Brown, L. S. (1987). Lesbians, weight, and eating: New analyses and
+perspectives. \emph{Lesbian Psychologies: Explorations and Challenges},
+294--309.
+
+\hypertarget{ref-brownlow1998relationship}{}
+Brownlow, B. S. (1998). \emph{The relationship between objectification,
+body image disturbances, and disordered eating: Investigating race,
+socioeconomic status, acculturation and self-objectification as
+mediators.} (PhD thesis). ProQuest Information \& Learning.
 
@@
 
+\hypertarget{ref-festinger1954theory}{}
+Festinger, L. (1954). A theory of social comparison processes.
+\emph{Human Relations}, \emph{7}(2), 117--140.
+
 \hypertarget{ref-frasernicholson1989}{}
@@
 
+\hypertarget{ref-gervais2013my}{}
+Gervais, S. J., Holland, A. M., \& Dodd, M. D. (2013). My eyes are up
+here: The nature of the objectifying gaze toward women. \emph{Sex
+Roles}, \emph{69}(11-12), 557--570.
+
 \hypertarget{ref-gervais2020social}{}
@@
 
+\hypertarget{ref-logel2009interacting}{}
+Logel, C., Walton, G. M., Spencer, S. J., Iserman, E. C., Hippel, W.
+von, \& Bell, A. E. (2009). Interacting with sexist men triggers social
+identity threat among female engineers. \emph{Journal of Personality and
+Social Psychology}, \emph{96}(6), 1089.
+
 \hypertarget{ref-loughnan2015exploring}{}
@@
 Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
+
+\hypertarget{ref-lum1994lesbians}{}
+LUM, E. (1994). Lesbians and physical appearance which model applies?
+\emph{Lesbian and Gay Psychology: Theory, Research, and Clinical
+Applications}, \emph{1}, 84.
 
@@
 
+\hypertarget{ref-noffsinger2004objectification}{}
+Noffsinger-Frazier, N. A. (2004). \emph{Objectification theory and
+disordered eating: The impact of feminist identification,
+internalization of sociocultural standards of appearance, and sexual
+orientation}. The University of Memphis.
+
 \hypertarget{ref-olsen2006structural}{}
@@
 \url{https://CRAN.R-project.org/package=nlme}
+
+\hypertarget{ref-pitman1999body}{}
+Pitman, G. E. (1999). Body image, compulsory heterosexuality, and
+internalized homophobia. \emph{Journal of Lesbian Studies}, \emph{3}(4),
+129--139.
 
@@
 
+\hypertarget{ref-quinn2011performance}{}
+Quinn, D. M., Chaudoir, S. R., \& Kallen, R. W. (2011). Performance and
+flow: A review and integration of self-objectification research.
+
 \hypertarget{ref-R-base}{}
@@
 
+\hypertarget{ref-siever1994sexual}{}
+Siever, M. D. (1994). Sexual orientation and gender as factors in
+socioculturally acquired vulnerability to body dissatisfaction and
+eating disorders. \emph{Journal of Consulting and Clinical Psychology},
+\emph{62}(2), 252.
+
 \hypertarget{ref-R-apaTables}{}
@@
 heterosexual relationships. \emph{Sex Roles}, \emph{79}(1-2), 72--82.
+
+\hypertarget{ref-strong2000eating}{}
+Strong, S. M., Williamson, D. A., Netemeyer, R. G., \& Geer, J. H.
+(2000). Eating disorder symptoms and concerns about body differ as a
+function of gender and sexual orientation. \emph{Journal of Social and
+Clinical Psychology}, \emph{19}(2), 240--255.
 
@@
 
+\hypertarget{ref-yilmaz2019whose}{}
+Yilmaz, T., \& Bozo, Ö. (2019). Whose gaze is more objectifying? An
+experimental study of college women's state self-objectification, body
+shame, negative mood, and body dissatisfaction. \emph{Mediterranean
+Journal of Clinical Psychology}, \emph{7}(2).
+
 \hypertarget{ref-young1979}{}

### 2020-08-03 Final_Manuscript.tex
commit

@@
-\documentclass[man]{apa6}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  man]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
   \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
   pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
@@
   pdfkeywords={keywords},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-  \title{Objectification in Action: Self- and Other-Objectification in
-Same-gender Interactions}
-    \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
-Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \& Laneé
-Jung\textsuperscript{1}}
-    \date{}
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \shorttitle{Objectification in Action}
@@
 
+\title{Objectification in Action: Self- and Other-Objectification in Same-gender Interactions}
+\author{Randi L. Garcia\textsuperscript{1, 2}, Kat Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \& Laneé Jung\textsuperscript{1}}
+\date{}
+
 \authornote{
@@
 Correspondence concerning this article should be addressed to Randi L.
-Garcia, 415 Bass Hall, Smith College, Northampton, MA 01060. E-mail:
-\href{mailto:rgarcia@smith.edu}{\nolinkurl{rgarcia@smith.edu}}}
+Garcia, 415 Bass Hall, Smith College, Northampton, MA 01060.
+E-mail: \href{mailto:rgarcia@smith.edu}{\nolinkurl{rgarcia@smith.edu}}}
 
 \abstract{
-Empirical evidence has only found links between objectification,
-self-objectification, and negative outcomes for woman within
-interpersonal interactions between male-female pairs. The purpose of the
-present study was to extend past research and consider the relationships
-between such valuable phenomena and their effects on authenticity within
-interactions between female pairs. Woman were brought into the
-laboratory and interacted in same-sex dyads. Dyadic analysis was
-utilized to detect whether partners' objectification of each other
-affected state self-objectification, and the resulting feelings of
-comfort and authenticity during the interaction. After the interaction,
-participants completed a questionnaire which measured many constructs
-including cognitive performance, career aspirations, and relationship
-agency. Results revealed no significant relationship between
-self-objectification and authenticity. Further, although there were
-significantly negative effects on career aspirations and relationship
-agency resulting from a lack of relationship authenticity, there was no
-evidence that this is due to feelings of sexual objectification. The
-significant partner effect of objectification on actor
-self-objectification suggests that women being objectified by other
-women still results in feelings of self-objectification, and such
-research has powerful implications for the ways that women interact in
-both sexual and non-sexual settings. AUTHOR NOTE: mention Clark trigram
-coders Hannah et al.
+Empirical evidence has only found links between objectification, self-objectification, and negative outcomes for woman within interpersonal interactions between male-female pairs.
+The purpose of the present study was to extend past research and consider the relationships between such valuable phenomena and their effects on authenticity within interactions between female pairs.
+Woman were brought into the laboratory and interacted in same-sex dyads.
+Dyadic analysis was utilized to detect whether partners' objectification of each other affected state self-objectification, and the resulting feelings of comfort and authenticity during the interaction.
+After the interaction, participants completed a questionnaire which measured many constructs including cognitive performance, career aspirations, and relationship agency.
+Results revealed no significant relationship between self-objectification and authenticity.
+Further, although there were significantly negative effects on career aspirations and relationship agency resulting from a lack of relationship authenticity, there was no evidence that this is due to feelings of sexual objectification.
+The significant partner effect of objectification on actor self-objectification suggests that women being objectified by other women still results in feelings of self-objectification, and such research has powerful implications for the ways that women interact in both sexual and non-sexual settings.
+AUTHOR NOTE: mention Clark trigram coders Hannah et al.~
 
@@
 
-Roberts and Fredrickson (1997) Objectification Theory, suggests that
-women are objectified in interpersonal encounters, and that the effect
-might be strongest from men, but possibly also from women. Psychological
-researchers studying the sexual objectification of women, and the
-resulting self-objectification that follows, have in recent years
-explored the interpersonal process of the objectification -
-self-objectification link (CITE INTERPERSONAL PROCESS LINKS LITERATURE).
-For example, in a face-to-face mixed-gender dyadic study, Garcia,
-Earnshaw, and Quinn (2016) found that men's reported objectification of
-their female interaction partner during an interaction was associated
-with increased self-objectification reported by their partner. Gervais,
-Sáez, Riemer, and Klein (2020) has reviewed the literature on
-interpersonal self-objectification and has organized the the process in
-a theoretical model called the SIMO, but this model is only relevant for
-mixed-gender encounters. Although there is ample evidence that women
-objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013),
-there is currently no studies investigating the process of interpersonal
-objectification same-gender interactions. Does objectification by a
-female interaction partner have the same downstream negative
-consequences as being objectified by a male interaction partner? For
-example, perhaps women could be amplifying each others'
-self-objectification as they get ready to go out for the night,
-\emph{before} the theoretical encounters with men outlined in Gervais et
-al. (2020) occur.
-
-\subsection{Self-Objectification}\label{self-objectification}
-
-Self-objectification is a multidimensional process that accounts for the
-cognitive mechanism that translates experiences of sexualization at the
-cultural level (Loughnan et al., 2015a) to psychological (e.g., anxiety,
-self-esteem, authenticity, motivational states) and behavioral
-(cognitive performance, body monitoring) features of mental health and
-well-being at the individual level (Calogero, Tantleff-Dunn, \&
-Thompson, 2011; Moradi \& Huang, 2008). Calogero et al. (2011) proposes
-that the construct of self-objectification can be conceptualized as a
-learned trait. Furthermore, it can also be elicited momentarily, through
-the media, for example, with sexualized images in movies and magazines
-(Morry \& Staska, 2001), which can lead to a state of
-self-objectification (Bernard, Legrand, \& Klein, 2018; Calogero et al.,
-2011; Moradi \& Huang, 2008). Being objectified by another person and
-possessing trait-level self-objectification (TSO) may interact to
-influence experiences of feeling like a body, or state
-self-objectification (SSO) (B. L. Fredrickson, Roberts, Noll, Quinn, \&
-Twenge, 1998, Garcia et al. (2016)). Does this habit
-self-objectification lead women to also objectify other women, possibly
-to compare oneself?
-
-\subsection{Women Objectifying Women}\label{women-objectifying-women}
-
-Past research has focused on men's objectifying behaviors, with little
-attention to the role that women may also play in enacting
-objectification of women. Hill and Fischer (2008) assessed women's
-experiences of objectification from men separately from women's
-experiences of objectification from women and found that women may be
-socialized not only to see themselves as objects but perhaps to see
-other women as objects as well (THEY DIDN'T DETERMINE THIS IN PERSON).
-Some studies have found that women objectify other women to a greater
-extent than they objectify men (Loughnan et al., 2015a). Women objectify
-(dehumanized) sexualized targets presented as images (Puvia \& Vaes,
-2013), but we know next to nothing about interpersonal sexual
-objectification among women and what the immediate effects might be.
-Further, do women objectify non-sexualized women they are interacting
-with? What might be different for same-gender interactions? Harsey and
-Zurbriggen (2020) found that self-objectification was related to the
-objectification of women to a similar degree for men and women
-participants, although men scored high than women on a measure of belief
-that objectification of women is natural for men. ASK RANDI-WE KNOW
-OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN
-(Gervais, Vescio, \& Allen, 2011; Moradi \& Huang, 2008; Saguy, Quinn,
-Dovidio, \& Pratto, 2010)\ldots{}MENTION THAT\ldots{}HOWEVER DOES WOMEN
-OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?\ldots{}STILL
-TRYING TO FIGURE THAT OUT? ADDITIONALLY Strelan and Hargreaves (2005)
-FOUND THAT THE MORE WOMEN SELF-OBJECTIFY, THE MORE THEY OBJECTIFY OTHER
-WOMEN.
-
-\subsection{Interpersonal
-Objectification}\label{interpersonal-objectification}
-
-SIMO model and literature review (Gervais et al., 2020). Studies have
-shown that within social encounters women are gazed at more than men
-(Briton \& Hall, 1995), often times feel \enquote{looked at} within
-interpersonal interactions (Argyle \& Williams, 1969; Miles-McLean et
-al., 2015), and will more than likely internalize the objectifying gaze
-on physical self (Puvia \& Vaes, 2013; Young, 1979). Moreover, perhaps
-the most adverse effect of objectifying treatment is that it effectively
-socializes girls and women to treat themselves as objects to be looked
-at and evaluated, an effect termed self-objectification (Bartky, 1990;
-Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et al., 1998). We
-don't know about women-on-women interpersonal objectification. What
-might be different?
-
-Self-objectification has been found to occur after a mere relationship
-prime among women (Sanchez \& Broccoli, 2008) because in our culture
-women need to look attractive to obtain and maintain successful
-relationship, thus, the ``college relationships condition may heighten
-self-objectification and the evaluation of other women in a sexualized
-way. Among heterosexual male and female college students, self-
-objectification has been found to be positively associated with the
-extent to which they objectify their romantic partners (Zurbriggen,
-Ramsey, \& Jaworski, 2011). Researchers have also studied interpersonal
-objectification and self-objectification in romantic relationships
-(Strelan \& Pagoudis, 2018). Evidence is mixed, and women can sometimes
-have positive outcomes from appearance valuation within the context of
-an established romantic relationship and they experience less SSO after
-appearance comments within romantic relationships (Meltzer, 2020), less
-is known about first dates. But this literature is also only about
-heterosexual relationships. A recent study has investigated the effect
-of self-objectification on the reduction of relationship building skills
-in general (including same-sex friendships) {[}CITE PWQ paper I
-reviewed, Yoder editor{]}. Empirical evidence reveals that
-objectification manifests through inauthenticity in romantic
-relationships (Brunell et al., 2010), adverse attitudes in regard to
-career aspirations, and a decrease in concentration and impairment in
-female cognitive performance (Kahalon, Shnabel, \& Becker, 2018; D. M.
-Quinn, Chaudoir, \& Kallen, 2011). Both romantic relationships and
-relationships in general have been studies in the context of
-objectification, but neither of these literatures have investigated
-specifically same-gender relationships.
-
-There is evidence that the experience of state self-objectification in
-mixed-gender contexts (stranger and romantic) and within the self in any
-moment (trying on a swimsuit) has negative consequences, but what about
-in the context of interaction with other women? Is the
-self-objectification experience in mixed-gender interactions the same as
-that experienced in same-gender interactions? The ample research
-demonstrating that the male gaze has a particularly detrimental effect
-would suggest no (Gay \& Castano, 2010; Gervais, Vescio, \& Allen, 2011;
-Saguy, Quinn, F Dovidio, \& Pratto, 2010, Calogero (2004); Yilmaz \&
-Bozo, 2019). Women do objectify other women (Harsey \& Zurbriggen, 2020;
-Loughnan et al., 2015a; Puvia \& Vaes, 2013), but when they do it, does
-it lead to self-objectification in the same way men's objectification of
-women does (Garcia et al., 2016)? If so, does the self-objectification
-experienced in these same-gender interactions have the same negative
-consequences for authenticity in that interaction?
-
-\subsection{Interpersonal Objectification and
-Authenticity}\label{interpersonal-objectification-and-authenticity}
-
-There is some evidence that reduced authenticity is a consequence of
-self-objectification in the moment {[}Garcia et al. (2016); again CITE
-PWQ paper I reviewed, Yoder editor{]}. This link has been justified by
-the literature on stigmatized-stigmatizer interactions (CITE LITERATURE
-DIDN'T COME ACROSS THIS), viewing the experience of being objectified in
-an interaction as an identity threat situation (MAYBE CITE MILES-MCLEAN
-PAPER \enquote{STOP LOOKING AT ME!}). When a woman is objectified by a
-man, and then experiences self-objectification, this intergroup
-encounter might trigger identitiy threat, but is the same negative
-consequence present when a woman is objectified by another woman?
-woman-woman interpersonal objectification processes might diverge from
-this process. One the one hand, she may not be having the same negative
-consequences the cascade from situations that threated group-based
-identity (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \& Shelton,
-2006; M. R. Hebl \& Dovidio, 2005), but feeling like a body, rather than
-a full human, in an interaction may be enough to reduce feelings of
-authenticity and social competence, regardless of the gender of the
-objectifyer {[}Tolman, Impett, Tracy, and Michael (2006); PWQ paper I
-reviewed, Yoder editor{]}. I DONT KNOW WHERE THIS PAPER IS? ASK RANDI
-ABOUT IDENTITY\_THREAT PAPERS
-
-\subsection{The Current Study}\label{the-current-study}
-
-In the current study, we sought to examine what occurs during an
-interaction in which one or both partners are objectifying each other,
-similarly to Garcia et al. (2016), but between same-sex female
-interpersonal interactions. Moreover, the current study uses a
-face-to-face interaction paradigm and dyadic data analysis techniques to
-examine the effects for both women simultaneously. We expected to
-replicate the results found in Garcia et al. (2016). We predicted that
-being objectified by one's interaction partner would lead to
-self-objectification, which in turn would lead to feelings of
-inauthenticity, then reduced feelings of agency in romantic
-relationships, reduced career aspiration, and reduced cognitive
-performance. Specifically, we expected to find a positive relationship
-between other-objectification by one's partner and state
-self-objectification. We also expect to find a negative relationship
-between self-state objectification and interaction authenticity, and
-that interaction authenticity will be positively related to cognitive
-performance, relationship agency, and career aspirations.
-
-Puvia and Vaes (2013) would alternatively predict that women's tendency
-to self-objectify (TSO) leads them to objectify other women
-(\ldots{}well, dehumanize a sexualized woman, but also Strelan and
-Hargreaves (2005) would predict the TSO-\textgreater{}SOO link and
-Harsey and Zurbriggen (2020) too), and this is mediated by the woman's
-own state self-objectification (SSO). So we also tested this as a
-possible alternative model.
-
-\section{Methods}\label{methods}
-
-\subsection{Procedure}\label{procedure}
-
-The procedure used was identical to that in Garcia et al. (2016), except
-for the instructions that the participants were given. In brief, that
-methodology is that each participant arrived at the laboratory and were
-then led into separate cubicles to prevent any communication between the
-participants before the interaction. In addition, each participant was
-screened for prior acquaintance to confirm that they had not met prior
-to the study. They were asked to sign the consent form to participate,
-and the study was described as follows: \enquote{This is a study looking
-at how students form different types of relationships at college.} A
-prompt on the computer screen told the participants that they were
-assigned to the \enquote{College Relationships} condition and gave the
-following instructions:
+Roberts \& Fredrickson (1997) Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
+Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link (CITE INTERPERSONAL PROCESS LINKS LITERATURE).
+For example, in a face-to-face mixed-gender dyadic study, Garcia, Earnshaw, \& Quinn (2016) found that men's reported objectification of their female interaction partner during an interaction was associated with increased self-objectification reported by their partner.
+Gervais, Sáez, Riemer, \& Klein (2020) has reviewed the literature on interpersonal self-objectification and has organized the the process in a theoretical model called the SIMO, but this model is only relevant for mixed-gender encounters.
+Although there is ample evidence that women objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013), there is currently no studies investigating the process of interpersonal objectification same-gender interactions.
+Does objectification by a female interaction partner have the same downstream negative consequences as being objectified by a male interaction partner?
+For example, perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, \emph{before} the theoretical encounters with men outlined in Gervais et al.
+(2020) occur.
+
+\#\#Self-Objectification
+Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level (Loughnan et al., 2015a) to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level (Calogero, Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008).
+Calogero et al.
+(2011) proposes that the construct of self-objectification can be conceptualized as a learned trait.
+Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines (Morry \& Staska, 2001), which can lead to a state of self-objectification (Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \& Huang, 2008).
+Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) (Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998, p.
+Garcia et al.
+(2016)).
+Does this habit self-objectification lead women to also objectify other women, possibly to compare oneself?
+
+\#\#Women Objectifying Women
+Past research has focused on men's objectifying behaviors, with little attention to the role that women may also play in enacting objectification of women.
+Hill \& Fischer (2008) assessed women's experiences of objectification from men separately from women's experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well (THEY DIDN'T DETERMINE THIS IN PERSON).
+Some studies have found that women objectify other women to a greater extent than they objectify men (Loughnan et al., 2015a).
+Women objectify (dehumanized) sexualized targets presented as images (Puvia \& Vaes, 2013), but we know next to nothing about interpersonal sexual objectification among women and what the immediate effects might be.
+Further, do women objectify non-sexualized women they are interacting with?
+What might be different for same-gender interactions?
+Harsey \& Zurbriggen (2020) found that self-objectification was related to the objectification of women to a similar degree for men and women participants, although men scored high than women on a measure of belief that objectification of women is natural for men.
+ASK RANDI-WE KNOW OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN (Gervais, Vescio, \& Allen, 2011; Moradi \& Huang, 2008; Saguy, Quinn, Dovidio, \& Pratto, 2010)\ldots MENTION THAT\ldots HOWEVER DOES WOMEN OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?\ldots STILL TRYING TO FIGURE THAT OUT?
+ADDITIONALLY Strelan \& Hargreaves (2005) FOUND THAT THE MORE WOMEN SELF-OBJECTIFY, THE MORE THEY OBJECTIFY OTHER WOMEN.
+
+\#\#Interpersonal Objectification
+SIMO model and literature review (Gervais et al., 2020).
+Studies have shown that within social encounters women are gazed at more than men (Briton \& Hall, 1995), often times feel \enquote{looked at} within interpersonal interactions (Argyle \& Williams, 1969; Miles-McLean et al., 2015), and will more than likely internalize the objectifying gaze on physical self (Puvia \& Vaes, 2013; Young, 1979).
+Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; Fredrickson et al., 1998).
+We don't know about women-on-women interpersonal objectification.
+What might be different?
+
+Self-objectification has been found to occur after a mere relationship prime among women (Sanchez \& Broccoli, 2008) because in our culture women need to look attractive to obtain and maintain successful relationship, thus, the "college relationships condition may heighten self-objectification and the evaluation of other women in a sexualized way.
+Among heterosexual male and female college students, self- objectification has been found to be positively associated with the extent to which they objectify their romantic partners (Zurbriggen, Ramsey, \& Jaworski, 2011).
+Researchers have also studied interpersonal objectification and self-objectification in romantic relationships (Strelan \& Pagoudis, 2018).
+Evidence is mixed, and women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship and they experience less SSO after appearance comments within romantic relationships (Meltzer, 2020), less is known about first dates.
+But this literature is also only about heterosexual relationships.
+A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) {[}CITE PWQ paper I reviewed, Yoder editor{]}.
+Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships (Brunell et al., 2010), adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance (Kahalon, Shnabel, \& Becker, 2018; D.
+M.
+Quinn et al., 2011).
+Both romantic relationships and relationships in general have been studies in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
+
+There is evidence that the experience of state self-objectification in mixed-gender contexts (stranger and romantic) and within the self in any moment (trying on a swimsuit) has negative consequences, but what about in the context of interaction with other women?
+Is the self-objectification experience in mixed-gender interactions the same as that experienced in same-gender interactions?
+The ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no (Gay \& Castano, 2010; Gervais, Vescio, \& Allen, 2011; Saguy, Quinn, F Dovidio, \& Pratto, 2010, p.
+Calogero (2004); Yilmaz \& Bozo, 2019).
+Women do objectify other women (Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013), but when they do it, does it lead to self-objectification in the same way men's objectification of women does (Garcia et al., 2016)?
+If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that interaction?
+
+\#\#Interpersonal Objectification and Authenticity
+There is some evidence that reduced authenticity is a consequence of self-objectification in the moment {[}Garcia et al.
+(2016); again CITE PWQ paper I reviewed, Yoder editor{]}.
+This link has been justified by the literature on stigmatized-stigmatizer interactions (CITE LITERATURE DIDN'T COME ACROSS THIS), viewing the experience of being objectified in an interaction as an identity threat situation (MAYBE CITE MILES-MCLEAN PAPER \enquote{STOP LOOKING AT ME!}).
+When a woman is objectified by a man, and then experiences self-objectification, this intergroup encounter might trigger identitiy threat, but is the same negative consequence present when a woman is objectified by another woman?
+woman-woman interpersonal objectification processes might diverge from this process.
+One the one hand, she may not be having the same negative consequences the cascade from situations that threated group-based identity (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \& Shelton, 2006; Hebl \& Dovidio, 2005), but feeling like a body, rather than a full human, in an interaction may be enough to reduce feelings of authenticity and social competence, regardless of the gender of the objectifyer {[}Tolman, Impett, Tracy, \& Michael (2006); PWQ paper I reviewed, Yoder editor{]}.
+I DONT KNOW WHERE THIS PAPER IS?
+ASK RANDI ABOUT IDENTITY\_THREAT PAPERS
+
+\#\#The Current Study
+In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to Garcia et al.
+(2016), but between same-sex female interpersonal interactions.
+Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously.
+We expected to replicate the results found in Garcia et al.
+(2016).
+We predicted that being objectified by one's interaction partner would lead to self-objectification, which in turn would lead to feelings of inauthenticity, then reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
+Specifically, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
+We also expect to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
+
+Puvia \& Vaes (2013) would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (\ldots well, dehumanize a sexualized woman, but also Strelan \& Hargreaves (2005) would predict the TSO-\textgreater SOO link and Harsey \& Zurbriggen (2020) too), and this is mediated by the woman's own state self-objectification (SSO).
+So we also tested this as a possible alternative model.
+
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
+
+\#\#Procedure
+The procedure used was identical to that in Garcia et al.
+(2016), except for the instructions that the participants were given.
+In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to prevent any communication between the participants before the interaction.
+In addition, each participant was screened for prior acquaintance to confirm that they had not met prior to the study.
+They were asked to sign the consent form to participate, and the study was described as follows: \enquote{This is a study looking at how students form different types of relationships at college.} A prompt on the computer screen told the participants that they were assigned to the \enquote{College Relationships} condition and gave the following instructions:
 
 \begin{quote}
-There are many types of relationships people form in college. During the
-interaction, please think about your partner's potential as a romantic
-partner. Even if they are not the gender you are attracted to, you can
-still judge their potential as a romantic partner. After the interaction
-you will be asked to evaluate how dateable your partner is. In other
-words, we would like to know if you think someone would date your
-interaction partner. Also, your interaction partner will be evaluating
-you in the same manner.
+There are many types of relationships people form in college.
+During the interaction, please think about your partner's potential as a romantic partner.
+Even if they are not the gender you are attracted to, you can still judge their potential as a romantic partner.
+After the interaction you will be asked to evaluate how dateable your partner is.
+In other words, we would like to know if you think someone would date your interaction partner.
+Also, your interaction partner will be evaluating you in the same manner.
 \end{quote}
 
-The decision was made to ask even heterosexual women to judge their
-women partners as potential romantic partners. We felt that this prompt
-would keep the study closest to a replication of the previous Garcia et
-al. (2016) version of the study. Past research has found that women,
-largely due to an increase self-objectifying state, are indeed able to
-evaluate other women's potential as romantic partners--indeed, women may
-be unfortunately used to thinking this way about themselves, and we
-suspect other women.
-
-Two participants were then brought into a larger interaction room where
-they sat on stools prearranged to be 36 inches apart. The experimenter
-instructed the participants to \enquote{get to know each other} for 10
-minutes and then left the room. After 10 minutes, the experimenter came
-back into the room and stopped the interaction. The participants then
-went back to their individual cubicles and completed a set of
-post-interaction measures. Participants were then thanked for their
-participation and debriefed Garcia et al. (2016). The full methodology
-used is found in Garcia et al. (2016)'s study.
-
-\subsection{Combined Samples}\label{combined-samples}
-
-Data from two different, but demographically equivalent, samples were
-combined to create the final analysis sample (\emph{N =} 64) used in
-this study. In the measures section that follows we refer to them as
-Sample 1 and Sample 2. Thirty-two previously unacquainted
-self-identifying female-sex dyads (64 total participants) from two
-liberal arts institutions in the Northeast of the United States
-participated in this study. Sample 1 (\emph{N =} 24) is from a co-ed
-liberal arts college in the northeast US and Sample 2 (\emph{N =} 40) is
-from a women's liberal arts college in the northeast US. More
-specifically, twelve of the pairs, which derived from Sample 1, were
-students at a co-ed liberal arts college, while the remaining twenty
-pairs who came from Sample 2 attended a women's liberal arts college.
-Initially, data was collected from same-sex and mixed-sex dyads that
-comprised of male and female gendered individuals. Sample 1 originally
-consisted of twenty-two pairs, twelve men and thirty-two women.
-Twenty-three pairs made up of forty-three women and one man, as well as
-two participants who did not identify with either gender category,
-formed Sample 2. For consistency, we limited participant data to same
-sex female pairs at the two colleges.
-
-Due these similarities across samples in regard to correlation patterns
-between significant variables within this study, the two datasets were
-combined. These participants were mostly first-year college students,
-with an average age of 18.85 (SD = 1.04). The sample was 48.44\%
-White/European American, 9.38\% Black/African-American, 28.12\%
-Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
-8 White/White pairs and 4 same race racial minority pairs, for a total
-of 12 same-race pairs. The remaining 20 were mixed race pairs, of which
-15 were White/racial minority pairings and 5 were cross-racial minority
-group pairs. 64.06\% of the sample identified as heterosexual, and 25\%
-identified as gay, lesbian or bisexual.
-
-\subsection{Post interaction Measures}\label{post-interaction-measures}
+The decision was made to ask even heterosexual women to judge their women partners as potential romantic partners.
+We felt that this prompt would keep the study closest to a replication of the previous Garcia et al.
+(2016) version of the study.
+Past research has found that women, largely due to an increase self-objectifying state, are indeed able to evaluate other women's potential as romantic partners--indeed, women may be unfortunately used to thinking this way about themselves, and we suspect other women.
+
+Two participants were then brought into a larger interaction room where they sat on stools prearranged to be 36 inches apart.
+The experimenter instructed the participants to \enquote{get to know each other} for 10 minutes and then left the room.
+After 10 minutes, the experimenter came back into the room and stopped the interaction.
+The participants then went back to their individual cubicles and completed a set of post-interaction measures.
+Participants were then thanked for their participation and debriefed Garcia et al.
+(2016).
+The full methodology used is found in Garcia et al.
+(2016)'s study.
+
+\#\#Combined Samples
+
+Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (\emph{N =} 64) used in this study.
+In the measures section that follows we refer to them as Sample 1 and Sample 2.
+Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
+Sample 1 (\emph{N =} 24) is from a co-ed liberal arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a women's liberal arts college in the northeast US.
+More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women's liberal arts college.
+Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
+Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
+Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
+For consistency, we limited participant data to same sex female pairs at the two colleges.
+
+Due these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
+These participants were mostly first-year college students, with an average age of 18.85 (SD = 1.04).
+The sample was 48.44\% White/European American, 9.38\% Black/African-American, 28.12\% Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race.
+There were 8 White/White pairs and 4 same race racial minority pairs, for a total of 12 same-race pairs.
+The remaining 20 were mixed race pairs, of which 15 were White/racial minority pairings and 5 were cross-racial minority group pairs.
+64.06\% of the sample identified as heterosexual, and 25\% identified as gay, lesbian or bisexual.
+
+\#\#Post interaction Measures
 
@@
 
-The following measures were collected in the order they are presented
-following the interaction. Correlations appear in
-Table~\ref{tab:corrtable}, and descriptive statistics appear in
-Table~\ref{tab:descriptives}.
-
-\subsubsection{Cognitive Performance}\label{cognitive-performance}
-
-Trigrams from the Remote Associates Task (McFarlin \& Blascovich, 1984)
-were utilized to assess cognitive performance after the interaction. Ten
-items were selected and presented to participants. For example, the
-correct answer for the trigram \enquote{Quack: Pond: Waddle} would be
-\enquote{Duck}. Participants are limited to 30 seconds. For every
-correct answer, 1 point is given. The mean score was 5.03 (SD = 2.29).
-Cognitive performance was measured first in order to measure potential
-immediate detriments to performance (Garcia et al., 2016).
-
-\subsubsection{State
-Other-Objectification}\label{state-other-objectification}
-
-To measure the participant's objectification of their partner in the
-interaction, participants were asked a series of questions about the
-frequency of thoughts in relation to multiple characteristics of their
-partner Garcia et al. (2016). Questions included aspects of their
-partner's internal traits such as personality, friends, family, and
-extracurricular interests, as well as external traits such as body,
-appearance, clothing, and body parts. All questions were to be rated on
-a scale from 1 (not at all) to 7 (constantly). Objectification was
-measured by getting the difference between the average frequency of
-thought about their partner's external traits (\(\alpha\) = 0.79 for
-Sample 1, \(\alpha\) = 0.79 for Sample 2) and frequency of thought about
-their partner's internal traits (\(\alpha\) = 0.79 for Sample 1,
-\(\alpha\) = 0.76 for Sample 2). A positive score in this scale would
-indicate that the participant thought about their partner's external
-traits more than the partner's internal traits, and a negative score
-would indicate the opposite.
-
-As can be seen in Table~\ref{tab:descriptives}, the mean
-other-objectification of women by women was \emph{M =} -1.58 (\emph{SD
-=} 1.21). This corresponds to women objectifying other women to a
-\emph{greater} extent than women's objectification of men reported in
-Garcia et al. (2016) (\emph{M =} -1.68, \emph{SD =} 1.52). Further, in
-the current sample the difference in other-objectification between
-heterosexual (\emph{M =} -1.77, \emph{SD =} 1.14) and non-heterosexual
-women (\emph{M =} -1.39, \emph{SD =} 1.35) was not statistically
-significant, \emph{t}(25.89) = 1.02, \emph{p =} 0.32.
-
-\subsubsection{Interaction Authenticity}\label{interaction-authenticity}
-
-To assess the magnitude to which individuals felt comfortable in the
-interaction and perceived the interaction to be authentic, we asked
-participants to rate the extent to which they felt comfortable, happy,
-friendly, warm, easygoing, sincere, and authentic on a scale ranging
-from 1 (not at all) to 7 (very much), much alike (Garcia et al., 2016).
-Participants were additionally asked to rate their interaction partner's
-authenticity as well as their own: \enquote{`Do you think your partner
-was authentic during your interaction?}' and \enquote{`Were you
-authentic during your interaction?}' These questions were ranked on a
-scale from 1 (not authentic at all). These were combined to form the
-authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) = 0.91
-for Sample 2).
-
-\subsubsection{State
-Self-Objectification}\label{state-self-objectification}
-
-To assess state self-objectification, we used an average of two items
-from Saguy et al. (2010) that were also used in Garcia et al. (2016).
-Participants were asked to rank how much they agreed with the following
-statements: \enquote{During the interaction I felt more like a body than
-a full self} and \enquote{I felt more like a body than as a real person
-in the interaction}. Originally, Saguy et al. (2010) used 3 items, but
-in both samples the reliability of the scale was higher once the third
-item was removed, so we chose to only use the first two for our measure
-of SSO, leaving us with a reliable scale (\(\alpha\) = 0.84 for Sample
-1, and \(\alpha\) = 0.85 for Sample 2.)
-
-\subsubsection{Relationship Agency}\label{relationship-agency}
-
-A scale was used from Garcia et al. (2016) to assess how much agency an
-individual believes they would possess in future romantic relationships.
-Participants were asked how likely it was that they would do the
-following: \enquote{`ask someone out on a date,}' \enquote{`open the
-door for your date,}' \enquote{`pay for a date,}' \enquote{`ask your
-boyfriend/girlfriend to marry you,}' \enquote{`initiate sex with your
-girlfriend/boyfriend,}' \enquote{`initiate condom use during sex,}'
-\enquote{`surprise your boyfriend/ girlfriend with a gift,}' and
-\enquote{`ask your girlfriend/boyfriend to move with you to a new
-place.}' Responses were measured on a scale ranging from 1 (not at all
-likely) to 7 (extremely likely). The scale originally had 9 items, but
-the 9th item had low correlations with the remaining items, ranging from
-.02 to .30 for the first sample, and .04 to .30 for the second sample.
-The item was intended to be reverse coded, but correlations were still
-low enough to make the scale unreliable. Therefore, the ninth item was
-removed. As a result, the scale had moderately high reliability for both
-samples (\(\alpha\) = 0.72 for Sample 1, (\(\alpha\) = 0.74 for Sample
-2).
-
-\subsubsection{Career Aspirations}\label{career-aspirations}
-
-To conceptualize participants' career aspirations after the interaction,
-we used the 10-item adaptation of P. Gray and M. OBrien (2007)'s Career
-Aspiration Scale employed in Garcia et al. (2016), which asked
-participants to consider how true 10 statements were in regard to their
-future careers on a scale from 0 (not at all true of me) to 4 (very true
-of me). Items include \enquote{I hope to become a leader in my career
-field} and \enquote{I hope to move up through any organization or
-business I work in.} Items were fairly reliable (\(\alpha\) = 0.73 for
-Sample 1, \(\alpha\) = 0.80 for Sample 2).
-
-\subsubsection{Trait
-Self-Objectification}\label{trait-self-objectification}
-
-Trait self-objectification (TSO) was assessed using the
-Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; M.
-Noll \& L. Fredrickson, 1998), which evaluates the extent to which
-individuals view their bodies in observable versus non-observable ways.
-The questionnaire asked participants to rank order both appearance and
-functional aspects of their bodies, from 1 (least important) to 10 (most
-important), with respect to physical self-concepts. Of the ten body
-attributes, five of the items were appearance-based (weight, sex appeal,
-physical attractiveness, firm/sculpted muscles and body measurements),
-and five of the items were competence-based (strength, physical
-coordination, energy level, health and physical fitness). Difference
-scores were computed by subtracting the sum of the 5 functional
-aspects/competence attributes (e.g., health, strength) from the sum of
-the 5 physical self-concepts/appearance attributes (e.g., physical
-attractiveness, weight), and all measures were multiplied by -1, as was
-done in Garcia et al. (2016), so that positive scores indicated greater
-TSO.
-
-\section{Results}\label{results}
-
-\subsection{Data analysis}\label{data-analysis}
-
-We used R (Version 3.5.2; R Core Team, 2017) and the R-packages
-\emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools}
-(Version 1.13.5; Wickham, Hester, \& Chang, 2018), \emph{dplyr} (Version
-0.8.3; Wickham, François, Henry, \& Müller, 2018), \emph{forcats}
-(Version 0.3.0; Wickham, 2018), \emph{ggformula} (Version 0.7.0; D.
-Kaplan \& Pruim, 2017), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
-\emph{haven} (Version 2.1.0; Wickham \& Miller, 2019), \emph{irr}
-(Version 0.84.1; Gamer, Lemon, \&
-\textless{}puspendra.pusp22@gmail.com\textgreater{}, 2012), \emph{knitr}
-(Version 1.25; Xie, 2015), \emph{kutils} (Version 1.70; Johnson, Kite,
-\& Redmon, 2019), \emph{lattice} (Version 0.20.38; Sarkar, 2008),
-\emph{lavaan} (Version 0.6.1; Rosseel, 2012), \emph{lpSolve} (Version
-5.6.15; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.15; Bates
-\& Maechler, 2017), \emph{mosaic} (Version 1.2.0; Pruim, Kaplan, \&
-Horton, 2017, 2016), \emph{mosaicData} (Version 0.17.0; Pruim et al.,
-2016), \emph{nlme} (Version 3.1.137; Pinheiro, Bates, DebRoy, Sarkar, \&
-R Core Team, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
-2018), \emph{psych} (Version 1.8.4; Revelle, 2017), \emph{purrr}
-(Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.1.1;
-Wickham, Hester, \& Francois, 2017), \emph{stringr} (Version 1.4.0;
-Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
-\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse}
-(Version 1.2.1; Wickham, 2017), \emph{usethis} (Wickham \& Bryan, 2018),
-and \emph{xtable} (Version 1.8.3; Dahl, Scott, Roosen, Magnusson, \&
-Swinton, 2019) for all our analyses.
-
-\subsection{Analysis Strategy}\label{analysis-strategy}
+The following measures were collected in the order they are presented following the interaction.
+Correlations appear in Table~\ref{tab:corrtable}, and descriptive statistics appear in Table~\ref{tab:descriptives}.
+
+\#\#\#Cognitive Performance
+
+Trigrams from the Remote Associates Task (McFarlin \& Blascovich, 1984) were utilized to assess cognitive performance after the interaction.
+Ten items were selected and presented to participants.
+For example, the correct answer for the trigram \enquote{Quack: Pond: Waddle} would be \enquote{Duck}.
+Participants are limited to 30 seconds.
+For every correct answer, 1 point is given.
+The mean score was 5.03 (SD = 2.29).
+Cognitive performance was measured first in order to measure potential immediate detriments to performance (Garcia et al., 2016).
+
+\#\#\#State Other-Objectification
+
+To measure the participant's objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to multiple characteristics of their partner Garcia et al.
+(2016).
+Questions included aspects of their partner's internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
+All questions were to be rated on a scale from 1 (not at all) to 7 (constantly).
+Objectification was measured by getting the difference between the average frequency of thought about their partner's external traits (\(\alpha\) = 0.79 for Sample 1, \(\alpha\) = 0.79 for Sample 2) and frequency of thought about their partner's internal traits (\(\alpha\) = 0.79 for Sample 1, \(\alpha\) = 0.76 for Sample 2).
+A positive score in this scale would indicate that the participant thought about their partner's external traits more than the partner's internal traits, and a negative score would indicate the opposite.
+
+As can be seen in Table~\ref{tab:descriptives}, the mean other-objectification of women by women was \emph{M =} -1.58 (\emph{SD =} 1.21).
+This corresponds to women objectifying other women to a \emph{greater} extent than women's objectification of men reported in Garcia et al.
+(2016) (\emph{M =} -1.68, \emph{SD =} 1.52).
+Further, in the current sample the difference in other-objectification between heterosexual (\emph{M =} -1.77, \emph{SD =} 1.14) and non-heterosexual women (\emph{M =} -1.39, \emph{SD =} 1.35) was not statistically significant, \emph{t}(25.89) = 1.02, \emph{p =} 0.32.
+
+\#\#\#Interaction Authenticity
+
+To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike (Garcia et al., 2016).
+Participants were additionally asked to rate their interaction partner's authenticity as well as their own: \enquote{`Do you think your partner was authentic during your interaction?}' and \enquote{`Were you authentic during your interaction?}' These questions were ranked on a scale from 1 (not authentic at all).
+These were combined to form the authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) = 0.91 for Sample 2).
+
+\#\#\#State Self-Objectification
+
+To assess state self-objectification, we used an average of two items from Saguy et al.
+(2010) that were also used in Garcia et al.
+(2016).
+Participants were asked to rank how much they agreed with the following statements: \enquote{During the interaction I felt more like a body than a full self} and \enquote{I felt more like a body than as a real person in the interaction}.
+Originally, Saguy et al.
+(2010) used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale (\(\alpha\) = 0.84 for Sample 1, and \(\alpha\) = 0.85 for Sample 2.)
+
+\#\#\#Relationship Agency
+
+A scale was used from Garcia et al.
+(2016) to assess how much agency an individual believes they would possess in future romantic relationships.
+Participants were asked how likely it was that they would do the following: \enquote{`ask someone out on a date,}' \enquote{`open the door for your date,}' \enquote{`pay for a date,}' \enquote{`ask your boyfriend/girlfriend to marry you,}' \enquote{`initiate sex with your girlfriend/boyfriend,}' \enquote{`initiate condom use during sex,}' \enquote{`surprise your boyfriend/ girlfriend with a gift,}' and \enquote{`ask your girlfriend/boyfriend to move with you to a new place.}' Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
+The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
+The item was intended to be reverse coded, but correlations were still low enough to make the scale unreliable.
+Therefore, the ninth item was removed.
+As a result, the scale had moderately high reliability for both samples (\(\alpha\) = 0.72 for Sample 1, (\(\alpha\) = 0.74 for Sample 2).
+
+\#\#\#Career Aspirations
+
+To conceptualize participants' career aspirations after the interaction, we used the 10-item adaptation of P.
+Gray \& M.
+OBrien (2007)'s Career Aspiration Scale employed in Garcia et al.
+(2016), which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
+Items include \enquote{I hope to become a leader in my career field} and \enquote{I hope to move up through any organization or business I work in.} Items were fairly reliable (\(\alpha\) = 0.73 for Sample 1, \(\alpha\) = 0.80 for Sample 2).
+
+\#\#\#Trait Self-Objectification
+
+Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire (Fredrickson et al., 1998; M.
+Noll \& L.
+Fredrickson, 1998), which evaluates the extent to which individuals view their bodies in observable versus non-observable ways.
+The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
+Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness).
+Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in Garcia et al.
+(2016), so that positive scores indicated greater TSO.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
+
+We used R (Version 3.6.2; R Core Team, 2017) and the R-packages \emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools} (Version 2.2.2; Wickham et al., 2018b), \emph{dplyr} (Version 1.0.0; Wickham et al., 2018a), \emph{forcats} (Version 0.4.0; Wickham, 2018), \emph{ggformula} (Version 0.9.3; Kaplan \& Pruim, 2017), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{ggstance} (Version 0.3.3; Henry et al., 2019), \emph{haven} (Version 2.2.0; Wickham \& Miller, 2019), \emph{irr} (Version 0.84.1; Gamer, Lemon, \& \textless puspendra.pusp22@gmail.com\textgreater, 2012), \emph{knitr} (Version 1.28; Xie, 2015), \emph{kutils} (Version 1.70; Johnson, Kite, \& Redmon, 2019), \emph{lattice} (Version 0.20.40; Sarkar, 2008), \emph{lavaan} (Version 0.6.7; Rosseel, 2012), \emph{lpSolve} (Version 5.6.15; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2017), \emph{mosaic} (Version 1.5.0; Pruim, Kaplan, \& Horton, 2017, 2016), \emph{mosaicData} (Version 0.17.0; Pruim et al., 2016), \emph{nlme} (Version 3.1.144; Pinheiro, Bates, DebRoy, Sarkar, \& R Core Team, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.9.12.31; Revelle, 2017), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham et al., 2017), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.2; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.3.0; Wickham, 2017), \emph{usethis} (Version 1.5.1; Wickham \& Bryan, 2018), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) for all our analyses.
+
+\hypertarget{analysis-strategy}{%
+\subsection{Analysis Strategy}\label{analysis-strategy}}
 
@@
 
-This study sought to replicate the results of Garcia et al. (2016)'s
-study, done with male-female pairs, which used a dyadic path analysis to
-detect whether partners' objectification of one another affected state
-self-objectification (SSO). See Figure~\ref{fig:2016figure} for the
-results of the analysis from this previous study. We hope to investigate
-how the central effects found in the previous study relate to
-interactions between two women. Specifically, we are interested in
-testing the relationship between state-other objectification and SSO,
-and how SSO in turn, affects feelings of inauthenticity during the
-interaction. In addition, we will also test if the effect of
-other-objectification in an interaction on SSO is only present for those
-women who are high in trait self-objectification, as in Garcia et al.
-(2016). Further, we will investigate the relationships between
-experiencing interaction inauthenticity and relationship agency, career
-aspirations, and cognitive performance.
-
-While Garcia et al. (2016) used dyadic path analysis, we will conduct
-our dyadic analyses using multilevel modeling. Dyadic analyses for
-distinguishable dyads (e.g., mixed-gender interacting pairs) is more
-natural in Structural Equation Modeling (SEM) than it is for
-indistinguishable dayds (e.g., same-gender interacting pairs) (Garcia,
-Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
-this asymmetry is that, due to the arbitrary distinctions made between
-\enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads,
-many estimates need to be fixed to be equal (i.e., paths, variances,
-covariances, endogenous intercepts, and exogenous means) for
-indistinguishable dyads but these equality constraints should not then
-be considered in the degrees of freedom calculations for fit estimations
-(Olsen \& Kenny, 2006). Further, Olsen and Kenny (2006) detail how a new
-independence model and the corresponding fit measure should be
-re-calculated for indistinguishable dyads models. The current study uses
-dyadic multilevel modeling (MLM) to test all relationships and mediation
-patterns. The online supplementary materials contains analysis using
-SEM. See Ledermann and Kenny (2017) for a more complete discussion of
-the considerations for using SEM versus MLM for dyadic analysis.
-
-Testing the Garcia et al. (2016) model on the current, same-gender,
-sample, involves using the Actor-Partner Independence Model (APIM)
-approach for each outcome variable (i.e., endogenous variable in
-Figure~\ref{fig:2016figure}). Thus, we ran five APIM's to test all the
-hypothesized relationships. See Figure~\ref{fig:apim} for a basic APIM
-model. The APIM includes effects due to one's own, as well as one's
-partner's, predictor variables (\(X\)'s) on the one's own outcome
-variable (\(Y\)). Unlike the original Garcia et al. (2016) study, our
-study deals with indistinguishable dyads, meaning the designation of who
-is designated as \enquote{actor} and who is designated as
-\enquote{partner} is arbitrary. Recall that the indistinguishable nature
-of the dyads in the current study led us to choose the MLM approach over
-SEM. These analyses are considered exploratory, given the lack of prior
-research theorizing about these linkages.
-
-Before moving to the main analyses, we discuss statistical equivalence
-test that provide support for combining Sample 1 and Sample 2 in one
-analysis sample. The online supplemental material contains the main
-analyses separated by samples. All results presented below are from
-models including sample as a control variable.
-
-\subsubsection{Combining Samples}\label{combining-samples}
-
-The correlations between study variables is similar across samples. The
-reliabilities for the study scales were also equivalent. (Note that the
-two samples were two small to conduct formal measurement equivalence
-tests for scales.) There are no statistically significant differences
-between samples in demographics including age, STATS, and ethnicity,
-STATS.
-
-\subsection{Main Results}\label{main-results}
+This study sought to replicate the results of Garcia et al.
+(2016)'s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners' objectification of one another affected state self-objectification (SSO).
+See Figure~\ref{fig:2016figure} for the results of the analysis from this previous study.
+We hope to investigate how the central effects found in the previous study relate to interactions between two women.
+Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction.
+In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in Garcia et al.
+(2016).
+Further, we will investigate the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.
+
+While Garcia et al.
+(2016) used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling.
+Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dayds (e.g., same-gender interacting pairs) (Garcia, Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017).
+One reason for this asymmetry is that, due to the arbitrary distinctions made between \enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations (Olsen \& Kenny, 2006).
+Further, Olsen \& Kenny (2006) detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models.
+The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation patterns.
+The online supplementary materials contains analysis using SEM.
+See Ledermann \& Kenny (2017) for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.
+
+Testing the Garcia et al.
+(2016) model on the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approach for each outcome variable (i.e., endogenous variable in Figure~\ref{fig:2016figure}).
+Thus, we ran five APIM's to test all the hypothesized relationships.
+See Figure~\ref{fig:apim} for a basic APIM model.
+The APIM includes effects due to one's own, as well as one's partner's, predictor variables (\(X\)'s) on the one's own outcome variable (\(Y\)).
+Unlike the original Garcia et al.
+(2016) study, our study deals with indistinguishable dyads, meaning the designation of who is designated as \enquote{actor} and who is designated as \enquote{partner} is arbitrary.
+Recall that the indistinguishable nature of the dyads in the current study led us to choose the MLM approach over SEM.
+These analyses are considered exploratory, given the lack of prior research theorizing about these linkages.
+
+Before moving to the main analyses, we discuss statistical equivalence test that provide support for combining Sample 1 and Sample 2 in one analysis sample.
+The online supplemental material contains the main analyses separated by samples.
+All results presented below are from models including sample as a control variable.
+
+\hypertarget{combining-samples}{%
+\subsubsection{Combining Samples}\label{combining-samples}}
+
+The correlations between study variables is similar across samples.
+The reliabilities for the study scales were also equivalent.
+(Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS.
+
+\#\#Main Results
 
@@
 
-All model estimates and p-values are found in Table~\ref{tab:mlm} and
-the relationships with estimates included are depicted in
-Figure~\ref{fig:semfigure}.
-
-The most important finding from Garcia et al. (2016) was the significant
-partner effect of other objectification and SSO (specifically men's
-objectification of women and women's SSO). As expected, the partner
-effect of other-objectification on SSO in the current all-women sample
-was statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12,
-\emph{p} = .019, replicating Garcia et al. (2016)'s finding. One's own
-other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
-= 0.12, \emph{p} = .210. Contrary to past finding however, there was no
-statistically significant interaction of partner's other objectification
-and the person's trait self-objectification on SSO, \emph{b} = 0.03,
-\emph{SE} = 0.27, \emph{p} = .910. There was also no significant main
-effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
-0.05, \emph{p} = .183.
-
-Contrary to expectations, there was no significant effect of SSO on
-interaction authenticity, although the estimate of this effect was in
-the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12,
-\emph{p} = .431. Because authenticity was a composite score of 9 items,
-two of which were interaction specific authenticity items, we also
-estimated the pairwise correlations between SSO and all these items
-individually. They were all small, ranging from only -0.01 to -0.14.
-Although we hypothesized that SSO would mediate the relationship between
-partner's other objectification and interaction authenticity, after
-finding no relationship between SSO and authenticity, we also tested if
-the partner's other objectification had a direct effect on authenticity,
-but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
-\emph{p} = .608 (nor was the total effect of partner's other
-objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11,
-\emph{p} = .787).
-
-Lastly, although there was no evidence that SSO was related to
-interaction authenticity in the current sample, we tested if interaction
-authenticity (composite of nine items) had effects on cognitive
-performance, career aspirations, and relationship agency, as it did in
-Garcia et al. (2016). We again used MLM and thus, these effects were
-tested in three separate models. There was no significant effect of
-interaction authenticity on cognitive performance, \emph{b} = 0.32,
-\emph{SE} = 0.28, \emph{p} = .258, but authenticity was significantly
-positively related to both career aspirations, \emph{b} = 0.18,
-\emph{SE} = 0.07, \emph{p} = .010, and relationships agency, \emph{b} =
-0.23, \emph{SE} = 0.12, \emph{p} = .049. There was no direct effect of
-SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25,
-\emph{p} = .872, and no direct effect of partner's other objectification
-on cognitive performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
-.962. There was no direct effect of SSO on career aspirations, \emph{b}
-= 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of
-partner's other objectification on career aspirations, \emph{b} = -0.06,
-\emph{SE} = 0.07, \emph{p} = .378. There was no direct effect of SSO on
-relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} =
-.659, and no direct effect of partner's other objectification on
-relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.
-
-The results were similar for analyses conducted on Sample 1 and Sample 2
-individually. See the online supplemental material for more detail on
-these analyses.
-
-\section{Discussion}\label{discussion}
-
-The current study tested whether the model of interpersonal
-objectification and state self-objectification (SSO) used in Garcia et
-al. (2016) replicates in a same-gender dyadic sample of women only.
-Although past reserach has found that women do objectify other women
-(Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes,
-2013), this is the first study to test if \emph{interpersonal}
-other-objectification by women is related to state self-objectification
-in their woman-identified interaction partners. As hypothesized, the
-current study did find a significant relationship bewteen a woman's
-partner's report of having objectified her and her own post-interaction
-feelings of self-objectification. That is, there was a significant
-partner effect of other-objectification on SSO. This effect extends the
-equivalent relationship found in mixed-gender interactions to the
-context of same-gender interactions between women. Thus, it could be
-that it is not only the male gaze, and male other-objectification that
-is related to women's state self-objectification, but being objectified
-by another woman can also results in SSO, at least in the context of a
-scenario where they know they are being evaluated as a potential dating
-partner.
-
-As is the case in all correlational studies, we cannot be sure in the
-causal direction. It could be that women's SSO causes them to be
-objectified by their interaction partner. This interpretation in
-theoreticall interesting given that, in both the Garcia et al. (2016)
-study and in the current study, it is \emph{women's} SSO this relates to
-being objectified by one's partner. However, Objectification Theory
-(Roberts \& Fredrickson, 1997), as well as past experimental studies
-{[}Saguy et al. (2010); CITE{]}, suggest that the causal flow is from
-other-objectification to SSO. Although, importantly, the current study
-found evidence for the partner effect of other-objectification on SSO,
-there was a lack of evidence for the connections between SSO and
-downstream negative consequences.
-
-Where the results of the current study diverge most notably from the
-results of studies testing interpersonal objectification among
-mixed-gender dyads is the lack of evidence for relationships between SSO
-and felt inauthenticity. In addition, we found no evidence of
-\emph{direct} or \emph{indirect} relationships between SSO and cognitive
-functioning, relationship agency, and career aspirations. Nor was there
-evidence of \emph{direct} or \emph{indirect} relationships between
-other-objectification and any of these outcomes. This is somewhat
-suprising given the plentiful evidence linking SSO and cognitive
-functioning (B. L. Fredrickson et al., 1998; Quinn, Chaudoir, \& Kallen,
-2011) and the small, but extant research on interpersonal
-other-ojectification and cognitive functioning (Garcia et al., 2016;
-Logel et al., 2009). This lack of evidence could potentially signal
-diverging processs between women's experiences with interpersonal
-objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is
-particularly detrimental (Calogero, 2004; Gervais, Holland, \& Dodd,
-2013; Gervais et al., 2011; Roberts \& Fredrickson, 1997), and perhaps
-the self-objectification experienced within an interaction with a women
-is not as harmful as the self-objectificatoin experienced within an
-interaction with a man. However, as a strong note of caution, we need to
-be careful not to interpret a null result as evidence of no
-relationship.
-
-The lack of evidence for a relationship between SSO and interaction
-authenticity is surprising and again, should not be interpreted as
-evidence of no realtionship. It should be noted that the estimate of
-this relationship was very small, but in the negative direction, as
-anticipated. If it is the case that there is a smaller (i.e., weaker)
-connection between women's feelings of SSO and inauthenticity in
-interactions with other women then in interactions with men, models of
-interpersonal objectification, like the SIMO (Gervais et al., 2020),
-could be extended by including inauthenticity as a potential mediating
-factor in decisions to continue objectifying interactions. Further,
-gender of the objectifyer/interaction partner could also be added to the
-SIMO model to help extend our understanding of under what circumstances
-other-objectification and SSO have negative concequences for women.
-
-Although we did not find a connection bewteen SSO and authenticity we
-did find significant positive relationships between authenticity and
-relationship agency and career aspirations. The relationship between
-authenticity and cognitive functioning was also estimated as positive,
-but it was not statistically signfiicant. Again, due to the lack of
-connection between SSO and authenticity, we found no evidence of
-\emph{indirect} relationships between SSO and these outcome variables.
-This evidence of a relationship between authenticity and the relational
-outcome variables (i.e., relationship agency and career aspirations)
-provides evidence that corrborates past findings that felt authenticity
-in interactions is important for healthy relationship functioning
-{[}Garcia et al. (2016); PWQ paper I reviewed{]}. Just as authenticity
-has been found to be important in intergroup interactions {[}CITE; CITE;
-CITE{]}, we again find more evidence here that distuptions in feelings
-of authenticity can negatively impact relationships beyond the current
-partner. Although the current study did not find a connection between
-authenticity and SSO, this seems theoretically to be a natural
-connection, and more work needs to be done to discover when and how SSO
-leads to inauthenticity in interpersonal objectification situations.
-
-\subsection{Limitations and Future
-Directions}\label{limitations-and-future-directions}
-
-\subsubsection{Sample Characteristics}\label{sample-characteristics}
-
-The sample size was small and combined across two higher education
-institutions.
-
-The sample of the current study was comprised of Western women, being
-that sexual objectification is most prevalent in this culture (Loughnan
-et al., 2015b), and research on objectification conducted outside of
-Western or Westernized countries is scarce (Moradi \& Huang, 2008),
-although more current work examines objectification from a
-cross-cultural framework (Loughnan et al., 2015b, Wollast et al.
-(2020)). Because \enquote{bodies exist within social and cultural
-contexts, and hence are also constructed through sociocultural practices
-and discourses} (Roberts \& Fredrickson, 1997, p. 174), it is important
-to consider how diverse social identities within unique cultural
-contexts may inform sexual objectification phenomenon to test the
-cross-cultural applicability of theoretical frameworks (Loughnan et al.,
-2015b). Further, sexualizing experiences and self-objectification are
-thought to begin a very young age, and thus, researchers have only
-recently begun to examine such experiences among children (Bury,
-Tiggemann, \& Slater, 2016; e.g., Holland \& Haslam, 2016; Jongenelis,
-Byrne, \& Pettigrew, 2014). Considering the fact that the average mean
-age of the investigated participants of this current study was 18.85
-years, research among younger and older individuals is needed,
-especially because self-objectification may change over time (Roberts \&
-Fredrickson, 1997). It may be valuable to question the extent to which
-children, adolescents, or emerging adults of different races or
-ethnicities are exposed to varied amounts of sexualizing content.
-
-\subsubsection{Sexual Objectification and the Objectifyer's
-Gender}\label{sexual-objectification-and-the-objectifyers-gender}
-
-The current sample contained a mixture of heterosexual and
-non-heterosexual women, but all participants were asked to think about
-and evaluate their partner as a potential data parter. While we think
-that hetereosexual women are indeed able to do this with other women as
-their target---indeed, there is evidence that they might do this readily
-(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---they might be more
-apt to activate social comparison processes (Festinger, 1954) than women
-who are sexually attracted to other women (non-heterosexual women). This
-differential psychological process between women with differing
-sexualities might have served to dampen our ability to detect
-relationships, adding variability.
-
-Previous research has found that when compared to heterosexual women,
-lesbian women report less concern with physical appearance (Siever,
-1994; Strong, Williamson, Netemeyer, \& Geer, 2000), and less
-self-objectification (Brownlow, 1998; Noffsinger-Frazier, 2004). However
-none of these studies examined the relationship between
-self-objectification and experiences of sexual objectification. Thus, it
-is unclear whether lesbians indeed experience similar levels of cultural
-sexual objectification but internalize them less than heterosexual women
-do. Consistent with previous reseach Hill and Fischer (2008) determined
-lesbians existed less physical appearance concerns compared to
-heterosexual women, however there was no difference found that lesbian
-women self-objectify less than heterosexual women and they did not find
-that sexual orientation moderates the relationshiotn between sexual
-objecitifcantion and self-objectification This contradicts older
-theoretical literature that suggests that lesbians internalize cultural
-sexual objectification less than do heterosexual women (Brown, 1987;
-LUM, 1994; Pitman, 1999; Siever, 1994)
-
-However, since both men and women are socialized in a culture that
-sexually objectifies women, both men and women may come to internalize
-this socialization and sexually objectify women. Indeed, recent research
-has found that the more women self-objectify, the more they objectify
-other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013), although not
-to the degree exhibited by men; that is, men were found to objectify
-women significantly more than women objectify other women (Strelan \&
-Hargreaves, 2005).
-
-\subsubsection{Sexism and Sexual
-Discrimination}\label{sexism-and-sexual-discrimination}
-
-Sexism has recently been found to be related to the objectification of
-women, but not men, for both men and women (Harsey \& Zurbriggen, 2020).
-Empirical evidence illustrates how women continue to be objects of
-interpersonal discrimination and experience daily sexist hassles (Swim,
-Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
-discrimination women face is the process by which their whole being is
-viewed as a collection of sexualized body parts valued predominantly for
-commodification, a phenomena termed sexual objectification (Bartky,
-1990). Sexual objectification occurs with both \enquote{endless variety
-and monotonous similarity,} and is thus mediated by unique combinations
-of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
-Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
-Nicholson (1989), p.~28). Amid such heterogeneity though,
-\enquote{having a reproductively mature female body} proposed by Roberts
-and Fredrickson (1997) is likely to create a shared vulnerability to
-sexual objectification and a variety of shared negative experiences as a
-result.
-
-\subsubsection{Measurement}\label{measurement}
-
-Also, future experiments or longitudinal studies should explore the
-external validity of the notions of self-objectification and how the
-operationalization of self-objectification may be improved.
-
-\subsubsection{Alternative Model}\label{alternative-model}
-
-Puvia and Vaes (2013) alternative model. TSO -\textgreater{} SOO,
-mediated by SSO.
-
-\subsection{Clinical Implications}\label{clinical-implications}
-
-Regardless, the results from the current analysis highlight how subtle
-forms of sexist discrimination operate to inform prevention and
-intervention efforts in both clinical and educational contexts. These
-results are quite useful for promoting mental health and within early
-action programs for girls and young women, where scholars and
-practitioners might provide the tools necessary to circumvent or
-mitigate negative effects on self-objectification, and combat such
-experiences.
-
-\section{Conclusion}\label{conclusion}
-
-The results of this study demonstrate the complex and ambivalent nature
-of female sexual objectification and additionally highlight the
-psychological and social consequences of such objectification processes
-on women's social relationships and well-being. We did not find a
-significant effect between actor SSO and felt authenticity in the
-interaction, which suggests that there is not sufficient evidence to
-support the claim that partner objectification is the cause for the
-diverse range of negative effects related to interaction inauthenticity.
-
-\section{References}\label{references}
+All model estimates and p-values are found in Table~\ref{tab:mlm} and the relationships with estimates included are depicted in Figure~\ref{fig:semfigure}.
+
+The most important finding from Garcia et al.
+(2016) was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
+As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12, \emph{p} = .019, replicating Garcia et al.
+(2016)'s finding.
+One's own other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE} = 0.12, \emph{p} = .210.
+Contrary to past finding however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, \emph{b} = 0.03, \emph{SE} = 0.27, \emph{p} = .910.
+There was also no significant main effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} = 0.05, \emph{p} = .183.
+
+Contrary to expectations, there was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12, \emph{p} = .431.
+Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also estimated the pairwise correlations between SSO and all these items individually.
+They were all small, ranging from only -0.01 to -0.14.
+Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship between SSO and authenticity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12, \emph{p} = .608 (nor was the total effect of partner's other objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11, \emph{p} = .787).
+
+Lastly, although there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performance, career aspirations, and relationship agency, as it did in Garcia et al.
+(2016).
+We again used MLM and thus, these effects were tested in three separate models.
+There was no significant effect of interaction authenticity on cognitive performance, \emph{b} = 0.32, \emph{SE} = 0.28, \emph{p} = .258, but authenticity was significantly positively related to both career aspirations, \emph{b} = 0.18, \emph{SE} = 0.07, \emph{p} = .010, and relationships agency, \emph{b} = 0.23, \emph{SE} = 0.12, \emph{p} = .049.
+There was no direct effect of SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25, \emph{p} = .872, and no direct effect of partner's other objectification on cognitive performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} = .962.
+There was no direct effect of SSO on career aspirations, \emph{b} = 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of partner's other objectification on career aspirations, \emph{b} = -0.06, \emph{SE} = 0.07, \emph{p} = .378.
+There was no direct effect of SSO on relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} = .659, and no direct effect of partner's other objectification on relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.
+
+The results were similar for analyses conducted on Sample 1 and Sample 2 individually. See the online supplemental material for more detail on these analyses.
+
+\#Discussion
+The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in Garcia et al.
+(2016) replicates in a same-gender dyadic sample of women only.
+Although past reserach has found that women do objectify other women (Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013), this is the first study to test if this interpersonal other-objectification by women is related to self-objectification in women.
+As hypothesized, the current study did find a significant relationship bewteen a woman's partner's report of having objectified her and her own post-interaction feelings of self-objectification.
+That is, there was a significant partner effect of other-objectification on SSO.
+This effect extends the equivalent relationship found in mixed-gender interactions to the context of same-gender interactions between women.
+Thus, it could be that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also results in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
+
+As is the case in all correlational studies, we cannot be sure in the causal direction.
+It could be that women's SSO causes them to be objectified by their interaction partner.
+This interpretation holds up given that, in both the Garcia et al.
+(2016) study and in the current study, it is \emph{women's} SSO this relates to being objectified by one's partner.
+However, Objectification Theory (Roberts \& Fredrickson, 1997) as past experimental studies {[}Saguy et al.
+(2010); CITE{]} suggest that the causal direction is indeed in the direction whereby other-objectification causes SSO.
+Although, importantly, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.
+
+Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and felt inauthenticity.
+In addition, we found no evidence of \emph{direct} or \emph{indirect} relationships between SSO and cognitive functioning, relationship agency, and career aspirations.
+Nor was there evidence of \emph{direct} or \emph{indirect} relationships between other-objectification and any of these outcomes.
+This is somewhat suprising given the plentiful evidence linking SSO and cognitive functioning (Fredrickson et al., 1998; Quinn et al., 2011) and the small, but extant research on interpersonal other-ojectification and cognitive functioning (Garcia et al., 2016; Logel et al., 2009).
+This lack of evidence could potentially signal diverging processs between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental (Calogero, 2004; Gervais, Holland, \& Dodd, 2013; Gervais et al., 2011; Roberts \& Fredrickson, 1997), and perhaps the self-objectification experienced within an interaction with a women is not as detrimental as the self-objectificatoin experienced within an interaction with a man.
+We need to be careful not to interpret a null result as evidence of no relationship.
+
+The lack of evidence for a relationship between SSO and interaction authenticity is surprising and again, should not be interpreted as evidence of no realtionship---this lack of statistical significance could also be due to the relatively small sample size in the current study.
+The estimate of this relationship was very small, but in the negative direction, as anticipated.
+If it is the case that there is a smaller, or weaker, connection between women's feelings of SSO in interactions with other women then in interactions with men, models of interpersonal objectification, like the SIMO, could be extended by including inauthenticity as a potential mediated factor in decisions to continue objectifying interactions.
+Further, gender of the objectifyer/interaction partner could also be added to the model to help extend our understanding of under what circumstances other-objectificant and SSO have negative concequences for women.
+
+Although we did not fid a connection bewteen SSO and authenticity we did find significant relationships in
+
+\#\#Limitations and Future Directions
+
+\#\#\#Sample Characteristics
+The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture (Loughnan et al., 2015b), and research on objectification conducted outside of Western or Westernized countries is scarce (Moradi \& Huang, 2008), although more current work examines objectification from a cross-cultural framework (Loughnan et al., 2015b, p.
+Wollast et al.
+(2020)).
+Because \enquote{bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses} (Roberts \& Fredrickson, 1997, p.
+174), it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks (Loughnan et al., 2015b).
+Further, sexualizing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children (e.g., Holland \& Haslam, 2016; Bury, Tiggemann, \& Slater, 2016; Jongenelis, Byrne, \& Pettigrew, 2014).
+Considering the fact that the average mean age of the investigated participants of this current study was 18.85 years, research among younger and older individuals is needed, especially because self-objectification may change over time (Roberts \& Fredrickson, 1997).
+It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.
+
+\#\#\#Sexual Objectification and the Objectifyer's Gender
+
+Previous research has found that when compared to heterosexual women, lesbian women report less concern with physical appearance (Siever, 1994; Strong, Williamson, Netemeyer, \& Geer, 2000), and less self-objectification (Brownlow, 1998; Noffsinger-Frazier, 2004).
+However none of these studies examined the relationship between self-objectification and experiences of sexual objectification.
+Thus, it is unclear whether lesbians indeed experience similar levels of cultural sexual objectification but internalize them less than heterosexual women do.
+Consistent with previous reseach Hill \& Fischer (2008) determined lesbians existed less physical appearance concerns compared to heterosexual women, however there was no difference found that lesbian women self-objectify less than heterosexual women and they did not find that sexual orientation moderates the relationshiotn between sexual objecitifcantion and self-objectification This contradicts older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women (Brown, 1987; LUM, 1994; Pitman, 1999; Siever, 1994)
+
+However, since both men and women are socialized in a culture that sexually objectifies women, both men and women may come to internalize this socialization and sexually objectify women.
+Indeed, recent research has found that the more women self-objectify, the more they objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013), although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women (Strelan \& Hargreaves, 2005).
+
+\#\#\#Sexism and Sexual Discrimination
+Sexism has recently been found to be related to the objectification of women, but not men, for both men and women (Harsey \& Zurbriggen, 2020).
+Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and experience daily sexist hassles (Swim, Hyers, Cohen, \& Ferguson, 2001).
+One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification (Bartky, 1990).
+Sexual objectification occurs with both \enquote{endless variety and monotonous similarity,} and is thus mediated by unique combinations of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler, Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and Nicholson (1989), p.~28).
+Amid such heterogeneity though, \enquote{having a reproductively mature female body} proposed by Roberts \& Fredrickson (1997) is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
+
+\#\#\#Measurement
+Also, future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operationalization of self-objectification may be improved.
+
+\#\#\#Alternative Model
+Puvia \& Vaes (2013) alternative model. TSO -\textgreater{} SOO, mediated by SSO.
+
+\#\#Clinical Implications
+Regardless, the results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts.
+These results are quite useful for promoting mental health and within early action programs for girls and young women, where scholars and practitioners might provide the tools necessary to circumvent or mitigate negative effects on self-objectification, and combat such experiences.
+
+\#Conclusion
+The results of this study demonstrate the complex and ambivalent nature of female sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women's social relationships and well-being.
+We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity.
+
+\#References
 
@@
 \begingroup
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-argyle1969}{}
-Argyle, M., \& Williams, M. (1969). Observer or observed? A reversible
-perspective in person perception. \emph{Sociometry}, 396--412.
-
-\hypertarget{ref-R-papaja}{}
-Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
-R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
-
-\hypertarget{ref-Bartky}{}
-Bartky, S. L. (1990). Femininity and domination studies in the
-phenomenology of oppression.
-
-\hypertarget{ref-R-Matrix}{}
-Bates, D., \& Maechler, M. (2017). \emph{Matrix: Sparse and dense matrix
-classes and methods}. Retrieved from
-\url{https://CRAN.R-project.org/package=Matrix}
-
-\hypertarget{ref-berger1972}{}
-Berger, J., Cohen, B. P., \& Zelditch Jr, M. (1972). Status
-characteristics and social interaction. \emph{American Sociological
-Review}, 241--255.
-
-\hypertarget{ref-R-lpSolve}{}
-Berkelaar, M., \& others. (2015). \emph{LpSolve: Interface to
-'lp\_solve' v. 5.5 to solve linear/integer programs}. Retrieved from
-\url{https://CRAN.R-project.org/package=lpSolve}
-
-\hypertarget{ref-bernard2018bodies}{}
-Bernard, P., Legrand, S., \& Klein, O. (2018). From bodies to blame:
-Exposure to sexually objectifying media increases tolerance toward
-sexual harassment. \emph{Psychology of Popular Media Culture},
-\emph{7}(2), 99.
-
-\hypertarget{ref-briton1995}{}
-Briton, N. J., \& Hall, J. A. (1995). Beliefs about female and male
-nonverbal communication. \emph{Sex Roles}, \emph{32}(1-2), 79--90.
-
-\hypertarget{ref-brown1987lesbians}{}
-Brown, L. S. (1987). Lesbians, weight, and eating: New analyses and
-perspectives. \emph{Lesbian Psychologies: Explorations and Challenges},
-294--309.
-
-\hypertarget{ref-brownlow1998relationship}{}
-Brownlow, B. S. (1998). \emph{The relationship between objectification,
-body image disturbances, and disordered eating: Investigating race,
-socioeconomic status, acculturation and self-objectification as
-mediators.} (PhD thesis). ProQuest Information \& Learning.
-
-\hypertarget{ref-brunelletal2010}{}
-Brunell, A. B., Kernis, M. H., Goldman, B. M., Heppner, W., Davis, P.,
-Cascio, E. V., \& Webster, G. D. (2010). Dispositional authenticity and
-romantic relationship functioning. \emph{Personality and Individual
-Differences}, \emph{48}(8), 900--905.
+\leavevmode\hypertarget{ref-argyle1969}{}%
+Argyle, M., \& Williams, M. (1969). Observer or observed? A reversible perspective in person perception. \emph{Sociometry}, 396--412.
+
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-Bartky}{}%
+Bartky, S. L. (1990). Femininity and domination studies in the phenomenology of oppression.
+
+\leavevmode\hypertarget{ref-R-Matrix}{}%
+Bates, D., \& Maechler, M. (2017). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\hypertarget{ref-berger1972}{}%
+Berger, J., Cohen, B. P., \& Zelditch Jr, M. (1972). Status characteristics and social interaction. \emph{American Sociological Review}, 241--255.
+
+\leavevmode\hypertarget{ref-R-lpSolve}{}%
+Berkelaar, M., \& others. (2015). Retrieved from \url{https://CRAN.R-project.org/package=lpSolve}
+
+\leavevmode\hypertarget{ref-bernard2018bodies}{}%
+Bernard, P., Legrand, S., \& Klein, O.
+(2018).
+From bodies to blame: Exposure to sexually objectifying media increases tolerance toward sexual harassment.
+\emph{Psychology of Popular Media Culture}, \emph{7}(2), 99.
+
+\leavevmode\hypertarget{ref-briton1995}{}%
+Briton, N. J., \& Hall, J. A. (1995). Beliefs about female and male nonverbal communication. \emph{Sex Roles}, \emph{32}(1-2), 79--90.
+
+\leavevmode\hypertarget{ref-brown1987lesbians}{}%
+Brown, L. S. (1987). Lesbians, weight, and eating: New analyses and perspectives. \emph{Lesbian Psychologies: Explorations and Challenges}, 294--309.
+
+\leavevmode\hypertarget{ref-brownlow1998relationship}{}%
+Brownlow, B.
+S.
+(1998).
+\emph{The relationship between objectification, body image disturbances, and disordered eating: Investigating race, socioeconomic status, acculturation and self-objectification as mediators.} (PhD thesis).
+ProQuest Information \& Learning.
+
+\leavevmode\hypertarget{ref-brunelletal2010}{}%
+Brunell, A.
+B., Kernis, M.
+H., Goldman, B.
+M., Heppner, W., Davis, P., Cascio, E.
+V., \& Webster, G.
+D.
+(2010).
+Dispositional authenticity and romantic relationship functioning.
+\emph{Personality and Individual Differences}, \emph{48}(8), 900--905.
 doi:\href{https://doi.org/10.1016/j.paid.2010.02.018}{10.1016/j.paid.2010.02.018}
 
-\hypertarget{ref-bury2016}{}
-Bury, B., Tiggemann, M., \& Slater, A. (2016). Disclaimer labels on
-fashion magazine advertisements: Impact on visual attention and
-relationship with body dissatisfaction. \emph{Body Image}, \emph{16},
-1--9.
-
-\hypertarget{ref-calogero2004test}{}
-Calogero, R. M. (2004). A test of objectification theory: The effect of
-the male gaze on appearance concerns in college women. \emph{Psychology
-of Women Quarterly}, \emph{28}(1), 16--21.
-
-\hypertarget{ref-calogero2011}{}
-Calogero, R. M., Tantleff-Dunn, S. E., \& Thompson, J. (2011).
-\emph{Self-objectification in women: Causes, consequences, and
-counteractions.} American Psychological Association.
-
-\hypertarget{ref-R-xtable}{}
-Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J.
-(2019). \emph{Xtable: Export tables to latex or html}. Retrieved from
-\url{https://CRAN.R-project.org/package=xtable}
-
-\hypertarget{ref-deaux1987putting}{}
-Deaux, K., \& Major, B. (1987). Putting gender into context: An
-interactive model of gender-related behavior. \emph{Psychological
-Review}, \emph{94}(3), 369.
-
-\hypertarget{ref-dovidio2006nonverbal}{}
-Dovidio, J. F., Hebl, M., Richeson, J. A., \& Shelton, J. N. (2006).
-Nonverbal communication, race, and intergroup interaction.
-
-\hypertarget{ref-festinger1954theory}{}
-Festinger, L. (1954). A theory of social comparison processes.
-\emph{Human Relations}, \emph{7}(2), 117--140.
-
-\hypertarget{ref-frasernicholson1989}{}
-Fraser, N., \& Nicholson, L. (1989). Social criticism without
-philosophy: An encounter between feminism and postmodernism.
+\leavevmode\hypertarget{ref-bury2016}{}%
+Bury, B., Tiggemann, M., \& Slater, A.
+(2016).
+Disclaimer labels on fashion magazine advertisements: Impact on visual attention and relationship with body dissatisfaction.
+\emph{Body Image}, \emph{16}, 1--9.
+
+\leavevmode\hypertarget{ref-calogero2004test}{}%
+Calogero, R. M. (2004). A test of objectification theory: The effect of the male gaze on appearance concerns in college women. \emph{Psychology of Women Quarterly}, \emph{28}(1), 16--21.
+
+\leavevmode\hypertarget{ref-calogero2011}{}%
+Calogero, R. M., Tantleff-Dunn, S. E., \& Thompson, J. (2011). \emph{Self-objectification in women: Causes, consequences, and counteractions.} American Psychological Association.
+
+\leavevmode\hypertarget{ref-R-xtable}{}%
+Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to latex or html}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
+
+\leavevmode\hypertarget{ref-deaux1987putting}{}%
+Deaux, K., \& Major, B. (1987). Putting gender into context: An interactive model of gender-related behavior. \emph{Psychological Review}, \emph{94}(3), 369.
+
+\leavevmode\hypertarget{ref-dovidio2006nonverbal}{}%
+Dovidio, J. F., Hebl, M., Richeson, J. A., \& Shelton, J. N. (2006). Nonverbal communication, race, and intergroup interaction.
+
+\leavevmode\hypertarget{ref-frasernicholson1989}{}%
+Fraser, N., \& Nicholson, L.
+(1989).
+Social criticism without philosophy: An encounter between feminism and postmodernism.
 \emph{Social Text}, (21), 83.
@@
 
-\hypertarget{ref-fredricksonetal2011}{}
-Fredrickson, B. L., Hendler, L. M., Nilsen, S., O'Barr, J. F., \&
-Roberts, T.-A. (2011). Bringing back the body. \emph{Psychology of Women
-Quarterly}, \emph{35}(4), 689--696.
+\leavevmode\hypertarget{ref-fredricksonetal2011}{}%
+Fredrickson, B.
+L., Hendler, L.
+M., Nilsen, S., O'Barr, J.
+F., \& Roberts, T.-A.
+(2011).
+Bringing back the body.
+\emph{Psychology of Women Quarterly}, \emph{35}(4), 689--696.
 doi:\href{https://doi.org/10.1177/0361684311426690}{10.1177/0361684311426690}
 
-\hypertarget{ref-fredrickson1998swimsuit}{}
-Fredrickson, B. L., Roberts, T.-A., Noll, S. M., Quinn, D. M., \&
-Twenge, J. M. (1998). That swimsuit becomes you: Sex differences in
-self-objectification, restrained eating, and math performance.
+\leavevmode\hypertarget{ref-fredrickson1998swimsuit}{}%
+Fredrickson, B.
+L., Roberts, T.-A., Noll, S.
+M., Quinn, D.
+M., \& Twenge, J.
+M.
+(1998).
+That swimsuit becomes you: Sex differences in self-objectification, restrained eating, and math performance.
 \emph{Journal of Personality and Social Psychology}, \emph{75}(1), 269.
 
-\hypertarget{ref-R-irr}{}
-Gamer, M., Lemon, J., \&
-\textless{}puspendra.pusp22@gmail.com\textgreater{}, I. F. P. S. (2012).
-\emph{Irr: Various coefficients of interrater reliability and
-agreement}. Retrieved from \url{https://CRAN.R-project.org/package=irr}
-
-\hypertarget{ref-garcia2016objectification}{}
-Garcia, R. L., Earnshaw, V. A., \& Quinn, D. M. (2016). Objectification
-in action: Self-and other-objectification in mixed-sex interpersonal
-interactions. \emph{Psychology of Women Quarterly}, \emph{40}(2),
-213--228.
-
-\hypertarget{ref-garcia2015moderation}{}
-Garcia, R. L., Kenny, D. A., \& Ledermann, T. (2015). Moderation in the
-actor--partner interdependence model. \emph{Personal Relationships},
-\emph{22}(1), 8--29.
-
-\hypertarget{ref-gay2010my}{}
-Gay, R. K., \& Castano, E. (2010). My body or my mind: The impact of
-state and trait objectification on women's cognitive resources.
+\leavevmode\hypertarget{ref-R-irr}{}%
+Gamer, M., Lemon, J., \& \textless puspendra.pusp22@gmail.com\textgreater, I.
+F.
+P.
+S.
+(2012).
+\emph{Irr: Various coefficients of interrater reliability and agreement}.
+Retrieved from \url{https://CRAN.R-project.org/package=irr}
+
+\leavevmode\hypertarget{ref-garcia2016objectification}{}%
+Garcia, R.
+L., Earnshaw, V.
+A., \& Quinn, D.
+M.
+(2016).
+Objectification in action: Self-and other-objectification in mixed-sex interpersonal interactions.
+\emph{Psychology of Women Quarterly}, \emph{40}(2), 213--228.
+
+\leavevmode\hypertarget{ref-garcia2015moderation}{}%
+Garcia, R. L., Kenny, D. A., \& Ledermann, T. (2015). Moderation in the actor--partner interdependence model. \emph{Personal Relationships}, \emph{22}(1), 8--29.
+
+\leavevmode\hypertarget{ref-gay2010my}{}%
+Gay, R.
+K., \& Castano, E.
+(2010).
+My body or my mind: The impact of state and trait objectification on women's cognitive resources.
 \emph{European Journal of Social Psychology}, \emph{40}(5), 695--703.
 
-\hypertarget{ref-gervais2013my}{}
-Gervais, S. J., Holland, A. M., \& Dodd, M. D. (2013). My eyes are up
-here: The nature of the objectifying gaze toward women. \emph{Sex
-Roles}, \emph{69}(11-12), 557--570.
-
-\hypertarget{ref-gervais2020social}{}
-Gervais, S. J., Sáez, G., Riemer, A. R., \& Klein, O. (2020). The social
-interaction model of objectification: A process model of goal-based
-objectifying exchanges between men and women. \emph{British Journal of
-Social Psychology}, \emph{59}(1), 248--283.
-
-\hypertarget{ref-gervais2011you}{}
-Gervais, S. J., Vescio, T. K., \& Allen, J. (2011). When what you see is
-what you get: The consequences of the objectifying gaze for women and
-men. \emph{Psychology of Women Quarterly}, \emph{35}(1), 5--17.
-
-\hypertarget{ref-harsey2020men}{}
-Harsey, S. J., \& Zurbriggen, E. L. (2020). Men and women's
-self-objectification, objectification of women, and sexist beliefs.
-\emph{Self and Identity}, 1--8.
-
-\hypertarget{ref-hebl2005promoting}{}
-Hebl, M. R., \& Dovidio, J. F. (2005). Promoting the ``social'' in the
-examination of social stigmas. \emph{Personality and Social Psychology
-Review}, \emph{9}(2), 156--182.
-
-\hypertarget{ref-R-purrr}{}
-Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
-tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
-
-\hypertarget{ref-hill2008examining}{}
-Hill, M. S., \& Fischer, A. R. (2008). Examining objectification theory:
-Lesbian and heterosexual women's experiences with sexual-and
-self-objectification. \emph{The Counseling Psychologist}, \emph{36}(5),
-745--776.
-
-\hypertarget{ref-holland2016}{}
-Holland, E., \& Haslam, N. (2016). Cute little things: The
-objectification of prepubescent girls. \emph{Psychology of Women
-Quarterly}, \emph{40}(1), 108--119.
-
-\hypertarget{ref-R-kutils}{}
-Johnson, P., Kite, B., \& Redmon, C. (2019). \emph{Kutils: Project
-management tools}. Retrieved from
-\url{https://CRAN.R-project.org/package=kutils}
-
-\hypertarget{ref-jongenelis2014}{}
-Jongenelis, M. I., Byrne, S. M., \& Pettigrew, S. (2014).
-Self-objectification, body image disturbance, and eating disorder
-symptoms in young australian children. \emph{Body Image}, \emph{11}(3),
-290--302.
-
-\hypertarget{ref-kahalon2018don}{}
-Kahalon, R., Shnabel, N., \& Becker, J. C. (2018). ``Don't bother your
-pretty little head'' appearance compliments lead to improved mood but
-impaired cognitive performance. \emph{Psychology of Women Quarterly},
-\emph{42}(2), 136--150.
-
-\hypertarget{ref-R-ggformula}{}
-Kaplan, D., \& Pruim, R. (2017). \emph{Ggformula: Formula interface to
-the grammar of graphics}. Retrieved from
-\url{https://CRAN.R-project.org/package=ggformula}
-
-\hypertarget{ref-ledermann2017analyzing}{}
-Ledermann, T., \& Kenny, D. A. (2017). Analyzing dyadic data with
-multilevel modeling versus structural equation modeling: A tale of two
-methods. \emph{Journal of Family Psychology}, \emph{31}(4), 442.
-
-\hypertarget{ref-logel2009interacting}{}
-Logel, C., Walton, G. M., Spencer, S. J., Iserman, E. C., Hippel, W.
-von, \& Bell, A. E. (2009). Interacting with sexist men triggers social
-identity threat among female engineers. \emph{Journal of Personality and
-Social Psychology}, \emph{96}(6), 1089.
-
-\hypertarget{ref-loughnan2015exploring}{}
-Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
-Harada, C., \ldots{} Tsuchiya, K. (2015a). Exploring the role of culture
-in sexual objectification: A seven nations study. \emph{Revue
-Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
-
-\hypertarget{ref-loughnan2015}{}
-Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
-Harada, C., \ldots{} Tsuchiya, K. (2015b). Exploring the role of culture
-in sexual objectification: A seven nations study. \emph{Revue
-Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
-
-\hypertarget{ref-lum1994lesbians}{}
-LUM, E. (1994). Lesbians and physical appearance which model applies?
-\emph{Lesbian and Gay Psychology: Theory, Research, and Clinical
-Applications}, \emph{1}, 84.
-
-\hypertarget{ref-nollfredrickson1998}{}
-M. Noll, S., \& L. Fredrickson, B. (1998). A mediational model linking
-self-objectification, body shame, and disordered eating.
+\leavevmode\hypertarget{ref-gervais2013my}{}%
+Gervais, S. J., Holland, A. M., \& Dodd, M. D. (2013). My eyes are up here: The nature of the objectifying gaze toward women. \emph{Sex Roles}, \emph{69}(11-12), 557--570.
+
+\leavevmode\hypertarget{ref-gervais2020social}{}%
+Gervais, S.
+J., Sáez, G., Riemer, A.
+R., \& Klein, O.
+(2020).
+The social interaction model of objectification: A process model of goal-based objectifying exchanges between men and women.
+\emph{British Journal of Social Psychology}, \emph{59}(1), 248--283.
+
+\leavevmode\hypertarget{ref-gervais2011you}{}%
+Gervais, S.
+J., Vescio, T.
+K., \& Allen, J.
+(2011).
+When what you see is what you get: The consequences of the objectifying gaze for women and men.
+\emph{Psychology of Women Quarterly}, \emph{35}(1), 5--17.
+
+\leavevmode\hypertarget{ref-harsey2020men}{}%
+Harsey, S. J., \& Zurbriggen, E. L. (2020). Men and women's self-objectification, objectification of women, and sexist beliefs. \emph{Self and Identity}, 1--8.
+
+\leavevmode\hypertarget{ref-hebl2005promoting}{}%
+Hebl, M. R., \& Dovidio, J. F. (2005). Promoting the ``social'' in the examination of social stigmas. \emph{Personality and Social Psychology Review}, \emph{9}(2), 156--182.
+
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-R-ggstance}{}%
+Henry, L., Wickham, H., \& Chang, W. (2019). \emph{Ggstance: Horizontal 'ggplot2' components}. Retrieved from \url{https://CRAN.R-project.org/package=ggstance}
+
+\leavevmode\hypertarget{ref-hill2008examining}{}%
+Hill, M.
+S., \& Fischer, A.
+R.
+(2008).
+Examining objectification theory: Lesbian and heterosexual women's experiences with sexual-and self-objectification.
+\emph{The Counseling Psychologist}, \emph{36}(5), 745--776.
+
+\leavevmode\hypertarget{ref-holland2016}{}%
+Holland, E., \& Haslam, N. (2016). Cute little things: The objectification of prepubescent girls. \emph{Psychology of Women Quarterly}, \emph{40}(1), 108--119.
+
+\leavevmode\hypertarget{ref-R-kutils}{}%
+Johnson, P., Kite, B., \& Redmon, C. (2019). \emph{Kutils: Project management tools}. Retrieved from \url{https://CRAN.R-project.org/package=kutils}
+
+\leavevmode\hypertarget{ref-jongenelis2014}{}%
+Jongenelis, M.
+I., Byrne, S.
+M., \& Pettigrew, S.
+(2014).
+Self-objectification, body image disturbance, and eating disorder symptoms in young australian children.
+\emph{Body Image}, \emph{11}(3), 290--302.
+
+\leavevmode\hypertarget{ref-kahalon2018don}{}%
+Kahalon, R., Shnabel, N., \& Becker, J.
+C.
+(2018).
+``Don't bother your pretty little head'' appearance compliments lead to improved mood but impaired cognitive performance.
+\emph{Psychology of Women Quarterly}, \emph{42}(2), 136--150.
+
+\leavevmode\hypertarget{ref-R-ggformula}{}%
+Kaplan, D., \& Pruim, R. (2017). \emph{Ggformula: Formula interface to the grammar of graphics}. Retrieved from \url{https://CRAN.R-project.org/package=ggformula}
+
+\leavevmode\hypertarget{ref-ledermann2017analyzing}{}%
+Ledermann, T., \& Kenny, D.
+A.
+(2017).
+Analyzing dyadic data with multilevel modeling versus structural equation modeling: A tale of two methods.
+\emph{Journal of Family Psychology}, \emph{31}(4), 442.
+
+\leavevmode\hypertarget{ref-logel2009interacting}{}%
+Logel, C., Walton, G.
+M., Spencer, S.
+J., Iserman, E.
+C., Hippel, W.
+von, \& Bell, A.
+E.
+(2009).
+Interacting with sexist men triggers social identity threat among female engineers.
+\emph{Journal of Personality and Social Psychology}, \emph{96}(6), 1089.
+
+\leavevmode\hypertarget{ref-loughnan2015exploring}{}%
+Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M., Harada, C., \ldots{} Tsuchiya, K.
+(2015a).
+Exploring the role of culture in sexual objectification: A seven nations study.
+\emph{Revue Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
+
+\leavevmode\hypertarget{ref-loughnan2015}{}%
+Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M., Harada, C., \ldots{} Tsuchiya, K.
+(2015b).
+Exploring the role of culture in sexual objectification: A seven nations study.
+\emph{Revue Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
+
+\leavevmode\hypertarget{ref-lum1994lesbians}{}%
+LUM, E. (1994). Lesbians and physical appearance which model applies? \emph{Lesbian and Gay Psychology: Theory, Research, and Clinical Applications}, \emph{1}, 84.
+
+\leavevmode\hypertarget{ref-mcfarlin1984remote}{}%
+McFarlin, D.
+B., \& Blascovich, J.
+(1984).
+On the remote associates test (rat) as an alternative to illusory performance feedback: A methodological note.
+\emph{Basic and Applied Social Psychology}, \emph{5}(3), 223--229.
+
+\leavevmode\hypertarget{ref-meltzer2020women}{}%
+Meltzer, A. L. (2020). Women can benefit from sexual and physical valuation in the context of a romantic relationship. \emph{Personality and Social Psychology Bulletin}, \emph{46}(2), 243--257.
+
+\leavevmode\hypertarget{ref-miles2015stop}{}%
+Miles-McLean, H., Liss, M., Erchull, M.
+J., Robertson, C.
+M., Hagerman, C., Gnoleba, M.
+A., \& Papp, L.
+J.
+(2015).
+``Stop looking at me!'' Interpersonal sexual objectification as a source of insidious trauma.
+\emph{Psychology of Women Quarterly}, \emph{39}(3), 363--374.
+
+\leavevmode\hypertarget{ref-nollfredrickson1998}{}%
+M.
+Noll, S., \& L.
+Fredrickson, B.
+(1998).
+A mediational model linking self-objectification, body shame, and disordered eating.
 \emph{Psychology of Women Quarterly}, \emph{22}, 623--636.
@@
 
-\hypertarget{ref-mcfarlin1984remote}{}
-McFarlin, D. B., \& Blascovich, J. (1984). On the remote associates test
-(rat) as an alternative to illusory performance feedback: A
-methodological note. \emph{Basic and Applied Social Psychology},
-\emph{5}(3), 223--229.
-
-\hypertarget{ref-meltzer2020women}{}
-Meltzer, A. L. (2020). Women can benefit from sexual and physical
-valuation in the context of a romantic relationship. \emph{Personality
-and Social Psychology Bulletin}, \emph{46}(2), 243--257.
-
-\hypertarget{ref-miles2015stop}{}
-Miles-McLean, H., Liss, M., Erchull, M. J., Robertson, C. M., Hagerman,
-C., Gnoleba, M. A., \& Papp, L. J. (2015). ``Stop looking at me!''
-interpersonal sexual objectification as a source of insidious trauma.
+\leavevmode\hypertarget{ref-moradi2008}{}%
+Moradi, B., \& Huang, Y.-P. (2008). Objectification theory and psychology of women: A decade of advances and future directions. \emph{Psychology of Women Quarterly}, \emph{32}(4), 377--398.
+
+\leavevmode\hypertarget{ref-morry2001magazine}{}%
+Morry, M.
+M., \& Staska, S.
+L.
+(2001).
+Magazine exposure: Internalization, self-objectification, eating attitudes, and body satisfaction in male and female university students.
+\emph{Canadian Journal of Behavioural Science/Revue Canadienne Des Sciences Du Comportement}, \emph{33}(4), 269.
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\hypertarget{ref-noffsinger2004objectification}{}%
+Noffsinger-Frazier, N.
+A.
+(2004).
+\emph{Objectification theory and disordered eating: The impact of feminist identification, internalization of sociocultural standards of appearance, and sexual orientation}.
+The University of Memphis.
+
+\leavevmode\hypertarget{ref-olsen2006structural}{}%
+Olsen, J. A., \& Kenny, D. A. (2006). Structural equation modeling with interchangeable dyads. \emph{Psychological Methods}, \emph{11}(2), 127.
+
+\leavevmode\hypertarget{ref-grayobrien2007}{}%
+P.
+Gray, M., \& M.
+OBrien, K.
+(2007).
+Advancing the assessment of women's career choices: The career aspiration scale.
+\emph{Journal of Career Assessment - J CAREER ASSESSMENT}, \emph{15}, 317--337.
+doi:\href{https://doi.org/10.1177/1069072707301211}{10.1177/1069072707301211}
+
+\leavevmode\hypertarget{ref-R-nlme}{}%
+Pinheiro, J., Bates, D., DebRoy, S., Sarkar, D., \& R Core Team. (2017). \emph{nlme: Linear and nonlinear mixed effects models}. Retrieved from \url{https://CRAN.R-project.org/package=nlme}
+
+\leavevmode\hypertarget{ref-pitman1999body}{}%
+Pitman, G. E. (1999). Body image, compulsory heterosexuality, and internalized homophobia. \emph{Journal of Lesbian Studies}, \emph{3}(4), 129--139.
+
+\leavevmode\hypertarget{ref-R-mosaicData}{}%
+Pruim, R., Kaplan, D., \& Horton, N. (2016). \emph{MosaicData: Project mosaic data sets}. Retrieved from \url{https://CRAN.R-project.org/package=mosaicData}
+
+\leavevmode\hypertarget{ref-R-mosaic}{}%
+Pruim, R., Kaplan, D.
+T., \& Horton, N.
+J.
+(2017).
+The mosaic package: Helping students to 'think with data' using r.
+\emph{The R Journal}, \emph{9}(1), 77--102.
+Retrieved from \url{https://journal.r-project.org/archive/2017/RJ-2017-024/index.html}
+
+\leavevmode\hypertarget{ref-puvia2013being}{}%
+Puvia, E., \& Vaes, J. (2013). Being a body: Women's appearance related self-views and their dehumanization of sexually objectified female targets. \emph{Sex Roles}, \emph{68}(7-8), 484--495.
+
+\leavevmode\hypertarget{ref-quinnetal}{}%
+Quinn, D.
+M., Chaudoir, S.
+R., \& Kallen, R.
+W.
+(2011).
+Performance and flow: A review and integration of self-objectification research.
+\emph{Self-Objectification in Women: Causes, Consequences, and Counteractions.}, 119--138.
+doi:\href{https://doi.org/10.1037/12304-006}{10.1037/12304-006}
+
+\leavevmode\hypertarget{ref-quinn2011performance}{}%
+Quinn, D. M., Chaudoir, S. R., \& Kallen, R. W. (2011). Performance and flow: A review and integration of self-objectification research.
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2017). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2017).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
+\leavevmode\hypertarget{ref-robertsfredrickson}{}%
+Roberts, T.-A., \& Fredrickson, B. L. (1997). Objectification theory. \emph{Encyclopedia of Social Psychology}. doi:\href{https://doi.org/10.4135/9781412956253.n377}{10.4135/9781412956253.n377}
+
+\leavevmode\hypertarget{ref-R-lavaan}{}%
+Rosseel, Y. (2012). lavaan: An R package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{http://www.jstatsoft.org/v48/i02/}
+
+\leavevmode\hypertarget{ref-rubin1975}{}%
+Rubin, J. (1975). What the "good language learner" can teach us. \emph{TESOL Quarterly}, \emph{9}(1), 41. doi:\href{https://doi.org/10.2307/3586011}{10.2307/3586011}
+
+\leavevmode\hypertarget{ref-saguyetal2010}{}%
+Saguy, T., Quinn, D., F Dovidio, J., \& Pratto, F.
+(2010).
+Interacting like a body: Objectification can lead women to narrow their presence in social interactions.
+\emph{Psychological Science}, \emph{21}, 178--82.
+doi:\href{https://doi.org/10.1177/0956797609357751}{10.1177/0956797609357751}
+
+\leavevmode\hypertarget{ref-sanchez2008romance}{}%
+Sanchez, D.
+T., \& Broccoli, T.
+L.
+(2008).
+The romance of self-objectification: Does priming romantic relationships induce states of self-objectification among women?
+\emph{Sex Roles}, \emph{59}(7-8), 545--554.
+
+\leavevmode\hypertarget{ref-R-lattice}{}%
+Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
+
+\leavevmode\hypertarget{ref-siever1994sexual}{}%
+Siever, M.
+D.
+(1994).
+Sexual orientation and gender as factors in socioculturally acquired vulnerability to body dissatisfaction and eating disorders.
+\emph{Journal of Consulting and Clinical Psychology}, \emph{62}(2), 252.
+
+\leavevmode\hypertarget{ref-R-apaTables}{}%
+Stanley, D. (2018). \emph{ApaTables: Create american psychological association (apa) style tables}. Retrieved from \url{https://CRAN.R-project.org/package=apaTables}
+
+\leavevmode\hypertarget{ref-strelan2005women}{}%
+Strelan, P., \& Hargreaves, D. (2005). Women who objectify other women: The vicious circle of objectification? \emph{Sex Roles}, \emph{52}(9-10), 707--712.
+
+\leavevmode\hypertarget{ref-strelan2018birds}{}%
+Strelan, P., \& Pagoudis, S.
+(2018).
+Birds of a feather flock together: The interpersonal process of objectification within intimate heterosexual relationships.
+\emph{Sex Roles}, \emph{79}(1-2), 72--82.
+
+\leavevmode\hypertarget{ref-strong2000eating}{}%
+Strong, S.
+M., Williamson, D.
+A., Netemeyer, R.
+G., \& Geer, J.
+H.
+(2000).
+Eating disorder symptoms and concerns about body differ as a function of gender and sexual orientation.
+\emph{Journal of Social and Clinical Psychology}, \emph{19}(2), 240--255.
+
+\leavevmode\hypertarget{ref-swimetal}{}%
+Swim, J.
+K., Hyers, L.
+L., Cohen, L.
+L., \& Ferguson, M.
+J.
+(2001).
+Everyday sexism: Evidence for its incidence, nature, and psychological impact from three daily diary studies.
+\emph{Journal of Social Issues}, \emph{57}(1), 31--53.
+doi:\href{https://doi.org/10.1111/0022-4537.00200}{10.1111/0022-4537.00200}
+
+\leavevmode\hypertarget{ref-tolman2006looking}{}%
+Tolman, D.
+L., Impett, E.
+A., Tracy, A.
+J., \& Michael, A.
+(2006).
+Looking good, sounding good: Femininity ideology and adolescent girls' mental health.
+\emph{Psychology of Women Quarterly}, \emph{30}(1), 85--95.
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2018). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-usethis}{}%
+Wickham, H., \& Bryan, J. (2018). \emph{Usethis: Automate package and project setup}. Retrieved from \url{https://CRAN.R-project.org/package=usethis}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2018a). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Easily tidy data with 'spread()' and 'gather()' functions}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-devtools}{}%
+Wickham, H., Hester, J., \& Chang, W. (2018b). \emph{Devtools: Tools to make developing r packages easier}. Retrieved from \url{https://CRAN.R-project.org/package=devtools}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2017). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-R-haven}{}%
+Wickham, H., \& Miller, E. (2019). \emph{Haven: Import and export 'spss', 'stata' and 'sas' files}. Retrieved from \url{https://CRAN.R-project.org/package=haven}
+
+\leavevmode\hypertarget{ref-wollast2020cultural}{}%
+Wollast, R., Riemer, A.
+R., Gervais, S.
+J., Grigoryan, L., Bernard, P., \& Klein, O.
+(2020).
+How cultural orientation and self-compassion shape objectified body consciousness for women from america, belgium, russia, and thailand.
+\emph{Self and Identity}, 1--21.
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
+
+\leavevmode\hypertarget{ref-yilmaz2019whose}{}%
+Yilmaz, T., \& Bozo, Ö.
+(2019).
+Whose gaze is more objectifying?
+An experimental study of college women's state self-objectification, body shame, negative mood, and body dissatisfaction.
+\emph{Mediterranean Journal of Clinical Psychology}, \emph{7}(2).
+
+\leavevmode\hypertarget{ref-young1979}{}%
+Young, I. M. (1979). \emph{Proceedings of the second sex---thirty years later: A commemorative conference on feminist theory,}
+
+\leavevmode\hypertarget{ref-zurbriggen2011self}{}%
+Zurbriggen, E.
+L., Ramsey, L.
+R., \& Jaworski, B.
+K.
+(2011).
+Self-and partner-objectification in romantic relationships: Associations with media consumption and relationship satisfaction.
+\emph{Sex Roles}, \emph{64}(7-8), 449--462.
+
+\leavevmode\hypertarget{ref-argyle1969}{}%
+Argyle, M., \& Williams, M. (1969). Observer or observed? A reversible perspective in person perception. \emph{Sociometry}, 396--412.
+
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-Bartky}{}%
+Bartky, S. L. (1990). Femininity and domination studies in the phenomenology of oppression.
+
+\leavevmode\hypertarget{ref-R-Matrix}{}%
+Bates, D., \& Maechler, M. (2017). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\hypertarget{ref-berger1972}{}%
+Berger, J., Cohen, B. P., \& Zelditch Jr, M. (1972). Status characteristics and social interaction. \emph{American Sociological Review}, 241--255.
+
+\leavevmode\hypertarget{ref-R-lpSolve}{}%
+Berkelaar, M., \& others. (2015). Retrieved from \url{https://CRAN.R-project.org/package=lpSolve}
+
+\leavevmode\hypertarget{ref-bernard2018bodies}{}%
+Bernard, P., Legrand, S., \& Klein, O.
+(2018).
+From bodies to blame: Exposure to sexually objectifying media increases tolerance toward sexual harassment.
+\emph{Psychology of Popular Media Culture}, \emph{7}(2), 99.
+
+\leavevmode\hypertarget{ref-briton1995}{}%
+Briton, N. J., \& Hall, J. A. (1995). Beliefs about female and male nonverbal communication. \emph{Sex Roles}, \emph{32}(1-2), 79--90.
+
+\leavevmode\hypertarget{ref-brown1987lesbians}{}%
+Brown, L. S. (1987). Lesbians, weight, and eating: New analyses and perspectives. \emph{Lesbian Psychologies: Explorations and Challenges}, 294--309.
+
+\leavevmode\hypertarget{ref-brownlow1998relationship}{}%
+Brownlow, B.
+S.
+(1998).
+\emph{The relationship between objectification, body image disturbances, and disordered eating: Investigating race, socioeconomic status, acculturation and self-objectification as mediators.} (PhD thesis).
+ProQuest Information \& Learning.
+
+\leavevmode\hypertarget{ref-brunelletal2010}{}%
+Brunell, A.
+B., Kernis, M.
+H., Goldman, B.
+M., Heppner, W., Davis, P., Cascio, E.
+V., \& Webster, G.
+D.
+(2010).
+Dispositional authenticity and romantic relationship functioning.
+\emph{Personality and Individual Differences}, \emph{48}(8), 900--905.
+doi:\href{https://doi.org/10.1016/j.paid.2010.02.018}{10.1016/j.paid.2010.02.018}
+
+\leavevmode\hypertarget{ref-bury2016}{}%
+Bury, B., Tiggemann, M., \& Slater, A.
+(2016).
+Disclaimer labels on fashion magazine advertisements: Impact on visual attention and relationship with body dissatisfaction.
+\emph{Body Image}, \emph{16}, 1--9.
+
+\leavevmode\hypertarget{ref-calogero2004test}{}%
+Calogero, R. M. (2004). A test of objectification theory: The effect of the male gaze on appearance concerns in college women. \emph{Psychology of Women Quarterly}, \emph{28}(1), 16--21.
+
+\leavevmode\hypertarget{ref-calogero2011}{}%
+Calogero, R. M., Tantleff-Dunn, S. E., \& Thompson, J. (2011). \emph{Self-objectification in women: Causes, consequences, and counteractions.} American Psychological Association.
+
+\leavevmode\hypertarget{ref-R-xtable}{}%
+Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to latex or html}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
+
+\leavevmode\hypertarget{ref-deaux1987putting}{}%
+Deaux, K., \& Major, B. (1987). Putting gender into context: An interactive model of gender-related behavior. \emph{Psychological Review}, \emph{94}(3), 369.
+
+\leavevmode\hypertarget{ref-dovidio2006nonverbal}{}%
+Dovidio, J. F., Hebl, M., Richeson, J. A., \& Shelton, J. N. (2006). Nonverbal communication, race, and intergroup interaction.
+
+\leavevmode\hypertarget{ref-frasernicholson1989}{}%
+Fraser, N., \& Nicholson, L.
+(1989).
+Social criticism without philosophy: An encounter between feminism and postmodernism.
+\emph{Social Text}, (21), 83.
+doi:\href{https://doi.org/10.2307/827810}{10.2307/827810}
+
+\leavevmode\hypertarget{ref-fredricksonetal2011}{}%
+Fredrickson, B.
+L., Hendler, L.
+M., Nilsen, S., O'Barr, J.
+F., \& Roberts, T.-A.
+(2011).
+Bringing back the body.
+\emph{Psychology of Women Quarterly}, \emph{35}(4), 689--696.
+doi:\href{https://doi.org/10.1177/0361684311426690}{10.1177/0361684311426690}
+
+\leavevmode\hypertarget{ref-fredrickson1998swimsuit}{}%
+Fredrickson, B.
+L., Roberts, T.-A., Noll, S.
+M., Quinn, D.
+M., \& Twenge, J.
+M.
+(1998).
+That swimsuit becomes you: Sex differences in self-objectification, restrained eating, and math performance.
+\emph{Journal of Personality and Social Psychology}, \emph{75}(1), 269.
+
+\leavevmode\hypertarget{ref-R-irr}{}%
+Gamer, M., Lemon, J., \& \textless puspendra.pusp22@gmail.com\textgreater, I.
+F.
+P.
+S.
+(2012).
+\emph{Irr: Various coefficients of interrater reliability and agreement}.
+Retrieved from \url{https://CRAN.R-project.org/package=irr}
+
+\leavevmode\hypertarget{ref-garcia2016objectification}{}%
+Garcia, R.
+L., Earnshaw, V.
+A., \& Quinn, D.
+M.
+(2016).
+Objectification in action: Self-and other-objectification in mixed-sex interpersonal interactions.
+\emph{Psychology of Women Quarterly}, \emph{40}(2), 213--228.
+
+\leavevmode\hypertarget{ref-garcia2015moderation}{}%
+Garcia, R. L., Kenny, D. A., \& Ledermann, T. (2015). Moderation in the actor--partner interdependence model. \emph{Personal Relationships}, \emph{22}(1), 8--29.
+
+\leavevmode\hypertarget{ref-gay2010my}{}%
+Gay, R.
+K., \& Castano, E.
+(2010).
+My body or my mind: The impact of state and trait objectification on women's cognitive resources.
+\emph{European Journal of Social Psychology}, \emph{40}(5), 695--703.
+
+\leavevmode\hypertarget{ref-gervais2013my}{}%
+Gervais, S. J., Holland, A. M., \& Dodd, M. D. (2013). My eyes are up here: The nature of the objectifying gaze toward women. \emph{Sex Roles}, \emph{69}(11-12), 557--570.
+
+\leavevmode\hypertarget{ref-gervais2020social}{}%
+Gervais, S.
+J., Sáez, G., Riemer, A.
+R., \& Klein, O.
+(2020).
+The social interaction model of objectification: A process model of goal-based objectifying exchanges between men and women.
+\emph{British Journal of Social Psychology}, \emph{59}(1), 248--283.
+
+\leavevmode\hypertarget{ref-gervais2011you}{}%
+Gervais, S.
+J., Vescio, T.
+K., \& Allen, J.
+(2011).
+When what you see is what you get: The consequences of the objectifying gaze for women and men.
+\emph{Psychology of Women Quarterly}, \emph{35}(1), 5--17.
+
+\leavevmode\hypertarget{ref-harsey2020men}{}%
+Harsey, S. J., \& Zurbriggen, E. L. (2020). Men and women's self-objectification, objectification of women, and sexist beliefs. \emph{Self and Identity}, 1--8.
+
+\leavevmode\hypertarget{ref-hebl2005promoting}{}%
+Hebl, M. R., \& Dovidio, J. F. (2005). Promoting the ``social'' in the examination of social stigmas. \emph{Personality and Social Psychology Review}, \emph{9}(2), 156--182.
+
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-R-ggstance}{}%
+Henry, L., Wickham, H., \& Chang, W. (2019). \emph{Ggstance: Horizontal 'ggplot2' components}. Retrieved from \url{https://CRAN.R-project.org/package=ggstance}
+
+\leavevmode\hypertarget{ref-hill2008examining}{}%
+Hill, M.
+S., \& Fischer, A.
+R.
+(2008).
+Examining objectification theory: Lesbian and heterosexual women's experiences with sexual-and self-objectification.
+\emph{The Counseling Psychologist}, \emph{36}(5), 745--776.
+
+\leavevmode\hypertarget{ref-holland2016}{}%
+Holland, E., \& Haslam, N. (2016). Cute little things: The objectification of prepubescent girls. \emph{Psychology of Women Quarterly}, \emph{40}(1), 108--119.
+
+\leavevmode\hypertarget{ref-R-kutils}{}%
+Johnson, P., Kite, B., \& Redmon, C. (2019). \emph{Kutils: Project management tools}. Retrieved from \url{https://CRAN.R-project.org/package=kutils}
+
+\leavevmode\hypertarget{ref-jongenelis2014}{}%
+Jongenelis, M.
+I., Byrne, S.
+M., \& Pettigrew, S.
+(2014).
+Self-objectification, body image disturbance, and eating disorder symptoms in young australian children.
+\emph{Body Image}, \emph{11}(3), 290--302.
+
+\leavevmode\hypertarget{ref-kahalon2018don}{}%
+Kahalon, R., Shnabel, N., \& Becker, J.
+C.
+(2018).
+``Don't bother your pretty little head'' appearance compliments lead to improved mood but impaired cognitive performance.
+\emph{Psychology of Women Quarterly}, \emph{42}(2), 136--150.
+
+\leavevmode\hypertarget{ref-R-ggformula}{}%
+Kaplan, D., \& Pruim, R. (2017). \emph{Ggformula: Formula interface to the grammar of graphics}. Retrieved from \url{https://CRAN.R-project.org/package=ggformula}
+
+\leavevmode\hypertarget{ref-ledermann2017analyzing}{}%
+Ledermann, T., \& Kenny, D.
+A.
+(2017).
+Analyzing dyadic data with multilevel modeling versus structural equation modeling: A tale of two methods.
+\emph{Journal of Family Psychology}, \emph{31}(4), 442.
+
+\leavevmode\hypertarget{ref-logel2009interacting}{}%
+Logel, C., Walton, G.
+M., Spencer, S.
+J., Iserman, E.
+C., Hippel, W.
+von, \& Bell, A.
+E.
+(2009).
+Interacting with sexist men triggers social identity threat among female engineers.
+\emph{Journal of Personality and Social Psychology}, \emph{96}(6), 1089.
+
+\leavevmode\hypertarget{ref-loughnan2015exploring}{}%
+Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M., Harada, C., \ldots{} Tsuchiya, K.
+(2015a).
+Exploring the role of culture in sexual objectification: A seven nations study.
+\emph{Revue Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
+
+\leavevmode\hypertarget{ref-loughnan2015}{}%
+Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M., Harada, C., \ldots{} Tsuchiya, K.
+(2015b).
+Exploring the role of culture in sexual objectification: A seven nations study.
+\emph{Revue Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
+
+\leavevmode\hypertarget{ref-lum1994lesbians}{}%
+LUM, E. (1994). Lesbians and physical appearance which model applies? \emph{Lesbian and Gay Psychology: Theory, Research, and Clinical Applications}, \emph{1}, 84.
+
+\leavevmode\hypertarget{ref-mcfarlin1984remote}{}%
+McFarlin, D.
+B., \& Blascovich, J.
+(1984).
+On the remote associates test (rat) as an alternative to illusory performance feedback: A methodological note.
+\emph{Basic and Applied Social Psychology}, \emph{5}(3), 223--229.
+
+\leavevmode\hypertarget{ref-meltzer2020women}{}%
+Meltzer, A. L. (2020). Women can benefit from sexual and physical valuation in the context of a romantic relationship. \emph{Personality and Social Psychology Bulletin}, \emph{46}(2), 243--257.
+
+\leavevmode\hypertarget{ref-miles2015stop}{}%
+Miles-McLean, H., Liss, M., Erchull, M.
+J., Robertson, C.
+M., Hagerman, C., Gnoleba, M.
+A., \& Papp, L.
+J.
+(2015).
+``Stop looking at me!'' Interpersonal sexual objectification as a source of insidious trauma.
 \emph{Psychology of Women Quarterly}, \emph{39}(3), 363--374.
 
-\hypertarget{ref-moradi2008}{}
-Moradi, B., \& Huang, Y.-P. (2008). Objectification theory and
-psychology of women: A decade of advances and future directions.
-\emph{Psychology of Women Quarterly}, \emph{32}(4), 377--398.
-
-\hypertarget{ref-morry2001magazine}{}
-Morry, M. M., \& Staska, S. L. (2001). Magazine exposure:
-Internalization, self-objectification, eating attitudes, and body
-satisfaction in male and female university students. \emph{Canadian
-Journal of Behavioural Science/Revue Canadienne Des Sciences Du
-Comportement}, \emph{33}(4), 269.
-
-\hypertarget{ref-R-tibble}{}
-Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
-Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
-\hypertarget{ref-noffsinger2004objectification}{}
-Noffsinger-Frazier, N. A. (2004). \emph{Objectification theory and
-disordered eating: The impact of feminist identification,
-internalization of sociocultural standards of appearance, and sexual
-orientation}. The University of Memphis.
-
-\hypertarget{ref-olsen2006structural}{}
-Olsen, J. A., \& Kenny, D. A. (2006). Structural equation modeling with
-interchangeable dyads. \emph{Psychological Methods}, \emph{11}(2), 127.
-
-\hypertarget{ref-grayobrien2007}{}
-P. Gray, M., \& M. OBrien, K. (2007). Advancing the assessment of
-women's career choices: The career aspiration scale. \emph{Journal of
-Career Assessment - J CAREER ASSESSMENT}, \emph{15}, 317--337.
+\leavevmode\hypertarget{ref-nollfredrickson1998}{}%
+M.
+Noll, S., \& L.
+Fredrickson, B.
+(1998).
+A mediational model linking self-objectification, body shame, and disordered eating.
+\emph{Psychology of Women Quarterly}, \emph{22}, 623--636.
+doi:\href{https://doi.org/10.1111/j.1471-6402.1998.tb00181.x}{10.1111/j.1471-6402.1998.tb00181.x}
+
+\leavevmode\hypertarget{ref-moradi2008}{}%
+Moradi, B., \& Huang, Y.-P. (2008). Objectification theory and psychology of women: A decade of advances and future directions. \emph{Psychology of Women Quarterly}, \emph{32}(4), 377--398.
+
+\leavevmode\hypertarget{ref-morry2001magazine}{}%
+Morry, M.
+M., \& Staska, S.
+L.
+(2001).
+Magazine exposure: Internalization, self-objectification, eating attitudes, and body satisfaction in male and female university students.
+\emph{Canadian Journal of Behavioural Science/Revue Canadienne Des Sciences Du Comportement}, \emph{33}(4), 269.
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\hypertarget{ref-noffsinger2004objectification}{}%
+Noffsinger-Frazier, N.
+A.
+(2004).
+\emph{Objectification theory and disordered eating: The impact of feminist identification, internalization of sociocultural standards of appearance, and sexual orientation}.
+The University of Memphis.
+
+\leavevmode\hypertarget{ref-olsen2006structural}{}%
+Olsen, J. A., \& Kenny, D. A. (2006). Structural equation modeling with interchangeable dyads. \emph{Psychological Methods}, \emph{11}(2), 127.
+
+\leavevmode\hypertarget{ref-grayobrien2007}{}%
+P.
+Gray, M., \& M.
+OBrien, K.
+(2007).
+Advancing the assessment of women's career choices: The career aspiration scale.
+\emph{Journal of Career Assessment - J CAREER ASSESSMENT}, \emph{15}, 317--337.
 doi:\href{https://doi.org/10.1177/1069072707301211}{10.1177/1069072707301211}
 
-\hypertarget{ref-R-nlme}{}
-Pinheiro, J., Bates, D., DebRoy, S., Sarkar, D., \& R Core Team. (2017).
-\emph{nlme: Linear and nonlinear mixed effects models}. Retrieved from
-\url{https://CRAN.R-project.org/package=nlme}
-
-\hypertarget{ref-pitman1999body}{}
-Pitman, G. E. (1999). Body image, compulsory heterosexuality, and
-internalized homophobia. \emph{Journal of Lesbian Studies}, \emph{3}(4),
-129--139.
-
-\hypertarget{ref-R-mosaic}{}
-Pruim, R., Kaplan, D. T., \& Horton, N. J. (2017). The mosaic package:
-Helping students to 'think with data' using r. \emph{The R Journal},
-\emph{9}(1), 77--102. Retrieved from
-\url{https://journal.r-project.org/archive/2017/RJ-2017-024/index.html}
-
-\hypertarget{ref-R-mosaicData}{}
-Pruim, R., Kaplan, D., \& Horton, N. (2016). \emph{MosaicData: Project
-mosaic data sets}. Retrieved from
-\url{https://CRAN.R-project.org/package=mosaicData}
-
-\hypertarget{ref-puvia2013being}{}
-Puvia, E., \& Vaes, J. (2013). Being a body: Women's appearance related
-self-views and their dehumanization of sexually objectified female
-targets. \emph{Sex Roles}, \emph{68}(7-8), 484--495.
-
-\hypertarget{ref-quinnetal}{}
-Quinn, D. M., Chaudoir, S. R., \& Kallen, R. W. (2011). Performance and
-flow: A review and integration of self-objectification research.
-\emph{Self-Objectification in Women: Causes, Consequences, and
-Counteractions.}, 119--138.
+\leavevmode\hypertarget{ref-R-nlme}{}%
+Pinheiro, J., Bates, D., DebRoy, S., Sarkar, D., \& R Core Team. (2017). \emph{nlme: Linear and nonlinear mixed effects models}. Retrieved from \url{https://CRAN.R-project.org/package=nlme}
+
+\leavevmode\hypertarget{ref-pitman1999body}{}%
+Pitman, G. E. (1999). Body image, compulsory heterosexuality, and internalized homophobia. \emph{Journal of Lesbian Studies}, \emph{3}(4), 129--139.
+
+\leavevmode\hypertarget{ref-R-mosaicData}{}%
+Pruim, R., Kaplan, D., \& Horton, N. (2016). \emph{MosaicData: Project mosaic data sets}. Retrieved from \url{https://CRAN.R-project.org/package=mosaicData}
+
+\leavevmode\hypertarget{ref-R-mosaic}{}%
+Pruim, R., Kaplan, D.
+T., \& Horton, N.
+J.
+(2017).
+The mosaic package: Helping students to 'think with data' using r.
+\emph{The R Journal}, \emph{9}(1), 77--102.
+Retrieved from \url{https://journal.r-project.org/archive/2017/RJ-2017-024/index.html}
+
+\leavevmode\hypertarget{ref-puvia2013being}{}%
+Puvia, E., \& Vaes, J. (2013). Being a body: Women's appearance related self-views and their dehumanization of sexually objectified female targets. \emph{Sex Roles}, \emph{68}(7-8), 484--495.
+
+\leavevmode\hypertarget{ref-quinnetal}{}%
+Quinn, D.
+M., Chaudoir, S.
+R., \& Kallen, R.
+W.
+(2011).
+Performance and flow: A review and integration of self-objectification research.
+\emph{Self-Objectification in Women: Causes, Consequences, and Counteractions.}, 119--138.
 doi:\href{https://doi.org/10.1037/12304-006}{10.1037/12304-006}
 
-\hypertarget{ref-quinn2011performance}{}
-Quinn, D. M., Chaudoir, S. R., \& Kallen, R. W. (2011). Performance and
-flow: A review and integration of self-objectification research.
-
-\hypertarget{ref-R-base}{}
-R Core Team. (2017). \emph{R: A language and environment for statistical
-computing}. Vienna, Austria: R Foundation for Statistical Computing.
-Retrieved from \url{https://www.R-project.org/}
-
-\hypertarget{ref-R-psych}{}
-Revelle, W. (2017). \emph{Psych: Procedures for psychological,
-psychometric, and personality research}. Evanston, Illinois:
-Northwestern University. Retrieved from
-\url{https://CRAN.R-project.org/package=psych}
-
-\hypertarget{ref-robertsfredrickson}{}
-Roberts, T.-A., \& Fredrickson, B. L. (1997). Objectification theory.
-\emph{Encyclopedia of Social Psychology}.
-doi:\href{https://doi.org/10.4135/9781412956253.n377}{10.4135/9781412956253.n377}
-
-\hypertarget{ref-R-lavaan}{}
-Rosseel, Y. (2012). lavaan: An R package for structural equation
-modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36.
-Retrieved from \url{http://www.jstatsoft.org/v48/i02/}
-
-\hypertarget{ref-rubin1975}{}
-Rubin, J. (1975). What the ``good language learner'' can teach us.
-\emph{TESOL Quarterly}, \emph{9}(1), 41.
-doi:\href{https://doi.org/10.2307/3586011}{10.2307/3586011}
-
-\hypertarget{ref-saguyetal2010}{}
-Saguy, T., Quinn, D., F Dovidio, J., \& Pratto, F. (2010). Interacting
-like a body: Objectification can lead women to narrow their presence in
-social interactions. \emph{Psychological Science}, \emph{21}, 178--82.
+\leavevmode\hypertarget{ref-quinn2011performance}{}%
+Quinn, D. M., Chaudoir, S. R., \& Kallen, R. W. (2011). Performance and flow: A review and integration of self-objectification research.
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2017). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2017).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
+\leavevmode\hypertarget{ref-robertsfredrickson}{}%
+Roberts, T.-A., \& Fredrickson, B. L. (1997). Objectification theory. \emph{Encyclopedia of Social Psychology}. doi:\href{https://doi.org/10.4135/9781412956253.n377}{10.4135/9781412956253.n377}
+
+\leavevmode\hypertarget{ref-R-lavaan}{}%
+Rosseel, Y. (2012). lavaan: An R package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{http://www.jstatsoft.org/v48/i02/}
+
+\leavevmode\hypertarget{ref-rubin1975}{}%
+Rubin, J. (1975). What the "good language learner" can teach us. \emph{TESOL Quarterly}, \emph{9}(1), 41. doi:\href{https://doi.org/10.2307/3586011}{10.2307/3586011}
+
+\leavevmode\hypertarget{ref-saguyetal2010}{}%
+Saguy, T., Quinn, D., F Dovidio, J., \& Pratto, F.
+(2010).
+Interacting like a body: Objectification can lead women to narrow their presence in social interactions.
+\emph{Psychological Science}, \emph{21}, 178--82.
 doi:\href{https://doi.org/10.1177/0956797609357751}{10.1177/0956797609357751}
 
-\hypertarget{ref-sanchez2008romance}{}
-Sanchez, D. T., \& Broccoli, T. L. (2008). The romance of
-self-objectification: Does priming romantic relationships induce states
-of self-objectification among women? \emph{Sex Roles}, \emph{59}(7-8),
-545--554.
-
-\hypertarget{ref-R-lattice}{}
-Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with
-r}. New York: Springer. Retrieved from
-\url{http://lmdvr.r-forge.r-project.org}
-
-\hypertarget{ref-siever1994sexual}{}
-Siever, M. D. (1994). Sexual orientation and gender as factors in
-socioculturally acquired vulnerability to body dissatisfaction and
-eating disorders. \emph{Journal of Consulting and Clinical Psychology},
-\emph{62}(2), 252.
-
-\hypertarget{ref-R-apaTables}{}
-Stanley, D. (2018). \emph{ApaTables: Create american psychological
-association (apa) style tables}. Retrieved from
-\url{https://CRAN.R-project.org/package=apaTables}
-
-\hypertarget{ref-strelan2005women}{}
-Strelan, P., \& Hargreaves, D. (2005). Women who objectify other women:
-The vicious circle of objectification? \emph{Sex Roles},
-\emph{52}(9-10), 707--712.
-
-\hypertarget{ref-strelan2018birds}{}
-Strelan, P., \& Pagoudis, S. (2018). Birds of a feather flock together:
-The interpersonal process of objectification within intimate
-heterosexual relationships. \emph{Sex Roles}, \emph{79}(1-2), 72--82.
-
-\hypertarget{ref-strong2000eating}{}
-Strong, S. M., Williamson, D. A., Netemeyer, R. G., \& Geer, J. H.
-(2000). Eating disorder symptoms and concerns about body differ as a
-function of gender and sexual orientation. \emph{Journal of Social and
-Clinical Psychology}, \emph{19}(2), 240--255.
-
-\hypertarget{ref-swimetal}{}
-Swim, J. K., Hyers, L. L., Cohen, L. L., \& Ferguson, M. J. (2001).
-Everyday sexism: Evidence for its incidence, nature, and psychological
-impact from three daily diary studies. \emph{Journal of Social Issues},
-\emph{57}(1), 31--53.
+\leavevmode\hypertarget{ref-sanchez2008romance}{}%
+Sanchez, D.
+T., \& Broccoli, T.
+L.
+(2008).
+The romance of self-objectification: Does priming romantic relationships induce states of self-objectification among women?
+\emph{Sex Roles}, \emph{59}(7-8), 545--554.
+
+\leavevmode\hypertarget{ref-R-lattice}{}%
+Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
+
+\leavevmode\hypertarget{ref-siever1994sexual}{}%
+Siever, M.
+D.
+(1994).
+Sexual orientation and gender as factors in socioculturally acquired vulnerability to body dissatisfaction and eating disorders.
+\emph{Journal of Consulting and Clinical Psychology}, \emph{62}(2), 252.
+
+\leavevmode\hypertarget{ref-R-apaTables}{}%
+Stanley, D. (2018). \emph{ApaTables: Create american psychological association (apa) style tables}. Retrieved from \url{https://CRAN.R-project.org/package=apaTables}
+
+\leavevmode\hypertarget{ref-strelan2005women}{}%
+Strelan, P., \& Hargreaves, D. (2005). Women who objectify other women: The vicious circle of objectification? \emph{Sex Roles}, \emph{52}(9-10), 707--712.
+
+\leavevmode\hypertarget{ref-strelan2018birds}{}%
+Strelan, P., \& Pagoudis, S.
+(2018).
+Birds of a feather flock together: The interpersonal process of objectification within intimate heterosexual relationships.
+\emph{Sex Roles}, \emph{79}(1-2), 72--82.
+
+\leavevmode\hypertarget{ref-strong2000eating}{}%
+Strong, S.
+M., Williamson, D.
+A., Netemeyer, R.
+G., \& Geer, J.
+H.
+(2000).
+Eating disorder symptoms and concerns about body differ as a function of gender and sexual orientation.
+\emph{Journal of Social and Clinical Psychology}, \emph{19}(2), 240--255.
+
+\leavevmode\hypertarget{ref-swimetal}{}%
+Swim, J.
+K., Hyers, L.
+L., Cohen, L.
+L., \& Ferguson, M.
+J.
+(2001).
+Everyday sexism: Evidence for its incidence, nature, and psychological impact from three daily diary studies.
+\emph{Journal of Social Issues}, \emph{57}(1), 31--53.
 doi:\href{https://doi.org/10.1111/0022-4537.00200}{10.1111/0022-4537.00200}
 
-\hypertarget{ref-tolman2006looking}{}
-Tolman, D. L., Impett, E. A., Tracy, A. J., \& Michael, A. (2006).
-Looking good, sounding good: Femininity ideology and adolescent girls'
-mental health. \emph{Psychology of Women Quarterly}, \emph{30}(1),
-85--95.
-
-\hypertarget{ref-R-ggplot2}{}
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
-Springer-Verlag New York. Retrieved from
-\url{https://ggplot2.tidyverse.org}
-
-\hypertarget{ref-R-tidyverse}{}
-Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
-'tidyverse'}. Retrieved from
-\url{https://CRAN.R-project.org/package=tidyverse}
-
-\hypertarget{ref-R-forcats}{}
-Wickham, H. (2018). \emph{Forcats: Tools for working with categorical
-variables (factors)}. Retrieved from
-\url{https://CRAN.R-project.org/package=forcats}
-
-\hypertarget{ref-R-stringr}{}
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for
-common string operations}. Retrieved from
-\url{https://CRAN.R-project.org/package=stringr}
-
-\hypertarget{ref-R-usethis}{}
-Wickham, H., \& Bryan, J. (2018). \emph{Usethis: Automate package and
-project setup}. Retrieved from
-\url{https://CRAN.R-project.org/package=usethis}
-
-\hypertarget{ref-R-tidyr}{}
-Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Easily tidy data with
-'spread()' and 'gather()' functions}. Retrieved from
-\url{https://CRAN.R-project.org/package=tidyr}
-
-\hypertarget{ref-R-haven}{}
-Wickham, H., \& Miller, E. (2019). \emph{Haven: Import and export
-'spss', 'stata' and 'sas' files}. Retrieved from
-\url{https://CRAN.R-project.org/package=haven}
-
-\hypertarget{ref-R-dplyr}{}
-Wickham, H., François, R., Henry, L., \& Müller, K. (2018). \emph{Dplyr:
-A grammar of data manipulation}. Retrieved from
-\url{https://CRAN.R-project.org/package=dplyr}
-
-\hypertarget{ref-R-devtools}{}
-Wickham, H., Hester, J., \& Chang, W. (2018). \emph{Devtools: Tools to
-make developing r packages easier}. Retrieved from
-\url{https://CRAN.R-project.org/package=devtools}
-
-\hypertarget{ref-R-readr}{}
-Wickham, H., Hester, J., \& Francois, R. (2017). \emph{Readr: Read
-rectangular text data}. Retrieved from
-\url{https://CRAN.R-project.org/package=readr}
-
-\hypertarget{ref-wollast2020cultural}{}
-Wollast, R., Riemer, A. R., Gervais, S. J., Grigoryan, L., Bernard, P.,
-\& Klein, O. (2020). How cultural orientation and self-compassion shape
-objectified body consciousness for women from america, belgium, russia,
-and thailand. \emph{Self and Identity}, 1--21.
-
-\hypertarget{ref-R-knitr}{}
-Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.).
-Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from
-\url{https://yihui.name/knitr/}
-
-\hypertarget{ref-yilmaz2019whose}{}
-Yilmaz, T., \& Bozo, Ö. (2019). Whose gaze is more objectifying? An
-experimental study of college women's state self-objectification, body
-shame, negative mood, and body dissatisfaction. \emph{Mediterranean
-Journal of Clinical Psychology}, \emph{7}(2).
-
-\hypertarget{ref-young1979}{}
-Young, I. M. (1979). \emph{Proceedings of the second sex---Thirty years
-later: A commemorative conference on feminist theory,}
-
-\hypertarget{ref-zurbriggen2011self}{}
-Zurbriggen, E. L., Ramsey, L. R., \& Jaworski, B. K. (2011). Self-and
-partner-objectification in romantic relationships: Associations with
-media consumption and relationship satisfaction. \emph{Sex Roles},
-\emph{64}(7-8), 449--462.
+\leavevmode\hypertarget{ref-tolman2006looking}{}%
+Tolman, D.
+L., Impett, E.
+A., Tracy, A.
+J., \& Michael, A.
+(2006).
+Looking good, sounding good: Femininity ideology and adolescent girls' mental health.
+\emph{Psychology of Women Quarterly}, \emph{30}(1), 85--95.
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2018). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-usethis}{}%
+Wickham, H., \& Bryan, J. (2018). \emph{Usethis: Automate package and project setup}. Retrieved from \url{https://CRAN.R-project.org/package=usethis}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2018a). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Easily tidy data with 'spread()' and 'gather()' functions}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-devtools}{}%
+Wickham, H., Hester, J., \& Chang, W. (2018b). \emph{Devtools: Tools to make developing r packages easier}. Retrieved from \url{https://CRAN.R-project.org/package=devtools}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2017). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-R-haven}{}%
+Wickham, H., \& Miller, E. (2019). \emph{Haven: Import and export 'spss', 'stata' and 'sas' files}. Retrieved from \url{https://CRAN.R-project.org/package=haven}
+
+\leavevmode\hypertarget{ref-wollast2020cultural}{}%
+Wollast, R., Riemer, A.
+R., Gervais, S.
+J., Grigoryan, L., Bernard, P., \& Klein, O.
+(2020).
+How cultural orientation and self-compassion shape objectified body consciousness for women from america, belgium, russia, and thailand.
+\emph{Self and Identity}, 1--21.
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
+
+\leavevmode\hypertarget{ref-yilmaz2019whose}{}%
+Yilmaz, T., \& Bozo, Ö.
+(2019).
+Whose gaze is more objectifying?
+An experimental study of college women's state self-objectification, body shame, negative mood, and body dissatisfaction.
+\emph{Mediterranean Journal of Clinical Psychology}, \emph{7}(2).
+
+\leavevmode\hypertarget{ref-young1979}{}%
+Young, I. M. (1979). \emph{Proceedings of the second sex---thirty years later: A commemorative conference on feminist theory,}
+
+\leavevmode\hypertarget{ref-zurbriggen2011self}{}%
+Zurbriggen, E.
+L., Ramsey, L.
+R., \& Jaworski, B.
+K.
+(2011).
+Self-and partner-objectification in romantic relationships: Associations with media consumption and relationship satisfaction.
+\emph{Sex Roles}, \emph{64}(7-8), 449--462.
 

### 2020-08-03 Final_Manuscript.Rmd

@@
 The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women only.
-Although past reserach has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if this interpersonal other-objectification by women is related to self-objectification in women.
+Although past reserach has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women is related to state self-objectification in their woman-identified interaction partners.
 As hypothesized, the current study did find a significant relationship bewteen a woman's partner's report of having objectified her and her own post-interaction feelings of self-objectification.
@@
 It could be that women's SSO causes them to be objectified by their interaction partner.
-This interpretation holds up given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO this relates to being objectified by one's partner.
-However, Objectification Theory [@robertsfredrickson] as past experimental studies [@saguyetal2010; CITE] suggest that the causal direction is indeed in the direction whereby other-objectification causes SSO.
+This interpretation in theoreticall interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO this relates to being objectified by one's partner.
+However, Objectification Theory [@robertsfredrickson], as well as past experimental studies [@saguyetal2010; CITE], suggest that the causal flow is from other-objectification to SSO.
 Although, importantly, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.
@@
 This lack of evidence could potentially signal diverging processs between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as detrimental as the self-objectificatoin experienced within an interaction with a man.
-We need to be careful not to interpret a null result as evidence of no relationship.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as harmful as the self-objectificatoin experienced within an interaction with a man.
+However, as a strong note of caution, we need to be careful not to interpret a null result as evidence of no relationship.
 
-The lack of evidence for a relationship between SSO and interaction authenticity is surprising and again, should not be interpreted as evidence of no realtionship---this lack of statistical significance could also be due to the relatively small sample size in the current study.
-The estimate of this relationship was very small, but in the negative direction, as anticipated.
-If it is the case that there is a smaller, or weaker, connection between women's feelings of SSO in interactions with other women then in interactions with men, models of interpersonal objectification, like the SIMO, could be extended by including inauthenticity as a potential mediated factor in decisions to continue objectifying interactions.
-Further, gender of the objectifyer/interaction partner could also be added to the model to help extend our understanding of under what circumstances other-objectificant and SSO have negative concequences for women.
+The lack of evidence for a relationship between SSO and interaction authenticity is surprising and again, should not be interpreted as evidence of no realtionship.
+It should be noted that the estimate of this relationship was very small, but in the negative direction, as anticipated.
+If it is the case that there is a smaller (i.e., weaker) connection between women's feelings of SSO and inauthenticity in interactions with other women then in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including inauthenticity as a potential mediating factor in decisions to continue objectifying interactions.
+Further, gender of the objectifyer/interaction partner could also be added to the SIMO model to help extend our understanding of under what circumstances other-objectification and SSO have negative concequences for women.
 
-Although we did not fid a connection bewteen SSO and authenticity we did find significant relationships in
+Although we did not find a connection bewteen SSO and authenticity we did find significant positive relationships between authenticity and relationship agency and career aspirations.
+The relationship between authenticity and cognitive functioning was also estimated as positive, but it was not statistically signfiicant.
+Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables.
+This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corrborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; PWQ paper I reviewed].
+Just as authenticity has been found to be important in intergroup interactions [CITE; CITE; CITE], we again find more evidence here that distuptions in feelings of authenticity can negatively impact relationships beyond the current partner.
+Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and more work needs to be done to discover when and how SSO leads to inauthenticity in interpersonal objectification situations.
 
@@
 ###Sample Characteristics
+The sample size was small and combined across two higher education institutions.
+
 The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008], although more current work examines objectification from a cross-cultural framework [@loughnan2015, @wollast2020cultural].
@@
 ###Sexual Objectification and the Objectifyer's Gender
+The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential data parter.
+While we think that hetereosexual women are indeed able to do this with other women as their target---indeed, there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they might be more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
+This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships, adding variability.
 

### 2020-08-05 Final_Manuscript.Rmd
more citations

@@
 @robertsfredrickson Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
-Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link (CITE INTERPERSONAL PROCESS LINKS LITERATURE).
+Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link [@garcia2016objectification, @strelan2018birds, @riemer2020self].
 For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men's reported objectification of their female interaction partner during an interaction was associated with increased self-objectification reported by their partner.
@@
 @harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women participants, although men scored high than women on a measure of belief that objectification of women is natural for men.
+Additionally, @strelan2005women found that the more women self-objectify, the more they objectify other women.
 ASK RANDI-WE KNOW OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN (Gervais, Vescio, & Allen, 2011; Moradi & Huang, 2008; Saguy, Quinn, Dovidio, & Pratto, 2010)...MENTION THAT...HOWEVER DOES WOMEN OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?...STILL TRYING TO FIGURE THAT OUT?
-ADDITIONALLY @strelan2005women FOUND THAT THE MORE WOMEN SELF-OBJECTIFY, THE MORE THEY OBJECTIFY OTHER WOMEN.
+ADDITIONALLY
 
@@
 There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor].
-This link has been justified by the literature on stigmatized-stigmatizer interactions (CITE LITERATURE DIDN'T COME ACROSS THIS), viewing the experience of being objectified in an interaction as an identity threat situation (MAYBE CITE MILES-MCLEAN PAPER "STOP LOOKING AT ME!").
+This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting] (CITE LITERATURE DIDN'T COME ACROSS THIS), viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop].
 When a woman is objectified by a man, and then experiences self-objectification, this intergroup encounter might trigger identitiy threat, but is the same negative consequence present when a woman is objectified by another woman?
-woman-woman interpersonal objectification processes might diverge from this process.
+Woman-woman interpersonal objectification processes might diverge from this process.
 One the one hand, she may not be having the same negative consequences the cascade from situations that threated group-based identity [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in an interaction may be enough to reduce feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
-I DONT KNOW WHERE THIS PAPER IS?
-ASK RANDI ABOUT IDENTITY_THREAT PAPERS
 
@@
 The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women only.
-Although past reserach has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women is related to state self-objectification in their woman-identified interaction partners.
-As hypothesized, the current study did find a significant relationship bewteen a woman's partner's report of having objectified her and her own post-interaction feelings of self-objectification.
+Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women is related to state self-objectification in their woman-identified interaction partners.
+As hypothesized, the current study did find a significant relationship between a woman's partner's report of having objectified her and her own post-interaction feelings of self-objectification.
 That is, there was a significant partner effect of other-objectification on SSO.
@@
 It could be that women's SSO causes them to be objectified by their interaction partner.
-This interpretation in theoreticall interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO this relates to being objectified by one's partner.
+This interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO this relates to being objectified by one's partner.
 However, Objectification Theory [@robertsfredrickson], as well as past experimental studies [@saguyetal2010; CITE], suggest that the causal flow is from other-objectification to SSO.
@@
 
-Although we did not find a connection bewteen SSO and authenticity we did find significant positive relationships between authenticity and relationship agency and career aspirations.
-The relationship between authenticity and cognitive functioning was also estimated as positive, but it was not statistically signfiicant.
+Although we did not find a connection between SSO and authenticity we did find significant positive relationships between authenticity and relationship agency and career aspirations.
+The relationship between authenticity and cognitive functioning was also estimated as positive, but it was not statistically signficant.
 Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables.
-This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corrborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; PWQ paper I reviewed].
-Just as authenticity has been found to be important in intergroup interactions [CITE; CITE; CITE], we again find more evidence here that distuptions in feelings of authenticity can negatively impact relationships beyond the current partner.
+This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; PWQ paper I reviewed].
+Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification; @tolman2006looking], we again find more evidence here that distuptions in feelings of authenticity can negatively impact relationships beyond the current partner.
 Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and more work needs to be done to discover when and how SSO leads to inauthenticity in interpersonal objectification situations.

### 2020-08-05 Final_Manuscript.Rmd
fixed up the intro

@@
 
-@robertsfredrickson Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women.
-Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link [@garcia2016objectification, @strelan2018birds, @riemer2020self].
+@robertsfredrickson Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
+The negative effects of this interpersonal objectification might be the strongest when it is a man doing the objectifying [@gervais2011you], but what are the consequences when a woman objectifies another woman in an interaction?
+Psychological researchers studying the sexual objectification of women, have in recent years explored the interpersonal process of the objectification, finding evidence for self-objectification in the target as a proximal consequence [@garcia2016objectification, @strelan2018birds, @riemer2020self].
 For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men's reported objectification of their female interaction partner during an interaction was associated with increased self-objectification reported by their partner.
-@gervais2020social has reviewed the literature on interpersonal self-objectification and has organized the the process in a theoretical model called the SIMO, but this model is only relevant for mixed-gender encounters.
-Although there is ample evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], there is currently no studies investigating the process of interpersonal objectification same-gender interactions.
+They did not include same-gender woman-woman interacting pairs.
+@gervais2020social has reviewed the literature on interpersonal self-objectification and has organized the the process in a theoretical model called the SIMO, but their model is currently only relevant for mixed-gender encounters.
+Although there is ample evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], there are currently no studies investigating the process of interpersonal objectification in same-gender interactions.
 Does objectification by a female interaction partner have the same downstream negative consequences as being objectified by a male interaction partner?
-For example, perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men outlined in @gervais2020social occur.
+The current study addressing this omission with a dyadic study of interacting pairs where both members identify as women.
 
 ##Self-Objectification
-Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level [@loughnan2015exploring] to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008].
-@calogero2011 proposes that the construct of self-objectification can be conceptualized as a learned trait.
-Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines [@morry2001magazine], which can lead to a state of self-objectification [@bernard2018bodies; @calogero2011; @moradi2008].
-Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [@fredrickson1998swimsuit, @garcia2016objectification].
-Does this habit self-objectification lead women to also objectify other women, possibly to compare oneself?
+Self-objectification is a psychological process that accounts offers a cognitive mechanism for translating the experiences of interpersonal objectification [@loughnan2015exploring] to negative mental health outcomes (e.g., anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008].
+@calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO).
+Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines [@morry2001magazine], or when wearing sexualizing clothing [@fredrickson1998swimsuit].
+This momentary self-objectification is referrd to as *state* self-objectification [@bernard2018bodies; @calogero2011; @moradi2008].
+Being objectified by another person may interact TSO to effect experiences of feeling like a body, or state self-objectification [SSO; @garcia2016objectification].
 
@@
 Past research has focused on men’s objectifying behaviors, with little attention to the role that women may also play in enacting objectification of women.
-@hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well (THEY DIDN'T DETERMINE THIS IN PERSON).
-Some studies have found that women objectify other women to a greater extent than they objectify men [@loughnan2015exploring].
-Women objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but we know next to nothing about interpersonal sexual objectification among women and what the immediate effects might be.
-Further, do women objectify non-sexualized women they are interacting with?
-What might be different for same-gender interactions?
-@harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women participants, although men scored high than women on a measure of belief that objectification of women is natural for men.
+@hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction.
+Some studies have actually found that women objectify other women to a greater extent than they objectify men [@loughnan2015exploring].
+Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but we know very little about interpersonal sexual objectification among women and what the immediate effects of this objectification might be.
+Objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this higher dose of objectification might be a detrimental combination.
+
+@harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women participants (although men scored higher than women on a measure of belief that objectification of women is natural for men).
 Additionally, @strelan2005women found that the more women self-objectify, the more they objectify other women.
-ASK RANDI-WE KNOW OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN (Gervais, Vescio, & Allen, 2011; Moradi & Huang, 2008; Saguy, Quinn, Dovidio, & Pratto, 2010)...MENTION THAT...HOWEVER DOES WOMEN OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?...STILL TRYING TO FIGURE THAT OUT?
-ADDITIONALLY
+Could the process work in the other direction as well, that is, could objectification by a women produce self-objectification, an a similar manner to mixed-gender interactions?
 
 ##Interpersonal Objectification
-SIMO model and literature review [@gervais2020social].
 Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979].
-Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredrickson1998swimsuit].
-We don't know about women-on-women interpersonal objectification.
-What might be different?
+Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated [self-objectification; @Bartky; @berger1972; @fredrickson1998swimsuit].
+@gervais2020social recently review the research on interpersonal objectification and organized our currentl theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
+What is clear from @gervais2020social is that we know little about women-on-women interpersonal objectification.
+Could there also be negative consequences of this type of interpersonal objectification?
+Perhaps women could be amplifying each others' state self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men oragnized in the SIMO occur.
+In this way, women's rituals of getting ready together might places even low TSO women in a higher SSO group.
 
-Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because in our culture women need to look attractive to obtain and maintain successful relationship, thus, the "college relationships condition may heighten self-objectification and the evaluation of other women in a sexualized way.
+Interpersonal objectification can also occur within the context of romantic relationships.
 Among heterosexual male and female college students, self- objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
@@
 A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor].
-Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
-Both romantic relationships and relationships in general have been studies in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
+Both romantic relationships and relationships in general have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
 
-There is evidence that the experience of state self-objectification in mixed-gender contexts (stranger and romantic) and within the self in any moment (trying on a swimsuit) has negative consequences, but what about in the context of interaction with other women?
-Is the self-objectification experience in mixed-gender interactions the same as that experienced in same-gender interactions?
-The ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose].
-Women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], but when they do it, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
+There is evidence that the experience of state self-objectification in mixed-gender contexts (stranger and romantic) has negative consequences for women, but what about in the context of interactions with other women?
+Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
+On the one hand, the ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but on the other hand, women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men].
+When they do it, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
 If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that interaction?
@@
 There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor].
-This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting] (CITE LITERATURE DIDN'T COME ACROSS THIS), viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop].
-When a woman is objectified by a man, and then experiences self-objectification, this intergroup encounter might trigger identitiy threat, but is the same negative consequence present when a woman is objectified by another woman?
-Woman-woman interpersonal objectification processes might diverge from this process.
-One the one hand, she may not be having the same negative consequences the cascade from situations that threated group-based identity [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in an interaction may be enough to reduce feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
+This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; CITE A SHELTON THING OR TWO], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop].
+Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
+When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identitiy threat.
+Thus, perhaps there are fewer negative consequence when a woman is objectified by another woman, that is, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
+A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
 
 ##The Current Study
-In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification,  but between same-sex female interpersonal interactions.
+In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification, but between same-gender interpersonal interactions among women.
 Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously.
-We expected to replicate the results found in @garcia2016objectification.
-We predicted that being objectified by one’s interaction partner would lead to self-objectification, which in turn would lead to feelings of inauthenticity, then reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
-Specifically, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
+Although the literature on woman-woman objectification is small, mixed, and does not cover interpersonal encourters, we expected to replicate some of the results found in @garcia2016objectification.
+Most importantly, we predicted that being objectified by one’s interaction partner would lead to self-objectification.
+We also expected, in line with @garcia2016objectification, that TSO would moderate this relationship, amplyfying the positive assocaition between being objectified and SSO for women higher in TSO.
+We hypothesized that SSO would, in turn, lead to feelings of inauthenticity [although there is ample support against this prediction from the identity threat within intergroup interactions literature; CITE CITE].
+Further, we hypothsized that these feelings of inauthencity would then be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
+In summary, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
 We also expect to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
 
-@puvia2013being would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (...well, dehumanize a sexualized woman, but also @strelan2005women would predict the TSO->SOO link and @harsey2020men too), and this is mediated by the woman's own state self-objectification (SSO).
-So we also tested this as a possible alternative model.
+Here we would like to note that @puvia2013being would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (more precisely, to dehumanize a sexualized woman).
+In addition, @strelan2005women and @harsey2020men would predict the TSO to other-objectification link, further theorezing that this relationships is mediated by the woman's own state self-objectification (SSO).
+This limited, but extant, set of literature on woman-woman objectification points to a possible alternative model from the model hypothesized in the current study.
+Where appropriate, we report results considering the causal directions implied by this alternative mediation model.
 
@@
 
+Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because in our culture women need to look attractive to obtain and maintain successful relationship, thus, the "college relationships condition may heighten self-objectification and the evaluation of other women in a sexualized way.
 The decision was made to ask even heterosexual women to judge their women partners as potential romantic partners.
@@
 We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity.
+Perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men outlined in @gervais2020social occur.
 

### 2020-08-05 Final_Manuscript.Rmd
updated method section

@@
 During the interaction, please think about your partner's potential as a romantic partner.
-Even if they are not the gender you are attracted to, you can still judge their potential as a romantic partner.
+**Even if they are not the gender you are attracted to**, you can still judge their potential as a romantic partner.
 After the interaction you will be asked to evaluate how dateable your partner is.
@@
 
-Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because in our culture women need to look attractive to obtain and maintain successful relationship, thus, the "college relationships condition may heighten self-objectification and the evaluation of other women in a sexualized way.
-The decision was made to ask even heterosexual women to judge their women partners as potential romantic partners.
-We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study.
-Past research has found that women, largely due to an increase self-objectifying state, are indeed able to evaluate other women's potential as romantic partners--indeed, women may be unfortunately used to thinking this way about themselves, and we suspect other women.
+*All* participants were told that they were assigned to the "College Relationships" condition.
+Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because, in Westurn culture and beyond, women need to look attractive to obtain and maintain successful relationship, thus, the "College Relationships" condition may heighten self-objectification and the evaluation of other women in a sexualized way.
+The decision was made to ask even heterosexual women to judge their fellow-woman partners for their potential as romantic partners.
+We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and amplify the potential for objectification that would normally be low in the context of a psychology laboratory.
+Recall that, past research has found that women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; CITE]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitial thought pattern will translate to their thoughts about other women.
 
-Two participants were then brought into a larger interaction room where they sat on stools prearranged to be 36 inches apart.
+After recieving the "College Relationships" prompt, the two participants were then brought into a larger interaction room where they sat on stools prearranged to be approximately 1 meter apart.
 The experimenter instructed the participants to “get to know each other” for 10 minutes and then left the room.
@@
 The participants then went back to their individual cubicles and completed a set of post-interaction measures.
-Participants were then thanked for their participation and debriefed @garcia2016objectification.
-The full methodology used is found in @garcia2016objectification’s study.
+Participants were then thanked for their participation and debriefed.
+More detail on this methodology can be found in @garcia2016objectification.
 

### 2020-08-24 Final_Manuscript.Rmd
incorportaing lanees edits

@@
 abstract: |
-  Empirical evidence has only found links between objectification, self-objectification, and negative outcomes for woman within interpersonal interactions between male-female pairs.
+  Empirical evidence has only found links between objectification, self-objectification, and negative outcomes for women within interpersonal interactions between male-female pairs.
 The purpose of the present study was to extend past research and consider the relationships between such valuable phenomena and their effects on authenticity within interactions between female pairs.
-Woman were brought into the laboratory and interacted in same-sex dyads.
+Women were brought into the laboratory and interacted in same-sex dyads.
 Dyadic analysis was utilized to detect whether partners’ objectification of each other affected state self-objectification, and the resulting feelings of comfort and authenticity during the interaction.
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 ---
@@
 Psychological researchers studying the sexual objectification of women, have in recent years explored the interpersonal process of the objectification, finding evidence for self-objectification in the target as a proximal consequence [@garcia2016objectification, @strelan2018birds, @riemer2020self].
-For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men's reported objectification of their female interaction partner during an interaction was associated with increased self-objectification reported by their partner.
-They did not include same-gender woman-woman interacting pairs.
-@gervais2020social has reviewed the literature on interpersonal self-objectification and has organized the the process in a theoretical model called the SIMO, but their model is currently only relevant for mixed-gender encounters.
+For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification reported by their partner.
+They did not include same-gender, woman-woman interacting pairs.
+@gervais2020social have reviewed the literature on interpersonal self-objectification and has organized the process in a theoretical model called the Social Interaction Model of Objectification (SIMO), but this model is currently only relevant for mixed-gender encounters.
 Although there is ample evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], there are currently no studies investigating the process of interpersonal objectification in same-gender interactions.
 Does objectification by a female interaction partner have the same downstream negative consequences as being objectified by a male interaction partner?
-The current study addressing this omission with a dyadic study of interacting pairs where both members identify as women.
+The current dyadic study addresses this omission using interacting pairs where both members identify as women.
 
 ##Self-Objectification
-Self-objectification is a psychological process that accounts offers a cognitive mechanism for translating the experiences of interpersonal objectification [@loughnan2015exploring] to negative mental health outcomes (e.g., anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008].
+Self-objectification is a psychological process that accounts offer a cognitive mechanism for translating the experiences of interpersonal objectification [@loughnan2015exploring] to negative mental health outcomes (e.g., anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008].
 @calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO).
 Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines [@morry2001magazine], or when wearing sexualizing clothing [@fredrickson1998swimsuit].
-This momentary self-objectification is referrd to as *state* self-objectification [@bernard2018bodies; @calogero2011; @moradi2008].
+This momentary self-objectification is referred to as *state* self-objectification [@bernard2018bodies; @calogero2011; @moradi2008].
 Being objectified by another person may interact TSO to effect experiences of feeling like a body, or state self-objectification [SSO; @garcia2016objectification].
@@
 ##Women Objectifying Women
-Past research has focused on men’s objectifying behaviors, with little attention to the role that women may also play in enacting objectification of women.
-@hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction.
-Some studies have actually found that women objectify other women to a greater extent than they objectify men [@loughnan2015exploring].
-Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but we know very little about interpersonal sexual objectification among women and what the immediate effects of this objectification might be.
-Objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this higher dose of objectification might be a detrimental combination.
-
 @harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women participants (although men scored higher than women on a measure of belief that objectification of women is natural for men).
@@
 
+Past research has focused on men’s objectifying behaviors, with little attention to the role that women may also play in objectifying other women.
+@hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction.
+@loughnan2015exploring found that women objectify other women to a greater extent than they objectify men.
+Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but we know very little about interpersonal sexual objectification among women and what the immediate effects of this objectification might be.
+We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this higher dose of objectification might be a detrimental combination.
+
 ##Interpersonal Objectification
-Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979].
-Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated [self-objectification; @Bartky; @berger1972; @fredrickson1998swimsuit].
-@gervais2020social recently review the research on interpersonal objectification and organized our currentl theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
+Studies have shown that within social encounters women are gazed at more than men [@briton1995], and often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979].
+Moreover, perhaps the most adverse effect is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
+@gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
 What is clear from @gervais2020social is that we know little about women-on-women interpersonal objectification.
 Could there also be negative consequences of this type of interpersonal objectification?
-Perhaps women could be amplifying each others' state self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men oragnized in the SIMO occur.
-In this way, women's rituals of getting ready together might places even low TSO women in a higher SSO group.
+Perhaps women could be amplifying each others' state self-objectification as they get ready to go out for the night [EDIT??], *before* the theoretical encounters with men oraganized in the SIMO occur.
+In this way, women's rituals of getting ready together might place even women with low TSO in a higher SSO group.
 
 Interpersonal objectification can also occur within the context of romantic relationships.
-Among heterosexual male and female college students, self- objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
+Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
 Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds].
-Evidence is mixed, and women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship and they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], less is known about first dates.
+Evidence is mixed, and women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship in that they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], less is known about first dates.
 But this literature is also only about heterosexual relationships.
@@
 Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
-On the one hand, the ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but on the other hand, women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men].
+On the one hand, there is ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but on the other hand, women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men].
 When they do it, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
@@
 There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor].
-This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; CITE A SHELTON THING OR TWO], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop].
+This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop; @nadal2012effects].
 Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
@@
 We also expected, in line with @garcia2016objectification, that TSO would moderate this relationship, amplyfying the positive assocaition between being objectified and SSO for women higher in TSO.
-We hypothesized that SSO would, in turn, lead to feelings of inauthenticity [although there is ample support against this prediction from the identity threat within intergroup interactions literature; CITE CITE].
+We hypothesized that SSO would, in turn, lead to feelings of inauthenticity [although there is ample support against this prediction from the identity threat within intergroup interactions literature; @rollero2016bringing].
 Further, we hypothsized that these feelings of inauthencity would then be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.

### 2020-09-02 Final_Manuscript.Rmd
added lanee's comments

@@
 library(xtable)
+library(rmarkdown)
 ```
@@
 We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and amplify the potential for objectification that would normally be low in the context of a psychology laboratory.
-Recall that, past research has found that women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; CITE]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitial thought pattern will translate to their thoughts about other women.
+Recall that, past research has found that women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; CITE]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.
 
@@
 
-Due these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
+Due to these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
 These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
@@
 ```
-To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner @garcia2016objectification.
+To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner [@garcia2016objectification].
 Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
-All questions were to be rated on a scale from 1 (not at all) to 7 (constantly).
+All questions were rated on a scale from 1 (not at all) to 7 (constantly).
 Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2).
@@
 To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike [@garcia2016objectification].
-Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: ‘‘Do you think your partner was authentic during your interaction?’’ and ‘‘Were you authentic during your interaction?’’ These questions were ranked on a scale from 1 (not authentic at all).
+Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: ‘‘Do you think your partner was authentic during your interaction?’’ and ‘‘Were you authentic during your interaction?’’ These questions were ranked on a scale from 1 (not at all) to 7 (very much).
 These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
@@
 ```{r create_r-references, warning=FALSE, message=FALSE}
-#cite_r(file = "references.bib")
 r_refs(file = "r-references.bib")
+
+#cite_r("r-references.bib") #There are other packages loaded as well, not sure which ones we use and which ones we dont. Consider putting all loaded packages in supplement.  
 ```
-We used `r cite_r("r-references.bib")` for all our analyses.
+We used R [Version 3.5.2; @R-base] and the R-packages *tidyverse* [Version 1.2.1; @R-tidyverse], *psych* [Version 1.8.4; @R-psych], *nlme* [Version 3.1.137; @R-nlme] for our analyses.
+Further, we used the R-packages *papaja* [Version 0.1.0.9842; @R-papaja], *apaTables* [Version 2.0.5; @R-apaTables], with *knitr* [Version 1.25; @R-knitr] to create a fully reproducible manuscript in *rmarkdown* [Version 1.15; @R-rmarkdown].
 
@@
 While @garcia2016objectification used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling.
-Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dayds (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation].
+Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation].
 One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural].
@@
 The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
-As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically significant, `r report_stats(apim1, 3)`, replicating @garcia2016objectification's finding.
+As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically significant, `r report_stats(apim1, 3)`.
 One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
@@
 ```
-Contrary to expectations, there was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
+There was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
 Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also estimated the pairwise correlations between SSO and all these items individually.
@@
 It could be that women's SSO causes them to be objectified by their interaction partner.
-This interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO this relates to being objectified by one's partner.
+This interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO that relates to being objectified by one's partner.
 However, Objectification Theory [@robertsfredrickson], as well as past experimental studies [@saguyetal2010; CITE], suggest that the causal flow is from other-objectification to SSO.
-Although, importantly, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.
+Although, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.
 
-Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and felt inauthenticity.
+Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity.
 In addition, we found no evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations.
 Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes.
-This is somewhat suprising given the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification].
+This is somewhat suprising given the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification].
 This lack of evidence could potentially signal diverging processs between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
@@
 It should be noted that the estimate of this relationship was very small, but in the negative direction, as anticipated.
-If it is the case that there is a smaller (i.e., weaker) connection between women's feelings of SSO and inauthenticity in interactions with other women then in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including inauthenticity as a potential mediating factor in decisions to continue objectifying interactions.
-Further, gender of the objectifyer/interaction partner could also be added to the SIMO model to help extend our understanding of under what circumstances other-objectification and SSO have negative concequences for women.
+If it is the case that there is a smaller (i.e., weaker) connection between women's feelings of SSO and inauthenticity in interactions with other women than in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including inauthenticity as a potential mediating factor.
+Further, gender of the objectifyer/interaction partner could also be added to the SIMO model to help understand the circumstances that require other-objectification and SSO to have negative consequences for women.
 
-Although we did not find a connection between SSO and authenticity we did find significant positive relationships between authenticity and relationship agency and career aspirations.
+Although we did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency and career aspirations.
 The relationship between authenticity and cognitive functioning was also estimated as positive, but it was not statistically signficant.
@@
 This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; PWQ paper I reviewed].
-Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification; @tolman2006looking], we again find more evidence here that distuptions in feelings of authenticity can negatively impact relationships beyond the current partner.
+Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification; @tolman2006looking], we again find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current partner.
 Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and more work needs to be done to discover when and how SSO leads to inauthenticity in interpersonal objectification situations.
@@
 ###Sexual Objectification and the Objectifyer's Gender
-The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential data parter.
-While we think that hetereosexual women are indeed able to do this with other women as their target---indeed, there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they might be more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
+The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating partner.
+We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they might be more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
 This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships, adding variability.
@@
 Thus, it is unclear whether lesbians indeed experience similar levels of cultural sexual objectification but internalize them less than heterosexual women do.
-Consistent with previous reseach @hill2008examining determined lesbians existed less physical appearance concerns compared to heterosexual women, however there was no difference found that lesbian women self-objectify less than heterosexual women and they did not find that sexual orientation moderates the relationshiotn between sexual objecitifcantion and self-objectification This contradicts older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women [@brown1987lesbians; @pitman1999body; @lum1994lesbians; @siever1994sexual]
+Consistent with previous research, @hill2008examining determined that lesbians existed less physical appearance concerns compared to heterosexual women, however there was no difference found that lesbian women self-objectify less than heterosexual women and they did not find that sexual orientation moderates the relationship between sexual objectification and self-objectification.
+This contradicts older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women [@brown1987lesbians; @pitman1999body; @lum1994lesbians; @siever1994sexual]
 
@@
 ###Alternative Model
-@puvia2013being alternative model. TSO -> SOO, mediated by SSO.
+@puvia2013being alternative model.
+TSO -> SOO, mediated by SSO.
+“Found that women’s motivation to look attractive (for men) and internalize sociocultural beauty standards were positively linked with the dehumanization of sexually objectified female targets.” Tis relationship was mediated by their own level of self-objectification.”
 
@@
 #Conclusion
-The results of this study demonstrate the complex and ambivalent nature of female sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
+The results of this study demonstrate the complex and ambivalent nature of sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
 We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity.

### 2020-09-07 Final_Manuscript.Rmd
added Kat's edits

@@
 Additionally, @strelan2005women found that the more women self-objectify, the more they objectify other women.
-Could the process work in the other direction as well, that is, could objectification by a women produce self-objectification, an a similar manner to mixed-gender interactions?
+Could the process work in the other direction as well, that is, could objectification by a woman produce self-objectification, in a similar manner to mixed-gender interactions?
 
@@
 ##Interpersonal Objectification
-Studies have shown that within social encounters women are gazed at more than men [@briton1995], and often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979].
+Studies have shown that within social encounters women are gazed at more than men [@briton1995], and often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
 Moreover, perhaps the most adverse effect is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
@@
 Could there also be negative consequences of this type of interpersonal objectification?
-Perhaps women could be amplifying each others' state self-objectification as they get ready to go out for the night [EDIT??], *before* the theoretical encounters with men oraganized in the SIMO occur.
+Perhaps women could be amplifying each others' state self-objectification as they get ready to go out for the night [EDIT??], *before* the theoretical encounters with men organized in the SIMO occur.
 In this way, women's rituals of getting ready together might place even women with low TSO in a higher SSO group.
+[Kat: This has me thinking about the difference between objectification in a romantic setting (which was the setting created in the initial experiment) vs objectification in a platonic setting/between friends.
+Might be useful to discuss this difference, or just have a sentence here that clarifies objectification can occur within non-sexual settings]
 
-Interpersonal objectification can also occur within the context of romantic relationships.
+Interpersonal objectification can also occur within the context of romantic relationships, in addition to interactions with strangers.
 Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
 Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds].
-Evidence is mixed, and women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship in that they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], less is known about first dates.
-But this literature is also only about heterosexual relationships.
+Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship.
+There is also evidence that they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], but less is known about first dates.
+An important caveat to this literature is that it is only about heterosexual relationships.
 A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor].
@@
 Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
-When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identitiy threat.
-Thus, perhaps there are fewer negative consequence when a woman is objectified by another woman, that is, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
+When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identity threat.
+Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, that is, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
 A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
@@
 Most importantly, we predicted that being objectified by one’s interaction partner would lead to self-objectification.
-We also expected, in line with @garcia2016objectification, that TSO would moderate this relationship, amplyfying the positive assocaition between being objectified and SSO for women higher in TSO.
+We also expected, in line with @garcia2016objectification, that TSO would moderate this relationship, amplifying the positive assocaition between being objectified and SSO for women higher in TSO.
 We hypothesized that SSO would, in turn, lead to feelings of inauthenticity [although there is ample support against this prediction from the identity threat within intergroup interactions literature; @rollero2016bringing].
-Further, we hypothsized that these feelings of inauthencity would then be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
+Further, we hypothesized that these feelings of inauthencity would then be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
 In summary, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
-We also expect to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
+We also expected to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
 
@@
 One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
-Contrary to past finding however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
+Inconsistent with past findings however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
 There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.
@@
 We again used MLM and thus, these effects were tested in three separate models.
-There was no significant effect of interaction authenticity on cognitive performance, `r report_stats(apim3, 2)`, but authenticity was significantly positively related to both career aspirations, `r report_stats(apim5, 2)`, and relationships agency, `r report_stats(apim4, 2)`.
+There was no significant effect of interaction authenticity on cognitive performance, `r report_stats(apim3, 2)`, but authenticity was significantly positively related to both career aspirations, `r report_stats(apim5, 2)`, and relationship agency, `r report_stats(apim4, 2)`.
 There was no direct effect of SSO on cognitive performance, `r report_stats(apim3.b, 3)`, and no direct effect of partner's other objectification on cognitive performance, `r report_stats(apim3.c, 4)`.
@@
 Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women is related to state self-objectification in their woman-identified interaction partners.
-As hypothesized, the current study did find a significant relationship between a woman's partner's report of having objectified her and her own post-interaction feelings of self-objectification.
+As hypothesized, the current study did find a significant relationship between a woman's interaction partner's report of having objectified her and her own post-interaction feelings of self-objectification.
 That is, there was a significant partner effect of other-objectification on SSO.
 This effect extends the equivalent relationship found in mixed-gender interactions to the context of same-gender interactions between women.
-Thus, it could be that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also results in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
+Thus, it could be that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also result in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
 
@@
 This is somewhat suprising given the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification].
-This lack of evidence could potentially signal diverging processs between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as harmful as the self-objectificatoin experienced within an interaction with a man.
+This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as harmful as the self-objectification experienced within an interaction with a man.
 However, as a strong note of caution, we need to be careful not to interpret a null result as evidence of no relationship.
 
-The lack of evidence for a relationship between SSO and interaction authenticity is surprising and again, should not be interpreted as evidence of no realtionship.
+The lack of evidence for a relationship between SSO and interaction authenticity is surprising and again, should not be interpreted as evidence of no relationship.
 It should be noted that the estimate of this relationship was very small, but in the negative direction, as anticipated.
@@
 Although we did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency and career aspirations.
-The relationship between authenticity and cognitive functioning was also estimated as positive, but it was not statistically signficant.
+The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically signficant.
 Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables.
@@
 ###Sample Characteristics
-The sample size was small and combined across two higher education institutions.
-
-The sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008], although more current work examines objectification from a cross-cultural framework [@loughnan2015, @wollast2020cultural].
-Because “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015].
+In addition to being small and combined across two institutions, the sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008], although more current work examines objectification from a cross-cultural framework [@loughnan2015, @wollast2020cultural].
+Since “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015].
 Further, sexualizing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014; @bury2016].
@@
 It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.
+[Kat: Or a longitudinal study is needed.]
 
@@
 The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating partner.
-We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they might be more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
+We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
 This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships, adding variability.
+[Kat: The only other thing I would add re: sexuality limitations are that we didn’t collect/use sexual orientation, so we couldn’t analyze results by that at all/our samples might have differed there.]
 
@@
 Thus, it is unclear whether lesbians indeed experience similar levels of cultural sexual objectification but internalize them less than heterosexual women do.
-Consistent with previous research, @hill2008examining determined that lesbians existed less physical appearance concerns compared to heterosexual women, however there was no difference found that lesbian women self-objectify less than heterosexual women and they did not find that sexual orientation moderates the relationship between sexual objectification and self-objectification.
-This contradicts older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women [@brown1987lesbians; @pitman1999body; @lum1994lesbians; @siever1994sexual]
+Consistent with previous research, @hill2008examining determined that lesbians existed less physical appearance concerns compared to heterosexual women, however there was no evidence found that lesbian women self-objectify less than heterosexual women and they did not find that sexual orientation moderates the relationship between sexual objectification and self-objectification.
+This contradicts older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women [@brown1987lesbians; @pitman1999body; @lum1994lesbians; @siever1994sexual].
 
@@
 ###Sexism and Sexual Discrimination
-Sexism has recently been found to be related to the objectification of women, but not men, for both men and women [@harsey2020men].
-Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and experience daily sexist hassles [@swimetal].
+Sexism has recently been found to be related to the objectification of women, but not men, for both men and women [@harsey2020men].[Kat: Is the relationship between sexism and objectification really this recent of a finding?
+Or was it just replicated recently?] Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and experience daily sexist hassles [@swimetal].
 One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
@@
 ###Measurement
-Also, future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operationalization of self-objectification may be improved.
+Future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operationalization of self-objectification may be improved.
 
@@
 ##Clinical Implications
-Regardless, the results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts.
+The results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts.
 These results are quite useful for promoting mental health and within early action programs for girls and young women, where scholars and practitioners might provide the tools necessary to circumvent or mitigate negative effects on self-objectification, and combat such experiences.

### 2020-09-07 Final_Manuscript.Rmd
added Asha's edits

@@
 ##Self-Objectification
-Self-objectification is a psychological process that accounts offer a cognitive mechanism for translating the experiences of interpersonal objectification [@loughnan2015exploring] to negative mental health outcomes (e.g., anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008].
+Self-objectification is a psychological process that provides a cognitive mechanism to translate the experiences of interpersonal objectification [@loughnan2015exploring] to negative mental health outcomes (e.g., anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008].
 @calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO).
@@
 
-Past research has focused on men’s objectifying behaviors, with little attention to the role that women may also play in objectifying other women.
+[Asha comment on next paragraph: Hill and Fischer (2008) assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women, and found that women may be socialized not only to see themselves as objects, but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction
+
+Could this sentence be written like:
+
+Though, when Hill and Fischer(2008) assessed women’s experiences of objectification from men independently from that of women, they found that women are likely to be socialized to not only to see themselves s objects, but potentially see other women as objects as well.
+This process ,however, was not confirmed to occur during an interpersonal interaction.]
+
+Past research has focused on men’s objectifying behaviors, with little attention paid to the role that women may also play in objectifying other women.
 @hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction.
 @loughnan2015exploring found that women objectify other women to a greater extent than they objectify men.
-Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but we know very little about interpersonal sexual objectification among women and what the immediate effects of this objectification might be.
-We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this higher dose of objectification might be a detrimental combination.
+Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the proximal effects of this objectification might be.
+We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this higher level of objectification might be a detrimental combination.
 
@@
 Studies have shown that within social encounters women are gazed at more than men [@briton1995], and often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
-Moreover, perhaps the most adverse effect is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
+Moreover, perhaps the most adverse effect is that it socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
 @gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
@@
 [Kat: This has me thinking about the difference between objectification in a romantic setting (which was the setting created in the initial experiment) vs objectification in a platonic setting/between friends.
-Might be useful to discuss this difference, or just have a sentence here that clarifies objectification can occur within non-sexual settings]
+Might be useful to discuss this difference, or just have a sentence here that clarifies objectification can occur within non-sexual settings] [Asha: I think this is a great way to illustrate the potential experience but when I read it I was kind of like “wait, when did we talk about women going out?”]
 
@@
 A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor].
-Both romantic relationships and relationships in general have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
+Both romantic relationships and stranger encounters have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
 
@@
 When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identity threat.
-Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, that is, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
+Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, specifically, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
 A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
@@
 Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously.
-Although the literature on woman-woman objectification is small, mixed, and does not cover interpersonal encourters, we expected to replicate some of the results found in @garcia2016objectification.
+Although the literature on woman-woman objectification is small, the results are mixed, and does not cover interpersonal encourters, we expected to replicate some of the results found in @garcia2016objectification.
 Most importantly, we predicted that being objectified by one’s interaction partner would lead to self-objectification.
@@
 ##Procedure
-The procedure used was identical to that in @garcia2016objectification, except for the instructions that the participants were given.
+Except for the instructions given to participants, the procedure used was identical to that in @garcia2016objectification.
 In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to prevent any communication between the participants before the interaction.
@@
 The decision was made to ask even heterosexual women to judge their fellow-woman partners for their potential as romantic partners.
-We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and amplify the potential for objectification that would normally be low in the context of a psychology laboratory.
+We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and strengthen the potential for objectification that would normally be low in the context of a psychology laboratory.
 Recall that, past research has found that women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; CITE]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.
@@
 See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study.
-We hope to investigate how the central effects found in the previous study relate to interactions between two women.
+We investigated how the central effects found in the previous study relate to interactions between two women.
 Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction.
@@
 Further, we will investigate the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.
+[Asha: This section feels like a mixture of explaining what the study was intended to investigate as wel as future directions.
+Is that the point, or can this be organized better?]
 
-While @garcia2016objectification used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling.
+While @garcia2016objectification used dyadic path analysis, the current study used multilevel modeling for our dyadic analyses.
 Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation].
@@
 
-Before moving to the main analyses, we discuss statistical equivalence test that provide support for combining Sample 1 and Sample 2 in one analysis sample.
+Before moving to the main analyses, we discuss statistical equivalence tests that provide support for combining Sample 1 and Sample 2 in one analysis sample.
 The online supplemental material contains the main analyses separated by samples.
@@
 This effect extends the equivalent relationship found in mixed-gender interactions to the context of same-gender interactions between women.
-Thus, it could be that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also result in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
+Thus, evidence suggests that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also result in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
+[Asha:Or … thus evidence provides support for the claim that women being objectified by another woman result in sso in ways that are not uniquely dissimilar from that of xyz]
 
-As is the case in all correlational studies, we cannot be sure in the causal direction.
+As is the case in all correlational studies, we cannot be sure about the causal direction.
 It could be that women's SSO causes them to be objectified by their interaction partner.
@@
 Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes.
-This is somewhat suprising given the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification].
+This is somewhat suprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification].
 This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
 There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as harmful as the self-objectification experienced within an interaction with a man.
-However, as a strong note of caution, we need to be careful not to interpret a null result as evidence of no relationship.
+As a strong note of caution, it is best not to interpret a null result as evidence of no relationship.
 
@@
 
-Although we did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency and career aspirations.
+Although we did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency, and authenticity and career aspirations.
 The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically signficant.
@@
 Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification; @tolman2006looking], we again find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current partner.
-Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and more work needs to be done to discover when and how SSO leads to inauthenticity in interpersonal objectification situations.
+Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and future work must explore when and how SSO leads to inauthenticity in interpersonal objectification situations.
 
@@
 ###Sexual Objectification and the Objectifyer's Gender
-The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating partner.
+The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating/romantic partner.
 We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
@@
 ##Clinical Implications
-The results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts.
-These results are quite useful for promoting mental health and within early action programs for girls and young women, where scholars and practitioners might provide the tools necessary to circumvent or mitigate negative effects on self-objectification, and combat such experiences.
+The results from the current analysis highlight how subtle forms of sexist discrimination operate, and provide valuable insight into prevention and intervention efforts in both clinical and educational contexts.
+These results are quite useful for promoting mental health, the creation and maintence of early action programs for girls and young women, and for scholars and practitioners to work intentially to provide the tools necessary to circumvent or mitigate negative effects on self-objectification to combat such experiences.
 
@@
 We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity.
-Perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men outlined in @gervais2020social occur.
+[Move to here: Perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men outlined in @gervais2020social occur.]
 

### 2020-09-07 Final_Manuscript.tex
re-knitted word and pdf

--- 2020-08-03 Final_Manuscript.tex
@@
 Empirical evidence has only found links between objectification,
-self-objectification, and negative outcomes for woman within
+self-objectification, and negative outcomes for women within
 interpersonal interactions between male-female pairs. The purpose of the
@@
 between such valuable phenomena and their effects on authenticity within
-interactions between female pairs. Woman were brought into the
+interactions between female pairs. Women were brought into the
 laboratory and interacted in same-sex dyads. Dyadic analysis was
@@
 
-Roberts and Fredrickson (1997) Objectification Theory, suggests that
-women are objectified in interpersonal encounters, and that the effect
-might be strongest from men, but possibly also from women. Psychological
-researchers studying the sexual objectification of women, and the
-resulting self-objectification that follows, have in recent years
-explored the interpersonal process of the objectification -
-self-objectification link (CITE INTERPERSONAL PROCESS LINKS LITERATURE).
-For example, in a face-to-face mixed-gender dyadic study, Garcia,
-Earnshaw, and Quinn (2016) found that men's reported objectification of
-their female interaction partner during an interaction was associated
-with increased self-objectification reported by their partner. Gervais,
-Sáez, Riemer, and Klein (2020) has reviewed the literature on
-interpersonal self-objectification and has organized the the process in
-a theoretical model called the SIMO, but this model is only relevant for
-mixed-gender encounters. Although there is ample evidence that women
-objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013),
-there is currently no studies investigating the process of interpersonal
-objectification same-gender interactions. Does objectification by a
-female interaction partner have the same downstream negative
-consequences as being objectified by a male interaction partner? For
-example, perhaps women could be amplifying each others'
-self-objectification as they get ready to go out for the night,
-\emph{before} the theoretical encounters with men outlined in Gervais et
-al. (2020) occur.
+Roberts and Fredrickson (1997) Objectification Theory, suggests that, in
+addition to being steeped in a culture that objectifies women, women are
+objectified in actual interpersonal encounters. The negative effects of
+this interpersonal objectification might be the strongest when it is a
+man doing the objectifying (Gervais, Vescio, \& Allen, 2011), but what
+are the consequences when a woman objectifies another woman in an
+interaction? Psychological researchers studying the sexual
+objectification of women, have in recent years explored the
+interpersonal process of the objectification, finding evidence for
+self-objectification in the target as a proximal consequence (Garcia,
+Earnshaw, \& Quinn, 2016, Strelan and Pagoudis (2018), Riemer, Sáez,
+Brock, and Gervais (2020)). For example, in a face-to-face mixed-gender
+dyadic study, Garcia et al. (2016) found that men's reported
+objectification of their female interaction partner was associated with
+increased self-objectification reported by their partner. They did not
+include same-gender, woman-woman interacting pairs. Gervais, Sáez,
+Riemer, and Klein (2020) have reviewed the literature on interpersonal
+self-objectification and has organized the process in a theoretical
+model called the Social Interaction Model of Objectification (SIMO), but
+this model is currently only relevant for mixed-gender encounters.
+Although there is ample evidence that women objectify other women
+(Loughnan et al., 2015a; Puvia \& Vaes, 2013), there are currently no
+studies investigating the process of interpersonal objectification in
+same-gender interactions. Does objectification by a female interaction
+partner have the same downstream negative consequences as being
+objectified by a male interaction partner? The current dyadic study
+addresses this omission using interacting pairs where both members
+identify as women.
 
@@
 
-Self-objectification is a multidimensional process that accounts for the
-cognitive mechanism that translates experiences of sexualization at the
-cultural level (Loughnan et al., 2015a) to psychological (e.g., anxiety,
-self-esteem, authenticity, motivational states) and behavioral
-(cognitive performance, body monitoring) features of mental health and
-well-being at the individual level (Calogero, Tantleff-Dunn, \&
-Thompson, 2011; Moradi \& Huang, 2008). Calogero et al. (2011) proposes
-that the construct of self-objectification can be conceptualized as a
-learned trait. Furthermore, it can also be elicited momentarily, through
-the media, for example, with sexualized images in movies and magazines
-(Morry \& Staska, 2001), which can lead to a state of
-self-objectification (Bernard, Legrand, \& Klein, 2018; Calogero et al.,
-2011; Moradi \& Huang, 2008). Being objectified by another person and
-possessing trait-level self-objectification (TSO) may interact to
-influence experiences of feeling like a body, or state
-self-objectification (SSO) (B. L. Fredrickson, Roberts, Noll, Quinn, \&
-Twenge, 1998, Garcia et al. (2016)). Does this habit
-self-objectification lead women to also objectify other women, possibly
-to compare oneself?
+Self-objectification is a psychological process that provides a
+cognitive mechanism to translate the experiences of interpersonal
+objectification (Loughnan et al., 2015a) to negative mental health
+outcomes (e.g., anxiety, self-esteem, and cognitive performance)
+(Calogero, Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008).
+Calogero et al. (2011) proposes that self-objectification can be
+conceptualized as a learned trait, or \emph{trait} self-objectification
+(TSO). Furthermore, it can also be elicited momentarily, through the
+media, for example, with sexualized images in movies and magazines
+(Morry \& Staska, 2001), or when wearing sexualizing clothing (B. L.
+Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998). This momentary
+self-objectification is referred to as \emph{state} self-objectification
+(Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \&
+Huang, 2008). Being objectified by another person may interact TSO to
+effect experiences of feeling like a body, or state self-objectification
+(SSO; Garcia et al., 2016).
 
@@
 
+Harsey and Zurbriggen (2020) found that self-objectification was related
+to the objectification of women to a similar degree for men and women
+participants (although men scored higher than women on a measure of
+belief that objectification of women is natural for men). Additionally,
+Strelan and Hargreaves (2005) found that the more women self-objectify,
+the more they objectify other women. Could the process work in the other
+direction as well, that is, could objectification by a woman produce
+self-objectification, in a similar manner to mixed-gender interactions?
+
+{[}Asha comment on next paragraph: Hill and Fischer (2008) assessed
+women's experiences of objectification from men separately from women's
+experiences of objectification from women, and found that women may be
+socialized not only to see themselves as objects, but perhaps to see
+other women as objects as well, although this process was not comfirmed
+to occur during an actual interpersonal interaction
+
+Could this sentence be written like:
+
+Though, when Hill and Fischer(2008) assessed women's experiences of
+objectification from men independently from that of women, they found
+that women are likely to be socialized to not only to see themselves s
+objects, but potentially see other women as objects as well. This
+process ,however, was not confirmed to occur during an interpersonal
+interaction.{]}
+
 Past research has focused on men's objectifying behaviors, with little
-attention to the role that women may also play in enacting
-objectification of women. Hill and Fischer (2008) assessed women's
-experiences of objectification from men separately from women's
-experiences of objectification from women and found that women may be
-socialized not only to see themselves as objects but perhaps to see
-other women as objects as well (THEY DIDN'T DETERMINE THIS IN PERSON).
-Some studies have found that women objectify other women to a greater
-extent than they objectify men (Loughnan et al., 2015a). Women objectify
-(dehumanized) sexualized targets presented as images (Puvia \& Vaes,
-2013), but we know next to nothing about interpersonal sexual
-objectification among women and what the immediate effects might be.
-Further, do women objectify non-sexualized women they are interacting
-with? What might be different for same-gender interactions? Harsey and
-Zurbriggen (2020) found that self-objectification was related to the
-objectification of women to a similar degree for men and women
-participants, although men scored high than women on a measure of belief
-that objectification of women is natural for men. ASK RANDI-WE KNOW
-OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN
-(Gervais, Vescio, \& Allen, 2011; Moradi \& Huang, 2008; Saguy, Quinn,
-Dovidio, \& Pratto, 2010)\ldots{}MENTION THAT\ldots{}HOWEVER DOES WOMEN
-OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?\ldots{}STILL
-TRYING TO FIGURE THAT OUT? ADDITIONALLY Strelan and Hargreaves (2005)
-FOUND THAT THE MORE WOMEN SELF-OBJECTIFY, THE MORE THEY OBJECTIFY OTHER
-WOMEN.
+attention paid to the role that women may also play in objectifying
+other women. Hill and Fischer (2008) assessed women's experiences of
+objectification from men separately from women's experiences of
+objectification from women and found that women may be socialized not
+only to see themselves as objects but perhaps to see other women as
+objects as well, although this process was not comfirmed to occur during
+an actual interpersonal interaction. Loughnan et al. (2015a) found that
+women objectify other women to a greater extent than they objectify men.
+Women have also been found to objectify (dehumanized) sexualized targets
+presented as images (Puvia \& Vaes, 2013), but very little is known
+about interpersonal sexual objectification among women and what the
+proximal effects of this objectification might be. We do know that
+objectification has more adverse consequences for women than men
+(Gervais et al., 2011; Moradi \& Huang, 2008; Saguy, Quinn, F Dovidio,
+\& Pratto, 2010), however, if women objectify other women, perhaps even
+to a stronger degree than they objectify men, this higher level of
+objectification might be a detrimental combination.
 
@@
 
-SIMO model and literature review (Gervais et al., 2020). Studies have
-shown that within social encounters women are gazed at more than men
-(Briton \& Hall, 1995), often times feel \enquote{looked at} within
-interpersonal interactions (Argyle \& Williams, 1969; Miles-McLean et
-al., 2015), and will more than likely internalize the objectifying gaze
-on physical self (Puvia \& Vaes, 2013; Young, 1979). Moreover, perhaps
-the most adverse effect of objectifying treatment is that it effectively
-socializes girls and women to treat themselves as objects to be looked
-at and evaluated, an effect termed self-objectification (Bartky, 1990;
-Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et al., 1998). We
-don't know about women-on-women interpersonal objectification. What
-might be different?
-
-Self-objectification has been found to occur after a mere relationship
-prime among women (Sanchez \& Broccoli, 2008) because in our culture
-women need to look attractive to obtain and maintain successful
-relationship, thus, the ``college relationships condition may heighten
-self-objectification and the evaluation of other women in a sexualized
-way. Among heterosexual male and female college students, self-
-objectification has been found to be positively associated with the
+Studies have shown that within social encounters women are gazed at more
+than men (Briton \& Hall, 1995), and often times feel \enquote{looked
+at} within interpersonal interactions (Argyle \& Williams, 1969;
+Miles-McLean et al., 2015), and will more than likely internalize the
+objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
+1979). Moreover, perhaps the most adverse effect is that it socializes
+girls and women to treat themselves as objects to be looked at and
+evaluated (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; B. L.
+Fredrickson et al., 1998). Gervais et al. (2020) recently reviewed the
+research on interpersonal objectification and organized our current
+theoretical understanding of this process in the Social Interaction
+Model of Objectification (SIMO). What is clear from Gervais et al.
+(2020) is that we know little about women-on-women interpersonal
+objectification. Could there also be negative consequences of this type
+of interpersonal objectification? Perhaps women could be amplifying each
+others' state self-objectification as they get ready to go out for the
+night {[}EDIT??{]}, \emph{before} the theoretical encounters with men
+organized in the SIMO occur. In this way, women's rituals of getting
+ready together might place even women with low TSO in a higher SSO
+group. {[}Kat: This has me thinking about the difference between
+objectification in a romantic setting (which was the setting created in
+the initial experiment) vs objectification in a platonic setting/between
+friends. Might be useful to discuss this difference, or just have a
+sentence here that clarifies objectification can occur within non-sexual
+settings{]} {[}Asha: I think this is a great way to illustrate the
+potential experience but when I read it I was kind of like
+\enquote{wait, when did we talk about women going out?}{]}
+
+Interpersonal objectification can also occur within the context of
+romantic relationships, in addition to interactions with strangers.
+Among heterosexual male and female college students,
+self-objectification has been found to be positively associated with the
 extent to which they objectify their romantic partners (Zurbriggen,
@@
 objectification and self-objectification in romantic relationships
-(Strelan \& Pagoudis, 2018). Evidence is mixed, and women can sometimes
-have positive outcomes from appearance valuation within the context of
-an established romantic relationship and they experience less SSO after
-appearance comments within romantic relationships (Meltzer, 2020), less
-is known about first dates. But this literature is also only about
+(Strelan \& Pagoudis, 2018). Evidence is mixed, suggesting that women
+can sometimes have positive outcomes from appearance valuation within
+the context of an established romantic relationship. There is also
+evidence that they experience less SSO after appearance comments within
+romantic relationships (Meltzer, 2020), but less is known about first
+dates. An important caveat to this literature is that it is only about
 heterosexual relationships. A recent study has investigated the effect
@@
 in general (including same-sex friendships) {[}CITE PWQ paper I
-reviewed, Yoder editor{]}. Empirical evidence reveals that
+reviewed, Yoder editor{]}. Both romantic relationships and stranger
+encounters have been studied in the context of objectification, but
+neither of these literatures have investigated specifically same-gender
+relationships.
+
+There is evidence that the experience of state self-objectification in
+mixed-gender contexts (stranger and romantic) has negative consequences
+for women, but what about in the context of interactions with other
+women? Is the self-objectification experienced in mixed-gender
+interactions associated with the same negative process as that
+experienced in same-gender interactions? On the one hand, there is ample
+research demonstrating that the male gaze has a particularly detrimental
+effect would suggest no (Gay \& Castano, 2010; Gervais et al., 2011;
+Saguy et al., 2010, Calogero (2004); Yilmaz \& Bozo, 2019), but on the
+other hand, women do objectify other women (Harsey \& Zurbriggen, 2020;
+Loughnan et al., 2015a; Puvia \& Vaes, 2013). When they do it, does it
+lead to self-objectification in the same way men's objectification of
+women does (Garcia et al., 2016)? If so, does the self-objectification
+experienced in these same-gender interactions have the same negative
+consequences for authenticity in that interaction?
+
+\subsection{Interpersonal Objectification and
+Authenticity}\label{interpersonal-objectification-and-authenticity}
+
+There is some evidence that reduced authenticity is a consequence of
+self-objectification in the moment {[}Garcia et al. (2016); again CITE
+PWQ paper I reviewed, Yoder editor{]}. This link has been justified by
+the literature on stigmatized-stigmatizer interactions (M. R. Hebl \&
+Dovidio, 2005; Richeson \& Shelton, 2003; Shelton, Richeson, \&
+Salvatore, 2005), viewing the experience of being objectified in an
+interaction as an identity threat situation (Miles-McLean et al., 2015;
+Nadal \& Haynes, 2012). Further, empirical evidence reveals that
 objectification manifests through inauthenticity in romantic
@@
 female cognitive performance (Kahalon, Shnabel, \& Becker, 2018; D. M.
-Quinn, Chaudoir, \& Kallen, 2011). Both romantic relationships and
-relationships in general have been studies in the context of
-objectification, but neither of these literatures have investigated
-specifically same-gender relationships.
-
-There is evidence that the experience of state self-objectification in
-mixed-gender contexts (stranger and romantic) and within the self in any
-moment (trying on a swimsuit) has negative consequences, but what about
-in the context of interaction with other women? Is the
-self-objectification experience in mixed-gender interactions the same as
-that experienced in same-gender interactions? The ample research
-demonstrating that the male gaze has a particularly detrimental effect
-would suggest no (Gay \& Castano, 2010; Gervais, Vescio, \& Allen, 2011;
-Saguy, Quinn, F Dovidio, \& Pratto, 2010, Calogero (2004); Yilmaz \&
-Bozo, 2019). Women do objectify other women (Harsey \& Zurbriggen, 2020;
-Loughnan et al., 2015a; Puvia \& Vaes, 2013), but when they do it, does
-it lead to self-objectification in the same way men's objectification of
-women does (Garcia et al., 2016)? If so, does the self-objectification
-experienced in these same-gender interactions have the same negative
-consequences for authenticity in that interaction?
-
-\subsection{Interpersonal Objectification and
-Authenticity}\label{interpersonal-objectification-and-authenticity}
-
-There is some evidence that reduced authenticity is a consequence of
-self-objectification in the moment {[}Garcia et al. (2016); again CITE
-PWQ paper I reviewed, Yoder editor{]}. This link has been justified by
-the literature on stigmatized-stigmatizer interactions (CITE LITERATURE
-DIDN'T COME ACROSS THIS), viewing the experience of being objectified in
-an interaction as an identity threat situation (MAYBE CITE MILES-MCLEAN
-PAPER \enquote{STOP LOOKING AT ME!}). When a woman is objectified by a
-man, and then experiences self-objectification, this intergroup
-encounter might trigger identitiy threat, but is the same negative
-consequence present when a woman is objectified by another woman?
-woman-woman interpersonal objectification processes might diverge from
-this process. One the one hand, she may not be having the same negative
-consequences the cascade from situations that threated group-based
-identity (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \& Shelton,
-2006; M. R. Hebl \& Dovidio, 2005), but feeling like a body, rather than
-a full human, in an interaction may be enough to reduce feelings of
-authenticity and social competence, regardless of the gender of the
-objectifyer {[}Tolman, Impett, Tracy, and Michael (2006); PWQ paper I
-reviewed, Yoder editor{]}. I DONT KNOW WHERE THIS PAPER IS? ASK RANDI
-ABOUT IDENTITY\_THREAT PAPERS
+Quinn, Chaudoir, \& Kallen, 2011). When a woman is objectified by a man,
+and subsequently experiences self-objectification, the intergroup nature
+of this encounter might trigger identity threat. Thus, perhaps there are
+fewer negative consequences when a woman is objectified by another
+woman, specifically, woman-woman interpersonal objectification processes
+might diverge from mix-gender interpersonal objectification processes
+precisely because they are not intergroup interactions (at least with
+respect to gender identity). A woman objectified by another woman may
+not be having the same negative consequences that cascade from
+situations that trigger group-based identity threat (Deaux \& Major,
+1987; Dovidio, Hebl, Richeson, \& Shelton, 2006; M. R. Hebl \& Dovidio,
+2005), but feeling like a body, rather than a full human, in any
+interaction (intergroup or ingroup) may be enough to reduce women's
+feelings of authenticity and social competence, regardless of the gender
+of the objectifyer {[}Tolman, Impett, Tracy, and Michael (2006); PWQ
+paper I reviewed, Yoder editor{]}.
 
@@
 interaction in which one or both partners are objectifying each other,
-similarly to Garcia et al. (2016), but between same-sex female
-interpersonal interactions. Moreover, the current study uses a
+similarly to Garcia et al. (2016), but between same-gender interpersonal
+interactions among women. Moreover, the current study uses a
 face-to-face interaction paradigm and dyadic data analysis techniques to
-examine the effects for both women simultaneously. We expected to
-replicate the results found in Garcia et al. (2016). We predicted that
-being objectified by one's interaction partner would lead to
-self-objectification, which in turn would lead to feelings of
-inauthenticity, then reduced feelings of agency in romantic
-relationships, reduced career aspiration, and reduced cognitive
-performance. Specifically, we expected to find a positive relationship
-between other-objectification by one's partner and state
-self-objectification. We also expect to find a negative relationship
+examine the effects for both women simultaneously. Although the
+literature on woman-woman objectification is small, the results are
+mixed, and does not cover interpersonal encourters, we expected to
+replicate some of the results found in Garcia et al. (2016). Most
+importantly, we predicted that being objectified by one's interaction
+partner would lead to self-objectification. We also expected, in line
+with Garcia et al. (2016), that TSO would moderate this relationship,
+amplifying the positive assocaition between being objectified and SSO
+for women higher in TSO. We hypothesized that SSO would, in turn, lead
+to feelings of inauthenticity (although there is ample support against
+this prediction from the identity threat within intergroup interactions
+literature; Rollero, 2016). Further, we hypothesized that these feelings
+of inauthencity would then be associated with reduced feelings of agency
+in romantic relationships, reduced career aspiration, and reduced
+cognitive performance. In summary, we expected to find a positive
+relationship between other-objectification by one's partner and state
+self-objectification. We also expected to find a negative relationship
 between self-state objectification and interaction authenticity, and
@@
 
-Puvia and Vaes (2013) would alternatively predict that women's tendency
-to self-objectify (TSO) leads them to objectify other women
-(\ldots{}well, dehumanize a sexualized woman, but also Strelan and
-Hargreaves (2005) would predict the TSO-\textgreater{}SOO link and
-Harsey and Zurbriggen (2020) too), and this is mediated by the woman's
-own state self-objectification (SSO). So we also tested this as a
-possible alternative model.
+Here we would like to note that Puvia and Vaes (2013) would
+alternatively predict that women's tendency to self-objectify (TSO)
+leads them to objectify other women (more precisely, to dehumanize a
+sexualized woman). In addition, Strelan and Hargreaves (2005) and Harsey
+and Zurbriggen (2020) would predict the TSO to other-objectification
+link, further theorezing that this relationships is mediated by the
+woman's own state self-objectification (SSO). This limited, but extant,
+set of literature on woman-woman objectification points to a possible
+alternative model from the model hypothesized in the current study.
+Where appropriate, we report results considering the causal directions
+implied by this alternative mediation model.
 
@@
 
-The procedure used was identical to that in Garcia et al. (2016), except
-for the instructions that the participants were given. In brief, that
+Except for the instructions given to participants, the procedure used
+was identical to that in Garcia et al. (2016). In brief, that
 methodology is that each participant arrived at the laboratory and were
@@
 interaction, please think about your partner's potential as a romantic
-partner. Even if they are not the gender you are attracted to, you can
-still judge their potential as a romantic partner. After the interaction
-you will be asked to evaluate how dateable your partner is. In other
-words, we would like to know if you think someone would date your
-interaction partner. Also, your interaction partner will be evaluating
-you in the same manner.
+partner. \textbf{Even if they are not the gender you are attracted to},
+you can still judge their potential as a romantic partner. After the
+interaction you will be asked to evaluate how dateable your partner is.
+In other words, we would like to know if you think someone would date
+your interaction partner. Also, your interaction partner will be
+evaluating you in the same manner.
 \end{quote}
 
-The decision was made to ask even heterosexual women to judge their
-women partners as potential romantic partners. We felt that this prompt
-would keep the study closest to a replication of the previous Garcia et
-al. (2016) version of the study. Past research has found that women,
-largely due to an increase self-objectifying state, are indeed able to
-evaluate other women's potential as romantic partners--indeed, women may
-be unfortunately used to thinking this way about themselves, and we
-suspect other women.
-
-Two participants were then brought into a larger interaction room where
-they sat on stools prearranged to be 36 inches apart. The experimenter
-instructed the participants to \enquote{get to know each other} for 10
-minutes and then left the room. After 10 minutes, the experimenter came
-back into the room and stopped the interaction. The participants then
-went back to their individual cubicles and completed a set of
-post-interaction measures. Participants were then thanked for their
-participation and debriefed Garcia et al. (2016). The full methodology
-used is found in Garcia et al. (2016)'s study.
+\emph{All} participants were told that they were assigned to the
+\enquote{College Relationships} condition. Self-objectification has been
+found to occur after a mere relationship prime among women (Sanchez \&
+Broccoli, 2008) because, in Westurn culture and beyond, women need to
+look attractive to obtain and maintain successful relationship, thus,
+the \enquote{College Relationships} condition may heighten
+self-objectification and the evaluation of other women in a sexualized
+way. The decision was made to ask even heterosexual women to judge their
+fellow-woman partners for their potential as romantic partners. We felt
+that this prompt would keep the study closest to a replication of the
+previous Garcia et al. (2016) version of the study, and strengthen the
+potential for objectification that would normally be low in the context
+of a psychology laboratory. Recall that, past research has found that
+women are indeed able to evaluate other women's potential as romantic
+partners {[}i.e., their sexual attractiveness; CITE{]}---indeed, women
+may be unfortunately quite used to thinking about their own
+\enquote{datability,} and we suspect this this habitual thought pattern
+will translate to their thoughts about other women.
+
+After recieving the \enquote{College Relationships} prompt, the two
+participants were then brought into a larger interaction room where they
+sat on stools prearranged to be approximately 1 meter apart. The
+experimenter instructed the participants to \enquote{get to know each
+other} for 10 minutes and then left the room. After 10 minutes, the
+experimenter came back into the room and stopped the interaction. The
+participants then went back to their individual cubicles and completed a
+set of post-interaction measures. Participants were then thanked for
+their participation and debriefed. More detail on this methodology can
+be found in Garcia et al. (2016).
 
@@
 
-Due these similarities across samples in regard to correlation patterns
-between significant variables within this study, the two datasets were
-combined. These participants were mostly first-year college students,
-with an average age of 18.85 (SD = 1.04). The sample was 48.44\%
-White/European American, 9.38\% Black/African-American, 28.12\%
-Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
-8 White/White pairs and 4 same race racial minority pairs, for a total
-of 12 same-race pairs. The remaining 20 were mixed race pairs, of which
-15 were White/racial minority pairings and 5 were cross-racial minority
-group pairs. 64.06\% of the sample identified as heterosexual, and 25\%
-identified as gay, lesbian or bisexual.
+Due to these similarities across samples in regard to correlation
+patterns between significant variables within this study, the two
+datasets were combined. These participants were mostly first-year
+college students, with an average age of 18.85 (SD = 1.04). The sample
+was 48.44\% White/European American, 9.38\% Black/African-American,
+28.12\% Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race.
+There were 8 White/White pairs and 4 same race racial minority pairs,
+for a total of 12 same-race pairs. The remaining 20 were mixed race
+pairs, of which 15 were White/racial minority pairings and 5 were
+cross-racial minority group pairs. 64.06\% of the sample identified as
+heterosexual, and 25\% identified as gay, lesbian or bisexual.
 
@@
 frequency of thoughts in relation to multiple characteristics of their
-partner Garcia et al. (2016). Questions included aspects of their
+partner (Garcia et al., 2016). Questions included aspects of their
 partner's internal traits such as personality, friends, family, and
 extracurricular interests, as well as external traits such as body,
-appearance, clothing, and body parts. All questions were to be rated on
-a scale from 1 (not at all) to 7 (constantly). Objectification was
+appearance, clothing, and body parts. All questions were rated on a
+scale from 1 (not at all) to 7 (constantly). Objectification was
 measured by getting the difference between the average frequency of
@@
 authentic during your interaction?}' These questions were ranked on a
-scale from 1 (not authentic at all). These were combined to form the
-authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) = 0.91
-for Sample 2).
+scale from 1 (not at all) to 7 (very much). These were combined to form
+the authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) =
+0.91 for Sample 2).
 
@@
 We used R (Version 3.5.2; R Core Team, 2017) and the R-packages
-\emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools}
-(Version 1.13.5; Wickham, Hester, \& Chang, 2018), \emph{dplyr} (Version
-0.8.3; Wickham, François, Henry, \& Müller, 2018), \emph{forcats}
-(Version 0.3.0; Wickham, 2018), \emph{ggformula} (Version 0.7.0; D.
-Kaplan \& Pruim, 2017), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
-\emph{haven} (Version 2.1.0; Wickham \& Miller, 2019), \emph{irr}
-(Version 0.84.1; Gamer, Lemon, \&
-\textless{}puspendra.pusp22@gmail.com\textgreater{}, 2012), \emph{knitr}
-(Version 1.25; Xie, 2015), \emph{kutils} (Version 1.70; Johnson, Kite,
-\& Redmon, 2019), \emph{lattice} (Version 0.20.38; Sarkar, 2008),
-\emph{lavaan} (Version 0.6.1; Rosseel, 2012), \emph{lpSolve} (Version
-5.6.15; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.15; Bates
-\& Maechler, 2017), \emph{mosaic} (Version 1.2.0; Pruim, Kaplan, \&
-Horton, 2017, 2016), \emph{mosaicData} (Version 0.17.0; Pruim et al.,
-2016), \emph{nlme} (Version 3.1.137; Pinheiro, Bates, DebRoy, Sarkar, \&
-R Core Team, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
-2018), \emph{psych} (Version 1.8.4; Revelle, 2017), \emph{purrr}
-(Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.1.1;
-Wickham, Hester, \& Francois, 2017), \emph{stringr} (Version 1.4.0;
-Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
-\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse}
-(Version 1.2.1; Wickham, 2017), \emph{usethis} (Wickham \& Bryan, 2018),
-and \emph{xtable} (Version 1.8.3; Dahl, Scott, Roosen, Magnusson, \&
-Swinton, 2019) for all our analyses.
+\emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{psych} (Version
+1.8.4; Revelle, 2017), \emph{nlme} (Version 3.1.137; Pinheiro, Bates,
+DebRoy, Sarkar, \& R Core Team, 2017) for our analyses. Further, we used
+the R-packages \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018),
+\emph{apaTables} (Version 2.0.5; Stanley, 2018), with \emph{knitr}
+(Version 1.25; Xie, 2015) to create a fully reproducible manuscript in
+\emph{rmarkdown} (Version 1.15; Xie, Allaire, \& Grolemund, 2018).
 
@@
 self-objectification (SSO). See Figure~\ref{fig:2016figure} for the
-results of the analysis from this previous study. We hope to investigate
-how the central effects found in the previous study relate to
-interactions between two women. Specifically, we are interested in
-testing the relationship between state-other objectification and SSO,
-and how SSO in turn, affects feelings of inauthenticity during the
-interaction. In addition, we will also test if the effect of
-other-objectification in an interaction on SSO is only present for those
-women who are high in trait self-objectification, as in Garcia et al.
-(2016). Further, we will investigate the relationships between
-experiencing interaction inauthenticity and relationship agency, career
-aspirations, and cognitive performance.
-
-While Garcia et al. (2016) used dyadic path analysis, we will conduct
-our dyadic analyses using multilevel modeling. Dyadic analyses for
+results of the analysis from this previous study. We investigated how
+the central effects found in the previous study relate to interactions
+between two women. Specifically, we are interested in testing the
+relationship between state-other objectification and SSO, and how SSO in
+turn, affects feelings of inauthenticity during the interaction. In
+addition, we will also test if the effect of other-objectification in an
+interaction on SSO is only present for those women who are high in trait
+self-objectification, as in Garcia et al. (2016). Further, we will
+investigate the relationships between experiencing interaction
+inauthenticity and relationship agency, career aspirations, and
+cognitive performance. {[}Asha: This section feels like a mixture of
+explaining what the study was intended to investigate as wel as future
+directions. Is that the point, or can this be organized better?{]}
+
+While Garcia et al. (2016) used dyadic path analysis, the current study
+used multilevel modeling for our dyadic analyses. Dyadic analyses for
 distinguishable dyads (e.g., mixed-gender interacting pairs) is more
 natural in Structural Equation Modeling (SEM) than it is for
-indistinguishable dayds (e.g., same-gender interacting pairs) (Garcia,
+indistinguishable dyads (e.g., same-gender interacting pairs) (Garcia,
 Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
@@
 Before moving to the main analyses, we discuss statistical equivalence
-test that provide support for combining Sample 1 and Sample 2 in one
+tests that provide support for combining Sample 1 and Sample 2 in one
 analysis sample. The online supplemental material contains the main
@@
 was statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12,
-\emph{p} = .019, replicating Garcia et al. (2016)'s finding. One's own
-other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
-= 0.12, \emph{p} = .210. Contrary to past finding however, there was no
-statistically significant interaction of partner's other objectification
-and the person's trait self-objectification on SSO, \emph{b} = 0.03,
-\emph{SE} = 0.27, \emph{p} = .910. There was also no significant main
-effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
-0.05, \emph{p} = .183.
-
-Contrary to expectations, there was no significant effect of SSO on
-interaction authenticity, although the estimate of this effect was in
-the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12,
-\emph{p} = .431. Because authenticity was a composite score of 9 items,
-two of which were interaction specific authenticity items, we also
-estimated the pairwise correlations between SSO and all these items
-individually. They were all small, ranging from only -0.01 to -0.14.
-Although we hypothesized that SSO would mediate the relationship between
-partner's other objectification and interaction authenticity, after
-finding no relationship between SSO and authenticity, we also tested if
-the partner's other objectification had a direct effect on authenticity,
-but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
+\emph{p} = .019. One's own other objectification had no effect on SSO,
+\emph{b} = -0.16, \emph{SE} = 0.12, \emph{p} = .210. Inconsistent with
+past findings however, there was no statistically significant
+interaction of partner's other objectification and the person's trait
+self-objectification on SSO, \emph{b} = 0.03, \emph{SE} = 0.27, \emph{p}
+= .910. There was also no significant main effect of trait
+self-objectification on SSO \emph{b} = 0.07, \emph{SE} = 0.05, \emph{p}
+= .183.
+
+There was no significant effect of SSO on interaction authenticity,
+although the estimate of this effect was in the hypothesized negative
+direction, \emph{b} = -0.09, \emph{SE} = 0.12, \emph{p} = .431. Because
+authenticity was a composite score of 9 items, two of which were
+interaction specific authenticity items, we also estimated the pairwise
+correlations between SSO and all these items individually. They were all
+small, ranging from only -0.01 to -0.14. Although we hypothesized that
+SSO would mediate the relationship between partner's other
+objectification and interaction authenticity, after finding no
+relationship between SSO and authenticity, we also tested if the
+partner's other objectification had a direct effect on authenticity, but
+this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
 \emph{p} = .608 (nor was the total effect of partner's other
@@
 positively related to both career aspirations, \emph{b} = 0.18,
-\emph{SE} = 0.07, \emph{p} = .010, and relationships agency, \emph{b} =
+\emph{SE} = 0.07, \emph{p} = .010, and relationship agency, \emph{b} =
 0.23, \emph{SE} = 0.12, \emph{p} = .049. There was no direct effect of
@@
 al. (2016) replicates in a same-gender dyadic sample of women only.
-Although past reserach has found that women do objectify other women
+Although past research has found that women do objectify other women
 (Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes,
@@
 in their woman-identified interaction partners. As hypothesized, the
-current study did find a significant relationship bewteen a woman's
-partner's report of having objectified her and her own post-interaction
-feelings of self-objectification. That is, there was a significant
-partner effect of other-objectification on SSO. This effect extends the
-equivalent relationship found in mixed-gender interactions to the
-context of same-gender interactions between women. Thus, it could be
-that it is not only the male gaze, and male other-objectification that
-is related to women's state self-objectification, but being objectified
-by another woman can also results in SSO, at least in the context of a
-scenario where they know they are being evaluated as a potential dating
-partner.
-
-As is the case in all correlational studies, we cannot be sure in the
+current study did find a significant relationship between a woman's
+interaction partner's report of having objectified her and her own
+post-interaction feelings of self-objectification. That is, there was a
+significant partner effect of other-objectification on SSO. This effect
+extends the equivalent relationship found in mixed-gender interactions
+to the context of same-gender interactions between women. Thus, evidence
+suggests that it is not only the male gaze, and male
+other-objectification that is related to women's state
+self-objectification, but being objectified by another woman can also
+result in SSO, at least in the context of a scenario where they know
+they are being evaluated as a potential dating partner. {[}Asha:Or
+\ldots{} thus evidence provides support for the claim that women being
+objectified by another woman result in sso in ways that are not uniquely
+dissimilar from that of xyz{]}
+
+As is the case in all correlational studies, we cannot be sure about the
 causal direction. It could be that women's SSO causes them to be
-objectified by their interaction partner. This interpretation in
-theoreticall interesting given that, in both the Garcia et al. (2016)
-study and in the current study, it is \emph{women's} SSO this relates to
+objectified by their interaction partner. This interpretation is
+theoretically interesting given that, in both the Garcia et al. (2016)
+study and in the current study, it is \emph{women's} SSO that relates to
 being objectified by one's partner. However, Objectification Theory
@@
 {[}Saguy et al. (2010); CITE{]}, suggest that the causal flow is from
-other-objectification to SSO. Although, importantly, the current study
-found evidence for the partner effect of other-objectification on SSO,
-there was a lack of evidence for the connections between SSO and
-downstream negative consequences.
+other-objectification to SSO. Although, the current study found evidence
+for the partner effect of other-objectification on SSO, there was a lack
+of evidence for the connections between SSO and downstream negative
+consequences.
 
@@
 mixed-gender dyads is the lack of evidence for relationships between SSO
-and felt inauthenticity. In addition, we found no evidence of
+and interaction inauthenticity. In addition, we found no evidence of
 \emph{direct} or \emph{indirect} relationships between SSO and cognitive
@@
 other-objectification and any of these outcomes. This is somewhat
-suprising given the plentiful evidence linking SSO and cognitive
-functioning (B. L. Fredrickson et al., 1998; Quinn, Chaudoir, \& Kallen,
-2011) and the small, but extant research on interpersonal
-other-ojectification and cognitive functioning (Garcia et al., 2016;
-Logel et al., 2009). This lack of evidence could potentially signal
-diverging processs between women's experiences with interpersonal
-objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is
-particularly detrimental (Calogero, 2004; Gervais, Holland, \& Dodd,
-2013; Gervais et al., 2011; Roberts \& Fredrickson, 1997), and perhaps
-the self-objectification experienced within an interaction with a women
-is not as harmful as the self-objectificatoin experienced within an
-interaction with a man. However, as a strong note of caution, we need to
-be careful not to interpret a null result as evidence of no
-relationship.
+suprising given the extant evidence linking SSO and cognitive
+functioning (B. L. Fredrickson et al., 1998; and see Moradi \& Huang,
+2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the small, but
+extant research on interpersonal other-ojectification and cognitive
+functioning (Garcia et al., 2016; Logel et al., 2009). This lack of
+evidence could potentially signal diverging processes between women's
+experiences with interpersonal objectification from men and
+interpersonal objectification from women. There is quite a bit of
+evidence suggesting that the male gaze is particularly detrimental
+(Calogero, 2004; Gervais, Holland, \& Dodd, 2013; Gervais et al., 2011;
+Roberts \& Fredrickson, 1997), and perhaps the self-objectification
+experienced within an interaction with a women is not as harmful as the
+self-objectification experienced within an interaction with a man. As a
+strong note of caution, it is best not to interpret a null result as
+evidence of no relationship.
 
@@
 authenticity is surprising and again, should not be interpreted as
-evidence of no realtionship. It should be noted that the estimate of
+evidence of no relationship. It should be noted that the estimate of
 this relationship was very small, but in the negative direction, as
@@
 connection between women's feelings of SSO and inauthenticity in
-interactions with other women then in interactions with men, models of
+interactions with other women than in interactions with men, models of
 interpersonal objectification, like the SIMO (Gervais et al., 2020),
 could be extended by including inauthenticity as a potential mediating
-factor in decisions to continue objectifying interactions. Further,
-gender of the objectifyer/interaction partner could also be added to the
-SIMO model to help extend our understanding of under what circumstances
-other-objectification and SSO have negative concequences for women.
-
-Although we did not find a connection bewteen SSO and authenticity we
+factor. Further, gender of the objectifyer/interaction partner could
+also be added to the SIMO model to help understand the circumstances
+that require other-objectification and SSO to have negative consequences
+for women.
+
+Although we did not find a connection between SSO and authenticity, we
 did find significant positive relationships between authenticity and
-relationship agency and career aspirations. The relationship between
-authenticity and cognitive functioning was also estimated as positive,
-but it was not statistically signfiicant. Again, due to the lack of
-connection between SSO and authenticity, we found no evidence of
-\emph{indirect} relationships between SSO and these outcome variables.
-This evidence of a relationship between authenticity and the relational
-outcome variables (i.e., relationship agency and career aspirations)
-provides evidence that corrborates past findings that felt authenticity
-in interactions is important for healthy relationship functioning
-{[}Garcia et al. (2016); PWQ paper I reviewed{]}. Just as authenticity
-has been found to be important in intergroup interactions {[}CITE; CITE;
-CITE{]}, we again find more evidence here that distuptions in feelings
-of authenticity can negatively impact relationships beyond the current
+relationship agency, and authenticity and career aspirations. The
+relationship between authenticity and cognitive functioning was also
+estimated as positive, but was not statistically signficant. Again, due
+to the lack of connection between SSO and authenticity, we found no
+evidence of \emph{indirect} relationships between SSO and these outcome
+variables. This evidence of a relationship between authenticity and the
+relational outcome variables (i.e., relationship agency and career
+aspirations) provides evidence that corroborates past findings that felt
+authenticity in interactions is important for healthy relationship
+functioning {[}Garcia et al. (2016); PWQ paper I reviewed{]}. Just as
+authenticity has been found to be important in intergroup interactions
+(Brunell et al., 2010; Garcia et al., 2016; Tolman et al., 2006), we
+again find more evidence here that disruptions in feelings of
+authenticity can negatively impact relationships beyond the current
 partner. Although the current study did not find a connection between
 authenticity and SSO, this seems theoretically to be a natural
-connection, and more work needs to be done to discover when and how SSO
-leads to inauthenticity in interpersonal objectification situations.
+connection, and future work must explore when and how SSO leads to
+inauthenticity in interpersonal objectification situations.
 
@@
 
-The sample size was small and combined across two higher education
-institutions.
-
-The sample of the current study was comprised of Western women, being
-that sexual objectification is most prevalent in this culture (Loughnan
-et al., 2015b), and research on objectification conducted outside of
+In addition to being small and combined across two institutions, the
+sample of the current study was comprised of Western women, being that
+sexual objectification is most prevalent in this culture (Loughnan et
+al., 2015b), and research on objectification conducted outside of
 Western or Westernized countries is scarce (Moradi \& Huang, 2008),
@@
 cross-cultural framework (Loughnan et al., 2015b, Wollast et al.
-(2020)). Because \enquote{bodies exist within social and cultural
+(2020)). Since \enquote{bodies exist within social and cultural
 contexts, and hence are also constructed through sociocultural practices
@@
 ethnicities are exposed to varied amounts of sexualizing content.
+{[}Kat: Or a longitudinal study is needed.{]}
 
@@
 non-heterosexual women, but all participants were asked to think about
-and evaluate their partner as a potential data parter. While we think
-that hetereosexual women are indeed able to do this with other women as
-their target---indeed, there is evidence that they might do this readily
-(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---they might be more
-apt to activate social comparison processes (Festinger, 1954) than women
-who are sexually attracted to other women (non-heterosexual women). This
-differential psychological process between women with differing
-sexualities might have served to dampen our ability to detect
-relationships, adding variability.
+and evaluate their partner as a potential dating/romantic partner. We
+think that hetereosexual women are able to do this with other women as
+their target---and there is evidence that they might do this readily
+(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---they may be even
+more apt to activate social comparison processes (Festinger, 1954) than
+women who are sexually attracted to other women (non-heterosexual
+women). This differential psychological process between women with
+differing sexualities might have served to dampen our ability to detect
+relationships, adding variability. {[}Kat: The only other thing I would
+add re: sexuality limitations are that we didn't collect/use sexual
+orientation, so we couldn't analyze results by that at all/our samples
+might have differed there.{]}
 
@@
 sexual objectification but internalize them less than heterosexual women
-do. Consistent with previous reseach Hill and Fischer (2008) determined
-lesbians existed less physical appearance concerns compared to
-heterosexual women, however there was no difference found that lesbian
-women self-objectify less than heterosexual women and they did not find
-that sexual orientation moderates the relationshiotn between sexual
-objecitifcantion and self-objectification This contradicts older
+do. Consistent with previous research, Hill and Fischer (2008)
+determined that lesbians existed less physical appearance concerns
+compared to heterosexual women, however there was no evidence found that
+lesbian women self-objectify less than heterosexual women and they did
+not find that sexual orientation moderates the relationship between
+sexual objectification and self-objectification. This contradicts older
 theoretical literature that suggests that lesbians internalize cultural
 sexual objectification less than do heterosexual women (Brown, 1987;
-LUM, 1994; Pitman, 1999; Siever, 1994)
+LUM, 1994; Pitman, 1999; Siever, 1994).
 
@@
 Sexism has recently been found to be related to the objectification of
-women, but not men, for both men and women (Harsey \& Zurbriggen, 2020).
+women, but not men, for both men and women (Harsey \& Zurbriggen,
+2020).{[}Kat: Is the relationship between sexism and objectification
+really this recent of a finding? Or was it just replicated recently?{]}
 Empirical evidence illustrates how women continue to be objects of
@@
 
-Also, future experiments or longitudinal studies should explore the
-external validity of the notions of self-objectification and how the
+Future experiments or longitudinal studies should explore the external
+validity of the notions of self-objectification and how the
 operationalization of self-objectification may be improved.
@@
 Puvia and Vaes (2013) alternative model. TSO -\textgreater{} SOO,
-mediated by SSO.
+mediated by SSO. \enquote{Found that women's motivation to look
+attractive (for men) and internalize sociocultural beauty standards were
+positively linked with the dehumanization of sexually objectified female
+targets.} Tis relationship was mediated by their own level of
+self-objectification.''
 
@@
 
-Regardless, the results from the current analysis highlight how subtle
-forms of sexist discrimination operate to inform prevention and
-intervention efforts in both clinical and educational contexts. These
-results are quite useful for promoting mental health and within early
-action programs for girls and young women, where scholars and
-practitioners might provide the tools necessary to circumvent or
-mitigate negative effects on self-objectification, and combat such
-experiences.
+The results from the current analysis highlight how subtle forms of
+sexist discrimination operate, and provide valuable insight into
+prevention and intervention efforts in both clinical and educational
+contexts. These results are quite useful for promoting mental health,
+the creation and maintence of early action programs for girls and young
+women, and for scholars and practitioners to work intentially to provide
+the tools necessary to circumvent or mitigate negative effects on
+self-objectification to combat such experiences.
 
@@
 The results of this study demonstrate the complex and ambivalent nature
-of female sexual objectification and additionally highlight the
-psychological and social consequences of such objectification processes
-on women's social relationships and well-being. We did not find a
-significant effect between actor SSO and felt authenticity in the
-interaction, which suggests that there is not sufficient evidence to
-support the claim that partner objectification is the cause for the
-diverse range of negative effects related to interaction inauthenticity.
+of sexual objectification and additionally highlight the psychological
+and social consequences of such objectification processes on women's
+social relationships and well-being. We did not find a significant
+effect between actor SSO and felt authenticity in the interaction, which
+suggests that there is not sufficient evidence to support the claim that
+partner objectification is the cause for the diverse range of negative
+effects related to interaction inauthenticity. (Move to here: Perhaps
+women could be amplifying each others' self-objectification as they get
+ready to go out for the night, \emph{before} the theoretical encounters
+with men outlined in Gervais et al., 2020 occur.)
 
@@
 
-\hypertarget{ref-R-Matrix}{}
-Bates, D., \& Maechler, M. (2017). \emph{Matrix: Sparse and dense matrix
-classes and methods}. Retrieved from
-\url{https://CRAN.R-project.org/package=Matrix}
-
 \hypertarget{ref-berger1972}{}
@@
 Review}, 241--255.
-
-\hypertarget{ref-R-lpSolve}{}
-Berkelaar, M., \& others. (2015). \emph{LpSolve: Interface to
-'lp\_solve' v. 5.5 to solve linear/integer programs}. Retrieved from
-\url{https://CRAN.R-project.org/package=lpSolve}
 
@@
 
-\hypertarget{ref-R-xtable}{}
-Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J.
-(2019). \emph{Xtable: Export tables to latex or html}. Retrieved from
-\url{https://CRAN.R-project.org/package=xtable}
-
 \hypertarget{ref-deaux1987putting}{}
@@
 
-\hypertarget{ref-R-irr}{}
-Gamer, M., Lemon, J., \&
-\textless{}puspendra.pusp22@gmail.com\textgreater{}, I. F. P. S. (2012).
-\emph{Irr: Various coefficients of interrater reliability and
-agreement}. Retrieved from \url{https://CRAN.R-project.org/package=irr}
-
 \hypertarget{ref-garcia2016objectification}{}
@@
 
-\hypertarget{ref-R-purrr}{}
-Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
-tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
-
 \hypertarget{ref-hill2008examining}{}
@@
 
-\hypertarget{ref-R-kutils}{}
-Johnson, P., Kite, B., \& Redmon, C. (2019). \emph{Kutils: Project
-management tools}. Retrieved from
-\url{https://CRAN.R-project.org/package=kutils}
-
 \hypertarget{ref-jongenelis2014}{}
@@
 \emph{42}(2), 136--150.
-
-\hypertarget{ref-R-ggformula}{}
-Kaplan, D., \& Pruim, R. (2017). \emph{Ggformula: Formula interface to
-the grammar of graphics}. Retrieved from
-\url{https://CRAN.R-project.org/package=ggformula}
 
@@
 
-\hypertarget{ref-R-tibble}{}
-Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
-Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+\hypertarget{ref-nadal2012effects}{}
+Nadal, K. L., \& Haynes, K. (2012). The effects of sexism, gender
+microaggressions, and other forms of discrimination on women's mental
+health and development.
 
@@
 129--139.
-
-\hypertarget{ref-R-mosaic}{}
-Pruim, R., Kaplan, D. T., \& Horton, N. J. (2017). The mosaic package:
-Helping students to 'think with data' using r. \emph{The R Journal},
-\emph{9}(1), 77--102. Retrieved from
-\url{https://journal.r-project.org/archive/2017/RJ-2017-024/index.html}
-
-\hypertarget{ref-R-mosaicData}{}
-Pruim, R., Kaplan, D., \& Horton, N. (2016). \emph{MosaicData: Project
-mosaic data sets}. Retrieved from
-\url{https://CRAN.R-project.org/package=mosaicData}
 
@@
 
+\hypertarget{ref-richeson2003prejudice}{}
+Richeson, J. A., \& Shelton, J. N. (2003). When prejudice does not pay:
+Effects of interracial contact on executive function.
+\emph{Psychological Science}, \emph{14}(3), 287--290.
+
+\hypertarget{ref-riemer2020self}{}
+Riemer, A. R., Sáez, G., Brock, R., \& Gervais, S. J. (2020).
+Self-fulfilling objectification in relationships: The effects of men's
+objectifying expectations on women's self-objectification during
+conflict in romantic relationships. \emph{Self and Identity}, 1--7.
+
 \hypertarget{ref-robertsfredrickson}{}
@@
 
-\hypertarget{ref-R-lavaan}{}
-Rosseel, Y. (2012). lavaan: An R package for structural equation
-modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36.
-Retrieved from \url{http://www.jstatsoft.org/v48/i02/}
+\hypertarget{ref-rollero2016bringing}{}
+Rollero, C. (2016). Bringing objectification into social relationships
+research: Is self-objectification harmful for authenticity?
 
@@
 
-\hypertarget{ref-R-lattice}{}
-Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with
-r}. New York: Springer. Retrieved from
-\url{http://lmdvr.r-forge.r-project.org}
+\hypertarget{ref-shelton2005expecting}{}
+Shelton, J. N., Richeson, J. A., \& Salvatore, J. (2005). Expecting to
+be the target of prejudice: Implications for interethnic interactions.
+\emph{Personality and Social Psychology Bulletin}, \emph{31}(9),
+1189--1202.
 
@@
 
-\hypertarget{ref-R-ggplot2}{}
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
-Springer-Verlag New York. Retrieved from
-\url{https://ggplot2.tidyverse.org}
-
 \hypertarget{ref-R-tidyverse}{}
@@
 \url{https://CRAN.R-project.org/package=tidyverse}
-
-\hypertarget{ref-R-forcats}{}
-Wickham, H. (2018). \emph{Forcats: Tools for working with categorical
-variables (factors)}. Retrieved from
-\url{https://CRAN.R-project.org/package=forcats}
-
-\hypertarget{ref-R-stringr}{}
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for
-common string operations}. Retrieved from
-\url{https://CRAN.R-project.org/package=stringr}
-
-\hypertarget{ref-R-usethis}{}
-Wickham, H., \& Bryan, J. (2018). \emph{Usethis: Automate package and
-project setup}. Retrieved from
-\url{https://CRAN.R-project.org/package=usethis}
-
-\hypertarget{ref-R-tidyr}{}
-Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Easily tidy data with
-'spread()' and 'gather()' functions}. Retrieved from
-\url{https://CRAN.R-project.org/package=tidyr}
-
-\hypertarget{ref-R-haven}{}
-Wickham, H., \& Miller, E. (2019). \emph{Haven: Import and export
-'spss', 'stata' and 'sas' files}. Retrieved from
-\url{https://CRAN.R-project.org/package=haven}
-
-\hypertarget{ref-R-dplyr}{}
-Wickham, H., François, R., Henry, L., \& Müller, K. (2018). \emph{Dplyr:
-A grammar of data manipulation}. Retrieved from
-\url{https://CRAN.R-project.org/package=dplyr}
-
-\hypertarget{ref-R-devtools}{}
-Wickham, H., Hester, J., \& Chang, W. (2018). \emph{Devtools: Tools to
-make developing r packages easier}. Retrieved from
-\url{https://CRAN.R-project.org/package=devtools}
-
-\hypertarget{ref-R-readr}{}
-Wickham, H., Hester, J., \& Francois, R. (2017). \emph{Readr: Read
-rectangular text data}. Retrieved from
-\url{https://CRAN.R-project.org/package=readr}
 
@@
 
+\hypertarget{ref-R-rmarkdown}{}
+Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The
+definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved
+from \url{https://bookdown.org/yihui/rmarkdown}
+
 \hypertarget{ref-yilmaz2019whose}{}

### 2020-09-08 Final_Manuscript.Rmd
re-knitted word and pdf
intro edits

@@
   Empirical evidence has only found links between objectification, self-objectification, and negative outcomes for women within interpersonal interactions between male-female pairs.
-The purpose of the present study was to extend past research and consider the relationships between such valuable phenomena and their effects on authenticity within interactions between female pairs.
+The purpose of the present study was to extend past research and consider the relationships between objectification and self-objectification within interactions between female pairs.
 Women were brought into the laboratory and interacted in same-sex dyads.
-Dyadic analysis was utilized to detect whether partners’ objectification of each other affected state self-objectification, and the resulting feelings of comfort and authenticity during the interaction.
-After the interaction, participants completed a questionnaire which measured many constructs including cognitive performance, career aspirations, and relationship agency.
-Results revealed no significant relationship between self-objectification and authenticity.
+Dyadic analysis was utilized to detect whether partners’ objectification of each other affected state self-objectification, as well as the resulting feelings of comfort and authenticity during the interaction.
+After the interaction, participants completed a questionnaire measuring, among other things, cognitive performance, career aspirations, and relationship agency.
+Results revealed a significant positive effect of being objectified by a female partner on women's self-objectification.
+There was no significant relationship between self-objectification and authenticity.
 Further, although there were significantly negative effects on career aspirations and relationship agency resulting from a lack of relationship authenticity, there was no evidence that this is due to feelings of sexual objectification.
-The significant partner effect of objectification on actor self-objectification suggests that women being objectified by other women still results in feelings of self-objectification, and such research has powerful implications for the ways that women interact in both sexual and non-sexual settings.
-AUTHOR NOTE: mention Clark trigram coders Hannah et al.
+The significant partner effect of objectification on actor self-objectification suggests that women being objectified by other women may result in feelings of self-objectification, and such research has powerful implications for the ways that women interact in both sexual and non-sexual settings.
 
@@
 @robertsfredrickson Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
-The negative effects of this interpersonal objectification might be the strongest when it is a man doing the objectifying [@gervais2011you], but what are the consequences when a woman objectifies another woman in an interaction?
+The negative effects of this interpersonal objectification are theorized be the strongest when it is a man doing the objectifying [@gervais2011you], but what are the consequences when a woman objectifies another woman in an interaction?
 Psychological researchers studying the sexual objectification of women, have in recent years explored the interpersonal process of the objectification, finding evidence for self-objectification in the target as a proximal consequence [@garcia2016objectification, @strelan2018birds, @riemer2020self].
@@
 ##Women Objectifying Women
-@harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women participants (although men scored higher than women on a measure of belief that objectification of women is natural for men).
+@harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women.
 Additionally, @strelan2005women found that the more women self-objectify, the more they objectify other women.
@@
 
-[Asha comment on next paragraph: Hill and Fischer (2008) assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women, and found that women may be socialized not only to see themselves as objects, but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction
-
-Could this sentence be written like:
-
-Though, when Hill and Fischer(2008) assessed women’s experiences of objectification from men independently from that of women, they found that women are likely to be socialized to not only to see themselves s objects, but potentially see other women as objects as well.
-This process ,however, was not confirmed to occur during an interpersonal interaction.]
-
 Past research has focused on men’s objectifying behaviors, with little attention paid to the role that women may also play in objectifying other women.
-@hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction.
+@hill2008examining assessed women’s experiences of objectification from men independently from women’s experiences of objectification from other women.
+They found that women may be socialized not only to see themselves as objects, but perhaps to see other women as objects as well.
+This process, however, was not comfirmed to occur during an actual interpersonal interaction.
 @loughnan2015exploring found that women objectify other women to a greater extent than they objectify men.
 Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the proximal effects of this objectification might be.
-We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this higher level of objectification might be a detrimental combination.
+We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this woman to woman objectification might have detrimental outcomes.
 
 ##Interpersonal Objectification
-Studies have shown that within social encounters women are gazed at more than men [@briton1995], and often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
-Moreover, perhaps the most adverse effect is that it socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
+Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and are likely to internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
+Moreover, perhaps the most adverse effect is that being objectified socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
 @gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
-What is clear from @gervais2020social is that we know little about women-on-women interpersonal objectification.
+What is clear from @gervais2020social's review is that we know little about women-on-women interpersonal objectification.
 Could there also be negative consequences of this type of interpersonal objectification?
-Perhaps women could be amplifying each others' state self-objectification as they get ready to go out for the night [EDIT??], *before* the theoretical encounters with men organized in the SIMO occur.
-In this way, women's rituals of getting ready together might place even women with low TSO in a higher SSO group.
-[Kat: This has me thinking about the difference between objectification in a romantic setting (which was the setting created in the initial experiment) vs objectification in a platonic setting/between friends.
-Might be useful to discuss this difference, or just have a sentence here that clarifies objectification can occur within non-sexual settings] [Asha: I think this is a great way to illustrate the potential experience but when I read it I was kind of like “wait, when did we talk about women going out?”]
 
@@
 An important caveat to this literature is that it is only about heterosexual relationships.
-A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor].
+A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
 Both romantic relationships and stranger encounters have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
@@
 Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
-On the one hand, there is ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but on the other hand, women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men].
+On the one hand, the ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but on the other hand, women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men].
 When they do it, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
@@
 ##Interpersonal Objectification and Authenticity
-There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor].
+There is some evidence that reduced authenticity is a consequence of self-objectification [@garcia2016objectification; @teran2020relational].
 This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop; @nadal2012effects].
@@
 Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, specifically, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
-A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].
+A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; @teran2020relational].
 
@@
 Most importantly, we predicted that being objectified by one’s interaction partner would lead to self-objectification.
-We also expected, in line with @garcia2016objectification, that TSO would moderate this relationship, amplifying the positive assocaition between being objectified and SSO for women higher in TSO.
+We also expected that TSO would moderate this relationship, amplifying the positive assocaition between being objectified and SSO for women higher in TSO.
 We hypothesized that SSO would, in turn, lead to feelings of inauthenticity [although there is ample support against this prediction from the identity threat within intergroup interactions literature; @rollero2016bringing].
@@
 Here we would like to note that @puvia2013being would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (more precisely, to dehumanize a sexualized woman).
-In addition, @strelan2005women and @harsey2020men would predict the TSO to other-objectification link, further theorezing that this relationships is mediated by the woman's own state self-objectification (SSO).
+In addition, @strelan2005women and @harsey2020men would predict the TSO to other-objectification link, further theorizing that this relationships is mediated by the woman's own state self-objectification (SSO).
 This limited, but extant, set of literature on woman-woman objectification points to a possible alternative model from the model hypothesized in the current study.
@@
 We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and strengthen the potential for objectification that would normally be low in the context of a psychology laboratory.
-Recall that, past research has found that women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; CITE]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.
+Recall that, past research has found that heterosexual women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; @puvia2013being]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.
 
@@
 
-##Combined Samples
+##Participants
 
@@
 
-Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study.
+Data from two different, but demographically equivalent, higher education institutions in the Northeast United States were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study.
 In the measures section that follows we refer to them as Sample 1 and Sample 2.
-Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.
-Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US.
-More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college.
-Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
+Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from institutions in the Northeast of the United States participated in this study.
+Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college.
+More specifically, twelve of the pairs were students at a co-ed liberal arts college, while the remaining twenty pairs attended a women’s liberal arts college.
+[Footnote: Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
 Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
 Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
-For consistency, we limited participant data to same sex female pairs at the two colleges.
+For consistency, we limited participant data to same sex female pairs at the two colleges.]
 
@@
 Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables.
-This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; PWQ paper I reviewed].
+This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; @teran2020relational].
 Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification; @tolman2006looking], we again find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current partner.
@@
 
+Objectification among platonic friends: Perhaps women could be amplifying each others' state self-objectification *before* the theoretical encounters with men organized in the SIMO occur.
+In this way, women's rituals of getting ready together might place even women with low TSO in a higher SSO group.
+
 ###Sexism and Sexual Discrimination
@@
 We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity.
-[Move to here: Perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men outlined in @gervais2020social occur.]
 

### 2020-09-09 Final_Manuscript.Rmd
edits to participants section and analysis strategy

@@
 
+These hypotheses are considered exploratory, given the lack of prior research theorizing about these linkages.
+
 Here we would like to note that @puvia2013being would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (more precisely, to dehumanize a sexualized woman).
@@
 
-Data from two different, but demographically equivalent, higher education institutions in the Northeast United States were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study.
+Data from two demographically equivalent higher education institutions in the Northeast United States were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study.
 In the measures section that follows we refer to them as Sample 1 and Sample 2.
-Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from institutions in the Northeast of the United States participated in this study.
+Thirty-two previously unacquainted self-identifying female dyads (64 total participants) from institutions in the Northeast of the United States participated in this study.
 Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college.
@@
 Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
-For consistency, we limited participant data to same sex female pairs at the two colleges.]
+For consistency, we limited participant data to same sex female pairs at the two colleges.] All results presented below are from models including sample as a control variable.
 
@@
 
-Due to these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined.
-These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
+The participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`).
 The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race.
@@
 All questions were rated on a scale from 1 (not at all) to 7 (constantly).
-Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2).
+Objectification was measured by taking the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2).
 A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
@@
 
-```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
-include_graphics("2016_figure.jpg")
+```{r theorfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
+include_graphics("theor_figure.jpg")
 ```
-This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
-See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study.
-We investigated how the central effects found in the previous study relate to interactions between two women.
-Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction.
-In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification.
-Further, we will investigate the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.
-[Asha: This section feels like a mixture of explaining what the study was intended to investigate as wel as future directions.
-Is that the point, or can this be organized better?]
 
-While @garcia2016objectification used dyadic path analysis, the current study used multilevel modeling for our dyadic analyses.
-Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation].
-One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural].
-Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models.
+This study sought to detect whether partners’ objectification of one another affected state self-objectification (SSO).
+Specifically, we were interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction.
+In addition, we also tested if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification.
+Further, we investigated the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.
+
+While past studies investigating objectification in interactions used dyadic path analysis [@garcia2016objectification], the current study used multilevel modeling proceedures.
+Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs), as we have here [@ledermann2017analyzing; @garcia2015moderation].
+One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means), but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural].
+Further, @olsen2006structural details how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models.
 The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation patterns.
@@
 
-Testing the @garcia2016objectification model on the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approach for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:2016figure)).
+Testing our hypotheses in the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approach for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:theorfigure)).
 Thus, we ran five APIM's to test all the hypothesized relationships.
@@
 The APIM includes effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$).
-Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
-Recall that the indistinguishable nature of the dyads in the current study led us to choose the MLM approach over SEM.
+The current study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
 These analyses are considered exploratory, given the lack of prior research theorizing about these linkages.
-
-Before moving to the main analyses, we discuss statistical equivalence tests that provide support for combining Sample 1 and Sample 2 in one analysis sample.
-The online supplemental material contains the main analyses separated by samples.
-All results presented below are from models including sample as a control variable.
 
@@
 -->
-
-### Combining Samples
-```{r}
-##Correlations
-round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Smith"), 
-                 a2pSOO_A, a2pSOO_P, TSO_A,
-                 howbody_avg_A,
-                 authenticity_A, 
-                 trigram_score_A, careerasp_A, relag_A))$r, 3)
-
-round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Clark"), 
-                 a2pSOO_A, a2pSOO_P, TSO_A, 
-                 howbody_avg_A,
-                 authenticity_A, 
-                 trigram_score_A, careerasp_A, relag_A))$r, 3)
-```
-The correlations between study variables is similar across samples.
-The reliabilities for the study scales were also equivalent.
-(Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS.
 

### 2020-09-09 Final_Manuscript.tex
re-knit paper

@@
 present study was to extend past research and consider the relationships
-between such valuable phenomena and their effects on authenticity within
-interactions between female pairs. Women were brought into the
-laboratory and interacted in same-sex dyads. Dyadic analysis was
-utilized to detect whether partners' objectification of each other
-affected state self-objectification, and the resulting feelings of
-comfort and authenticity during the interaction. After the interaction,
-participants completed a questionnaire which measured many constructs
-including cognitive performance, career aspirations, and relationship
-agency. Results revealed no significant relationship between
-self-objectification and authenticity. Further, although there were
-significantly negative effects on career aspirations and relationship
-agency resulting from a lack of relationship authenticity, there was no
-evidence that this is due to feelings of sexual objectification. The
-significant partner effect of objectification on actor
-self-objectification suggests that women being objectified by other
-women still results in feelings of self-objectification, and such
-research has powerful implications for the ways that women interact in
-both sexual and non-sexual settings. AUTHOR NOTE: mention Clark trigram
-coders Hannah et al.
+between objectification and self-objectification within interactions
+between female pairs. Women were brought into the laboratory and
+interacted in same-sex dyads. Dyadic analysis was utilized to detect
+whether partners' objectification of each other affected state
+self-objectification, as well as the resulting feelings of comfort and
+authenticity during the interaction. After the interaction, participants
+completed a questionnaire measuring, among other things, cognitive
+performance, career aspirations, and relationship agency. Results
+revealed a significant positive effect of being objectified by a female
+partner on women's self-objectification. There was no significant
+relationship between self-objectification and authenticity. Further,
+although there were significantly negative effects on career aspirations
+and relationship agency resulting from a lack of relationship
+authenticity, there was no evidence that this is due to feelings of
+sexual objectification. The significant partner effect of
+objectification on actor self-objectification suggests that women being
+objectified by other women may result in feelings of
+self-objectification, and such research has powerful implications for
+the ways that women interact in both sexual and non-sexual settings.
 
@@
 objectified in actual interpersonal encounters. The negative effects of
-this interpersonal objectification might be the strongest when it is a
-man doing the objectifying (Gervais, Vescio, \& Allen, 2011), but what
-are the consequences when a woman objectifies another woman in an
-interaction? Psychological researchers studying the sexual
+this interpersonal objectification are theorized be the strongest when
+it is a man doing the objectifying (Gervais, Vescio, \& Allen, 2011),
+but what are the consequences when a woman objectifies another woman in
+an interaction? Psychological researchers studying the sexual
 objectification of women, have in recent years explored the
@@
 Harsey and Zurbriggen (2020) found that self-objectification was related
-to the objectification of women to a similar degree for men and women
-participants (although men scored higher than women on a measure of
-belief that objectification of women is natural for men). Additionally,
-Strelan and Hargreaves (2005) found that the more women self-objectify,
-the more they objectify other women. Could the process work in the other
-direction as well, that is, could objectification by a woman produce
-self-objectification, in a similar manner to mixed-gender interactions?
-
-{[}Asha comment on next paragraph: Hill and Fischer (2008) assessed
-women's experiences of objectification from men separately from women's
-experiences of objectification from women, and found that women may be
-socialized not only to see themselves as objects, but perhaps to see
-other women as objects as well, although this process was not comfirmed
-to occur during an actual interpersonal interaction
-
-Could this sentence be written like:
-
-Though, when Hill and Fischer(2008) assessed women's experiences of
-objectification from men independently from that of women, they found
-that women are likely to be socialized to not only to see themselves s
-objects, but potentially see other women as objects as well. This
-process ,however, was not confirmed to occur during an interpersonal
-interaction.{]}
+to the objectification of women to a similar degree for men and women.
+Additionally, Strelan and Hargreaves (2005) found that the more women
+self-objectify, the more they objectify other women. Could the process
+work in the other direction as well, that is, could objectification by a
+woman produce self-objectification, in a similar manner to mixed-gender
+interactions?
 
@@
 other women. Hill and Fischer (2008) assessed women's experiences of
-objectification from men separately from women's experiences of
-objectification from women and found that women may be socialized not
-only to see themselves as objects but perhaps to see other women as
-objects as well, although this process was not comfirmed to occur during
-an actual interpersonal interaction. Loughnan et al. (2015a) found that
-women objectify other women to a greater extent than they objectify men.
-Women have also been found to objectify (dehumanized) sexualized targets
-presented as images (Puvia \& Vaes, 2013), but very little is known
-about interpersonal sexual objectification among women and what the
-proximal effects of this objectification might be. We do know that
-objectification has more adverse consequences for women than men
-(Gervais et al., 2011; Moradi \& Huang, 2008; Saguy, Quinn, F Dovidio,
-\& Pratto, 2010), however, if women objectify other women, perhaps even
-to a stronger degree than they objectify men, this higher level of
-objectification might be a detrimental combination.
+objectification from men independently from women's experiences of
+objectification from other women. They found that women may be
+socialized not only to see themselves as objects, but perhaps to see
+other women as objects as well. This process, however, was not comfirmed
+to occur during an actual interpersonal interaction. Loughnan et al.
+(2015a) found that women objectify other women to a greater extent than
+they objectify men. Women have also been found to objectify
+(dehumanized) sexualized targets presented as images (Puvia \& Vaes,
+2013), but very little is known about interpersonal sexual
+objectification among women and what the proximal effects of this
+objectification might be. We do know that objectification has more
+adverse consequences for women than men (Gervais et al., 2011; Moradi \&
+Huang, 2008; Saguy, Quinn, F Dovidio, \& Pratto, 2010), however, if
+women objectify other women, perhaps even to a stronger degree than they
+objectify men, this woman to woman objectification might have
+detrimental outcomes.
 
@@
 Studies have shown that within social encounters women are gazed at more
-than men (Briton \& Hall, 1995), and often times feel \enquote{looked
-at} within interpersonal interactions (Argyle \& Williams, 1969;
-Miles-McLean et al., 2015), and will more than likely internalize the
+than men (Briton \& Hall, 1995), often times feel \enquote{looked at}
+within interpersonal interactions (Argyle \& Williams, 1969;
+Miles-McLean et al., 2015), and are likely to internalize the
 objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
-1979). Moreover, perhaps the most adverse effect is that it socializes
-girls and women to treat themselves as objects to be looked at and
-evaluated (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; B. L.
-Fredrickson et al., 1998). Gervais et al. (2020) recently reviewed the
-research on interpersonal objectification and organized our current
-theoretical understanding of this process in the Social Interaction
-Model of Objectification (SIMO). What is clear from Gervais et al.
-(2020) is that we know little about women-on-women interpersonal
-objectification. Could there also be negative consequences of this type
-of interpersonal objectification? Perhaps women could be amplifying each
-others' state self-objectification as they get ready to go out for the
-night {[}EDIT??{]}, \emph{before} the theoretical encounters with men
-organized in the SIMO occur. In this way, women's rituals of getting
-ready together might place even women with low TSO in a higher SSO
-group. {[}Kat: This has me thinking about the difference between
-objectification in a romantic setting (which was the setting created in
-the initial experiment) vs objectification in a platonic setting/between
-friends. Might be useful to discuss this difference, or just have a
-sentence here that clarifies objectification can occur within non-sexual
-settings{]} {[}Asha: I think this is a great way to illustrate the
-potential experience but when I read it I was kind of like
-\enquote{wait, when did we talk about women going out?}{]}
+1979). Moreover, perhaps the most adverse effect is that being
+objectified socializes girls and women to treat themselves as objects to
+be looked at and evaluated (Bartky, 1990; Berger, Cohen, \& Zelditch Jr,
+1972; B. L. Fredrickson et al., 1998). Gervais et al. (2020) recently
+reviewed the research on interpersonal objectification and organized our
+current theoretical understanding of this process in the Social
+Interaction Model of Objectification (SIMO). What is clear from Gervais
+et al. (2020)'s review is that we know little about women-on-women
+interpersonal objectification. Could there also be negative consequences
+of this type of interpersonal objectification?
 
@@
 of self-objectification on the reduction of relationship building skills
-in general (including same-sex friendships) {[}CITE PWQ paper I
-reviewed, Yoder editor{]}. Both romantic relationships and stranger
-encounters have been studied in the context of objectification, but
-neither of these literatures have investigated specifically same-gender
-relationships.
+in general (including same-sex friendships) (Terán, Jiao, \& Aubrey,
+2020). Both romantic relationships and stranger encounters have been
+studied in the context of objectification, but neither of these
+literatures have investigated specifically same-gender relationships.
 
@@
 interactions associated with the same negative process as that
-experienced in same-gender interactions? On the one hand, there is ample
+experienced in same-gender interactions? On the one hand, the ample
 research demonstrating that the male gaze has a particularly detrimental
@@
 There is some evidence that reduced authenticity is a consequence of
-self-objectification in the moment {[}Garcia et al. (2016); again CITE
-PWQ paper I reviewed, Yoder editor{]}. This link has been justified by
-the literature on stigmatized-stigmatizer interactions (M. R. Hebl \&
-Dovidio, 2005; Richeson \& Shelton, 2003; Shelton, Richeson, \&
-Salvatore, 2005), viewing the experience of being objectified in an
-interaction as an identity threat situation (Miles-McLean et al., 2015;
-Nadal \& Haynes, 2012). Further, empirical evidence reveals that
-objectification manifests through inauthenticity in romantic
-relationships (Brunell et al., 2010), adverse attitudes in regard to
-career aspirations, and a decrease in concentration and impairment in
-female cognitive performance (Kahalon, Shnabel, \& Becker, 2018; D. M.
-Quinn, Chaudoir, \& Kallen, 2011). When a woman is objectified by a man,
-and subsequently experiences self-objectification, the intergroup nature
-of this encounter might trigger identity threat. Thus, perhaps there are
-fewer negative consequences when a woman is objectified by another
-woman, specifically, woman-woman interpersonal objectification processes
-might diverge from mix-gender interpersonal objectification processes
-precisely because they are not intergroup interactions (at least with
-respect to gender identity). A woman objectified by another woman may
-not be having the same negative consequences that cascade from
-situations that trigger group-based identity threat (Deaux \& Major,
-1987; Dovidio, Hebl, Richeson, \& Shelton, 2006; M. R. Hebl \& Dovidio,
-2005), but feeling like a body, rather than a full human, in any
-interaction (intergroup or ingroup) may be enough to reduce women's
-feelings of authenticity and social competence, regardless of the gender
-of the objectifyer {[}Tolman, Impett, Tracy, and Michael (2006); PWQ
-paper I reviewed, Yoder editor{]}.
+self-objectification (Garcia et al., 2016; Terán et al., 2020). This
+link has been justified by the literature on stigmatized-stigmatizer
+interactions (M. R. Hebl \& Dovidio, 2005; Richeson \& Shelton, 2003;
+Shelton, Richeson, \& Salvatore, 2005), viewing the experience of being
+objectified in an interaction as an identity threat situation
+(Miles-McLean et al., 2015; Nadal \& Haynes, 2012). Further, empirical
+evidence reveals that objectification manifests through inauthenticity
+in romantic relationships (Brunell et al., 2010), adverse attitudes in
+regard to career aspirations, and a decrease in concentration and
+impairment in female cognitive performance (Kahalon, Shnabel, \& Becker,
+2018; D. M. Quinn, Chaudoir, \& Kallen, 2011). When a woman is
+objectified by a man, and subsequently experiences self-objectification,
+the intergroup nature of this encounter might trigger identity threat.
+Thus, perhaps there are fewer negative consequences when a woman is
+objectified by another woman, specifically, woman-woman interpersonal
+objectification processes might diverge from mix-gender interpersonal
+objectification processes precisely because they are not intergroup
+interactions (at least with respect to gender identity). A woman
+objectified by another woman may not be having the same negative
+consequences that cascade from situations that trigger group-based
+identity threat (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \&
+Shelton, 2006; M. R. Hebl \& Dovidio, 2005), but feeling like a body,
+rather than a full human, in any interaction (intergroup or ingroup) may
+be enough to reduce women's feelings of authenticity and social
+competence, regardless of the gender of the objectifyer (Terán et al.,
+2020; Tolman, Impett, Tracy, \& Michael, 2006).
 
@@
 importantly, we predicted that being objectified by one's interaction
-partner would lead to self-objectification. We also expected, in line
-with Garcia et al. (2016), that TSO would moderate this relationship,
-amplifying the positive assocaition between being objectified and SSO
-for women higher in TSO. We hypothesized that SSO would, in turn, lead
-to feelings of inauthenticity (although there is ample support against
-this prediction from the identity threat within intergroup interactions
-literature; Rollero, 2016). Further, we hypothesized that these feelings
-of inauthencity would then be associated with reduced feelings of agency
-in romantic relationships, reduced career aspiration, and reduced
-cognitive performance. In summary, we expected to find a positive
-relationship between other-objectification by one's partner and state
+partner would lead to self-objectification. We also expected that TSO
+would moderate this relationship, amplifying the positive assocaition
+between being objectified and SSO for women higher in TSO. We
+hypothesized that SSO would, in turn, lead to feelings of inauthenticity
+(although there is ample support against this prediction from the
+identity threat within intergroup interactions literature; Rollero,
+2016). Further, we hypothesized that these feelings of inauthencity
+would then be associated with reduced feelings of agency in romantic
+relationships, reduced career aspiration, and reduced cognitive
+performance. In summary, we expected to find a positive relationship
+between other-objectification by one's partner and state
 self-objectification. We also expected to find a negative relationship
@@
 performance, relationship agency, and career aspirations.
+
+These hypotheses are considered exploratory, given the lack of prior
+research theorizing about these linkages.
 
@@
 and Zurbriggen (2020) would predict the TSO to other-objectification
-link, further theorezing that this relationships is mediated by the
+link, further theorizing that this relationships is mediated by the
 woman's own state self-objectification (SSO). This limited, but extant,
@@
 of a psychology laboratory. Recall that, past research has found that
-women are indeed able to evaluate other women's potential as romantic
-partners {[}i.e., their sexual attractiveness; CITE{]}---indeed, women
-may be unfortunately quite used to thinking about their own
-\enquote{datability,} and we suspect this this habitual thought pattern
-will translate to their thoughts about other women.
+heterosexual women are indeed able to evaluate other women's potential
+as romantic partners (i.e., their sexual attractiveness; Puvia \& Vaes,
+2013)---indeed, women may be unfortunately quite used to thinking about
+their own \enquote{datability,} and we suspect this this habitual
+thought pattern will translate to their thoughts about other women.
 
@@
 
-\subsection{Combined Samples}\label{combined-samples}
-
-Data from two different, but demographically equivalent, samples were
-combined to create the final analysis sample (\emph{N =} 64) used in
-this study. In the measures section that follows we refer to them as
-Sample 1 and Sample 2. Thirty-two previously unacquainted
-self-identifying female-sex dyads (64 total participants) from two
-liberal arts institutions in the Northeast of the United States
-participated in this study. Sample 1 (\emph{N =} 24) is from a co-ed
-liberal arts college in the northeast US and Sample 2 (\emph{N =} 40) is
-from a women's liberal arts college in the northeast US. More
-specifically, twelve of the pairs, which derived from Sample 1, were
-students at a co-ed liberal arts college, while the remaining twenty
-pairs who came from Sample 2 attended a women's liberal arts college.
+\subsection{Participants}\label{participants}
+
+Data from two demographically equivalent higher education institutions
+in the Northeast United States were combined to create the final
+analysis sample (\emph{N =} 64) used in this study. In the measures
+section that follows we refer to them as Sample 1 and Sample 2.
+Thirty-two previously unacquainted self-identifying female dyads (64
+total participants) from institutions in the Northeast of the United
+States participated in this study. Sample 1 (\emph{N =} 24) is from a
+co-ed liberal arts college and Sample 2 (\emph{N =} 40) is from a
+women's liberal arts college. More specifically, twelve of the pairs
+were students at a co-ed liberal arts college, while the remaining
+twenty pairs attended a women's liberal arts college. {[}Footnote:
 Initially, data was collected from same-sex and mixed-sex dyads that
@@
 formed Sample 2. For consistency, we limited participant data to same
-sex female pairs at the two colleges.
-
-Due to these similarities across samples in regard to correlation
-patterns between significant variables within this study, the two
-datasets were combined. These participants were mostly first-year
-college students, with an average age of 18.85 (SD = 1.04). The sample
-was 48.44\% White/European American, 9.38\% Black/African-American,
-28.12\% Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race.
-There were 8 White/White pairs and 4 same race racial minority pairs,
-for a total of 12 same-race pairs. The remaining 20 were mixed race
-pairs, of which 15 were White/racial minority pairings and 5 were
-cross-racial minority group pairs. 64.06\% of the sample identified as
-heterosexual, and 25\% identified as gay, lesbian or bisexual.
+sex female pairs at the two colleges.{]} All results presented below are
+from models including sample as a control variable.
+
+The participants were mostly first-year college students, with an
+average age of 18.85 (SD = 1.04). The sample was 48.44\% White/European
+American, 9.38\% Black/African-American, 28.12\% Asian/Pacific Islander,
+9.38\% Latinx, and 4.69\% mixed-race. There were 8 White/White pairs and
+4 same race racial minority pairs, for a total of 12 same-race pairs.
+The remaining 20 were mixed race pairs, of which 15 were White/racial
+minority pairings and 5 were cross-racial minority group pairs. 64.06\%
+of the sample identified as heterosexual, and 25\% identified as gay,
+lesbian or bisexual.
 
@@
 scale from 1 (not at all) to 7 (constantly). Objectification was
-measured by getting the difference between the average frequency of
+measured by taking the difference between the average frequency of
 thought about their partner's external traits (\(\alpha\) = 0.79 for
@@
 \begin{figure}
-\includegraphics[width=400px]{2016_figure} \caption{Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads.}\label{fig:2016figure}
+\includegraphics[width=400px]{theor_figure} \caption{Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads.}\label{fig:theorfigure}
 \end{figure}
 
-This study sought to replicate the results of Garcia et al. (2016)'s
-study, done with male-female pairs, which used a dyadic path analysis to
-detect whether partners' objectification of one another affected state
-self-objectification (SSO). See Figure~\ref{fig:2016figure} for the
-results of the analysis from this previous study. We investigated how
-the central effects found in the previous study relate to interactions
-between two women. Specifically, we are interested in testing the
-relationship between state-other objectification and SSO, and how SSO in
-turn, affects feelings of inauthenticity during the interaction. In
-addition, we will also test if the effect of other-objectification in an
-interaction on SSO is only present for those women who are high in trait
-self-objectification, as in Garcia et al. (2016). Further, we will
-investigate the relationships between experiencing interaction
-inauthenticity and relationship agency, career aspirations, and
-cognitive performance. {[}Asha: This section feels like a mixture of
-explaining what the study was intended to investigate as wel as future
-directions. Is that the point, or can this be organized better?{]}
-
-While Garcia et al. (2016) used dyadic path analysis, the current study
-used multilevel modeling for our dyadic analyses. Dyadic analyses for
-distinguishable dyads (e.g., mixed-gender interacting pairs) is more
-natural in Structural Equation Modeling (SEM) than it is for
-indistinguishable dyads (e.g., same-gender interacting pairs) (Garcia,
+This study sought to detect whether partners' objectification of one
+another affected state self-objectification (SSO). Specifically, we were
+interested in testing the relationship between state-other
+objectification and SSO, and how SSO in turn, affects feelings of
+inauthenticity during the interaction. In addition, we also tested if
+the effect of other-objectification in an interaction on SSO is only
+present for those women who are high in trait self-objectification.
+Further, we investigated the relationships between experiencing
+interaction inauthenticity and relationship agency, career aspirations,
+and cognitive performance.
+
+While past studies investigating objectification in interactions used
+dyadic path analysis (Garcia et al., 2016), the current study used
+multilevel modeling proceedures. Dyadic analyses for distinguishable
+dyads (e.g., mixed-gender interacting pairs) is more natural in
+Structural Equation Modeling (SEM) than it is for indistinguishable
+dyads (e.g., same-gender interacting pairs), as we have here (Garcia,
 Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
@@
 many estimates need to be fixed to be equal (i.e., paths, variances,
-covariances, endogenous intercepts, and exogenous means) for
-indistinguishable dyads but these equality constraints should not then
-be considered in the degrees of freedom calculations for fit estimations
-(Olsen \& Kenny, 2006). Further, Olsen and Kenny (2006) detail how a new
-independence model and the corresponding fit measure should be
-re-calculated for indistinguishable dyads models. The current study uses
-dyadic multilevel modeling (MLM) to test all relationships and mediation
-patterns. The online supplementary materials contains analysis using
-SEM. See Ledermann and Kenny (2017) for a more complete discussion of
-the considerations for using SEM versus MLM for dyadic analysis.
-
-Testing the Garcia et al. (2016) model on the current, same-gender,
-sample, involves using the Actor-Partner Independence Model (APIM)
-approach for each outcome variable (i.e., endogenous variable in
-Figure~\ref{fig:2016figure}). Thus, we ran five APIM's to test all the
+covariances, endogenous intercepts, and exogenous means), but these
+equality constraints should not then be considered in the degrees of
+freedom calculations for fit estimations (Olsen \& Kenny, 2006).
+Further, Olsen and Kenny (2006) details how a new independence model and
+the corresponding fit measure should be re-calculated for
+indistinguishable dyads models. The current study uses dyadic multilevel
+modeling (MLM) to test all relationships and mediation patterns. The
+online supplementary materials contains analysis using SEM. See
+Ledermann and Kenny (2017) for a more complete discussion of the
+considerations for using SEM versus MLM for dyadic analysis.
+
+Testing our hypotheses in the current, same-gender, sample, involves
+using the Actor-Partner Independence Model (APIM) approach for each
+outcome variable (i.e., endogenous variable in
+Figure~\ref{fig:theorfigure}). Thus, we ran five APIM's to test all the
 hypothesized relationships. See Figure~\ref{fig:apim} for a basic APIM
@@
 partner's, predictor variables (\(X\)'s) on the one's own outcome
-variable (\(Y\)). Unlike the original Garcia et al. (2016) study, our
-study deals with indistinguishable dyads, meaning the designation of who
-is designated as \enquote{actor} and who is designated as
-\enquote{partner} is arbitrary. Recall that the indistinguishable nature
-of the dyads in the current study led us to choose the MLM approach over
-SEM. These analyses are considered exploratory, given the lack of prior
-research theorizing about these linkages.
-
-Before moving to the main analyses, we discuss statistical equivalence
-tests that provide support for combining Sample 1 and Sample 2 in one
-analysis sample. The online supplemental material contains the main
-analyses separated by samples. All results presented below are from
-models including sample as a control variable.
-
-\subsubsection{Combining Samples}\label{combining-samples}
-
-The correlations between study variables is similar across samples. The
-reliabilities for the study scales were also equivalent. (Note that the
-two samples were two small to conduct formal measurement equivalence
-tests for scales.) There are no statistically significant differences
-between samples in demographics including age, STATS, and ethnicity,
-STATS.
+variable (\(Y\)). The current study deals with indistinguishable dyads,
+meaning the designation of who is designated as \enquote{actor} and who
+is designated as \enquote{partner} is arbitrary. These analyses are
+considered exploratory, given the lack of prior research theorizing
+about these linkages.
 
@@
 relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.
-
-The results were similar for analyses conducted on Sample 1 and Sample 2
-individually. See the online supplemental material for more detail on
-these analyses.
 
@@
 authenticity in interactions is important for healthy relationship
-functioning {[}Garcia et al. (2016); PWQ paper I reviewed{]}. Just as
+functioning (Garcia et al., 2016; Terán et al., 2020). Just as
 authenticity has been found to be important in intergroup interactions
@@
 
+Objectification among platonic friends: Perhaps women could be
+amplifying each others' state self-objectification \emph{before} the
+theoretical encounters with men organized in the SIMO occur. In this
+way, women's rituals of getting ready together might place even women
+with low TSO in a higher SSO group.
+
 \subsubsection{Sexism and Sexual
@@
 partner objectification is the cause for the diverse range of negative
-effects related to interaction inauthenticity. (Move to here: Perhaps
-women could be amplifying each others' self-objectification as they get
-ready to go out for the night, \emph{before} the theoretical encounters
-with men outlined in Gervais et al., 2020 occur.)
+effects related to interaction inauthenticity.
 
@@
 
+\hypertarget{ref-teran2020relational}{}
+Terán, L., Jiao, J., \& Aubrey, J. S. (2020). The relational burden of
+objectification: Exploring how past experiences of interpersonal sexual
+objectification are related to relationship competencies. \emph{Sex
+Roles}, 1--16.
+
 \hypertarget{ref-tolman2006looking}{}

### 2020-09-10 Final_Manuscript.Rmd
re-knit paper
added an example theoreitcal figure updated table 1

@@
 
-corr_cswomen <- clarksmith_women %>%
-  select(TSO_A, authenticity_A, a2pSOO_A, howbody_avg_A, relag_A, trigram_score_A)
+corr_cswomen <-clarksmith_women %>%
+  select(TSO_A, a2pSOO_A, a2pSOO_P, howbody_avg_A, authenticity_A, relag_A, trigram_score_A, careerasp_A)
 
 corr.table <- glrstab(corr_cswomen)
-rownames(corr.table) <- c("Actor's trait self objectification (TSO)", "Actor's authenticity of interaction", "Actor's objectification of partner", "Actor's state self-objectification", "Actor's future relationship agency", "Actor's cognitive performance")
-colnames(corr.table)   <- c("$M$", "$SD$", "1", "2", "3", "4", "5")
+rownames(corr.table) <- c("1.
+Actor's trait self objectification (TSO)", "2.
+Actor's objectification of partner", "3.
+Partner's objectification of the actor", "4.
+Actor's state self-objectification", "5.
+Actor's authenticity of interaction", "6.
+Actor's future relationship agency", "7.
+Actor's cognitive performance", "8.
+Actor's career aspirations")
+colnames(corr.table)   <- c("$M$", "$SD$", "1.", "2.", "3.", "4.", "5.", "6.")
 
-apa_table(corr.table, caption="Correlations among study variables.", escape=FALSE)
+apa_table(corr.table, caption="Correlations and Descriptive Statistics among Study Variables", escape=FALSE)
 ```
 
-```{r descriptives, include=TRUE, echo=FALSE, results='asis'}
-#table 2
+```{r descriptives}
 descriptives_cswomen <- clarksmith_women %>%
@@
 
-rownames(descriptives) <- c("Actor's trait self objectification (TSO)", 
-                            "Actor's authenticity of interaction", 
-                            "Actor's objectification of partner", 
-                            "Actor's state self-objectification", 
-                            "Actor's future relationship agency", 
-                            "Actor's cognitive performance")
+# rownames(descriptives) <- c("Actor's trait self objectification (TSO)", 
+#                             "Actor's authenticity of interaction", 
+#                             "Actor's objectification of partner", 
+#                             "Actor's state self-objectification", 
+#                             "Actor's future relationship agency", 
+#                             "Actor's cognitive performance")
+# 
+# colnames(descriptives) <- c("M", "SD")
 
-colnames(descriptives) <- c("M", "SD")
-
-apa_table(descriptives, caption = "Descriptive Statistics for Study Variables")
+#apa_table(descriptives, caption = "Descriptive Statistics for Study Variables")
 ```
 
-The following measures were collected in the order they are presented following the interaction.
-Correlations appear in Table\ \@ref(tab:corrtable), and descriptive statistics appear in Table\ \@ref(tab:descriptives).
+The following measures were collected in the order they are presented following the interaction. Correlations and descriptive statistics appear in Table\ \@ref(tab:corrtable).
 
@@
 
-As can be seen in Table\ \@ref(tab:descriptives), the mean other-objectification of women by women was *M =* `r descriptives[3,1]` (*SD =* `r descriptives[3,2]`).
+As can be seen in Table\ \@ref(tab:corrtable), the mean other-objectification of women by women was *M =* `r descriptives[3,1]` (*SD =* `r descriptives[3,2]`).
 This corresponds to women objectifying other women to a *greater* extent than women's objectification of men reported in @garcia2016objectification (*M =* -1.68, *SD =* 1.52).
@@
 
-```{r theorfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
-include_graphics("theor_figure.jpg")
+```{r theorfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Theoretical Model from Garcia et al. (2016)."}
+include_graphics("theor_figure.png")
 ```
@@
 
-The results were similar for analyses conducted on Sample 1 and Sample 2 individually. See the online supplemental material for more detail on these analyses.
-
 #Discussion

### 2020-09-10 Final_Manuscript.tex
added an example theoreitcal figure updated table 1

@@
 \begin{threeparttable}
-\caption{\label{tab:corrtable}Correlations among study variables.}
-\begin{tabular}{llllllll}
+\caption{\label{tab:corrtable}Correlations and Descriptive Statistics among Study Variables}
+\begin{tabular}{llllllllll}
 \toprule
- & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5}\\
+ & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1.} & \multicolumn{1}{c}{2.} & \multicolumn{1}{c}{3.} & \multicolumn{1}{c}{4.} & \multicolumn{1}{c}{5.} & \multicolumn{1}{c}{6.} & \multicolumn{1}{c}{NA}\\
 \midrule
-Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  & \\
-Actor's authenticity of interaction & 5.23 & 1.02 & -.02 &  &  &  & \\
-Actor's objectification of partner & -1.58 & 1.21 & .20 & -.07 &  &  & \\
-Actor's state self-objectification & 1.92 & 1.13 & .13 & -.10 & -.09 &  & \\
-Actor's future relationship agency & 4.69 & 0.96 & .04 & .23+ & .09 & -.09 & \\
-Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .11 & .02 & .07\\
+1. Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  &  &  & \\
+2. Actor's objectification of partner & -1.58 & 1.21 & .20 &  &  &  &  &  & \\
+3. Partner's objectification of the actor & -1.58 & 1.21 & .09 & .14 &  &  &  &  & \\
+4. Actor's state self-objectification & 1.92 & 1.13 & .13 & -.09 & .30* &  &  &  & \\
+5. Actor's authenticity of interaction & 5.23 & 1.02 & -.02 & -.07 & .03 & -.10 &  &  & \\
+6. Actor's future relationship agency & 4.69 & 0.96 & .04 & .09 & -.10 & -.09 & .23+ &  & \\
+7. Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .06 & .02 & .11 & .07 & \\
+8. Actor's career aspirations & 3.88 & 0.61 & .05 & -.14 & -.08 & .01 & .33** & .26* & -.07\\
 \bottomrule
@@
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:descriptives}Descriptive Statistics for Study Variables}
-\begin{tabular}{lll}
-\toprule
- & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD}\\
-\midrule
-Actor's trait self objectification (TSO) & -0.35 & 2.64\\
-Actor's authenticity of interaction & 5.23 & 1.02\\
-Actor's objectification of partner & -1.58 & 1.21\\
-Actor's state self-objectification & 1.92 & 1.13\\
-Actor's future relationship agency & 4.69 & 0.96\\
-Actor's cognitive performance & 5.03 & 2.29\\
-\bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
-
 The following measures were collected in the order they are presented
-following the interaction. Correlations appear in
-Table~\ref{tab:corrtable}, and descriptive statistics appear in
-Table~\ref{tab:descriptives}.
+following the interaction. Correlations and descriptive statistics
+appear in Table~\ref{tab:corrtable}.
 
@@
 
-As can be seen in Table~\ref{tab:descriptives}, the mean
+As can be seen in Table~\ref{tab:corrtable}, the mean
 other-objectification of women by women was \emph{M =} -1.58 (\emph{SD
@@
 \begin{figure}
-\includegraphics[width=400px]{theor_figure} \caption{Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads.}\label{fig:theorfigure}
+\includegraphics[width=400px]{theor_figure} \caption{Theoretical Model from Garcia et al. (2016).}\label{fig:theorfigure}
 \end{figure}

### 2020-09-15 Final_Manuscript.Rmd
Some edits here and there

@@
 @robertsfredrickson Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
-The negative effects of this interpersonal objectification are theorized be the strongest when it is a man doing the objectifying [@gervais2011you], but what are the consequences when a woman objectifies another woman in an interaction?
-Psychological researchers studying the sexual objectification of women, have in recent years explored the interpersonal process of the objectification, finding evidence for self-objectification in the target as a proximal consequence [@garcia2016objectification, @strelan2018birds, @riemer2020self].
-For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification reported by their partner.
-They did not include same-gender, woman-woman interacting pairs.
-@gervais2020social have reviewed the literature on interpersonal self-objectification and has organized the process in a theoretical model called the Social Interaction Model of Objectification (SIMO), but this model is currently only relevant for mixed-gender encounters.
-Although there is ample evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], there are currently no studies investigating the process of interpersonal objectification in same-gender interactions.
-Does objectification by a female interaction partner have the same downstream negative consequences as being objectified by a male interaction partner?
-The current dyadic study addresses this omission using interacting pairs where both members identify as women.
+The negative effects of this interpersonal objectification for women are theorized be the strongest when it is a man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction?
+Psychological researchers studying the sexual objectification of women, have in recent years explored the interpersonal process of the objectification, finding evidence for self-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification, @strelan2018birds, @riemer2020self].
+In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO), however this model focuses on mixed-gender encounters.
+Although there is evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], there are currently no studies investigating the process of interpersonal objectification in interactions between women.
+Is objectification by a female interaction partner related to an increase in self-objectification for the woman being objectified?
+Further, does objectification by a woman have the same downstream negative consequences for women as being objectified by a male interaction partner?
+The current study begins to address these questions by investigating interpersonal objectification among interacting pairs where both partners identify as women.
 
@@
 @calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO).
-Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines [@morry2001magazine], or when wearing sexualizing clothing [@fredrickson1998swimsuit].
-This momentary self-objectification is referred to as *state* self-objectification [@bernard2018bodies; @calogero2011; @moradi2008].
-Being objectified by another person may interact TSO to effect experiences of feeling like a body, or state self-objectification [SSO; @garcia2016objectification].
+Furthermore, self-objectification can also be elicited momentarily, for example, when viewing sexualized images in movies and magazines [@morry2001magazine], when trying on sexualizing clothing [@fredrickson1998swimsuit], or during video chat when you believe your interaction partner can only see your body [not face; @saguyetal2010].
+This momentary self-objectification is referred to as *state* self-objectification [SSO; @bernard2018bodies; @calogero2011; @moradi2008] and is characterized by feeling like a body rather than a full self within a particular moment, instance, or context [@robertsfredrickson].
 
-##Women Objectifying Women
-@harsey2020men found that self-objectification was related to the objectification of women to a similar degree for men and women.
-Additionally, @strelan2005women found that the more women self-objectify, the more they objectify other women.
-Could the process work in the other direction as well, that is, could objectification by a woman produce self-objectification, in a similar manner to mixed-gender interactions?
-
-Past research has focused on men’s objectifying behaviors, with little attention paid to the role that women may also play in objectifying other women.
-@hill2008examining assessed women’s experiences of objectification from men independently from women’s experiences of objectification from other women.
-They found that women may be socialized not only to see themselves as objects, but perhaps to see other women as objects as well.
-This process, however, was not comfirmed to occur during an actual interpersonal interaction.
-@loughnan2015exploring found that women objectify other women to a greater extent than they objectify men.
-Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the proximal effects of this objectification might be.
-We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this woman to woman objectification might have detrimental outcomes.
+There is evidence that being objectified by another person during an interaction elicits SSO.
+For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification as reported by their female partner.
+Further, this negative effect of the men's objectification on women's SSO was strongest for women higher in TSO.
+The current study uses this same dyadic paradigm to study same-gender, woman-woman interacting pairs.
 
@@
 Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and are likely to internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
-Moreover, perhaps the most adverse effect is that being objectified socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
+Interpersonal objectification has been found to have negative consequences for women.
+@gervais2011you found that an objectifying gaze by a male interaction partner (confederate) was associated with lower math performance for women, than being objectified by a female interaction partner.
+Moreover, perhaps the most adverse effect of interpersonal objectificaiton is that being objectified socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
 @gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
@@
 Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
-On the one hand, the ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but on the other hand, women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men].
-When they do it, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
+The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and to would be helpful to understand the consequencs of this intragroup objectification for women.
+When women objectify other women, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
 If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that interaction?
 
-##Interpersonal Objectification and Authenticity
 There is some evidence that reduced authenticity is a consequence of self-objectification [@garcia2016objectification; @teran2020relational].
@@
 A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; @teran2020relational].
+
+##Women Objectifying Women
+Past research investigating women objectifying other women has focused on the psychological conditions that led women to objectify women.
+@harsey2020men found that self-objectification was related to the objectification of women to a similar degree for male and female participants.
+Along the same lines, @strelan2005women found that the more women self-objectify, the more they objectify other women.
+Could the process work in the other direction as well, that is, could objectification by a woman produce self-objectification, in a similar manner to objectification by a man?
+@hill2008examining assessed women’s experiences of objectification from men independently from women’s experiences of objectification from other women.
+They found that women may be socialized not only to see themselves as objects, but perhaps to see other women as objects as well.
+This process, however, was not comfirmed to occur during an actual interpersonal interaction.
+@loughnan2015exploring found that women objectify other women to a greater extent than they objectify men.
+Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the proximal effects of this objectification might be.
+We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this woman to woman objectification might have detrimental outcomes.
 
@@
 
-Data from two demographically equivalent higher education institutions in the Northeast United States were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study.
+Data from two demographically similar higher education institutions in the Northeast United States were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study.
 In the measures section that follows we refer to them as Sample 1 and Sample 2.
@@
 Thus, evidence suggests that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also result in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
-[Asha:Or … thus evidence provides support for the claim that women being objectified by another woman result in sso in ways that are not uniquely dissimilar from that of xyz]
+
+MORE ABOUT THIS PARTNER EFFECT
 
@@
 It could be that women's SSO causes them to be objectified by their interaction partner.
-This interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO that relates to being objectified by one's partner.
-However, Objectification Theory [@robertsfredrickson], as well as past experimental studies [@saguyetal2010; CITE], suggest that the causal flow is from other-objectification to SSO.
-Although, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.
+This interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* state self-objectification that relates to being objectified by one's partner.
+However, Objectification Theory [@robertsfredrickson], as well as past experimental studies [@saguyetal2010], suggest that the causal flow is from other-objectification to SSO.
 
@@
 Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes.
-This is somewhat suprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification].
+This is somewhat suprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification; @gervais2011you].
 This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
 There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as harmful as the self-objectification experienced within an interaction with a man.
-As a strong note of caution, it is best not to interpret a null result as evidence of no relationship.
+However, as a strong note of caution, it is best not to interpret a null result as evidence of no relationship.
 
@@
 
-Although we did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency, and authenticity and career aspirations.
+Although the urrent study did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency, and authenticity and career aspirations.
 The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically signficant.
@@
 [Kat: Or a longitudinal study is needed.]
+
+Men-men
 

### 2020-09-17 Final_Manuscript.Rmd
finalizing article

@@
 # Results
-## Data analysis
+## Analysis Strategy
 ```{r create_r-references, warning=FALSE, message=FALSE}
@@
 
-## Analysis Strategy
 ```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
@@
 
-##Main Results
+## Main Results
 ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
@@
 
-#Discussion
-The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women only.
+# Discussion
+The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women.
 Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women is related to state self-objectification in their woman-identified interaction partners.
@@
 This effect extends the equivalent relationship found in mixed-gender interactions to the context of same-gender interactions between women.
-Thus, evidence suggests that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also result in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
-
-MORE ABOUT THIS PARTNER EFFECT
+Thus, evidence suggests that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman is also related to women's SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
 
 As is the case in all correlational studies, we cannot be sure about the causal direction.
-It could be that women's SSO causes them to be objectified by their interaction partner.
-This interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* state self-objectification that relates to being objectified by one's partner.
-However, Objectification Theory [@robertsfredrickson], as well as past experimental studies [@saguyetal2010], suggest that the causal flow is from other-objectification to SSO.
+The model used by the current study asserts that being objectified by a woman causes women to self-objectify, but it could be that women's SSO causes them to be objectified by their interaction partner.
+This latter interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* state self-objectification that relates to being objectified by one's partner.
+Objectification Theory [@robertsfredrickson], as well as some past experimental studies [@saguyetal2010] suggest that at least one direction of the causal flow is from other-objectification to SSO.
+Other studies, especailly those investigating explicitly women objectifying other women [@puvia2013being], have relately found evidence that women's *trait* self-objectification causes women to objectify (dehumanize) other women and this link is mediated by *state* self-objectification.
+It could follow that we tend to objectify other women who objectify us and through a process of TSO causes SSO which in turn causes objectifation of one's partner, which in turn causes one's partner to objectify us.
+The current study does not provide any evidence of this alternative model, however---TSO was not significantly correlated with SSO and actor's objectification was not correlated with partner's objectification.
 
@@
 This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as harmful as the self-objectification experienced within an interaction with a man.
-However, as a strong note of caution, it is best not to interpret a null result as evidence of no relationship.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is qualtatively different, and perhaps not as harmful, as the self-objectification experienced within an interaction with a man.
+However, as a strong note of caution, it is best not to interpret a null result as evidence of no relationship and more research on interpersonal objectification among women is needed.
 
 The lack of evidence for a relationship between SSO and interaction authenticity is surprising and again, should not be interpreted as evidence of no relationship.
-It should be noted that the estimate of this relationship was very small, but in the negative direction, as anticipated.
+It should be noted that the estimate of this relationship was small (close to zero), but in the negative direction.
 If it is the case that there is a smaller (i.e., weaker) connection between women's feelings of SSO and inauthenticity in interactions with other women than in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including inauthenticity as a potential mediating factor.
-Further, gender of the objectifyer/interaction partner could also be added to the SIMO model to help understand the circumstances that require other-objectification and SSO to have negative consequences for women.
+Further, gender of the objectifyer/interaction partner could be added as a moderator of the self-objectificaiton to authenticity process to help understand the circumstances that require other-objectification and SSO to have negative consequences for women.
 
-Although the urrent study did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency, and authenticity and career aspirations.
+Although the current study did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency, and authenticity and career aspirations.
 The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically signficant.
@@
 ###Sample Characteristics
-In addition to being small and combined across two institutions, the sample of the current study was comprised of Western women, being that sexual objectification is most prevalent in this culture [@loughnan2015], and research on objectification conducted outside of Western or Westernized countries is scarce [@moradi2008], although more current work examines objectification from a cross-cultural framework [@loughnan2015, @wollast2020cultural].
+In addition to being relatively small and combined across two institutions, another limitation of the current study is that the sample was comprised of Western women only.
+Being that self-objectification is most prevalent in Western culture [@loughnan2015] research on objectification conducted outside of Western or Westernized countries has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015, @wollast2020cultural].
 Since “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015].
+
 Further, sexualizing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014; @bury2016].
@@
 It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.
-[Kat: Or a longitudinal study is needed.]
-
-Men-men
+Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectificaion are needed [see CITE and CITE for exmaples].
 
@@
 This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships, adding variability.
-[Kat: The only other thing I would add re: sexuality limitations are that we didn’t collect/use sexual orientation, so we couldn’t analyze results by that at all/our samples might have differed there.]
 
@@
 
-###Measurement
-Future experiments or longitudinal studies should explore the external validity of the notions of self-objectification and how the operationalization of self-objectification may be improved.
-
-###Alternative Model
-@puvia2013being alternative model.
-TSO -> SOO, mediated by SSO.
-“Found that women’s motivation to look attractive (for men) and internalize sociocultural beauty standards were positively linked with the dehumanization of sexually objectified female targets.” Tis relationship was mediated by their own level of self-objectification.”
-
-##Clinical Implications
+#Conclusion
 The results from the current analysis highlight how subtle forms of sexist discrimination operate, and provide valuable insight into prevention and intervention efforts in both clinical and educational contexts.
@@
 
-#Conclusion
 The results of this study demonstrate the complex and ambivalent nature of sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.

### 2020-09-17 Final_Manuscript.tex
finalizing article

@@
 objectified in actual interpersonal encounters. The negative effects of
-this interpersonal objectification are theorized be the strongest when
-it is a man doing the objectifying (Gervais, Vescio, \& Allen, 2011),
-but what are the consequences when a woman objectifies another woman in
-an interaction? Psychological researchers studying the sexual
-objectification of women, have in recent years explored the
-interpersonal process of the objectification, finding evidence for
-self-objectification in the target as a proximal consequence (Garcia,
-Earnshaw, \& Quinn, 2016, Strelan and Pagoudis (2018), Riemer, Sáez,
-Brock, and Gervais (2020)). For example, in a face-to-face mixed-gender
-dyadic study, Garcia et al. (2016) found that men's reported
-objectification of their female interaction partner was associated with
-increased self-objectification reported by their partner. They did not
-include same-gender, woman-woman interacting pairs. Gervais, Sáez,
-Riemer, and Klein (2020) have reviewed the literature on interpersonal
-self-objectification and has organized the process in a theoretical
-model called the Social Interaction Model of Objectification (SIMO), but
-this model is currently only relevant for mixed-gender encounters.
-Although there is ample evidence that women objectify other women
-(Loughnan et al., 2015a; Puvia \& Vaes, 2013), there are currently no
-studies investigating the process of interpersonal objectification in
-same-gender interactions. Does objectification by a female interaction
-partner have the same downstream negative consequences as being
-objectified by a male interaction partner? The current dyadic study
-addresses this omission using interacting pairs where both members
-identify as women.
+this interpersonal objectification for women are theorized be the
+strongest when it is a man doing the objectifying (Calogero, 2004; Gay
+\& Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
+consequences when a woman objectifies another woman in an interaction?
+Psychological researchers studying the sexual objectification of women,
+have in recent years explored the interpersonal process of the
+objectification, finding evidence for self-objectification in the target
+as a proximal consequence of being objectified (Garcia, Earnshaw, \&
+Quinn, 2016, Strelan and Pagoudis (2018), Riemer, Sáez, Brock, and
+Gervais (2020)). In a recent review, Gervais, Sáez, Riemer, and Klein
+(2020) organized the extant literature on interpersonal
+self-objectification and proposed a theoretical model called the Social
+Interaction Model of Objectification (SIMO), however this model focuses
+on mixed-gender encounters. Although there is evidence that women
+objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013),
+there are currently no studies investigating the process of
+interpersonal objectification in interactions between women. Is
+objectification by a female interaction partner related to an increase
+in self-objectification for the woman being objectified? Further, does
+objectification by a woman have the same downstream negative
+consequences for women as being objectified by a male interaction
+partner? The current study begins to address these questions by
+investigating interpersonal objectification among interacting pairs
+where both partners identify as women.
 
@@
 conceptualized as a learned trait, or \emph{trait} self-objectification
-(TSO). Furthermore, it can also be elicited momentarily, through the
-media, for example, with sexualized images in movies and magazines
-(Morry \& Staska, 2001), or when wearing sexualizing clothing (B. L.
-Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998). This momentary
-self-objectification is referred to as \emph{state} self-objectification
-(Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \&
-Huang, 2008). Being objectified by another person may interact TSO to
-effect experiences of feeling like a body, or state self-objectification
-(SSO; Garcia et al., 2016).
-
-\subsection{Women Objectifying Women}\label{women-objectifying-women}
-
-Harsey and Zurbriggen (2020) found that self-objectification was related
-to the objectification of women to a similar degree for men and women.
-Additionally, Strelan and Hargreaves (2005) found that the more women
-self-objectify, the more they objectify other women. Could the process
-work in the other direction as well, that is, could objectification by a
-woman produce self-objectification, in a similar manner to mixed-gender
-interactions?
-
-Past research has focused on men's objectifying behaviors, with little
-attention paid to the role that women may also play in objectifying
-other women. Hill and Fischer (2008) assessed women's experiences of
-objectification from men independently from women's experiences of
-objectification from other women. They found that women may be
-socialized not only to see themselves as objects, but perhaps to see
-other women as objects as well. This process, however, was not comfirmed
-to occur during an actual interpersonal interaction. Loughnan et al.
-(2015a) found that women objectify other women to a greater extent than
-they objectify men. Women have also been found to objectify
-(dehumanized) sexualized targets presented as images (Puvia \& Vaes,
-2013), but very little is known about interpersonal sexual
-objectification among women and what the proximal effects of this
-objectification might be. We do know that objectification has more
-adverse consequences for women than men (Gervais et al., 2011; Moradi \&
-Huang, 2008; Saguy, Quinn, F Dovidio, \& Pratto, 2010), however, if
-women objectify other women, perhaps even to a stronger degree than they
-objectify men, this woman to woman objectification might have
-detrimental outcomes.
+(TSO). Furthermore, self-objectification can also be elicited
+momentarily, for example, when viewing sexualized images in movies and
+magazines (Morry \& Staska, 2001), when trying on sexualizing clothing
+(B. L. Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998), or during
+video chat when you believe your interaction partner can only see your
+body (not face; Saguy, Quinn, F Dovidio, \& Pratto, 2010). This
+momentary self-objectification is referred to as \emph{state}
+self-objectification (SSO; Bernard, Legrand, \& Klein, 2018; Calogero et
+al., 2011; Moradi \& Huang, 2008) and is characterized by feeling like a
+body rather than a full self within a particular moment, instance, or
+context (Roberts \& Fredrickson, 1997).
+
+There is evidence that being objectified by another person during an
+interaction elicits SSO. For example, in a face-to-face mixed-gender
+dyadic study, Garcia et al. (2016) found that men's reported
+objectification of their female interaction partner was associated with
+increased self-objectification as reported by their female partner.
+Further, this negative effect of the men's objectification on women's
+SSO was strongest for women higher in TSO. The current study uses this
+same dyadic paradigm to study same-gender, woman-woman interacting
+pairs.
 
@@
 objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
-1979). Moreover, perhaps the most adverse effect is that being
-objectified socializes girls and women to treat themselves as objects to
-be looked at and evaluated (Bartky, 1990; Berger, Cohen, \& Zelditch Jr,
-1972; B. L. Fredrickson et al., 1998). Gervais et al. (2020) recently
-reviewed the research on interpersonal objectification and organized our
-current theoretical understanding of this process in the Social
-Interaction Model of Objectification (SIMO). What is clear from Gervais
-et al. (2020)'s review is that we know little about women-on-women
-interpersonal objectification. Could there also be negative consequences
-of this type of interpersonal objectification?
+1979). Interpersonal objectification has been found to have negative
+consequences for women. Gervais et al. (2011) found that an objectifying
+gaze by a male interaction partner (confederate) was associated with
+lower math performance for women, than being objectified by a female
+interaction partner. Moreover, perhaps the most adverse effect of
+interpersonal objectificaiton is that being objectified socializes girls
+and women to treat themselves as objects to be looked at and evaluated
+(Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et
+al., 1998). Gervais et al. (2020) recently reviewed the research on
+interpersonal objectification and organized our current theoretical
+understanding of this process in the Social Interaction Model of
+Objectification (SIMO). What is clear from Gervais et al. (2020)'s
+review is that we know little about women-on-women interpersonal
+objectification. Could there also be negative consequences of this type
+of interpersonal objectification?
 
@@
 interactions associated with the same negative process as that
-experienced in same-gender interactions? On the one hand, the ample
-research demonstrating that the male gaze has a particularly detrimental
-effect would suggest no (Gay \& Castano, 2010; Gervais et al., 2011;
-Saguy et al., 2010, Calogero (2004); Yilmaz \& Bozo, 2019), but on the
-other hand, women do objectify other women (Harsey \& Zurbriggen, 2020;
-Loughnan et al., 2015a; Puvia \& Vaes, 2013). When they do it, does it
-lead to self-objectification in the same way men's objectification of
-women does (Garcia et al., 2016)? If so, does the self-objectification
-experienced in these same-gender interactions have the same negative
-consequences for authenticity in that interaction?
-
-\subsection{Interpersonal Objectification and
-Authenticity}\label{interpersonal-objectification-and-authenticity}
+experienced in same-gender interactions? The ample research
+demonstrating that the male gaze has a particularly detrimental effect
+for women would suggest no (Gay \& Castano, 2010; Gervais et al., 2011;
+Saguy et al., 2010, Calogero (2004); Yilmaz \& Bozo, 2019), but, there
+is evidence that women do objectify other women (Harsey \& Zurbriggen,
+2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and to would be
+helpful to understand the consequencs of this intragroup objectification
+for women. When women objectify other women, does it lead to
+self-objectification in the same way men's objectification of women does
+(Garcia et al., 2016)? If so, does the self-objectification experienced
+in these same-gender interactions have the same negative consequences
+for authenticity in that interaction?
 
@@
 
+\subsection{Women Objectifying Women}\label{women-objectifying-women}
+
+Past research investigating women objectifying other women has focused
+on the psychological conditions that led women to objectify women.
+Harsey and Zurbriggen (2020) found that self-objectification was related
+to the objectification of women to a similar degree for male and female
+participants. Along the same lines, Strelan and Hargreaves (2005) found
+that the more women self-objectify, the more they objectify other women.
+Could the process work in the other direction as well, that is, could
+objectification by a woman produce self-objectification, in a similar
+manner to objectification by a man? Hill and Fischer (2008) assessed
+women's experiences of objectification from men independently from
+women's experiences of objectification from other women. They found that
+women may be socialized not only to see themselves as objects, but
+perhaps to see other women as objects as well. This process, however,
+was not comfirmed to occur during an actual interpersonal interaction.
+Loughnan et al. (2015a) found that women objectify other women to a
+greater extent than they objectify men. Women have also been found to
+objectify (dehumanized) sexualized targets presented as images (Puvia \&
+Vaes, 2013), but very little is known about interpersonal sexual
+objectification among women and what the proximal effects of this
+objectification might be. We do know that objectification has more
+adverse consequences for women than men (Gervais et al., 2011; Moradi \&
+Huang, 2008; Saguy et al., 2010), however, if women objectify other
+women, perhaps even to a stronger degree than they objectify men, this
+woman to woman objectification might have detrimental outcomes.
+
 \subsection{The Current Study}\label{the-current-study}
@@
 
-Data from two demographically equivalent higher education institutions
-in the Northeast United States were combined to create the final
-analysis sample (\emph{N =} 64) used in this study. In the measures
-section that follows we refer to them as Sample 1 and Sample 2.
-Thirty-two previously unacquainted self-identifying female dyads (64
-total participants) from institutions in the Northeast of the United
-States participated in this study. Sample 1 (\emph{N =} 24) is from a
-co-ed liberal arts college and Sample 2 (\emph{N =} 40) is from a
-women's liberal arts college. More specifically, twelve of the pairs
-were students at a co-ed liberal arts college, while the remaining
-twenty pairs attended a women's liberal arts college. {[}Footnote:
-Initially, data was collected from same-sex and mixed-sex dyads that
-comprised of male and female gendered individuals. Sample 1 originally
-consisted of twenty-two pairs, twelve men and thirty-two women.
-Twenty-three pairs made up of forty-three women and one man, as well as
-two participants who did not identify with either gender category,
-formed Sample 2. For consistency, we limited participant data to same
-sex female pairs at the two colleges.{]} All results presented below are
-from models including sample as a control variable.
+Data from two demographically similar higher education institutions in
+the Northeast United States were combined to create the final analysis
+sample (\emph{N =} 64) used in this study. In the measures section that
+follows we refer to them as Sample 1 and Sample 2. Thirty-two previously
+unacquainted self-identifying female dyads (64 total participants) from
+institutions in the Northeast of the United States participated in this
+study. Sample 1 (\emph{N =} 24) is from a co-ed liberal arts college and
+Sample 2 (\emph{N =} 40) is from a women's liberal arts college. More
+specifically, twelve of the pairs were students at a co-ed liberal arts
+college, while the remaining twenty pairs attended a women's liberal
+arts college. {[}Footnote: Initially, data was collected from same-sex
+and mixed-sex dyads that comprised of male and female gendered
+individuals. Sample 1 originally consisted of twenty-two pairs, twelve
+men and thirty-two women. Twenty-three pairs made up of forty-three
+women and one man, as well as two participants who did not identify with
+either gender category, formed Sample 2. For consistency, we limited
+participant data to same sex female pairs at the two colleges.{]} All
+results presented below are from models including sample as a control
+variable.
 
@@
 
-\subsection{Data analysis}\label{data-analysis}
+\subsection{Analysis Strategy}\label{analysis-strategy}
 
@@
 \emph{rmarkdown} (Version 1.15; Xie, Allaire, \& Grolemund, 2018).
-
-\subsection{Analysis Strategy}\label{analysis-strategy}
 
@@
 objectification and state self-objectification (SSO) used in Garcia et
-al. (2016) replicates in a same-gender dyadic sample of women only.
-Although past research has found that women do objectify other women
-(Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes,
-2013), this is the first study to test if \emph{interpersonal}
-other-objectification by women is related to state self-objectification
-in their woman-identified interaction partners. As hypothesized, the
-current study did find a significant relationship between a woman's
-interaction partner's report of having objectified her and her own
-post-interaction feelings of self-objectification. That is, there was a
-significant partner effect of other-objectification on SSO. This effect
-extends the equivalent relationship found in mixed-gender interactions
-to the context of same-gender interactions between women. Thus, evidence
-suggests that it is not only the male gaze, and male
-other-objectification that is related to women's state
-self-objectification, but being objectified by another woman can also
-result in SSO, at least in the context of a scenario where they know
-they are being evaluated as a potential dating partner. {[}Asha:Or
-\ldots{} thus evidence provides support for the claim that women being
-objectified by another woman result in sso in ways that are not uniquely
-dissimilar from that of xyz{]}
+al. (2016) replicates in a same-gender dyadic sample of women. Although
+past research has found that women do objectify other women (Harsey \&
+Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013), this is
+the first study to test if \emph{interpersonal} other-objectification by
+women is related to state self-objectification in their woman-identified
+interaction partners. As hypothesized, the current study did find a
+significant relationship between a woman's interaction partner's report
+of having objectified her and her own post-interaction feelings of
+self-objectification. That is, there was a significant partner effect of
+other-objectification on SSO. This effect extends the equivalent
+relationship found in mixed-gender interactions to the context of
+same-gender interactions between women. Thus, evidence suggests that it
+is not only the male gaze, and male other-objectification that is
+related to women's state self-objectification, but being objectified by
+another woman is also related to women's SSO, at least in the context of
+a scenario where they know they are being evaluated as a potential
+dating partner.
 
 As is the case in all correlational studies, we cannot be sure about the
-causal direction. It could be that women's SSO causes them to be
-objectified by their interaction partner. This interpretation is
-theoretically interesting given that, in both the Garcia et al. (2016)
-study and in the current study, it is \emph{women's} SSO that relates to
-being objectified by one's partner. However, Objectification Theory
-(Roberts \& Fredrickson, 1997), as well as past experimental studies
-{[}Saguy et al. (2010); CITE{]}, suggest that the causal flow is from
-other-objectification to SSO. Although, the current study found evidence
-for the partner effect of other-objectification on SSO, there was a lack
-of evidence for the connections between SSO and downstream negative
-consequences.
+causal direction. The model used by the current study asserts that being
+objectified by a woman causes women to self-objectify, but it could be
+that women's SSO causes them to be objectified by their interaction
+partner. This latter interpretation is theoretically interesting given
+that, in both the Garcia et al. (2016) study and in the current study,
+it is \emph{women's} state self-objectification that relates to being
+objectified by one's partner. Objectification Theory (Roberts \&
+Fredrickson, 1997), as well as some past experimental studies (Saguy et
+al., 2010) suggest that at least one direction of the causal flow is
+from other-objectification to SSO. Other studies, especailly those
+investigating explicitly women objectifying other women (Puvia \& Vaes,
+2013), have relately found evidence that women's \emph{trait}
+self-objectification causes women to objectify (dehumanize) other women
+and this link is mediated by \emph{state} self-objectification. It could
+follow that we tend to objectify other women who objectify us and
+through a process of TSO causes SSO which in turn causes objectifation
+of one's partner, which in turn causes one's partner to objectify us.
+The current study does not provide any evidence of this alternative
+model, however---TSO was not significantly correlated with SSO and
+actor's objectification was not correlated with partner's
+objectification.
 
@@
 functioning (B. L. Fredrickson et al., 1998; and see Moradi \& Huang,
-2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the small, but
-extant research on interpersonal other-ojectification and cognitive
-functioning (Garcia et al., 2016; Logel et al., 2009). This lack of
+2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the research on
+interpersonal other-ojectification and cognitive functioning (Garcia et
+al., 2016; Gervais et al., 2011; Logel et al., 2009). This lack of
 evidence could potentially signal diverging processes between women's
@@
 Roberts \& Fredrickson, 1997), and perhaps the self-objectification
-experienced within an interaction with a women is not as harmful as the
-self-objectification experienced within an interaction with a man. As a
-strong note of caution, it is best not to interpret a null result as
-evidence of no relationship.
+experienced within an interaction with a women is qualtatively
+different, and perhaps not as harmful, as the self-objectification
+experienced within an interaction with a man. However, as a strong note
+of caution, it is best not to interpret a null result as evidence of no
+relationship and more research on interpersonal objectification among
+women is needed.
 
@@
 evidence of no relationship. It should be noted that the estimate of
-this relationship was very small, but in the negative direction, as
-anticipated. If it is the case that there is a smaller (i.e., weaker)
+this relationship was small (close to zero), but in the negative
+direction. If it is the case that there is a smaller (i.e., weaker)
 connection between women's feelings of SSO and inauthenticity in
@@
 could be extended by including inauthenticity as a potential mediating
-factor. Further, gender of the objectifyer/interaction partner could
-also be added to the SIMO model to help understand the circumstances
-that require other-objectification and SSO to have negative consequences
-for women.
-
-Although we did not find a connection between SSO and authenticity, we
-did find significant positive relationships between authenticity and
-relationship agency, and authenticity and career aspirations. The
-relationship between authenticity and cognitive functioning was also
-estimated as positive, but was not statistically signficant. Again, due
-to the lack of connection between SSO and authenticity, we found no
-evidence of \emph{indirect} relationships between SSO and these outcome
-variables. This evidence of a relationship between authenticity and the
-relational outcome variables (i.e., relationship agency and career
-aspirations) provides evidence that corroborates past findings that felt
-authenticity in interactions is important for healthy relationship
-functioning (Garcia et al., 2016; Terán et al., 2020). Just as
-authenticity has been found to be important in intergroup interactions
-(Brunell et al., 2010; Garcia et al., 2016; Tolman et al., 2006), we
-again find more evidence here that disruptions in feelings of
-authenticity can negatively impact relationships beyond the current
-partner. Although the current study did not find a connection between
-authenticity and SSO, this seems theoretically to be a natural
-connection, and future work must explore when and how SSO leads to
-inauthenticity in interpersonal objectification situations.
+factor. Further, gender of the objectifyer/interaction partner could be
+added as a moderator of the self-objectificaiton to authenticity process
+to help understand the circumstances that require other-objectification
+and SSO to have negative consequences for women.
+
+Although the current study did not find a connection between SSO and
+authenticity, we did find significant positive relationships between
+authenticity and relationship agency, and authenticity and career
+aspirations. The relationship between authenticity and cognitive
+functioning was also estimated as positive, but was not statistically
+signficant. Again, due to the lack of connection between SSO and
+authenticity, we found no evidence of \emph{indirect} relationships
+between SSO and these outcome variables. This evidence of a relationship
+between authenticity and the relational outcome variables (i.e.,
+relationship agency and career aspirations) provides evidence that
+corroborates past findings that felt authenticity in interactions is
+important for healthy relationship functioning (Garcia et al., 2016;
+Terán et al., 2020). Just as authenticity has been found to be important
+in intergroup interactions (Brunell et al., 2010; Garcia et al., 2016;
+Tolman et al., 2006), we again find more evidence here that disruptions
+in feelings of authenticity can negatively impact relationships beyond
+the current partner. Although the current study did not find a
+connection between authenticity and SSO, this seems theoretically to be
+a natural connection, and future work must explore when and how SSO
+leads to inauthenticity in interpersonal objectification situations.
 
@@
 
-In addition to being small and combined across two institutions, the
-sample of the current study was comprised of Western women, being that
-sexual objectification is most prevalent in this culture (Loughnan et
-al., 2015b), and research on objectification conducted outside of
-Western or Westernized countries is scarce (Moradi \& Huang, 2008),
-although more current work examines objectification from a
-cross-cultural framework (Loughnan et al., 2015b, Wollast et al.
-(2020)). Since \enquote{bodies exist within social and cultural
-contexts, and hence are also constructed through sociocultural practices
-and discourses} (Roberts \& Fredrickson, 1997, p. 174), it is important
-to consider how diverse social identities within unique cultural
-contexts may inform sexual objectification phenomenon to test the
-cross-cultural applicability of theoretical frameworks (Loughnan et al.,
-2015b). Further, sexualizing experiences and self-objectification are
-thought to begin a very young age, and thus, researchers have only
-recently begun to examine such experiences among children (Bury,
-Tiggemann, \& Slater, 2016; e.g., Holland \& Haslam, 2016; Jongenelis,
-Byrne, \& Pettigrew, 2014). Considering the fact that the average mean
-age of the investigated participants of this current study was 18.85
-years, research among younger and older individuals is needed,
-especially because self-objectification may change over time (Roberts \&
+In addition to being relatively small and combined across two
+institutions, another limitation of the current study is that the sample
+was comprised of Western women only. Being that self-objectification is
+most prevalent in Western culture (Loughnan et al., 2015b) research on
+objectification conducted outside of Western or Westernized countries
+has been scarce (Moradi \& Huang, 2008), although more recent work has
+examined objectification from a cross-cultural framework (Loughnan et
+al., 2015b, Wollast et al. (2020)). Since \enquote{bodies exist within
+social and cultural contexts, and hence are also constructed through
+sociocultural practices and discourses} (Roberts \& Fredrickson, 1997,
+p. 174), it is important to consider how diverse social identities
+within unique cultural contexts may inform sexual objectification
+phenomenon to test the cross-cultural applicability of theoretical
+frameworks (Loughnan et al., 2015b).
+
+Further, sexualizing experiences and self-objectification are thought to
+begin a very young age, and thus, researchers have only recently begun
+to examine such experiences among children (Bury, Tiggemann, \& Slater,
+2016; e.g., Holland \& Haslam, 2016; Jongenelis, Byrne, \& Pettigrew,
+2014). Considering the fact that the average mean age of the
+investigated participants of this current study was 18.85 years,
+research among younger and older individuals is needed, especially
+because self-objectification may change over time (Roberts \&
 Fredrickson, 1997). It may be valuable to question the extent to which
@@
 ethnicities are exposed to varied amounts of sexualizing content.
-{[}Kat: Or a longitudinal study is needed.{]}
+Further, more longitudinal studies investigating the developmental
+experience of interpersonal objectification and self-objectificaion are
+needed {[}see CITE and CITE for exmaples{]}.
 
@@
 differing sexualities might have served to dampen our ability to detect
-relationships, adding variability. {[}Kat: The only other thing I would
-add re: sexuality limitations are that we didn't collect/use sexual
-orientation, so we couldn't analyze results by that at all/our samples
-might have differed there.{]}
+relationships, adding variability.
 
@@
 
-\subsubsection{Measurement}\label{measurement}
-
-Future experiments or longitudinal studies should explore the external
-validity of the notions of self-objectification and how the
-operationalization of self-objectification may be improved.
-
-\subsubsection{Alternative Model}\label{alternative-model}
-
-Puvia and Vaes (2013) alternative model. TSO -\textgreater{} SOO,
-mediated by SSO. \enquote{Found that women's motivation to look
-attractive (for men) and internalize sociocultural beauty standards were
-positively linked with the dehumanization of sexually objectified female
-targets.} Tis relationship was mediated by their own level of
-self-objectification.''
-
-\subsection{Clinical Implications}\label{clinical-implications}
+\section{Conclusion}\label{conclusion}
 
@@
 
-\section{Conclusion}\label{conclusion}
-
 The results of this study demonstrate the complex and ambivalent nature

### 2020-09-22 Final_Manuscript.Rmd
editing and fixing footnote

@@
 abstract: |
-  Empirical evidence has only found links between objectification, self-objectification, and negative outcomes for women within interpersonal interactions between male-female pairs.
-The purpose of the present study was to extend past research and consider the relationships between objectification and self-objectification within interactions between female pairs.
-Women were brought into the laboratory and interacted in same-sex dyads.
-Dyadic analysis was utilized to detect whether partners’ objectification of each other affected state self-objectification, as well as the resulting feelings of comfort and authenticity during the interaction.
-After the interaction, participants completed a questionnaire measuring, among other things, cognitive performance, career aspirations, and relationship agency.
-Results revealed a significant positive effect of being objectified by a female partner on women's self-objectification.
-There was no significant relationship between self-objectification and authenticity.
-Further, although there were significantly negative effects on career aspirations and relationship agency resulting from a lack of relationship authenticity, there was no evidence that this is due to feelings of sexual objectification.
-The significant partner effect of objectification on actor self-objectification suggests that women being objectified by other women may result in feelings of self-objectification, and such research has powerful implications for the ways that women interact in both sexual and non-sexual settings.
+  Extant research on interpersonal objectification has focused mostly on links between objectification, self-objectification, and negative outcomes for women within mixed-gender interactions [@gervais2020social; @garcia2016objectification].
+The purpose of the present study was to extend past research on interpersonal objectification to interactions between pairs of women.
+Women were brought into the laboratory and interacted face-to-face in same-sex dyads.
+Dyadic analysis [@kenny2006dyadic] was utilized to detect whether partners’ objectification of each other affected state self-objectification, as well as the resulting feelings of comfort and authenticity during the interaction.
+Results revealed a significant positive relationship between being objectified by a woman interaction partner and women’s own self-objectification (a partner effect).
+There was no significant relationship between self-objectification and interaction inauthenticity.
+Further, there were significant negative effects of inauthenticity on career aspirations and relationship agency (actor effects).
+The significant partner effect of objectification on self-objectification suggests that women being objectified by other women may result in feelings of self-objectification, and this finding opens up questions for future research about how interpersonal objectification might function in situations without an immediate male gaze.
 
@@
 The negative effects of this interpersonal objectification for women are theorized be the strongest when it is a man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction?
-Psychological researchers studying the sexual objectification of women, have in recent years explored the interpersonal process of the objectification, finding evidence for self-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification, @strelan2018birds, @riemer2020self].
-In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO), however this model focuses on mixed-gender encounters.
-Although there is evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], there are currently no studies investigating the process of interpersonal objectification in interactions between women.
-Is objectification by a female interaction partner related to an increase in self-objectification for the woman being objectified?
+Psychological researchers studying the sexual objectification of women, have in recent years explored the interpersonal process of the objectification, finding evidence for *self*-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification; @strelan2018birds; @riemer2020self].
+In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO).
+The SIMO is useful for studying mixed-gender interactions, but what about interactions among women?
+Although there is evidence that women objectify other women [@loughnan205exploring; @puvia2013being], studies investigating the process of interpersonal objectification in interactions between women is scarce.
+
+Is objectification by a female interaction partner related to an increases in self-objectification for the woman being objectified?
 Further, does objectification by a woman have the same downstream negative consequences for women as being objectified by a male interaction partner?
@@
 ##Self-Objectification
-Self-objectification is a psychological process that provides a cognitive mechanism to translate the experiences of interpersonal objectification [@loughnan2015exploring] to negative mental health outcomes (e.g., anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008].
-@calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO).
+Self-objectification is a psychological process that provides that translates the experiences of interpersonal objectification [@loughnan2015exploring; @gervais2020social into negative mental health outcomes (e.g., interaction inauthenticity, anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008].
+@calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO), whereby one abopts a habitual third-person perspective on one's own appearance.
 Furthermore, self-objectification can also be elicited momentarily, for example, when viewing sexualized images in movies and magazines [@morry2001magazine], when trying on sexualizing clothing [@fredrickson1998swimsuit], or during video chat when you believe your interaction partner can only see your body [not face; @saguyetal2010].
-This momentary self-objectification is referred to as *state* self-objectification [SSO; @bernard2018bodies; @calogero2011; @moradi2008] and is characterized by feeling like a body rather than a full self within a particular moment, instance, or context [@robertsfredrickson].
+This momentary self-objectification is referred to as *state* self-objectification [SSO; @bernard2018bodies; @calogero2011; @moradi2008] and is characterized by feeling like a body rather than a full self within a particular moment, instance, or context.
 
@@
 The current study uses this same dyadic paradigm to study same-gender, woman-woman interacting pairs.
-
-##Interpersonal Objectification
-Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and are likely to internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
-Interpersonal objectification has been found to have negative consequences for women.
-@gervais2011you found that an objectifying gaze by a male interaction partner (confederate) was associated with lower math performance for women, than being objectified by a female interaction partner.
-Moreover, perhaps the most adverse effect of interpersonal objectificaiton is that being objectified socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
-@gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
-What is clear from @gervais2020social's review is that we know little about women-on-women interpersonal objectification.
-Could there also be negative consequences of this type of interpersonal objectification?
-
-Interpersonal objectification can also occur within the context of romantic relationships, in addition to interactions with strangers.
-Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
-Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds].
-Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship.
-There is also evidence that they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], but less is known about first dates.
-An important caveat to this literature is that it is only about heterosexual relationships.
-A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
-Both romantic relationships and stranger encounters have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
-
-There is evidence that the experience of state self-objectification in mixed-gender contexts (stranger and romantic) has negative consequences for women, but what about in the context of interactions with other women?
-Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
-The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010, @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and to would be helpful to understand the consequencs of this intragroup objectification for women.
-When women objectify other women, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
-If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that interaction?
-
-There is some evidence that reduced authenticity is a consequence of self-objectification [@garcia2016objectification; @teran2020relational].
-This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop; @nadal2012effects].
-Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
-When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identity threat.
-Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, specifically, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
-A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; @teran2020relational].
 
@@
 
+##Interpersonal Objectification
+Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and are likely to internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
+Interpersonal objectification has been found to have negative consequences for women.
+@gervais2011you found that an objectifying gaze by a male interaction partner (confederate) was associated with lower math performance for women, than being objectified by a female interaction partner.
+Perhaps the most adverse negative consequence of interpersonal objectificaiton is that being objectified socializes girls and women to routinely treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
+@gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
+What is clear from @gervais2020social's review is that we know little about women-on-women interpersonal objectification.
+Could there also be negative consequences for women of interpersonal objectification by women?
+
+Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds], in addition to interactions with strangers.
+Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
+Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship.
+There is also evidence that they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], but less is known about first dates.
+An important caveat to this literature is that it is only about heterosexual relationships.
+A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
+Both romantic relationships and stranger encounters have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
+
+There is evidence that the experience of state self-objectification in mixed-gender contexts (stranger and romantic) has negative consequences for women, but what about in the context of interactions with other women?
+Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
+The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010; @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and to would be helpful to understand the consequencs of this intragroup objectification for women.
+When women objectify other women, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
+If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that interaction?
+
+There is some evidence that reduced authenticity is a consequence of self-objectification [@garcia2016objectification; @teran2020relational].
+This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop; @nadal2012effects].
+Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
+When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identity threat.
+Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, specifically, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
+A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; @teran2020relational].
+
 ##The Current Study
@@
 We also expected that TSO would moderate this relationship, amplifying the positive assocaition between being objectified and SSO for women higher in TSO.
-We hypothesized that SSO would, in turn, lead to feelings of inauthenticity [although there is ample support against this prediction from the identity threat within intergroup interactions literature; @rollero2016bringing].
-Further, we hypothesized that these feelings of inauthencity would then be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
-In summary, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
-We also expected to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
-
-These hypotheses are considered exploratory, given the lack of prior research theorizing about these linkages.
-
 Here we would like to note that @puvia2013being would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (more precisely, to dehumanize a sexualized woman).
@@
 Where appropriate, we report results considering the causal directions implied by this alternative mediation model.
+
+We also tested whether SSO would, in turn, lead to feelings of inauthenticity.
+The investigation of the SSO - inauthenticity connection is considered exploratory given the lack of support for this connection from the literature on identity threat in intragroup interactions [@rollero2016bringing] but support for this connection in the objectification literature [@garcia2016objectification; @teran2020relational].
+Regardless of whether there was an association between SSO and inauthenticity, we hypothesized that feelings of inauthencity would be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
+In summary, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
+We also expected to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
 
@@
 
+Thirty-two previously unacquainted dyads of self-identifying women participated in this study.
 Data from two demographically similar higher education institutions in the Northeast United States were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study.
 In the measures section that follows we refer to them as Sample 1 and Sample 2.
-Thirty-two previously unacquainted self-identifying female dyads (64 total participants) from institutions in the Northeast of the United States participated in this study.
 Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college.
-More specifically, twelve of the pairs were students at a co-ed liberal arts college, while the remaining twenty pairs attended a women’s liberal arts college.
-[Footnote: Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals.
-Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women.
-Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2.
-For consistency, we limited participant data to same sex female pairs at the two colleges.] All results presented below are from models including sample as a control variable.
+More specifically, twelve of the pairs were students at a co-ed liberal arts college, while the remaining twenty pairs attended a women’s liberal arts college.^[Initially, data was collected from both same-gender and mixed-gender dyads at both institutions.
+Sample 1 originally consisted of 22 pairs, 12 men and 32 women.
+In Sample 2 there were 23 pairs made up of 43 women and one man, as well as two participants who did not identify with either gender category.
+To investigate only same-gender pairs of women, we limited participant data to women in both samples.] All results presented below are from models including sample as a control variable.
 

### 2020-09-25 Final_Manuscript.Rmd
updated SEM figure

@@
 The SIMO is useful for studying mixed-gender interactions, but what about interactions among women?
-Although there is evidence that women objectify other women [@loughnan205exploring; @puvia2013being], studies investigating the process of interpersonal objectification in interactions between women is scarce.
+Although there is evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], studies investigating the process of interpersonal objectification in interactions between women is scarce.
 
@@
 There is evidence that being objectified by another person during an interaction elicits SSO.
-For example, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification as reported by their female partner.
+For example, @loughnan2017internalizing found that for women, imagining a time when they were objectified by another person cause reductions in human traits attributed to the self, and further, the gender of the person doing the objectification was not a moderating factor.
+In addition, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification as reported by their female partner.
 Further, this negative effect of the men's objectification on women's SSO was strongest for women higher in TSO.
@@
 `r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
+See the analysis of differences between heteroseuxal and non-heterosexual women in levels of other-objectification of their female partners in the measures section below.
 
@@
 ```
-To conceptualize participants’ career aspirations after the interaction, we used the 10-item adaptation of @grayobrien2007’s Career Aspiration Scale employed in @garcia2016objectification, which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
+To conceptualize participants’ career aspirations after the interaction, we used the 10-item adaptation of @grayobrien2007’s Career Aspiration Scale which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
 Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
@@
 Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness).
-Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.
+Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1 so that positive scores indicated greater TSO.
 
 # Results
-## Analysis Strategy
 ```{r create_r-references, warning=FALSE, message=FALSE}
@@
 
+The R-package *papaja* [Version 0.1.0.9842; @R-papaja] was used to create a fully reproducible research document containing the analysis code and manuscript text integrated into one source file.
+The benefit of this integration is that the numbers reported throughout this document are softcoded into the text, ensuring that no errors were made during a workflow marked by a copy-and-paste from statistical software to word processing software.
+Note that here we are using the term reproducibility to mean getting the same results when running analyses again using the same data, not to be confused with replicability meaning collecting a new dataset using the same methods and obtaining the same results [@patil2016statistical].
+The source code for this manuscript along with survey materials and experimenter scripts for the study protocol are all avaliable at https://github.com/kkyuchukova/object-in-action.
+The data unfortunutely cannot be made publically avaliable given the dyadic nature of the observations.
+For example, with dyadic data, if a person who participated in the study found their own scores, using the dyad identification number, they could then see their partner's scores and thus confidentiality would be broken.
+
+## Analysis Strategy
 ```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
@@
 
-```{r theorfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Theoretical Model from Garcia et al. (2016)."}
-include_graphics("theor_figure.png")
-```
-
 This study sought to detect whether partners’ objectification of one another affected state self-objectification (SSO).
-Specifically, we were interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction.
-In addition, we also tested if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification.
+Specifically, we were interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, may or may not affects feelings of inauthenticity during the interaction.
+In addition, we also tested if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification (moderation effect).
 Further, we investigated the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.
@@
 While past studies investigating objectification in interactions used dyadic path analysis [@garcia2016objectification], the current study used multilevel modeling proceedures.
-Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs), as we have here [@ledermann2017analyzing; @garcia2015moderation].
+Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs), as we had in the current study [@ledermann2017analyzing; @garcia2015moderation].
 One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means), but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural].
 Further, @olsen2006structural details how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models.
-The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation patterns.
-The online supplementary materials contains analysis using SEM.
+The current study used dyadic multilevel modeling (MLM) to test all relationships, moderation, and mediation patterns.
+The online supplementary materials found at https://github.com/kkyuchukova/object-in-action contain model estimates obtained with SEM.
 See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.
 
-Testing our hypotheses in the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approach for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:theorfigure)).
-Thus, we ran five APIM's to test all the hypothesized relationships.
+Testing hypotheses and exploring relationships in the current sample of indistinguishable dyads involved using the Actor-Partner Independence Model (APIM) approach for each outcome variable.
+The current study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
+Thus, we ran five APIM's to test all the relationships (i.e., for SSO, inauthenticity, career aspirations, relationship agency, and cognitive performance as outcome variables).
 See Figure\ \@ref(fig:apim) for a basic APIM model.
 The APIM includes effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$).
-The current study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
-These analyses are considered exploratory, given the lack of prior research theorizing about these linkages.
+The analysis of the relationship between SSO and inauthenticity in this same-gender sample are considered exploratory, given that prior research points to mixed possibilities.
 
@@
 ## Main Results
-```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
+```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="This figure depicts the relationships tested bewteen study variables.
+The light gray variables represent redundant variables and are shown to emphasize the dyadic nature of the data.
+The estimates were from obtained from separate MLMs.
+Sample was controlled for in all models.
+The effects of TSO, actor other-objectification, and partner other-objectification are from a model where the interaction of TSO and partner other-objectification had been trimmed.
+*p < .05, dashed lines represent non-significant relationships."}
 include_graphics("SEMfigure.png")
-```
-
-```{r mlm, include=TRUE, results='asis'}
-# fit_table <- xtable(parameterEstimates(fit))
-# 
-# fit_table <- fit_table %>%
-#   filter(op=="~") %>%
-#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
-#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
-#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
-#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
-#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
-#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
-#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
-#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
-#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
-#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
-#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
-#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
-#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
-#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
-#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
-#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
-#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
-#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
-#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
-#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
-#   select(lhs, op, rhs, est, se, z, pvalue) %>%
-#   #taking out partner-partner estimates
-#   slice(1:5,11:13)
-# 
-# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
-# 
-# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
 ```
@@
 
-All model estimates and p-values are found in Table\ \@ref(tab:mlm) and the relationships with estimates included are depicted in Figure\ \@ref(fig:semfigure).
-
 ```{r}
@@
 summary(apim1)
+
 summary(apim1.b)
+
 ```
-The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
-As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically significant, `r report_stats(apim1, 3)`.
-One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
-Inconsistent with past findings however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
-There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.
 
@@
 ```
-There was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
-Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also estimated the pairwise correlations between SSO and all these items individually.
-They were all small, ranging from only `r -1*min_corr` to `r -1*max_corr`.
-Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship between SSO and authenticity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, `r report_stats(apim2.b, 3)` (nor was the total effect of partner's other objectification on authenticity, `r report_stats(apim2.c, 2)`).
 
@@
 ```
+
+```{r mlm, include=TRUE, results='asis'}
+# fit_table <- bind_rows(xtable(summary(apim1)$tTable))
+# 
+# 
+# colnames(fit_table) <- c("Estimate", "SE", "z-value", "p-value")
+# 
+# apa_table(fit_table, caption = "Estimates from Multilevel Models", font_size = "small")
+```
+
+All relationships between study variables and the MLM estimates are depicted in Figure\ \@ref(fig:semfigure).
+
+The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
+As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically significant, `r report_stats(apim1, 3)`.
+One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
+Inconsistent with past findings however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
+There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.
+
+There was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
+Because authenticity was a composite score of 9 items, two of which were interaction specific authenticity items, we also estimated the pairwise correlations between SSO and all these items individually.
+They were all small, ranging from only `r -1*min_corr` to `r -1*max_corr`.
+Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship between SSO and authenticity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, `r report_stats(apim2.b, 3)` (nor was the total effect of partner's other objectification on authenticity, `r report_stats(apim2.c, 2)`).
+
 Lastly, although there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performance, career aspirations, and relationship agency, as it did in @garcia2016objectification.

### 2020-09-25 Final_Manuscript.tex
updated SEM figure

@@
 \abstract{
-Empirical evidence has only found links between objectification,
-self-objectification, and negative outcomes for women within
-interpersonal interactions between male-female pairs. The purpose of the
-present study was to extend past research and consider the relationships
-between objectification and self-objectification within interactions
-between female pairs. Women were brought into the laboratory and
-interacted in same-sex dyads. Dyadic analysis was utilized to detect
-whether partners' objectification of each other affected state
+Extant research on interpersonal objectification has focused mostly on
+links between objectification, self-objectification, and negative
+outcomes for women within mixed-gender interactions (Garcia, Earnshaw,
+\& Quinn, 2016; Gervais, Sáez, Riemer, \& Klein, 2020). The purpose of
+the present study was to extend past research on interpersonal
+objectification to interactions between pairs of women. Women were
+brought into the laboratory and interacted face-to-face in same-sex
+dyads. Dyadic analysis (Kenny, Kashy, \& Cook, 2006) was utilized to
+detect whether partners' objectification of each other affected state
 self-objectification, as well as the resulting feelings of comfort and
-authenticity during the interaction. After the interaction, participants
-completed a questionnaire measuring, among other things, cognitive
-performance, career aspirations, and relationship agency. Results
-revealed a significant positive effect of being objectified by a female
-partner on women's self-objectification. There was no significant
-relationship between self-objectification and authenticity. Further,
-although there were significantly negative effects on career aspirations
-and relationship agency resulting from a lack of relationship
-authenticity, there was no evidence that this is due to feelings of
-sexual objectification. The significant partner effect of
-objectification on actor self-objectification suggests that women being
-objectified by other women may result in feelings of
-self-objectification, and such research has powerful implications for
-the ways that women interact in both sexual and non-sexual settings.
+authenticity during the interaction. Results revealed a significant
+positive relationship between being objectified by a woman interaction
+partner and women's own self-objectification (a partner effect). There
+was no significant relationship between self-objectification and
+interaction inauthenticity. Further, there were significant negative
+effects of inauthenticity on career aspirations and relationship agency
+(actor effects). The significant partner effect of objectification on
+self-objectification suggests that women being objectified by other
+women may result in feelings of self-objectification, and this finding
+opens up questions for future research about how interpersonal
+objectification might function in situations without an immediate male
+gaze.
 
@@
 
-Roberts and Fredrickson (1997) Objectification Theory, suggests that, in
-addition to being steeped in a culture that objectifies women, women are
-objectified in actual interpersonal encounters. The negative effects of
-this interpersonal objectification for women are theorized be the
-strongest when it is a man doing the objectifying (Calogero, 2004; Gay
-\& Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
-consequences when a woman objectifies another woman in an interaction?
-Psychological researchers studying the sexual objectification of women,
-have in recent years explored the interpersonal process of the
-objectification, finding evidence for self-objectification in the target
-as a proximal consequence of being objectified (Garcia, Earnshaw, \&
-Quinn, 2016, Strelan and Pagoudis (2018), Riemer, Sáez, Brock, and
-Gervais (2020)). In a recent review, Gervais, Sáez, Riemer, and Klein
+Barbara L Fredrickson and Roberts (1997) Objectification Theory,
+suggests that, in addition to being steeped in a culture that
+objectifies women, women are objectified in actual interpersonal
+encounters. The negative effects of this interpersonal objectification
+for women are theorized be the strongest when it is a man doing the
+objectifying (Calogero, 2004; Gay \& Castano, 2010; Gervais, Vescio, \&
+Allen, 2011), but what are the consequences when a woman objectifies
+another woman in an interaction? Psychological researchers studying the
+sexual objectification of women, have in recent years explored the
+interpersonal process of the objectification, finding evidence for
+\emph{self}-objectification in the target as a proximal consequence of
+being objectified (Garcia et al., 2016; Riemer, Sáez, Brock, \& Gervais,
+2020; Strelan \& Pagoudis, 2018). In a recent review, Gervais et al.
 (2020) organized the extant literature on interpersonal
 self-objectification and proposed a theoretical model called the Social
-Interaction Model of Objectification (SIMO), however this model focuses
-on mixed-gender encounters. Although there is evidence that women
-objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013),
-there are currently no studies investigating the process of
-interpersonal objectification in interactions between women. Is
-objectification by a female interaction partner related to an increase
-in self-objectification for the woman being objectified? Further, does
-objectification by a woman have the same downstream negative
-consequences for women as being objectified by a male interaction
-partner? The current study begins to address these questions by
-investigating interpersonal objectification among interacting pairs
+Interaction Model of Objectification (SIMO). The SIMO is useful for
+studying mixed-gender interactions, but what about interactions among
+women? Although there is evidence that women objectify other women
+(Loughnan et al., 2015a; Puvia \& Vaes, 2013), studies investigating the
+process of interpersonal objectification in interactions between women
+is scarce.
+
+Is objectification by a female interaction partner related to an
+increases in self-objectification for the woman being objectified?
+Further, does objectification by a woman have the same downstream
+negative consequences for women as being objectified by a male
+interaction partner? The current study begins to address these questions
+by investigating interpersonal objectification among interacting pairs
 where both partners identify as women.
@@
 
-Self-objectification is a psychological process that provides a
-cognitive mechanism to translate the experiences of interpersonal
-objectification (Loughnan et al., 2015a) to negative mental health
-outcomes (e.g., anxiety, self-esteem, and cognitive performance)
-(Calogero, Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008).
-Calogero et al. (2011) proposes that self-objectification can be
-conceptualized as a learned trait, or \emph{trait} self-objectification
-(TSO). Furthermore, self-objectification can also be elicited
-momentarily, for example, when viewing sexualized images in movies and
-magazines (Morry \& Staska, 2001), when trying on sexualizing clothing
-(B. L. Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998), or during
-video chat when you believe your interaction partner can only see your
-body (not face; Saguy, Quinn, F Dovidio, \& Pratto, 2010). This
-momentary self-objectification is referred to as \emph{state}
-self-objectification (SSO; Bernard, Legrand, \& Klein, 2018; Calogero et
-al., 2011; Moradi \& Huang, 2008) and is characterized by feeling like a
-body rather than a full self within a particular moment, instance, or
-context (Roberts \& Fredrickson, 1997).
+Self-objectification is a psychological process that provides that
+translates the experiences of interpersonal objectification {[}Loughnan
+et al. (2015a); Gervais et al. (2020) into negative mental health
+outcomes (e.g., interaction inauthenticity, anxiety, self-esteem, and
+cognitive performance) (Calogero, Tantleff-Dunn, \& Thompson, 2011;
+Moradi \& Huang, 2008). Calogero et al. (2011) proposes that
+self-objectification can be conceptualized as a learned trait, or
+\emph{trait} self-objectification (TSO), whereby one abopts a habitual
+third-person perspective on one's own appearance. Furthermore,
+self-objectification can also be elicited momentarily, for example, when
+viewing sexualized images in movies and magazines (Morry \& Staska,
+2001), when trying on sexualizing clothing (Barbara L Fredrickson,
+Roberts, Noll, Quinn, \& Twenge, 1998), or during video chat when you
+believe your interaction partner can only see your body (not face;
+Saguy, Quinn, F Dovidio, \& Pratto, 2010). This momentary
+self-objectification is referred to as \emph{state} self-objectification
+(SSO; Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \&
+Huang, 2008) and is characterized by feeling like a body rather than a
+full self within a particular moment, instance, or context.
 
 There is evidence that being objectified by another person during an
-interaction elicits SSO. For example, in a face-to-face mixed-gender
-dyadic study, Garcia et al. (2016) found that men's reported
-objectification of their female interaction partner was associated with
-increased self-objectification as reported by their female partner.
-Further, this negative effect of the men's objectification on women's
-SSO was strongest for women higher in TSO. The current study uses this
-same dyadic paradigm to study same-gender, woman-woman interacting
-pairs.
+interaction elicits SSO. For example, Loughnan, Baldissarri, Spaccatini,
+and Elder (2017) found that for women, imagining a time when they were
+objectified by another person cause reductions in human traits
+attributed to the self, and further, the gender of the person doing the
+objectification was not a moderating factor. In addition, in a
+face-to-face mixed-gender dyadic study, Garcia et al. (2016) found that
+men's reported objectification of their female interaction partner was
+associated with increased self-objectification as reported by their
+female partner. Further, this negative effect of the men's
+objectification on women's SSO was strongest for women higher in TSO.
+The current study uses this same dyadic paradigm to study same-gender,
+woman-woman interacting pairs.
+
+\subsection{Women Objectifying Women}\label{women-objectifying-women}
+
+Past research investigating women objectifying other women has focused
+on the psychological conditions that led women to objectify women.
+Harsey and Zurbriggen (2020) found that self-objectification was related
+to the objectification of women to a similar degree for male and female
+participants. Along the same lines, Strelan and Hargreaves (2005) found
+that the more women self-objectify, the more they objectify other women.
+Could the process work in the other direction as well, that is, could
+objectification by a woman produce self-objectification, in a similar
+manner to objectification by a man? Hill and Fischer (2008) assessed
+women's experiences of objectification from men independently from
+women's experiences of objectification from other women. They found that
+women may be socialized not only to see themselves as objects, but
+perhaps to see other women as objects as well. This process, however,
+was not comfirmed to occur during an actual interpersonal interaction.
+Loughnan et al. (2015a) found that women objectify other women to a
+greater extent than they objectify men. Women have also been found to
+objectify (dehumanized) sexualized targets presented as images (Puvia \&
+Vaes, 2013), but very little is known about interpersonal sexual
+objectification among women and what the proximal effects of this
+objectification might be. We do know that objectification has more
+adverse consequences for women than men (Gervais et al., 2011; Moradi \&
+Huang, 2008; Saguy et al., 2010), however, if women objectify other
+women, perhaps even to a stronger degree than they objectify men, this
+woman to woman objectification might have detrimental outcomes.
 
@@
 lower math performance for women, than being objectified by a female
-interaction partner. Moreover, perhaps the most adverse effect of
+interaction partner. Perhaps the most adverse negative consequence of
 interpersonal objectificaiton is that being objectified socializes girls
-and women to treat themselves as objects to be looked at and evaluated
-(Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et
-al., 1998). Gervais et al. (2020) recently reviewed the research on
-interpersonal objectification and organized our current theoretical
-understanding of this process in the Social Interaction Model of
-Objectification (SIMO). What is clear from Gervais et al. (2020)'s
-review is that we know little about women-on-women interpersonal
-objectification. Could there also be negative consequences of this type
-of interpersonal objectification?
-
-Interpersonal objectification can also occur within the context of
-romantic relationships, in addition to interactions with strangers.
-Among heterosexual male and female college students,
-self-objectification has been found to be positively associated with the
-extent to which they objectify their romantic partners (Zurbriggen,
-Ramsey, \& Jaworski, 2011). Researchers have also studied interpersonal
-objectification and self-objectification in romantic relationships
-(Strelan \& Pagoudis, 2018). Evidence is mixed, suggesting that women
-can sometimes have positive outcomes from appearance valuation within
-the context of an established romantic relationship. There is also
-evidence that they experience less SSO after appearance comments within
-romantic relationships (Meltzer, 2020), but less is known about first
-dates. An important caveat to this literature is that it is only about
-heterosexual relationships. A recent study has investigated the effect
-of self-objectification on the reduction of relationship building skills
-in general (including same-sex friendships) (Terán, Jiao, \& Aubrey,
-2020). Both romantic relationships and stranger encounters have been
-studied in the context of objectification, but neither of these
-literatures have investigated specifically same-gender relationships.
+and women to routinely treat themselves as objects to be looked at and
+evaluated (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; Barbara L
+Fredrickson et al., 1998). Gervais et al. (2020) recently reviewed the
+research on interpersonal objectification and organized our current
+theoretical understanding of this process in the Social Interaction
+Model of Objectification (SIMO). What is clear from Gervais et al.
+(2020)'s review is that we know little about women-on-women
+interpersonal objectification. Could there also be negative consequences
+for women of interpersonal objectification by women?
+
+Researchers have also studied interpersonal objectification and
+self-objectification in romantic relationships (Strelan \& Pagoudis,
+2018), in addition to interactions with strangers. Among heterosexual
+male and female college students, self-objectification has been found to
+be positively associated with the extent to which they objectify their
+romantic partners (Zurbriggen, Ramsey, \& Jaworski, 2011). Evidence is
+mixed, suggesting that women can sometimes have positive outcomes from
+appearance valuation within the context of an established romantic
+relationship. There is also evidence that they experience less SSO after
+appearance comments within romantic relationships (Meltzer, 2020), but
+less is known about first dates. An important caveat to this literature
+is that it is only about heterosexual relationships. A recent study has
+investigated the effect of self-objectification on the reduction of
+relationship building skills in general (including same-sex friendships)
+(Terán, Jiao, \& Aubrey, 2020). Both romantic relationships and stranger
+encounters have been studied in the context of objectification, but
+neither of these literatures have investigated specifically same-gender
+relationships.
 
@@
 demonstrating that the male gaze has a particularly detrimental effect
-for women would suggest no (Gay \& Castano, 2010; Gervais et al., 2011;
-Saguy et al., 2010, Calogero (2004); Yilmaz \& Bozo, 2019), but, there
-is evidence that women do objectify other women (Harsey \& Zurbriggen,
-2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and to would be
-helpful to understand the consequencs of this intragroup objectification
-for women. When women objectify other women, does it lead to
-self-objectification in the same way men's objectification of women does
-(Garcia et al., 2016)? If so, does the self-objectification experienced
-in these same-gender interactions have the same negative consequences
-for authenticity in that interaction?
+for women would suggest no (Calogero, 2004; Gay \& Castano, 2010;
+Gervais et al., 2011; Saguy et al., 2010; Yilmaz \& Bozo, 2019), but,
+there is evidence that women do objectify other women (Harsey \&
+Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and to
+would be helpful to understand the consequencs of this intragroup
+objectification for women. When women objectify other women, does it
+lead to self-objectification in the same way men's objectification of
+women does (Garcia et al., 2016)? If so, does the self-objectification
+experienced in these same-gender interactions have the same negative
+consequences for authenticity in that interaction?
 
@@
 
-\subsection{Women Objectifying Women}\label{women-objectifying-women}
-
-Past research investigating women objectifying other women has focused
-on the psychological conditions that led women to objectify women.
-Harsey and Zurbriggen (2020) found that self-objectification was related
-to the objectification of women to a similar degree for male and female
-participants. Along the same lines, Strelan and Hargreaves (2005) found
-that the more women self-objectify, the more they objectify other women.
-Could the process work in the other direction as well, that is, could
-objectification by a woman produce self-objectification, in a similar
-manner to objectification by a man? Hill and Fischer (2008) assessed
-women's experiences of objectification from men independently from
-women's experiences of objectification from other women. They found that
-women may be socialized not only to see themselves as objects, but
-perhaps to see other women as objects as well. This process, however,
-was not comfirmed to occur during an actual interpersonal interaction.
-Loughnan et al. (2015a) found that women objectify other women to a
-greater extent than they objectify men. Women have also been found to
-objectify (dehumanized) sexualized targets presented as images (Puvia \&
-Vaes, 2013), but very little is known about interpersonal sexual
-objectification among women and what the proximal effects of this
-objectification might be. We do know that objectification has more
-adverse consequences for women than men (Gervais et al., 2011; Moradi \&
-Huang, 2008; Saguy et al., 2010), however, if women objectify other
-women, perhaps even to a stronger degree than they objectify men, this
-woman to woman objectification might have detrimental outcomes.
-
 \subsection{The Current Study}\label{the-current-study}
@@
 would moderate this relationship, amplifying the positive assocaition
-between being objectified and SSO for women higher in TSO. We
-hypothesized that SSO would, in turn, lead to feelings of inauthenticity
-(although there is ample support against this prediction from the
-identity threat within intergroup interactions literature; Rollero,
-2016). Further, we hypothesized that these feelings of inauthencity
-would then be associated with reduced feelings of agency in romantic
-relationships, reduced career aspiration, and reduced cognitive
-performance. In summary, we expected to find a positive relationship
-between other-objectification by one's partner and state
-self-objectification. We also expected to find a negative relationship
-between self-state objectification and interaction authenticity, and
-that interaction authenticity will be positively related to cognitive
-performance, relationship agency, and career aspirations.
-
-These hypotheses are considered exploratory, given the lack of prior
-research theorizing about these linkages.
-
-Here we would like to note that Puvia and Vaes (2013) would
-alternatively predict that women's tendency to self-objectify (TSO)
-leads them to objectify other women (more precisely, to dehumanize a
-sexualized woman). In addition, Strelan and Hargreaves (2005) and Harsey
-and Zurbriggen (2020) would predict the TSO to other-objectification
-link, further theorizing that this relationships is mediated by the
-woman's own state self-objectification (SSO). This limited, but extant,
-set of literature on woman-woman objectification points to a possible
-alternative model from the model hypothesized in the current study.
-Where appropriate, we report results considering the causal directions
-implied by this alternative mediation model.
+between being objectified and SSO for women higher in TSO. Here we would
+like to note that Puvia and Vaes (2013) would alternatively predict that
+women's tendency to self-objectify (TSO) leads them to objectify other
+women (more precisely, to dehumanize a sexualized woman). In addition,
+Strelan and Hargreaves (2005) and Harsey and Zurbriggen (2020) would
+predict the TSO to other-objectification link, further theorizing that
+this relationships is mediated by the woman's own state
+self-objectification (SSO). This limited, but extant, set of literature
+on woman-woman objectification points to a possible alternative model
+from the model hypothesized in the current study. Where appropriate, we
+report results considering the causal directions implied by this
+alternative mediation model.
+
+We also tested whether SSO would, in turn, lead to feelings of
+inauthenticity. The investigation of the SSO - inauthenticity connection
+is considered exploratory given the lack of support for this connection
+from the literature on identity threat in intragroup interactions
+(Rollero, 2016) but support for this connection in the objectification
+literature (Garcia et al., 2016; Terán et al., 2020). Regardless of
+whether there was an association between SSO and inauthenticity, we
+hypothesized that feelings of inauthencity would be associated with
+reduced feelings of agency in romantic relationships, reduced career
+aspiration, and reduced cognitive performance. In summary, we expected
+to find a positive relationship between other-objectification by one's
+partner and state self-objectification. We also expected to find a
+negative relationship between self-state objectification and interaction
+authenticity, and that interaction authenticity will be positively
+related to cognitive performance, relationship agency, and career
+aspirations.
 
@@
 
-Data from two demographically similar higher education institutions in
-the Northeast United States were combined to create the final analysis
-sample (\emph{N =} 64) used in this study. In the measures section that
-follows we refer to them as Sample 1 and Sample 2. Thirty-two previously
-unacquainted self-identifying female dyads (64 total participants) from
-institutions in the Northeast of the United States participated in this
-study. Sample 1 (\emph{N =} 24) is from a co-ed liberal arts college and
-Sample 2 (\emph{N =} 40) is from a women's liberal arts college. More
-specifically, twelve of the pairs were students at a co-ed liberal arts
-college, while the remaining twenty pairs attended a women's liberal
-arts college. {[}Footnote: Initially, data was collected from same-sex
-and mixed-sex dyads that comprised of male and female gendered
-individuals. Sample 1 originally consisted of twenty-two pairs, twelve
-men and thirty-two women. Twenty-three pairs made up of forty-three
-women and one man, as well as two participants who did not identify with
-either gender category, formed Sample 2. For consistency, we limited
-participant data to same sex female pairs at the two colleges.{]} All
-results presented below are from models including sample as a control
-variable.
+Thirty-two previously unacquainted dyads of self-identifying women
+participated in this study. Data from two demographically similar higher
+education institutions in the Northeast United States were combined to
+create the final analysis sample (\emph{N =} 64) used in this study. In
+the measures section that follows we refer to them as Sample 1 and
+Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal arts college
+and Sample 2 (\emph{N =} 40) is from a women's liberal arts college.
+More specifically, twelve of the pairs were students at a co-ed liberal
+arts college, while the remaining twenty pairs attended a women's
+liberal arts college.\footnote{Initially, data was collected from both
+  same-gender and mixed-gender dyads at both institutions. Sample 1
+  originally consisted of 22 pairs, 12 men and 32 women. In Sample 2
+  there were 23 pairs made up of 43 women and one man, as well as two
+  participants who did not identify with either gender category. To
+  investigate only same-gender pairs of women, we limited participant
+  data to women in both samples.} All results presented below are from
+models including sample as a control variable.
 
@@
 of the sample identified as heterosexual, and 25\% identified as gay,
-lesbian or bisexual.
+lesbian or bisexual. See the analysis of differences between
+heteroseuxal and non-heterosexual women in levels of
+other-objectification of their female partners in the measures section
+below.
 
@@
 we used the 10-item adaptation of P. Gray and M. OBrien (2007)'s Career
-Aspiration Scale employed in Garcia et al. (2016), which asked
-participants to consider how true 10 statements were in regard to their
-future careers on a scale from 0 (not at all true of me) to 4 (very true
-of me). Items include \enquote{I hope to become a leader in my career
-field} and \enquote{I hope to move up through any organization or
-business I work in.} Items were fairly reliable (\(\alpha\) = 0.73 for
-Sample 1, \(\alpha\) = 0.80 for Sample 2).
+Aspiration Scale which asked participants to consider how true 10
+statements were in regard to their future careers on a scale from 0 (not
+at all true of me) to 4 (very true of me). Items include \enquote{I hope
+to become a leader in my career field} and \enquote{I hope to move up
+through any organization or business I work in.} Items were fairly
+reliable (\(\alpha\) = 0.73 for Sample 1, \(\alpha\) = 0.80 for Sample
+2).
 
@@
 Trait self-objectification (TSO) was assessed using the
-Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; M.
-Noll \& L. Fredrickson, 1998), which evaluates the extent to which
+Self-Objectification Questionnaire (Barbara L Fredrickson et al., 1998;
+M. Noll \& L. Fredrickson, 1998), which evaluates the extent to which
 individuals view their bodies in observable versus non-observable ways.
@@
 the 5 physical self-concepts/appearance attributes (e.g., physical
-attractiveness, weight), and all measures were multiplied by -1, as was
-done in Garcia et al. (2016), so that positive scores indicated greater
-TSO.
+attractiveness, weight), and all measures were multiplied by -1 so that
+positive scores indicated greater TSO.
 
 \section{Results}\label{results}
-
-\subsection{Analysis Strategy}\label{analysis-strategy}
 
@@
 
+The R-package \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018)
+was used to create a fully reproducible research document containing the
+analysis code and manuscript text integrated into one source file. The
+benefit of this integration is that the numbers reported throughout this
+document are softcoded into the text, ensuring that no errors were made
+during a workflow marked by a copy-and-paste from statistical software
+to word processing software. Note that here we are using the term
+reproducibility to mean getting the same results when running analyses
+again using the same data, not to be confused with replicability meaning
+collecting a new dataset using the same methods and obtaining the same
+results (Patil, Peng, \& Leek, 2016). The source code for this
+manuscript along with survey materials and experimenter scripts for the
+study protocol are all avaliable at
+\url{https://github.com/kkyuchukova/object-in-action}. The data
+unfortunutely cannot be made publically avaliable given the dyadic
+nature of the observations. For example, with dyadic data, if a person
+who participated in the study found their own scores, using the dyad
+identification number, they could then see their partner's scores and
+thus confidentiality would be broken.
+
+\subsection{Analysis Strategy}\label{analysis-strategy}
+
 \begin{figure}
@@
 
-\begin{figure}
-\includegraphics[width=400px]{theor_figure} \caption{Theoretical Model from Garcia et al. (2016).}\label{fig:theorfigure}
-\end{figure}
-
 This study sought to detect whether partners' objectification of one
@@
 interested in testing the relationship between state-other
-objectification and SSO, and how SSO in turn, affects feelings of
-inauthenticity during the interaction. In addition, we also tested if
-the effect of other-objectification in an interaction on SSO is only
-present for those women who are high in trait self-objectification.
-Further, we investigated the relationships between experiencing
-interaction inauthenticity and relationship agency, career aspirations,
-and cognitive performance.
+objectification and SSO, and how SSO in turn, may or may not affects
+feelings of inauthenticity during the interaction. In addition, we also
+tested if the effect of other-objectification in an interaction on SSO
+is only present for those women who are high in trait
+self-objectification (moderation effect). Further, we investigated the
+relationships between experiencing interaction inauthenticity and
+relationship agency, career aspirations, and cognitive performance.
 
@@
 Structural Equation Modeling (SEM) than it is for indistinguishable
-dyads (e.g., same-gender interacting pairs), as we have here (Garcia,
-Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
-this asymmetry is that, due to the arbitrary distinctions made between
-\enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads,
-many estimates need to be fixed to be equal (i.e., paths, variances,
-covariances, endogenous intercepts, and exogenous means), but these
-equality constraints should not then be considered in the degrees of
-freedom calculations for fit estimations (Olsen \& Kenny, 2006).
-Further, Olsen and Kenny (2006) details how a new independence model and
-the corresponding fit measure should be re-calculated for
-indistinguishable dyads models. The current study uses dyadic multilevel
-modeling (MLM) to test all relationships and mediation patterns. The
-online supplementary materials contains analysis using SEM. See
-Ledermann and Kenny (2017) for a more complete discussion of the
-considerations for using SEM versus MLM for dyadic analysis.
-
-Testing our hypotheses in the current, same-gender, sample, involves
-using the Actor-Partner Independence Model (APIM) approach for each
-outcome variable (i.e., endogenous variable in
-Figure~\ref{fig:theorfigure}). Thus, we ran five APIM's to test all the
-hypothesized relationships. See Figure~\ref{fig:apim} for a basic APIM
-model. The APIM includes effects due to one's own, as well as one's
-partner's, predictor variables (\(X\)'s) on the one's own outcome
-variable (\(Y\)). The current study deals with indistinguishable dyads,
-meaning the designation of who is designated as \enquote{actor} and who
-is designated as \enquote{partner} is arbitrary. These analyses are
-considered exploratory, given the lack of prior research theorizing
-about these linkages.
+dyads (e.g., same-gender interacting pairs), as we had in the current
+study (Garcia, Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One
+reason for this asymmetry is that, due to the arbitrary distinctions
+made between \enquote{partner 1} and \enquote{partner 2} in
+indistinguishable dyads, many estimates need to be fixed to be equal
+(i.e., paths, variances, covariances, endogenous intercepts, and
+exogenous means), but these equality constraints should not then be
+considered in the degrees of freedom calculations for fit estimations
+(Olsen \& Kenny, 2006). Further, Olsen and Kenny (2006) details how a
+new independence model and the corresponding fit measure should be
+re-calculated for indistinguishable dyads models. The current study used
+dyadic multilevel modeling (MLM) to test all relationships, moderation,
+and mediation patterns. The online supplementary materials found at
+\url{https://github.com/kkyuchukova/object-in-action} contain model
+estimates obtained with SEM. See Ledermann and Kenny (2017) for a more
+complete discussion of the considerations for using SEM versus MLM for
+dyadic analysis.
+
+Testing hypotheses and exploring relationships in the current sample of
+indistinguishable dyads involved using the Actor-Partner Independence
+Model (APIM) approach for each outcome variable. The current study deals
+with indistinguishable dyads, meaning the designation of who is
+designated as \enquote{actor} and who is designated as \enquote{partner}
+is arbitrary. Thus, we ran five APIM's to test all the relationships
+(i.e., for SSO, inauthenticity, career aspirations, relationship agency,
+and cognitive performance as outcome variables). See
+Figure~\ref{fig:apim} for a basic APIM model. The APIM includes effects
+due to one's own, as well as one's partner's, predictor variables
+(\(X\)'s) on the one's own outcome variable (\(Y\)). The analysis of the
+relationship between SSO and inauthenticity in this same-gender sample
+are considered exploratory, given that prior research points to mixed
+possibilities.
 
@@
 \begin{figure}
-\includegraphics[width=400px]{SEMfigure} \caption{Path Analysis Model with Estimates}\label{fig:semfigure}
+\includegraphics[width=400px]{SEMfigure} \caption{This figure depicts the relationships tested bewteen study variables.
+The light gray variables represent redundant variables and are shown to emphasize the dyadic nature of the data.
+The estimates were from obtained from separate MLMs.
+Sample was controlled for in all models.
+The effects of TSO, actor other-objectification, and partner other-objectification are from a model where the interaction of TSO and partner other-objectification had been trimmed.
+*p < .05, dashed lines represent non-significant relationships.}\label{fig:semfigure}
 \end{figure}
 
-All model estimates and p-values are found in Table~\ref{tab:mlm} and
-the relationships with estimates included are depicted in
-Figure~\ref{fig:semfigure}.
+All relationships between study variables and the MLM estimates are
+depicted in Figure~\ref{fig:semfigure}.
 
@@
 it is \emph{women's} state self-objectification that relates to being
-objectified by one's partner. Objectification Theory (Roberts \&
-Fredrickson, 1997), as well as some past experimental studies (Saguy et
-al., 2010) suggest that at least one direction of the causal flow is
-from other-objectification to SSO. Other studies, especailly those
-investigating explicitly women objectifying other women (Puvia \& Vaes,
-2013), have relately found evidence that women's \emph{trait}
+objectified by one's partner. Objectification Theory (Barbara L
+Fredrickson \& Roberts, 1997), as well as some past experimental studies
+(Saguy et al., 2010) suggest that at least one direction of the causal
+flow is from other-objectification to SSO. Other studies, especailly
+those investigating explicitly women objectifying other women (Puvia \&
+Vaes, 2013), have relately found evidence that women's \emph{trait}
 self-objectification causes women to objectify (dehumanize) other women
@@
 suprising given the extant evidence linking SSO and cognitive
-functioning (B. L. Fredrickson et al., 1998; and see Moradi \& Huang,
-2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the research on
-interpersonal other-ojectification and cognitive functioning (Garcia et
-al., 2016; Gervais et al., 2011; Logel et al., 2009). This lack of
-evidence could potentially signal diverging processes between women's
-experiences with interpersonal objectification from men and
+functioning (Barbara L Fredrickson et al., 1998; and see Moradi \&
+Huang, 2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the
+research on interpersonal other-ojectification and cognitive functioning
+(Garcia et al., 2016; Gervais et al., 2011; Logel et al., 2009). This
+lack of evidence could potentially signal diverging processes between
+women's experiences with interpersonal objectification from men and
 interpersonal objectification from women. There is quite a bit of
 evidence suggesting that the male gaze is particularly detrimental
-(Calogero, 2004; Gervais, Holland, \& Dodd, 2013; Gervais et al., 2011;
-Roberts \& Fredrickson, 1997), and perhaps the self-objectification
-experienced within an interaction with a women is qualtatively
-different, and perhaps not as harmful, as the self-objectification
-experienced within an interaction with a man. However, as a strong note
-of caution, it is best not to interpret a null result as evidence of no
-relationship and more research on interpersonal objectification among
-women is needed.
+(Calogero, 2004; Barbara L Fredrickson \& Roberts, 1997; Gervais,
+Holland, \& Dodd, 2013; Gervais et al., 2011), and perhaps the
+self-objectification experienced within an interaction with a women is
+qualtatively different, and perhaps not as harmful, as the
+self-objectification experienced within an interaction with a man.
+However, as a strong note of caution, it is best not to interpret a null
+result as evidence of no relationship and more research on interpersonal
+objectification among women is needed.
 
@@
 social and cultural contexts, and hence are also constructed through
-sociocultural practices and discourses} (Roberts \& Fredrickson, 1997,
-p. 174), it is important to consider how diverse social identities
-within unique cultural contexts may inform sexual objectification
-phenomenon to test the cross-cultural applicability of theoretical
-frameworks (Loughnan et al., 2015b).
+sociocultural practices and discourses} (Barbara L Fredrickson \&
+Roberts, 1997, p. 174), it is important to consider how diverse social
+identities within unique cultural contexts may inform sexual
+objectification phenomenon to test the cross-cultural applicability of
+theoretical frameworks (Loughnan et al., 2015b).
 
@@
 research among younger and older individuals is needed, especially
-because self-objectification may change over time (Roberts \&
-Fredrickson, 1997). It may be valuable to question the extent to which
+because self-objectification may change over time (Barbara L Fredrickson
+\& Roberts, 1997). It may be valuable to question the extent to which
 children, adolescents, or emerging adults of different races or
@@
 and monotonous similarity,} and is thus mediated by unique combinations
-of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
-Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
-Nicholson (1989), p.~28). Amid such heterogeneity though,
-\enquote{having a reproductively mature female body} proposed by Roberts
-and Fredrickson (1997) is likely to create a shared vulnerability to
-sexual objectification and a variety of shared negative experiences as a
-result.
+of race, ethnicity, sexuality, age, and class (Barbara L. Fredrickson,
+Hendler, Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser
+and Nicholson (1989), p.~28). Amid such heterogeneity though,
+\enquote{having a reproductively mature female body} proposed by Barbara
+L Fredrickson and Roberts (1997) is likely to create a shared
+vulnerability to sexual objectification and a variety of shared negative
+experiences as a result.
 
@@
 
+\hypertarget{ref-robertsfredrickson}{}
+Fredrickson, B. L., \& Roberts, T.-A. (1997). Objectification theory:
+Toward understanding women's lived experiences and mental health risks.
+\emph{Psychology of Women Quarterly}, \emph{21}(2), 173--206.
+
 \hypertarget{ref-fredricksonetal2011}{}
@@
 
+\hypertarget{ref-kenny2006dyadic}{}
+Kenny, D. A., Kashy, D. A., \& Cook, W. L. (2006). \emph{Dyadic data
+analysis}. Guilford press.
+
 \hypertarget{ref-ledermann2017analyzing}{}
@@
 Social Psychology}, \emph{96}(6), 1089.
+
+\hypertarget{ref-loughnan2017internalizing}{}
+Loughnan, S., Baldissarri, C., Spaccatini, F., \& Elder, L. (2017).
+Internalizing objectification: Objectified individuals see themselves as
+less warm, competent, moral, and human. \emph{British Journal of Social
+Psychology}, \emph{56}(2), 217--232.
 
@@
 
+\hypertarget{ref-patil2016statistical}{}
+Patil, P., Peng, R. D., \& Leek, J. T. (2016). A statistical definition
+for reproducibility and replicability. \emph{BioRxiv}, 066803.
+
 \hypertarget{ref-R-nlme}{}
@@
 
-\hypertarget{ref-robertsfredrickson}{}
-Roberts, T.-A., \& Fredrickson, B. L. (1997). Objectification theory.
-\emph{Encyclopedia of Social Psychology}.
-doi:\href{https://doi.org/10.4135/9781412956253.n377}{10.4135/9781412956253.n377}
-
 \hypertarget{ref-rollero2016bringing}{}

### 2020-09-29 Final_Manuscript.Rmd
added csvs to gitignore

@@
 #SSO
+apim1_empty <- gls(howbody_avg_A ~ 1, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
+
 apim1 <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + a2pSOO_P*TSO_A + smith_or_clark, 
@@
 summary(apim1.b)
+summary(apim1_empty)
 
+apim1_r2 <- 1 - (1.094517/1.128858)
 ```
@@
 #authenticity
+apim2_empty <- gls(authenticity_A ~ 1, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
 apim2 <- gls(authenticity_A ~ howbody_avg_A + smith_or_clark, 
@@
 summary(apim2)
+summary(apim2_empty)
+apim2_r2 <- 1 - (1.029834/1.019483)
 
@@
 #cognitive performance
+apim3_empty <- gls(trigram_score_A ~ 1, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
 apim3 <- gls(trigram_score_A ~ authenticity_A + smith_or_clark, 
@@
 summary(apim3)
+summary(apim3_empty)
+apim3_r2 <- 1 - (2.320106/2.295617)
 
@@
 #relationship agency
+apim4_empty <- gls(relag_A ~ 1, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
 apim4 <- gls(relag_A ~ authenticity_A + smith_or_clark, 
@@
 summary(apim4)
+summary(apim4_empty)
+apim4_r2 <- 1 - (0.9420959/0.9556186)
 
@@
 #career aspirations
+apim5_empty <- gls(careerasp_A ~ 1, 
+                 na.action=na.omit, 
+                 correlation=corCompSymm (form=~1|dyadID),
+                 data=clarksmith_women)
 apim5 <- gls(careerasp_A ~ authenticity_A + smith_or_clark, 
@@
 summary(apim5)
+summary(apim5_empty)
+apim5_r2 <- 1 - (0.5816273/0.6068203)
 

### 2020-09-29 SEM analysis supplement/SEM Proposal.Rmd
rename coursework file to sem supplement

---
title: "Objectification in Same-Sex Pairs: Proposal"
author: "Kat Kyuchukova & Asha Hinson"
date: "3/3/2019"
output: html_document
---
##Purpose
Sexual objectification, the process by which a woman’s whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, is a phenomenon that undoubtedly results in a variety of negative outcomes (Bartky, 1990). Fredrickson and Roberts (1997) highlight the objectification theory as a framework that works to place female bodies within a sociocultural context with the intention of illuminating the lived experiences and risks of women who encounter sexual objectification on a daily basis, such as their physical, psychological, and social well-being. A critical consequence of being viewed by others in ways that are sexually objectifying is that, over time, individuals may be influenced to internalize an observer's perspective on self, an effect termed trait self-objectification. Thus, the purpose of this statistical study is to explore whether partners’ objectification of each other affects trait self-objectification, and the resulting feelings of authenticity. Furthermore, this project is additionally interested in the links between exposure to sexual objectification experiences, authenticity, and postinteraction outcomes including feelings of agency in romantic relationships, career aspirations, and cognitive performance, within a same-sex interaction (Quinn, Kallen, Twenge, & Fredrickson, 2006). Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships (Lamb, 2010), adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance (Swim, Hyers, Cohen, & Ferguson, 2001). By using dyadic analysis, we expect to find results consistent with previous literature to illustrate that self-objectification is both a self and interpersonal process, heightened by the real-time sexual objectification of a female interaction partner.

##Data/Population

The data collected in this study sought to replicate Garcia et al. (2016), which sought to measure objectification in previously unacquainted male-female pairs. This data was given to us by Dr. Garcia, who collected data from both Smith College and Clark University. The data was ultimately merged and filtered to only include only self-identified female same-sex pairs from both schools. The two samples are often referred to below as Sample 1 (data from Clark University) and Sample 2 (data from Smith College). These participants were mostly first-year college students, with an average age of 18.85 years (SD=1.04). The sample was 48% White/European American, 9% Black/African-American, 28% Asian/Pacific Islander, 9% Latinx, and 5% mixed-race. There were eight White/White pairs and four same race racial minority pairs, for a total of twelve same-race pairs. The remaining twenty were mixed race pairs, of which fifteen were White/racial minority pairings and five were cross-racial minority group pairs. 64% of the sample identified as heterosexual, and 23% identified as gay, lesbian or bisexual. The data is organized in a pairwise fashion such that each row corresponds to one participant in the study, and includes data for themselves and their partner. We would want to generalize these findings to general interactions between women.

##Model

![](/Users/katerinakyuchukova/Downloads/SEMmodel.jpg)

All variables in this model are measured. The endogenous variables are actor/partner SSO, authenticity, cognitive performance, career aspirations and relationship agency. The exogenous variables are actor/partner trait self-objectification, and actor objectification of partner and vice versa, as well as the interaction between the two.

The variables are as follows:

#####TSO. 
TSO was assessed using the Self-Objectification Questionnaire (Fredrickson et al., 1998; Noll & Fredrickson, 1998). This asks participants to rank order functional aspects of their bodies as well as physical self-concepts. The average rank of the functional aspects is then subtracted from the rank of the physical self-concepts. As was done in Garcia et al. (2016), all measures are multiplied by -1 so that positive scores correspond to more TSO.

#####Cognitive performance. 
Cognitive performance was assessed using trigrams from the Remote Associates Task (McFarlin & Blascovich, 1984). Ten items were selected and presented to participants. For example, the correct answer for the trigram “Quack: Pond: Waddle” would be “Duck”. Participants are limited to 30 seconds. For every correct answer, 1 point is given. The mean score was 5.03. Cognitive performance was measured first in order to measure potential immediate detriments to performance (Garcia et al., 2016).

#####SOO.
To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts of several aspects of their partner (Garcia et al., 2016). Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts. All questions were to be rated on a scale from 1 (not at all) to 7 (constantly). Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits (α=.78 for Sample 1, α=.74 for Sample 2) and frequency of thought about their partner’s internal traits (α=.70 for Sample 1, α=.78 for Sample 2). A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.

#####Interaction Authenticity. 
Just like Garcia et al. (2016), we assessed the extent to which participants felt comfortable in the interaction and felt it was authentic. We did this by asking them to rate the extent to which they felt the interaction was comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale from 1 (not at all) to 7 (very much). Participants were also asked whether they thought their partner was authentic in the interaction, and if they felt they were authentic in the interaction. These questions were ranked on a scale from 1 (not authentic at all). These were combined to form the authenticity scale (α=.91).

#####SSO. 
To assess state self-objectification, we used an average of two items from Saguy et al. (2010) that was also used in Garcia et al. (2016). Participants were asked to rank how much they agreed with the following statements: “During the interaction I felt more like a body than a full self” and “I felt more like a body than as a real person in the interaction”. Saguy et al. (2010) originally used 3 items, but the 3rd item had a low reliability score (r=*), so we chose to only use the first two for our measure of SSO.

#####Relationship Agency.
To assess how much relationship agency participants felt they would have in future relationships, we used the scale from Garcia et al. (2016), asking how likely it was that they would do the following: ‘‘ask someone out on a date,’’ ‘‘open the door for your date,’’ ‘‘pay for a date,’’ ‘‘ask your boyfriend/girlfriend to marry you,’’ ‘‘initiate sex with your girlfriend/boyfriend,’’ ‘‘initiate condom use during sex,’’ ‘‘surprise your boyfriend/ girlfriend with a gift,’’ and ‘‘ask your girlfriend/boyfriend to move with you to a new place.’’ Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely). This item had high reliability for Sample 1 (α=0.73) but low reliability for Sample 2 (α=0.58).

#####Career Aspirations.
To measure career aspirations, we used the 10-item adaptation of Gray & O’Brien (2007)’s Career Aspiration Scale used in Garcia et al. (2016). This asked participants how true statements were about their future careers on a scale from 0 (not at all true of me) to 4 (very true of me). Items include ‘‘I hope to become a leader in my career field’’ and ‘‘I hope to move up through any organization or business I work in.’’ Items were fairly reliable (α=0.72 for Sample 1, α=0.81 for Sample 2).

### 2020-09-29 Final_Manuscript.Rmd
more cleaning

@@
 ```{r data}
-clark_final <- read.csv("Cleaned data/clark_final.csv")
-smith_final <- read.csv("Cleaned data/smith_final.csv")
-clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
+clark_final <- read.csv("Cleaned-data/clark_final.csv")
+smith_final <- read.csv("Cleaned-data/smith_final.csv")
+clarksmith_women <- read.csv("Cleaned-data/clarksmith_women.csv")
 ```
@@
 ```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
-include_graphics("APIM_figure.png")
+include_graphics("figures/APIM_figure.png")
 ```
@@
 *p < .05, dashed lines represent non-significant relationships."}
-include_graphics("SEMfigure.png")
+include_graphics("figrues/SEMfigure.png")
 ```

### 2020-09-29 Variable creation.Rmd
more cleaning

@@
 #clark
-clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
-clark_pairwise <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")
+clark_measures <- read_spss("Raw-data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
+clark_pairwise <- read_spss("Raw-data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")
 
 #smith
-smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")
+smith <- read_spss("Raw-data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")
 
-clark_sentences <- read.csv("Raw data/Clark College Relationships Data/sexist sentences/coded_sentences.csv")
+clark_sentences <- read.csv("Raw-data/Clark College Relationships Data/sexist sentences/coded_sentences.csv")
 
 #trigrams
-trigram_check <- read.csv("Raw data/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
+trigram_check <- read.csv("Raw-data/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
 ```
@@
 #Write out csv with created variables
-#write.csv(clark_measures, "Cleaned data/clark_measures.csv")
-#write.csv(smith, "Cleaned data/smith.csv")
+#write.csv(clark_measures, "Cleaned-data/clark_measures.csv")
+#write.csv(smith, "Cleaned-data/smith.csv")
 ```
@@
 ##Write out file to grade
-#write.csv(smith_trigrams_long, "Raw data/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)
+#write.csv(smith_trigrams_long, "Raw-data/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)
 
 #Read in graded trigram file
-smith_trigrams_graded <- read.csv("Raw data/Smith College Relationships Data/trigrams_graded.csv")
+smith_trigrams_graded <- read.csv("Raw-data/Smith College Relationships Data/trigrams_graded.csv")
 
@@
 #Write out csv
-#write.csv(smith_sentences_long, "Raw data/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)
+#write.csv(smith_sentences_long, "Raw-data/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)
 
 #Read in coded sentences, code correlations
-kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")
-xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")
+kat_codes <- read.csv("Raw-data/Smith College Relationships Data/kat_recode.csv")
+xinyu_codes <- read.csv("Raw-data/Smith College Relationships Data/xinyu_recode.csv")
 
@@
 
-Write out cleaned data!
+Write out Cleaned-data!
 ```{r}
-write.csv(smith_final, "Cleaned data/smith_final.csv" )
-write.csv(clark_final, "Cleaned data/clark_final.csv")
+write.csv(smith_final, "Cleaned-data/smith_final.csv" )
+write.csv(clark_final, "Cleaned-data/clark_final.csv")
 ```

### 2020-09-29 Final_Manuscript.Rmd
sem supplement cleaning

@@
   - name          : "Kat Kyuchukova"
-    affiliation   : "1"
+    affiliation   : "1, 2"
   - name          : "Asha Hinson"
@@
   - name          : "Laneé Jung"
-    affiliation   : "1"
+    affiliation   : "2"
 
@@
 *p < .05, dashed lines represent non-significant relationships."}
-include_graphics("figrues/SEMfigure.png")
+include_graphics("figures/SEMfigure.png")
 ```

### 2020-09-29 Final_Manuscript.tex
sem supplement cleaning

@@
     \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
-Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \& Laneé
-Jung\textsuperscript{1}}
+Kyuchukova\textsuperscript{1, 2}, Asha Hinson\textsuperscript{1}, \&
+Laneé Jung\textsuperscript{2}}
     \date{}
@@
 \begin{figure}
-\includegraphics[width=400px]{APIM_figure} \caption{Basic actor-partner interdependence model (APIM) depiction.}\label{fig:apim}
+\includegraphics[width=400px]{figures/APIM_figure} \caption{Basic actor-partner interdependence model (APIM) depiction.}\label{fig:apim}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=400px]{SEMfigure} \caption{This figure depicts the relationships tested bewteen study variables.
+\includegraphics[width=400px]{figures/SEMfigure} \caption{This figure depicts the relationships tested bewteen study variables.
 The light gray variables represent redundant variables and are shown to emphasize the dyadic nature of the data.

### 2020-09-29 SEM analysis supplement/Final Manuscript.Rmd
sem supplement cleaning

--- 2020-06-30 Old coursework files/Final Manuscript.Rmd
@@
 ---
-title             : "Objectification in Action: Self- and Other-Objectification in Same-gender Interactions"
-shorttitle        : "Objectification in Action"
+title             : "Objectification in Action: SEM Supplement"
+shorttitle        : "SEM Supplement"
 
@@
 library(xtable)
-clark_measures <- read.csv("Cleaned data/clark_measures.csv")
-smith <- read.csv("Cleaned data/smith.csv")
-clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
+clark_measures <- read.csv("../Cleaned-data/clark_final.csv")
+smith <- read.csv("../Cleaned-data/smith_final.csv")
+clarksmith_women <- read.csv("../Cleaned-data/clarksmith_women.csv")
 ```
@@
 Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and will more than likely internalize the objectifying gaze on physical self [@young1979].
-Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998].
+Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredrickson1998swimsuit].
 Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008].
@@
 ###Trait Self-Objectification
-Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
+Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredrickson1998swimsuit; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus nonobservable ways.
 The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
@@
 This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used dyadic analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO).
-See Figure\ \@ref(fig:2016figure) for the path analysis results of the previous study.
 We hope to investigate how the main effects found in the previous study relay to interactions between women: specifically, the relationship between state-other objectification and self-state objectification and the resulting effect of self-state objectification on inauthenticity during the interaction.
@@
 ```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
-include_graphics("APIM_figure.png")
+include_graphics("../figures/APIM_figure.png")
 ```
@@
 ```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
-include_graphics("2016_figure.jpg")
+#include_graphics("../figures/2016_figure.jpg")
 ```
@@
 ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
-include_graphics("SEMfigure.png")
+include_graphics("../figures/SEMfigure.png")
 ```

### 2020-09-29 SEM analysis supplement/Final-Manuscript.tex
sem supplement cleaning

--- 2020-09-17 Final_Manuscript.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
-            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
+            pdftitle={Objectification in Action: SEM Supplement},
+            pdfauthor={Kat Kyuchukova, Asha Hinson, \& Randi L. Garcia},
             pdfkeywords={keywords},
@@
 
-  \title{Objectification in Action: Self- and Other-Objectification in
-Same-gender Interactions}
-    \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
-Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \& Laneé
-Jung\textsuperscript{1}}
+  \title{Objectification in Action: SEM Supplement}
+    \author{Kat Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \&
+Randi L. Garcia\textsuperscript{1}}
     \date{}
 
-\shorttitle{Objectification in Action}
+\shorttitle{SEM Supplement}
 \affiliation{
 \vspace{0.5cm}
-\textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
+\textsuperscript{1} Smith College}
 \keywords{keywords}
@@
 
-Correspondence concerning this article should be addressed to Randi L.
-Garcia, 415 Bass Hall, Smith College, Northampton, MA 01060. E-mail:
-\href{mailto:rgarcia@smith.edu}{\nolinkurl{rgarcia@smith.edu}}}
+Correspondence concerning this article should be addressed to Kat
+Kyuchukova, Postal address. E-mail:
+\href{mailto:my@email.com}{\nolinkurl{my@email.com}}}
 
 \abstract{
-Empirical evidence has only found links between objectification,
-self-objectification, and negative outcomes for women within
-interpersonal interactions between male-female pairs. The purpose of the
-present study was to extend past research and consider the relationships
-between objectification and self-objectification within interactions
-between female pairs. Women were brought into the laboratory and
-interacted in same-sex dyads. Dyadic analysis was utilized to detect
-whether partners' objectification of each other affected state
-self-objectification, as well as the resulting feelings of comfort and
-authenticity during the interaction. After the interaction, participants
-completed a questionnaire measuring, among other things, cognitive
-performance, career aspirations, and relationship agency. Results
-revealed a significant positive effect of being objectified by a female
-partner on women's self-objectification. There was no significant
-relationship between self-objectification and authenticity. Further,
-although there were significantly negative effects on career aspirations
-and relationship agency resulting from a lack of relationship
-authenticity, there was no evidence that this is due to feelings of
-sexual objectification. The significant partner effect of
-objectification on actor self-objectification suggests that women being
-objectified by other women may result in feelings of
-self-objectification, and such research has powerful implications for
-the ways that women interact in both sexual and non-sexual settings.
+Objectification theory is a valuable framework for conceptualizing the
+psychological consequences of being female within a society that
+sexually objectifies the female body, and considering the ways in which
+girls and women are acculturated to then internalize an observer's
+perspective as a primary view of their appearance. Empirical evidence
+has largely elucidated links between objectification,
+self-objectification, and negative outcomes for woman within
+interpersonal interactions between male-female pairs particularly. The
+purpose of the present study was to extend past research and consider
+the relationships between such valuable phenomena and their effects on
+authenticity within interactions between female pairs. Woman were
+brought into the laboratory and interacted in same-sex dyads. Dyadic
+analysis was utilized to detect whether partners' objectification of
+each other affected state self-objectification, and the resulting
+feelings of comfort and authenticity during the interaction. After the
+interaction, participants completed a questionnaire which measured many
+constructs including cognitive performance, career aspirations, and
+relationship agency. Results revealed no significant relationship
+between self-objectification and authenticity. Further, although there
+were significantly negative effects on career aspirations and
+relationship agency resulting from a lack of relationship authenticity,
+there was no evidence that this is due to feelings of sexual
+objectification. The significant partner effect of objectification on
+actor self-objectification suggests that women being objectified by
+other women still results in feelings of self-objectification, and such
+research has powerful implications for the ways that women interact in
+both sexual and non-sexual settings.
 
@@
 
-Roberts and Fredrickson (1997) Objectification Theory, suggests that, in
-addition to being steeped in a culture that objectifies women, women are
-objectified in actual interpersonal encounters. The negative effects of
-this interpersonal objectification for women are theorized be the
-strongest when it is a man doing the objectifying (Calogero, 2004; Gay
-\& Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
-consequences when a woman objectifies another woman in an interaction?
-Psychological researchers studying the sexual objectification of women,
-have in recent years explored the interpersonal process of the
-objectification, finding evidence for self-objectification in the target
-as a proximal consequence of being objectified (Garcia, Earnshaw, \&
-Quinn, 2016, Strelan and Pagoudis (2018), Riemer, Sáez, Brock, and
-Gervais (2020)). In a recent review, Gervais, Sáez, Riemer, and Klein
-(2020) organized the extant literature on interpersonal
-self-objectification and proposed a theoretical model called the Social
-Interaction Model of Objectification (SIMO), however this model focuses
-on mixed-gender encounters. Although there is evidence that women
-objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013),
-there are currently no studies investigating the process of
-interpersonal objectification in interactions between women. Is
-objectification by a female interaction partner related to an increase
-in self-objectification for the woman being objectified? Further, does
-objectification by a woman have the same downstream negative
-consequences for women as being objectified by a male interaction
-partner? The current study begins to address these questions by
-investigating interpersonal objectification among interacting pairs
-where both partners identify as women.
-
-\subsection{Self-Objectification}\label{self-objectification}
-
-Self-objectification is a psychological process that provides a
-cognitive mechanism to translate the experiences of interpersonal
-objectification (Loughnan et al., 2015a) to negative mental health
-outcomes (e.g., anxiety, self-esteem, and cognitive performance)
-(Calogero, Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008).
-Calogero et al. (2011) proposes that self-objectification can be
-conceptualized as a learned trait, or \emph{trait} self-objectification
-(TSO). Furthermore, self-objectification can also be elicited
-momentarily, for example, when viewing sexualized images in movies and
-magazines (Morry \& Staska, 2001), when trying on sexualizing clothing
-(B. L. Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998), or during
-video chat when you believe your interaction partner can only see your
-body (not face; Saguy, Quinn, F Dovidio, \& Pratto, 2010). This
-momentary self-objectification is referred to as \emph{state}
-self-objectification (SSO; Bernard, Legrand, \& Klein, 2018; Calogero et
-al., 2011; Moradi \& Huang, 2008) and is characterized by feeling like a
-body rather than a full self within a particular moment, instance, or
-context (Roberts \& Fredrickson, 1997).
-
-There is evidence that being objectified by another person during an
-interaction elicits SSO. For example, in a face-to-face mixed-gender
-dyadic study, Garcia et al. (2016) found that men's reported
-objectification of their female interaction partner was associated with
-increased self-objectification as reported by their female partner.
-Further, this negative effect of the men's objectification on women's
-SSO was strongest for women higher in TSO. The current study uses this
-same dyadic paradigm to study same-gender, woman-woman interacting
-pairs.
-
-\subsection{Interpersonal
-Objectification}\label{interpersonal-objectification}
-
-Studies have shown that within social encounters women are gazed at more
-than men (Briton \& Hall, 1995), often times feel \enquote{looked at}
-within interpersonal interactions (Argyle \& Williams, 1969;
-Miles-McLean et al., 2015), and are likely to internalize the
-objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
-1979). Interpersonal objectification has been found to have negative
-consequences for women. Gervais et al. (2011) found that an objectifying
-gaze by a male interaction partner (confederate) was associated with
-lower math performance for women, than being objectified by a female
-interaction partner. Moreover, perhaps the most adverse effect of
-interpersonal objectificaiton is that being objectified socializes girls
-and women to treat themselves as objects to be looked at and evaluated
-(Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et
-al., 1998). Gervais et al. (2020) recently reviewed the research on
-interpersonal objectification and organized our current theoretical
-understanding of this process in the Social Interaction Model of
-Objectification (SIMO). What is clear from Gervais et al. (2020)'s
-review is that we know little about women-on-women interpersonal
-objectification. Could there also be negative consequences of this type
-of interpersonal objectification?
-
-Interpersonal objectification can also occur within the context of
-romantic relationships, in addition to interactions with strangers.
-Among heterosexual male and female college students,
-self-objectification has been found to be positively associated with the
-extent to which they objectify their romantic partners (Zurbriggen,
-Ramsey, \& Jaworski, 2011). Researchers have also studied interpersonal
-objectification and self-objectification in romantic relationships
-(Strelan \& Pagoudis, 2018). Evidence is mixed, suggesting that women
-can sometimes have positive outcomes from appearance valuation within
-the context of an established romantic relationship. There is also
-evidence that they experience less SSO after appearance comments within
-romantic relationships (Meltzer, 2020), but less is known about first
-dates. An important caveat to this literature is that it is only about
-heterosexual relationships. A recent study has investigated the effect
-of self-objectification on the reduction of relationship building skills
-in general (including same-sex friendships) (Terán, Jiao, \& Aubrey,
-2020). Both romantic relationships and stranger encounters have been
-studied in the context of objectification, but neither of these
-literatures have investigated specifically same-gender relationships.
-
-There is evidence that the experience of state self-objectification in
-mixed-gender contexts (stranger and romantic) has negative consequences
-for women, but what about in the context of interactions with other
-women? Is the self-objectification experienced in mixed-gender
-interactions associated with the same negative process as that
-experienced in same-gender interactions? The ample research
-demonstrating that the male gaze has a particularly detrimental effect
-for women would suggest no (Gay \& Castano, 2010; Gervais et al., 2011;
-Saguy et al., 2010, Calogero (2004); Yilmaz \& Bozo, 2019), but, there
-is evidence that women do objectify other women (Harsey \& Zurbriggen,
-2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and to would be
-helpful to understand the consequencs of this intragroup objectification
-for women. When women objectify other women, does it lead to
-self-objectification in the same way men's objectification of women does
-(Garcia et al., 2016)? If so, does the self-objectification experienced
-in these same-gender interactions have the same negative consequences
-for authenticity in that interaction?
-
-There is some evidence that reduced authenticity is a consequence of
-self-objectification (Garcia et al., 2016; Terán et al., 2020). This
-link has been justified by the literature on stigmatized-stigmatizer
-interactions (M. R. Hebl \& Dovidio, 2005; Richeson \& Shelton, 2003;
-Shelton, Richeson, \& Salvatore, 2005), viewing the experience of being
-objectified in an interaction as an identity threat situation
-(Miles-McLean et al., 2015; Nadal \& Haynes, 2012). Further, empirical
-evidence reveals that objectification manifests through inauthenticity
-in romantic relationships (Brunell et al., 2010), adverse attitudes in
-regard to career aspirations, and a decrease in concentration and
-impairment in female cognitive performance (Kahalon, Shnabel, \& Becker,
-2018; D. M. Quinn, Chaudoir, \& Kallen, 2011). When a woman is
-objectified by a man, and subsequently experiences self-objectification,
-the intergroup nature of this encounter might trigger identity threat.
-Thus, perhaps there are fewer negative consequences when a woman is
-objectified by another woman, specifically, woman-woman interpersonal
-objectification processes might diverge from mix-gender interpersonal
-objectification processes precisely because they are not intergroup
-interactions (at least with respect to gender identity). A woman
-objectified by another woman may not be having the same negative
-consequences that cascade from situations that trigger group-based
-identity threat (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \&
-Shelton, 2006; M. R. Hebl \& Dovidio, 2005), but feeling like a body,
-rather than a full human, in any interaction (intergroup or ingroup) may
-be enough to reduce women's feelings of authenticity and social
-competence, regardless of the gender of the objectifyer (Terán et al.,
-2020; Tolman, Impett, Tracy, \& Michael, 2006).
-
-\subsection{Women Objectifying Women}\label{women-objectifying-women}
-
-Past research investigating women objectifying other women has focused
-on the psychological conditions that led women to objectify women.
-Harsey and Zurbriggen (2020) found that self-objectification was related
-to the objectification of women to a similar degree for male and female
-participants. Along the same lines, Strelan and Hargreaves (2005) found
-that the more women self-objectify, the more they objectify other women.
-Could the process work in the other direction as well, that is, could
-objectification by a woman produce self-objectification, in a similar
-manner to objectification by a man? Hill and Fischer (2008) assessed
-women's experiences of objectification from men independently from
-women's experiences of objectification from other women. They found that
-women may be socialized not only to see themselves as objects, but
-perhaps to see other women as objects as well. This process, however,
-was not comfirmed to occur during an actual interpersonal interaction.
-Loughnan et al. (2015a) found that women objectify other women to a
-greater extent than they objectify men. Women have also been found to
-objectify (dehumanized) sexualized targets presented as images (Puvia \&
-Vaes, 2013), but very little is known about interpersonal sexual
-objectification among women and what the proximal effects of this
-objectification might be. We do know that objectification has more
-adverse consequences for women than men (Gervais et al., 2011; Moradi \&
-Huang, 2008; Saguy et al., 2010), however, if women objectify other
-women, perhaps even to a stronger degree than they objectify men, this
-woman to woman objectification might have detrimental outcomes.
-
-\subsection{The Current Study}\label{the-current-study}
-
-In the current study, we sought to examine what occurs during an
-interaction in which one or both partners are objectifying each other,
-similarly to Garcia et al. (2016), but between same-gender interpersonal
-interactions among women. Moreover, the current study uses a
-face-to-face interaction paradigm and dyadic data analysis techniques to
-examine the effects for both women simultaneously. Although the
-literature on woman-woman objectification is small, the results are
-mixed, and does not cover interpersonal encourters, we expected to
-replicate some of the results found in Garcia et al. (2016). Most
-importantly, we predicted that being objectified by one's interaction
-partner would lead to self-objectification. We also expected that TSO
-would moderate this relationship, amplifying the positive assocaition
-between being objectified and SSO for women higher in TSO. We
-hypothesized that SSO would, in turn, lead to feelings of inauthenticity
-(although there is ample support against this prediction from the
-identity threat within intergroup interactions literature; Rollero,
-2016). Further, we hypothesized that these feelings of inauthencity
-would then be associated with reduced feelings of agency in romantic
-relationships, reduced career aspiration, and reduced cognitive
-performance. In summary, we expected to find a positive relationship
-between other-objectification by one's partner and state
-self-objectification. We also expected to find a negative relationship
-between self-state objectification and interaction authenticity, and
-that interaction authenticity will be positively related to cognitive
-performance, relationship agency, and career aspirations.
-
-These hypotheses are considered exploratory, given the lack of prior
-research theorizing about these linkages.
-
-Here we would like to note that Puvia and Vaes (2013) would
-alternatively predict that women's tendency to self-objectify (TSO)
-leads them to objectify other women (more precisely, to dehumanize a
-sexualized woman). In addition, Strelan and Hargreaves (2005) and Harsey
-and Zurbriggen (2020) would predict the TSO to other-objectification
-link, further theorizing that this relationships is mediated by the
-woman's own state self-objectification (SSO). This limited, but extant,
-set of literature on woman-woman objectification points to a possible
-alternative model from the model hypothesized in the current study.
-Where appropriate, we report results considering the causal directions
-implied by this alternative mediation model.
+\section{Introduction}\label{introduction}
+
+Theorists across diverse disciplines have explored the multiple ways
+that the body conveys social meaning, as well as how these meanings
+shape gendered experiences and therefore inform individuals' thinking,
+feeling, and behavior, especially during interpersonal interactions with
+members of different social groups (``Engendered lives,'' 1993).
+Empirical evidence illustrates how women, in particular, continue to be
+objects of perpetual discrimination as a result of psychosocial markers,
+like gender, that produce modes through which their identity is
+understood (Swim, Hyers, Cohen, \& Ferguson, 2001). Objectification
+theory, a valuable theoretical framework proposed by Barbara L
+Fredrickson and Roberts (1997) which works to contextualize female
+bodies as socio-cultural constructions, can be employed to illuminate
+the gender oppression and negative lived experiences of girls and women.
+Additionally, one of the most detrimental forms of discrimination
+against them is thought to be the process by which their whole being is
+viewed as a collection of sexualized body parts valued predominantly for
+commodification, a phenomena termed sexual objectification (Bartky,
+1990). Sexual objectification occurs with both \enquote{endless variety
+and monotonous similarity,} and is thus mediated by unique combinations
+of race, ethnicity, sexuality, age, and class (Barbara L. Fredrickson,
+Hendler, Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser
+and Nicholson (1989), p.~28). Amid such heterogeneity though,
+\enquote{having a reproductively mature female body} proposed by Barbara
+L Fredrickson and Roberts (1997) is likely to create a shared
+vulnerability to sexual objectification and a variety of shared negative
+experiences as a result. Studies have shown that within social
+encounters women are gazed at more than men (Briton \& Hall, 1995),
+often times feel \enquote{looked at} within interpersonal interactions
+(Argyle \& Williams, 1969), and will more than likely internalize the
+objectifying gaze on physical self (Young, 1979). Moreover, perhaps the
+most adverse effect of objectifying treatment is that it effectively
+socializes girls and women to treat themselves as objects to be looked
+at and evaluated, an effect termed self-objectification (Bartky, 1990;
+Berger, Cohen, \& Zelditch Jr, 1972; Barbara L Fredrickson, Roberts,
+Noll, Quinn, \& Twenge, 1998). Self-objectification is a
+multidimensional process that accounts for the cognitive mechanism that
+translates experiences of sexualization at the cultural level to
+psychological (e.g., anxiety, self-esteem, authenticity, motivational
+states) and behavioral (cognitive performance, body monitoring) features
+of mental health and well-being at the individual level (Calogero,
+Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008). Calogero et
+al. (2011) proposes that the construct of self-objectification can be
+conceptualized as a learned trait. Furthermore, it can also be elicited
+momentarily, through the media, for example, with sexualized images in
+movies and magazines, which can lead to a state of self-objectification
+(Calogero et al., 2011, Moradi and Huang (2008)). Being objectified by
+another person and possessing trait-level self-objectification (TSO) may
+interact to influence experiences of feeling like a body, or state
+self-objectification (SSO). In the current work, we sought to examine
+what occurs during an interaction in which one or both partners are
+objectifying each other, similarly to Garcia, Earnshaw, and Quinn
+(2016), but between same-sex female interpersonal interactions. We
+predicted that being objectified by one's interaction partner would lead
+to self-objectification, in addition to modified feelings of
+authenticity in postinteraciton outcomes, including feelings of agency
+in romantic relationships, career aspiration, and cognitive performance
+(D. M. Quinn, Chaudoir, \& Kallen, 2011). Empirical evidence reveals
+that objectification manifests through inauthenticity in romantic
+relationships (Brunell et al., 2010), adverse attitudes in regard to
+career aspirations, and a decrease in concentration and impairment in
+female cognitive performance (Swim et al., 2001). Moreover, it was the
+goal of this research to empirically explore the role of interaction
+authenticity in objectification by utilizing a structural equation
+modeling to examine the effects for both women simultaneously. We
+expected to replicate the results found in the previous Garcia et al.
+(2016) study. More specifically, we expected to find a positive
+relationship between state-other objectification and self-state
+objectification, and a resulting negative relationship between
+self-state objectification and interaction authenticity. Finally, we
+expected there to be a positive relationship between interaction
+authenticity and cognitive performance, relationship agency, and career
+aspirations.
 
@@
 
-Except for the instructions given to participants, the procedure used
-was identical to that in Garcia et al. (2016). In brief, that
+The procedure used was identical to that in Garcia et al. (2016), except
+for the instructions that the participants were given. In brief, that
 methodology is that each participant arrived at the laboratory and were
@@
 
-\begin{quote}
 There are many types of relationships people form in college. During the
 interaction, please think about your partner's potential as a romantic
-partner. \textbf{Even if they are not the gender you are attracted to},
-you can still judge their potential as a romantic partner. After the
-interaction you will be asked to evaluate how dateable your partner is.
-In other words, we would like to know if you think someone would date
-your interaction partner. Also, your interaction partner will be
-evaluating you in the same manner.
-\end{quote}
-
-\emph{All} participants were told that they were assigned to the
-\enquote{College Relationships} condition. Self-objectification has been
-found to occur after a mere relationship prime among women (Sanchez \&
-Broccoli, 2008) because, in Westurn culture and beyond, women need to
-look attractive to obtain and maintain successful relationship, thus,
-the \enquote{College Relationships} condition may heighten
-self-objectification and the evaluation of other women in a sexualized
-way. The decision was made to ask even heterosexual women to judge their
-fellow-woman partners for their potential as romantic partners. We felt
-that this prompt would keep the study closest to a replication of the
-previous Garcia et al. (2016) version of the study, and strengthen the
-potential for objectification that would normally be low in the context
-of a psychology laboratory. Recall that, past research has found that
-heterosexual women are indeed able to evaluate other women's potential
-as romantic partners (i.e., their sexual attractiveness; Puvia \& Vaes,
-2013)---indeed, women may be unfortunately quite used to thinking about
-their own \enquote{datability,} and we suspect this this habitual
-thought pattern will translate to their thoughts about other women.
-
-After recieving the \enquote{College Relationships} prompt, the two
-participants were then brought into a larger interaction room where they
-sat on stools prearranged to be approximately 1 meter apart. The
-experimenter instructed the participants to \enquote{get to know each
-other} for 10 minutes and then left the room. After 10 minutes, the
-experimenter came back into the room and stopped the interaction. The
-participants then went back to their individual cubicles and completed a
-set of post-interaction measures. Participants were then thanked for
-their participation and debriefed. More detail on this methodology can
-be found in Garcia et al. (2016).
-
-\subsection{Participants}\label{participants}
-
-Data from two demographically similar higher education institutions in
-the Northeast United States were combined to create the final analysis
-sample (\emph{N =} 64) used in this study. In the measures section that
-follows we refer to them as Sample 1 and Sample 2. Thirty-two previously
-unacquainted self-identifying female dyads (64 total participants) from
-institutions in the Northeast of the United States participated in this
-study. Sample 1 (\emph{N =} 24) is from a co-ed liberal arts college and
-Sample 2 (\emph{N =} 40) is from a women's liberal arts college. More
-specifically, twelve of the pairs were students at a co-ed liberal arts
-college, while the remaining twenty pairs attended a women's liberal
-arts college. {[}Footnote: Initially, data was collected from same-sex
-and mixed-sex dyads that comprised of male and female gendered
-individuals. Sample 1 originally consisted of twenty-two pairs, twelve
-men and thirty-two women. Twenty-three pairs made up of forty-three
-women and one man, as well as two participants who did not identify with
-either gender category, formed Sample 2. For consistency, we limited
-participant data to same sex female pairs at the two colleges.{]} All
-results presented below are from models including sample as a control
-variable.
-
-The participants were mostly first-year college students, with an
-average age of 18.85 (SD = 1.04). The sample was 48.44\% White/European
-American, 9.38\% Black/African-American, 28.12\% Asian/Pacific Islander,
-9.38\% Latinx, and 4.69\% mixed-race. There were 8 White/White pairs and
-4 same race racial minority pairs, for a total of 12 same-race pairs.
-The remaining 20 were mixed race pairs, of which 15 were White/racial
-minority pairings and 5 were cross-racial minority group pairs. 64.06\%
-of the sample identified as heterosexual, and 25\% identified as gay,
-lesbian or bisexual.
+partner. Even if they are not the gender you are attracted to, you can
+still judge their potential as a romantic partner. After the interaction
+you will be asked to evaluate how dateable your partner is. In other
+words, we would like to know if you think someone would date your
+interaction partner. Also, your interaction partner will be evaluating
+you in the same manner.
+
+Two participants were then brought into a larger interaction room where
+they sat on stools prearranged to be 36 inches apart. The experimenter
+instructed the participants to \enquote{get to know each other} for 10
+minutes and then left the room. After 10 minutes, the experimenter came
+back into the room and stopped the interaction. The participants then
+went back to their individual cubicles and completed a set of
+post-interaction measures. Participants were then thanked for their
+participation and debriefed Garcia et al. (2016). The full methodology
+used is found in Garcia et al. (2016)'s study.
+
+\subsection{Combining Samples}\label{combining-samples}
+
+Data from two different samples were used for this study and are
+discussed below. In the measures section that follows we refer to them
+as Sample 1 and Sample 2. Sample 1 is from a co-ed liberal arts college
+in the northeast and Sample 2 is from a women's liberal arts college in
+the northeast.
 
@@
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:corrtable}Correlations and Descriptive Statistics among Study Variables}
-\begin{tabular}{llllllllll}
-\toprule
- & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1.} & \multicolumn{1}{c}{2.} & \multicolumn{1}{c}{3.} & \multicolumn{1}{c}{4.} & \multicolumn{1}{c}{5.} & \multicolumn{1}{c}{6.} & \multicolumn{1}{c}{NA}\\
-\midrule
-1. Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  &  &  & \\
-2. Actor's objectification of partner & -1.58 & 1.21 & .20 &  &  &  &  &  & \\
-3. Partner's objectification of the actor & -1.58 & 1.21 & .09 & .14 &  &  &  &  & \\
-4. Actor's state self-objectification & 1.92 & 1.13 & .13 & -.09 & .30* &  &  &  & \\
-5. Actor's authenticity of interaction & 5.23 & 1.02 & -.02 & -.07 & .03 & -.10 &  &  & \\
-6. Actor's future relationship agency & 4.69 & 0.96 & .04 & .09 & -.10 & -.09 & .23+ &  & \\
-7. Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .06 & .02 & .11 & .07 & \\
-8. Actor's career aspirations & 3.88 & 0.61 & .05 & -.14 & -.08 & .01 & .33** & .26* & -.07\\
-\bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
-
 The following measures were collected in the order they are presented
-following the interaction. Correlations and descriptive statistics
-appear in Table~\ref{tab:corrtable}.
+following the interaction. Correlations appear in
+Table~\ref{tab:corrtable}, and descriptive statistics appear in
+Table~\ref{tab:descriptives}.
 
@@
 frequency of thoughts in relation to multiple characteristics of their
-partner (Garcia et al., 2016). Questions included aspects of their
+partner Garcia et al. (2016). Questions included aspects of their
 partner's internal traits such as personality, friends, family, and
 extracurricular interests, as well as external traits such as body,
-appearance, clothing, and body parts. All questions were rated on a
-scale from 1 (not at all) to 7 (constantly). Objectification was
-measured by taking the difference between the average frequency of
+appearance, clothing, and body parts. All questions were to be rated on
+a scale from 1 (not at all) to 7 (constantly). Objectification was
+measured by getting the difference between the average frequency of
 thought about their partner's external traits (\(\alpha\) = 0.79 for
@@
 would indicate the opposite.
-
-As can be seen in Table~\ref{tab:corrtable}, the mean
-other-objectification of women by women was \emph{M =} -1.58 (\emph{SD
-=} 1.21). This corresponds to women objectifying other women to a
-\emph{greater} extent than women's objectification of men reported in
-Garcia et al. (2016) (\emph{M =} -1.68, \emph{SD =} 1.52). Further, in
-the current sample the difference in other-objectification between
-heterosexual (\emph{M =} -1.77, \emph{SD =} 1.14) and non-heterosexual
-women (\emph{M =} -1.39, \emph{SD =} 1.35) was not statistically
-significant, \emph{t}(25.89) = 1.02, \emph{p =} 0.32.
 
@@
 authentic during your interaction?}' These questions were ranked on a
-scale from 1 (not at all) to 7 (very much). These were combined to form
-the authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) =
-0.91 for Sample 2).
+scale from 1 (not authentic at all). These were combined to form the
+authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) = 0.91
+for Sample 2).
 
@@
 To assess state self-objectification, we used an average of two items
-from Saguy et al. (2010) that were also used in Garcia et al. (2016).
-Participants were asked to rank how much they agreed with the following
-statements: \enquote{During the interaction I felt more like a body than
-a full self} and \enquote{I felt more like a body than as a real person
-in the interaction}. Originally, Saguy et al. (2010) used 3 items, but
-in both samples the reliability of the scale was higher once the third
-item was removed, so we chose to only use the first two for our measure
-of SSO, leaving us with a reliable scale (\(\alpha\) = 0.84 for Sample
-1, and \(\alpha\) = 0.85 for Sample 2.)
+from Saguy, Quinn, F Dovidio, and Pratto (2010) that were also used in
+Garcia et al. (2016). Participants were asked to rank how much they
+agreed with the following statements: \enquote{During the interaction I
+felt more like a body than a full self} and \enquote{I felt more like a
+body than as a real person in the interaction}. Originally, Saguy et al.
+(2010) used 3 items, but in both samples the reliability of the scale
+was higher once the third item was removed, so we chose to only use the
+first two for our measure of SSO, leaving us with a reliable scale
+(\(\alpha\) = 0.84 for Sample 1, and \(\alpha\) = 0.85 for Sample 2.)
 
@@
 Trait self-objectification (TSO) was assessed using the
-Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; M.
-Noll \& L. Fredrickson, 1998), which evaluates the extent to which
-individuals view their bodies in observable versus non-observable ways.
+Self-Objectification Questionnaire (Barbara L Fredrickson et al., 1998;
+M. Noll \& L. Fredrickson, 1998), which evaluates the extent to which
+individuals view their bodies in observable versus nonobservable ways.
 The questionnaire asked participants to rank order both appearance and
@@
 
+\subsubsection{Description of the
+Samples}\label{description-of-the-samples}
+
+Thirty-two previously unacquainted self-identifying female-sex dyads (64
+total participants) from two liberal arts institutions in the Northeast
+of the United States participated in this study. More specifically,
+twelve of the pairs, which derived from Sample 1, were students at a
+co-ed liberal arts college, while the remaining twenty pairs who came
+from Sample 2 attended a women's liberal arts college. Initially, data
+was collected from same-sex and mixed-sex dyads that comprised of male
+and female gendered individuals. Sample 1 originally consisted of
+twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs
+made up of forty-three women and one man, as well as two participants
+who did not identify with either gender category, formed Sample 2. Due
+to similarities across samples in regard to correlation patterns between
+significant variables within this study, the two datasets were combined.
+For consistency, we limited participant data to same sex female pairs at
+the two colleges. These participants were mostly first-year college
+students, with an average age of 18.85 (SD = 1.04). The sample was
+48.44\% White/European American, 9.38\% Black/African-American, 28.12\%
+Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
+8 White/White pairs and 4 same race racial minority pairs, for a total
+of 12 same-race pairs. The remaining 20 were mixed race pairs, of which
+15 were White/racial minority pairings and 5 were cross-racial minority
+group pairs. 64.06\% of the sample identified as heterosexual, and 25\%
+identified as gay, lesbian or bisexual.
+
+\subsection{Data analysis}\label{data-analysis}
+
+We used R (Version 3.5.2; R Core Team, 2018) and the R-packages
+\emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools}
+(Version 1.13.5; Wickham, Hester, \& Chang, 2018), \emph{dplyr} (Version
+0.8.3; Wickham, François, Henry, \& Müller, 2019), \emph{forcats}
+(Version 0.3.0; Wickham, 2018), \emph{ggformula} (Version 0.7.0; D.
+Kaplan \& Pruim, 2018), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
+\emph{haven} (Version 2.1.0; Wickham \& Miller, 2019), \emph{irr}
+(Version 0.84.1; Gamer, Lemon, \&
+\textless{}puspendra.pusp22@gmail.com\textgreater{}, 2019), \emph{knitr}
+(Version 1.25; Xie, 2015), \emph{kutils} (Version 1.70; Johnson, Kite,
+\& Redmon, 2020), \emph{lattice} (Version 0.20.38; Sarkar, 2008),
+\emph{lavaan} (Version 0.6.1; Rosseel, 2012), \emph{lpSolve} (Version
+5.6.15; Berkelaar \& others, 2020), \emph{Matrix} (Version 1.2.15; Bates
+\& Maechler, 2018), \emph{mosaic} (Version 1.2.0; Pruim, Kaplan, \&
+Horton, 2017, 2018), \emph{mosaicData} (Version 0.17.0; Pruim et al.,
+2018), \emph{nlme} (Version 3.1.137; Pinheiro, Bates, DebRoy, Sarkar, \&
+R Core Team, 2018), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
+2018), \emph{psych} (Version 1.8.4; Revelle, 2018), \emph{purrr}
+(Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.1.1;
+Wickham, Hester, \& Francois, 2017), \emph{stringr} (Version 1.4.0;
+Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
+\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse}
+(Version 1.2.1; Wickham, 2017), and \emph{xtable} (Version 1.8.3; Dahl,
+Scott, Roosen, Magnusson, \& Swinton, 2018) for all our analyses.
+
 \section{Results}\label{results}
@@
 
-We used R (Version 3.5.2; R Core Team, 2017) and the R-packages
-\emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{psych} (Version
-1.8.4; Revelle, 2017), \emph{nlme} (Version 3.1.137; Pinheiro, Bates,
-DebRoy, Sarkar, \& R Core Team, 2017) for our analyses. Further, we used
-the R-packages \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018),
-\emph{apaTables} (Version 2.0.5; Stanley, 2018), with \emph{knitr}
-(Version 1.25; Xie, 2015) to create a fully reproducible manuscript in
-\emph{rmarkdown} (Version 1.15; Xie, Allaire, \& Grolemund, 2018).
-
-\begin{figure}
-\includegraphics[width=400px]{APIM_figure} \caption{Basic actor-partner interdependence model (APIM) depiction.}\label{fig:apim}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=400px]{theor_figure} \caption{Theoretical Model from Garcia et al. (2016).}\label{fig:theorfigure}
-\end{figure}
-
-This study sought to detect whether partners' objectification of one
-another affected state self-objectification (SSO). Specifically, we were
-interested in testing the relationship between state-other
-objectification and SSO, and how SSO in turn, affects feelings of
-inauthenticity during the interaction. In addition, we also tested if
-the effect of other-objectification in an interaction on SSO is only
-present for those women who are high in trait self-objectification.
-Further, we investigated the relationships between experiencing
-interaction inauthenticity and relationship agency, career aspirations,
-and cognitive performance.
-
-While past studies investigating objectification in interactions used
-dyadic path analysis (Garcia et al., 2016), the current study used
-multilevel modeling proceedures. Dyadic analyses for distinguishable
-dyads (e.g., mixed-gender interacting pairs) is more natural in
-Structural Equation Modeling (SEM) than it is for indistinguishable
-dyads (e.g., same-gender interacting pairs), as we have here (Garcia,
-Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
-this asymmetry is that, due to the arbitrary distinctions made between
-\enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads,
-many estimates need to be fixed to be equal (i.e., paths, variances,
-covariances, endogenous intercepts, and exogenous means), but these
-equality constraints should not then be considered in the degrees of
-freedom calculations for fit estimations (Olsen \& Kenny, 2006).
-Further, Olsen and Kenny (2006) details how a new independence model and
-the corresponding fit measure should be re-calculated for
-indistinguishable dyads models. The current study uses dyadic multilevel
-modeling (MLM) to test all relationships and mediation patterns. The
-online supplementary materials contains analysis using SEM. See
-Ledermann and Kenny (2017) for a more complete discussion of the
-considerations for using SEM versus MLM for dyadic analysis.
-
-Testing our hypotheses in the current, same-gender, sample, involves
-using the Actor-Partner Independence Model (APIM) approach for each
-outcome variable (i.e., endogenous variable in
-Figure~\ref{fig:theorfigure}). Thus, we ran five APIM's to test all the
-hypothesized relationships. See Figure~\ref{fig:apim} for a basic APIM
-model. The APIM includes effects due to one's own, as well as one's
-partner's, predictor variables (\(X\)'s) on the one's own outcome
-variable (\(Y\)). The current study deals with indistinguishable dyads,
+This study sought to replicate the results of Garcia et al. (2016)'s
+study, done with male-female pairs, which used dyadic analysis to detect
+whether partners' objectification of one another affected state
+self-objectification (SSO). We hope to investigate how the main effects
+found in the previous study relay to interactions between women:
+specifically, the relationship between state-other objectification and
+self-state objectification and the resulting effect of self-state
+objectification on inauthenticity during the interaction.
+
+We used path analysis to obtain our estimates, but because our sample is
+nonindependent, we used the indistinguishable actor--partner
+interdependence model (Olsen \& Kenny, 2006). The APIM can be defined as
+a \enquote{model of dyadic relationships that integrates a conceptual
+view of interdependence with the appropriate statistical techniques for
+measuring and testing it} (Olsen \& Kenny, 2006). See
+Figure~\ref{fig:apim} for a basic APIM model. Unlike the original Garcia
+et al. (2016) study, our study deals with indistinguishable dyads,
 meaning the designation of who is designated as \enquote{actor} and who
-is designated as \enquote{partner} is arbitrary. These analyses are
-considered exploratory, given the lack of prior research theorizing
-about these linkages.
+is designated as \enquote{partner} is arbitrary. Due to constraints of
+the basic APIM, in that this was an exploration of indistinguishable
+female dyads, we had to fix all path estimates to be the same
+across/between people and partners, in addition to all variances,
+covariances, endogenous intercepts, and exogenous means. Due to the
+complexity of the original Garcia et al. (2016) study, we also had to
+set the exogenous covariances equal. More specifically, the covariances
+between TSO, actor and partner objectification, and the interaction
+between actor TSO and partner objectification (and vice versa).
+
+In order to interpret model fit, which refers to the ability of a model
+to reproduce the data (i.e., usually the varience-covariance matrix) we
+utilized both the I-SAT (saturated) model, and the Null model to ensure
+that all possible corresponding covariences are fixed to be equal across
+partners. We obtained fit estimates by subtracting the chi-square
+estimate for the I-SAT model from the analysis model (Olsen \& Kenny,
+2006, Peugh, DiLillo, and Panuzio (2013)).
 
@@
 
-\begin{figure}
-\includegraphics[width=400px]{SEMfigure} \caption{Path Analysis Model with Estimates}\label{fig:semfigure}
-\end{figure}
-
-All model estimates and p-values are found in Table~\ref{tab:mlm} and
-the relationships with estimates included are depicted in
-Figure~\ref{fig:semfigure}.
-
-The most important finding from Garcia et al. (2016) was the significant
-partner effect of other objectification and SSO (specifically men's
-objectification of women and women's SSO). As expected, the partner
-effect of other-objectification on SSO in the current all-women sample
-was statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12,
-\emph{p} = .019. One's own other objectification had no effect on SSO,
-\emph{b} = -0.16, \emph{SE} = 0.12, \emph{p} = .210. Inconsistent with
-past findings however, there was no statistically significant
-interaction of partner's other objectification and the person's trait
-self-objectification on SSO, \emph{b} = 0.03, \emph{SE} = 0.27, \emph{p}
-= .910. There was also no significant main effect of trait
-self-objectification on SSO \emph{b} = 0.07, \emph{SE} = 0.05, \emph{p}
-= .183.
-
-There was no significant effect of SSO on interaction authenticity,
-although the estimate of this effect was in the hypothesized negative
-direction, \emph{b} = -0.09, \emph{SE} = 0.12, \emph{p} = .431. Because
-authenticity was a composite score of 9 items, two of which were
-interaction specific authenticity items, we also estimated the pairwise
-correlations between SSO and all these items individually. They were all
-small, ranging from only -0.01 to -0.14. Although we hypothesized that
-SSO would mediate the relationship between partner's other
-objectification and interaction authenticity, after finding no
-relationship between SSO and authenticity, we also tested if the
-partner's other objectification had a direct effect on authenticity, but
-this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
-\emph{p} = .608 (nor was the total effect of partner's other
-objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11,
-\emph{p} = .787).
-
-Lastly, although there was no evidence that SSO was related to
-interaction authenticity in the current sample, we tested if interaction
-authenticity (composite of nine items) had effects on cognitive
-performance, career aspirations, and relationship agency, as it did in
-Garcia et al. (2016). We again used MLM and thus, these effects were
-tested in three separate models. There was no significant effect of
-interaction authenticity on cognitive performance, \emph{b} = 0.32,
-\emph{SE} = 0.28, \emph{p} = .258, but authenticity was significantly
-positively related to both career aspirations, \emph{b} = 0.18,
-\emph{SE} = 0.07, \emph{p} = .010, and relationship agency, \emph{b} =
-0.23, \emph{SE} = 0.12, \emph{p} = .049. There was no direct effect of
-SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25,
-\emph{p} = .872, and no direct effect of partner's other objectification
-on cognitive performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
-.962. There was no direct effect of SSO on career aspirations, \emph{b}
-= 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of
-partner's other objectification on career aspirations, \emph{b} = -0.06,
-\emph{SE} = 0.07, \emph{p} = .378. There was no direct effect of SSO on
-relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} =
-.659, and no direct effect of partner's other objectification on
-relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.
+All model estimates and p-values are found in Table~\ref{tab:sem}. The
+most important findings from Garcia et al. (2016) were the significant
+partner effect between actor SSO and partner objectification
+(specifically men's objectification of women and women's SSO), and the
+link between actor SSO and actor authenticity (also specifically for
+women). We did not find a significant effect between actor SSO and actor
+authenticity (\(\beta\)= -.10, \(p\)=.38), which means we do not have
+evidence to support the idea that partner objectification is the cause
+for the negative effects related to relationship inauthenticity.
+However, we did find a significant relationship between partner
+objectification and actor SSO (\(\beta\)= .25, \(p\)=.03), which
+supports our hypothesis that objectification from other women also
+causes women to self-objectify just as it does in interactions between
+male-female pairs. We also found a significantly negative effect of
+authenticity on career aspirations (\(\beta\)= .18, \(p\)=.01) and
+relationship agency (\(\beta\)=.27, \(p\)=.01). We found that the model
+had good fit (\(\chi^2\)=22.33, \(df\)=34). In this case, a good fit
+indicates that there are no direct effects of SSO or SOO on the outcomes
+on cognitive performance, relationship agency, and career aspirations,
+which indicates that the path we chose makes sense.
 
@@
 
-The current study tested whether the model of interpersonal
-objectification and state self-objectification (SSO) used in Garcia et
-al. (2016) replicates in a same-gender dyadic sample of women. Although
-past research has found that women do objectify other women (Harsey \&
-Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013), this is
-the first study to test if \emph{interpersonal} other-objectification by
-women is related to state self-objectification in their woman-identified
-interaction partners. As hypothesized, the current study did find a
-significant relationship between a woman's interaction partner's report
-of having objectified her and her own post-interaction feelings of
-self-objectification. That is, there was a significant partner effect of
-other-objectification on SSO. This effect extends the equivalent
-relationship found in mixed-gender interactions to the context of
-same-gender interactions between women. Thus, evidence suggests that it
-is not only the male gaze, and male other-objectification that is
-related to women's state self-objectification, but being objectified by
-another woman is also related to women's SSO, at least in the context of
-a scenario where they know they are being evaluated as a potential
-dating partner.
-
-As is the case in all correlational studies, we cannot be sure about the
-causal direction. The model used by the current study asserts that being
-objectified by a woman causes women to self-objectify, but it could be
-that women's SSO causes them to be objectified by their interaction
-partner. This latter interpretation is theoretically interesting given
-that, in both the Garcia et al. (2016) study and in the current study,
-it is \emph{women's} state self-objectification that relates to being
-objectified by one's partner. Objectification Theory (Roberts \&
-Fredrickson, 1997), as well as some past experimental studies (Saguy et
-al., 2010) suggest that at least one direction of the causal flow is
-from other-objectification to SSO. Other studies, especailly those
-investigating explicitly women objectifying other women (Puvia \& Vaes,
-2013), have relately found evidence that women's \emph{trait}
-self-objectification causes women to objectify (dehumanize) other women
-and this link is mediated by \emph{state} self-objectification. It could
-follow that we tend to objectify other women who objectify us and
-through a process of TSO causes SSO which in turn causes objectifation
-of one's partner, which in turn causes one's partner to objectify us.
-The current study does not provide any evidence of this alternative
-model, however---TSO was not significantly correlated with SSO and
-actor's objectification was not correlated with partner's
-objectification.
-
-Where the results of the current study diverge most notably from the
-results of studies testing interpersonal objectification among
-mixed-gender dyads is the lack of evidence for relationships between SSO
-and interaction inauthenticity. In addition, we found no evidence of
-\emph{direct} or \emph{indirect} relationships between SSO and cognitive
-functioning, relationship agency, and career aspirations. Nor was there
-evidence of \emph{direct} or \emph{indirect} relationships between
-other-objectification and any of these outcomes. This is somewhat
-suprising given the extant evidence linking SSO and cognitive
-functioning (B. L. Fredrickson et al., 1998; and see Moradi \& Huang,
-2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the research on
-interpersonal other-ojectification and cognitive functioning (Garcia et
-al., 2016; Gervais et al., 2011; Logel et al., 2009). This lack of
-evidence could potentially signal diverging processes between women's
-experiences with interpersonal objectification from men and
-interpersonal objectification from women. There is quite a bit of
-evidence suggesting that the male gaze is particularly detrimental
-(Calogero, 2004; Gervais, Holland, \& Dodd, 2013; Gervais et al., 2011;
-Roberts \& Fredrickson, 1997), and perhaps the self-objectification
-experienced within an interaction with a women is qualtatively
-different, and perhaps not as harmful, as the self-objectification
-experienced within an interaction with a man. However, as a strong note
-of caution, it is best not to interpret a null result as evidence of no
-relationship and more research on interpersonal objectification among
-women is needed.
-
-The lack of evidence for a relationship between SSO and interaction
-authenticity is surprising and again, should not be interpreted as
-evidence of no relationship. It should be noted that the estimate of
-this relationship was small (close to zero), but in the negative
-direction. If it is the case that there is a smaller (i.e., weaker)
-connection between women's feelings of SSO and inauthenticity in
-interactions with other women than in interactions with men, models of
-interpersonal objectification, like the SIMO (Gervais et al., 2020),
-could be extended by including inauthenticity as a potential mediating
-factor. Further, gender of the objectifyer/interaction partner could be
-added as a moderator of the self-objectificaiton to authenticity process
-to help understand the circumstances that require other-objectification
-and SSO to have negative consequences for women.
-
-Although the current study did not find a connection between SSO and
-authenticity, we did find significant positive relationships between
-authenticity and relationship agency, and authenticity and career
-aspirations. The relationship between authenticity and cognitive
-functioning was also estimated as positive, but was not statistically
-signficant. Again, due to the lack of connection between SSO and
-authenticity, we found no evidence of \emph{indirect} relationships
-between SSO and these outcome variables. This evidence of a relationship
-between authenticity and the relational outcome variables (i.e.,
-relationship agency and career aspirations) provides evidence that
-corroborates past findings that felt authenticity in interactions is
-important for healthy relationship functioning (Garcia et al., 2016;
-Terán et al., 2020). Just as authenticity has been found to be important
-in intergroup interactions (Brunell et al., 2010; Garcia et al., 2016;
-Tolman et al., 2006), we again find more evidence here that disruptions
-in feelings of authenticity can negatively impact relationships beyond
-the current partner. Although the current study did not find a
-connection between authenticity and SSO, this seems theoretically to be
-a natural connection, and future work must explore when and how SSO
-leads to inauthenticity in interpersonal objectification situations.
-
-\subsection{Limitations and Future
-Directions}\label{limitations-and-future-directions}
-
-\subsubsection{Sample Characteristics}\label{sample-characteristics}
-
-In addition to being relatively small and combined across two
-institutions, another limitation of the current study is that the sample
-was comprised of Western women only. Being that self-objectification is
-most prevalent in Western culture (Loughnan et al., 2015b) research on
-objectification conducted outside of Western or Westernized countries
-has been scarce (Moradi \& Huang, 2008), although more recent work has
-examined objectification from a cross-cultural framework (Loughnan et
-al., 2015b, Wollast et al. (2020)). Since \enquote{bodies exist within
-social and cultural contexts, and hence are also constructed through
-sociocultural practices and discourses} (Roberts \& Fredrickson, 1997,
-p. 174), it is important to consider how diverse social identities
-within unique cultural contexts may inform sexual objectification
-phenomenon to test the cross-cultural applicability of theoretical
-frameworks (Loughnan et al., 2015b).
-
-Further, sexualizing experiences and self-objectification are thought to
+As stated previously, we did not find a significant effect between actor
+SSO and actor authenticity (\(\beta\)= -.10, \(p\)=.38), which suggests
+that there is not sufficient evidence to support the claim that partner
+objectification is the cause for the diverse range of negative effects
+related to relationship inauthenticity. However, we did observe a
+significant partner effect of objectification on actor
+self-objectification, which does align with our hypothesis that
+theorized objectification from other women can also cause women to
+self-objectify just as they do within interactions between male-female
+pairs. The results of this study demonstrate the complex and ambivalent
+nature of female sexual objectification and additionally highlight the
+psychological and social consequences of such objectification processes
+on women's social relationships and well-being. The sample of the
+current study was comprised of Western women, being that sexual
+objectification is most prevalent in this culture (Loughnan et al.,
+2015), and research on objectification conducted outside of Western or
+Westernized countries is scarce (Moradi \& Huang, 2008). Because
+\enquote{bodies exist within social and cultural contexts, and hence are
+also constructed through sociocultural practices and discourses}
+(Barbara L Fredrickson \& Roberts, 1997, p. 174), it is important to
+consider how diverse social identities within unique cultural contexts
+may inform sexual objectification phenomenon to test the cross-cultural
+applicability of theoretical frameworks (Loughnan et al., 2015).
+Further, sexualzing experiences and self-objectification are thought to
 begin a very young age, and thus, researchers have only recently begun
@@
 research among younger and older individuals is needed, especially
-because self-objectification may change over time (Roberts \&
-Fredrickson, 1997). It may be valuable to question the extent to which
+because self-objectification may change over time (Barbara L Fredrickson
+\& Roberts, 1997). It may be valuable to question the extent to which
 children, adolescents, or emerging adults of different races or
-ethnicities are exposed to varied amounts of sexualizing content.
-Further, more longitudinal studies investigating the developmental
-experience of interpersonal objectification and self-objectificaion are
-needed {[}see CITE and CITE for exmaples{]}.
-
-\subsubsection{Sexual Objectification and the Objectifyer's
-Gender}\label{sexual-objectification-and-the-objectifyers-gender}
-
-The current sample contained a mixture of heterosexual and
-non-heterosexual women, but all participants were asked to think about
-and evaluate their partner as a potential dating/romantic partner. We
-think that hetereosexual women are able to do this with other women as
-their target---and there is evidence that they might do this readily
-(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---they may be even
-more apt to activate social comparison processes (Festinger, 1954) than
-women who are sexually attracted to other women (non-heterosexual
-women). This differential psychological process between women with
-differing sexualities might have served to dampen our ability to detect
-relationships, adding variability.
-
-Previous research has found that when compared to heterosexual women,
-lesbian women report less concern with physical appearance (Siever,
-1994; Strong, Williamson, Netemeyer, \& Geer, 2000), and less
-self-objectification (Brownlow, 1998; Noffsinger-Frazier, 2004). However
-none of these studies examined the relationship between
-self-objectification and experiences of sexual objectification. Thus, it
-is unclear whether lesbians indeed experience similar levels of cultural
-sexual objectification but internalize them less than heterosexual women
-do. Consistent with previous research, Hill and Fischer (2008)
-determined that lesbians existed less physical appearance concerns
-compared to heterosexual women, however there was no evidence found that
-lesbian women self-objectify less than heterosexual women and they did
-not find that sexual orientation moderates the relationship between
-sexual objectification and self-objectification. This contradicts older
-theoretical literature that suggests that lesbians internalize cultural
-sexual objectification less than do heterosexual women (Brown, 1987;
-LUM, 1994; Pitman, 1999; Siever, 1994).
-
-However, since both men and women are socialized in a culture that
-sexually objectifies women, both men and women may come to internalize
-this socialization and sexually objectify women. Indeed, recent research
-has found that the more women self-objectify, the more they objectify
-other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013), although not
-to the degree exhibited by men; that is, men were found to objectify
-women significantly more than women objectify other women (Strelan \&
-Hargreaves, 2005).
-
-Objectification among platonic friends: Perhaps women could be
-amplifying each others' state self-objectification \emph{before} the
-theoretical encounters with men organized in the SIMO occur. In this
-way, women's rituals of getting ready together might place even women
-with low TSO in a higher SSO group.
-
-\subsubsection{Sexism and Sexual
-Discrimination}\label{sexism-and-sexual-discrimination}
-
-Sexism has recently been found to be related to the objectification of
-women, but not men, for both men and women (Harsey \& Zurbriggen,
-2020).{[}Kat: Is the relationship between sexism and objectification
-really this recent of a finding? Or was it just replicated recently?{]}
-Empirical evidence illustrates how women continue to be objects of
-interpersonal discrimination and experience daily sexist hassles (Swim,
-Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
-discrimination women face is the process by which their whole being is
-viewed as a collection of sexualized body parts valued predominantly for
-commodification, a phenomena termed sexual objectification (Bartky,
-1990). Sexual objectification occurs with both \enquote{endless variety
-and monotonous similarity,} and is thus mediated by unique combinations
-of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
-Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
-Nicholson (1989), p.~28). Amid such heterogeneity though,
-\enquote{having a reproductively mature female body} proposed by Roberts
-and Fredrickson (1997) is likely to create a shared vulnerability to
-sexual objectification and a variety of shared negative experiences as a
-result.
-
-\section{Conclusion}\label{conclusion}
-
-The results from the current analysis highlight how subtle forms of
-sexist discrimination operate, and provide valuable insight into
-prevention and intervention efforts in both clinical and educational
-contexts. These results are quite useful for promoting mental health,
-the creation and maintence of early action programs for girls and young
-women, and for scholars and practitioners to work intentially to provide
-the tools necessary to circumvent or mitigate negative effects on
-self-objectification to combat such experiences.
-
-The results of this study demonstrate the complex and ambivalent nature
-of sexual objectification and additionally highlight the psychological
-and social consequences of such objectification processes on women's
-social relationships and well-being. We did not find a significant
-effect between actor SSO and felt authenticity in the interaction, which
-suggests that there is not sufficient evidence to support the claim that
-partner objectification is the cause for the diverse range of negative
-effects related to interaction inauthenticity.
+ethnicities are exposed to varied amounts of sexulizing content. Also,
+future experiments or longitudinal studies should explore the external
+validity of the notions of self-objectification and how the
+operalization of self-objectification may be improved. Regardless, the
+results from the current analysis highlight how subtle forms of sexist
+discrimination operate to inform prevention and intervention efforts in
+both clinical and educational contexts. These results are quite useful
+for promoting mental health and within early action programs for girls
+and young women, where scholars and practitioners might provide the
+tools necessary to circumvent or mitigate negative effects on
+self-objectification, and combat such experiences.
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:corrtable}Correlations among study variables.}
+\begin{tabular}{llllllll}
+\toprule
+ & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5}\\
+\midrule
+Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  & \\
+Actor's authenticity of interaction & 5.23 & 1.02 & -.02 &  &  &  & \\
+Actor's objectification of partner & -1.58 & 1.21 & .20 & -.07 &  &  & \\
+Actor's state self-objectification & 1.92 & 1.13 & .13 & -.10 & -.09 &  & \\
+Actor's future relationship agency & 4.69 & 0.96 & .04 & .23+ & .09 & -.09 & \\
+Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .11 & .02 & .07\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:descriptives}Descriptive Statistics for Study Variables}
+\begin{tabular}{lll}
+\toprule
+ & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD}\\
+\midrule
+Actor's trait self objectification (TSO) & -0.35 & 2.64\\
+Actor's authenticity of interaction & 5.23 & 1.02\\
+Actor's objectification of partner & -1.58 & 1.21\\
+Actor's state self-objectification & 1.92 & 1.13\\
+Actor's future relationship agency & 4.69 & 0.96\\
+Actor's cognitive performance & 5.03 & 2.29\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:sem}Estimates from final Path Analysis Model}
+\small{
+\begin{tabular}{lllllll}
+\toprule
+Path & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{z-value} & \multicolumn{1}{c}{p-value}\\
+\midrule
+Actor SSO & \textasciitilde{} & Actor TSO & 0.08 & 0.09 & 0.91 & 0.36\\
+Actor SSO & \textasciitilde{} & Actor Obj. of Partner & -0.17 & 0.12 & -1.41 & 0.16\\
+Actor SSO & \textasciitilde{} & Partner Obj. of Actor & 0.25 & 0.12 & 2.15 & 0.03\\
+Actor SSO & \textasciitilde{} & Actor TSO x Partner Obj. & 0.00 & 0.04 & -0.10 & 0.92\\
+Actor Authenticity & \textasciitilde{} & Actor SSO & -0.10 & 0.12 & -0.88 & 0.38\\
+Actor Cog. Performance & \textasciitilde{} & Actor Authenticity & 0.33 & 0.27 & 1.22 & 0.22\\
+Actor Career Aspirations & \textasciitilde{} & Actor Authenticity & 0.18 & 0.07 & 2.66 & 0.01\\
+Actor Rel. Agency & \textasciitilde{} & Actor Authenticity & 0.27 & 0.10 & 2.64 & 0.01\\
+\bottomrule
+\end{tabular}
+}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{figure}
+\includegraphics[width=400px]{../figures/APIM_figure} \caption{Basic actor-partner interdependence model (APIM) depiction.}\label{fig:apim}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=400px]{../figures/SEMfigure} \caption{Path Analysis Model with Estimates}\label{fig:semfigure}
+\end{figure}
+
+\newpage
 
@@
 
-\newpage
+\begin{verbatim}
+## [1] "R [Version 3.5.2; @R-base]"
+\end{verbatim}
 
@@
 
+\hypertarget{ref-R-Matrix}{}
+Bates, D., \& Maechler, M. (2018). \emph{Matrix: Sparse and dense matrix
+classes and methods}. Retrieved from
+\url{https://CRAN.R-project.org/package=Matrix}
+
 \hypertarget{ref-berger1972}{}
@@
 
-\hypertarget{ref-bernard2018bodies}{}
-Bernard, P., Legrand, S., \& Klein, O. (2018). From bodies to blame:
-Exposure to sexually objectifying media increases tolerance toward
-sexual harassment. \emph{Psychology of Popular Media Culture},
-\emph{7}(2), 99.
+\hypertarget{ref-R-lpSolve}{}
+Berkelaar, M., \& others. (2020). \emph{LpSolve: Interface to
+'lp\_solve' v. 5.5 to solve linear/integer programs}. Retrieved from
+\url{https://CRAN.R-project.org/package=lpSolve}
 
@@
 nonverbal communication. \emph{Sex Roles}, \emph{32}(1-2), 79--90.
-
-\hypertarget{ref-brown1987lesbians}{}
-Brown, L. S. (1987). Lesbians, weight, and eating: New analyses and
-perspectives. \emph{Lesbian Psychologies: Explorations and Challenges},
-294--309.
-
-\hypertarget{ref-brownlow1998relationship}{}
-Brownlow, B. S. (1998). \emph{The relationship between objectification,
-body image disturbances, and disordered eating: Investigating race,
-socioeconomic status, acculturation and self-objectification as
-mediators.} (PhD thesis). ProQuest Information \& Learning.
 
@@
 
-\hypertarget{ref-calogero2004test}{}
-Calogero, R. M. (2004). A test of objectification theory: The effect of
-the male gaze on appearance concerns in college women. \emph{Psychology
-of Women Quarterly}, \emph{28}(1), 16--21.
-
 \hypertarget{ref-calogero2011}{}
@@
 
-\hypertarget{ref-deaux1987putting}{}
-Deaux, K., \& Major, B. (1987). Putting gender into context: An
-interactive model of gender-related behavior. \emph{Psychological
-Review}, \emph{94}(3), 369.
-
-\hypertarget{ref-dovidio2006nonverbal}{}
-Dovidio, J. F., Hebl, M., Richeson, J. A., \& Shelton, J. N. (2006).
-Nonverbal communication, race, and intergroup interaction.
-
-\hypertarget{ref-festinger1954theory}{}
-Festinger, L. (1954). A theory of social comparison processes.
-\emph{Human Relations}, \emph{7}(2), 117--140.
+\hypertarget{ref-R-xtable}{}
+Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J.
+(2018). \emph{Xtable: Export tables to latex or html}. Retrieved from
+\url{https://CRAN.R-project.org/package=xtable}
+
+\hypertarget{ref-Kaschak}{}
+Engendered lives: A new psychology of womens experience. (1993).
+\emph{Choice Reviews Online}, \emph{30}(07).
+doi:\href{https://doi.org/10.5860/choice.30-4102}{10.5860/choice.30-4102}
 
@@
 
+\hypertarget{ref-R-irr}{}
+Gamer, M., Lemon, J., \&
+\textless{}puspendra.pusp22@gmail.com\textgreater{}, I. F. P. S. (2019).
+\emph{Irr: Various coefficients of interrater reliability and
+agreement}. Retrieved from \url{https://CRAN.R-project.org/package=irr}
+
 \hypertarget{ref-garcia2016objectification}{}
@@
 
-\hypertarget{ref-garcia2015moderation}{}
-Garcia, R. L., Kenny, D. A., \& Ledermann, T. (2015). Moderation in the
-actor--partner interdependence model. \emph{Personal Relationships},
-\emph{22}(1), 8--29.
-
-\hypertarget{ref-gay2010my}{}
-Gay, R. K., \& Castano, E. (2010). My body or my mind: The impact of
-state and trait objectification on women's cognitive resources.
-\emph{European Journal of Social Psychology}, \emph{40}(5), 695--703.
-
-\hypertarget{ref-gervais2013my}{}
-Gervais, S. J., Holland, A. M., \& Dodd, M. D. (2013). My eyes are up
-here: The nature of the objectifying gaze toward women. \emph{Sex
-Roles}, \emph{69}(11-12), 557--570.
-
-\hypertarget{ref-gervais2020social}{}
-Gervais, S. J., Sáez, G., Riemer, A. R., \& Klein, O. (2020). The social
-interaction model of objectification: A process model of goal-based
-objectifying exchanges between men and women. \emph{British Journal of
-Social Psychology}, \emph{59}(1), 248--283.
-
-\hypertarget{ref-gervais2011you}{}
-Gervais, S. J., Vescio, T. K., \& Allen, J. (2011). When what you see is
-what you get: The consequences of the objectifying gaze for women and
-men. \emph{Psychology of Women Quarterly}, \emph{35}(1), 5--17.
-
-\hypertarget{ref-harsey2020men}{}
-Harsey, S. J., \& Zurbriggen, E. L. (2020). Men and women's
-self-objectification, objectification of women, and sexist beliefs.
-\emph{Self and Identity}, 1--8.
-
-\hypertarget{ref-hebl2005promoting}{}
-Hebl, M. R., \& Dovidio, J. F. (2005). Promoting the ``social'' in the
-examination of social stigmas. \emph{Personality and Social Psychology
-Review}, \emph{9}(2), 156--182.
-
-\hypertarget{ref-hill2008examining}{}
-Hill, M. S., \& Fischer, A. R. (2008). Examining objectification theory:
-Lesbian and heterosexual women's experiences with sexual-and
-self-objectification. \emph{The Counseling Psychologist}, \emph{36}(5),
-745--776.
+\hypertarget{ref-R-purrr}{}
+Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
+tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
 
@@
 Quarterly}, \emph{40}(1), 108--119.
+
+\hypertarget{ref-R-kutils}{}
+Johnson, P., Kite, B., \& Redmon, C. (2020). \emph{Kutils: Project
+management tools}. Retrieved from
+\url{https://CRAN.R-project.org/package=kutils}
 
@@
 
-\hypertarget{ref-kahalon2018don}{}
-Kahalon, R., Shnabel, N., \& Becker, J. C. (2018). ``Don't bother your
-pretty little head'' appearance compliments lead to improved mood but
-impaired cognitive performance. \emph{Psychology of Women Quarterly},
-\emph{42}(2), 136--150.
-
-\hypertarget{ref-ledermann2017analyzing}{}
-Ledermann, T., \& Kenny, D. A. (2017). Analyzing dyadic data with
-multilevel modeling versus structural equation modeling: A tale of two
-methods. \emph{Journal of Family Psychology}, \emph{31}(4), 442.
-
-\hypertarget{ref-logel2009interacting}{}
-Logel, C., Walton, G. M., Spencer, S. J., Iserman, E. C., Hippel, W.
-von, \& Bell, A. E. (2009). Interacting with sexist men triggers social
-identity threat among female engineers. \emph{Journal of Personality and
-Social Psychology}, \emph{96}(6), 1089.
-
-\hypertarget{ref-loughnan2015exploring}{}
+\hypertarget{ref-R-ggformula}{}
+Kaplan, D., \& Pruim, R. (2018). \emph{Ggformula: Formula interface to
+the grammar of graphics}. Retrieved from
+\url{https://CRAN.R-project.org/package=ggformula}
+
+\hypertarget{ref-loughnan2015}{}
 Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
-Harada, C., \ldots{} Tsuchiya, K. (2015a). Exploring the role of culture
+Harada, C., \ldots{} Tsuchiya, K. (2015). Exploring the role of culture
 in sexual objectification: A seven nations study. \emph{Revue
 Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
-
-\hypertarget{ref-loughnan2015}{}
-Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
-Harada, C., \ldots{} Tsuchiya, K. (2015b). Exploring the role of culture
-in sexual objectification: A seven nations study. \emph{Revue
-Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
-
-\hypertarget{ref-lum1994lesbians}{}
-LUM, E. (1994). Lesbians and physical appearance which model applies?
-\emph{Lesbian and Gay Psychology: Theory, Research, and Clinical
-Applications}, \emph{1}, 84.
 
@@
 
-\hypertarget{ref-meltzer2020women}{}
-Meltzer, A. L. (2020). Women can benefit from sexual and physical
-valuation in the context of a romantic relationship. \emph{Personality
-and Social Psychology Bulletin}, \emph{46}(2), 243--257.
-
-\hypertarget{ref-miles2015stop}{}
-Miles-McLean, H., Liss, M., Erchull, M. J., Robertson, C. M., Hagerman,
-C., Gnoleba, M. A., \& Papp, L. J. (2015). ``Stop looking at me!''
-interpersonal sexual objectification as a source of insidious trauma.
-\emph{Psychology of Women Quarterly}, \emph{39}(3), 363--374.
-
 \hypertarget{ref-moradi2008}{}
@@
 
-\hypertarget{ref-morry2001magazine}{}
-Morry, M. M., \& Staska, S. L. (2001). Magazine exposure:
-Internalization, self-objectification, eating attitudes, and body
-satisfaction in male and female university students. \emph{Canadian
-Journal of Behavioural Science/Revue Canadienne Des Sciences Du
-Comportement}, \emph{33}(4), 269.
-
-\hypertarget{ref-nadal2012effects}{}
-Nadal, K. L., \& Haynes, K. (2012). The effects of sexism, gender
-microaggressions, and other forms of discrimination on women's mental
-health and development.
-
-\hypertarget{ref-noffsinger2004objectification}{}
-Noffsinger-Frazier, N. A. (2004). \emph{Objectification theory and
-disordered eating: The impact of feminist identification,
-internalization of sociocultural standards of appearance, and sexual
-orientation}. The University of Memphis.
+\hypertarget{ref-R-tibble}{}
+Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
+Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
@@
 
+\hypertarget{ref-peugh2013analyzing}{}
+Peugh, J. L., DiLillo, D., \& Panuzio, J. (2013). Analyzing mixed-dyadic
+data using structural equation models. \emph{Structural Equation
+Modeling: A Multidisciplinary Journal}, \emph{20}(2), 314--337.
+
 \hypertarget{ref-R-nlme}{}
-Pinheiro, J., Bates, D., DebRoy, S., Sarkar, D., \& R Core Team. (2017).
+Pinheiro, J., Bates, D., DebRoy, S., Sarkar, D., \& R Core Team. (2018).
 \emph{nlme: Linear and nonlinear mixed effects models}. Retrieved from
@@
 
-\hypertarget{ref-pitman1999body}{}
-Pitman, G. E. (1999). Body image, compulsory heterosexuality, and
-internalized homophobia. \emph{Journal of Lesbian Studies}, \emph{3}(4),
-129--139.
-
-\hypertarget{ref-puvia2013being}{}
-Puvia, E., \& Vaes, J. (2013). Being a body: Women's appearance related
-self-views and their dehumanization of sexually objectified female
-targets. \emph{Sex Roles}, \emph{68}(7-8), 484--495.
+\hypertarget{ref-R-mosaic}{}
+Pruim, R., Kaplan, D. T., \& Horton, N. J. (2017). The mosaic package:
+Helping students to 'think with data' using r. \emph{The R Journal},
+\emph{9}(1), 77--102. Retrieved from
+\url{https://journal.r-project.org/archive/2017/RJ-2017-024/index.html}
+
+\hypertarget{ref-R-mosaicData}{}
+Pruim, R., Kaplan, D., \& Horton, N. (2018). \emph{MosaicData: Project
+mosaic data sets}. Retrieved from
+\url{https://CRAN.R-project.org/package=mosaicData}
 
@@
 
-\hypertarget{ref-quinn2011performance}{}
-Quinn, D. M., Chaudoir, S. R., \& Kallen, R. W. (2011). Performance and
-flow: A review and integration of self-objectification research.
-
 \hypertarget{ref-R-base}{}
-R Core Team. (2017). \emph{R: A language and environment for statistical
+R Core Team. (2018). \emph{R: A language and environment for statistical
 computing}. Vienna, Austria: R Foundation for Statistical Computing.
@@
 \hypertarget{ref-R-psych}{}
-Revelle, W. (2017). \emph{Psych: Procedures for psychological,
+Revelle, W. (2018). \emph{Psych: Procedures for psychological,
 psychometric, and personality research}. Evanston, Illinois:
@@
 
-\hypertarget{ref-richeson2003prejudice}{}
-Richeson, J. A., \& Shelton, J. N. (2003). When prejudice does not pay:
-Effects of interracial contact on executive function.
-\emph{Psychological Science}, \emph{14}(3), 287--290.
-
-\hypertarget{ref-riemer2020self}{}
-Riemer, A. R., Sáez, G., Brock, R., \& Gervais, S. J. (2020).
-Self-fulfilling objectification in relationships: The effects of men's
-objectifying expectations on women's self-objectification during
-conflict in romantic relationships. \emph{Self and Identity}, 1--7.
-
-\hypertarget{ref-robertsfredrickson}{}
-Roberts, T.-A., \& Fredrickson, B. L. (1997). Objectification theory.
-\emph{Encyclopedia of Social Psychology}.
-doi:\href{https://doi.org/10.4135/9781412956253.n377}{10.4135/9781412956253.n377}
-
-\hypertarget{ref-rollero2016bringing}{}
-Rollero, C. (2016). Bringing objectification into social relationships
-research: Is self-objectification harmful for authenticity?
+\hypertarget{ref-R-lavaan}{}
+Rosseel, Y. (2012). lavaan: An R package for structural equation
+modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36.
+Retrieved from \url{http://www.jstatsoft.org/v48/i02/}
 
@@
 
-\hypertarget{ref-sanchez2008romance}{}
-Sanchez, D. T., \& Broccoli, T. L. (2008). The romance of
-self-objectification: Does priming romantic relationships induce states
-of self-objectification among women? \emph{Sex Roles}, \emph{59}(7-8),
-545--554.
-
-\hypertarget{ref-shelton2005expecting}{}
-Shelton, J. N., Richeson, J. A., \& Salvatore, J. (2005). Expecting to
-be the target of prejudice: Implications for interethnic interactions.
-\emph{Personality and Social Psychology Bulletin}, \emph{31}(9),
-1189--1202.
-
-\hypertarget{ref-siever1994sexual}{}
-Siever, M. D. (1994). Sexual orientation and gender as factors in
-socioculturally acquired vulnerability to body dissatisfaction and
-eating disorders. \emph{Journal of Consulting and Clinical Psychology},
-\emph{62}(2), 252.
+\hypertarget{ref-R-lattice}{}
+Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with
+r}. New York: Springer. Retrieved from
+\url{http://lmdvr.r-forge.r-project.org}
 
@@
 \url{https://CRAN.R-project.org/package=apaTables}
-
-\hypertarget{ref-strelan2005women}{}
-Strelan, P., \& Hargreaves, D. (2005). Women who objectify other women:
-The vicious circle of objectification? \emph{Sex Roles},
-\emph{52}(9-10), 707--712.
-
-\hypertarget{ref-strelan2018birds}{}
-Strelan, P., \& Pagoudis, S. (2018). Birds of a feather flock together:
-The interpersonal process of objectification within intimate
-heterosexual relationships. \emph{Sex Roles}, \emph{79}(1-2), 72--82.
-
-\hypertarget{ref-strong2000eating}{}
-Strong, S. M., Williamson, D. A., Netemeyer, R. G., \& Geer, J. H.
-(2000). Eating disorder symptoms and concerns about body differ as a
-function of gender and sexual orientation. \emph{Journal of Social and
-Clinical Psychology}, \emph{19}(2), 240--255.
 
@@
 
-\hypertarget{ref-teran2020relational}{}
-Terán, L., Jiao, J., \& Aubrey, J. S. (2020). The relational burden of
-objectification: Exploring how past experiences of interpersonal sexual
-objectification are related to relationship competencies. \emph{Sex
-Roles}, 1--16.
-
-\hypertarget{ref-tolman2006looking}{}
-Tolman, D. L., Impett, E. A., Tracy, A. J., \& Michael, A. (2006).
-Looking good, sounding good: Femininity ideology and adolescent girls'
-mental health. \emph{Psychology of Women Quarterly}, \emph{30}(1),
-85--95.
+\hypertarget{ref-R-ggplot2}{}
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
+Springer-Verlag New York. Retrieved from
+\url{https://ggplot2.tidyverse.org}
 
@@
 
-\hypertarget{ref-wollast2020cultural}{}
-Wollast, R., Riemer, A. R., Gervais, S. J., Grigoryan, L., Bernard, P.,
-\& Klein, O. (2020). How cultural orientation and self-compassion shape
-objectified body consciousness for women from america, belgium, russia,
-and thailand. \emph{Self and Identity}, 1--21.
+\hypertarget{ref-R-forcats}{}
+Wickham, H. (2018). \emph{Forcats: Tools for working with categorical
+variables (factors)}. Retrieved from
+\url{https://CRAN.R-project.org/package=forcats}
+
+\hypertarget{ref-R-stringr}{}
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for
+common string operations}. Retrieved from
+\url{https://CRAN.R-project.org/package=stringr}
+
+\hypertarget{ref-R-tidyr}{}
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}.
+Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\hypertarget{ref-R-haven}{}
+Wickham, H., \& Miller, E. (2019). \emph{Haven: Import and export
+'spss', 'stata' and 'sas' files}. Retrieved from
+\url{https://CRAN.R-project.org/package=haven}
+
+\hypertarget{ref-R-dplyr}{}
+Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr:
+A grammar of data manipulation}. Retrieved from
+\url{https://CRAN.R-project.org/package=dplyr}
+
+\hypertarget{ref-R-devtools}{}
+Wickham, H., Hester, J., \& Chang, W. (2018). \emph{Devtools: Tools to
+make developing r packages easier}. Retrieved from
+\url{https://CRAN.R-project.org/package=devtools}
+
+\hypertarget{ref-R-readr}{}
+Wickham, H., Hester, J., \& Francois, R. (2017). \emph{Readr: Read
+rectangular text data}. Retrieved from
+\url{https://CRAN.R-project.org/package=readr}
 
@@
 
-\hypertarget{ref-R-rmarkdown}{}
-Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The
-definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved
-from \url{https://bookdown.org/yihui/rmarkdown}
-
-\hypertarget{ref-yilmaz2019whose}{}
-Yilmaz, T., \& Bozo, Ö. (2019). Whose gaze is more objectifying? An
-experimental study of college women's state self-objectification, body
-shame, negative mood, and body dissatisfaction. \emph{Mediterranean
-Journal of Clinical Psychology}, \emph{7}(2).
-
 \hypertarget{ref-young1979}{}
@@
 
-\hypertarget{ref-zurbriggen2011self}{}
-Zurbriggen, E. L., Ramsey, L. R., \& Jaworski, B. K. (2011). Self-and
-partner-objectification in romantic relationships: Associations with
-media consumption and relationship satisfaction. \emph{Sex Roles},
-\emph{64}(7-8), 449--462.
-
 \endgroup

### 2020-10-06 Final_Manuscript.Rmd
edits, almost there

@@
 classoption       : "man"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 ---
-
 ```{r setup, analysis-preferences}
@@
 ```
-
 ```{r packages, warning = FALSE, message = FALSE}
@@
 ```
-
-@robertsfredrickson Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
-The negative effects of this interpersonal objectification for women are theorized be the strongest when it is a man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction?
-Psychological researchers studying the sexual objectification of women, have in recent years explored the interpersonal process of the objectification, finding evidence for *self*-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification; @strelan2018birds; @riemer2020self].
+@robertsfredrickson's Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
+The negative effects of this interpersonal objectification for women have been theorized to be the strongest under the "male gaze," that is, when it is a percieved or actual man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction?
+Psychological researchers studying the sexual objectification of women have in recent years explored the interpersonal process of the objectification, finding evidence for *self*-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification; @strelan2018birds; @riemer2020self].
 In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO).
-The SIMO is useful for studying mixed-gender interactions, but what about interactions among women?
+The SIMO is useful for studying mixed-gender interactions, but can it be extended to interactions among women?
 Although there is evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], studies investigating the process of interpersonal objectification in interactions between women is scarce.
 
-Is objectification by a female interaction partner related to an increases in self-objectification for the woman being objectified?
-Further, does objectification by a woman have the same downstream negative consequences for women as being objectified by a male interaction partner?
-The current study begins to address these questions by investigating interpersonal objectification among interacting pairs where both partners identify as women.
+The current study uses a face-to-face interaction methodology to being to answer a series of research questions about interpersonal objectification among women: Is objectification by a female interaction partner related to an increase in self-objectification for the woman being objectified?
+Does objectification by a woman have the same downstream negative consequences for women as being objectified by a male interaction partner?
+The current study addresses these questions by investigating interpersonal objectification among interacting pairs where both partners identify as women.
+We first review the literature on self-objectification, then we review the evidence for women objectifying other women before turning to the literature on interpersonal objectification.
 
 ##Self-Objectification
-Self-objectification is a psychological process that provides that translates the experiences of interpersonal objectification [@loughnan2015exploring; @gervais2020social into negative mental health outcomes (e.g., interaction inauthenticity, anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008].
+Self-objectification is a psychological process that translates the experiences of interpersonal objectification [@loughnan2015exploring; @gervais2020social] into negative mental health outcomes [e.g., interaction inauthenticity, anxiety, lower self-esteem, and poor cognitive performance; @calogero2011; @moradi2008].
 @calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO), whereby one abopts a habitual third-person perspective on one's own appearance.
@@
 There is evidence that being objectified by another person during an interaction elicits SSO.
-For example, @loughnan2017internalizing found that for women, imagining a time when they were objectified by another person cause reductions in human traits attributed to the self, and further, the gender of the person doing the objectification was not a moderating factor.
-In addition, in a face-to-face mixed-gender dyadic study, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification as reported by their female partner.
+For example, @loughnan2017internalizing found that for women, imagining a time when they were objectified by another person caused reductions in human traits attributed to the self, and notably, the gender of the person doing the objectification was not a moderating factor.
+In addition, in a mixed-gender dyadic study of actual interactions, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification (as reported by their female partner).
 Further, this negative effect of the men's objectification on women's SSO was strongest for women higher in TSO.
@@
 Past research investigating women objectifying other women has focused on the psychological conditions that led women to objectify women.
-@harsey2020men found that self-objectification was related to the objectification of women to a similar degree for male and female participants.
+@harsey2020men found that (trait) self-objectification was related to the objectification of women to a similar degree for male and female participants.
 Along the same lines, @strelan2005women found that the more women self-objectify, the more they objectify other women.
-Could the process work in the other direction as well, that is, could objectification by a woman produce self-objectification, in a similar manner to objectification by a man?
+Could the process work in the other direction as well, that is, could objectification by a woman produce (state) self-objectification, in a similar manner to objectification by a man?
 @hill2008examining assessed women’s experiences of objectification from men independently from women’s experiences of objectification from other women.
@@
 This process, however, was not comfirmed to occur during an actual interpersonal interaction.
-@loughnan2015exploring found that women objectify other women to a greater extent than they objectify men.
-Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the proximal effects of this objectification might be.
-We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this woman to woman objectification might have detrimental outcomes.
+Thus, there is evidence that women do objectify other women, indeed, @loughnan2015exploring found that women objectify other women to a greater extent than they objectify men.
+Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the effects of this objectification might be.
+Past studies have foud that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, we do not know much about the effect of the gender of the *objectifyer* on potential detrimental outcomes.
 
@@
 Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and are likely to internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
-Interpersonal objectification has been found to have negative consequences for women.
-@gervais2011you found that an objectifying gaze by a male interaction partner (confederate) was associated with lower math performance for women, than being objectified by a female interaction partner.
+As mentiond above, interpersonal objectification has been found to have negative consequences for women.
+@gervais2011you found that an objectifying gaze by a male interaction partner (confederate) was associated with lower math performance for women than being objectified by a female interaction partner.
 Perhaps the most adverse negative consequence of interpersonal objectificaiton is that being objectified socializes girls and women to routinely treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
@@
 What is clear from @gervais2020social's review is that we know little about women-on-women interpersonal objectification.
-Could there also be negative consequences for women of interpersonal objectification by women?
+Could there also be negative consequences for women after being objectified by a woman?
 
-Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds], in addition to interactions with strangers.
-Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
-Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship.
-There is also evidence that they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], but less is known about first dates.
-An important caveat to this literature is that it is only about heterosexual relationships.
-A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
-Both romantic relationships and stranger encounters have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.
-
-There is evidence that the experience of state self-objectification in mixed-gender contexts (stranger and romantic) has negative consequences for women, but what about in the context of interactions with other women?
+Past research has found that the experience of state self-objectification in mixed-gender contexts (stranger and romantic; @strelan2018birds; @meltzer2020women) has negative consequences for women, but what about in the context of interactions with other women?
 Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
-The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010; @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and to would be helpful to understand the consequencs of this intragroup objectification for women.
+The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010; @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and it would be helpful to understand the consequencs of this *intra*group objectification for women.
 When women objectify other women, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
@@
 There is some evidence that reduced authenticity is a consequence of self-objectification [@garcia2016objectification; @teran2020relational].
-This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop; @nadal2012effects].
-Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
-When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identity threat.
-Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, specifically, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
-A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; @teran2020relational].
+A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
+This link has also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], and we might view the experience of being objectified in an interaction as a potential identity threat, stigmatizing, situation [@miles2015stop; @nadal2012effects].
+Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], an intergroup context at least in heterosexual relationships.
+Evidence for otehr adverse consquences of interpersonal objectification include reductions in career aspirations [@garcia2016objectification] and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
+These are also negative conseqences found for women under steroetype threat [@davies2005clearing].
+When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger threat.
+Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman.
+That is, the intergroup threat literature might predict that woman-woman interpersonal objectification processes diverge from mixed-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
+
+In summary, a woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting]; however, feeling like a body rather than a full human (higher SSO) in any interaction, whether intergroup or intragroup, may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; @teran2020relational].
 
@@
 Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously.
-Although the literature on woman-woman objectification is small, the results are mixed, and does not cover interpersonal encourters, we expected to replicate some of the results found in @garcia2016objectification.
-Most importantly, we predicted that being objectified by one’s interaction partner would lead to self-objectification.
+Although the literature on intragroup woman objectification is small, the results are mixed and do not cover interpersonal encourters, we expected to replicate some of the results found in @garcia2016objectification.
+Most importantly, we predicted that being objectified by one’s interaction partner would be related to state self-objectification (SSO).
 We also expected that TSO would moderate this relationship, amplifying the positive assocaition between being objectified and SSO for women higher in TSO.
 Here we would like to note that @puvia2013being would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (more precisely, to dehumanize a sexualized woman).
-In addition, @strelan2005women and @harsey2020men would predict the TSO to other-objectification link, further theorizing that this relationships is mediated by the woman's own state self-objectification (SSO).
-This limited, but extant, set of literature on woman-woman objectification points to a possible alternative model from the model hypothesized in the current study.
+In addition, @strelan2005women and @harsey2020men would also predict the TSO to other-objectification link, further theorizing that this relationship is mediated by the woman's own state self-objectification (SSO).
+Thus, the limited but extant literature on woman-woman objectification points to a possible alternative model from the model tested in the current study.
 Where appropriate, we report results considering the causal directions implied by this alternative mediation model.
@@
 We also tested whether SSO would, in turn, lead to feelings of inauthenticity.
-The investigation of the SSO - inauthenticity connection is considered exploratory given the lack of support for this connection from the literature on identity threat in intragroup interactions [@rollero2016bringing] but support for this connection in the objectification literature [@garcia2016objectification; @teran2020relational].
-Regardless of whether there was an association between SSO and inauthenticity, we hypothesized that feelings of inauthencity would be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance.
+The investigation of the SSO to inauthenticity connection is considered exploratory given the lack of support for this connection from the literature on identity threat in *intr*agroup interactions [@rollero2016bringing] but support for this connection in the objectification literature [@garcia2016objectification; @teran2020relational].
+Regardless of whether there was an association between SSO and inauthenticity, we hypothesized that feelings of inauthencity would be associated with reduced feelings of agency in romantic relationships, reduced career aspirations, and reduced cognitive performance.
 In summary, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
@@
 *All* participants were told that they were assigned to the "College Relationships" condition.
-Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because, in Westurn culture and beyond, women need to look attractive to obtain and maintain successful relationship, thus, the "College Relationships" condition may heighten self-objectification and the evaluation of other women in a sexualized way.
+Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because, in Westurn culture and beyond, women need to look attractive to obtain and maintain successful relationships, thus, the "College Relationships" condition may heighten self-objectification and the evaluation of other women in a sexualized way.
 The decision was made to ask even heterosexual women to judge their fellow-woman partners for their potential as romantic partners.
@@
 Recall that, past research has found that heterosexual women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; @puvia2013being]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.
+Analyses comparing levels of other-objectification between heterosexual and non-heterosexual women are provided in the measures section below.
 
@@
 Sample 1 originally consisted of 22 pairs, 12 men and 32 women.
-In Sample 2 there were 23 pairs made up of 43 women and one man, as well as two participants who did not identify with either gender category.
+In Sample 2 there were 23 pairs made up of 43 women and one man, as well as two participants who did not identify as either a woman or man.
 To investigate only same-gender pairs of women, we limited participant data to women in both samples.] All results presented below are from models including sample as a control variable.
@@
 There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs.
-The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs.
+The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were different racial minority group pairs.
 `r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
@@
 Actor's career aspirations")
-colnames(corr.table)   <- c("$M$", "$SD$", "1.", "2.", "3.", "4.", "5.", "6.")
+colnames(corr.table)   <- c("$M$", "$SD$", "1.", "2.", "3.", "4.", "5.", "6.", "7.")
 
@@
 
-The following measures were collected in the order they are presented following the interaction. Correlations and descriptive statistics appear in Table\ \@ref(tab:corrtable).
+The following measures were collected in the order they are presented following the interaction. Correlations and descriptive statistics of all study variables appear in Table\ \@ref(tab:corrtable).
 
@@
 Ten items were selected and presented to participants.
-For example, the correct answer for the trigram “Quack: Pond: Waddle” would be “Duck”.
-Participants are limited to 30 seconds.
+For example, the correct answer for the trigram "Quack: Pond: Waddle" would be "Duck".
+Participants are limited to 30 seconds to provide their answers.
 For every correct answer, 1 point is given.
 The mean score was `r mean_trigram` (SD = `r sd_trigram`).
-Cognitive performance was measured first in order to measure potential immediate detriments to performance [@garcia2016objectification].
+Cognitive performance was measured first directly after the intercation in order to measure potential immediate detriments to performance [@garcia2016objectification].
 
@@
 ```
-To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner [@garcia2016objectification].
+To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts during the interaction in relation to multiple characteristics of their partner [@garcia2016objectification].
 Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
@@
 ```
-To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much alike [@garcia2016objectification].
-Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: ‘‘Do you think your partner was authentic during your interaction?’’ and ‘‘Were you authentic during your interaction?’’ These questions were ranked on a scale from 1 (not at all) to 7 (very much).
+To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much like [@garcia2016objectification].
+Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: "Do you think your partner was authentic during your interaction?" and "Were you authentic during your interaction?" These questions were ranked on a scale from 1 (not at all) to 7 (very much).
 These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
@@
 To assess state self-objectification, we used an average of two items from @saguyetal2010 that were also used in @garcia2016objectification.
-Participants were asked to rank how much they agreed with the following statements: “During the interaction I felt more like a body than a full self” and “I felt more like a body than as a real person in the interaction”.
+Participants were asked to rank how much they agreed with the following statements: "During the interaction I felt more like a body than a full self" and "I felt more like a body than as a real person in the interaction".
 Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
@@
 A scale was used from @garcia2016objectification to assess how much agency an individual believes they would possess in future romantic relationships.
-Participants were asked how likely it was that they would do the following: ‘‘ask someone out on a date,’’ ‘‘open the door for your date,’’ ‘‘pay for a date,’’ ‘‘ask your boyfriend/girlfriend to marry you,’’ ‘‘initiate sex with your girlfriend/boyfriend,’’ ‘‘initiate condom use during sex,’’ ‘‘surprise your boyfriend/ girlfriend with a gift,’’ and ‘‘ask your girlfriend/boyfriend to move with you to a new place.’’ Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
+Participants were asked how likely it was that they would do the following: "ask someone out on a date," "open the door for your date," "pay for a date," "ask your boyfriend/girlfriend to marry you," "initiate sex with your girlfriend/boyfriend," "initiate condom use during sex," "surprise your boyfriend/ girlfriend with a gift," and "ask your girlfriend/boyfriend to move with you to a new place." Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
 The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
@@
 Therefore, the ninth item was removed.
-As a result, the scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
+As a result, the 8-item scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
 
@@
 ```
-We used R [Version 3.5.2; @R-base] and the R-packages *tidyverse* [Version 1.2.1; @R-tidyverse], *psych* [Version 1.8.4; @R-psych], *nlme* [Version 3.1.137; @R-nlme] for our analyses.
+We used R [Version 3.5.2; @R-base] and the R-packages *tidyverse* [Version 1.2.1; @R-tidyverse], *psych* [Version 1.8.4; @R-psych], and *nlme* [Version 3.1.137; @R-nlme] for our analyses.
 Further, we used the R-packages *papaja* [Version 0.1.0.9842; @R-papaja], *apaTables* [Version 2.0.5; @R-apaTables], with *knitr* [Version 1.25; @R-knitr] to create a fully reproducible manuscript in *rmarkdown* [Version 1.15; @R-rmarkdown].
@@
 The R-package *papaja* [Version 0.1.0.9842; @R-papaja] was used to create a fully reproducible research document containing the analysis code and manuscript text integrated into one source file.
-The benefit of this integration is that the numbers reported throughout this document are softcoded into the text, ensuring that no errors were made during a workflow marked by a copy-and-paste from statistical software to word processing software.
-Note that here we are using the term reproducibility to mean getting the same results when running analyses again using the same data, not to be confused with replicability meaning collecting a new dataset using the same methods and obtaining the same results [@patil2016statistical].
+The benefit of this integration is that the numbers reported throughout this document are softcoded into the text, ensuring that no errors were made during a workflow marked by copying and pasting from statistical software to word processing software.
+Note that here we are using the term reproducibility to mean getting the same results when running analyses again using the *same* data, not to be confused with replicability meaning collecting a new dataset using the same methods and obtaining the same results [@patil2016statistical].
 The source code for this manuscript along with survey materials and experimenter scripts for the study protocol are all avaliable at https://github.com/kkyuchukova/object-in-action.
@@
 This study sought to detect whether partners’ objectification of one another affected state self-objectification (SSO).
-Specifically, we were interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, may or may not affects feelings of inauthenticity during the interaction.
+Specifically, we were interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, may or may not affect feelings of inauthenticity during the interaction.
 In addition, we also tested if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification (moderation effect).
@@
 While past studies investigating objectification in interactions used dyadic path analysis [@garcia2016objectification], the current study used multilevel modeling proceedures.
-Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs), as we had in the current study [@ledermann2017analyzing; @garcia2015moderation].
+Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural using Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs), as we had in the current study [@ledermann2017analyzing; @garcia2015moderation].
 One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means), but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural].
@@
 The current study used dyadic multilevel modeling (MLM) to test all relationships, moderation, and mediation patterns.
-The online supplementary materials found at https://github.com/kkyuchukova/object-in-action contain model estimates obtained with SEM.
+The online supplementary materials found at https://github.com/kkyuchukova/object-in-action contain model estimates obtained using SEM.
 See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.
@@
 Testing hypotheses and exploring relationships in the current sample of indistinguishable dyads involved using the Actor-Partner Independence Model (APIM) approach for each outcome variable.
-The current study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary.
-Thus, we ran five APIM's to test all the relationships (i.e., for SSO, inauthenticity, career aspirations, relationship agency, and cognitive performance as outcome variables).
 See Figure\ \@ref(fig:apim) for a basic APIM model.
 The APIM includes effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$).
-The analysis of the relationship between SSO and inauthenticity in this same-gender sample are considered exploratory, given that prior research points to mixed possibilities.
+The current study deals with indistinguishable dyads, meaning the designation of who is the "actor" and who is the "partner" is arbitrary.
+In total we ran five APIM's---one for each outcome variable---to test the series of the relationships proposed (i.e., for SSO, inauthenticity, career aspirations, relationship agency, and cognitive performance).
 
@@
 ```{r}
-# apim0 <- gls(a2pSOO_A ~ TSO_A, 
-#                  na.action=na.omit, 
-#                  correlation=corCompSymm (form=~1|dyadID),
-#                  data=clarksmith_women)
-# summary(apim0)
+apim0 <- gls(a2pSOO_A ~ TSO_A, 
+                  na.action=na.omit, 
+                  correlation=corCompSymm (form=~1|dyadID),
+                  data=clarksmith_women)
+summary(apim0)
 
@@
 
-The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO).
+First, use used to the APIM to test for evidence of a partner effect of other objectification and SSO in this sample of same-gender woman-woman interacting dyads.
+In @garcia2016objectification men's objectification of women was significantly related to women's SSO, the current study sought to replicate this effect.
 As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically significant, `r report_stats(apim1, 3)`.
+That is, the extent to which one's partner reported thinking about a woman's external characteristics more than her internal characteristics was significantly related to the woman's own reported feeling more like a body than a full self.
+Along side the @garcia2016objectification study, there is now evidence that interpersonal objectification in an actual interpersonal encounter is realted to state self-objectification for women both when the objectifyer is a man and when the objectifyer is a woman.
+
+In addition to partner other-objectification, this model also included one's own objectification of their partner (actor other-objectification), actor trait self-objectification (TSO), and the interaction of partner other-objectification and TSO.
 One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
-Inconsistent with past findings however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
+Further, inconsistent with past findings however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
 There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.
+The $R^2$ of this model was `r round(apim1_r2,2)`.
+As a test of the potential alternative models discussed above, we ran a MLM with other-objectification predicted by actor TSO but there was no statistically significant relationship between these two variables, `r report_stats(apim0, 2)`.
 
+We next moved on to test the link between SSO and interaction authenticity.
 There was no significant effect of SSO on interaction authenticity, although the estimate of this effect was in the hypothesized negative direction, `r report_stats(apim2, 2)`.
@@
 Although we hypothesized that SSO would mediate the relationship between partner's other objectification and interaction authenticity, after finding no relationship between SSO and authenticity, we also tested if the partner's other objectification had a direct effect on authenticity, but this effect was not significant, `r report_stats(apim2.b, 3)` (nor was the total effect of partner's other objectification on authenticity, `r report_stats(apim2.c, 2)`).
+Note that these analyses of the relationship between SSO and inauthenticity in this same-gender sample were considered exploratory, given that prior research on intragroup interactions points to mixed possibilities.
 
-Lastly, although there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performance, career aspirations, and relationship agency, as it did in @garcia2016objectification.
-We again used MLM and thus, these effects were tested in three separate models.
-There was no significant effect of interaction authenticity on cognitive performance, `r report_stats(apim3, 2)`, but authenticity was significantly positively related to both career aspirations, `r report_stats(apim5, 2)`, and relationship agency, `r report_stats(apim4, 2)`.
-There was no direct effect of SSO on cognitive performance, `r report_stats(apim3.b, 3)`, and no direct effect of partner's other objectification on cognitive performance, `r report_stats(apim3.c, 4)`.
+Lastly, although there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performance, career aspirations, and relationship agency, as it did in @garcia2016objectification and as would be predicted by @teran2020relational.
+We again used MLM and thus, these effects were tested in three separate multilevel linear models.
+There was no significant effect of interaction authenticity on cognitive performance, `r report_stats(apim3, 2)`, but authenticity was significantly positively related to both career aspirations, `r report_stats(apim5, 2)` ($R^2 =$ `r round(apim5_r2,2)`), and relationship agency, `r report_stats(apim4, 2)` ($R^2 =$ `r round(apim4_r2,2)`).^[There was no direct effect of SSO on cognitive performance, `r report_stats(apim3.b, 3)`, and no direct effect of partner's other objectification on cognitive performance, `r report_stats(apim3.c, 4)`.
 There was no direct effect of SSO on career aspirations, `r report_stats(apim5.b, 3)`, and no direct effect of partner's other objectification on career aspirations, `r report_stats(apim5.c, 4)`.
-There was no direct effect of SSO on relationship agency, `r report_stats(apim4.b, 3)`, and no direct effect of partner's other objectification on relationship agency, `r report_stats(apim4.c, 4)`.
+There was no direct effect of SSO on relationship agency, `r report_stats(apim4.b, 3)`, and no direct effect of partner's other objectification on relationship agency, `r report_stats(apim4.c, 4)`.]
 
@@
 
+Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
+Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship.
+There is also evidence that they experience less SSO after appearance comments within romantic relationships [], but less is known about first dates.
+An important caveat to this literature is that it is only about heterosexual relationships.
+
 However, since both men and women are socialized in a culture that sexually objectifies women, both men and women may come to internalize this socialization and sexually objectify women.

### 2020-10-06 Final_Manuscript.tex
edits, almost there

@@
 
-Barbara L Fredrickson and Roberts (1997) Objectification Theory,
-suggests that, in addition to being steeped in a culture that
-objectifies women, women are objectified in actual interpersonal
-encounters. The negative effects of this interpersonal objectification
-for women are theorized be the strongest when it is a man doing the
-objectifying (Calogero, 2004; Gay \& Castano, 2010; Gervais, Vescio, \&
-Allen, 2011), but what are the consequences when a woman objectifies
-another woman in an interaction? Psychological researchers studying the
-sexual objectification of women, have in recent years explored the
-interpersonal process of the objectification, finding evidence for
-\emph{self}-objectification in the target as a proximal consequence of
-being objectified (Garcia et al., 2016; Riemer, Sáez, Brock, \& Gervais,
-2020; Strelan \& Pagoudis, 2018). In a recent review, Gervais et al.
-(2020) organized the extant literature on interpersonal
-self-objectification and proposed a theoretical model called the Social
-Interaction Model of Objectification (SIMO). The SIMO is useful for
-studying mixed-gender interactions, but what about interactions among
-women? Although there is evidence that women objectify other women
-(Loughnan et al., 2015a; Puvia \& Vaes, 2013), studies investigating the
-process of interpersonal objectification in interactions between women
-is scarce.
-
-Is objectification by a female interaction partner related to an
-increases in self-objectification for the woman being objectified?
-Further, does objectification by a woman have the same downstream
-negative consequences for women as being objectified by a male
-interaction partner? The current study begins to address these questions
-by investigating interpersonal objectification among interacting pairs
-where both partners identify as women.
+Fredrickson and Roberts (1997)'s Objectification Theory, suggests that,
+in addition to being steeped in a culture that objectifies women, women
+are objectified in actual interpersonal encounters. The negative effects
+of this interpersonal objectification for women have been theorized to
+be the strongest under the \enquote{male gaze,} that is, when it is a
+percieved or actual man doing the objectifying (Calogero, 2004; Gay \&
+Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
+consequences when a woman objectifies another woman in an interaction?
+Psychological researchers studying the sexual objectification of women
+have in recent years explored the interpersonal process of the
+objectification, finding evidence for \emph{self}-objectification in the
+target as a proximal consequence of being objectified (Garcia et al.,
+2016; Riemer, Sáez, Brock, \& Gervais, 2020; Strelan \& Pagoudis, 2018).
+In a recent review, Gervais et al. (2020) organized the extant
+literature on interpersonal self-objectification and proposed a
+theoretical model called the Social Interaction Model of Objectification
+(SIMO). The SIMO is useful for studying mixed-gender interactions, but
+can it be extended to interactions among women? Although there is
+evidence that women objectify other women (Loughnan et al., 2015a; Puvia
+\& Vaes, 2013), studies investigating the process of interpersonal
+objectification in interactions between women is scarce.
+
+The current study uses a face-to-face interaction methodology to being
+to answer a series of research questions about interpersonal
+objectification among women: Is objectification by a female interaction
+partner related to an increase in self-objectification for the woman
+being objectified? Does objectification by a woman have the same
+downstream negative consequences for women as being objectified by a
+male interaction partner? The current study addresses these questions by
+investigating interpersonal objectification among interacting pairs
+where both partners identify as women. We first review the literature on
+self-objectification, then we review the evidence for women objectifying
+other women before turning to the literature on interpersonal
+objectification.
 
@@
 
-Self-objectification is a psychological process that provides that
-translates the experiences of interpersonal objectification {[}Loughnan
-et al. (2015a); Gervais et al. (2020) into negative mental health
-outcomes (e.g., interaction inauthenticity, anxiety, self-esteem, and
-cognitive performance) (Calogero, Tantleff-Dunn, \& Thompson, 2011;
+Self-objectification is a psychological process that translates the
+experiences of interpersonal objectification (Gervais et al., 2020;
+Loughnan et al., 2015a) into negative mental health outcomes (e.g.,
+interaction inauthenticity, anxiety, lower self-esteem, and poor
+cognitive performance; Calogero, Tantleff-Dunn, \& Thompson, 2011;
 Moradi \& Huang, 2008). Calogero et al. (2011) proposes that
@@
 and Elder (2017) found that for women, imagining a time when they were
-objectified by another person cause reductions in human traits
-attributed to the self, and further, the gender of the person doing the
+objectified by another person caused reductions in human traits
+attributed to the self, and notably, the gender of the person doing the
 objectification was not a moderating factor. In addition, in a
-face-to-face mixed-gender dyadic study, Garcia et al. (2016) found that
-men's reported objectification of their female interaction partner was
-associated with increased self-objectification as reported by their
-female partner. Further, this negative effect of the men's
+mixed-gender dyadic study of actual interactions, Garcia et al. (2016)
+found that men's reported objectification of their female interaction
+partner was associated with increased self-objectification (as reported
+by their female partner). Further, this negative effect of the men's
 objectification on women's SSO was strongest for women higher in TSO.
@@
 on the psychological conditions that led women to objectify women.
-Harsey and Zurbriggen (2020) found that self-objectification was related
-to the objectification of women to a similar degree for male and female
-participants. Along the same lines, Strelan and Hargreaves (2005) found
-that the more women self-objectify, the more they objectify other women.
-Could the process work in the other direction as well, that is, could
-objectification by a woman produce self-objectification, in a similar
-manner to objectification by a man? Hill and Fischer (2008) assessed
-women's experiences of objectification from men independently from
-women's experiences of objectification from other women. They found that
-women may be socialized not only to see themselves as objects, but
+Harsey and Zurbriggen (2020) found that (trait) self-objectification was
+related to the objectification of women to a similar degree for male and
+female participants. Along the same lines, Strelan and Hargreaves (2005)
+found that the more women self-objectify, the more they objectify other
+women. Could the process work in the other direction as well, that is,
+could objectification by a woman produce (state) self-objectification,
+in a similar manner to objectification by a man? Hill and Fischer (2008)
+assessed women's experiences of objectification from men independently
+from women's experiences of objectification from other women. They found
+that women may be socialized not only to see themselves as objects, but
 perhaps to see other women as objects as well. This process, however,
 was not comfirmed to occur during an actual interpersonal interaction.
+Thus, there is evidence that women do objectify other women, indeed,
 Loughnan et al. (2015a) found that women objectify other women to a
@@
 Vaes, 2013), but very little is known about interpersonal sexual
-objectification among women and what the proximal effects of this
-objectification might be. We do know that objectification has more
-adverse consequences for women than men (Gervais et al., 2011; Moradi \&
-Huang, 2008; Saguy et al., 2010), however, if women objectify other
-women, perhaps even to a stronger degree than they objectify men, this
-woman to woman objectification might have detrimental outcomes.
+objectification among women and what the effects of this objectification
+might be. Past studies have foud that objectification has more adverse
+consequences for women than men (Gervais et al., 2011; Moradi \& Huang,
+2008; Saguy et al., 2010), however, we do not know much about the effect
+of the gender of the \emph{objectifyer} on potential detrimental
+outcomes.
 
@@
 objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
-1979). Interpersonal objectification has been found to have negative
-consequences for women. Gervais et al. (2011) found that an objectifying
-gaze by a male interaction partner (confederate) was associated with
-lower math performance for women, than being objectified by a female
-interaction partner. Perhaps the most adverse negative consequence of
-interpersonal objectificaiton is that being objectified socializes girls
-and women to routinely treat themselves as objects to be looked at and
-evaluated (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; Barbara L
-Fredrickson et al., 1998). Gervais et al. (2020) recently reviewed the
-research on interpersonal objectification and organized our current
-theoretical understanding of this process in the Social Interaction
-Model of Objectification (SIMO). What is clear from Gervais et al.
-(2020)'s review is that we know little about women-on-women
-interpersonal objectification. Could there also be negative consequences
-for women of interpersonal objectification by women?
-
-Researchers have also studied interpersonal objectification and
-self-objectification in romantic relationships (Strelan \& Pagoudis,
-2018), in addition to interactions with strangers. Among heterosexual
-male and female college students, self-objectification has been found to
-be positively associated with the extent to which they objectify their
-romantic partners (Zurbriggen, Ramsey, \& Jaworski, 2011). Evidence is
-mixed, suggesting that women can sometimes have positive outcomes from
-appearance valuation within the context of an established romantic
-relationship. There is also evidence that they experience less SSO after
-appearance comments within romantic relationships (Meltzer, 2020), but
-less is known about first dates. An important caveat to this literature
-is that it is only about heterosexual relationships. A recent study has
-investigated the effect of self-objectification on the reduction of
-relationship building skills in general (including same-sex friendships)
-(Terán, Jiao, \& Aubrey, 2020). Both romantic relationships and stranger
-encounters have been studied in the context of objectification, but
-neither of these literatures have investigated specifically same-gender
-relationships.
-
-There is evidence that the experience of state self-objectification in
-mixed-gender contexts (stranger and romantic) has negative consequences
+1979). As mentiond above, interpersonal objectification has been found
+to have negative consequences for women. Gervais et al. (2011) found
+that an objectifying gaze by a male interaction partner (confederate)
+was associated with lower math performance for women than being
+objectified by a female interaction partner. Perhaps the most adverse
+negative consequence of interpersonal objectificaiton is that being
+objectified socializes girls and women to routinely treat themselves as
+objects to be looked at and evaluated (Bartky, 1990; Berger, Cohen, \&
+Zelditch Jr, 1972; Barbara L Fredrickson et al., 1998). Gervais et al.
+(2020) recently reviewed the research on interpersonal objectification
+and organized our current theoretical understanding of this process in
+the Social Interaction Model of Objectification (SIMO). What is clear
+from Gervais et al. (2020)'s review is that we know little about
+women-on-women interpersonal objectification. Could there also be
+negative consequences for women after being objectified by a woman?
+
+Past research has found that the experience of state
+self-objectification in mixed-gender contexts (stranger and romantic;
+Strelan and Pagoudis (2018); Meltzer (2020)) has negative consequences
 for women, but what about in the context of interactions with other
@@
 there is evidence that women do objectify other women (Harsey \&
-Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and to
-would be helpful to understand the consequencs of this intragroup
+Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and it
+would be helpful to understand the consequencs of this \emph{intra}group
 objectification for women. When women objectify other women, does it
@@
 There is some evidence that reduced authenticity is a consequence of
-self-objectification (Garcia et al., 2016; Terán et al., 2020). This
-link has been justified by the literature on stigmatized-stigmatizer
-interactions (M. R. Hebl \& Dovidio, 2005; Richeson \& Shelton, 2003;
-Shelton, Richeson, \& Salvatore, 2005), viewing the experience of being
-objectified in an interaction as an identity threat situation
-(Miles-McLean et al., 2015; Nadal \& Haynes, 2012). Further, empirical
-evidence reveals that objectification manifests through inauthenticity
-in romantic relationships (Brunell et al., 2010), adverse attitudes in
-regard to career aspirations, and a decrease in concentration and
-impairment in female cognitive performance (Kahalon, Shnabel, \& Becker,
-2018; D. M. Quinn, Chaudoir, \& Kallen, 2011). When a woman is
-objectified by a man, and subsequently experiences self-objectification,
-the intergroup nature of this encounter might trigger identity threat.
-Thus, perhaps there are fewer negative consequences when a woman is
-objectified by another woman, specifically, woman-woman interpersonal
-objectification processes might diverge from mix-gender interpersonal
-objectification processes precisely because they are not intergroup
-interactions (at least with respect to gender identity). A woman
-objectified by another woman may not be having the same negative
-consequences that cascade from situations that trigger group-based
-identity threat (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \&
-Shelton, 2006; M. R. Hebl \& Dovidio, 2005), but feeling like a body,
-rather than a full human, in any interaction (intergroup or ingroup) may
-be enough to reduce women's feelings of authenticity and social
-competence, regardless of the gender of the objectifyer (Terán et al.,
-2020; Tolman, Impett, Tracy, \& Michael, 2006).
+self-objectification (Garcia et al., 2016; Terán, Jiao, \& Aubrey,
+2020). A recent study has investigated the effect of
+self-objectification on the reduction of relationship building skills in
+general (including same-sex friendships) (Terán et al., 2020). This link
+has also been found in research on stigmatized-stigmatizer interactions
+(M. R. Hebl \& Dovidio, 2005; Richeson \& Shelton, 2003; Shelton,
+Richeson, \& Salvatore, 2005), and we might view the experience of being
+objectified in an interaction as a potential identity threat,
+stigmatizing, situation (Miles-McLean et al., 2015; Nadal \& Haynes,
+2012). Further, empirical evidence reveals that objectification
+manifests through inauthenticity in romantic relationships (Brunell et
+al., 2010), an intergroup context at least in heterosexual
+relationships. Evidence for otehr adverse consquences of interpersonal
+objectification include reductions in career aspirations (Garcia et al.,
+2016) and a decrease in concentration and impairment in female cognitive
+performance (Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn, Chaudoir,
+\& Kallen, 2011). These are also negative conseqences found for women
+under steroetype threat (Davies, Spencer, \& Steele, 2005). When a woman
+is objectified by a man, and subsequently experiences
+self-objectification, the intergroup nature of this encounter might
+trigger threat. Thus, perhaps there are fewer negative consequences when
+a woman is objectified by another woman. That is, the intergroup threat
+literature might predict that woman-woman interpersonal objectification
+processes diverge from mixed-gender interpersonal objectification
+processes precisely because they are not intergroup interactions (at
+least with respect to gender identity).
+
+In summary, a woman objectified by another woman may not be having the
+same negative consequences that cascade from situations that trigger
+group-based identity threat (Deaux \& Major, 1987; Dovidio, Hebl,
+Richeson, \& Shelton, 2006; M. R. Hebl \& Dovidio, 2005); however,
+feeling like a body rather than a full human (higher SSO) in any
+interaction, whether intergroup or intragroup, may be enough to reduce
+women's feelings of authenticity and social competence, regardless of
+the gender of the objectifyer (Terán et al., 2020; Tolman, Impett,
+Tracy, \& Michael, 2006).
 
@@
 examine the effects for both women simultaneously. Although the
-literature on woman-woman objectification is small, the results are
-mixed, and does not cover interpersonal encourters, we expected to
+literature on intragroup woman objectification is small, the results are
+mixed and do not cover interpersonal encourters, we expected to
 replicate some of the results found in Garcia et al. (2016). Most
 importantly, we predicted that being objectified by one's interaction
-partner would lead to self-objectification. We also expected that TSO
-would moderate this relationship, amplifying the positive assocaition
-between being objectified and SSO for women higher in TSO. Here we would
-like to note that Puvia and Vaes (2013) would alternatively predict that
-women's tendency to self-objectify (TSO) leads them to objectify other
-women (more precisely, to dehumanize a sexualized woman). In addition,
-Strelan and Hargreaves (2005) and Harsey and Zurbriggen (2020) would
-predict the TSO to other-objectification link, further theorizing that
-this relationships is mediated by the woman's own state
-self-objectification (SSO). This limited, but extant, set of literature
-on woman-woman objectification points to a possible alternative model
-from the model hypothesized in the current study. Where appropriate, we
-report results considering the causal directions implied by this
-alternative mediation model.
+partner would be related to state self-objectification (SSO). We also
+expected that TSO would moderate this relationship, amplifying the
+positive assocaition between being objectified and SSO for women higher
+in TSO. Here we would like to note that Puvia and Vaes (2013) would
+alternatively predict that women's tendency to self-objectify (TSO)
+leads them to objectify other women (more precisely, to dehumanize a
+sexualized woman). In addition, Strelan and Hargreaves (2005) and Harsey
+and Zurbriggen (2020) would also predict the TSO to
+other-objectification link, further theorizing that this relationship is
+mediated by the woman's own state self-objectification (SSO). Thus, the
+limited but extant literature on woman-woman objectification points to a
+possible alternative model from the model tested in the current study.
+Where appropriate, we report results considering the causal directions
+implied by this alternative mediation model.
 
 We also tested whether SSO would, in turn, lead to feelings of
-inauthenticity. The investigation of the SSO - inauthenticity connection
-is considered exploratory given the lack of support for this connection
-from the literature on identity threat in intragroup interactions
-(Rollero, 2016) but support for this connection in the objectification
-literature (Garcia et al., 2016; Terán et al., 2020). Regardless of
-whether there was an association between SSO and inauthenticity, we
-hypothesized that feelings of inauthencity would be associated with
-reduced feelings of agency in romantic relationships, reduced career
-aspiration, and reduced cognitive performance. In summary, we expected
-to find a positive relationship between other-objectification by one's
-partner and state self-objectification. We also expected to find a
-negative relationship between self-state objectification and interaction
-authenticity, and that interaction authenticity will be positively
-related to cognitive performance, relationship agency, and career
-aspirations.
+inauthenticity. The investigation of the SSO to inauthenticity
+connection is considered exploratory given the lack of support for this
+connection from the literature on identity threat in \emph{intr}agroup
+interactions (Rollero, 2016) but support for this connection in the
+objectification literature (Garcia et al., 2016; Terán et al., 2020).
+Regardless of whether there was an association between SSO and
+inauthenticity, we hypothesized that feelings of inauthencity would be
+associated with reduced feelings of agency in romantic relationships,
+reduced career aspirations, and reduced cognitive performance. In
+summary, we expected to find a positive relationship between
+other-objectification by one's partner and state self-objectification.
+We also expected to find a negative relationship between self-state
+objectification and interaction authenticity, and that interaction
+authenticity will be positively related to cognitive performance,
+relationship agency, and career aspirations.
 
@@
 Broccoli, 2008) because, in Westurn culture and beyond, women need to
-look attractive to obtain and maintain successful relationship, thus,
+look attractive to obtain and maintain successful relationships, thus,
 the \enquote{College Relationships} condition may heighten
@@
 thought pattern will translate to their thoughts about other women.
+Analyses comparing levels of other-objectification between heterosexual
+and non-heterosexual women are provided in the measures section below.
 
@@
   there were 23 pairs made up of 43 women and one man, as well as two
-  participants who did not identify with either gender category. To
+  participants who did not identify as either a woman or man. To
   investigate only same-gender pairs of women, we limited participant
@@
 The remaining 20 were mixed race pairs, of which 15 were White/racial
-minority pairings and 5 were cross-racial minority group pairs. 64.06\%
-of the sample identified as heterosexual, and 25\% identified as gay,
-lesbian or bisexual. See the analysis of differences between
+minority pairings and 5 were different racial minority group pairs.
+64.06\% of the sample identified as heterosexual, and 25\% identified as
+gay, lesbian or bisexual. See the analysis of differences between
 heteroseuxal and non-heterosexual women in levels of
@@
 The following measures were collected in the order they are presented
-following the interaction. Correlations and descriptive statistics
-appear in Table~\ref{tab:corrtable}.
+following the interaction. Correlations and descriptive statistics of
+all study variables appear in Table~\ref{tab:corrtable}.
 
@@
 correct answer for the trigram \enquote{Quack: Pond: Waddle} would be
-\enquote{Duck}. Participants are limited to 30 seconds. For every
-correct answer, 1 point is given. The mean score was 5.03 (SD = 2.29).
-Cognitive performance was measured first in order to measure potential
-immediate detriments to performance (Garcia et al., 2016).
+\enquote{Duck}. Participants are limited to 30 seconds to provide their
+answers. For every correct answer, 1 point is given. The mean score was
+5.03 (SD = 2.29). Cognitive performance was measured first directly
+after the intercation in order to measure potential immediate detriments
+to performance (Garcia et al., 2016).
 
@@
 interaction, participants were asked a series of questions about the
-frequency of thoughts in relation to multiple characteristics of their
-partner (Garcia et al., 2016). Questions included aspects of their
-partner's internal traits such as personality, friends, family, and
-extracurricular interests, as well as external traits such as body,
-appearance, clothing, and body parts. All questions were rated on a
-scale from 1 (not at all) to 7 (constantly). Objectification was
-measured by taking the difference between the average frequency of
-thought about their partner's external traits (\(\alpha\) = 0.79 for
-Sample 1, \(\alpha\) = 0.79 for Sample 2) and frequency of thought about
-their partner's internal traits (\(\alpha\) = 0.79 for Sample 1,
-\(\alpha\) = 0.76 for Sample 2). A positive score in this scale would
-indicate that the participant thought about their partner's external
-traits more than the partner's internal traits, and a negative score
-would indicate the opposite.
+frequency of thoughts during the interaction in relation to multiple
+characteristics of their partner (Garcia et al., 2016). Questions
+included aspects of their partner's internal traits such as personality,
+friends, family, and extracurricular interests, as well as external
+traits such as body, appearance, clothing, and body parts. All questions
+were rated on a scale from 1 (not at all) to 7 (constantly).
+Objectification was measured by taking the difference between the
+average frequency of thought about their partner's external traits
+(\(\alpha\) = 0.79 for Sample 1, \(\alpha\) = 0.79 for Sample 2) and
+frequency of thought about their partner's internal traits (\(\alpha\) =
+0.79 for Sample 1, \(\alpha\) = 0.76 for Sample 2). A positive score in
+this scale would indicate that the participant thought about their
+partner's external traits more than the partner's internal traits, and a
+negative score would indicate the opposite.
 
@@
 friendly, warm, easygoing, sincere, and authentic on a scale ranging
-from 1 (not at all) to 7 (very much), much alike (Garcia et al., 2016).
+from 1 (not at all) to 7 (very much), much like (Garcia et al., 2016).
 Participants were additionally asked to rate their interaction partner's
-authenticity as well as their own: \enquote{`Do you think your partner
-was authentic during your interaction?}' and \enquote{`Were you
-authentic during your interaction?}' These questions were ranked on a
-scale from 1 (not at all) to 7 (very much). These were combined to form
-the authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) =
-0.91 for Sample 2).
+authenticity as well as their own: \enquote{Do you think your partner
+was authentic during your interaction?} and \enquote{Were you authentic
+during your interaction?} These questions were ranked on a scale from 1
+(not at all) to 7 (very much). These were combined to form the
+authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) = 0.91
+for Sample 2).
 
@@
 Participants were asked how likely it was that they would do the
-following: \enquote{`ask someone out on a date,}' \enquote{`open the
-door for your date,}' \enquote{`pay for a date,}' \enquote{`ask your
-boyfriend/girlfriend to marry you,}' \enquote{`initiate sex with your
-girlfriend/boyfriend,}' \enquote{`initiate condom use during sex,}'
-\enquote{`surprise your boyfriend/ girlfriend with a gift,}' and
-\enquote{`ask your girlfriend/boyfriend to move with you to a new
-place.}' Responses were measured on a scale ranging from 1 (not at all
-likely) to 7 (extremely likely). The scale originally had 9 items, but
-the 9th item had low correlations with the remaining items, ranging from
-.02 to .30 for the first sample, and .04 to .30 for the second sample.
-The item was intended to be reverse coded, but correlations were still
-low enough to make the scale unreliable. Therefore, the ninth item was
-removed. As a result, the scale had moderately high reliability for both
+following: \enquote{ask someone out on a date,} \enquote{open the door
+for your date,} \enquote{pay for a date,} \enquote{ask your
+boyfriend/girlfriend to marry you,} \enquote{initiate sex with your
+girlfriend/boyfriend,} \enquote{initiate condom use during sex,}
+\enquote{surprise your boyfriend/ girlfriend with a gift,} and
+\enquote{ask your girlfriend/boyfriend to move with you to a new place.}
+Responses were measured on a scale ranging from 1 (not at all likely) to
+7 (extremely likely). The scale originally had 9 items, but the 9th item
+had low correlations with the remaining items, ranging from .02 to .30
+for the first sample, and .04 to .30 for the second sample. The item was
+intended to be reverse coded, but correlations were still low enough to
+make the scale unreliable. Therefore, the ninth item was removed. As a
+result, the 8-item scale had moderately high reliability for both
 samples (\(\alpha\) = 0.72 for Sample 1, (\(\alpha\) = 0.74 for Sample
@@
 \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{psych} (Version
-1.8.4; Revelle, 2017), \emph{nlme} (Version 3.1.137; Pinheiro, Bates,
-DebRoy, Sarkar, \& R Core Team, 2017) for our analyses. Further, we used
-the R-packages \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018),
-\emph{apaTables} (Version 2.0.5; Stanley, 2018), with \emph{knitr}
-(Version 1.25; Xie, 2015) to create a fully reproducible manuscript in
-\emph{rmarkdown} (Version 1.15; Xie, Allaire, \& Grolemund, 2018).
+1.8.4; Revelle, 2017), and \emph{nlme} (Version 3.1.137; Pinheiro,
+Bates, DebRoy, Sarkar, \& R Core Team, 2017) for our analyses. Further,
+we used the R-packages \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
+2018), \emph{apaTables} (Version 2.0.5; Stanley, 2018), with
+\emph{knitr} (Version 1.25; Xie, 2015) to create a fully reproducible
+manuscript in \emph{rmarkdown} (Version 1.15; Xie, Allaire, \&
+Grolemund, 2018).
 
@@
 document are softcoded into the text, ensuring that no errors were made
-during a workflow marked by a copy-and-paste from statistical software
-to word processing software. Note that here we are using the term
-reproducibility to mean getting the same results when running analyses
-again using the same data, not to be confused with replicability meaning
-collecting a new dataset using the same methods and obtaining the same
-results (Patil, Peng, \& Leek, 2016). The source code for this
-manuscript along with survey materials and experimenter scripts for the
-study protocol are all avaliable at
+during a workflow marked by copying and pasting from statistical
+software to word processing software. Note that here we are using the
+term reproducibility to mean getting the same results when running
+analyses again using the \emph{same} data, not to be confused with
+replicability meaning collecting a new dataset using the same methods
+and obtaining the same results (Patil, Peng, \& Leek, 2016). The source
+code for this manuscript along with survey materials and experimenter
+scripts for the study protocol are all avaliable at
 \url{https://github.com/kkyuchukova/object-in-action}. The data
@@
 interested in testing the relationship between state-other
-objectification and SSO, and how SSO in turn, may or may not affects
+objectification and SSO, and how SSO in turn, may or may not affect
 feelings of inauthenticity during the interaction. In addition, we also
@@
 multilevel modeling proceedures. Dyadic analyses for distinguishable
-dyads (e.g., mixed-gender interacting pairs) is more natural in
+dyads (e.g., mixed-gender interacting pairs) is more natural using
 Structural Equation Modeling (SEM) than it is for indistinguishable
@@
 \url{https://github.com/kkyuchukova/object-in-action} contain model
-estimates obtained with SEM. See Ledermann and Kenny (2017) for a more
+estimates obtained using SEM. See Ledermann and Kenny (2017) for a more
 complete discussion of the considerations for using SEM versus MLM for
@@
 indistinguishable dyads involved using the Actor-Partner Independence
-Model (APIM) approach for each outcome variable. The current study deals
-with indistinguishable dyads, meaning the designation of who is
-designated as \enquote{actor} and who is designated as \enquote{partner}
-is arbitrary. Thus, we ran five APIM's to test all the relationships
-(i.e., for SSO, inauthenticity, career aspirations, relationship agency,
-and cognitive performance as outcome variables). See
+Model (APIM) approach for each outcome variable. See
 Figure~\ref{fig:apim} for a basic APIM model. The APIM includes effects
 due to one's own, as well as one's partner's, predictor variables
-(\(X\)'s) on the one's own outcome variable (\(Y\)). The analysis of the
-relationship between SSO and inauthenticity in this same-gender sample
-are considered exploratory, given that prior research points to mixed
-possibilities.
+(\(X\)'s) on the one's own outcome variable (\(Y\)). The current study
+deals with indistinguishable dyads, meaning the designation of who is
+the \enquote{actor} and who is the \enquote{partner} is arbitrary. In
+total we ran five APIM's---one for each outcome variable---to test the
+series of the relationships proposed (i.e., for SSO, inauthenticity,
+career aspirations, relationship agency, and cognitive performance).
 
@@
 
-The most important finding from Garcia et al. (2016) was the significant
-partner effect of other objectification and SSO (specifically men's
-objectification of women and women's SSO). As expected, the partner
-effect of other-objectification on SSO in the current all-women sample
-was statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12,
-\emph{p} = .019. One's own other objectification had no effect on SSO,
-\emph{b} = -0.16, \emph{SE} = 0.12, \emph{p} = .210. Inconsistent with
-past findings however, there was no statistically significant
-interaction of partner's other objectification and the person's trait
-self-objectification on SSO, \emph{b} = 0.03, \emph{SE} = 0.27, \emph{p}
-= .910. There was also no significant main effect of trait
-self-objectification on SSO \emph{b} = 0.07, \emph{SE} = 0.05, \emph{p}
-= .183.
-
-There was no significant effect of SSO on interaction authenticity,
-although the estimate of this effect was in the hypothesized negative
-direction, \emph{b} = -0.09, \emph{SE} = 0.12, \emph{p} = .431. Because
-authenticity was a composite score of 9 items, two of which were
-interaction specific authenticity items, we also estimated the pairwise
-correlations between SSO and all these items individually. They were all
-small, ranging from only -0.01 to -0.14. Although we hypothesized that
-SSO would mediate the relationship between partner's other
-objectification and interaction authenticity, after finding no
-relationship between SSO and authenticity, we also tested if the
-partner's other objectification had a direct effect on authenticity, but
-this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
+First, use used to the APIM to test for evidence of a partner effect of
+other objectification and SSO in this sample of same-gender woman-woman
+interacting dyads. In Garcia et al. (2016) men's objectification of
+women was significantly related to women's SSO, the current study sought
+to replicate this effect. As expected, the partner effect of
+other-objectification on SSO in the current all-women sample was
+statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12, \emph{p} =
+.019. That is, the extent to which one's partner reported thinking about
+a woman's external characteristics more than her internal
+characteristics was significantly related to the woman's own reported
+feeling more like a body than a full self. Along side the Garcia et al.
+(2016) study, there is now evidence that interpersonal objectification
+in an actual interpersonal encounter is realted to state
+self-objectification for women both when the objectifyer is a man and
+when the objectifyer is a woman.
+
+In addition to partner other-objectification, this model also included
+one's own objectification of their partner (actor
+other-objectification), actor trait self-objectification (TSO), and the
+interaction of partner other-objectification and TSO. One's own other
+objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE} =
+0.12, \emph{p} = .210. Further, inconsistent with past findings however,
+there was no statistically significant interaction of partner's other
+objectification and the person's trait self-objectification on SSO,
+\emph{b} = 0.03, \emph{SE} = 0.27, \emph{p} = .910. There was also no
+significant main effect of trait self-objectification on SSO \emph{b} =
+0.07, \emph{SE} = 0.05, \emph{p} = .183. The \(R^2\) of this model was
+0.03. As a test of the potential alternative models discussed above, we
+ran a MLM with other-objectification predicted by actor TSO but there
+was no statistically significant relationship between these two
+variables, \emph{b} = 0.09, \emph{SE} = 0.06, \emph{p} = .133.
+
+We next moved on to test the link between SSO and interaction
+authenticity. There was no significant effect of SSO on interaction
+authenticity, although the estimate of this effect was in the
+hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12,
+\emph{p} = .431. Because authenticity was a composite score of 9 items,
+two of which were interaction specific authenticity items, we also
+estimated the pairwise correlations between SSO and all these items
+individually. They were all small, ranging from only -0.01 to -0.14.
+Although we hypothesized that SSO would mediate the relationship between
+partner's other objectification and interaction authenticity, after
+finding no relationship between SSO and authenticity, we also tested if
+the partner's other objectification had a direct effect on authenticity,
+but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
 \emph{p} = .608 (nor was the total effect of partner's other
 objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11,
-\emph{p} = .787).
+\emph{p} = .787). Note that these analyses of the relationship between
+SSO and inauthenticity in this same-gender sample were considered
+exploratory, given that prior research on intragroup interactions points
+to mixed possibilities.
 
@@
 performance, career aspirations, and relationship agency, as it did in
-Garcia et al. (2016). We again used MLM and thus, these effects were
-tested in three separate models. There was no significant effect of
-interaction authenticity on cognitive performance, \emph{b} = 0.32,
-\emph{SE} = 0.28, \emph{p} = .258, but authenticity was significantly
-positively related to both career aspirations, \emph{b} = 0.18,
-\emph{SE} = 0.07, \emph{p} = .010, and relationship agency, \emph{b} =
-0.23, \emph{SE} = 0.12, \emph{p} = .049. There was no direct effect of
-SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25,
-\emph{p} = .872, and no direct effect of partner's other objectification
-on cognitive performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
-.962. There was no direct effect of SSO on career aspirations, \emph{b}
-= 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of
-partner's other objectification on career aspirations, \emph{b} = -0.06,
-\emph{SE} = 0.07, \emph{p} = .378. There was no direct effect of SSO on
-relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} =
-.659, and no direct effect of partner's other objectification on
-relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.
+Garcia et al. (2016) and as would be predicted by Terán et al. (2020).
+We again used MLM and thus, these effects were tested in three separate
+multilevel linear models. There was no significant effect of interaction
+authenticity on cognitive performance, \emph{b} = 0.32, \emph{SE} =
+0.28, \emph{p} = .258, but authenticity was significantly positively
+related to both career aspirations, \emph{b} = 0.18, \emph{SE} = 0.07,
+\emph{p} = .010 (\(R^2 =\) 0.04), and relationship agency, \emph{b} =
+0.23, \emph{SE} = 0.12, \emph{p} = .049 (\(R^2 =\) 0.01).\footnote{There
+  was no direct effect of SSO on cognitive performance, \emph{b} = 0.04,
+  \emph{SE} = 0.25, \emph{p} = .872, and no direct effect of partner's
+  other objectification on cognitive performance, \emph{b} = 0.01,
+  \emph{SE} = 0.27, \emph{p} = .962. There was no direct effect of SSO
+  on career aspirations, \emph{b} = 0.03, \emph{SE} = 0.06, \emph{p} =
+  .657, and no direct effect of partner's other objectification on
+  career aspirations, \emph{b} = -0.06, \emph{SE} = 0.07, \emph{p} =
+  .378. There was no direct effect of SSO on relationship agency,
+  \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} = .659, and no direct
+  effect of partner's other objectification on relationship agency,
+  \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.}
 
@@
 it is \emph{women's} state self-objectification that relates to being
-objectified by one's partner. Objectification Theory (Barbara L
-Fredrickson \& Roberts, 1997), as well as some past experimental studies
-(Saguy et al., 2010) suggest that at least one direction of the causal
-flow is from other-objectification to SSO. Other studies, especailly
-those investigating explicitly women objectifying other women (Puvia \&
-Vaes, 2013), have relately found evidence that women's \emph{trait}
+objectified by one's partner. Objectification Theory (Fredrickson \&
+Roberts, 1997), as well as some past experimental studies (Saguy et al.,
+2010) suggest that at least one direction of the causal flow is from
+other-objectification to SSO. Other studies, especailly those
+investigating explicitly women objectifying other women (Puvia \& Vaes,
+2013), have relately found evidence that women's \emph{trait}
 self-objectification causes women to objectify (dehumanize) other women
@@
 evidence suggesting that the male gaze is particularly detrimental
-(Calogero, 2004; Barbara L Fredrickson \& Roberts, 1997; Gervais,
-Holland, \& Dodd, 2013; Gervais et al., 2011), and perhaps the
-self-objectification experienced within an interaction with a women is
-qualtatively different, and perhaps not as harmful, as the
-self-objectification experienced within an interaction with a man.
-However, as a strong note of caution, it is best not to interpret a null
-result as evidence of no relationship and more research on interpersonal
-objectification among women is needed.
+(Calogero, 2004; Fredrickson \& Roberts, 1997; Gervais, Holland, \&
+Dodd, 2013; Gervais et al., 2011), and perhaps the self-objectification
+experienced within an interaction with a women is qualtatively
+different, and perhaps not as harmful, as the self-objectification
+experienced within an interaction with a man. However, as a strong note
+of caution, it is best not to interpret a null result as evidence of no
+relationship and more research on interpersonal objectification among
+women is needed.
 
@@
 social and cultural contexts, and hence are also constructed through
-sociocultural practices and discourses} (Barbara L Fredrickson \&
-Roberts, 1997, p. 174), it is important to consider how diverse social
-identities within unique cultural contexts may inform sexual
-objectification phenomenon to test the cross-cultural applicability of
-theoretical frameworks (Loughnan et al., 2015b).
+sociocultural practices and discourses} (Fredrickson \& Roberts, 1997,
+p. 174), it is important to consider how diverse social identities
+within unique cultural contexts may inform sexual objectification
+phenomenon to test the cross-cultural applicability of theoretical
+frameworks (Loughnan et al., 2015b).
 
@@
 research among younger and older individuals is needed, especially
-because self-objectification may change over time (Barbara L Fredrickson
-\& Roberts, 1997). It may be valuable to question the extent to which
+because self-objectification may change over time (Fredrickson \&
+Roberts, 1997). It may be valuable to question the extent to which
 children, adolescents, or emerging adults of different races or
@@
 
+Among heterosexual male and female college students,
+self-objectification has been found to be positively associated with the
+extent to which they objectify their romantic partners (Zurbriggen,
+Ramsey, \& Jaworski, 2011). Evidence is mixed, suggesting that women can
+sometimes have positive outcomes from appearance valuation within the
+context of an established romantic relationship. There is also evidence
+that they experience less SSO after appearance comments within romantic
+relationships {[}{]}, but less is known about first dates. An important
+caveat to this literature is that it is only about heterosexual
+relationships.
+
 However, since both men and women are socialized in a culture that
@@
 and Nicholson (1989), p.~28). Amid such heterogeneity though,
-\enquote{having a reproductively mature female body} proposed by Barbara
-L Fredrickson and Roberts (1997) is likely to create a shared
+\enquote{having a reproductively mature female body} proposed by
+Fredrickson and Roberts (1997) is likely to create a shared
 vulnerability to sexual objectification and a variety of shared negative
@@
 
+\hypertarget{ref-davies2005clearing}{}
+Davies, P. G., Spencer, S. J., \& Steele, C. M. (2005). Clearing the
+air: Identity safety moderates the effects of stereotype threat on
+women's leadership aspirations. \emph{Journal of Personality and Social
+Psychology}, \emph{88}(2), 276.
+
 \hypertarget{ref-deaux1987putting}{}
@@
 
-\hypertarget{ref-robertsfredrickson}{}
-Fredrickson, B. L., \& Roberts, T.-A. (1997). Objectification theory:
-Toward understanding women's lived experiences and mental health risks.
-\emph{Psychology of Women Quarterly}, \emph{21}(2), 173--206.
-
 \hypertarget{ref-fredricksonetal2011}{}
@@
 \emph{Journal of Personality and Social Psychology}, \emph{75}(1), 269.
+
+\hypertarget{ref-robertsfredrickson}{}
+Fredrickson, \& Roberts. (1997). Objectification theory: Toward
+understanding women's lived experiences and mental health risks.
+\emph{Psychology of Women Quarterly}, \emph{21}(2), 173--206.
 

### 2020-10-14 Final_Manuscript.Rmd
cleaned up a bunch

@@
 
-keywords          : "keywords"
+keywords          : "Interpersonal sexual objectification, self-objectifiation, authenticity, actual interactions, psychology of women, dyadic data analysis"
 
@@
 The SIMO is useful for studying mixed-gender interactions, but can it be extended to interactions among women?
-Although there is evidence that women objectify other women [@loughnan2015exploring; @puvia2013being], studies investigating the process of interpersonal objectification in interactions between women is scarce.
+Although there is evidence that women can objectify other women [@loughnan2015exploring; @puvia2013being; @gervais2013my], studies investigating the process of interpersonal objectification in interactions between women is scarce.
 
@@
 ##Self-Objectification
-Self-objectification is a psychological process that translates the experiences of interpersonal objectification [@loughnan2015exploring; @gervais2020social] into negative mental health outcomes [e.g., interaction inauthenticity, anxiety, lower self-esteem, and poor cognitive performance; @calogero2011; @moradi2008].
+Self-objectification is a psychological process that translates the experiences of interpersonal objectification [@loughnan2017internalizing; @gervais2020social] into negative mental health outcomes [e.g., interaction inauthenticity, anxiety, lower self-esteem, and poor cognitive performance; @calogero2011; @moradi2008].
 @calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO), whereby one abopts a habitual third-person perspective on one's own appearance.
 Furthermore, self-objectification can also be elicited momentarily, for example, when viewing sexualized images in movies and magazines [@morry2001magazine], when trying on sexualizing clothing [@fredrickson1998swimsuit], or during video chat when you believe your interaction partner can only see your body [not face; @saguyetal2010].
-This momentary self-objectification is referred to as *state* self-objectification [SSO; @bernard2018bodies; @calogero2011; @moradi2008] and is characterized by feeling like a body rather than a full self within a particular moment, instance, or context.
+This momentary self-objectification is referred to as *state* self-objectification [SSO; @calogero2011; @moradi2008] and is characterized by feeling like a body rather than a full self within a particular moment, instance, or context.
 
@@
 This process, however, was not comfirmed to occur during an actual interpersonal interaction.
-Thus, there is evidence that women do objectify other women, indeed, @loughnan2015exploring found that women objectify other women to a greater extent than they objectify men.
+Thus, there is evidence that women do objectify other women, indeed, @loughnan2017internalizing found that women objectify other women to a greater extent than they objectify men.
 Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the effects of this objectification might be.
@@
 ##Interpersonal Objectification
-Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and are likely to internalize the objectifying gaze on their physical self [@puvia2013being; @young1979].
+Studies have shown that within social encounters women are gazed at more than men [@henley1977body], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and are likely to internalize the objectifying gaze on their physical self [@puvia2013being].
 As mentiond above, interpersonal objectification has been found to have negative consequences for women.
 @gervais2011you found that an objectifying gaze by a male interaction partner (confederate) was associated with lower math performance for women than being objectified by a female interaction partner.
-Perhaps the most adverse negative consequence of interpersonal objectificaiton is that being objectified socializes girls and women to routinely treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit].
+Perhaps the most adverse negative consequence of interpersonal objectificaiton is that being objectified socializes girls and women to routinely treat themselves as objects to be looked at and evaluated [@Bartky; @fredrickson1998swimsuit].
 @gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
@@
 
-Past research has found that the experience of state self-objectification in mixed-gender contexts (stranger and romantic; @strelan2018birds; @meltzer2020women) has negative consequences for women, but what about in the context of interactions with other women?
+Past research has found that the experience of state self-objectification in mixed-gender contexts (stranger and romantic; @strelan2018birds; @meltzer2020women; @zurbriggen2011self) has negative consequences for women, but what about in the context of interactions with other women?
 Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
-The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010; @calogero2004test; @gervais2011you; @gay2010my; @yilmaz2019whose], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and it would be helpful to understand the consequencs of this *intra*group objectification for women.
+The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010; @calogero2004test; @gervais2011you; @gay2010my], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and recent experimental evidence suggests that the female gaze causes no less self-objectification than the male gaze [@yilmaz2019whose].
+It would be helpful to understand the consequencs of this *intra*group objectification for women.
 When women objectify other women, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
@@
 A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
-This link has also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], and we might view the experience of being objectified in an interaction as a potential identity threat, stigmatizing, situation [@miles2015stop; @nadal2012effects].
-Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], an intergroup context at least in heterosexual relationships.
+This link has also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], and we might view the experience of being objectified in an interaction as a potential identity threat, stigmatizing, situation [@nadal2012effects; @gervais2020social].
+Further, empirical evidence reveals that healthy relationship functioning manifests through authenticity in romantic relationships [@brunelletal2010], an intergroup context at least in heterosexual relationships.
 Evidence for otehr adverse consquences of interpersonal objectification include reductions in career aspirations [@garcia2016objectification] and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
 These are also negative conseqences found for women under steroetype threat [@davies2005clearing].
-When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger threat.
+When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature and power differential of this encounter might trigger threat.
 Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman.
@@
 We also tested whether SSO would, in turn, lead to feelings of inauthenticity.
-The investigation of the SSO to inauthenticity connection is considered exploratory given the lack of support for this connection from the literature on identity threat in *intr*agroup interactions [@rollero2016bringing] but support for this connection in the objectification literature [@garcia2016objectification; @teran2020relational].
+The investigation of the SSO to inauthenticity connection is considered exploratory given the lack of support for this connection from the literature on identity threat in *intr*agroup interactions but support for this connection in the objectification literature [@garcia2016objectification; @teran2020relational; @rollero2016bringing].
 Regardless of whether there was an association between SSO and inauthenticity, we hypothesized that feelings of inauthencity would be associated with reduced feelings of agency in romantic relationships, reduced career aspirations, and reduced cognitive performance.
@@
 summary(apim0)
+apim0.b <- gls(a2pSOO_A ~ howbody_avg_A + TSO_A, 
+                  na.action=na.omit, 
+                  correlation=corCompSymm (form=~1|dyadID),
+                  data=clarksmith_women)
+summary(apim0.b)
 
@@
 The $R^2$ of this model was `r round(apim1_r2,2)`.
-As a test of the potential alternative models discussed above, we ran a MLM with other-objectification predicted by actor TSO but there was no statistically significant relationship between these two variables, `r report_stats(apim0, 2)`.
+
+As a test of the potential alternative models discussed above---if trait-self-objectification is related to objectifying one's partner to a greater degree---we ran a MLM with other-objectification predicted by actor TSO.
+There was no statistically significant relationship between these two variables, `r report_stats(apim0, 2)`.
+We also ran a model with both TSO and SSO predicting other-objectification, given past theorizing that state self-objectification might mediate the relationship between TSO and objectification of fellow women, but there was no effect of SSO on other-objectification in this model, `r report_stats(apim0.b, 2)`.
 
@@
 # Discussion
-The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women.
-Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women is related to state self-objectification in their woman-identified interaction partners.
+The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a sample of women engaging in actual dyadic interactions with each other.
+Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women during actual interactions is related to state self-objectification in their woman-identified interaction partners.
 As hypothesized, the current study did find a significant relationship between a woman's interaction partner's report of having objectified her and her own post-interaction feelings of self-objectification.
@@
 This effect extends the equivalent relationship found in mixed-gender interactions to the context of same-gender interactions between women.
-Thus, evidence suggests that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman is also related to women's SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
+Thus, evidence suggests that it is not only the real or imagined male gaze that is related to women's state self-objectification, but there is now also evidence that being objectified by another woman could be related to women's SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.
 
-As is the case in all correlational studies, we cannot be sure about the causal direction.
-The model used by the current study asserts that being objectified by a woman causes women to self-objectify, but it could be that women's SSO causes them to be objectified by their interaction partner.
-This latter interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* state self-objectification that relates to being objectified by one's partner.
-Objectification Theory [@robertsfredrickson], as well as some past experimental studies [@saguyetal2010] suggest that at least one direction of the causal flow is from other-objectification to SSO.
-Other studies, especailly those investigating explicitly women objectifying other women [@puvia2013being], have relately found evidence that women's *trait* self-objectification causes women to objectify (dehumanize) other women and this link is mediated by *state* self-objectification.
-It could follow that we tend to objectify other women who objectify us and through a process of TSO causes SSO which in turn causes objectifation of one's partner, which in turn causes one's partner to objectify us.
-The current study does not provide any evidence of this alternative model, however---TSO was not significantly correlated with SSO and actor's objectification was not correlated with partner's objectification.
+As is the case in all correlational studies, we cannot be sure about the causal direction between other-objectification and SSO.
+The linear model used by the current study implies that being objectified by a woman leads women to self-objectify, but it could be that women's SSO causes them to be objectified by their interaction partner.
+This latter interpretation is possible given the empiricle evidence that it is *women's* state self-objectification that relates to being objectified by one's partner---men partners [@garcia2016objectification] and now women partners.
+Objectification Theory [@robertsfredrickson], as well as some past experimental studies [for example, @saguyetal2010], suggest that the causal flow is from other-objectification to SSO.
+Other studies, especailly those investigating explicitly women objectifying other women [@puvia2013being], have relately found evidence that women's *trait* self-objectification is related to women objectifying (dehumanizing) other women and this link is mediated by *state* self-objectification.
+The process of interpersonal objectification among women could also contain a feedback loop.
+That is, perhaps we tend to objectify other women who objectify us and through a process of TSO causing SSO which in turn causes objectifation of one's partner, which in turn causes one's partner to objectify us.
+However, the current study does not provide any evidence of the TSO to other-objectifixation link---TSO was not significantly correlated with SSO and, further, actor's other-objectification was not correlated with partner's other-objectification.
 
-Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity.
-In addition, we found no evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations.
-Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes.
-This is somewhat suprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification; @gervais2011you].
+Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity.^[In addition, we found no evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations.
+Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes.] This is somewhat suprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification; @gervais2011you].
 This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is qualtatively different, and perhaps not as harmful, as the self-objectification experienced within an interaction with a man.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you], and perhaps the self-objectification experienced within an interaction with a women is qualitatively different, and perhaps not as harmful, as the state self-objectification experienced within an interaction with a man.
 However, as a strong note of caution, it is best not to interpret a null result as evidence of no relationship and more research on interpersonal objectification among women is needed.
@@
 It should be noted that the estimate of this relationship was small (close to zero), but in the negative direction.
-If it is the case that there is a smaller (i.e., weaker) connection between women's feelings of SSO and inauthenticity in interactions with other women than in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including inauthenticity as a potential mediating factor.
-Further, gender of the objectifyer/interaction partner could be added as a moderator of the self-objectificaiton to authenticity process to help understand the circumstances that require other-objectification and SSO to have negative consequences for women.
+If it is the case that there is a smaller (i.e., weaker) or zero connection between women's feelings of SSO and inauthenticity in interactions with other women than in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including gender of the objectifyer/interaction partner as a moderator.
+Inauthenticity could be added as a potential moderated mediating factor to help understand the circumstances that require other-objectification and SSO to have negative consequences for women.
+Perhaps one important difference is the lack of a power differential across gendered lines -- the patriarchy is present, but the interafction partners are not a stigmatizer-stigmatized pair.
 
@@
 Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables.
-This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; @teran2020relational].
-Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification; @tolman2006looking], we again find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current partner.
+This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; @teran2020relational] and is related to mental health correlates [@tolman2006looking].
+Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification], we find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current partner.
 Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and future work must explore when and how SSO leads to inauthenticity in interpersonal objectification situations.
@@
 ###Sample Characteristics
-In addition to being relatively small and combined across two institutions, another limitation of the current study is that the sample was comprised of Western women only.
-Being that self-objectification is most prevalent in Western culture [@loughnan2015] research on objectification conducted outside of Western or Westernized countries has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015, @wollast2020cultural].
-Since “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015].
+In addition to being relatively small and combined across two institutions, another limitation of the current study sample is that the it was comprised of Western women only.
+Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring] research on objectification conducted outside of Western or Westernized countries has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
+Since “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015exploring].
 
-Further, sexualizing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014; @bury2016].
-Considering the fact that the average mean age of the investigated participants of this current study was 18.85 years, research among younger and older individuals is needed, especially because self-objectification may change over time [@robertsfredrickson].
+Further, sexualizing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014].
+Considering the fact that the average mean age of the investigated participants of this current study was `r mean_age` years, research among younger and older individuals is needed, especially because the processes of self-objectification may change over time [@robertsfredrickson].
 It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.
-Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectificaion are needed [see CITE and CITE for exmaples].
+Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectificaion are needed.
 
-###Sexual Objectification and the Objectifyer's Gender
+###Interpersonal Sexual Objectification, Gender, and Sexual Attraction
 The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating/romantic partner.
-We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
+We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---perhaps they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
+Since both men and women are socialized in a culture that sexually objectifies women, both men and women may come to internalize this socialization and sexually objectify women.
+Indeed, recent research has found that the more women self-objectify, the more they objectify other women [@loughnan2015exploring; @puvia2013being], although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women [@strelan2005women].
 This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships, adding variability.
 
-Previous research has found that when compared to heterosexual women, lesbian women report less concern with physical appearance [@siever1994sexual; @strong2000eating], and less self-objectification [@brownlow1998relationship; @noffsinger2004objectification].
+Previous research has found that when compared to heterosexual women, lesbian women report less concern with physical appearance [@siever1994sexual; @strong2000eating], lower body surveillance [@hill2008examining], and lower self-objectification [@noffsinger2004objectification].
 However none of these studies examined the relationship between self-objectification and experiences of sexual objectification.
-Thus, it is unclear whether lesbians indeed experience similar levels of cultural sexual objectification but internalize them less than heterosexual women do.
-Consistent with previous research, @hill2008examining determined that lesbians existed less physical appearance concerns compared to heterosexual women, however there was no evidence found that lesbian women self-objectify less than heterosexual women and they did not find that sexual orientation moderates the relationship between sexual objectification and self-objectification.
-This contradicts older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women [@brown1987lesbians; @pitman1999body; @lum1994lesbians; @siever1994sexual].
+Thus, it is unclear whether lesbian women indeed experience similar levels of cultural sexual objectification but internalize them less than heterosexual women do.
+Consistent with previous research, @hill2008examining determined that lesbians exhibited less physical appearance concerns compared to heterosexual women, however there was no evidence found that lesbian women self-objectify less than heterosexual women and they did not find that sexual orientation moderates the relationship between sexual objectification and self-objectification.
+This evidence sits in contrast to older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women [@brown1987lesbians; @pitman1999body; @rothblum1994lesbians; @siever1994sexual].
 
+Interpersonal sexual objectification has been studied in both romantic and platonic contexts.
 Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
 Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship.
-There is also evidence that they experience less SSO after appearance comments within romantic relationships [], but less is known about first dates.
+There is also evidence that they experience less SSO after appearance comments within established romantic relationships [@meltzer2020women], but less is known about first dates.
 An important caveat to this literature is that it is only about heterosexual relationships.
-
-However, since both men and women are socialized in a culture that sexually objectifies women, both men and women may come to internalize this socialization and sexually objectify women.
-Indeed, recent research has found that the more women self-objectify, the more they objectify other women [@loughnan2015exploring; @puvia2013being], although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women [@strelan2005women].
-
-Objectification among platonic friends: Perhaps women could be amplifying each others' state self-objectification *before* the theoretical encounters with men organized in the SIMO occur.
-In this way, women's rituals of getting ready together might place even women with low TSO in a higher SSO group.
+Objectification might also occur among platonic friends: Perhaps women could be amplifying each others' state self-objectification *before* the theoretical encounters with men organized in the SIMO occur.
+In this way, women's rituals of getting ready together before socilizing in co-ed groups might place even women with low TSO in a higher SSO group.
 
 ###Sexism and Sexual Discrimination
-Sexism has recently been found to be related to the objectification of women, but not men, for both men and women [@harsey2020men].[Kat: Is the relationship between sexism and objectification really this recent of a finding?
-Or was it just replicated recently?] Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and experience daily sexist hassles [@swimetal].
+Sexism has been found to be related to the objectification of women, but not men [@cikara2011agents; @harsey2020men], and in addition, TSO has been found to be associated with less negative attitudes towards sexual harassment [@bernard2018bodies].
+Both of these effects are present for both men and women.
+Empirical evidence illustrates how women continue to be objects of interpersonal discrimination and experience daily sexist hassles [@swimetal].
 One form of interpersonal discrimination women face is the process by which their whole being is viewed as a collection of sexualized body parts valued predominantly for commodification, a phenomena termed sexual objectification [@Bartky].
-Sexual objectification occurs with both “endless variety and monotonous similarity,” and is thus mediated by unique combinations of race, ethnicity, sexuality, age, and class [@fredricksonetal2011; @rubin1975, cited in @frasernicholson1989, p.
-28].
+Sexual objectification of women has also been linked to trauma [@miles2015stop].
+Sexual objectification occurs in a mirad of ways in women's lives and is modified by unique combinations of race, ethnicity, sexuality, age, and class [@robertsfredrickson].
 Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
@@
 #Conclusion
-The results from the current analysis highlight how subtle forms of sexist discrimination operate, and provide valuable insight into prevention and intervention efforts in both clinical and educational contexts.
+The results of this study demonstrate the complex and ambivalent nature of sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
 These results are quite useful for promoting mental health, the creation and maintence of early action programs for girls and young women, and for scholars and practitioners to work intentially to provide the tools necessary to circumvent or mitigate negative effects on self-objectification to combat such experiences.
-
-The results of this study demonstrate the complex and ambivalent nature of sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
-We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity.
 

### 2020-10-14 Final_Manuscript.tex
cleaned up a bunch

@@
             pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
-            pdfkeywords={keywords},
+            pdfkeywords={Interpersonal sexual objectification, self-objectifiation, authenticity,
+actual interactions, psychology of women, dyadic data analysis},
             pdfborder={0 0 0},
@@
 \textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
-\keywords{keywords}
+\keywords{Interpersonal sexual objectification, self-objectifiation, authenticity, actual interactions, psychology of women, dyadic data analysis}
 \usepackage{csquotes}
@@
 can it be extended to interactions among women? Although there is
-evidence that women objectify other women (Loughnan et al., 2015a; Puvia
-\& Vaes, 2013), studies investigating the process of interpersonal
-objectification in interactions between women is scarce.
+evidence that women can objectify other women (Gervais, Holland, \&
+Dodd, 2013; Loughnan et al., 2015; Puvia \& Vaes, 2013), studies
+investigating the process of interpersonal objectification in
+interactions between women is scarce.
 
@@
 experiences of interpersonal objectification (Gervais et al., 2020;
-Loughnan et al., 2015a) into negative mental health outcomes (e.g.,
-interaction inauthenticity, anxiety, lower self-esteem, and poor
-cognitive performance; Calogero, Tantleff-Dunn, \& Thompson, 2011;
-Moradi \& Huang, 2008). Calogero et al. (2011) proposes that
-self-objectification can be conceptualized as a learned trait, or
+Loughnan, Baldissarri, Spaccatini, \& Elder, 2017) into negative mental
+health outcomes (e.g., interaction inauthenticity, anxiety, lower
+self-esteem, and poor cognitive performance; Calogero, Tantleff-Dunn, \&
+Thompson, 2011; Moradi \& Huang, 2008). Calogero et al. (2011) proposes
+that self-objectification can be conceptualized as a learned trait, or
 \emph{trait} self-objectification (TSO), whereby one abopts a habitual
@@
 viewing sexualized images in movies and magazines (Morry \& Staska,
-2001), when trying on sexualizing clothing (Barbara L Fredrickson,
-Roberts, Noll, Quinn, \& Twenge, 1998), or during video chat when you
-believe your interaction partner can only see your body (not face;
-Saguy, Quinn, F Dovidio, \& Pratto, 2010). This momentary
-self-objectification is referred to as \emph{state} self-objectification
-(SSO; Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \&
-Huang, 2008) and is characterized by feeling like a body rather than a
-full self within a particular moment, instance, or context.
+2001), when trying on sexualizing clothing (B. L. Fredrickson, Roberts,
+Noll, Quinn, \& Twenge, 1998), or during video chat when you believe
+your interaction partner can only see your body (not face; Saguy, Quinn,
+F Dovidio, \& Pratto, 2010). This momentary self-objectification is
+referred to as \emph{state} self-objectification (SSO; Calogero et al.,
+2011; Moradi \& Huang, 2008) and is characterized by feeling like a body
+rather than a full self within a particular moment, instance, or
+context.
 
 There is evidence that being objectified by another person during an
-interaction elicits SSO. For example, Loughnan, Baldissarri, Spaccatini,
-and Elder (2017) found that for women, imagining a time when they were
-objectified by another person caused reductions in human traits
-attributed to the self, and notably, the gender of the person doing the
-objectification was not a moderating factor. In addition, in a
-mixed-gender dyadic study of actual interactions, Garcia et al. (2016)
-found that men's reported objectification of their female interaction
-partner was associated with increased self-objectification (as reported
-by their female partner). Further, this negative effect of the men's
-objectification on women's SSO was strongest for women higher in TSO.
-The current study uses this same dyadic paradigm to study same-gender,
-woman-woman interacting pairs.
+interaction elicits SSO. For example, Loughnan et al. (2017) found that
+for women, imagining a time when they were objectified by another person
+caused reductions in human traits attributed to the self, and notably,
+the gender of the person doing the objectification was not a moderating
+factor. In addition, in a mixed-gender dyadic study of actual
+interactions, Garcia et al. (2016) found that men's reported
+objectification of their female interaction partner was associated with
+increased self-objectification (as reported by their female partner).
+Further, this negative effect of the men's objectification on women's
+SSO was strongest for women higher in TSO. The current study uses this
+same dyadic paradigm to study same-gender, woman-woman interacting
+pairs.
 
@@
 Thus, there is evidence that women do objectify other women, indeed,
-Loughnan et al. (2015a) found that women objectify other women to a
+Loughnan et al. (2017) found that women objectify other women to a
 greater extent than they objectify men. Women have also been found to
@@
 Studies have shown that within social encounters women are gazed at more
-than men (Briton \& Hall, 1995), often times feel \enquote{looked at}
-within interpersonal interactions (Argyle \& Williams, 1969;
-Miles-McLean et al., 2015), and are likely to internalize the
-objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
-1979). As mentiond above, interpersonal objectification has been found
-to have negative consequences for women. Gervais et al. (2011) found
-that an objectifying gaze by a male interaction partner (confederate)
-was associated with lower math performance for women than being
-objectified by a female interaction partner. Perhaps the most adverse
-negative consequence of interpersonal objectificaiton is that being
-objectified socializes girls and women to routinely treat themselves as
-objects to be looked at and evaluated (Bartky, 1990; Berger, Cohen, \&
-Zelditch Jr, 1972; Barbara L Fredrickson et al., 1998). Gervais et al.
-(2020) recently reviewed the research on interpersonal objectification
-and organized our current theoretical understanding of this process in
-the Social Interaction Model of Objectification (SIMO). What is clear
-from Gervais et al. (2020)'s review is that we know little about
-women-on-women interpersonal objectification. Could there also be
-negative consequences for women after being objectified by a woman?
+than men (Henley, 1977), often times feel \enquote{looked at} within
+interpersonal interactions (Argyle \& Williams, 1969), and are likely to
+internalize the objectifying gaze on their physical self (Puvia \& Vaes,
+2013; Young, 1979). As mentiond above, interpersonal objectification has
+been found to have negative consequences for women. Gervais et al.
+(2011) found that an objectifying gaze by a male interaction partner
+(confederate) was associated with lower math performance for women than
+being objectified by a female interaction partner. Perhaps the most
+adverse negative consequence of interpersonal objectificaiton is that
+being objectified socializes girls and women to routinely treat
+themselves as objects to be looked at and evaluated (Bartky, 1990; B. L.
+Fredrickson et al., 1998). Gervais et al. (2020) recently reviewed the
+research on interpersonal objectification and organized our current
+theoretical understanding of this process in the Social Interaction
+Model of Objectification (SIMO). What is clear from Gervais et al.
+(2020)'s review is that we know little about women-on-women
+interpersonal objectification. Could there also be negative consequences
+for women after being objectified by a woman?
 
@@
 there is evidence that women do objectify other women (Harsey \&
-Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and it
+Zurbriggen, 2020; Loughnan et al., 2015; Puvia \& Vaes, 2013) and it
 would be helpful to understand the consequencs of this \emph{intra}group
@@
 objectified in an interaction as a potential identity threat,
-stigmatizing, situation (Miles-McLean et al., 2015; Nadal \& Haynes,
-2012). Further, empirical evidence reveals that objectification
-manifests through inauthenticity in romantic relationships (Brunell et
-al., 2010), an intergroup context at least in heterosexual
+stigmatizing, situation (Gervais et al., 2020; Nadal \& Haynes, 2012).
+Further, empirical evidence reveals that healthy relationship
+functioning manifests through authenticity in romantic relationships
+(Brunell et al., 2010), an intergroup context at least in heterosexual
 relationships. Evidence for otehr adverse consquences of interpersonal
@@
 is objectified by a man, and subsequently experiences
-self-objectification, the intergroup nature of this encounter might
-trigger threat. Thus, perhaps there are fewer negative consequences when
-a woman is objectified by another woman. That is, the intergroup threat
-literature might predict that woman-woman interpersonal objectification
-processes diverge from mixed-gender interpersonal objectification
-processes precisely because they are not intergroup interactions (at
-least with respect to gender identity).
+self-objectification, the intergroup nature and power differential of
+this encounter might trigger threat. Thus, perhaps there are fewer
+negative consequences when a woman is objectified by another woman. That
+is, the intergroup threat literature might predict that woman-woman
+interpersonal objectification processes diverge from mixed-gender
+interpersonal objectification processes precisely because they are not
+intergroup interactions (at least with respect to gender identity).
 
@@
 \toprule
- & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1.} & \multicolumn{1}{c}{2.} & \multicolumn{1}{c}{3.} & \multicolumn{1}{c}{4.} & \multicolumn{1}{c}{5.} & \multicolumn{1}{c}{6.} & \multicolumn{1}{c}{NA}\\
+ & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1.} & \multicolumn{1}{c}{2.} & \multicolumn{1}{c}{3.} & \multicolumn{1}{c}{4.} & \multicolumn{1}{c}{5.} & \multicolumn{1}{c}{6.} & \multicolumn{1}{c}{7.}\\
 \midrule
@@
 Trait self-objectification (TSO) was assessed using the
-Self-Objectification Questionnaire (Barbara L Fredrickson et al., 1998;
-M. Noll \& L. Fredrickson, 1998), which evaluates the extent to which
+Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; S.
+Noll \& Fredrickson, 1998), which evaluates the extent to which
 individuals view their bodies in observable versus non-observable ways.
@@
 0.07, \emph{SE} = 0.05, \emph{p} = .183. The \(R^2\) of this model was
-0.03. As a test of the potential alternative models discussed above, we
-ran a MLM with other-objectification predicted by actor TSO but there
-was no statistically significant relationship between these two
-variables, \emph{b} = 0.09, \emph{SE} = 0.06, \emph{p} = .133.
+0.03.
+
+As a test of the potential alternative models discussed above---if
+trait-self-objectification is related to objectifying one's partner to a
+greater degree---we ran a MLM with other-objectification predicted by
+actor TSO. There was no statistically significant relationship between
+these two variables, \emph{b} = 0.09, \emph{SE} = 0.06, \emph{p} = .133.
+We also ran a model with both TSO and SSO predicting
+other-objectification, given past theorizing that state
+self-objectification might mediate the relationship between TSO and
+objectification of fellow women, but there was no effect of SSO on
+other-objectification in this model, \emph{b} = -0.17, \emph{SE} = 0.13,
+\emph{p} = .199.
 
@@
 objectification and state self-objectification (SSO) used in Garcia et
-al. (2016) replicates in a same-gender dyadic sample of women. Although
-past research has found that women do objectify other women (Harsey \&
-Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013), this is
-the first study to test if \emph{interpersonal} other-objectification by
-women is related to state self-objectification in their woman-identified
-interaction partners. As hypothesized, the current study did find a
-significant relationship between a woman's interaction partner's report
-of having objectified her and her own post-interaction feelings of
-self-objectification. That is, there was a significant partner effect of
-other-objectification on SSO. This effect extends the equivalent
-relationship found in mixed-gender interactions to the context of
-same-gender interactions between women. Thus, evidence suggests that it
-is not only the male gaze, and male other-objectification that is
-related to women's state self-objectification, but being objectified by
-another woman is also related to women's SSO, at least in the context of
-a scenario where they know they are being evaluated as a potential
-dating partner.
+al. (2016) replicates in a sample of women engaging in actual dyadic
+interactions with each other. Although past research has found that
+women do objectify other women (Harsey \& Zurbriggen, 2020; Loughnan et
+al., 2015; Puvia \& Vaes, 2013), this is the first study to test if
+\emph{interpersonal} other-objectification by women during actual
+interactions is related to state self-objectification in their
+woman-identified interaction partners. As hypothesized, the current
+study did find a significant relationship between a woman's interaction
+partner's report of having objectified her and her own post-interaction
+feelings of self-objectification. That is, there was a significant
+partner effect of other-objectification on SSO. This effect extends the
+equivalent relationship found in mixed-gender interactions to the
+context of same-gender interactions between women. Thus, evidence
+suggests that it is not only the real or imagined male gaze that is
+related to women's state self-objectification, but there is now also
+evidence that being objectified by another woman could be related to
+women's SSO, at least in the context of a scenario where they know they
+are being evaluated as a potential dating partner.
 
 As is the case in all correlational studies, we cannot be sure about the
-causal direction. The model used by the current study asserts that being
-objectified by a woman causes women to self-objectify, but it could be
-that women's SSO causes them to be objectified by their interaction
-partner. This latter interpretation is theoretically interesting given
-that, in both the Garcia et al. (2016) study and in the current study,
-it is \emph{women's} state self-objectification that relates to being
-objectified by one's partner. Objectification Theory (Fredrickson \&
-Roberts, 1997), as well as some past experimental studies (Saguy et al.,
-2010) suggest that at least one direction of the causal flow is from
-other-objectification to SSO. Other studies, especailly those
-investigating explicitly women objectifying other women (Puvia \& Vaes,
-2013), have relately found evidence that women's \emph{trait}
-self-objectification causes women to objectify (dehumanize) other women
-and this link is mediated by \emph{state} self-objectification. It could
-follow that we tend to objectify other women who objectify us and
-through a process of TSO causes SSO which in turn causes objectifation
-of one's partner, which in turn causes one's partner to objectify us.
-The current study does not provide any evidence of this alternative
-model, however---TSO was not significantly correlated with SSO and
-actor's objectification was not correlated with partner's
-objectification.
+causal direction between other-objectification and SSO. The linear model
+used by the current study implies that being objectified by a woman
+leads women to self-objectify, but it could be that women's SSO causes
+them to be objectified by their interaction partner. This latter
+interpretation is possible given the empiricle evidence that it is
+\emph{women's} state self-objectification that relates to being
+objectified by one's partner---men partners (Garcia et al., 2016) and
+now women partners. Objectification Theory (Fredrickson \& Roberts,
+1997), as well as some past experimental studies (for example, Saguy et
+al., 2010), suggest that the causal flow is from other-objectification
+to SSO. Other studies, especailly those investigating explicitly women
+objectifying other women (Puvia \& Vaes, 2013), have relately found
+evidence that women's \emph{trait} self-objectification is related to
+women objectifying (dehumanizing) other women and this link is mediated
+by \emph{state} self-objectification. The process of interpersonal
+objectification among women could also contain a feedback loop. That is,
+perhaps we tend to objectify other women who objectify us and through a
+process of TSO causing SSO which in turn causes objectifation of one's
+partner, which in turn causes one's partner to objectify us. However,
+the current study does not provide any evidence of the TSO to
+other-objectifixation link---TSO was not significantly correlated with
+SSO and, further, actor's other-objectification was not correlated with
+partner's other-objectification.
 
@@
 mixed-gender dyads is the lack of evidence for relationships between SSO
-and interaction inauthenticity. In addition, we found no evidence of
-\emph{direct} or \emph{indirect} relationships between SSO and cognitive
-functioning, relationship agency, and career aspirations. Nor was there
-evidence of \emph{direct} or \emph{indirect} relationships between
-other-objectification and any of these outcomes. This is somewhat
-suprising given the extant evidence linking SSO and cognitive
-functioning (Barbara L Fredrickson et al., 1998; and see Moradi \&
-Huang, 2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the
-research on interpersonal other-ojectification and cognitive functioning
-(Garcia et al., 2016; Gervais et al., 2011; Logel et al., 2009). This
-lack of evidence could potentially signal diverging processes between
-women's experiences with interpersonal objectification from men and
-interpersonal objectification from women. There is quite a bit of
-evidence suggesting that the male gaze is particularly detrimental
-(Calogero, 2004; Fredrickson \& Roberts, 1997; Gervais, Holland, \&
-Dodd, 2013; Gervais et al., 2011), and perhaps the self-objectification
-experienced within an interaction with a women is qualtatively
-different, and perhaps not as harmful, as the self-objectification
-experienced within an interaction with a man. However, as a strong note
-of caution, it is best not to interpret a null result as evidence of no
-relationship and more research on interpersonal objectification among
-women is needed.
+and interaction inauthenticity.\footnote{In addition, we found no
+  evidence of \emph{direct} or \emph{indirect} relationships between SSO
+  and cognitive functioning, relationship agency, and career
+  aspirations. Nor was there evidence of \emph{direct} or
+  \emph{indirect} relationships between other-objectification and any of
+  these outcomes.} This is somewhat suprising given the extant evidence
+linking SSO and cognitive functioning (B. L. Fredrickson et al., 1998;
+and see Moradi \& Huang, 2008 for a review; Quinn, Chaudoir, \& Kallen,
+2011) and the research on interpersonal other-ojectification and
+cognitive functioning (Garcia et al., 2016; Gervais et al., 2011; Logel
+et al., 2009). This lack of evidence could potentially signal diverging
+processes between women's experiences with interpersonal objectification
+from men and interpersonal objectification from women. There is quite a
+bit of evidence suggesting that the male gaze is particularly
+detrimental (Calogero, 2004; Fredrickson \& Roberts, 1997; Gervais et
+al., 2011), and perhaps the self-objectification experienced within an
+interaction with a women is qualitatively different, and perhaps not as
+harmful, as the state self-objectification experienced within an
+interaction with a man. However, as a strong note of caution, it is best
+not to interpret a null result as evidence of no relationship and more
+research on interpersonal objectification among women is needed.
 
@@
 this relationship was small (close to zero), but in the negative
-direction. If it is the case that there is a smaller (i.e., weaker)
-connection between women's feelings of SSO and inauthenticity in
+direction. If it is the case that there is a smaller (i.e., weaker) or
+zero connection between women's feelings of SSO and inauthenticity in
 interactions with other women than in interactions with men, models of
 interpersonal objectification, like the SIMO (Gervais et al., 2020),
-could be extended by including inauthenticity as a potential mediating
-factor. Further, gender of the objectifyer/interaction partner could be
-added as a moderator of the self-objectificaiton to authenticity process
-to help understand the circumstances that require other-objectification
-and SSO to have negative consequences for women.
+could be extended by including gender of the objectifyer/interaction
+partner as a moderator. Inauthenticity could be added as a potential
+moderated mediating factor to help understand the circumstances that
+require other-objectification and SSO to have negative consequences for
+women. Perhaps one important difference is the lack of a power
+differential across gendered lines -- the patriarchy is present, but the
+interafction partners are not a stigmatizer-stigmatized pair.
 
@@
 in intergroup interactions (Brunell et al., 2010; Garcia et al., 2016;
-Tolman et al., 2006), we again find more evidence here that disruptions
-in feelings of authenticity can negatively impact relationships beyond
-the current partner. Although the current study did not find a
-connection between authenticity and SSO, this seems theoretically to be
-a natural connection, and future work must explore when and how SSO
-leads to inauthenticity in interpersonal objectification situations.
+Tolman et al., 2006), we find more evidence here that disruptions in
+feelings of authenticity can negatively impact relationships beyond the
+current partner. Although the current study did not find a connection
+between authenticity and SSO, this seems theoretically to be a natural
+connection, and future work must explore when and how SSO leads to
+inauthenticity in interpersonal objectification situations.
 
@@
 In addition to being relatively small and combined across two
-institutions, another limitation of the current study is that the sample
-was comprised of Western women only. Being that self-objectification is
-most prevalent in Western culture (Loughnan et al., 2015b) research on
-objectification conducted outside of Western or Westernized countries
-has been scarce (Moradi \& Huang, 2008), although more recent work has
-examined objectification from a cross-cultural framework (Loughnan et
-al., 2015b, Wollast et al. (2020)). Since \enquote{bodies exist within
-social and cultural contexts, and hence are also constructed through
-sociocultural practices and discourses} (Fredrickson \& Roberts, 1997,
-p. 174), it is important to consider how diverse social identities
-within unique cultural contexts may inform sexual objectification
-phenomenon to test the cross-cultural applicability of theoretical
-frameworks (Loughnan et al., 2015b).
+institutions, another limitation of the current study sample is that the
+it was comprised of Western women only. Being that self-objectification
+has been found to be most prevalent in Western culture (Loughnan et al.,
+2015) research on objectification conducted outside of Western or
+Westernized countries has been scarce (Moradi \& Huang, 2008), although
+more recent work has examined objectification from a cross-cultural
+framework (Loughnan et al., 2015, Wollast et al. (2020)). Since
+\enquote{bodies exist within social and cultural contexts, and hence are
+also constructed through sociocultural practices and discourses}
+(Fredrickson \& Roberts, 1997, p. 174), it is important to consider how
+diverse social identities within unique cultural contexts may inform
+sexual objectification phenomenon to test the cross-cultural
+applicability of theoretical frameworks (Loughnan et al., 2015).
 
@@
 begin a very young age, and thus, researchers have only recently begun
-to examine such experiences among children (Bury, Tiggemann, \& Slater,
-2016; e.g., Holland \& Haslam, 2016; Jongenelis, Byrne, \& Pettigrew,
-2014). Considering the fact that the average mean age of the
-investigated participants of this current study was 18.85 years,
-research among younger and older individuals is needed, especially
-because self-objectification may change over time (Fredrickson \&
-Roberts, 1997). It may be valuable to question the extent to which
-children, adolescents, or emerging adults of different races or
-ethnicities are exposed to varied amounts of sexualizing content.
-Further, more longitudinal studies investigating the developmental
-experience of interpersonal objectification and self-objectificaion are
-needed {[}see CITE and CITE for exmaples{]}.
-
-\subsubsection{Sexual Objectification and the Objectifyer's
-Gender}\label{sexual-objectification-and-the-objectifyers-gender}
+to examine such experiences among children (e.g., Holland \& Haslam,
+2016; Jongenelis, Byrne, \& Pettigrew, 2014). Considering the fact that
+the average mean age of the investigated participants of this current
+study was 18.85 years, research among younger and older individuals is
+needed, especially because the processes of self-objectification may
+change over time (Fredrickson \& Roberts, 1997). It may be valuable to
+question the extent to which children, adolescents, or emerging adults
+of different races or ethnicities are exposed to varied amounts of
+sexualizing content. Further, more longitudinal studies investigating
+the developmental experience of interpersonal objectification and
+self-objectificaion are needed.
+
+\subsubsection{Interpersonal Sexual Objectification, Gender, and Sexual
+Attraction}\label{interpersonal-sexual-objectification-gender-and-sexual-attraction}
 
@@
 their target---and there is evidence that they might do this readily
-(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---they may be even
-more apt to activate social comparison processes (Festinger, 1954) than
-women who are sexually attracted to other women (non-heterosexual
-women). This differential psychological process between women with
-differing sexualities might have served to dampen our ability to detect
-relationships, adding variability.
-
-Previous research has found that when compared to heterosexual women,
-lesbian women report less concern with physical appearance (Siever,
-1994; Strong, Williamson, Netemeyer, \& Geer, 2000), and less
-self-objectification (Brownlow, 1998; Noffsinger-Frazier, 2004). However
-none of these studies examined the relationship between
-self-objectification and experiences of sexual objectification. Thus, it
-is unclear whether lesbians indeed experience similar levels of cultural
-sexual objectification but internalize them less than heterosexual women
-do. Consistent with previous research, Hill and Fischer (2008)
-determined that lesbians existed less physical appearance concerns
-compared to heterosexual women, however there was no evidence found that
-lesbian women self-objectify less than heterosexual women and they did
-not find that sexual orientation moderates the relationship between
-sexual objectification and self-objectification. This contradicts older
-theoretical literature that suggests that lesbians internalize cultural
-sexual objectification less than do heterosexual women (Brown, 1987;
-LUM, 1994; Pitman, 1999; Siever, 1994).
-
-Among heterosexual male and female college students,
-self-objectification has been found to be positively associated with the
-extent to which they objectify their romantic partners (Zurbriggen,
-Ramsey, \& Jaworski, 2011). Evidence is mixed, suggesting that women can
-sometimes have positive outcomes from appearance valuation within the
-context of an established romantic relationship. There is also evidence
-that they experience less SSO after appearance comments within romantic
-relationships {[}{]}, but less is known about first dates. An important
-caveat to this literature is that it is only about heterosexual
-relationships.
-
-However, since both men and women are socialized in a culture that
+(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---perhaps they may be
+even more apt to activate social comparison processes (Festinger, 1954)
+than women who are sexually attracted to other women (non-heterosexual
+women). Since both men and women are socialized in a culture that
 sexually objectifies women, both men and women may come to internalize
@@
 has found that the more women self-objectify, the more they objectify
-other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013), although not
+other women (Loughnan et al., 2015; Puvia \& Vaes, 2013), although not
 to the degree exhibited by men; that is, men were found to objectify
 women significantly more than women objectify other women (Strelan \&
-Hargreaves, 2005).
-
-Objectification among platonic friends: Perhaps women could be
-amplifying each others' state self-objectification \emph{before} the
-theoretical encounters with men organized in the SIMO occur. In this
-way, women's rituals of getting ready together might place even women
-with low TSO in a higher SSO group.
+Hargreaves, 2005). This differential psychological process between women
+with differing sexualities might have served to dampen our ability to
+detect relationships, adding variability.
+
+Previous research has found that when compared to heterosexual women,
+lesbian women report less concern with physical appearance (Siever,
+1994; Strong, Williamson, Netemeyer, \& Geer, 2000), lower body
+surveillance (Hill \& Fischer, 2008), and lower self-objectification
+(Noffsinger-Frazier, 2004). However none of these studies examined the
+relationship between self-objectification and experiences of sexual
+objectification. Thus, it is unclear whether lesbian women indeed
+experience similar levels of cultural sexual objectification but
+internalize them less than heterosexual women do. Consistent with
+previous research, Hill and Fischer (2008) determined that lesbians
+exhibited less physical appearance concerns compared to heterosexual
+women, however there was no evidence found that lesbian women
+self-objectify less than heterosexual women and they did not find that
+sexual orientation moderates the relationship between sexual
+objectification and self-objectification. This evidence sits in contrast
+to older theoretical literature that suggests that lesbians internalize
+cultural sexual objectification less than do heterosexual women (Brown,
+1987; Pitman, 1999; Rothblum, 1994; Siever, 1994).
+
+Interpersonal sexual objectification has been studied in both romantic
+and platonic contexts. Among heterosexual male and female college
+students, self-objectification has been found to be positively
+associated with the extent to which they objectify their romantic
+partners (Zurbriggen, Ramsey, \& Jaworski, 2011). Evidence is mixed,
+suggesting that women can sometimes have positive outcomes from
+appearance valuation within the context of an established romantic
+relationship. There is also evidence that they experience less SSO after
+appearance comments within established romantic relationships (Meltzer,
+2020), but less is known about first dates. An important caveat to this
+literature is that it is only about heterosexual relationships.
+Objectification might also occur among platonic friends: Perhaps women
+could be amplifying each others' state self-objectification
+\emph{before} the theoretical encounters with men organized in the SIMO
+occur. In this way, women's rituals of getting ready together before
+socilizing in co-ed groups might place even women with low TSO in a
+higher SSO group.
 
@@
 
-Sexism has recently been found to be related to the objectification of
-women, but not men, for both men and women (Harsey \& Zurbriggen,
-2020).{[}Kat: Is the relationship between sexism and objectification
-really this recent of a finding? Or was it just replicated recently?{]}
-Empirical evidence illustrates how women continue to be objects of
-interpersonal discrimination and experience daily sexist hassles (Swim,
-Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
-discrimination women face is the process by which their whole being is
-viewed as a collection of sexualized body parts valued predominantly for
-commodification, a phenomena termed sexual objectification (Bartky,
-1990). Sexual objectification occurs with both \enquote{endless variety
-and monotonous similarity,} and is thus mediated by unique combinations
-of race, ethnicity, sexuality, age, and class (Barbara L. Fredrickson,
-Hendler, Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser
-and Nicholson (1989), p.~28). Amid such heterogeneity though,
-\enquote{having a reproductively mature female body} proposed by
-Fredrickson and Roberts (1997) is likely to create a shared
-vulnerability to sexual objectification and a variety of shared negative
-experiences as a result.
+Sexism has been found to be related to the objectification of women, but
+not men (Cikara, Eberhardt, \& Fiske, 2011; Harsey \& Zurbriggen, 2020),
+and in addition, TSO has been found to be associated with less negative
+attitudes towards sexual harassment (Bernard, Legrand, \& Klein, 2018).
+Both of these effects are present for both men and women. Empirical
+evidence illustrates how women continue to be objects of interpersonal
+discrimination and experience daily sexist hassles (Swim, Hyers, Cohen,
+\& Ferguson, 2001). One form of interpersonal discrimination women face
+is the process by which their whole being is viewed as a collection of
+sexualized body parts valued predominantly for commodification, a
+phenomena termed sexual objectification (Bartky, 1990). Sexual
+objectification of women has also been linked to trauma (Miles-McLean et
+al., 2015). Sexual objectification occurs in a mirad of ways in women's
+lives and is modified by unique combinations of race, ethnicity,
+sexuality, age, and class (Fredrickson \& Roberts, 1997). Amid such
+heterogeneity though, \enquote{having a reproductively mature female
+body} proposed by Fredrickson and Roberts (1997) is likely to create a
+shared vulnerability to sexual objectification and a variety of shared
+negative experiences as a result.
 
 \section{Conclusion}\label{conclusion}
-
-The results from the current analysis highlight how subtle forms of
-sexist discrimination operate, and provide valuable insight into
-prevention and intervention efforts in both clinical and educational
-contexts. These results are quite useful for promoting mental health,
-the creation and maintence of early action programs for girls and young
-women, and for scholars and practitioners to work intentially to provide
-the tools necessary to circumvent or mitigate negative effects on
-self-objectification to combat such experiences.
 
@@
 and social consequences of such objectification processes on women's
-social relationships and well-being. We did not find a significant
-effect between actor SSO and felt authenticity in the interaction, which
-suggests that there is not sufficient evidence to support the claim that
-partner objectification is the cause for the diverse range of negative
-effects related to interaction inauthenticity.
+social relationships and well-being. These results are quite useful for
+promoting mental health, the creation and maintence of early action
+programs for girls and young women, and for scholars and practitioners
+to work intentially to provide the tools necessary to circumvent or
+mitigate negative effects on self-objectification to combat such
+experiences.
 
@@
 \hypertarget{ref-Bartky}{}
-Bartky, S. L. (1990). Femininity and domination studies in the
-phenomenology of oppression.
-
-\hypertarget{ref-berger1972}{}
-Berger, J., Cohen, B. P., \& Zelditch Jr, M. (1972). Status
-characteristics and social interaction. \emph{American Sociological
-Review}, 241--255.
+Bartky, S. (1990). \emph{Femininity and domination: Studies in the
+phenomenology of oppression}. Routledge, New York.
 
@@
 
-\hypertarget{ref-briton1995}{}
-Briton, N. J., \& Hall, J. A. (1995). Beliefs about female and male
-nonverbal communication. \emph{Sex Roles}, \emph{32}(1-2), 79--90.
-
 \hypertarget{ref-brown1987lesbians}{}
@@
 294--309.
-
-\hypertarget{ref-brownlow1998relationship}{}
-Brownlow, B. S. (1998). \emph{The relationship between objectification,
-body image disturbances, and disordered eating: Investigating race,
-socioeconomic status, acculturation and self-objectification as
-mediators.} (PhD thesis). ProQuest Information \& Learning.
 
@@
 
-\hypertarget{ref-bury2016}{}
-Bury, B., Tiggemann, M., \& Slater, A. (2016). Disclaimer labels on
-fashion magazine advertisements: Impact on visual attention and
-relationship with body dissatisfaction. \emph{Body Image}, \emph{16},
-1--9.
-
 \hypertarget{ref-calogero2004test}{}
@@
 counteractions.} American Psychological Association.
+
+\hypertarget{ref-cikara2011agents}{}
+Cikara, M., Eberhardt, J. L., \& Fiske, S. T. (2011). From agents to
+objects: Sexist attitudes and neural responses to sexualized targets.
+\emph{Journal of Cognitive Neuroscience}, \emph{23}(3), 540--551.
 
@@
 
-\hypertarget{ref-frasernicholson1989}{}
-Fraser, N., \& Nicholson, L. (1989). Social criticism without
-philosophy: An encounter between feminism and postmodernism.
-\emph{Social Text}, (21), 83.
-doi:\href{https://doi.org/10.2307/827810}{10.2307/827810}
-
-\hypertarget{ref-fredricksonetal2011}{}
-Fredrickson, B. L., Hendler, L. M., Nilsen, S., O'Barr, J. F., \&
-Roberts, T.-A. (2011). Bringing back the body. \emph{Psychology of Women
-Quarterly}, \emph{35}(4), 689--696.
-doi:\href{https://doi.org/10.1177/0361684311426690}{10.1177/0361684311426690}
-
 \hypertarget{ref-fredrickson1998swimsuit}{}
@@
 
+\hypertarget{ref-henley1977body}{}
+Henley, N. (1977). \emph{Body politics: Power, sex, and nonverbal
+communication}. Prentice Hall.
+
 \hypertarget{ref-hill2008examining}{}
@@
 Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
-Harada, C., \ldots{} Tsuchiya, K. (2015a). Exploring the role of culture
+Harada, C., \ldots{} Tsuchiya, K. (2015). Exploring the role of culture
 in sexual objectification: A seven nations study. \emph{Revue
 Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
-
-\hypertarget{ref-loughnan2015}{}
-Loughnan, S., Fernandez-Campos, S., Vaes, J., Anjum, G., Aziz, M.,
-Harada, C., \ldots{} Tsuchiya, K. (2015b). Exploring the role of culture
-in sexual objectification: A seven nations study. \emph{Revue
-Internationale de Psychologie Sociale}, \emph{28}(1), 125--152.
-
-\hypertarget{ref-lum1994lesbians}{}
-LUM, E. (1994). Lesbians and physical appearance which model applies?
-\emph{Lesbian and Gay Psychology: Theory, Research, and Clinical
-Applications}, \emph{1}, 84.
-
-\hypertarget{ref-nollfredrickson1998}{}
-M. Noll, S., \& L. Fredrickson, B. (1998). A mediational model linking
-self-objectification, body shame, and disordered eating.
-\emph{Psychology of Women Quarterly}, \emph{22}, 623--636.
-doi:\href{https://doi.org/10.1111/j.1471-6402.1998.tb00181.x}{10.1111/j.1471-6402.1998.tb00181.x}
 
@@
 \hypertarget{ref-nadal2012effects}{}
-Nadal, K. L., \& Haynes, K. (2012). The effects of sexism, gender
-microaggressions, and other forms of discrimination on women's mental
-health and development.
+Nadal, K. L., \& Haynes, K. (2012). Women's psychology. women and mental
+disorders. In N. Lundberg-Love P. K. \& M. A. Paludi (Eds.), (pp.
+87--101). Praeger/ABC-CLIO.
 
@@
 internalization of sociocultural standards of appearance, and sexual
-orientation}. The University of Memphis.
+orientation} (PhD thesis). The University of Memphis.
+
+\hypertarget{ref-nollfredrickson1998}{}
+Noll, S., \& Fredrickson, B. (1998). A mediational model linking
+self-objectification, body shame, and disordered eating.
+\emph{Psychology of Women Quarterly}, \emph{22}, 623--636.
+doi:\href{https://doi.org/10.1111/j.1471-6402.1998.tb00181.x}{10.1111/j.1471-6402.1998.tb00181.x}
 
@@
 
-\hypertarget{ref-rubin1975}{}
-Rubin, J. (1975). What the ``good language learner'' can teach us.
-\emph{TESOL Quarterly}, \emph{9}(1), 41.
-doi:\href{https://doi.org/10.2307/3586011}{10.2307/3586011}
+\hypertarget{ref-rothblum1994lesbians}{}
+Rothblum, E. (1994). Lesbians and physical appearance which model
+applies? \emph{Lesbian and Gay Psychology: Theory, Research, and
+Clinical Applications}, \emph{1}, 84.
 

### 2020-10-16 Final_Manuscript.Rmd
final read through

@@
 abstract: |
-  Extant research on interpersonal objectification has focused mostly on links between objectification, self-objectification, and negative outcomes for women within mixed-gender interactions [@gervais2020social; @garcia2016objectification].
-The purpose of the present study was to extend past research on interpersonal objectification to interactions between pairs of women.
+  Existing research on interpersonal objectification has focused mostly on links between objectification, self-objectification, and negative outcomes for women within mixed-gender interactions [@gervais2020social; @garcia2016objectification].
+The purpose of the present study was to extend past research on interpersonal objectification to interactions between women.
 Women were brought into the laboratory and interacted face-to-face in same-sex dyads.
@@
 Results revealed a significant positive relationship between being objectified by a woman interaction partner and women’s own self-objectification (a partner effect).
-There was no significant relationship between self-objectification and interaction inauthenticity.
-Further, there were significant negative effects of inauthenticity on career aspirations and relationship agency (actor effects).
+There was no significant relationship between self-objectification and interaction inauthenticity, but there were significant negative effects of inauthenticity on career aspirations and relationship agency (actor effects).
 The significant partner effect of objectification on self-objectification suggests that women being objectified by other women may result in feelings of self-objectification, and this finding opens up questions for future research about how interpersonal objectification might function in situations without an immediate male gaze.
@@
 In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO).
-The SIMO is useful for studying mixed-gender interactions, but can it be extended to interactions among women?
+The SIMO focuses on understanding mixed-gender interactions, ackowledging the patriarchal power structure embedded in these mixed interactions, but can it be extended to interactions among women?
 Although there is evidence that women can objectify other women [@loughnan2015exploring; @puvia2013being; @gervais2013my], studies investigating the process of interpersonal objectification in interactions between women is scarce.
@@
 
-There is evidence that being objectified by another person during an interaction elicits SSO.
+Perhaps the most adverse negative consequence of interpersonal objectificaiton is that being objectified socializes girls and women to routinely treat themselves as objects to be looked at and evaluated [@Bartky].
+There is experimental and observational evidence that being objectified by another person during an interaction elicits SSO.
 For example, @loughnan2017internalizing found that for women, imagining a time when they were objectified by another person caused reductions in human traits attributed to the self, and notably, the gender of the person doing the objectification was not a moderating factor.
-In addition, in a mixed-gender dyadic study of actual interactions, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification (as reported by their female partner).
+In addition, in a mixed-gender dyadic study of actual interactions, @garcia2016objectification found that men’s reported objectification of their female interaction partner was associated with increased self-objectification in the female partner.
 Further, this negative effect of the men's objectification on women's SSO was strongest for women higher in TSO.
@@
 ##Women Objectifying Women
-Past research investigating women objectifying other women has focused on the psychological conditions that led women to objectify women.
+Past research investigating women objectifying other women has focused on the psychological conditions that lead women to objectify other women.
 @harsey2020men found that (trait) self-objectification was related to the objectification of women to a similar degree for male and female participants.
@@
 Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the effects of this objectification might be.
-Past studies have foud that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, we do not know much about the effect of the gender of the *objectifyer* on potential detrimental outcomes.
+Past studies have foud that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, we do not know much about the effect of the gender of the *objectifyer* on these potential detrimental outcomes.
 
@@
 @gervais2011you found that an objectifying gaze by a male interaction partner (confederate) was associated with lower math performance for women than being objectified by a female interaction partner.
-Perhaps the most adverse negative consequence of interpersonal objectificaiton is that being objectified socializes girls and women to routinely treat themselves as objects to be looked at and evaluated [@Bartky; @fredrickson1998swimsuit].
-@gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO).
+@gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the SIMO.
 What is clear from @gervais2020social's review is that we know little about women-on-women interpersonal objectification.
@@
 A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
-This link has also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], and we might view the experience of being objectified in an interaction as a potential identity threat, stigmatizing, situation [@nadal2012effects; @gervais2020social].
+Authenticity reduction and interaction quality disrutptions hve also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting; @pearson2008fragility], and we might view the experience of being objectified in an interaction as a potential identity threat situation [@nadal2012effects; @gervais2020social].
 Further, empirical evidence reveals that healthy relationship functioning manifests through authenticity in romantic relationships [@brunelletal2010], an intergroup context at least in heterosexual relationships.
-Evidence for otehr adverse consquences of interpersonal objectification include reductions in career aspirations [@garcia2016objectification] and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
+Evidence for other adverse consquences of interpersonal objectification include reductions in career aspirations [@garcia2016objectification] and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
 These are also negative conseqences found for women under steroetype threat [@davies2005clearing].

### 2020-10-19 Final_Manuscript.Rmd
final edits for first submission

@@
     institution   : "Program in Statistical and Data Sciences, Smith College"
+
+authornote: |
+  Randi L. Garcia is in the Psychology Department and the Statitsical and Data Sciences program at Smith College.
+
+  The data that support the findings of this study are available on request from the corresponding author. The data are not publicly available due to privacy or ethical restrictions.
 
@@
 @robertsfredrickson's Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
-The negative effects of this interpersonal objectification for women have been theorized to be the strongest under the "male gaze," that is, when it is a percieved or actual man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction?
+The negative effects of this interpersonal objectification for women have been theorized to be the strongest under the "male gaze," that is, when it is a perceived or actual man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction?
 Psychological researchers studying the sexual objectification of women have in recent years explored the interpersonal process of the objectification, finding evidence for *self*-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification; @strelan2018birds; @riemer2020self].
 In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO).
-The SIMO focuses on understanding mixed-gender interactions, ackowledging the patriarchal power structure embedded in these mixed interactions, but can it be extended to interactions among women?
+The SIMO focuses on understanding mixed-gender interactions, acknowledging the patriarchal power structure embedded in these mixed interactions, but can it be extended to interactions among women?
 Although there is evidence that women can objectify other women [@loughnan2015exploring; @puvia2013being; @gervais2013my], studies investigating the process of interpersonal objectification in interactions between women is scarce.
@@
 The current study addresses these questions by investigating interpersonal objectification among interacting pairs where both partners identify as women.
-We first review the literature on self-objectification, then we review the evidence for women objectifying other women before turning to the literature on interpersonal objectification.
 
@@
 Self-objectification is a psychological process that translates the experiences of interpersonal objectification [@loughnan2017internalizing; @gervais2020social] into negative mental health outcomes [e.g., interaction inauthenticity, anxiety, lower self-esteem, and poor cognitive performance; @calogero2011; @moradi2008].
-@calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO), whereby one abopts a habitual third-person perspective on one's own appearance.
+@calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO), whereby one adopts a habitual third-person perspective on one's own appearance.
 Furthermore, self-objectification can also be elicited momentarily, for example, when viewing sexualized images in movies and magazines [@morry2001magazine], when trying on sexualizing clothing [@fredrickson1998swimsuit], or during video chat when you believe your interaction partner can only see your body [not face; @saguyetal2010].
@@
 
-Perhaps the most adverse negative consequence of interpersonal objectificaiton is that being objectified socializes girls and women to routinely treat themselves as objects to be looked at and evaluated [@Bartky].
+Perhaps the most adverse negative consequence of interpersonal objectification is that being objectified socializes girls and women to routinely treat themselves as objects to be looked at and evaluated [@Bartky].
 There is experimental and observational evidence that being objectified by another person during an interaction elicits SSO.
@@
 They found that women may be socialized not only to see themselves as objects, but perhaps to see other women as objects as well.
-This process, however, was not comfirmed to occur during an actual interpersonal interaction.
+This process, however, was not confirmed to occur during an actual interpersonal interaction.
 Thus, there is evidence that women do objectify other women, indeed, @loughnan2017internalizing found that women objectify other women to a greater extent than they objectify men.
 Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the effects of this objectification might be.
-Past studies have foud that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, we do not know much about the effect of the gender of the *objectifyer* on these potential detrimental outcomes.
+Past studies have found that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, we do not know much about the effect of the gender of the *objectifyer* on these potential detrimental outcomes.
 
@@
 Studies have shown that within social encounters women are gazed at more than men [@henley1977body], often times feel ‘looked at’ within interpersonal interactions [@argyle1969], and are likely to internalize the objectifying gaze on their physical self [@puvia2013being].
-As mentiond above, interpersonal objectification has been found to have negative consequences for women.
+As mentioned above, interpersonal objectification has been found to have negative consequences for women.
 @gervais2011you found that an objectifying gaze by a male interaction partner (confederate) was associated with lower math performance for women than being objectified by a female interaction partner.
@@
 What is clear from @gervais2020social's review is that we know little about women-on-women interpersonal objectification.
-Could there also be negative consequences for women after being objectified by a woman?
 
@@
 The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010; @calogero2004test; @gervais2011you; @gay2010my], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and recent experimental evidence suggests that the female gaze causes no less self-objectification than the male gaze [@yilmaz2019whose].
-It would be helpful to understand the consequencs of this *intra*group objectification for women.
+It would be helpful to understand the consequences of this *intra*group objectification for women.
 When women objectify other women, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
@@
 A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
-Authenticity reduction and interaction quality disrutptions hve also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting; @pearson2008fragility], and we might view the experience of being objectified in an interaction as a potential identity threat situation [@nadal2012effects; @gervais2020social].
+Authenticity reduction and interaction quality disruptions have also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting; @pearson2008fragility], and we might view the experience of being objectified in an interaction as a potential identity threat situation [@nadal2012effects; @gervais2020social].
 Further, empirical evidence reveals that healthy relationship functioning manifests through authenticity in romantic relationships [@brunelletal2010], an intergroup context at least in heterosexual relationships.
-Evidence for other adverse consquences of interpersonal objectification include reductions in career aspirations [@garcia2016objectification] and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
-These are also negative conseqences found for women under steroetype threat [@davies2005clearing].
+Evidence for other adverse consequences of interpersonal objectification include reductions in career aspirations [@garcia2016objectification] and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
+These are also negative consequences found for women under stereotype threat [@davies2005clearing].
 When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature and power differential of this encounter might trigger threat.
@@
 In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification, but between same-gender interpersonal interactions among women.
-Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously.
-Although the literature on intragroup woman objectification is small, the results are mixed and do not cover interpersonal encourters, we expected to replicate some of the results found in @garcia2016objectification.
+Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the relationships for both women simultaneously.
+Although the literature on intragroup objectification among women is small, the results are mixed, and they do not cover interpersonal encounters, we expected to replicate some of the results found in @garcia2016objectification.
 Most importantly, we predicted that being objectified by one’s interaction partner would be related to state self-objectification (SSO).
-We also expected that TSO would moderate this relationship, amplifying the positive assocaition between being objectified and SSO for women higher in TSO.
+We also expected that TSO would moderate this relationship, amplifying the positive association between being objectified and SSO for women higher in TSO.
 Here we would like to note that @puvia2013being would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (more precisely, to dehumanize a sexualized woman).
@@
 We also tested whether SSO would, in turn, lead to feelings of inauthenticity.
-The investigation of the SSO to inauthenticity connection is considered exploratory given the lack of support for this connection from the literature on identity threat in *intr*agroup interactions but support for this connection in the objectification literature [@garcia2016objectification; @teran2020relational; @rollero2016bringing].
+The investigation of the SSO to inauthenticity connection is considered exploratory given the lack of support for this connection from the literature on identity threat in *intra*group interactions but support for this connection in the objectification literature [@garcia2016objectification; @teran2020relational; @rollero2016bringing].
 Regardless of whether there was an association between SSO and inauthenticity, we hypothesized that feelings of inauthencity would be associated with reduced feelings of agency in romantic relationships, reduced career aspirations, and reduced cognitive performance.
 In summary, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification.
-We also expected to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
+We also expected to find a negative relationship between state-self objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.
 
@@
 *All* participants were told that they were assigned to the "College Relationships" condition.
-Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because, in Westurn culture and beyond, women need to look attractive to obtain and maintain successful relationships, thus, the "College Relationships" condition may heighten self-objectification and the evaluation of other women in a sexualized way.
+Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because, in Western culture and beyond, women need to look attractive to obtain and maintain successful relationships, thus, the "College Relationships" condition may heighten self-objectification and the evaluation of other women in a sexualized way.
 The decision was made to ask even heterosexual women to judge their fellow-woman partners for their potential as romantic partners.
 We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and strengthen the potential for objectification that would normally be low in the context of a psychology laboratory.
-Recall that, past research has found that heterosexual women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; @puvia2013being]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.
+Recall that, past research has found that heterosexual women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; @puvia2013being]---women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.
 Analyses comparing levels of other-objectification between heterosexual and non-heterosexual women are provided in the measures section below.
 
-After recieving the "College Relationships" prompt, the two participants were then brought into a larger interaction room where they sat on stools prearranged to be approximately 1 meter apart.
+After receiving the "College Relationships" prompt, the two participants were then brought into a larger interaction room where they sat on stools prearranged to be approximately 1 meter apart.
 The experimenter instructed the participants to “get to know each other” for 10 minutes and then left the room.
@@
 In the measures section that follows we refer to them as Sample 1 and Sample 2.
-Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college.
-More specifically, twelve of the pairs were students at a co-ed liberal arts college, while the remaining twenty pairs attended a women’s liberal arts college.^[Initially, data was collected from both same-gender and mixed-gender dyads at both institutions.
+Sample 1 (*N =* `r ns[3]`, or 12 pairs) is from a co-ed liberal arts college and Sample 2 (*N =* `r ns[4]`, or 20 pairs) is from a women’s liberal arts college.
+Initially, data was collected from both same-gender and mixed-gender dyads at both institutions.
 Sample 1 originally consisted of 22 pairs, 12 men and 32 women.
 In Sample 2 there were 23 pairs made up of 43 women and one man, as well as two participants who did not identify as either a woman or man.
-To investigate only same-gender pairs of women, we limited participant data to women in both samples.] All results presented below are from models including sample as a control variable.
+To investigate only same-gender pairs of women, we limited participant data to women in both samples.
+Due to difficulties in the logistics of dyadic interaction studies, data collection was discontinued after one year at the second institution and the sample size was taken as the number of women-women dyads at this point in time.
+All results presented below are from models including sample as a control variable.
 
@@
 `r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.
-See the analysis of differences between heteroseuxal and non-heterosexual women in levels of other-objectification of their female partners in the measures section below.
+See the analysis of differences between heterosexual and non-heterosexual women in levels of other-objectification of their female partners in the measures section below.
 
@@
 The mean score was `r mean_trigram` (SD = `r sd_trigram`).
-Cognitive performance was measured first directly after the intercation in order to measure potential immediate detriments to performance [@garcia2016objectification].
+Cognitive performance was measured first directly after the interaction in order to measure potential immediate detriments to performance [@garcia2016objectification].
 
@@
 The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
-The item was intended to be reverse coded, but correlations were still low enough to make the scale unreliable.
-Therefore, the ninth item was removed.
+Therefore, this item was removed.
 As a result, the 8-item scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
@@
 
-The R-package *papaja* [Version 0.1.0.9842; @R-papaja] was used to create a fully reproducible research document containing the analysis code and manuscript text integrated into one source file.
-The benefit of this integration is that the numbers reported throughout this document are softcoded into the text, ensuring that no errors were made during a workflow marked by copying and pasting from statistical software to word processing software.
+The R-package *papaja* [Version 0.1.0.9842; @R-papaja] was used to create a fully reproducible APA style manuscript containing the analysis code and manuscript text integrated into one source file.
+The benefit of this integration is that the numbers reported throughout this document are coded into the text, ensuring that no errors were made during a workflow marked by copying and pasting from statistical software to word processing software.
 Note that here we are using the term reproducibility to mean getting the same results when running analyses again using the *same* data, not to be confused with replicability meaning collecting a new dataset using the same methods and obtaining the same results [@patil2016statistical].
-The source code for this manuscript along with survey materials and experimenter scripts for the study protocol are all avaliable at https://github.com/kkyuchukova/object-in-action.
-The data unfortunutely cannot be made publically avaliable given the dyadic nature of the observations.
-For example, with dyadic data, if a person who participated in the study found their own scores, using the dyad identification number, they could then see their partner's scores and thus confidentiality would be broken.
+The source code for this manuscript along with survey materials and experimenter scripts for the study protocol are all available at https://github.com/kkyuchukova/object-in-action.
+The data unfortunately cannot be made publicly available given the dyadic nature of the observations.
+That is, with dyadic data, if a person who participated in the study found their own scores, using the dyad identification number, they could then see their partner's scores and thus confidentiality would be breached.
 
@@
 
-While past studies investigating objectification in interactions used dyadic path analysis [@garcia2016objectification], the current study used multilevel modeling proceedures.
+While past studies investigating objectification in interactions used dyadic path analysis [@garcia2016objectification], the current study used multilevel modeling procedures.
 Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural using Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs), as we had in the current study [@ledermann2017analyzing; @garcia2015moderation].
@@
 First, use used to the APIM to test for evidence of a partner effect of other objectification and SSO in this sample of same-gender woman-woman interacting dyads.
-In @garcia2016objectification men's objectification of women was significantly related to women's SSO, the current study sought to replicate this effect.
+In @garcia2016objectification, men's objectification of women was significantly related to women's SSO, the current study sought to replicate this partner effect.
 As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically significant, `r report_stats(apim1, 3)`.
 That is, the extent to which one's partner reported thinking about a woman's external characteristics more than her internal characteristics was significantly related to the woman's own reported feeling more like a body than a full self.
-Along side the @garcia2016objectification study, there is now evidence that interpersonal objectification in an actual interpersonal encounter is realted to state self-objectification for women both when the objectifyer is a man and when the objectifyer is a woman.
+Along side the @garcia2016objectification study, there is now evidence that interpersonal objectification in an actual interpersonal encounter is related to state self-objectification for women both when the objectifyer is a man and when the objectifyer is a woman.
 
 In addition to partner other-objectification, this model also included one's own objectification of their partner (actor other-objectification), actor trait self-objectification (TSO), and the interaction of partner other-objectification and TSO.
-One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`.
-Further, inconsistent with past findings however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
+One's own other objectification had no significant effect on SSO (actor effect of other-objectification), `r report_stats(apim1, 2)`.
+Further, inconsistent with past findings, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`.
 There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.
-The $R^2$ of this model was `r round(apim1_r2,2)`.
+The $R^2$ of this model (which includes the partner effect of other-objectification discussed in the previous paragraph) was only `r round(apim1_r2,2)`.
 
-As a test of the potential alternative models discussed above---if trait-self-objectification is related to objectifying one's partner to a greater degree---we ran a MLM with other-objectification predicted by actor TSO.
+As a test of the potential alternative models discussed in the introduction---if trait-self-objectification is positively related to objectifying one's partner---we ran a MLM with other-objectification predicted by actor TSO.
 There was no statistically significant relationship between these two variables, `r report_stats(apim0, 2)`.
-We also ran a model with both TSO and SSO predicting other-objectification, given past theorizing that state self-objectification might mediate the relationship between TSO and objectification of fellow women, but there was no effect of SSO on other-objectification in this model, `r report_stats(apim0.b, 2)`.
+We also ran a model with both TSO and SSO predicting other-objectification, given past theorizing that state self-objectification might mediate the relationship between TSO and objectification of fellow women, but there was also no effect of SSO on other-objectification in this model, `r report_stats(apim0.b, 2)`.
 
@@
 
-Lastly, although there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performance, career aspirations, and relationship agency, as it did in @garcia2016objectification and as would be predicted by @teran2020relational.
+Lastly, although there was no evidence that SSO was related to interaction authenticity in the current sample, we tested if interaction authenticity (composite of nine items) had effects on cognitive performance, career aspirations, and relationship agency, as it did in @garcia2016objectification.
 We again used MLM and thus, these effects were tested in three separate multilevel linear models.
-There was no significant effect of interaction authenticity on cognitive performance, `r report_stats(apim3, 2)`, but authenticity was significantly positively related to both career aspirations, `r report_stats(apim5, 2)` ($R^2 =$ `r round(apim5_r2,2)`), and relationship agency, `r report_stats(apim4, 2)` ($R^2 =$ `r round(apim4_r2,2)`).^[There was no direct effect of SSO on cognitive performance, `r report_stats(apim3.b, 3)`, and no direct effect of partner's other objectification on cognitive performance, `r report_stats(apim3.c, 4)`.
+There was no significant effect of interaction authenticity on cognitive performance, `r report_stats(apim3, 2)`, but authenticity was significantly positively related to both career aspirations, `r report_stats(apim5, 2)` ($R^2 =$ `r round(apim5_r2,2)`), and relationship agency, `r report_stats(apim4, 2)` ($R^2 =$ `r round(apim4_r2,2)`).
+
+<!-- ^[There was no direct effect of SSO on cognitive performance, `r report_stats(apim3.b, 3)`, and no direct effect of partner's other objectification on cognitive performance, `r report_stats(apim3.c, 4)`.
 There was no direct effect of SSO on career aspirations, `r report_stats(apim5.b, 3)`, and no direct effect of partner's other objectification on career aspirations, `r report_stats(apim5.c, 4)`.
-There was no direct effect of SSO on relationship agency, `r report_stats(apim4.b, 3)`, and no direct effect of partner's other objectification on relationship agency, `r report_stats(apim4.c, 4)`.]
+There was no direct effect of SSO on relationship agency, `r report_stats(apim4.b, 3)`, and no direct effect of partner's other objectification on relationship agency, `r report_stats(apim4.c, 4)`.] -->
 
@@
 The linear model used by the current study implies that being objectified by a woman leads women to self-objectify, but it could be that women's SSO causes them to be objectified by their interaction partner.
-This latter interpretation is possible given the empiricle evidence that it is *women's* state self-objectification that relates to being objectified by one's partner---men partners [@garcia2016objectification] and now women partners.
+This latter interpretation is possible given the empirical evidence that it is *women's* state self-objectification that relates to being objectified by one's partner---men partners [@garcia2016objectification] and now women partners.
 Objectification Theory [@robertsfredrickson], as well as some past experimental studies [for example, @saguyetal2010], suggest that the causal flow is from other-objectification to SSO.
-Other studies, especailly those investigating explicitly women objectifying other women [@puvia2013being], have relately found evidence that women's *trait* self-objectification is related to women objectifying (dehumanizing) other women and this link is mediated by *state* self-objectification.
+Other studies, especially those investigating explicitly women objectifying other women [@puvia2013being], have relatedly found evidence that women's *trait* self-objectification is related to women objectifying (dehumanizing) other women and this link is mediated by *state* self-objectification.
 The process of interpersonal objectification among women could also contain a feedback loop.
-That is, perhaps we tend to objectify other women who objectify us and through a process of TSO causing SSO which in turn causes objectifation of one's partner, which in turn causes one's partner to objectify us.
-However, the current study does not provide any evidence of the TSO to other-objectifixation link---TSO was not significantly correlated with SSO and, further, actor's other-objectification was not correlated with partner's other-objectification.
+That is, perhaps we tend to objectify other women who objectify us and through a process of TSO causing SSO which in turn causes objectification of one's partner, which in turn causes one's partner to objectify us.
+However, the current study does not provide any evidence of the TSO to other-objectification link---TSO was not significantly correlated with SSO and, further, actor's other-objectification was not correlated with partner's other-objectification.
 
-Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity.^[In addition, we found no evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations.
-Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes.] This is somewhat suprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification; @gervais2011you].
+Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity.
+This is somewhat surprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the research on interpersonal other-objectification and cognitive functioning [@logel2009interacting; @garcia2016objectification; @gervais2011you].
 This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
@@
 Inauthenticity could be added as a potential moderated mediating factor to help understand the circumstances that require other-objectification and SSO to have negative consequences for women.
-Perhaps one important difference is the lack of a power differential across gendered lines -- the patriarchy is present, but the interafction partners are not a stigmatizer-stigmatized pair.
+Perhaps one important difference is the lack of a power differential across gendered lines -- the patriarchal culture is present, but the interaction partners are not a stigmatizer-stigmatized pair.
 
 Although the current study did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency, and authenticity and career aspirations.
-The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically signficant.
+The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically significant.
 Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables.
@@
 It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.
-Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectificaion are needed.
+Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are needed.
 
@@
 The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating/romantic partner.
-We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---perhaps they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
+We think that heterosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---perhaps they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
 Since both men and women are socialized in a culture that sexually objectifies women, both men and women may come to internalize this socialization and sexually objectify women.
 Indeed, recent research has found that the more women self-objectify, the more they objectify other women [@loughnan2015exploring; @puvia2013being], although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women [@strelan2005women].
-This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships, adding variability.
+This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships.
 
@@
 
-Interpersonal sexual objectification has been studied in both romantic and platonic contexts.
+<!-- Interpersonal sexual objectification has been studied in both romantic and platonic contexts.
 Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
@@
 Objectification might also occur among platonic friends: Perhaps women could be amplifying each others' state self-objectification *before* the theoretical encounters with men organized in the SIMO occur.
-In this way, women's rituals of getting ready together before socilizing in co-ed groups might place even women with low TSO in a higher SSO group.
+In this way, women's rituals of getting ready together before socializing in co-ed groups might place even women with low TSO in a higher SSO group.
+-->
 
-###Sexism and Sexual Discrimination
-Sexism has been found to be related to the objectification of women, but not men [@cikara2011agents; @harsey2020men], and in addition, TSO has been found to be associated with less negative attitudes towards sexual harassment [@bernard2018bodies].
+<!-- ###Sexism and Sexual Discrimination -->
+<!-- Sexism has been found to be related to the objectification of women, but not men [@cikara2011agents; @harsey2020men], and in addition, TSO has been found to be associated with less negative attitudes towards sexual harassment [@bernard2018bodies].
 Both of these effects are present for both men and women.
@@
 Sexual objectification of women has also been linked to trauma [@miles2015stop].
-Sexual objectification occurs in a mirad of ways in women's lives and is modified by unique combinations of race, ethnicity, sexuality, age, and class [@robertsfredrickson].
+Sexual objectification occurs in a myriad of ways in women's lives and is modified by unique combinations of race, ethnicity, sexuality, age, and class [@robertsfredrickson].
 Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
+-->
 
@@
 The results of this study demonstrate the complex and ambivalent nature of sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
-These results are quite useful for promoting mental health, the creation and maintence of early action programs for girls and young women, and for scholars and practitioners to work intentially to provide the tools necessary to circumvent or mitigate negative effects on self-objectification to combat such experiences.
+These results are quite useful for promoting mental health, the creation and maintenance of early action programs for girls and young women, and for scholars and practitioners to work intentionally to provide the tools necessary to circumvent or mitigate negative effects on self-objectification to combat such experiences.
+
+\newpage
 
 #References
-
-\newpage
 

### 2020-10-19 Final_Manuscript.tex
final edits for first submission

@@
 
-\authornote{
+\authornote{Randi L. Garcia is in the Psychology Department
+and the Statitsical and Data Sciences program at Smith College.
+
+The data that support the findings of this study are available on
+request from the corresponding author. The data are not publicly
+available due to privacy or ethical restrictions.
 
@@
 \abstract{
-Extant research on interpersonal objectification has focused mostly on
+Existing research on interpersonal objectification has focused mostly on
 links between objectification, self-objectification, and negative
@@
 the present study was to extend past research on interpersonal
-objectification to interactions between pairs of women. Women were
-brought into the laboratory and interacted face-to-face in same-sex
-dyads. Dyadic analysis (Kenny, Kashy, \& Cook, 2006) was utilized to
-detect whether partners' objectification of each other affected state
+objectification to interactions between women. Women were brought into
+the laboratory and interacted face-to-face in same-sex dyads. Dyadic
+analysis (Kenny, Kashy, \& Cook, 2006) was utilized to detect whether
+partners' objectification of each other affected state
 self-objectification, as well as the resulting feelings of comfort and
@@
 was no significant relationship between self-objectification and
-interaction inauthenticity. Further, there were significant negative
-effects of inauthenticity on career aspirations and relationship agency
-(actor effects). The significant partner effect of objectification on
+interaction inauthenticity, but there were significant negative effects
+of inauthenticity on career aspirations and relationship agency (actor
+effects). The significant partner effect of objectification on
 self-objectification suggests that women being objectified by other
@@
 be the strongest under the \enquote{male gaze,} that is, when it is a
-percieved or actual man doing the objectifying (Calogero, 2004; Gay \&
+perceived or actual man doing the objectifying (Calogero, 2004; Gay \&
 Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
@@
 theoretical model called the Social Interaction Model of Objectification
-(SIMO). The SIMO is useful for studying mixed-gender interactions, but
-can it be extended to interactions among women? Although there is
-evidence that women can objectify other women (Gervais, Holland, \&
-Dodd, 2013; Loughnan et al., 2015; Puvia \& Vaes, 2013), studies
-investigating the process of interpersonal objectification in
-interactions between women is scarce.
+(SIMO). The SIMO focuses on understanding mixed-gender interactions,
+acknowledging the patriarchal power structure embedded in these mixed
+interactions, but can it be extended to interactions among women?
+Although there is evidence that women can objectify other women
+(Gervais, Holland, \& Dodd, 2013; Loughnan et al., 2015; Puvia \& Vaes,
+2013), studies investigating the process of interpersonal
+objectification in interactions between women is scarce.
 
@@
 investigating interpersonal objectification among interacting pairs
-where both partners identify as women. We first review the literature on
-self-objectification, then we review the evidence for women objectifying
-other women before turning to the literature on interpersonal
-objectification.
+where both partners identify as women.
 
@@
 that self-objectification can be conceptualized as a learned trait, or
-\emph{trait} self-objectification (TSO), whereby one abopts a habitual
+\emph{trait} self-objectification (TSO), whereby one adopts a habitual
 third-person perspective on one's own appearance. Furthermore,
@@
 
-There is evidence that being objectified by another person during an
-interaction elicits SSO. For example, Loughnan et al. (2017) found that
-for women, imagining a time when they were objectified by another person
-caused reductions in human traits attributed to the self, and notably,
-the gender of the person doing the objectification was not a moderating
-factor. In addition, in a mixed-gender dyadic study of actual
-interactions, Garcia et al. (2016) found that men's reported
-objectification of their female interaction partner was associated with
-increased self-objectification (as reported by their female partner).
-Further, this negative effect of the men's objectification on women's
-SSO was strongest for women higher in TSO. The current study uses this
-same dyadic paradigm to study same-gender, woman-woman interacting
-pairs.
+Perhaps the most adverse negative consequence of interpersonal
+objectification is that being objectified socializes girls and women to
+routinely treat themselves as objects to be looked at and evaluated
+(Bartky, 1990). There is experimental and observational evidence that
+being objectified by another person during an interaction elicits SSO.
+For example, Loughnan et al. (2017) found that for women, imagining a
+time when they were objectified by another person caused reductions in
+human traits attributed to the self, and notably, the gender of the
+person doing the objectification was not a moderating factor. In
+addition, in a mixed-gender dyadic study of actual interactions, Garcia
+et al. (2016) found that men's reported objectification of their female
+interaction partner was associated with increased self-objectification
+in the female partner. Further, this negative effect of the men's
+objectification on women's SSO was strongest for women higher in TSO.
+The current study uses this same dyadic paradigm to study same-gender,
+woman-woman interacting pairs.
 
@@
 Past research investigating women objectifying other women has focused
-on the psychological conditions that led women to objectify women.
-Harsey and Zurbriggen (2020) found that (trait) self-objectification was
-related to the objectification of women to a similar degree for male and
-female participants. Along the same lines, Strelan and Hargreaves (2005)
-found that the more women self-objectify, the more they objectify other
-women. Could the process work in the other direction as well, that is,
-could objectification by a woman produce (state) self-objectification,
-in a similar manner to objectification by a man? Hill and Fischer (2008)
-assessed women's experiences of objectification from men independently
-from women's experiences of objectification from other women. They found
-that women may be socialized not only to see themselves as objects, but
-perhaps to see other women as objects as well. This process, however,
-was not comfirmed to occur during an actual interpersonal interaction.
-Thus, there is evidence that women do objectify other women, indeed,
-Loughnan et al. (2017) found that women objectify other women to a
-greater extent than they objectify men. Women have also been found to
-objectify (dehumanized) sexualized targets presented as images (Puvia \&
-Vaes, 2013), but very little is known about interpersonal sexual
+on the psychological conditions that lead women to objectify other
+women. Harsey and Zurbriggen (2020) found that (trait)
+self-objectification was related to the objectification of women to a
+similar degree for male and female participants. Along the same lines,
+Strelan and Hargreaves (2005) found that the more women self-objectify,
+the more they objectify other women. Could the process work in the other
+direction as well, that is, could objectification by a woman produce
+(state) self-objectification, in a similar manner to objectification by
+a man? Hill and Fischer (2008) assessed women's experiences of
+objectification from men independently from women's experiences of
+objectification from other women. They found that women may be
+socialized not only to see themselves as objects, but perhaps to see
+other women as objects as well. This process, however, was not confirmed
+to occur during an actual interpersonal interaction. Thus, there is
+evidence that women do objectify other women, indeed, Loughnan et al.
+(2017) found that women objectify other women to a greater extent than
+they objectify men. Women have also been found to objectify
+(dehumanized) sexualized targets presented as images (Puvia \& Vaes,
+2013), but very little is known about interpersonal sexual
 objectification among women and what the effects of this objectification
-might be. Past studies have foud that objectification has more adverse
+might be. Past studies have found that objectification has more adverse
 consequences for women than men (Gervais et al., 2011; Moradi \& Huang,
 2008; Saguy et al., 2010), however, we do not know much about the effect
-of the gender of the \emph{objectifyer} on potential detrimental
+of the gender of the \emph{objectifyer} on these potential detrimental
 outcomes.
@@
 internalize the objectifying gaze on their physical self (Puvia \& Vaes,
-2013; Young, 1979). As mentiond above, interpersonal objectification has
-been found to have negative consequences for women. Gervais et al.
-(2011) found that an objectifying gaze by a male interaction partner
-(confederate) was associated with lower math performance for women than
-being objectified by a female interaction partner. Perhaps the most
-adverse negative consequence of interpersonal objectificaiton is that
-being objectified socializes girls and women to routinely treat
-themselves as objects to be looked at and evaluated (Bartky, 1990; B. L.
-Fredrickson et al., 1998). Gervais et al. (2020) recently reviewed the
-research on interpersonal objectification and organized our current
-theoretical understanding of this process in the Social Interaction
-Model of Objectification (SIMO). What is clear from Gervais et al.
-(2020)'s review is that we know little about women-on-women
-interpersonal objectification. Could there also be negative consequences
-for women after being objectified by a woman?
+2013). As mentioned above, interpersonal objectification has been found
+to have negative consequences for women. Gervais et al. (2011) found
+that an objectifying gaze by a male interaction partner (confederate)
+was associated with lower math performance for women than being
+objectified by a female interaction partner. Gervais et al. (2020)
+recently reviewed the research on interpersonal objectification and
+organized our current theoretical understanding of this process in the
+SIMO. What is clear from Gervais et al. (2020)'s review is that we know
+little about women-on-women interpersonal objectification.
 
@@
 self-objectification in mixed-gender contexts (stranger and romantic;
-Strelan and Pagoudis (2018); Meltzer (2020)) has negative consequences
-for women, but what about in the context of interactions with other
-women? Is the self-objectification experienced in mixed-gender
-interactions associated with the same negative process as that
-experienced in same-gender interactions? The ample research
-demonstrating that the male gaze has a particularly detrimental effect
-for women would suggest no (Calogero, 2004; Gay \& Castano, 2010;
-Gervais et al., 2011; Saguy et al., 2010; Yilmaz \& Bozo, 2019), but,
-there is evidence that women do objectify other women (Harsey \&
-Zurbriggen, 2020; Loughnan et al., 2015; Puvia \& Vaes, 2013) and it
-would be helpful to understand the consequencs of this \emph{intra}group
+Strelan and Pagoudis (2018); Meltzer (2020); Zurbriggen, Ramsey, and
+Jaworski (2011)) has negative consequences for women, but what about in
+the context of interactions with other women? Is the
+self-objectification experienced in mixed-gender interactions associated
+with the same negative process as that experienced in same-gender
+interactions? The ample research demonstrating that the male gaze has a
+particularly detrimental effect for women would suggest no (Calogero,
+2004; Gay \& Castano, 2010; Gervais et al., 2011; Saguy et al., 2010),
+but, there is evidence that women do objectify other women (Harsey \&
+Zurbriggen, 2020; Loughnan et al., 2015; Puvia \& Vaes, 2013) and recent
+experimental evidence suggests that the female gaze causes no less
+self-objectification than the male gaze (Yilmaz \& Bozo, 2019). It would
+be helpful to understand the consequences of this \emph{intra}group
 objectification for women. When women objectify other women, does it
@@
 self-objectification on the reduction of relationship building skills in
-general (including same-sex friendships) (Terán et al., 2020). This link
-has also been found in research on stigmatized-stigmatizer interactions
-(M. R. Hebl \& Dovidio, 2005; Richeson \& Shelton, 2003; Shelton,
-Richeson, \& Salvatore, 2005), and we might view the experience of being
-objectified in an interaction as a potential identity threat,
-stigmatizing, situation (Gervais et al., 2020; Nadal \& Haynes, 2012).
-Further, empirical evidence reveals that healthy relationship
-functioning manifests through authenticity in romantic relationships
-(Brunell et al., 2010), an intergroup context at least in heterosexual
-relationships. Evidence for otehr adverse consquences of interpersonal
+general (including same-sex friendships) (Terán et al., 2020).
+Authenticity reduction and interaction quality disruptions have also
+been found in research on stigmatized-stigmatizer interactions (M. R.
+Hebl \& Dovidio, 2005; Pearson et al., 2008; Richeson \& Shelton, 2003;
+Shelton, Richeson, \& Salvatore, 2005), and we might view the experience
+of being objectified in an interaction as a potential identity threat
+situation (Gervais et al., 2020; Nadal \& Haynes, 2012). Further,
+empirical evidence reveals that healthy relationship functioning
+manifests through authenticity in romantic relationships (Brunell et
+al., 2010), an intergroup context at least in heterosexual
+relationships. Evidence for other adverse consequences of interpersonal
 objectification include reductions in career aspirations (Garcia et al.,
@@
 performance (Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn, Chaudoir,
-\& Kallen, 2011). These are also negative conseqences found for women
-under steroetype threat (Davies, Spencer, \& Steele, 2005). When a woman
+\& Kallen, 2011). These are also negative consequences found for women
+under stereotype threat (Davies, Spencer, \& Steele, 2005). When a woman
 is objectified by a man, and subsequently experiences
@@
 face-to-face interaction paradigm and dyadic data analysis techniques to
-examine the effects for both women simultaneously. Although the
-literature on intragroup woman objectification is small, the results are
-mixed and do not cover interpersonal encourters, we expected to
-replicate some of the results found in Garcia et al. (2016). Most
-importantly, we predicted that being objectified by one's interaction
-partner would be related to state self-objectification (SSO). We also
-expected that TSO would moderate this relationship, amplifying the
-positive assocaition between being objectified and SSO for women higher
-in TSO. Here we would like to note that Puvia and Vaes (2013) would
-alternatively predict that women's tendency to self-objectify (TSO)
-leads them to objectify other women (more precisely, to dehumanize a
-sexualized woman). In addition, Strelan and Hargreaves (2005) and Harsey
-and Zurbriggen (2020) would also predict the TSO to
-other-objectification link, further theorizing that this relationship is
-mediated by the woman's own state self-objectification (SSO). Thus, the
-limited but extant literature on woman-woman objectification points to a
-possible alternative model from the model tested in the current study.
-Where appropriate, we report results considering the causal directions
-implied by this alternative mediation model.
+examine the relationships for both women simultaneously. Although the
+literature on intragroup objectification among women is small, the
+results are mixed, and they do not cover interpersonal encounters, we
+expected to replicate some of the results found in Garcia et al. (2016).
+Most importantly, we predicted that being objectified by one's
+interaction partner would be related to state self-objectification
+(SSO). We also expected that TSO would moderate this relationship,
+amplifying the positive association between being objectified and SSO
+for women higher in TSO. Here we would like to note that Puvia and Vaes
+(2013) would alternatively predict that women's tendency to
+self-objectify (TSO) leads them to objectify other women (more
+precisely, to dehumanize a sexualized woman). In addition, Strelan and
+Hargreaves (2005) and Harsey and Zurbriggen (2020) would also predict
+the TSO to other-objectification link, further theorizing that this
+relationship is mediated by the woman's own state self-objectification
+(SSO). Thus, the limited but extant literature on woman-woman
+objectification points to a possible alternative model from the model
+tested in the current study. Where appropriate, we report results
+considering the causal directions implied by this alternative mediation
+model.
 
@@
 connection is considered exploratory given the lack of support for this
-connection from the literature on identity threat in \emph{intr}agroup
-interactions (Rollero, 2016) but support for this connection in the
-objectification literature (Garcia et al., 2016; Terán et al., 2020).
+connection from the literature on identity threat in \emph{intra}group
+interactions but support for this connection in the objectification
+literature (Garcia et al., 2016; Rollero, 2016; Terán et al., 2020).
 Regardless of whether there was an association between SSO and
@@
 other-objectification by one's partner and state self-objectification.
-We also expected to find a negative relationship between self-state
+We also expected to find a negative relationship between state-self
 objectification and interaction authenticity, and that interaction
@@
 found to occur after a mere relationship prime among women (Sanchez \&
-Broccoli, 2008) because, in Westurn culture and beyond, women need to
+Broccoli, 2008) because, in Western culture and beyond, women need to
 look attractive to obtain and maintain successful relationships, thus,
@@
 as romantic partners (i.e., their sexual attractiveness; Puvia \& Vaes,
-2013)---indeed, women may be unfortunately quite used to thinking about
-their own \enquote{datability,} and we suspect this this habitual
-thought pattern will translate to their thoughts about other women.
-Analyses comparing levels of other-objectification between heterosexual
-and non-heterosexual women are provided in the measures section below.
-
-After recieving the \enquote{College Relationships} prompt, the two
+2013)---women may be unfortunately quite used to thinking about their
+own \enquote{datability,} and we suspect this this habitual thought
+pattern will translate to their thoughts about other women. Analyses
+comparing levels of other-objectification between heterosexual and
+non-heterosexual women are provided in the measures section below.
+
+After receiving the \enquote{College Relationships} prompt, the two
 participants were then brought into a larger interaction room where they
@@
 the measures section that follows we refer to them as Sample 1 and
-Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal arts college
-and Sample 2 (\emph{N =} 40) is from a women's liberal arts college.
-More specifically, twelve of the pairs were students at a co-ed liberal
-arts college, while the remaining twenty pairs attended a women's
-liberal arts college.\footnote{Initially, data was collected from both
+Sample 2. Sample 1 (\emph{N =} 24, or 12 pairs) is from a co-ed liberal
+arts college and Sample 2 (\emph{N =} 40, or 20 pairs) is from a women's
+liberal arts college. Initially, data was collected from both
 same-gender and mixed-gender dyads at both institutions. Sample 1
-  originally consisted of 22 pairs, 12 men and 32 women. In Sample 2
-  there were 23 pairs made up of 43 women and one man, as well as two
+originally consisted of 22 pairs, 12 men and 32 women. In Sample 2 there
+were 23 pairs made up of 43 women and one man, as well as two
 participants who did not identify as either a woman or man. To
-  investigate only same-gender pairs of women, we limited participant
-  data to women in both samples.} All results presented below are from
-models including sample as a control variable.
+investigate only same-gender pairs of women, we limited participant data
+to women in both samples. Due to difficulties in the logistics of dyadic
+interaction studies, data collection was discontinued after one year at
+the second institution and the sample size was taken as the number of
+women-women dyads at this point in time. All results presented below are
+from models including sample as a control variable.
 
@@
 gay, lesbian or bisexual. See the analysis of differences between
-heteroseuxal and non-heterosexual women in levels of
+heterosexual and non-heterosexual women in levels of
 other-objectification of their female partners in the measures section
@@
 5.03 (SD = 2.29). Cognitive performance was measured first directly
-after the intercation in order to measure potential immediate detriments
+after the interaction in order to measure potential immediate detriments
 to performance (Garcia et al., 2016).
@@
 had low correlations with the remaining items, ranging from .02 to .30
-for the first sample, and .04 to .30 for the second sample. The item was
-intended to be reverse coded, but correlations were still low enough to
-make the scale unreliable. Therefore, the ninth item was removed. As a
-result, the 8-item scale had moderately high reliability for both
-samples (\(\alpha\) = 0.72 for Sample 1, (\(\alpha\) = 0.74 for Sample
-2).
+for the first sample, and .04 to .30 for the second sample. Therefore,
+this item was removed. As a result, the 8-item scale had moderately high
+reliability for both samples (\(\alpha\) = 0.72 for Sample 1,
+(\(\alpha\) = 0.74 for Sample 2).
 
@@
 To conceptualize participants' career aspirations after the interaction,
-we used the 10-item adaptation of P. Gray and M. OBrien (2007)'s Career
+we used the 10-item adaptation of Gray and OBrien (2007)'s Career
 Aspiration Scale which asked participants to consider how true 10
@@
 The R-package \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018)
-was used to create a fully reproducible research document containing the
-analysis code and manuscript text integrated into one source file. The
-benefit of this integration is that the numbers reported throughout this
-document are softcoded into the text, ensuring that no errors were made
+was used to create a fully reproducible APA style manuscript containing
+the analysis code and manuscript text integrated into one source file.
+The benefit of this integration is that the numbers reported throughout
+this document are coded into the text, ensuring that no errors were made
 during a workflow marked by copying and pasting from statistical
@@
 code for this manuscript along with survey materials and experimenter
-scripts for the study protocol are all avaliable at
+scripts for the study protocol are all available at
 \url{https://github.com/kkyuchukova/object-in-action}. The data
-unfortunutely cannot be made publically avaliable given the dyadic
-nature of the observations. For example, with dyadic data, if a person
-who participated in the study found their own scores, using the dyad
+unfortunately cannot be made publicly available given the dyadic nature
+of the observations. That is, with dyadic data, if a person who
+participated in the study found their own scores, using the dyad
 identification number, they could then see their partner's scores and
-thus confidentiality would be broken.
+thus confidentiality would be breached.
 
@@
 dyadic path analysis (Garcia et al., 2016), the current study used
-multilevel modeling proceedures. Dyadic analyses for distinguishable
+multilevel modeling procedures. Dyadic analyses for distinguishable
 dyads (e.g., mixed-gender interacting pairs) is more natural using
@@
 other objectification and SSO in this sample of same-gender woman-woman
-interacting dyads. In Garcia et al. (2016) men's objectification of
+interacting dyads. In Garcia et al. (2016), men's objectification of
 women was significantly related to women's SSO, the current study sought
-to replicate this effect. As expected, the partner effect of
+to replicate this partner effect. As expected, the partner effect of
 other-objectification on SSO in the current all-women sample was
@@
 (2016) study, there is now evidence that interpersonal objectification
-in an actual interpersonal encounter is realted to state
+in an actual interpersonal encounter is related to state
 self-objectification for women both when the objectifyer is a man and
@@
 interaction of partner other-objectification and TSO. One's own other
-objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE} =
-0.12, \emph{p} = .210. Further, inconsistent with past findings however,
-there was no statistically significant interaction of partner's other
-objectification and the person's trait self-objectification on SSO,
-\emph{b} = 0.03, \emph{SE} = 0.27, \emph{p} = .910. There was also no
-significant main effect of trait self-objectification on SSO \emph{b} =
-0.07, \emph{SE} = 0.05, \emph{p} = .183. The \(R^2\) of this model was
-0.03.
-
-As a test of the potential alternative models discussed above---if
-trait-self-objectification is related to objectifying one's partner to a
-greater degree---we ran a MLM with other-objectification predicted by
-actor TSO. There was no statistically significant relationship between
-these two variables, \emph{b} = 0.09, \emph{SE} = 0.06, \emph{p} = .133.
-We also ran a model with both TSO and SSO predicting
-other-objectification, given past theorizing that state
+objectification had no significant effect on SSO (actor effect of
+other-objectification), \emph{b} = -0.16, \emph{SE} = 0.12, \emph{p} =
+.210. Further, inconsistent with past findings, there was no
+statistically significant interaction of partner's other objectification
+and the person's trait self-objectification on SSO, \emph{b} = 0.03,
+\emph{SE} = 0.27, \emph{p} = .910. There was also no significant main
+effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
+0.05, \emph{p} = .183. The \(R^2\) of this model (which includes the
+partner effect of other-objectification discussed in the previous
+paragraph) was only 0.03.
+
+As a test of the potential alternative models discussed in the
+introduction---if trait-self-objectification is positively related to
+objectifying one's partner---we ran a MLM with other-objectification
+predicted by actor TSO. There was no statistically significant
+relationship between these two variables, \emph{b} = 0.09, \emph{SE} =
+0.06, \emph{p} = .133. We also ran a model with both TSO and SSO
+predicting other-objectification, given past theorizing that state
 self-objectification might mediate the relationship between TSO and
-objectification of fellow women, but there was no effect of SSO on
+objectification of fellow women, but there was also no effect of SSO on
 other-objectification in this model, \emph{b} = -0.17, \emph{SE} = 0.13,
@@
 performance, career aspirations, and relationship agency, as it did in
-Garcia et al. (2016) and as would be predicted by Terán et al. (2020).
-We again used MLM and thus, these effects were tested in three separate
-multilevel linear models. There was no significant effect of interaction
-authenticity on cognitive performance, \emph{b} = 0.32, \emph{SE} =
-0.28, \emph{p} = .258, but authenticity was significantly positively
-related to both career aspirations, \emph{b} = 0.18, \emph{SE} = 0.07,
-\emph{p} = .010 (\(R^2 =\) 0.04), and relationship agency, \emph{b} =
-0.23, \emph{SE} = 0.12, \emph{p} = .049 (\(R^2 =\) 0.01).\footnote{There
-  was no direct effect of SSO on cognitive performance, \emph{b} = 0.04,
-  \emph{SE} = 0.25, \emph{p} = .872, and no direct effect of partner's
-  other objectification on cognitive performance, \emph{b} = 0.01,
-  \emph{SE} = 0.27, \emph{p} = .962. There was no direct effect of SSO
-  on career aspirations, \emph{b} = 0.03, \emph{SE} = 0.06, \emph{p} =
-  .657, and no direct effect of partner's other objectification on
-  career aspirations, \emph{b} = -0.06, \emph{SE} = 0.07, \emph{p} =
-  .378. There was no direct effect of SSO on relationship agency,
-  \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} = .659, and no direct
-  effect of partner's other objectification on relationship agency,
-  \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.}
+Garcia et al. (2016). We again used MLM and thus, these effects were
+tested in three separate multilevel linear models. There was no
+significant effect of interaction authenticity on cognitive performance,
+\emph{b} = 0.32, \emph{SE} = 0.28, \emph{p} = .258, but authenticity was
+significantly positively related to both career aspirations, \emph{b} =
+0.18, \emph{SE} = 0.07, \emph{p} = .010 (\(R^2 =\) 0.04), and
+relationship agency, \emph{b} = 0.23, \emph{SE} = 0.12, \emph{p} = .049
+(\(R^2 =\) 0.01).
 
@@
 them to be objectified by their interaction partner. This latter
-interpretation is possible given the empiricle evidence that it is
+interpretation is possible given the empirical evidence that it is
 \emph{women's} state self-objectification that relates to being
@@
 al., 2010), suggest that the causal flow is from other-objectification
-to SSO. Other studies, especailly those investigating explicitly women
-objectifying other women (Puvia \& Vaes, 2013), have relately found
+to SSO. Other studies, especially those investigating explicitly women
+objectifying other women (Puvia \& Vaes, 2013), have relatedly found
 evidence that women's \emph{trait} self-objectification is related to
@@
 perhaps we tend to objectify other women who objectify us and through a
-process of TSO causing SSO which in turn causes objectifation of one's
+process of TSO causing SSO which in turn causes objectification of one's
 partner, which in turn causes one's partner to objectify us. However,
 the current study does not provide any evidence of the TSO to
-other-objectifixation link---TSO was not significantly correlated with
+other-objectification link---TSO was not significantly correlated with
 SSO and, further, actor's other-objectification was not correlated with
@@
 mixed-gender dyads is the lack of evidence for relationships between SSO
-and interaction inauthenticity.\footnote{In addition, we found no
-  evidence of \emph{direct} or \emph{indirect} relationships between SSO
-  and cognitive functioning, relationship agency, and career
-  aspirations. Nor was there evidence of \emph{direct} or
-  \emph{indirect} relationships between other-objectification and any of
-  these outcomes.} This is somewhat suprising given the extant evidence
-linking SSO and cognitive functioning (B. L. Fredrickson et al., 1998;
-and see Moradi \& Huang, 2008 for a review; Quinn, Chaudoir, \& Kallen,
-2011) and the research on interpersonal other-ojectification and
-cognitive functioning (Garcia et al., 2016; Gervais et al., 2011; Logel
-et al., 2009). This lack of evidence could potentially signal diverging
-processes between women's experiences with interpersonal objectification
-from men and interpersonal objectification from women. There is quite a
-bit of evidence suggesting that the male gaze is particularly
-detrimental (Calogero, 2004; Fredrickson \& Roberts, 1997; Gervais et
-al., 2011), and perhaps the self-objectification experienced within an
-interaction with a women is qualitatively different, and perhaps not as
-harmful, as the state self-objectification experienced within an
-interaction with a man. However, as a strong note of caution, it is best
-not to interpret a null result as evidence of no relationship and more
-research on interpersonal objectification among women is needed.
+and interaction inauthenticity. This is somewhat surprising given the
+extant evidence linking SSO and cognitive functioning (B. L. Fredrickson
+et al., 1998; and see Moradi \& Huang, 2008 for a review; Quinn,
+Chaudoir, \& Kallen, 2011) and the research on interpersonal
+other-objectification and cognitive functioning (Garcia et al., 2016;
+Gervais et al., 2011; Logel et al., 2009). This lack of evidence could
+potentially signal diverging processes between women's experiences with
+interpersonal objectification from men and interpersonal objectification
+from women. There is quite a bit of evidence suggesting that the male
+gaze is particularly detrimental (Calogero, 2004; Fredrickson \&
+Roberts, 1997; Gervais et al., 2011), and perhaps the
+self-objectification experienced within an interaction with a women is
+qualitatively different, and perhaps not as harmful, as the state
+self-objectification experienced within an interaction with a man.
+However, as a strong note of caution, it is best not to interpret a null
+result as evidence of no relationship and more research on interpersonal
+objectification among women is needed.
 
@@
 women. Perhaps one important difference is the lack of a power
-differential across gendered lines -- the patriarchy is present, but the
-interafction partners are not a stigmatizer-stigmatized pair.
+differential across gendered lines -- the patriarchal culture is
+present, but the interaction partners are not a stigmatizer-stigmatized
+pair.
 
@@
 functioning was also estimated as positive, but was not statistically
-signficant. Again, due to the lack of connection between SSO and
+significant. Again, due to the lack of connection between SSO and
 authenticity, we found no evidence of \emph{indirect} relationships
@@
 important for healthy relationship functioning (Garcia et al., 2016;
-Terán et al., 2020). Just as authenticity has been found to be important
-in intergroup interactions (Brunell et al., 2010; Garcia et al., 2016;
-Tolman et al., 2006), we find more evidence here that disruptions in
-feelings of authenticity can negatively impact relationships beyond the
-current partner. Although the current study did not find a connection
-between authenticity and SSO, this seems theoretically to be a natural
-connection, and future work must explore when and how SSO leads to
-inauthenticity in interpersonal objectification situations.
+Terán et al., 2020) and is related to mental health correlates (Tolman
+et al., 2006). Just as authenticity has been found to be important in
+intergroup interactions (Brunell et al., 2010; Garcia et al., 2016), we
+find more evidence here that disruptions in feelings of authenticity can
+negatively impact relationships beyond the current partner. Although the
+current study did not find a connection between authenticity and SSO,
+this seems theoretically to be a natural connection, and future work
+must explore when and how SSO leads to inauthenticity in interpersonal
+objectification situations.
 
@@
 the developmental experience of interpersonal objectification and
-self-objectificaion are needed.
+self-objectification are needed.
 
@@
 and evaluate their partner as a potential dating/romantic partner. We
-think that hetereosexual women are able to do this with other women as
+think that heterosexual women are able to do this with other women as
 their target---and there is evidence that they might do this readily
@@
 with differing sexualities might have served to dampen our ability to
-detect relationships, adding variability.
+detect relationships.
 
@@
 
-Interpersonal sexual objectification has been studied in both romantic
-and platonic contexts. Among heterosexual male and female college
-students, self-objectification has been found to be positively
-associated with the extent to which they objectify their romantic
-partners (Zurbriggen, Ramsey, \& Jaworski, 2011). Evidence is mixed,
-suggesting that women can sometimes have positive outcomes from
-appearance valuation within the context of an established romantic
-relationship. There is also evidence that they experience less SSO after
-appearance comments within established romantic relationships (Meltzer,
-2020), but less is known about first dates. An important caveat to this
-literature is that it is only about heterosexual relationships.
-Objectification might also occur among platonic friends: Perhaps women
-could be amplifying each others' state self-objectification
-\emph{before} the theoretical encounters with men organized in the SIMO
-occur. In this way, women's rituals of getting ready together before
-socilizing in co-ed groups might place even women with low TSO in a
-higher SSO group.
-
-\subsubsection{Sexism and Sexual
-Discrimination}\label{sexism-and-sexual-discrimination}
-
-Sexism has been found to be related to the objectification of women, but
-not men (Cikara, Eberhardt, \& Fiske, 2011; Harsey \& Zurbriggen, 2020),
-and in addition, TSO has been found to be associated with less negative
-attitudes towards sexual harassment (Bernard, Legrand, \& Klein, 2018).
-Both of these effects are present for both men and women. Empirical
-evidence illustrates how women continue to be objects of interpersonal
-discrimination and experience daily sexist hassles (Swim, Hyers, Cohen,
-\& Ferguson, 2001). One form of interpersonal discrimination women face
-is the process by which their whole being is viewed as a collection of
-sexualized body parts valued predominantly for commodification, a
-phenomena termed sexual objectification (Bartky, 1990). Sexual
-objectification of women has also been linked to trauma (Miles-McLean et
-al., 2015). Sexual objectification occurs in a mirad of ways in women's
-lives and is modified by unique combinations of race, ethnicity,
-sexuality, age, and class (Fredrickson \& Roberts, 1997). Amid such
-heterogeneity though, \enquote{having a reproductively mature female
-body} proposed by Fredrickson and Roberts (1997) is likely to create a
-shared vulnerability to sexual objectification and a variety of shared
-negative experiences as a result.
-
 \section{Conclusion}\label{conclusion}
@@
 social relationships and well-being. These results are quite useful for
-promoting mental health, the creation and maintence of early action
+promoting mental health, the creation and maintenance of early action
 programs for girls and young women, and for scholars and practitioners
-to work intentially to provide the tools necessary to circumvent or
+to work intentionally to provide the tools necessary to circumvent or
 mitigate negative effects on self-objectification to combat such
@@
 
+\newpage
+
 \section{References}\label{references}
-
-\newpage
 
@@
 phenomenology of oppression}. Routledge, New York.
-
-\hypertarget{ref-bernard2018bodies}{}
-Bernard, P., Legrand, S., \& Klein, O. (2018). From bodies to blame:
-Exposure to sexually objectifying media increases tolerance toward
-sexual harassment. \emph{Psychology of Popular Media Culture},
-\emph{7}(2), 99.
 
@@
 
-\hypertarget{ref-cikara2011agents}{}
-Cikara, M., Eberhardt, J. L., \& Fiske, S. T. (2011). From agents to
-objects: Sexist attitudes and neural responses to sexualized targets.
-\emph{Journal of Cognitive Neuroscience}, \emph{23}(3), 540--551.
-
 \hypertarget{ref-davies2005clearing}{}
@@
 
+\hypertarget{ref-grayobrien2007}{}
+Gray, M. P., \& OBrien, K. M. (2007). Advancing the assessment of
+women's career choices: The career aspiration scale. \emph{Journal of
+Career Assessment - J CAREER ASSESSMENT}, \emph{15}, 317--337.
+doi:\href{https://doi.org/10.1177/1069072707301211}{10.1177/1069072707301211}
+
 \hypertarget{ref-harsey2020men}{}
@@
 and Social Psychology Bulletin}, \emph{46}(2), 243--257.
-
-\hypertarget{ref-miles2015stop}{}
-Miles-McLean, H., Liss, M., Erchull, M. J., Robertson, C. M., Hagerman,
-C., Gnoleba, M. A., \& Papp, L. J. (2015). ``Stop looking at me!''
-interpersonal sexual objectification as a source of insidious trauma.
-\emph{Psychology of Women Quarterly}, \emph{39}(3), 363--374.
 
@@
 
-\hypertarget{ref-grayobrien2007}{}
-P. Gray, M., \& M. OBrien, K. (2007). Advancing the assessment of
-women's career choices: The career aspiration scale. \emph{Journal of
-Career Assessment - J CAREER ASSESSMENT}, \emph{15}, 317--337.
-doi:\href{https://doi.org/10.1177/1069072707301211}{10.1177/1069072707301211}
-
 \hypertarget{ref-patil2016statistical}{}
@@
 for reproducibility and replicability. \emph{BioRxiv}, 066803.
+
+\hypertarget{ref-pearson2008fragility}{}
+Pearson, A. R., West, T. V., Dovidio, J. F., Powers, S. R., Buck, R., \&
+Henning, R. (2008). The fragility of intergroup relations: Divergent
+effects of delayed audiovisual feedback in intergroup and intragroup
+interaction. \emph{Psychological Science}, \emph{19}(12), 1272--1279.
 
@@
 Rollero, C. (2016). Bringing objectification into social relationships
-research: Is self-objectification harmful for authenticity?
+research: Is self-objectification harmful for authenticity? \emph{The
+Spanish Journal of Psychology}, (19), 1--7.
 
@@
 
-\hypertarget{ref-swimetal}{}
-Swim, J. K., Hyers, L. L., Cohen, L. L., \& Ferguson, M. J. (2001).
-Everyday sexism: Evidence for its incidence, nature, and psychological
-impact from three daily diary studies. \emph{Journal of Social Issues},
-\emph{57}(1), 31--53.
-doi:\href{https://doi.org/10.1111/0022-4537.00200}{10.1111/0022-4537.00200}
-
 \hypertarget{ref-teran2020relational}{}
@@
 
-\hypertarget{ref-young1979}{}
-Young, I. M. (1979). \emph{Proceedings of the second sex---Thirty years
-later: A commemorative conference on feminist theory,}
-
 \hypertarget{ref-zurbriggen2011self}{}

### 2020-11-09 Final_Manuscript.Rmd
tabling measures

@@
 
-##Post interaction Measures
+## Measures
 
@@
 
-The following measures were collected in the order they are presented following the interaction. Correlations and descriptive statistics of all study variables appear in Table\ \@ref(tab:corrtable).
-
-###Cognitive Performance
-```{r trigram}
+```{r measures, include=TRUE, echo=FALSE, results='asis'}
 #Cognitive performance - Full sample
@@
 sd_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$sd
-```
 
-Trigrams from the Remote Associates Task [@mcfarlin1984remote] were utilized to assess cognitive performance after the interaction.
-Ten items were selected and presented to participants.
-For example, the correct answer for the trigram "Quack: Pond: Waddle" would be "Duck".
-Participants are limited to 30 seconds to provide their answers.
-For every correct answer, 1 point is given.
-The mean score was `r mean_trigram` (SD = `r sd_trigram`).
-Cognitive performance was measured first directly after the interaction in order to measure potential immediate detriments to performance [@garcia2016objectification].
-
-###State Other-Objectification
-```{r alpha_SOO}
 ##SOO
@@
 soo_diff <- t.test(a2pSOO_A ~ (sexor_A == 1), data = clarksmith_women)
-```
-To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts during the interaction in relation to multiple characteristics of their partner [@garcia2016objectification].
-Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
-All questions were rated on a scale from 1 (not at all) to 7 (constantly).
-Objectification was measured by taking the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2).
-A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.
 
-As can be seen in Table\ \@ref(tab:corrtable), the mean other-objectification of women by women was *M =* `r descriptives[3,1]` (*SD =* `r descriptives[3,2]`).
-This corresponds to women objectifying other women to a *greater* extent than women's objectification of men reported in @garcia2016objectification (*M =* -1.68, *SD =* 1.52).
-Further, in the current sample the difference in other-objectification between heterosexual (*M =* `r round(as.numeric(descsplit[2,2]),2)`, *SD =* `r round(as.numeric(descsplit[2,3]),2)`) and non-heterosexual women (*M =* `r round(as.numeric(descsplit[1,2]),2)`, *SD =* `r round(as.numeric(descsplit[1,3]),2)`) was not statistically significant, *t*(`r round(soo_diff$parameter,2)`) = `r round(soo_diff$statistic, 2)`, *p =* `r round(soo_diff$p.value,3)`.
-
-###Interaction Authenticity
-```{r alpha_intauth}
 ##Interaction Authenticity
@@
                                            interaux_6))$total[2]
-```
-To assess the magnitude to which individuals felt comfortable in the interaction and perceived the interaction to be authentic, we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much), much like [@garcia2016objectification].
-Participants were additionally asked to rate their interaction partner’s authenticity as well as their own: "Do you think your partner was authentic during your interaction?" and "Were you authentic during your interaction?" These questions were ranked on a scale from 1 (not at all) to 7 (very much).
-These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2).
 
-###State Self-Objectification
-```{r alpha_SSO}
 ##SSO
@@
 smith_howbody3 <- psych::alpha(select(smith_final, howbody_1, howbody_2, howbody_3))
-```
-To assess state self-objectification, we used an average of two items from @saguyetal2010 that were also used in @garcia2016objectification.
-Participants were asked to rank how much they agreed with the following statements: "During the interaction I felt more like a body than a full self" and "I felt more like a body than as a real person in the interaction".
-Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)
 
-###Relationship Agency
-```{r alpha_relagen}
 ##Relationship Agency
@@
                                          relag_5, relag_6, relag_7, relag_8))$total[2]
-```
-A scale was used from @garcia2016objectification to assess how much agency an individual believes they would possess in future romantic relationships.
-Participants were asked how likely it was that they would do the following: "ask someone out on a date," "open the door for your date," "pay for a date," "ask your boyfriend/girlfriend to marry you," "initiate sex with your girlfriend/boyfriend," "initiate condom use during sex," "surprise your boyfriend/ girlfriend with a gift," and "ask your girlfriend/boyfriend to move with you to a new place." Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).
-The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
-Therefore, this item was removed.
-As a result, the 8-item scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
 
-###Career Aspirations
-```{r alpha_career}
 ##Career Aspirations
@@
                                              careerasp_9, careerasp10.r))$total[2]
-```
-To conceptualize participants’ career aspirations after the interaction, we used the 10-item adaptation of @grayobrien2007’s Career Aspiration Scale which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me).
-Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).
 
-###Trait Self-Objectification
-```{r alpha_TSO}
 ###TSO
@@
 smith_physTSO_alpha <- psych::alpha(select(smith_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
-```
-Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredrickson1998swimsuit; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus non-observable ways.
-The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
+
+source <- c("@mcfarlin1984remote", 
+            "@garcia2016objectification", 
+            "@garcia2016objectification", 
+            "@garcia2016objectification", 
+            "@garcia2016objectification", 
+            "@grayobrien2007", 
+            "@nollfredrickson1998")
+
+ex_item <- c("he correct answer for the trigram "Quack: Pond: Waddle" would be "Duck"",
+             "Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
+All questions were rated on a scale from 1 (not at all) to 7 (constantly).
+A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite",
+             " we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much)
+These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2). 	",
+"Participants were asked to rank how much they agreed with the following statements: "During the interaction I felt more like a body than a full self" and "I felt more like a body than as a real person in the interaction".
+Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)",
+""ask someone out on a date," "open the door for your date," "pay for a date," "ask your boyfriend/girlfriend to marry you," "initiate sex with your girlfriend/boyfriend," "initiate condom use during sex," "surprise your boyfriend/ girlfriend with a gift," and "ask your girlfriend/boyfriend to move with you to a new place." Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).",
+"a scale from 0 (not at all true of me) to 4 (very true of me). 
+Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).",
+"The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
 Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness).
 Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1 so that positive scores indicated greater TSO.
+")
+
+alpha_s1 <- c()
+alpha_s2 <- c()
+
+data.frame(source, ex_item, alpha_s1, alpha_s2)
+
+rownames(corr.table) <- c("Cognitive performance", 
+                          "Objectification of partner", 
+                          "Authenticity of interaction", 
+                          "State self-objectification", 
+                          "Relationship agency", 
+                          "Career aspirations", 
+                          "Trait self objectification (TSO)")
+
+colnames(corr.table)   <- c("Original Source", "Example Item", "Reliability ($\alpha$) Sample 1", "Reliability ($\alpha$) Sample 2")
+
+apa_table(corr.table, caption="Correlations and Descriptive Statistics among Study Variables", escape=FALSE)
+```
+
+The same set of measures given in @garcia2016objectification were given to participants in the current study.
+For more details about each of these measures please see that previous paper.
+To summarize, the list of measures in the order given to participants appears in Table\ \@ref(tab:measures) along side the orginal source for the scale, an example item, and the reliability in the current sample.
+Correlations and descriptive statistics of all study variables appear in Table\ \@ref(tab:corrtable).
+
+Cognitive performance with the Remote Associates Task's trigrams [@mcfarlin1984remote] was given first, to capture any attentional changes that may have been affected by the interaction.
+Next participants were given a set of measure about their thoughts and feelings during the interaction that included State-Other Objectification, Interaction Authenticity, and State Self-Objectification.
+Following these measures participants completed the Relationship Agency Scale and the Career Aspirations Scale.
+Lastly, as was the case in @garcia2016objectification, Trait Self-Objectification was given last, as not to arouse suspicious at the start of the study that we were actually focusing on objectification and to give enough time that immediate effects of the interaction would have worn off.
+
+As can be seen in Table\ \@ref(tab:corrtable), the mean other-objectification of women by women was *M =* `r descriptives[3,1]` (*SD =* `r descriptives[3,2]`).
+This corresponds to women objectifying other women to a *greater* extent than women's objectification of men reported in @garcia2016objectification (*M =* -1.68, *SD =* 1.52).
+Further, in the current sample the difference in other-objectification between heterosexual (*M =* `r round(as.numeric(descsplit[2,2]),2)`, *SD =* `r round(as.numeric(descsplit[2,3]),2)`) and non-heterosexual women (*M =* `r round(as.numeric(descsplit[1,2]),2)`, *SD =* `r round(as.numeric(descsplit[1,3]),2)`) was not statistically significant, *t*(`r round(soo_diff$parameter,2)`) = `r round(soo_diff$statistic, 2)`, *p =* `r round(soo_diff$p.value,3)`.
+
+Relationship agency The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
+Therefore, this item was removed.
+As a result, the 8-item scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
 
@@
 In addition to being relatively small and combined across two institutions, another limitation of the current study sample is that the it was comprised of Western women only.
-Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring] research on objectification conducted outside of Western or Westernized countries has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
-Since “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses” [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon to test the cross-cultural applicability of theoretical frameworks [@loughnan2015exploring].
+Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring] research on objectification [[[conducted outside of Western or Westernized countries]]] has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
+[[[Since “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses”]]] [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon [[[to test the cross-cultural applicability of theoretical frameworks]]] [@loughnan2015exploring].
 
 Further, sexualizing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014].
-Considering the fact that the average mean age of the investigated participants of this current study was `r mean_age` years, research among younger and older individuals is needed, especially because the processes of self-objectification may change over time [@robertsfredrickson].
-It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.
-Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are needed.
+[[Considering the fact that the average mean age of the investigated participants of this current study was `r mean_age` years, research among younger and older individuals is needed]]], especially because the processes of self-objectification may change over time [@robertsfredrickson].
+[[[It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.]]] Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are needed.
 
@@
 We think that heterosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---perhaps they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
-Since both men and women are socialized in a culture that sexually objectifies women, both men and women may come to internalize this socialization and sexually objectify women.
-Indeed, recent research has found that the more women self-objectify, the more they objectify other women [@loughnan2015exploring; @puvia2013being], although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women [@strelan2005women].
+[[[Indeed, recent research has found that the more women self-objectify, the more they objectify other women]]] [@loughnan2015exploring; @puvia2013being], [[[although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women]]] [@strelan2005women].
 This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships.
 
-Previous research has found that when compared to heterosexual women, lesbian women report less concern with physical appearance [@siever1994sexual; @strong2000eating], lower body surveillance [@hill2008examining], and lower self-objectification [@noffsinger2004objectification].
+<!-- Previous research has found that when compared to heterosexual women, lesbian women report less concern with physical appearance [@siever1994sexual; @strong2000eating], lower body surveillance [@hill2008examining], and lower self-objectification [@noffsinger2004objectification].
 However none of these studies examined the relationship between self-objectification and experiences of sexual objectification.
@@
 This evidence sits in contrast to older theoretical literature that suggests that lesbians internalize cultural sexual objectification less than do heterosexual women [@brown1987lesbians; @pitman1999body; @rothblum1994lesbians; @siever1994sexual].
+-->
 
@@
 
-<!-- ###Sexism and Sexual Discrimination -->
-<!-- Sexism has been found to be related to the objectification of women, but not men [@cikara2011agents; @harsey2020men], and in addition, TSO has been found to be associated with less negative attitudes towards sexual harassment [@bernard2018bodies].
+###Sexism and Sexual Discrimination
+Sexism has been found to be related to the objectification of women, but not men [@cikara2011agents; @harsey2020men], and in addition, TSO has been found to be associated with less negative attitudes towards sexual harassment [@bernard2018bodies].
 Both of these effects are present for both men and women.
@@
 Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
--->
 
 #Conclusion
-The results of this study demonstrate the complex and ambivalent nature of sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
+The results of this study ...
+and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
 These results are quite useful for promoting mental health, the creation and maintenance of early action programs for girls and young women, and for scholars and practitioners to work intentionally to provide the tools necessary to circumvent or mitigate negative effects on self-objectification to combat such experiences.

### 2020-11-10 Final_Manuscript.Rmd
tabled measures

@@
 
-```{r measures, include=TRUE, echo=FALSE, results='asis'}
+```{r}
+#Reliabilities and some descriptives
+
 #Cognitive performance - Full sample
@@
                                           otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
-
 descsplit <- clarksmith_women %>%
@@
                                              careerasp_9, careerasp10.r))$total[2]
-
 #Smith
@@
 smith_physTSO_alpha <- psych::alpha(select(smith_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2] 
+```
+
+```{r measures, include=TRUE, echo=FALSE, results='asis'}
+############### TABLE MAKING ###################
 
@@
             "@garcia2016objectification", 
-            "@garcia2016objectification", 
+            "@saguyetal2010", 
             "@garcia2016objectification", 
@@
 
-ex_item <- c("he correct answer for the trigram "Quack: Pond: Waddle" would be "Duck"",
-             "Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts.
-All questions were rated on a scale from 1 (not at all) to 7 (constantly).
-A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite",
-             " we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much)
-These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2). 	",
-"Participants were asked to rank how much they agreed with the following statements: "During the interaction I felt more like a body than a full self" and "I felt more like a body than as a real person in the interaction".
-Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)",
-""ask someone out on a date," "open the door for your date," "pay for a date," "ask your boyfriend/girlfriend to marry you," "initiate sex with your girlfriend/boyfriend," "initiate condom use during sex," "surprise your boyfriend/ girlfriend with a gift," and "ask your girlfriend/boyfriend to move with you to a new place." Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).",
-"a scale from 0 (not at all true of me) to 4 (very true of me). 
-Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).",
-"The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts.
-Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness).
-Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1 so that positive scores indicated greater TSO.
-")
+ex_item <- c("The correct answer for the trigram \"Quack: Pond: Waddle\" would be \"Duck\"",
+             "\"During the interaction, how often did you think about your partner’s personality?\" (...friends, family, and extracurricular interests, body, appearance, clothing, and body parts) on a scale from 1 (not at all) to 7 (constantly).
+A difference between the average internal and exxternal traits is taken",
+             "\"During the interaction, to what extent did you feel comfortable?\" (...happy, friendly, warm, easygoing, sincere, and authentic) on a scale ranging from 1 (not at all) to 7 (very much)",
+             "\"During the interaction I felt more like a body than a full self\"",
+             "\"ask someone out on a date\" Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely)",
+             "\"I hope to become a leader in my career field\"",
+             "Participants rank order aspects of their bodies from 1 (least important) to 10 (most important): weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements, strength, physical coordination, energy level, health and physical fitness.
+Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1 so that positive scores indicated greater TSO.")
 
-alpha_s1 <- c()
-alpha_s2 <- c()
+alpha_s1 <- c("Not avaliable",
+paste("external: ", printnum(clark_extsoo_alpha)[1,1], "; internal: ", printnum(clark_intsoo_alpha)[1,1]),
+printnum(clark_intauth_alpha)[1,1],
+printnum(clark_howbody_alpha)[1,1],
+printnum(clark_relag_alpha)[1,1],
+printnum(clark_careerasp_alpha)[1,1],
+paste("appearance: ", printnum(clark_physTSO_alpha)[1,1], "; competence: ", printnum(clark_funcTSO_alpha)[1,1]))
 
-data.frame(source, ex_item, alpha_s1, alpha_s2)
+alpha_s2 <- c("Not avaliable",
+paste("external: ", printnum(smith_extsoo_alpha)[1,1], "; internal: ", printnum(smith_intsoo_alpha)[1,1]),
+printnum(smith_intauth_alpha)[1,1],
+printnum(smith_howbody_alpha)[1,1],
+printnum(smith_relag_alpha)[1,1],
+printnum(smith_careerasp_alpha)[1,1],
+paste("appearance: ", printnum(smith_physTSO_alpha)[1,1], "; competence: ", printnum(smith_funcTSO_alpha)[1,1]))
 
-rownames(corr.table) <- c("Cognitive performance", 
+meas_table <- data.frame(source, ex_item, alpha_s1, alpha_s2)
+
+rownames(meas_table) <- c("Cognitive performance", 
                           "Objectification of partner", 
@@
 
-colnames(corr.table)   <- c("Original Source", "Example Item", "Reliability ($\alpha$) Sample 1", "Reliability ($\alpha$) Sample 2")
+colnames(meas_table)   <- c("Original Source", "Example Item", "Reliability ($\alpha$) Sample 1", "Reliability ($\alpha$) Sample 2")
 
-apa_table(corr.table, caption="Correlations and Descriptive Statistics among Study Variables", escape=FALSE)
+apa_table(meas_table, caption="Measures", escape=FALSE)
 ```
@@
 
+Howbody used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale (see Table\ \@ref(tab:measures)).
+
 Relationship agency The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
 Therefore, this item was removed.
-As a result, the 8-item scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).
+As a result, the 8-item scale had moderately high reliability for both samples (see Table\ \@ref(tab:measures)).
 

### 2020-11-10 Final_Manuscript.tex
measures table

@@
 
-\subsection{Post interaction Measures}\label{post-interaction-measures}
+\subsection{Measures}\label{measures}
 
@@
 
-The following measures were collected in the order they are presented
-following the interaction. Correlations and descriptive statistics of
-all study variables appear in Table~\ref{tab:corrtable}.
-
-\subsubsection{Cognitive Performance}\label{cognitive-performance}
-
-Trigrams from the Remote Associates Task (McFarlin \& Blascovich, 1984)
-were utilized to assess cognitive performance after the interaction. Ten
-items were selected and presented to participants. For example, the
-correct answer for the trigram \enquote{Quack: Pond: Waddle} would be
-\enquote{Duck}. Participants are limited to 30 seconds to provide their
-answers. For every correct answer, 1 point is given. The mean score was
-5.03 (SD = 2.29). Cognitive performance was measured first directly
-after the interaction in order to measure potential immediate detriments
-to performance (Garcia et al., 2016).
-
-\subsubsection{State
-Other-Objectification}\label{state-other-objectification}
-
-To measure the participant's objectification of their partner in the
-interaction, participants were asked a series of questions about the
-frequency of thoughts during the interaction in relation to multiple
-characteristics of their partner (Garcia et al., 2016). Questions
-included aspects of their partner's internal traits such as personality,
-friends, family, and extracurricular interests, as well as external
-traits such as body, appearance, clothing, and body parts. All questions
-were rated on a scale from 1 (not at all) to 7 (constantly).
-Objectification was measured by taking the difference between the
-average frequency of thought about their partner's external traits
-(\(\alpha\) = 0.79 for Sample 1, \(\alpha\) = 0.79 for Sample 2) and
-frequency of thought about their partner's internal traits (\(\alpha\) =
-0.79 for Sample 1, \(\alpha\) = 0.76 for Sample 2). A positive score in
-this scale would indicate that the participant thought about their
-partner's external traits more than the partner's internal traits, and a
-negative score would indicate the opposite.
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:measures}Measures}
+\begin{tabular}{lllll}
+\toprule
+ & \multicolumn{1}{c}{Original Source} & \multicolumn{1}{c}{Example Item} & \multicolumn{1}{c}{Reliability Sample 1} & \multicolumn{1}{c}{Reliability Sample 2}\\
+\midrule
+Cognitive performance & @mcfarlin1984remote & The correct answer for the trigram "Quack: Pond: Waddle" would be "Duck" & Not avaliable & Not avaliable\\
+Objectification of partner & @garcia2016objectification & "During the interaction, how often did you think about your partner’s personality?" (...friends, family, and extracurricular interests, body, appearance, clothing, and body parts) on a scale from 1 (not at all) to 7 (constantly).
+A difference between the average internal and exxternal traits is taken & external:  0.79 ; internal:  0.71 & external:  0.76 ; internal:  0.79\\
+Authenticity of interaction & @garcia2016objectification & "During the interaction, to what extent did you feel comfortable?" (...happy, friendly, warm, easygoing, sincere, and authentic) on a scale ranging from 1 (not at all) to 7 (very much) & 0.91 & 0.91\\
+State self-objectification & @saguyetal2010 & "During the interaction I felt more like a body than a full self" & 0.84 & 0.85\\
+Relationship agency & @garcia2016objectification & "ask someone out on a date" Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely) & 0.72 & 0.74\\
+Career aspirations & @grayobrien2007 & "I hope to become a leader in my career field" & 0.73 & 0.80\\
+Trait self objectification (TSO) & @nollfredrickson1998 & Participants rank order aspects of their bodies from 1 (least important) to 10 (most important): weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements, strength, physical coordination, energy level, health and physical fitness.
+Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1 so that positive scores indicated greater TSO.
+& appearance:  0.44 ; competence:  0.43 & appearance:  0.51 ; competence:  0.30\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+The same set of measures given in Garcia et al. (2016) were given to
+participants in the current study. For more details about each of these
+measures please see that previous paper. To summarize, the list of
+measures in the order given to participants appears in
+Table~\ref{tab:measures} along side the orginal source for the scale, an
+example item, and the reliability in the current sample. Correlations
+and descriptive statistics of all study variables appear in
+Table~\ref{tab:corrtable}.
+
+Cognitive performance with the Remote Associates Task's trigrams
+(McFarlin \& Blascovich, 1984) was given first, to capture any
+attentional changes that may have been affected by the interaction. Next
+participants were given a set of measure about their thoughts and
+feelings during the interaction that included State-Other
+Objectification, Interaction Authenticity, and State
+Self-Objectification. Following these measures participants completed
+the Relationship Agency Scale and the Career Aspirations Scale. Lastly,
+as was the case in Garcia et al. (2016), Trait Self-Objectification was
+given last, as not to arouse suspicious at the start of the study that
+we were actually focusing on objectification and to give enough time
+that immediate effects of the interaction would have worn off.
 
@@
 
-\subsubsection{Interaction Authenticity}\label{interaction-authenticity}
-
-To assess the magnitude to which individuals felt comfortable in the
-interaction and perceived the interaction to be authentic, we asked
-participants to rate the extent to which they felt comfortable, happy,
-friendly, warm, easygoing, sincere, and authentic on a scale ranging
-from 1 (not at all) to 7 (very much), much like (Garcia et al., 2016).
-Participants were additionally asked to rate their interaction partner's
-authenticity as well as their own: \enquote{Do you think your partner
-was authentic during your interaction?} and \enquote{Were you authentic
-during your interaction?} These questions were ranked on a scale from 1
-(not at all) to 7 (very much). These were combined to form the
-authenticity scale (\(\alpha\) = 0.91 for Sample 1, \(\alpha\) = 0.91
-for Sample 2).
-
-\subsubsection{State
-Self-Objectification}\label{state-self-objectification}
-
-To assess state self-objectification, we used an average of two items
-from Saguy et al. (2010) that were also used in Garcia et al. (2016).
-Participants were asked to rank how much they agreed with the following
-statements: \enquote{During the interaction I felt more like a body than
-a full self} and \enquote{I felt more like a body than as a real person
-in the interaction}. Originally, Saguy et al. (2010) used 3 items, but
-in both samples the reliability of the scale was higher once the third
-item was removed, so we chose to only use the first two for our measure
-of SSO, leaving us with a reliable scale (\(\alpha\) = 0.84 for Sample
-1, and \(\alpha\) = 0.85 for Sample 2.)
-
-\subsubsection{Relationship Agency}\label{relationship-agency}
-
-A scale was used from Garcia et al. (2016) to assess how much agency an
-individual believes they would possess in future romantic relationships.
-Participants were asked how likely it was that they would do the
-following: \enquote{ask someone out on a date,} \enquote{open the door
-for your date,} \enquote{pay for a date,} \enquote{ask your
-boyfriend/girlfriend to marry you,} \enquote{initiate sex with your
-girlfriend/boyfriend,} \enquote{initiate condom use during sex,}
-\enquote{surprise your boyfriend/ girlfriend with a gift,} and
-\enquote{ask your girlfriend/boyfriend to move with you to a new place.}
-Responses were measured on a scale ranging from 1 (not at all likely) to
-7 (extremely likely). The scale originally had 9 items, but the 9th item
+Howbody used 3 items, but in both samples the reliability of the scale
+was higher once the third item was removed, so we chose to only use the
+first two for our measure of SSO, leaving us with a reliable scale (see
+Table~\ref{tab:measures}).
+
+Relationship agency The scale originally had 9 items, but the 9th item
 had low correlations with the remaining items, ranging from .02 to .30
@@
 this item was removed. As a result, the 8-item scale had moderately high
-reliability for both samples (\(\alpha\) = 0.72 for Sample 1,
-(\(\alpha\) = 0.74 for Sample 2).
-
-\subsubsection{Career Aspirations}\label{career-aspirations}
-
-To conceptualize participants' career aspirations after the interaction,
-we used the 10-item adaptation of Gray and OBrien (2007)'s Career
-Aspiration Scale which asked participants to consider how true 10
-statements were in regard to their future careers on a scale from 0 (not
-at all true of me) to 4 (very true of me). Items include \enquote{I hope
-to become a leader in my career field} and \enquote{I hope to move up
-through any organization or business I work in.} Items were fairly
-reliable (\(\alpha\) = 0.73 for Sample 1, \(\alpha\) = 0.80 for Sample
-2).
-
-\subsubsection{Trait
-Self-Objectification}\label{trait-self-objectification}
-
-Trait self-objectification (TSO) was assessed using the
-Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; S.
-Noll \& Fredrickson, 1998), which evaluates the extent to which
-individuals view their bodies in observable versus non-observable ways.
-The questionnaire asked participants to rank order both appearance and
-functional aspects of their bodies, from 1 (least important) to 10 (most
-important), with respect to physical self-concepts. Of the ten body
-attributes, five of the items were appearance-based (weight, sex appeal,
-physical attractiveness, firm/sculpted muscles and body measurements),
-and five of the items were competence-based (strength, physical
-coordination, energy level, health and physical fitness). Difference
-scores were computed by subtracting the sum of the 5 functional
-aspects/competence attributes (e.g., health, strength) from the sum of
-the 5 physical self-concepts/appearance attributes (e.g., physical
-attractiveness, weight), and all measures were multiplied by -1 so that
-positive scores indicated greater TSO.
+reliability for both samples (see Table~\ref{tab:measures}).
 
@@
 has been found to be most prevalent in Western culture (Loughnan et al.,
-2015) research on objectification conducted outside of Western or
-Westernized countries has been scarce (Moradi \& Huang, 2008), although
-more recent work has examined objectification from a cross-cultural
-framework (Loughnan et al., 2015, Wollast et al. (2020)). Since
-\enquote{bodies exist within social and cultural contexts, and hence are
-also constructed through sociocultural practices and discourses}
-(Fredrickson \& Roberts, 1997, p. 174), it is important to consider how
-diverse social identities within unique cultural contexts may inform
-sexual objectification phenomenon to test the cross-cultural
-applicability of theoretical frameworks (Loughnan et al., 2015).
+2015) research on objectification {[}{[}{[}conducted outside of Western
+or Westernized countries{]}{]}{]} has been scarce (Moradi \& Huang,
+2008), although more recent work has examined objectification from a
+cross-cultural framework (Loughnan et al., 2015, Wollast et al. (2020)).
+{[}{[}{[}Since \enquote{bodies exist within social and cultural
+contexts, and hence are also constructed through sociocultural practices
+and discourses}{]}{]}{]} (Fredrickson \& Roberts, 1997, p. 174), it is
+important to consider how diverse social identities within unique
+cultural contexts may inform sexual objectification phenomenon
+{[}{[}{[}to test the cross-cultural applicability of theoretical
+frameworks{]}{]}{]} (Loughnan et al., 2015).
 
@@
 to examine such experiences among children (e.g., Holland \& Haslam,
-2016; Jongenelis, Byrne, \& Pettigrew, 2014). Considering the fact that
-the average mean age of the investigated participants of this current
-study was 18.85 years, research among younger and older individuals is
-needed, especially because the processes of self-objectification may
-change over time (Fredrickson \& Roberts, 1997). It may be valuable to
-question the extent to which children, adolescents, or emerging adults
-of different races or ethnicities are exposed to varied amounts of
-sexualizing content. Further, more longitudinal studies investigating
-the developmental experience of interpersonal objectification and
+2016; Jongenelis, Byrne, \& Pettigrew, 2014). {[}{[}Considering the fact
+that the average mean age of the investigated participants of this
+current study was 18.85 years, research among younger and older
+individuals is needed{]}{]}{]}, especially because the processes of
+self-objectification may change over time (Fredrickson \& Roberts,
+1997). {[}{[}{[}It may be valuable to question the extent to which
+children, adolescents, or emerging adults of different races or
+ethnicities are exposed to varied amounts of sexualizing
+content.{]}{]}{]} Further, more longitudinal studies investigating the
+developmental experience of interpersonal objectification and
 self-objectification are needed.
@@
 than women who are sexually attracted to other women (non-heterosexual
-women). Since both men and women are socialized in a culture that
-sexually objectifies women, both men and women may come to internalize
-this socialization and sexually objectify women. Indeed, recent research
-has found that the more women self-objectify, the more they objectify
-other women (Loughnan et al., 2015; Puvia \& Vaes, 2013), although not
-to the degree exhibited by men; that is, men were found to objectify
-women significantly more than women objectify other women (Strelan \&
+women). {[}{[}{[}Indeed, recent research has found that the more women
+self-objectify, the more they objectify other women{]}{]}{]} (Loughnan
+et al., 2015; Puvia \& Vaes, 2013), {[}{[}{[}although not to the degree
+exhibited by men; that is, men were found to objectify women
+significantly more than women objectify other women{]}{]}{]} (Strelan \&
 Hargreaves, 2005). This differential psychological process between women
@@
 
-Previous research has found that when compared to heterosexual women,
-lesbian women report less concern with physical appearance (Siever,
-1994; Strong, Williamson, Netemeyer, \& Geer, 2000), lower body
-surveillance (Hill \& Fischer, 2008), and lower self-objectification
-(Noffsinger-Frazier, 2004). However none of these studies examined the
-relationship between self-objectification and experiences of sexual
-objectification. Thus, it is unclear whether lesbian women indeed
-experience similar levels of cultural sexual objectification but
-internalize them less than heterosexual women do. Consistent with
-previous research, Hill and Fischer (2008) determined that lesbians
-exhibited less physical appearance concerns compared to heterosexual
-women, however there was no evidence found that lesbian women
-self-objectify less than heterosexual women and they did not find that
-sexual orientation moderates the relationship between sexual
-objectification and self-objectification. This evidence sits in contrast
-to older theoretical literature that suggests that lesbians internalize
-cultural sexual objectification less than do heterosexual women (Brown,
-1987; Pitman, 1999; Rothblum, 1994; Siever, 1994).
+\subsubsection{Sexism and Sexual
+Discrimination}\label{sexism-and-sexual-discrimination}
+
+Sexism has been found to be related to the objectification of women, but
+not men (Cikara, Eberhardt, \& Fiske, 2011; Harsey \& Zurbriggen, 2020),
+and in addition, TSO has been found to be associated with less negative
+attitudes towards sexual harassment (Bernard, Legrand, \& Klein, 2018).
+Both of these effects are present for both men and women. Empirical
+evidence illustrates how women continue to be objects of interpersonal
+discrimination and experience daily sexist hassles (Swim, Hyers, Cohen,
+\& Ferguson, 2001). One form of interpersonal discrimination women face
+is the process by which their whole being is viewed as a collection of
+sexualized body parts valued predominantly for commodification, a
+phenomena termed sexual objectification (Bartky, 1990). Sexual
+objectification of women has also been linked to trauma (Miles-McLean et
+al., 2015). Sexual objectification occurs in a myriad of ways in women's
+lives and is modified by unique combinations of race, ethnicity,
+sexuality, age, and class (Fredrickson \& Roberts, 1997). Amid such
+heterogeneity though, \enquote{having a reproductively mature female
+body} proposed by Fredrickson and Roberts (1997) is likely to create a
+shared vulnerability to sexual objectification and a variety of shared
+negative experiences as a result.
 
@@
 
-The results of this study demonstrate the complex and ambivalent nature
-of sexual objectification and additionally highlight the psychological
-and social consequences of such objectification processes on women's
-social relationships and well-being. These results are quite useful for
-promoting mental health, the creation and maintenance of early action
-programs for girls and young women, and for scholars and practitioners
-to work intentionally to provide the tools necessary to circumvent or
-mitigate negative effects on self-objectification to combat such
-experiences.
+The results of this study \ldots{} and additionally highlight the
+psychological and social consequences of such objectification processes
+on women's social relationships and well-being. These results are quite
+useful for promoting mental health, the creation and maintenance of
+early action programs for girls and young women, and for scholars and
+practitioners to work intentionally to provide the tools necessary to
+circumvent or mitigate negative effects on self-objectification to
+combat such experiences.
 
@@
 
-\hypertarget{ref-brown1987lesbians}{}
-Brown, L. S. (1987). Lesbians, weight, and eating: New analyses and
-perspectives. \emph{Lesbian Psychologies: Explorations and Challenges},
-294--309.
+\hypertarget{ref-bernard2018bodies}{}
+Bernard, P., Legrand, S., \& Klein, O. (2018). From bodies to blame:
+Exposure to sexually objectifying media increases tolerance toward
+sexual harassment. \emph{Psychology of Popular Media Culture},
+\emph{7}(2), 99.
 
@@
 
+\hypertarget{ref-cikara2011agents}{}
+Cikara, M., Eberhardt, J. L., \& Fiske, S. T. (2011). From agents to
+objects: Sexist attitudes and neural responses to sexualized targets.
+\emph{Journal of Cognitive Neuroscience}, \emph{23}(3), 540--551.
+
 \hypertarget{ref-davies2005clearing}{}
@@
 
-\hypertarget{ref-grayobrien2007}{}
-Gray, M. P., \& OBrien, K. M. (2007). Advancing the assessment of
-women's career choices: The career aspiration scale. \emph{Journal of
-Career Assessment - J CAREER ASSESSMENT}, \emph{15}, 317--337.
-doi:\href{https://doi.org/10.1177/1069072707301211}{10.1177/1069072707301211}
-
 \hypertarget{ref-harsey2020men}{}
@@
 
-\hypertarget{ref-noffsinger2004objectification}{}
-Noffsinger-Frazier, N. A. (2004). \emph{Objectification theory and
-disordered eating: The impact of feminist identification,
-internalization of sociocultural standards of appearance, and sexual
-orientation} (PhD thesis). The University of Memphis.
-
-\hypertarget{ref-nollfredrickson1998}{}
-Noll, S., \& Fredrickson, B. (1998). A mediational model linking
-self-objectification, body shame, and disordered eating.
-\emph{Psychology of Women Quarterly}, \emph{22}, 623--636.
-doi:\href{https://doi.org/10.1111/j.1471-6402.1998.tb00181.x}{10.1111/j.1471-6402.1998.tb00181.x}
-
 \hypertarget{ref-olsen2006structural}{}
@@
 \url{https://CRAN.R-project.org/package=nlme}
-
-\hypertarget{ref-pitman1999body}{}
-Pitman, G. E. (1999). Body image, compulsory heterosexuality, and
-internalized homophobia. \emph{Journal of Lesbian Studies}, \emph{3}(4),
-129--139.
 
@@
 
-\hypertarget{ref-rothblum1994lesbians}{}
-Rothblum, E. (1994). Lesbians and physical appearance which model
-applies? \emph{Lesbian and Gay Psychology: Theory, Research, and
-Clinical Applications}, \emph{1}, 84.
-
 \hypertarget{ref-saguyetal2010}{}
@@
 
-\hypertarget{ref-siever1994sexual}{}
-Siever, M. D. (1994). Sexual orientation and gender as factors in
-socioculturally acquired vulnerability to body dissatisfaction and
-eating disorders. \emph{Journal of Consulting and Clinical Psychology},
-\emph{62}(2), 252.
-
 \hypertarget{ref-R-apaTables}{}
@@
 
-\hypertarget{ref-strong2000eating}{}
-Strong, S. M., Williamson, D. A., Netemeyer, R. G., \& Geer, J. H.
-(2000). Eating disorder symptoms and concerns about body differ as a
-function of gender and sexual orientation. \emph{Journal of Social and
-Clinical Psychology}, \emph{19}(2), 240--255.
+\hypertarget{ref-swimetal}{}
+Swim, J. K., Hyers, L. L., Cohen, L. L., \& Ferguson, M. J. (2001).
+Everyday sexism: Evidence for its incidence, nature, and psychological
+impact from three daily diary studies. \emph{Journal of Social Issues},
+\emph{57}(1), 31--53.
+doi:\href{https://doi.org/10.1111/0022-4537.00200}{10.1111/0022-4537.00200}
 

### 2020-11-16 Final_Manuscript.Rmd
measures table
added kable package, read through intro, table 2

@@
 ---
-title             : "Objectification in Action: Self- and Other-Objectification in Same-gender Interactions"
-shorttitle        : "Objectification in Action"
+title             : "Interpersonal Objectification among Women: Evidence for the Relationship between Being Objectified and Self-Objectification in Same-Gender Interactions"
+shorttitle        : "Objectification among Women"
 
@@
   Existing research on interpersonal objectification has focused mostly on links between objectification, self-objectification, and negative outcomes for women within mixed-gender interactions [@gervais2020social; @garcia2016objectification].
-The purpose of the present study was to extend past research on interpersonal objectification to interactions between women.
+The purpose of the present study was to extend @garcia2016objectification's past research on mixed-gender interpersonal objectification to interactions between women.
 Women were brought into the laboratory and interacted face-to-face in same-sex dyads.
@@
 output            : papaja::apa6_pdf
+
+header-include:
+    - \DeclareDelayedFloatFlavor{foo}{table}
 ---
@@
 library(xtable)
+library(kableExtra)
 library(rmarkdown)
@@
 Psychological researchers studying the sexual objectification of women have in recent years explored the interpersonal process of the objectification, finding evidence for *self*-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification; @strelan2018birds; @riemer2020self].
+However, this research has largely focused on mixed-gender interactions only.
 In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO).
-The SIMO focuses on understanding mixed-gender interactions, acknowledging the patriarchal power structure embedded in these mixed interactions, but can it be extended to interactions among women?
+The SIMO focuses on understanding mixed-gender interactions, acknowledging the patriarchal power structure embedded in these mixed interactions, but can this model be extended to interactions among women?
 Although there is evidence that women can objectify other women [@loughnan2015exploring; @puvia2013being; @gervais2013my], studies investigating the process of interpersonal objectification in interactions between women is scarce.
 
-The current study uses a face-to-face interaction methodology to being to answer a series of research questions about interpersonal objectification among women: Is objectification by a female interaction partner related to an increase in self-objectification for the woman being objectified?
+The current study uses the face-to-face interaction methodology deployed in @garcia2016objectification to being to answer a series of research questions about interpersonal objectification among women: Is objectification by a female interaction partner related to an increase in self-objectification for the woman being objectified?
 Does objectification by a woman have the same downstream negative consequences for women as being objectified by a male interaction partner?
@@
 There is some evidence that reduced authenticity is a consequence of self-objectification [@garcia2016objectification; @teran2020relational].
-A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [@teran2020relational].
+A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general [including same-sex friendships; @teran2020relational].
 Authenticity reduction and interaction quality disruptions have also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting; @pearson2008fragility], and we might view the experience of being objectified in an interaction as a potential identity threat situation [@nadal2012effects; @gervais2020social].
@@
 Evidence for other adverse consequences of interpersonal objectification include reductions in career aspirations [@garcia2016objectification] and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
-These are also negative consequences found for women under stereotype threat [@davies2005clearing].
+These are also negative consequences found for women under stereotype threat [@spencer1999stereotype; @davies2005clearing].
 When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature and power differential of this encounter might trigger threat.
@@
 ##The Current Study
-In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification, but between same-gender interpersonal interactions among women.
-Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the relationships for both women simultaneously.
+In the current study, we sought to examine what occurs during an interaction in which one or both partners are potentially objectifying each other and where both interaction partners identify as women.
+Moreover, the current study used the same face-to-face interaction paradigm as @garcia2016objectification and dyadic data analysis techniques to examine the relationships for both women simultaneously.
 Although the literature on intragroup objectification among women is small, the results are mixed, and they do not cover interpersonal encounters, we expected to replicate some of the results found in @garcia2016objectification.
@@
 
-apa_table(corr.table, caption="Correlations and Descriptive Statistics among Study Variables", escape=FALSE)
+apa_table(corr.table, caption="Correlations and Descriptive Statistics among Study Variables", escape=FALSE, note = "* p < .05. ** p < .01.")
 ```
@@
 
-colnames(meas_table)   <- c("Original Source", "Example Item", "Reliability ($\alpha$) Sample 1", "Reliability ($\alpha$) Sample 2")
+colnames(meas_table)   <- c("Original Source", "Example Item", "Reliability Sample 1", "Reliability Sample 2")
 
-apa_table(meas_table, caption="Measures", escape=FALSE)
+# kable(meas_table, "latex", align = "l", booktabs = T, linesep="", caption = "A very long table", longtable=T) %>%
+#   column_spec(1, width = "5em", bold = F, italic = F) %>%
+#   kable_styling(font_size = 7) %>% 
+#   column_spec(2, width = "8em", bold = F, italic = F) %>% 
+#   kable_styling(latex_options = "repeat_header") %>%
+
+apa_table(meas_table, caption="Measures", escape=FALSE, landscape = TRUE, font_size = "small")
+
+write.csv(meas_table, "meas_table.csv")
+
+####REproducible example from github - in here is the answer to floating kable tables.. maybe with "longtable"
+# table1 <- tibble(first=rep(letters,3),
+#                  second = rnorm(78,10,2))
+# 
+# kable(table1, "latex", align = "l", booktabs = T, linesep="", caption = "A very long table", longtable=T) %>% 
+#   column_spec(1, width = "5em", bold = F, italic = F) %>%
+#   kable_styling(font_size = 7) %>% 
+#   column_spec(2, width = "8em", bold = F, italic = F) %>% 
+#   kable_styling(latex_options = "repeat_header")
 ```
@@
 For more details about each of these measures please see that previous paper.
-To summarize, the list of measures in the order given to participants appears in Table\ \@ref(tab:measures) along side the orginal source for the scale, an example item, and the reliability in the current sample.
+To summarize here, the list of measures in the order given to participants appears in Table\ \@ref(tab:measures) along side the orginal source for each scale, an example item, and the reliability in the current sample.
 Correlations and descriptive statistics of all study variables appear in Table\ \@ref(tab:corrtable).
 
-Cognitive performance with the Remote Associates Task's trigrams [@mcfarlin1984remote] was given first, to capture any attentional changes that may have been affected by the interaction.
+Cognitive performance with the Remote Associates Task's trigrams [@mcfarlin1984remote] was given first, to capture any immediate cognitive effects of the interaction.
 Next participants were given a set of measure about their thoughts and feelings during the interaction that included State-Other Objectification, Interaction Authenticity, and State Self-Objectification.
-Following these measures participants completed the Relationship Agency Scale and the Career Aspirations Scale.
+Breaking from the @garcia2016objectification methodlogy, we used a three item state self-objectification scale as originally given in @saguyetal2010, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two items for our measure of SSO.
+Following these interaction measures participants completed the Relationship Agency Scale and the Career Aspirations Scale.
+Relationship agency The scale originally had 9 items, but the 9th item had low correlations with the remaining items so it was trimmed.
+As a result, the 8-item scale had moderately high reliability for both samples (see Table\ \@ref(tab:measures)).
 Lastly, as was the case in @garcia2016objectification, Trait Self-Objectification was given last, as not to arouse suspicious at the start of the study that we were actually focusing on objectification and to give enough time that immediate effects of the interaction would have worn off.
@@
 Further, in the current sample the difference in other-objectification between heterosexual (*M =* `r round(as.numeric(descsplit[2,2]),2)`, *SD =* `r round(as.numeric(descsplit[2,3]),2)`) and non-heterosexual women (*M =* `r round(as.numeric(descsplit[1,2]),2)`, *SD =* `r round(as.numeric(descsplit[1,3]),2)`) was not statistically significant, *t*(`r round(soo_diff$parameter,2)`) = `r round(soo_diff$statistic, 2)`, *p =* `r round(soo_diff$p.value,3)`.
-
-Howbody used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale (see Table\ \@ref(tab:measures)).
-
-Relationship agency The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample.
-Therefore, this item was removed.
-As a result, the 8-item scale had moderately high reliability for both samples (see Table\ \@ref(tab:measures)).
 

### 2020-11-18 Final_Manuscript.Rmd
added confidence intervals, worked on discussion

@@
 
-Cognitive performance with the Remote Associates Task's trigrams [@mcfarlin1984remote] was given first, to capture any immediate cognitive effects of the interaction.
-Next participants were given a set of measure about their thoughts and feelings during the interaction that included State-Other Objectification, Interaction Authenticity, and State Self-Objectification.
+Cognitive performance as measured with the Remote Associates Task's trigrams [@mcfarlin1984remote] was given first after the interaction to capture any immediate cognitive effects of the interaction.
+Next participants were given a set of self-report measures about their thoughts and feelings during the interaction that included State-Other Objectification, Interaction Authenticity, and State Self-Objectification.
 Breaking from the @garcia2016objectification methodlogy, we used a three item state self-objectification scale as originally given in @saguyetal2010, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two items for our measure of SSO.
 Following these interaction measures participants completed the Relationship Agency Scale and the Career Aspirations Scale.
-Relationship agency The scale originally had 9 items, but the 9th item had low correlations with the remaining items so it was trimmed.
+The Relationship agency scale originally had 9 items, but the 9th item had low correlations with the remaining items so it was trimmed.
 As a result, the 8-item scale had moderately high reliability for both samples (see Table\ \@ref(tab:measures)).
@@
 See Figure\ \@ref(fig:apim) for a basic APIM model.
-The APIM includes effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$).
+The APIM estimates effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$).
 The current study deals with indistinguishable dyads, meaning the designation of who is the "actor" and who is the "partner" is arbitrary.
@@
         ifelse(p[est] < .001, ", *p* < ", ", *p* = "),  as.character(pround(p[est])),
+        ", *95%CI* = [",as.character(estround(confint(mod, est)[1])), ", ", as.character(estround(confint(mod, est)[2])), "]",
         sep = "") %>%
@@
 
-First, use used to the APIM to test for evidence of a partner effect of other objectification and SSO in this sample of same-gender woman-woman interacting dyads.
+First, we used the APIM to test for evidence of a partner effect of other objectification and SSO in this sample of same-gender woman-woman interacting dyads.
 In @garcia2016objectification, men's objectification of women was significantly related to women's SSO, the current study sought to replicate this partner effect.
@@
 ###Sample Characteristics
-In addition to being relatively small and combined across two institutions, another limitation of the current study sample is that the it was comprised of Western women only.
-Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring] research on objectification [[[conducted outside of Western or Westernized countries]]] has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
-[[[Since “bodies exist within social and cultural contexts, and hence are also constructed through sociocultural practices and discourses”]]] [@robertsfredrickson, p.174], it is important to consider how diverse social identities within unique cultural contexts may inform sexual objectification phenomenon [[[to test the cross-cultural applicability of theoretical frameworks]]] [@loughnan2015exploring].
-
-Further, sexualizing experiences and self-objectification are thought to begin a very young age, and thus, researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014].
-[[Considering the fact that the average mean age of the investigated participants of this current study was `r mean_age` years, research among younger and older individuals is needed]]], especially because the processes of self-objectification may change over time [@robertsfredrickson].
-[[[It may be valuable to question the extent to which children, adolescents, or emerging adults of different races or ethnicities are exposed to varied amounts of sexualizing content.]]] Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are needed.
+In addition to being relatively small and combined across two institutions, another limitation of the current study sample is that the it was comprised of mostly women from Western cultures.
+Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring] research on objectification that includes people from non-Western cultures has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
+Further, sexualizing experiences and self-objectification are thought to begin a very young age, but researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014].
+The mean age of the current sample was `r mean_age` years, an emerging adult sample.
+@vangeel2018multidimensional found that self-objectification among emerging adults....
+Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are needed, especially because the processes of self-objectification may change over time [@vangeel2018multidimensional; @robertsfredrickson].
 

### 2020-11-23 Final_Manuscript.Rmd
some edits

@@
 abstract: |
-  Existing research on interpersonal objectification has focused mostly on links between objectification, self-objectification, and negative outcomes for women within mixed-gender interactions [@gervais2020social; @garcia2016objectification].
+ Existing research on interpersonal objectification has focused mostly on links between sexual objectification, self-objectification, and negative outcomes for women within mixed-gender interactions [@gervais2020social; @garcia2016objectification].
 The purpose of the present study was to extend @garcia2016objectification's past research on mixed-gender interpersonal objectification to interactions between women.
@@
 Dyadic analysis [@kenny2006dyadic] was utilized to detect whether partners’ objectification of each other affected state self-objectification, as well as the resulting feelings of comfort and authenticity during the interaction.
-Results revealed a significant positive relationship between being objectified by a woman interaction partner and women’s own self-objectification (a partner effect).
+Results revealed a significant positive relationship between being objectified by a woman interaction partner and a woman’s own self-objectification (a partner effect).
 There was no significant relationship between self-objectification and interaction inauthenticity, but there were significant negative effects of inauthenticity on career aspirations and relationship agency (actor effects).
@@
 @robertsfredrickson's Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
-The negative effects of this interpersonal objectification for women have been theorized to be the strongest under the "male gaze," that is, when it is a perceived or actual man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction?
+The negative effects of this interpersonal objectification for women have been theorized to be the strongest under the "male gaze," that is, when it is a perceived or actual man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my].
+What are the consequences when a woman objectifies another woman in an interaction?
 Psychological researchers studying the sexual objectification of women have in recent years explored the interpersonal process of the objectification, finding evidence for *self*-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification; @strelan2018birds; @riemer2020self].
@@
 
-The current study uses the face-to-face interaction methodology deployed in @garcia2016objectification to being to answer a series of research questions about interpersonal objectification among women: Is objectification by a female interaction partner related to an increase in self-objectification for the woman being objectified?
+The current study uses the face-to-face interaction methodology deployed in @garcia2016objectification to begin to answer a series of research questions about interpersonal objectification among women: Is objectification by a female interaction partner related to an increase in self-objectification for the woman being objectified?
 Does objectification by a woman have the same downstream negative consequences for women as being objectified by a male interaction partner?
@@
 @calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO), whereby one adopts a habitual third-person perspective on one's own appearance.
-Furthermore, self-objectification can also be elicited momentarily, for example, when viewing sexualized images in movies and magazines [@morry2001magazine], when trying on sexualizing clothing [@fredrickson1998swimsuit], or during video chat when you believe your interaction partner can only see your body [not face; @saguyetal2010].
+Furthermore, self-objectification can also be elicited momentarily, for example, when viewing sexualized images in movies and magazines [@morry2001magazine], when trying on sexualizing clothing [@fredrickson1998swimsuit], or during video chat when you believe your interaction partner can only see your body and not your face [@saguyetal2010].
 This momentary self-objectification is referred to as *state* self-objectification [SSO; @calogero2011; @moradi2008] and is characterized by feeling like a body rather than a full self within a particular moment, instance, or context.
@@
 Along the same lines, @strelan2005women found that the more women self-objectify, the more they objectify other women.
-Could the process work in the other direction as well, that is, could objectification by a woman produce (state) self-objectification, in a similar manner to objectification by a man?
+Could the process work in the other direction as well?
+That is, could objectification by a woman produce (state) self-objectification, in a similar manner to objectification by a man?
 @hill2008examining assessed women’s experiences of objectification from men independently from women’s experiences of objectification from other women.
@@
 Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the effects of this objectification might be.
-Past studies have found that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, we do not know much about the effect of the gender of the *objectifyer* on these potential detrimental outcomes.
+Past studies have found that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, we do not know much about the effect of the gender of the *objectifier* on these potential detrimental outcomes.
 
@@
 @gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the SIMO.
-What is clear from @gervais2020social's review is that we know little about women-on-women interpersonal objectification.
+What is clear from @gervais2020social's review is that we know little about women-on-women interpersonal objectification, in unstructured contexts.
 
-Past research has found that the experience of state self-objectification in mixed-gender contexts (stranger and romantic; @strelan2018birds; @meltzer2020women; @zurbriggen2011self) has negative consequences for women, but what about in the context of interactions with other women?
+Past research has found that the experience of state self-objectification in mixed-gender contexts [stranger and romantic; @strelan2018birds; @meltzer2020women; @zurbriggen2011self] has negative consequences for women, but what about in the context of interactions with other women?
 Is the self-objectification experienced in mixed-gender interactions associated with the same negative process as that experienced in same-gender interactions?
-The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010; @calogero2004test; @gervais2011you; @gay2010my], but, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and recent experimental evidence suggests that the female gaze causes no less self-objectification than the male gaze [@yilmaz2019whose].
+The ample research demonstrating that the male gaze has a particularly detrimental effect for women would suggest no [@saguyetal2010; @calogero2004test; @gervais2011you; @gay2010my].
+However, there is evidence that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men] and recent experimental evidence suggests that the female gaze causes no less self-objectification than the male gaze [@yilmaz2019whose].
 It would be helpful to understand the consequences of this *intra*group objectification for women.
 When women objectify other women, does it lead to self-objectification in the same way men's objectification of women does [@garcia2016objectification]?
+
 If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that interaction?
 
+One mechanism by which interpersonal objectification translates into negative consequences is interaction inauthenticity - when actors feel that they are not being their true selves in an interaction.
 There is some evidence that reduced authenticity is a consequence of self-objectification [@garcia2016objectification; @teran2020relational].
-A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general [including same-sex friendships; @teran2020relational].
+A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general, including same-sex friendships [@teran2020relational].
 Authenticity reduction and interaction quality disruptions have also been found in research on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting; @pearson2008fragility], and we might view the experience of being objectified in an interaction as a potential identity threat situation [@nadal2012effects; @gervais2020social].
-Further, empirical evidence reveals that healthy relationship functioning manifests through authenticity in romantic relationships [@brunelletal2010], an intergroup context at least in heterosexual relationships.
+Further, empirical evidence reveals that healthy relationship functioning manifests through authenticity in romantic relationships [@brunelletal2010], at least in an intergroup context such as heterosexual romantic relationships.
 Evidence for other adverse consequences of interpersonal objectification include reductions in career aspirations [@garcia2016objectification] and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal].
@@
 When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature and power differential of this encounter might trigger threat.
-Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman.
-That is, the intergroup threat literature might predict that woman-woman interpersonal objectification processes diverge from mixed-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity).
+Thus, me might expect there to fewer negative consequences when a woman is objectified by another woman.
+That is, the intergroup threat literature might predict that woman-woman interpersonal objectification processes diverge from mixed-gender interpersonal objectification processes precisely because they are not intergroup interactions, at least with respect to gender identity.
 
-In summary, a woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting]; however, feeling like a body rather than a full human (higher SSO) in any interaction, whether intergroup or intragroup, may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; @teran2020relational].
+In summary, a woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting]; however, feeling like a body rather than a full human (higher SSO) in any interaction, whether intergroup or intragroup, may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifier [@tolman2006looking; @teran2020relational].
 
@@
 Moreover, the current study used the same face-to-face interaction paradigm as @garcia2016objectification and dyadic data analysis techniques to examine the relationships for both women simultaneously.
-Although the literature on intragroup objectification among women is small, the results are mixed, and they do not cover interpersonal encounters, we expected to replicate some of the results found in @garcia2016objectification.
+Although the literature on intragroup objectification among women is small, the results are mixed, and they do not cover actual interpersonal encounters, we expected to replicate some of the results found in @garcia2016objectification.
 Most importantly, we predicted that being objectified by one’s interaction partner would be related to state self-objectification (SSO).
@@
 Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because, in Western culture and beyond, women need to look attractive to obtain and maintain successful relationships, thus, the "College Relationships" condition may heighten self-objectification and the evaluation of other women in a sexualized way.
-The decision was made to ask even heterosexual women to judge their fellow-woman partners for their potential as romantic partners.
-We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and strengthen the potential for objectification that would normally be low in the context of a psychology laboratory.
-Recall that, past research has found that heterosexual women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; @puvia2013being]---women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.
+The decision was made to ask all women participating in the study, even heterosexual women, to judge their fellow-woman partners for their potential as romantic partners.
+We felt that this prompt would keep the study closest to a replication (and extension) of the previous @garcia2016objectification version of the study, and strengthen the potential for objectification that would normally be low in the context of a psychology laboratory.
+Recall that, past research has found that heterosexual women are indeed able to evaluate other women's potential as romantic partners, specifically, their sexual attractiveness [@puvia2013being].
+Women may be unfortunately quite used to thinking about their own "datability," and we suspected that this habitual thought pattern would translate to their thoughts about other women.
 Analyses comparing levels of other-objectification between heterosexual and non-heterosexual women are provided in the measures section below.
@@
 The same set of measures given in @garcia2016objectification were given to participants in the current study.
-For more details about each of these measures please see that previous paper.
-To summarize here, the list of measures in the order given to participants appears in Table\ \@ref(tab:measures) along side the orginal source for each scale, an example item, and the reliability in the current sample.
+For more details about each of these measures please refer to that previous paper.
+To summarize here, the list of measures in the order given to participants appears in Table\ \@ref(tab:measures) along side the original source for each scale, an example item, and the reliability in the current sample.
 Correlations and descriptive statistics of all study variables appear in Table\ \@ref(tab:corrtable).
@@
 Next participants were given a set of self-report measures about their thoughts and feelings during the interaction that included State-Other Objectification, Interaction Authenticity, and State Self-Objectification.
-Breaking from the @garcia2016objectification methodlogy, we used a three item state self-objectification scale as originally given in @saguyetal2010, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two items for our measure of SSO.
-Following these interaction measures participants completed the Relationship Agency Scale and the Career Aspirations Scale.
+Breaking from the @garcia2016objectification methodology, we used a three item state self-objectification scale as originally given in @saguyetal2010, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two items for our measure of SSO.
+Following these interaction measures, participants completed the Relationship Agency Scale and the Career Aspirations Scale.
 The Relationship agency scale originally had 9 items, but the 9th item had low correlations with the remaining items so it was trimmed.
@@
 See Figure\ \@ref(fig:apim) for a basic APIM model.
-The APIM estimates effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$).
+The APIM estimates effects due to one's own, as well as one's partner's, predictor variables on the one's own outcome variable.
 The current study deals with indistinguishable dyads, meaning the designation of who is the "actor" and who is the "partner" is arbitrary.
@@
 That is, the extent to which one's partner reported thinking about a woman's external characteristics more than her internal characteristics was significantly related to the woman's own reported feeling more like a body than a full self.
-Along side the @garcia2016objectification study, there is now evidence that interpersonal objectification in an actual interpersonal encounter is related to state self-objectification for women both when the objectifyer is a man and when the objectifyer is a woman.
+Along side the @garcia2016objectification study, there is now evidence that interpersonal objectification in an actual interpersonal encounter is related to state self-objectification for women both when the objectifier is a man and when the objectifier is a woman.
 
@@
 The linear model used by the current study implies that being objectified by a woman leads women to self-objectify, but it could be that women's SSO causes them to be objectified by their interaction partner.
-This latter interpretation is possible given the empirical evidence that it is *women's* state self-objectification that relates to being objectified by one's partner---men partners [@garcia2016objectification] and now women partners.
+This latter interpretation is possible given the empirical evidence that it is *women's* state self-objectification that relates to being objectified by one's partner---men-identifying partners [@garcia2016objectification] and now women-identifying partners.
 Objectification Theory [@robertsfredrickson], as well as some past experimental studies [for example, @saguyetal2010], suggest that the causal flow is from other-objectification to SSO.
-Other studies, especially those investigating explicitly women objectifying other women [@puvia2013being], have relatedly found evidence that women's *trait* self-objectification is related to women objectifying (dehumanizing) other women and this link is mediated by *state* self-objectification.
-The process of interpersonal objectification among women could also contain a feedback loop.
-That is, perhaps we tend to objectify other women who objectify us and through a process of TSO causing SSO which in turn causes objectification of one's partner, which in turn causes one's partner to objectify us.
-However, the current study does not provide any evidence of the TSO to other-objectification link---TSO was not significantly correlated with SSO and, further, actor's other-objectification was not correlated with partner's other-objectification.
+Other studies, especially those investigating women objectifying other women [@puvia2013being], have found evidence that women's *trait* self-objectification is related to women objectifying (dehumanizing) other women and this link is mediated by *state* self-objectification.
+The process of interpersonal objectification among women could also very well contain a feedback loop.
+That is, perhaps we tend to objectify other women who objectify us.
+Then, if there tended to be reciprocity in sexual objectification among women, through a process of TSO causing SSO which in turn causes other-objectification of one's partner, which in turn causes one's partner to objectify us, and finally, being objectified further increases our own SSO.
+However, the current study does not provide any evidence of the TSO to other-objectification link (through SSO or directly)---TSO was not significantly correlated with SSO.
+Further, actor's other-objectification was not correlated with partner's other-objectification in the current sample.
 
-Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity.
+Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity (and, in turn, cognitive functioning).
 This is somewhat surprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the research on interpersonal other-objectification and cognitive functioning [@logel2009interacting; @garcia2016objectification; @gervais2011you].
 This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you], and perhaps the self-objectification experienced within an interaction with a women is qualitatively different, and perhaps not as harmful, as the state self-objectification experienced within an interaction with a man.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you], and perhaps the self-objectification experienced within an interaction with a women is qualitatively different, as the state self-objectification experienced within an interaction with a man.
 However, as a strong note of caution, it is best not to interpret a null result as evidence of no relationship and more research on interpersonal objectification among women is needed.
@@
 It should be noted that the estimate of this relationship was small (close to zero), but in the negative direction.
-If it is the case that there is a smaller (i.e., weaker) or zero connection between women's feelings of SSO and inauthenticity in interactions with other women than in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including gender of the objectifyer/interaction partner as a moderator.
+If it is the case that there is a smaller (i.e., weaker) or zero connection between women's feelings of SSO and inauthenticity in interactions with other women than in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including gender of the objectifier/interaction partner as a moderator.
 Inauthenticity could be added as a potential moderated mediating factor to help understand the circumstances that require other-objectification and SSO to have negative consequences for women.
-Perhaps one important difference is the lack of a power differential across gendered lines -- the patriarchal culture is present, but the interaction partners are not a stigmatizer-stigmatized pair.
+Perhaps one important difference is the lack of a power differential across gendered lines---the patriarchal culture is present, but the interaction partners are not a stigmatizer-stigmatized pair.
+This work on intragroup sexual objectification among women could also have connections to the small but growing literature investigating same-race racial minority interactions [@taylor2018threat; @garcia2017racial].
 
@@
 In addition to being relatively small and combined across two institutions, another limitation of the current study sample is that the it was comprised of mostly women from Western cultures.
-Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring] research on objectification that includes people from non-Western cultures has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
+Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring], research on objectification that includes people from non-Western cultures has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
 Further, sexualizing experiences and self-objectification are thought to begin a very young age, but researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014].
-The mean age of the current sample was `r mean_age` years, an emerging adult sample.
-@vangeel2018multidimensional found that self-objectification among emerging adults....
-Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are needed, especially because the processes of self-objectification may change over time [@vangeel2018multidimensional; @robertsfredrickson].
+The mean age of the current sample was `r mean_age` years, a young adult sample.
+Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are needed, especially because the processes of self-objectification have been found to unfold between the periods of adolescence and young adulthood [@vangeel2018multidimensional].
 
@@
 The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating/romantic partner.
-We think that heterosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---perhaps they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
-[[[Indeed, recent research has found that the more women self-objectify, the more they objectify other women]]] [@loughnan2015exploring; @puvia2013being], [[[although not to the degree exhibited by men; that is, men were found to objectify women significantly more than women objectify other women]]] [@strelan2005women].
-This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships.
+We think that the heterosexual women in our sample were able to do this with other women as their target---indeed, there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---but, perhaps they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
+These differential psychological process between heterosexual and lesbian women might have served to dampen our ability to detect the proposed relationships between study variables.
 

### 2020-11-24 Final_Manuscript.Rmd
edits

@@
 The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a sample of women engaging in actual dyadic interactions with each other.
-Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women during actual interactions is related to state self-objectification in their woman-identified interaction partners.
+Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if interpersonal other-objectification by women during *actual* interactions is related to state self-objectification in their woman-identified interaction partners.
 As hypothesized, the current study did find a significant relationship between a woman's interaction partner's report of having objectified her and her own post-interaction feelings of self-objectification.
@@
 Objectification Theory [@robertsfredrickson], as well as some past experimental studies [for example, @saguyetal2010], suggest that the causal flow is from other-objectification to SSO.
-Other studies, especially those investigating women objectifying other women [@puvia2013being], have found evidence that women's *trait* self-objectification is related to women objectifying (dehumanizing) other women and this link is mediated by *state* self-objectification.
+However, some studies investigating women objectifying other women [@puvia2013being], have found evidence that women's *trait* self-objectification is related to women objectifying (dehumanizing) other women and this link is mediated by *state* self-objectification.
 The process of interpersonal objectification among women could also very well contain a feedback loop.
-That is, perhaps we tend to objectify other women who objectify us.
-Then, if there tended to be reciprocity in sexual objectification among women, through a process of TSO causing SSO which in turn causes other-objectification of one's partner, which in turn causes one's partner to objectify us, and finally, being objectified further increases our own SSO.
+That is, perhaps we tend to objectify other women who are objectifying us.
+Then, if there indeed tends to be reciprocity in sexual objectification among women, a vicious cycle could ensue through a process of TSO causing SSO which in turn causes other-objectification of one's partner, which in turn causes one's partner to objectify us, and finally, being objectified further increases our own SSO.
 However, the current study does not provide any evidence of the TSO to other-objectification link (through SSO or directly)---TSO was not significantly correlated with SSO.
 Further, actor's other-objectification was not correlated with partner's other-objectification in the current sample.
+Future experimental work testing if sexual objectification by a woman can cause an increase in a woman's state self-objectification would be helpful.
 
@@
 This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women.
-There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you], and perhaps the self-objectification experienced within an interaction with a women is qualitatively different, as the state self-objectification experienced within an interaction with a man.
-However, as a strong note of caution, it is best not to interpret a null result as evidence of no relationship and more research on interpersonal objectification among women is needed.
+There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you] for women, and perhaps the self-objectification experienced within an interaction with a women is qualitatively different from the state self-objectification experienced within an interaction with a man.
+However, as a strong note of caution, we cannot interpret a null result as evidence of no relationship and more research on interpersonal objectification among women is needed.
 
 The lack of evidence for a relationship between SSO and interaction authenticity is surprising and again, should not be interpreted as evidence of no relationship.
-It should be noted that the estimate of this relationship was small (close to zero), but in the negative direction.
-If it is the case that there is a smaller (i.e., weaker) or zero connection between women's feelings of SSO and inauthenticity in interactions with other women than in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including gender of the objectifier/interaction partner as a moderator.
+The estimate of this relationship was small (close to zero), but in the negative direction.
+If perhaps it is the case that there is a smaller (i.e., weaker) or zero connection between women's feelings of SSO and inauthenticity in interactions with other women than in interactions with men, models of interpersonal objectification, like the SIMO [@gervais2020social], could be extended by including gender of the objectifier/interaction partner as a moderator.
 Inauthenticity could be added as a potential moderated mediating factor to help understand the circumstances that require other-objectification and SSO to have negative consequences for women.
-Perhaps one important difference is the lack of a power differential across gendered lines---the patriarchal culture is present, but the interaction partners are not a stigmatizer-stigmatized pair.
-This work on intragroup sexual objectification among women could also have connections to the small but growing literature investigating same-race racial minority interactions [@taylor2018threat; @garcia2017racial].
+Perhaps one important difference is the lack of a power differential across gendered lines---the patriarchal culture is present, but the interaction partners are not a stigmatizer-stigmatized pair in interpersonal objectification encounters among women.
+Lastly, This theoretical work on intragroup sexual objectification among women could potentially benefit from making connections to the small but growing literature investigating same-race racial minority interactions [@taylor2018threat; @garcia2017racial].
 
 Although the current study did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency, and authenticity and career aspirations.
-The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically significant.
+The relationship between authenticity and cognitive functioning was estimated as positive (the point estimate), but was not statistically significant.
 Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables.
 This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; @teran2020relational] and is related to mental health correlates [@tolman2006looking].
-Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification], we find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current partner.
-Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and future work must explore when and how SSO leads to inauthenticity in interpersonal objectification situations.
+Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification], we find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current interaction partner.
+Although the current study did not find a connection between authenticity and SSO, this seems to us to remain a theoretically viable connection, and future work must explore when and how SSO leads to inauthenticity in interpersonal objectification situations.
 
@@
 ###Sample Characteristics
+Although the sample size was relatively small, due to the difficulty in collecting data on actual interpersonal encounters, we believe that the results from the current analyses are important and push work in interpersonal objectification forward in an important way.
+Of course, more data is better, especially for evaluating null results.
+Follow-up studies investigating interpersonal objectification among women are necessary and should strive for larger samples.
 In addition to being relatively small and combined across two institutions, another limitation of the current study sample is that the it was comprised of mostly women from Western cultures.
 Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring], research on objectification that includes people from non-Western cultures has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
+
 Further, sexualizing experiences and self-objectification are thought to begin a very young age, but researchers have only recently begun to examine such experiences among children [e.g., @holland2016; @jongenelis2014].
-The mean age of the current sample was `r mean_age` years, a young adult sample.
-Further, more longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are needed, especially because the processes of self-objectification have been found to unfold between the periods of adolescence and young adulthood [@vangeel2018multidimensional].
+The mean age of the current sample was `r mean_age` years, a young adult sample, limiting the generalizability of our results to this age group.
+More longitudinal studies investigating the developmental experience of interpersonal objectification and self-objectification are recommended, especially because the processes of self-objectification have been found to unfold between the periods of adolescence and young adulthood [@vangeel2018multidimensional].
 
-###Interpersonal Sexual Objectification, Gender, and Sexual Attraction
-The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating/romantic partner.
+The current sample contained a mixture of both heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating/romantic partner.
 We think that the heterosexual women in our sample were able to do this with other women as their target---indeed, there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---but, perhaps they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
-These differential psychological process between heterosexual and lesbian women might have served to dampen our ability to detect the proposed relationships between study variables.
+Social comparison processes have been linked to self-objectification and negative body image among women in general [@tylka2010integrating, @lindner2012social] and, more recently, specifically with regard to consumption of social media site content [@hanna2017contributions, @fox2016selective, @feltman2018instagram].
+However, these none of these studies compared heterosexual women to non-heterosexual women.
+If it is the case that there are two differential psychological processes between heterosexual and lesbian women at play, this added variance might have served to dampen our ability to detect the proposed relationships between study variables.
 
@@
 
-<!-- Interpersonal sexual objectification has been studied in both romantic and platonic contexts.
+An additional issue with including both heterosexual and lesbian women in the sample is that the interpersonal encounter in the current study was experience as a potentially romantic context for some and as a strictly platonic context for others.
+Interpersonal sexual objectification has been studied in both romantic and platonic contexts.
 Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self].
-Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship.
-There is also evidence that they experience less SSO after appearance comments within established romantic relationships [@meltzer2020women], but less is known about first dates.
-An important caveat to this literature is that it is only about heterosexual relationships.
-Objectification might also occur among platonic friends: Perhaps women could be amplifying each others' state self-objectification *before* the theoretical encounters with men organized in the SIMO occur.
-In this way, women's rituals of getting ready together before socializing in co-ed groups might place even women with low TSO in a higher SSO group.
--->
+Evidence is the romantic context is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship.
+There is also evidence that they experience less SSO after appearance comments within established romantic relationships [@meltzer2020women].
+Less is known about first dates and there is little research on objectification processes in lesbian relationships specifically.
+Further, objectification might also occur among platonic friends: Perhaps women could be amplifying each others' state self-objectification *before* the theoretical encounters with men organized in the SIMO occur.
 
-###Sexism and Sexual Discrimination
-Sexism has been found to be related to the objectification of women, but not men [@cikara2011agents; @harsey2020men], and in addition, TSO has been found to be associated with less negative attitudes towards sexual harassment [@bernard2018bodies].
+<!-- ###Sexism and Sexual Discrimination -->
+<!-- Sexism has been found to be related to the objectification of women, but not men [@cikara2011agents; @harsey2020men], and in addition, TSO has been found to be associated with less negative attitudes towards sexual harassment [@bernard2018bodies].
 Both of these effects are present for both men and women.
@@
 Amid such heterogeneity though, “having a reproductively mature female body” proposed by @robertsfredrickson is likely to create a shared vulnerability to sexual objectification and a variety of shared negative experiences as a result.
+-->
 
 #Conclusion
-The results of this study ...
-and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being.
-These results are quite useful for promoting mental health, the creation and maintenance of early action programs for girls and young women, and for scholars and practitioners to work intentionally to provide the tools necessary to circumvent or mitigate negative effects on self-objectification to combat such experiences.
+To the best of our knowledge, this was the first study to test the relationship between objectification and self-objectification within actual interpersonal interactions among women.
+The results of this study replicated the partner effect of other-objectification on state self-objectification found in @garcia2016objectification in a sample of same-gender pairs all identifying as women.
+That is, the more a woman's female interaction partner reported having objectified her, the more she reported a state of self-objectification during the interaction.
+Unlike past research finding that trait self-objectification moderated this relationship, we did not find any evidence of such an effect.
+Further, we did not find that inauthenticity was an important mediating factor between self-objectification and the negative psychological and social consequences of such objectification for women’s, as was the case in past studies on interpersonal objectification of women by men.
+Further research should be conducted with larger samples that investigate interpersonal objecticiation among women and compare these processes to parallel processes among mixed-gender dyads.
 

### 2020-11-30 Final_Manuscript.Rmd
final edits

@@
 authornote: |
-  Randi L. Garcia is in the Psychology Department and the Statitsical and Data Sciences program at Smith College.
+  Randi L. Garcia is in the Psychology Department and the Program in Statistical and Data Sciences at Smith College.
 
@@
 ```
-@robertsfredrickson's Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
+@robertsfredrickson's Objectification Theory suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters.
 The negative effects of this interpersonal objectification for women have been theorized to be the strongest under the "male gaze," that is, when it is a perceived or actual man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my].
@@
 In addition to being relatively small and combined across two institutions, another limitation of the current study sample is that the it was comprised of mostly women from Western cultures.
-Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring], research on objectification that includes people from non-Western cultures has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring, @wollast2020cultural].
+Being that self-objectification has been found to be most prevalent in Western culture [@loughnan2015exploring], research on objectification that includes people from non-Western cultures has been scarce [@moradi2008], although more recent work has examined objectification from a cross-cultural framework [@loughnan2015exploring; @wollast2020cultural].
 
@@
 We think that the heterosexual women in our sample were able to do this with other women as their target---indeed, there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---but, perhaps they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women).
-Social comparison processes have been linked to self-objectification and negative body image among women in general [@tylka2010integrating, @lindner2012social] and, more recently, specifically with regard to consumption of social media site content [@hanna2017contributions, @fox2016selective, @feltman2018instagram].
-However, these none of these studies compared heterosexual women to non-heterosexual women.
+Social comparison processes have been linked to self-objectification and negative body image among women in general [@tylka2010integrating; @lindner2012social] and, more recently, specifically with regard to consumption of social media site content [@hanna2017contributions; @fox2016selective; @feltman2018instagram].
+However, these none of these social comparison studies compared heterosexual women to non-heterosexual women.
 If it is the case that there are two differential psychological processes between heterosexual and lesbian women at play, this added variance might have served to dampen our ability to detect the proposed relationships between study variables.
@@
 Less is known about first dates and there is little research on objectification processes in lesbian relationships specifically.
-Further, objectification might also occur among platonic friends: Perhaps women could be amplifying each others' state self-objectification *before* the theoretical encounters with men organized in the SIMO occur.
+Further, objectification might also occur among platonic friends: Perhaps women could be amplifying each others' state self-objectification *before* the theoretical encounters with men, and the processes organized in the SIMO, occur.
 
@@
 Unlike past research finding that trait self-objectification moderated this relationship, we did not find any evidence of such an effect.
-Further, we did not find that inauthenticity was an important mediating factor between self-objectification and the negative psychological and social consequences of such objectification for women’s, as was the case in past studies on interpersonal objectification of women by men.
+Further, we did not find that inauthenticity was an important mediating factor between self-objectification and the negative psychological and social consequences for women objectified by women, as was the case in past studies on interpersonal objectification of women by men.
 Further research should be conducted with larger samples that investigate interpersonal objecticiation among women and compare these processes to parallel processes among mixed-gender dyads.

### 2020-11-30 Final_Manuscript.tex
final edits

@@
 \hypersetup{unicode=true,
-            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
+            pdftitle={Interpersonal Objectification among Women: Evidence for the Relationship between Being Objectified and Self-Objectification in Same-Gender Interactions},
             pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
@@
 
-  \title{Objectification in Action: Self- and Other-Objectification in
-Same-gender Interactions}
+  \title{Interpersonal Objectification among Women: Evidence for the Relationship
+between Being Objectified and Self-Objectification in Same-Gender
+Interactions}
     \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
@@
 
-\shorttitle{Objectification in Action}
+\shorttitle{Objectification among Women}
 \affiliation{
@@
 \authornote{Randi L. Garcia is in the Psychology Department
-and the Statitsical and Data Sciences program at Smith College.
+and the Program in Statistical and Data Sciences at Smith College.
 
@@
 Existing research on interpersonal objectification has focused mostly on
-links between objectification, self-objectification, and negative
+links between sexual objectification, self-objectification, and negative
 outcomes for women within mixed-gender interactions (Garcia, Earnshaw,
 \& Quinn, 2016; Gervais, Sáez, Riemer, \& Klein, 2020). The purpose of
-the present study was to extend past research on interpersonal
-objectification to interactions between women. Women were brought into
-the laboratory and interacted face-to-face in same-sex dyads. Dyadic
-analysis (Kenny, Kashy, \& Cook, 2006) was utilized to detect whether
-partners' objectification of each other affected state
-self-objectification, as well as the resulting feelings of comfort and
-authenticity during the interaction. Results revealed a significant
-positive relationship between being objectified by a woman interaction
-partner and women's own self-objectification (a partner effect). There
-was no significant relationship between self-objectification and
-interaction inauthenticity, but there were significant negative effects
-of inauthenticity on career aspirations and relationship agency (actor
-effects). The significant partner effect of objectification on
-self-objectification suggests that women being objectified by other
-women may result in feelings of self-objectification, and this finding
-opens up questions for future research about how interpersonal
-objectification might function in situations without an immediate male
-gaze.
+the present study was to extend Garcia et al. (2016)`s past research on
+mixed-gender interpersonal objectification to interactions between
+women. Women were brought into the laboratory and interacted
+face-to-face in same-sex dyads. Dyadic analysis (Kenny, Kashy, \& Cook,
+2006) was utilized to detect whether partners' objectification of each
+other affected state self-objectification, as well as the resulting
+feelings of comfort and authenticity during the interaction. Results
+revealed a significant positive relationship between being objectified
+by a woman interaction partner and a woman's own self-objectification (a
+partner effect). There was no significant relationship between
+self-objectification and interaction inauthenticity, but there were
+significant negative effects of inauthenticity on career aspirations and
+relationship agency (actor effects). The significant partner effect of
+objectification on self-objectification suggests that women being
+objectified by other women may result in feelings of
+self-objectification, and this finding opens up questions for future
+research about how interpersonal objectification might function in
+situations without an immediate male gaze.
 
@@
 
-Fredrickson and Roberts (1997)'s Objectification Theory, suggests that,
+Fredrickson and Roberts (1997)'s Objectification Theory suggests that,
 in addition to being steeped in a culture that objectifies women, women
@@
 perceived or actual man doing the objectifying (Calogero, 2004; Gay \&
-Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
+Castano, 2010; Gervais, Vescio, \& Allen, 2011). What are the
 consequences when a woman objectifies another woman in an interaction?
@@
 2016; Riemer, Sáez, Brock, \& Gervais, 2020; Strelan \& Pagoudis, 2018).
-In a recent review, Gervais et al. (2020) organized the extant
+However, this research has largely focused on mixed-gender interactions
+only. In a recent review, Gervais et al. (2020) organized the extant
 literature on interpersonal self-objectification and proposed a
@@
 acknowledging the patriarchal power structure embedded in these mixed
-interactions, but can it be extended to interactions among women?
-Although there is evidence that women can objectify other women
+interactions, but can this model be extended to interactions among
+women? Although there is evidence that women can objectify other women
 (Gervais, Holland, \& Dodd, 2013; Loughnan et al., 2015; Puvia \& Vaes,
@@
 
-The current study uses a face-to-face interaction methodology to being
-to answer a series of research questions about interpersonal
-objectification among women: Is objectification by a female interaction
-partner related to an increase in self-objectification for the woman
-being objectified? Does objectification by a woman have the same
-downstream negative consequences for women as being objectified by a
-male interaction partner? The current study addresses these questions by
-investigating interpersonal objectification among interacting pairs
-where both partners identify as women.
+The current study uses the face-to-face interaction methodology deployed
+in Garcia et al. (2016) to begin to answer a series of research
+questions about interpersonal objectification among women: Is
+objectification by a female interaction partner related to an increase
+in self-objectification for the woman being objectified? Does
+objectification by a woman have the same downstream negative
+consequences for women as being objectified by a male interaction
+partner? The current study addresses these questions by investigating
+interpersonal objectification among interacting pairs where both
+partners identify as women.
 
@@
 Noll, Quinn, \& Twenge, 1998), or during video chat when you believe
-your interaction partner can only see your body (not face; Saguy, Quinn,
-F Dovidio, \& Pratto, 2010). This momentary self-objectification is
-referred to as \emph{state} self-objectification (SSO; Calogero et al.,
-2011; Moradi \& Huang, 2008) and is characterized by feeling like a body
-rather than a full self within a particular moment, instance, or
-context.
+your interaction partner can only see your body and not your face
+(Saguy, Quinn, Dovidio, \& Pratto, 2010). This momentary
+self-objectification is referred to as \emph{state} self-objectification
+(SSO; Calogero et al., 2011; Moradi \& Huang, 2008) and is characterized
+by feeling like a body rather than a full self within a particular
+moment, instance, or context.
 
@@
 the more they objectify other women. Could the process work in the other
-direction as well, that is, could objectification by a woman produce
+direction as well? That is, could objectification by a woman produce
 (state) self-objectification, in a similar manner to objectification by
@@
 2008; Saguy et al., 2010), however, we do not know much about the effect
-of the gender of the \emph{objectifyer} on these potential detrimental
+of the gender of the \emph{objectifier} on these potential detrimental
 outcomes.
@@
 SIMO. What is clear from Gervais et al. (2020)'s review is that we know
-little about women-on-women interpersonal objectification.
+little about women-on-women interpersonal objectification, in
+unstructured contexts.
 
 Past research has found that the experience of state
-self-objectification in mixed-gender contexts (stranger and romantic;
-Strelan and Pagoudis (2018); Meltzer (2020); Zurbriggen, Ramsey, and
-Jaworski (2011)) has negative consequences for women, but what about in
+self-objectification in mixed-gender contexts (Meltzer, 2020; stranger
+and romantic; Strelan \& Pagoudis, 2018; Zurbriggen, Ramsey, \&
+Jaworski, 2011) has negative consequences for women, but what about in
 the context of interactions with other women? Is the
@@
 particularly detrimental effect for women would suggest no (Calogero,
-2004; Gay \& Castano, 2010; Gervais et al., 2011; Saguy et al., 2010),
-but, there is evidence that women do objectify other women (Harsey \&
-Zurbriggen, 2020; Loughnan et al., 2015; Puvia \& Vaes, 2013) and recent
-experimental evidence suggests that the female gaze causes no less
-self-objectification than the male gaze (Yilmaz \& Bozo, 2019). It would
-be helpful to understand the consequences of this \emph{intra}group
-objectification for women. When women objectify other women, does it
-lead to self-objectification in the same way men's objectification of
-women does (Garcia et al., 2016)? If so, does the self-objectification
-experienced in these same-gender interactions have the same negative
-consequences for authenticity in that interaction?
-
-There is some evidence that reduced authenticity is a consequence of
+2004; Gay \& Castano, 2010; Gervais et al., 2011; Saguy et al., 2010).
+However, there is evidence that women do objectify other women (Harsey
+\& Zurbriggen, 2020; Loughnan et al., 2015; Puvia \& Vaes, 2013) and
+recent experimental evidence suggests that the female gaze causes no
+less self-objectification than the male gaze (Yilmaz \& Bozo, 2019). It
+would be helpful to understand the consequences of this
+\emph{intra}group objectification for women. When women objectify other
+women, does it lead to self-objectification in the same way men's
+objectification of women does (Garcia et al., 2016)?
+
+If so, does the self-objectification experienced in these same-gender
+interactions have the same negative consequences for authenticity in
+that interaction?
+
+One mechanism by which interpersonal objectification translates into
+negative consequences is interaction inauthenticity - when actors feel
+that they are not being their true selves in an interaction. There is
+some evidence that reduced authenticity is a consequence of
 self-objectification (Garcia et al., 2016; Terán, Jiao, \& Aubrey,
@@
 self-objectification on the reduction of relationship building skills in
-general (including same-sex friendships) (Terán et al., 2020).
+general, including same-sex friendships (Terán et al., 2020).
 Authenticity reduction and interaction quality disruptions have also
@@
 manifests through authenticity in romantic relationships (Brunell et
-al., 2010), an intergroup context at least in heterosexual
-relationships. Evidence for other adverse consequences of interpersonal
-objectification include reductions in career aspirations (Garcia et al.,
-2016) and a decrease in concentration and impairment in female cognitive
-performance (Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn, Chaudoir,
-\& Kallen, 2011). These are also negative consequences found for women
-under stereotype threat (Davies, Spencer, \& Steele, 2005). When a woman
-is objectified by a man, and subsequently experiences
-self-objectification, the intergroup nature and power differential of
-this encounter might trigger threat. Thus, perhaps there are fewer
-negative consequences when a woman is objectified by another woman. That
-is, the intergroup threat literature might predict that woman-woman
-interpersonal objectification processes diverge from mixed-gender
-interpersonal objectification processes precisely because they are not
-intergroup interactions (at least with respect to gender identity).
+al., 2010), at least in an intergroup context such as heterosexual
+romantic relationships. Evidence for other adverse consequences of
+interpersonal objectification include reductions in career aspirations
+(Garcia et al., 2016) and a decrease in concentration and impairment in
+female cognitive performance (Kahalon, Shnabel, \& Becker, 2018; D. M.
+Quinn, Chaudoir, \& Kallen, 2011). These are also negative consequences
+found for women under stereotype threat (Davies, Spencer, \& Steele,
+2005; Spencer, Steele, \& Quinn, 1999). When a woman is objectified by a
+man, and subsequently experiences self-objectification, the intergroup
+nature and power differential of this encounter might trigger threat.
+Thus, me might expect there to fewer negative consequences when a woman
+is objectified by another woman. That is, the intergroup threat
+literature might predict that woman-woman interpersonal objectification
+processes diverge from mixed-gender interpersonal objectification
+processes precisely because they are not intergroup interactions, at
+least with respect to gender identity.
 
@@
 women's feelings of authenticity and social competence, regardless of
-the gender of the objectifyer (Terán et al., 2020; Tolman, Impett,
+the gender of the objectifier (Terán et al., 2020; Tolman, Impett,
 Tracy, \& Michael, 2006).
@@
 In the current study, we sought to examine what occurs during an
-interaction in which one or both partners are objectifying each other,
-similarly to Garcia et al. (2016), but between same-gender interpersonal
-interactions among women. Moreover, the current study uses a
-face-to-face interaction paradigm and dyadic data analysis techniques to
+interaction in which one or both partners are potentially objectifying
+each other and where both interaction partners identify as women.
+Moreover, the current study used the same face-to-face interaction
+paradigm as Garcia et al. (2016) and dyadic data analysis techniques to
 examine the relationships for both women simultaneously. Although the
 literature on intragroup objectification among women is small, the
-results are mixed, and they do not cover interpersonal encounters, we
-expected to replicate some of the results found in Garcia et al. (2016).
-Most importantly, we predicted that being objectified by one's
-interaction partner would be related to state self-objectification
+results are mixed, and they do not cover actual interpersonal
+encounters, we expected to replicate some of the results found in Garcia
+et al. (2016). Most importantly, we predicted that being objectified by
+one's interaction partner would be related to state self-objectification
 (SSO). We also expected that TSO would moderate this relationship,
@@
 self-objectification and the evaluation of other women in a sexualized
-way. The decision was made to ask even heterosexual women to judge their
-fellow-woman partners for their potential as romantic partners. We felt
-that this prompt would keep the study closest to a replication of the
-previous Garcia et al. (2016) version of the study, and strengthen the
-potential for objectification that would normally be low in the context
-of a psychology laboratory. Recall that, past research has found that
+way. The decision was made to ask all women participating in the study,
+even heterosexual women, to judge their fellow-woman partners for their
+potential as romantic partners. We felt that this prompt would keep the
+study closest to a replication (and extension) of the previous Garcia et
+al. (2016) version of the study, and strengthen the potential for
+objectification that would normally be low in the context of a
+psychology laboratory. Recall that, past research has found that
 heterosexual women are indeed able to evaluate other women's potential
-as romantic partners (i.e., their sexual attractiveness; Puvia \& Vaes,
-2013)---women may be unfortunately quite used to thinking about their
-own \enquote{datability,} and we suspect this this habitual thought
-pattern will translate to their thoughts about other women. Analyses
-comparing levels of other-objectification between heterosexual and
-non-heterosexual women are provided in the measures section below.
+as romantic partners, specifically, their sexual attractiveness (Puvia
+\& Vaes, 2013). Women may be unfortunately quite used to thinking about
+their own \enquote{datability,} and we suspected that this habitual
+thought pattern would translate to their thoughts about other women.
+Analyses comparing levels of other-objectification between heterosexual
+and non-heterosexual women are provided in the measures section below.
 
@@
 \bottomrule
+\addlinespace
 \end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} * p < .05. ** p < .01.}
+\end{tablenotes}
 \end{threeparttable}
@@
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:measures}Measures}
-\begin{tabular}{lllll}
+\begin{lltable}
+
+\small{
+\begin{longtable}{lllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:measures}Measures}\\
 \toprule
@@
 \bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
+\end{longtable}
+}
+\end{lltable}
 
@@
 participants in the current study. For more details about each of these
-measures please see that previous paper. To summarize, the list of
-measures in the order given to participants appears in
-Table~\ref{tab:measures} along side the orginal source for the scale, an
-example item, and the reliability in the current sample. Correlations
+measures please refer to that previous paper. To summarize here, the
+list of measures in the order given to participants appears in
+Table~\ref{tab:measures} along side the original source for each scale,
+an example item, and the reliability in the current sample. Correlations
 and descriptive statistics of all study variables appear in
@@
 
-Cognitive performance with the Remote Associates Task's trigrams
-(McFarlin \& Blascovich, 1984) was given first, to capture any
-attentional changes that may have been affected by the interaction. Next
-participants were given a set of measure about their thoughts and
-feelings during the interaction that included State-Other
-Objectification, Interaction Authenticity, and State
-Self-Objectification. Following these measures participants completed
-the Relationship Agency Scale and the Career Aspirations Scale. Lastly,
-as was the case in Garcia et al. (2016), Trait Self-Objectification was
-given last, as not to arouse suspicious at the start of the study that
-we were actually focusing on objectification and to give enough time
-that immediate effects of the interaction would have worn off.
+Cognitive performance as measured with the Remote Associates Task's
+trigrams (McFarlin \& Blascovich, 1984) was given first after the
+interaction to capture any immediate cognitive effects of the
+interaction. Next participants were given a set of self-report measures
+about their thoughts and feelings during the interaction that included
+State-Other Objectification, Interaction Authenticity, and State
+Self-Objectification. Breaking from the Garcia et al. (2016)
+methodology, we used a three item state self-objectification scale as
+originally given in Saguy et al. (2010), but in both samples the
+reliability of the scale was higher once the third item was removed, so
+we chose to only use the first two items for our measure of SSO.
+Following these interaction measures, participants completed the
+Relationship Agency Scale and the Career Aspirations Scale. The
+Relationship agency scale originally had 9 items, but the 9th item had
+low correlations with the remaining items so it was trimmed. As a
+result, the 8-item scale had moderately high reliability for both
+samples (see Table~\ref{tab:measures}). Lastly, as was the case in
+Garcia et al. (2016), Trait Self-Objectification was given last, as not
+to arouse suspicious at the start of the study that we were actually
+focusing on objectification and to give enough time that immediate
+effects of the interaction would have worn off.
 
@@
 significant, \emph{t}(25.89) = 1.02, \emph{p =} 0.32.
-
-Howbody used 3 items, but in both samples the reliability of the scale
-was higher once the third item was removed, so we chose to only use the
-first two for our measure of SSO, leaving us with a reliable scale (see
-Table~\ref{tab:measures}).
-
-Relationship agency The scale originally had 9 items, but the 9th item
-had low correlations with the remaining items, ranging from .02 to .30
-for the first sample, and .04 to .30 for the second sample. Therefore,
-this item was removed. As a result, the 8-item scale had moderately high
-reliability for both samples (see Table~\ref{tab:measures}).
 
@@
 Model (APIM) approach for each outcome variable. See
-Figure~\ref{fig:apim} for a basic APIM model. The APIM includes effects
-due to one's own, as well as one's partner's, predictor variables
-(\(X\)'s) on the one's own outcome variable (\(Y\)). The current study
-deals with indistinguishable dyads, meaning the designation of who is
-the \enquote{actor} and who is the \enquote{partner} is arbitrary. In
-total we ran five APIM's---one for each outcome variable---to test the
-series of the relationships proposed (i.e., for SSO, inauthenticity,
-career aspirations, relationship agency, and cognitive performance).
+Figure~\ref{fig:apim} for a basic APIM model. The APIM estimates effects
+due to one's own, as well as one's partner's, predictor variables on the
+one's own outcome variable. The current study deals with
+indistinguishable dyads, meaning the designation of who is the
+\enquote{actor} and who is the \enquote{partner} is arbitrary. In total
+we ran five APIM's---one for each outcome variable---to test the series
+of the relationships proposed (i.e., for SSO, inauthenticity, career
+aspirations, relationship agency, and cognitive performance).
 
@@
 
-First, use used to the APIM to test for evidence of a partner effect of
+First, we used the APIM to test for evidence of a partner effect of
 other objectification and SSO in this sample of same-gender woman-woman
@@
 statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12, \emph{p} =
-.019. That is, the extent to which one's partner reported thinking about
-a woman's external characteristics more than her internal
-characteristics was significantly related to the woman's own reported
-feeling more like a body than a full self. Along side the Garcia et al.
-(2016) study, there is now evidence that interpersonal objectification
-in an actual interpersonal encounter is related to state
-self-objectification for women both when the objectifyer is a man and
-when the objectifyer is a woman.
+.019, \emph{95\%CI} = {[}0.06, 0.53{]}. That is, the extent to which
+one's partner reported thinking about a woman's external characteristics
+more than her internal characteristics was significantly related to the
+woman's own reported feeling more like a body than a full self. Along
+side the Garcia et al. (2016) study, there is now evidence that
+interpersonal objectification in an actual interpersonal encounter is
+related to state self-objectification for women both when the
+objectifier is a man and when the objectifier is a woman.
 
@@
 other-objectification), \emph{b} = -0.16, \emph{SE} = 0.12, \emph{p} =
-.210. Further, inconsistent with past findings, there was no
-statistically significant interaction of partner's other objectification
-and the person's trait self-objectification on SSO, \emph{b} = 0.03,
-\emph{SE} = 0.27, \emph{p} = .910. There was also no significant main
-effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
-0.05, \emph{p} = .183. The \(R^2\) of this model (which includes the
-partner effect of other-objectification discussed in the previous
-paragraph) was only 0.03.
+.210, \emph{95\%CI} = {[}-0.4, 0.09{]}. Further, inconsistent with past
+findings, there was no statistically significant interaction of
+partner's other objectification and the person's trait
+self-objectification on SSO, \emph{b} = 0.03, \emph{SE} = 0.27, \emph{p}
+= .910, \emph{95\%CI} = {[}-0.5, 0.56{]}. There was also no significant
+main effect of trait self-objectification on SSO \emph{b} = 0.07,
+\emph{SE} = 0.05, \emph{p} = .183, \emph{95\%CI} = {[}-0.03, 0.17{]}.
+The \(R^2\) of this model (which includes the partner effect of
+other-objectification discussed in the previous paragraph) was only
+0.03.
 
@@
 relationship between these two variables, \emph{b} = 0.09, \emph{SE} =
-0.06, \emph{p} = .133. We also ran a model with both TSO and SSO
-predicting other-objectification, given past theorizing that state
-self-objectification might mediate the relationship between TSO and
-objectification of fellow women, but there was also no effect of SSO on
-other-objectification in this model, \emph{b} = -0.17, \emph{SE} = 0.13,
-\emph{p} = .199.
+0.06, \emph{p} = .133, \emph{95\%CI} = {[}-0.03, 0.2{]}. We also ran a
+model with both TSO and SSO predicting other-objectification, given past
+theorizing that state self-objectification might mediate the
+relationship between TSO and objectification of fellow women, but there
+was also no effect of SSO on other-objectification in this model,
+\emph{b} = -0.17, \emph{SE} = 0.13, \emph{p} = .199, \emph{95\%CI} =
+{[}-0.42, 0.08{]}.
 
@@
 hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12,
-\emph{p} = .431. Because authenticity was a composite score of 9 items,
-two of which were interaction specific authenticity items, we also
-estimated the pairwise correlations between SSO and all these items
-individually. They were all small, ranging from only -0.01 to -0.14.
-Although we hypothesized that SSO would mediate the relationship between
-partner's other objectification and interaction authenticity, after
-finding no relationship between SSO and authenticity, we also tested if
-the partner's other objectification had a direct effect on authenticity,
-but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
-\emph{p} = .608 (nor was the total effect of partner's other
+\emph{p} = .431, \emph{95\%CI} = {[}-0.32, 0.14{]}. Because authenticity
+was a composite score of 9 items, two of which were interaction specific
+authenticity items, we also estimated the pairwise correlations between
+SSO and all these items individually. They were all small, ranging from
+only -0.01 to -0.14. Although we hypothesized that SSO would mediate the
+relationship between partner's other objectification and interaction
+authenticity, after finding no relationship between SSO and
+authenticity, we also tested if the partner's other objectification had
+a direct effect on authenticity, but this effect was not significant,
+\emph{b} = 0.06, \emph{SE} = 0.12, \emph{p} = .608, \emph{95\%CI} =
+{[}-0.17, 0.29{]} (nor was the total effect of partner's other
 objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11,
-\emph{p} = .787). Note that these analyses of the relationship between
-SSO and inauthenticity in this same-gender sample were considered
-exploratory, given that prior research on intragroup interactions points
-to mixed possibilities.
+\emph{p} = .787, \emph{95\%CI} = {[}-0.19, 0.25{]}). Note that these
+analyses of the relationship between SSO and inauthenticity in this
+same-gender sample were considered exploratory, given that prior
+research on intragroup interactions points to mixed possibilities.
 
@@
 significant effect of interaction authenticity on cognitive performance,
-\emph{b} = 0.32, \emph{SE} = 0.28, \emph{p} = .258, but authenticity was
-significantly positively related to both career aspirations, \emph{b} =
-0.18, \emph{SE} = 0.07, \emph{p} = .010 (\(R^2 =\) 0.04), and
-relationship agency, \emph{b} = 0.23, \emph{SE} = 0.12, \emph{p} = .049
-(\(R^2 =\) 0.01).
+\emph{b} = 0.32, \emph{SE} = 0.28, \emph{p} = .258, \emph{95\%CI} =
+{[}-0.23, 0.86{]}, but authenticity was significantly positively related
+to both career aspirations, \emph{b} = 0.18, \emph{SE} = 0.07, \emph{p}
+= .010, \emph{95\%CI} = {[}0.05, 0.32{]} (\(R^2 =\) 0.04), and
+relationship agency, \emph{b} = 0.23, \emph{SE} = 0.12, \emph{p} = .049,
+\emph{95\%CI} = {[}0.01, 0.46{]} (\(R^2 =\) 0.01).
 
@@
 al., 2015; Puvia \& Vaes, 2013), this is the first study to test if
-\emph{interpersonal} other-objectification by women during actual
+interpersonal other-objectification by women during \emph{actual}
 interactions is related to state self-objectification in their
@@
 \emph{women's} state self-objectification that relates to being
-objectified by one's partner---men partners (Garcia et al., 2016) and
-now women partners. Objectification Theory (Fredrickson \& Roberts,
-1997), as well as some past experimental studies (for example, Saguy et
-al., 2010), suggest that the causal flow is from other-objectification
-to SSO. Other studies, especially those investigating explicitly women
-objectifying other women (Puvia \& Vaes, 2013), have relatedly found
-evidence that women's \emph{trait} self-objectification is related to
-women objectifying (dehumanizing) other women and this link is mediated
-by \emph{state} self-objectification. The process of interpersonal
-objectification among women could also contain a feedback loop. That is,
-perhaps we tend to objectify other women who objectify us and through a
-process of TSO causing SSO which in turn causes objectification of one's
-partner, which in turn causes one's partner to objectify us. However,
-the current study does not provide any evidence of the TSO to
-other-objectification link---TSO was not significantly correlated with
-SSO and, further, actor's other-objectification was not correlated with
-partner's other-objectification.
+objectified by one's partner---men-identifying partners (Garcia et al.,
+2016) and now women-identifying partners. Objectification Theory
+(Fredrickson \& Roberts, 1997), as well as some past experimental
+studies (for example, Saguy et al., 2010), suggest that the causal flow
+is from other-objectification to SSO. However, some studies
+investigating women objectifying other women (Puvia \& Vaes, 2013), have
+found evidence that women's \emph{trait} self-objectification is related
+to women objectifying (dehumanizing) other women and this link is
+mediated by \emph{state} self-objectification. The process of
+interpersonal objectification among women could also very well contain a
+feedback loop. That is, perhaps we tend to objectify other women who are
+objectifying us. Then, if there indeed tends to be reciprocity in sexual
+objectification among women, a vicious cycle could ensue through a
+process of TSO causing SSO which in turn causes other-objectification of
+one's partner, which in turn causes one's partner to objectify us, and
+finally, being objectified further increases our own SSO. However, the
+current study does not provide any evidence of the TSO to
+other-objectification link (through SSO or directly)---TSO was not
+significantly correlated with SSO. Further, actor's
+other-objectification was not correlated with partner's
+other-objectification in the current sample. Future experimental work
+testing if sexual objectification by a woman can cause an increase in a
+woman's state self-objectification would be helpful.
 
@@
 mixed-gender dyads is the lack of evidence for relationships between SSO
-and interaction inauthenticity. This is somewhat surprising given the
-extant evidence linking SSO and cognitive functioning (B. L. Fredrickson
-et al., 1998; and see Moradi \& Huang, 2008 for a review; Quinn,
-Chaudoir, \& Kallen, 2011) and the research on interpersonal
-other-objectification and cognitive functioning (Garcia et al., 2016;
-Gervais et al., 2011; Logel et al., 2009). This lack of evidence could
-potentially signal diverging processes between women's experiences with
-interpersonal objectification from men and interpersonal objectification
-from women. There is quite a bit of evidence suggesting that the male
-gaze is particularly detrimental (Calogero, 2004; Fredrickson \&
-Roberts, 1997; Gervais et al., 2011), and perhaps the
-self-objectification experienced within an interaction with a women is
-qualitatively different, and perhaps not as harmful, as the state
-self-objectification experienced within an interaction with a man.
-However, as a strong note of caution, it is best not to interpret a null
-result as evidence of no relationship and more research on interpersonal
+and interaction inauthenticity (and, in turn, cognitive functioning).
+This is somewhat surprising given the extant evidence linking SSO and
+cognitive functioning (B. L. Fredrickson et al., 1998; and see Moradi \&
+Huang, 2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the
+research on interpersonal other-objectification and cognitive
+functioning (Garcia et al., 2016; Gervais et al., 2011; Logel et al.,
+2009). This lack of evidence could potentially signal diverging
+processes between women's experiences with interpersonal objectification
+from men and interpersonal objectification from women. There is quite a
+bit of evidence suggesting that the male gaze is particularly
+detrimental (Calogero, 2004; Fredrickson \& Roberts, 1997; Gervais et
+al., 2011) for women, and perhaps the self-objectification experienced
+within an interaction with a women is qualitatively different from the
+state self-objectification experienced within an interaction with a man.
+However, as a strong note of caution, we cannot interpret a null result
+as evidence of no relationship and more research on interpersonal
 objectification among women is needed.
@@
 authenticity is surprising and again, should not be interpreted as
-evidence of no relationship. It should be noted that the estimate of
-this relationship was small (close to zero), but in the negative
-direction. If it is the case that there is a smaller (i.e., weaker) or
-zero connection between women's feelings of SSO and inauthenticity in
-interactions with other women than in interactions with men, models of
-interpersonal objectification, like the SIMO (Gervais et al., 2020),
-could be extended by including gender of the objectifyer/interaction
-partner as a moderator. Inauthenticity could be added as a potential
-moderated mediating factor to help understand the circumstances that
-require other-objectification and SSO to have negative consequences for
-women. Perhaps one important difference is the lack of a power
-differential across gendered lines -- the patriarchal culture is
-present, but the interaction partners are not a stigmatizer-stigmatized
-pair.
+evidence of no relationship. The estimate of this relationship was small
+(close to zero), but in the negative direction. If perhaps it is the
+case that there is a smaller (i.e., weaker) or zero connection between
+women's feelings of SSO and inauthenticity in interactions with other
+women than in interactions with men, models of interpersonal
+objectification, like the SIMO (Gervais et al., 2020), could be extended
+by including gender of the objectifier/interaction partner as a
+moderator. Inauthenticity could be added as a potential moderated
+mediating factor to help understand the circumstances that require
+other-objectification and SSO to have negative consequences for women.
+Perhaps one important difference is the lack of a power differential
+across gendered lines---the patriarchal culture is present, but the
+interaction partners are not a stigmatizer-stigmatized pair in
+interpersonal objectification encounters among women. Lastly, This
+theoretical work on intragroup sexual objectification among women could
+potentially benefit from making connections to the small but growing
+literature investigating same-race racial minority interactions (Garcia,
+Bergsieker, \& Shelton, 2017; Taylor, Garcia, Shelton, \& Yantis, 2018).
 
@@
 aspirations. The relationship between authenticity and cognitive
-functioning was also estimated as positive, but was not statistically
-significant. Again, due to the lack of connection between SSO and
-authenticity, we found no evidence of \emph{indirect} relationships
-between SSO and these outcome variables. This evidence of a relationship
-between authenticity and the relational outcome variables (i.e.,
-relationship agency and career aspirations) provides evidence that
-corroborates past findings that felt authenticity in interactions is
-important for healthy relationship functioning (Garcia et al., 2016;
+functioning was estimated as positive (the point estimate), but was not
+statistically significant. Again, due to the lack of connection between
+SSO and authenticity, we found no evidence of \emph{indirect}
+relationships between SSO and these outcome variables. This evidence of
+a relationship between authenticity and the relational outcome variables
+(i.e., relationship agency and career aspirations) provides evidence
+that corroborates past findings that felt authenticity in interactions
+is important for healthy relationship functioning (Garcia et al., 2016;
 Terán et al., 2020) and is related to mental health correlates (Tolman
@@
 find more evidence here that disruptions in feelings of authenticity can
-negatively impact relationships beyond the current partner. Although the
-current study did not find a connection between authenticity and SSO,
-this seems theoretically to be a natural connection, and future work
-must explore when and how SSO leads to inauthenticity in interpersonal
-objectification situations.
+negatively impact relationships beyond the current interaction partner.
+Although the current study did not find a connection between
+authenticity and SSO, this seems to us to remain a theoretically viable
+connection, and future work must explore when and how SSO leads to
+inauthenticity in interpersonal objectification situations.
 
@@
 
-In addition to being relatively small and combined across two
-institutions, another limitation of the current study sample is that the
-it was comprised of Western women only. Being that self-objectification
-has been found to be most prevalent in Western culture (Loughnan et al.,
-2015) research on objectification {[}{[}{[}conducted outside of Western
-or Westernized countries{]}{]}{]} has been scarce (Moradi \& Huang,
-2008), although more recent work has examined objectification from a
-cross-cultural framework (Loughnan et al., 2015, Wollast et al. (2020)).
-{[}{[}{[}Since \enquote{bodies exist within social and cultural
-contexts, and hence are also constructed through sociocultural practices
-and discourses}{]}{]}{]} (Fredrickson \& Roberts, 1997, p. 174), it is
-important to consider how diverse social identities within unique
-cultural contexts may inform sexual objectification phenomenon
-{[}{[}{[}to test the cross-cultural applicability of theoretical
-frameworks{]}{]}{]} (Loughnan et al., 2015).
+Although the sample size was relatively small, due to the difficulty in
+collecting data on actual interpersonal encounters, we believe that the
+results from the current analyses are important and push work in
+interpersonal objectification forward in an important way. Of course,
+more data is better, especially for evaluating null results. Follow-up
+studies investigating interpersonal objectification among women are
+necessary and should strive for larger samples. In addition to being
+relatively small and combined across two institutions, another
+limitation of the current study sample is that the it was comprised of
+mostly women from Western cultures. Being that self-objectification has
+been found to be most prevalent in Western culture (Loughnan et al.,
+2015), research on objectification that includes people from non-Western
+cultures has been scarce (Moradi \& Huang, 2008), although more recent
+work has examined objectification from a cross-cultural framework
+(Loughnan et al., 2015; Wollast et al., 2020).
 
 Further, sexualizing experiences and self-objectification are thought to
-begin a very young age, and thus, researchers have only recently begun
-to examine such experiences among children (e.g., Holland \& Haslam,
-2016; Jongenelis, Byrne, \& Pettigrew, 2014). {[}{[}Considering the fact
-that the average mean age of the investigated participants of this
-current study was 18.85 years, research among younger and older
-individuals is needed{]}{]}{]}, especially because the processes of
-self-objectification may change over time (Fredrickson \& Roberts,
-1997). {[}{[}{[}It may be valuable to question the extent to which
-children, adolescents, or emerging adults of different races or
-ethnicities are exposed to varied amounts of sexualizing
-content.{]}{]}{]} Further, more longitudinal studies investigating the
-developmental experience of interpersonal objectification and
-self-objectification are needed.
-
-\subsubsection{Interpersonal Sexual Objectification, Gender, and Sexual
-Attraction}\label{interpersonal-sexual-objectification-gender-and-sexual-attraction}
-
-The current sample contained a mixture of heterosexual and
+begin a very young age, but researchers have only recently begun to
+examine such experiences among children (e.g., Holland \& Haslam, 2016;
+Jongenelis, Byrne, \& Pettigrew, 2014). The mean age of the current
+sample was 18.85 years, a young adult sample, limiting the
+generalizability of our results to this age group. More longitudinal
+studies investigating the developmental experience of interpersonal
+objectification and self-objectification are recommended, especially
+because the processes of self-objectification have been found to unfold
+between the periods of adolescence and young adulthood (Vangeel,
+Vandenbosch, \& Eggermont, 2018).
+
+The current sample contained a mixture of both heterosexual and
 non-heterosexual women, but all participants were asked to think about
 and evaluate their partner as a potential dating/romantic partner. We
-think that heterosexual women are able to do this with other women as
-their target---and there is evidence that they might do this readily
-(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---perhaps they may be
-even more apt to activate social comparison processes (Festinger, 1954)
-than women who are sexually attracted to other women (non-heterosexual
-women). {[}{[}{[}Indeed, recent research has found that the more women
-self-objectify, the more they objectify other women{]}{]}{]} (Loughnan
-et al., 2015; Puvia \& Vaes, 2013), {[}{[}{[}although not to the degree
-exhibited by men; that is, men were found to objectify women
-significantly more than women objectify other women{]}{]}{]} (Strelan \&
-Hargreaves, 2005). This differential psychological process between women
-with differing sexualities might have served to dampen our ability to
-detect relationships.
-
-\subsubsection{Sexism and Sexual
-Discrimination}\label{sexism-and-sexual-discrimination}
-
-Sexism has been found to be related to the objectification of women, but
-not men (Cikara, Eberhardt, \& Fiske, 2011; Harsey \& Zurbriggen, 2020),
-and in addition, TSO has been found to be associated with less negative
-attitudes towards sexual harassment (Bernard, Legrand, \& Klein, 2018).
-Both of these effects are present for both men and women. Empirical
-evidence illustrates how women continue to be objects of interpersonal
-discrimination and experience daily sexist hassles (Swim, Hyers, Cohen,
-\& Ferguson, 2001). One form of interpersonal discrimination women face
-is the process by which their whole being is viewed as a collection of
-sexualized body parts valued predominantly for commodification, a
-phenomena termed sexual objectification (Bartky, 1990). Sexual
-objectification of women has also been linked to trauma (Miles-McLean et
-al., 2015). Sexual objectification occurs in a myriad of ways in women's
-lives and is modified by unique combinations of race, ethnicity,
-sexuality, age, and class (Fredrickson \& Roberts, 1997). Amid such
-heterogeneity though, \enquote{having a reproductively mature female
-body} proposed by Fredrickson and Roberts (1997) is likely to create a
-shared vulnerability to sexual objectification and a variety of shared
-negative experiences as a result.
+think that the heterosexual women in our sample were able to do this
+with other women as their target---indeed, there is evidence that they
+might do this readily (Puvia \& Vaes, 2013; Strelan \& Hargreaves,
+2005)---but, perhaps they may be even more apt to activate social
+comparison processes (Festinger, 1954) than women who are sexually
+attracted to other women (non-heterosexual women). Social comparison
+processes have been linked to self-objectification and negative body
+image among women in general (Lindner, Tantleff-Dunn, \& Jentsch, 2012;
+Tylka \& Sabik, 2010) and, more recently, specifically with regard to
+consumption of social media site content (Feltman \& Szymanski, 2018;
+Fox \& Vendemia, 2016; Hanna et al., 2017). However, these none of these
+social comparison studies compared heterosexual women to
+non-heterosexual women. If it is the case that there are two
+differential psychological processes between heterosexual and lesbian
+women at play, this added variance might have served to dampen our
+ability to detect the proposed relationships between study variables.
+
+An additional issue with including both heterosexual and lesbian women
+in the sample is that the interpersonal encounter in the current study
+was experience as a potentially romantic context for some and as a
+strictly platonic context for others. Interpersonal sexual
+objectification has been studied in both romantic and platonic contexts.
+Among heterosexual male and female college students,
+self-objectification has been found to be positively associated with the
+extent to which they objectify their romantic partners (Zurbriggen et
+al., 2011). Evidence is the romantic context is mixed, suggesting that
+women can sometimes have positive outcomes from appearance valuation
+within the context of an established romantic relationship. There is
+also evidence that they experience less SSO after appearance comments
+within established romantic relationships (Meltzer, 2020). Less is known
+about first dates and there is little research on objectification
+processes in lesbian relationships specifically. Further,
+objectification might also occur among platonic friends: Perhaps women
+could be amplifying each others' state self-objectification
+\emph{before} the theoretical encounters with men, and the processes
+organized in the SIMO, occur.
 
@@
 
-The results of this study \ldots{} and additionally highlight the
-psychological and social consequences of such objectification processes
-on women's social relationships and well-being. These results are quite
-useful for promoting mental health, the creation and maintenance of
-early action programs for girls and young women, and for scholars and
-practitioners to work intentionally to provide the tools necessary to
-circumvent or mitigate negative effects on self-objectification to
-combat such experiences.
+To the best of our knowledge, this was the first study to test the
+relationship between objectification and self-objectification within
+actual interpersonal interactions among women. The results of this study
+replicated the partner effect of other-objectification on state
+self-objectification found in Garcia et al. (2016) in a sample of
+same-gender pairs all identifying as women. That is, the more a woman's
+female interaction partner reported having objectified her, the more she
+reported a state of self-objectification during the interaction. Unlike
+past research finding that trait self-objectification moderated this
+relationship, we did not find any evidence of such an effect. Further,
+we did not find that inauthenticity was an important mediating factor
+between self-objectification and the negative psychological and social
+consequences for women objectified by women, as was the case in past
+studies on interpersonal objectification of women by men. Further
+research should be conducted with larger samples that investigate
+interpersonal objecticiation among women and compare these processes to
+parallel processes among mixed-gender dyads.
 
@@
 
+\hypertarget{ref-feltman2018instagram}{}
+Feltman, C. E., \& Szymanski, D. M. (2018). Instagram use and
+self-objectification: The roles of internalization, comparison,
+appearance commentary, and feminism. \emph{Sex Roles}, \emph{78}(5-6),
+311--324.
+
 \hypertarget{ref-festinger1954theory}{}
@@
 \emph{Human Relations}, \emph{7}(2), 117--140.
+
+\hypertarget{ref-fox2016selective}{}
+Fox, J., \& Vendemia, M. A. (2016). Selective self-presentation and
+social comparison through photographs on social networking sites.
+\emph{Cyberpsychology, Behavior, and Social Networking}, \emph{19}(10),
+593--600.
 
@@
 
+\hypertarget{ref-garcia2017racial}{}
+Garcia, R. L., Bergsieker, H. B., \& Shelton, J. N. (2017). Racial
+attitude (dis) similarity and liking in same-race minority interactions.
+\emph{Group Processes \& Intergroup Relations}, \emph{20}(4), 501--518.
+
 \hypertarget{ref-garcia2016objectification}{}
@@
 
+\hypertarget{ref-hanna2017contributions}{}
+Hanna, E., Ward, L. M., Seabrook, R. C., Jerald, M., Reed, L.,
+Giaccardi, S., \& Lippman, J. R. (2017). Contributions of social
+comparison and self-objectification in mediating associations between
+facebook use and emergent adults' psychological well-being.
+\emph{Cyberpsychology, Behavior, and Social Networking}, \emph{20}(3),
+172--179.
+
 \hypertarget{ref-harsey2020men}{}
@@
 
+\hypertarget{ref-lindner2012social}{}
+Lindner, D., Tantleff-Dunn, S., \& Jentsch, F. (2012). Social comparison
+and the ``circle of objectification''. \emph{Sex Roles}, \emph{67}(3-4),
+222--235.
+
 \hypertarget{ref-logel2009interacting}{}
@@
 \hypertarget{ref-saguyetal2010}{}
-Saguy, T., Quinn, D., F Dovidio, J., \& Pratto, F. (2010). Interacting
+Saguy, T., Quinn, D., Dovidio, J., \& Pratto, F. (2010). Interacting
 like a body: Objectification can lead women to narrow their presence in
@@
 
+\hypertarget{ref-spencer1999stereotype}{}
+Spencer, S. J., Steele, C. M., \& Quinn, D. M. (1999). Stereotype threat
+and women's math performance. \emph{Journal of Experimental Social
+Psychology}, \emph{35}(1), 4--28.
+
 \hypertarget{ref-R-apaTables}{}
@@
 
-\hypertarget{ref-swimetal}{}
-Swim, J. K., Hyers, L. L., Cohen, L. L., \& Ferguson, M. J. (2001).
-Everyday sexism: Evidence for its incidence, nature, and psychological
-impact from three daily diary studies. \emph{Journal of Social Issues},
-\emph{57}(1), 31--53.
-doi:\href{https://doi.org/10.1111/0022-4537.00200}{10.1111/0022-4537.00200}
+\hypertarget{ref-taylor2018threat}{}
+Taylor, V. J., Garcia, R. L., Shelton, J. N., \& Yantis, C. (2018). ``A
+threat on the ground'': The consequences of witnessing
+stereotype-confirming ingroup members in interracial interactions.
+\emph{Cultural Diversity and Ethnic Minority Psychology}, \emph{24}(3),
+319.
 
@@
 
+\hypertarget{ref-tylka2010integrating}{}
+Tylka, T. L., \& Sabik, N. J. (2010). Integrating social comparison
+theory and self-esteem within objectification theory to predict women's
+disordered eating. \emph{Sex Roles}, \emph{63}(1-2), 18--31.
+
+\hypertarget{ref-vangeel2018multidimensional}{}
+Vangeel, L., Vandenbosch, L., \& Eggermont, S. (2018). The
+multidimensional self-objectification process from adolescence to
+emerging adulthood. \emph{Body Image}, \emph{26}, 60--69.
+
 \hypertarget{ref-R-tidyverse}{}
